### 2019-12-15 algo/ask01.tex
Algorithms: Added ask01 tex file

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}
\setlength{\parskip}{1em}

\newcommand\nlambda[1]{\ensuremath{\lambda #1.\,}}
\newcommand\nred{\ensuremath{\longrightarrow}}

% Main document
\begin{document}
\title{Αλγόριθμοι - 1η Σειρά Ασκήσεων}
\author{Θωμάς Παππάς}
\date{12 Νοεμβρίου 2019}
\maketitle
\begin{center}ΑΜ: AL1180011\end{center}

\section*{Ασκηση 1}
(α) Η σειρά κατάταξης είναι:
\begin{center}
\begin{tabular}{ c c c c }
$\sum_{k=1}^nk2^{-k}$ & $\log{(n!)}/(\log{n})^3$ & $n2^{2^{2^{100}}}$ & $\log{2n\choose n}$ \\
$2^{(\log_2n)^4}$ & $(\sqrt{n})!$ & $n\sum_{k=0}^n{n\choose k}$ & $\sum_{k=1}^nk2^k$ \\
\end{tabular}
\end{center}
όπου $n\sum_{k=0}^n{n\choose k} = \sum_{k=1}^nk2^k = \Theta(n2^n)$, αφού $n\sum_{k=0}^n{n\choose k} = n\sum_{k=1}^n(1+1)^n = n2^n$

%\section*{Άσκηση 2}
%
%(α) Ο ακόλουθος αλγόριθμος υπολογίζει την ελάχιστην τιμή της παράστασης $|A_1[i_1]-A_2[i_2]|$.
%
%\begin{verbatim}
%function getMinDist(array a1, array a2):
%  if a1[0] > a2[0]:
%    inverseResult = getMinDist(a2, a1);
%    return (inverseResult[1], inverseResult[0]);
%
%  int i = 0;
%  int j = 0;
%  while a1[i] =< a2[j]:
%    if (a1[i] == a2[j]:
%      return (i,j);
%    j++;
%\end{verbatim}
%
%Ο αλγόριθμος \verb|getMinDist| χρεάζεται

\section*{Άσκηση 3}
1. Ο αλγόριθμος \verb|minifyStacks| που ελαχιστοποιεί το πλήθος των στοιβών που δημιουργούνται κατά τη διάρκεια του παιχνιδιού είναι ο εξής:\\
Πρώτα θα κρατήσουμε τις κορυφές της κάθε στοίβας σε ένα δυαδικό δέντρο \verb|topCardTree|. Κάθε φορά που θα τραβάμε μια κάρτα \verb|card| κάνουμε δυαδική αναζήτηση στο δέντρο και βρίσκουμε θέση \verb|i| τέτοια ώστε \verb|topCardTree[i] < card < topCardTree[i+1]|. Αντικαθιστούμε το \verb|topCardTree[i+1]| με την τιμή \verb|card|. Εάν το στοιχείο δεν υπάρχει στο δέντρο (δηλαδή η κάρτα έχει μεγαλύτερη τιμή από κάθε στήλη) τότε δημιουργούμε μια νέα στοίβα και προσθέτουμε ένα κλαδί στο \verb|topCardTree|.

\begin{verbatim}
function minifyStacks(stack deck):
  stacks = new stack[]
  topCardTree = new BinaryTree()

  index = 0
  while deck.length > 0:
    card = deck[index].pop()
    i = topCardTree.binarySearch(card).getLowerIndex()
    if topCardTree[i+1]:
      stacks[i].push(card)
      topCardTree[i+1] = card
    else:
      stacks.append(new stack({}))
      topCardTree.add(card)
\end{verbatim}

Η ιδέα του αλγορίθμου είναι ότι τοποθετούμε την κάρτα στη στοίβα με τη μικρότερη δυνατή τιμή και εάν δεν υπάρχει δυνατή στοίβα προφανώς δημιούργούμε καινούργια στοίβα. Ο αλγόριθμος είναι ορθός διότι οποιαδήποτε άλλη κίνηση θα δημιουργήσει ενδεχόμενα να δημιούργηθούν επιπλέον στοίβες. Εάν επιλέξουμε να βάλουμε μια κάρτα \verb|card| στη στοίβα \verb|stack1| ενώ υπάρχει επίσης δυνατή στοίβα \verb|stack2 > stack1|, τότε μια κάρτα \verb|stack1 < card < stack2| θα αναγκαστούμε να την βάλουμε σε καινούργια στοίβα. Το να καρατάμε τις κορυφές ταξινομημένες δεν είναι απαραίτητο πχ. αν έχουμε στην κορυφή κάρτες \verb|3| και \verb|4|, το \verb|2| θα μπορούσαμε να το βάλουμε σε οποιαδήποτε από τις δύο στοίβες χωρίς να επηρεάσουμε το πλήθος των στοιβών που δημιουργούνται. Απλά κρατώντας τις κορυφές ταξινομιμένες, καταφέρνουμε να εκτελέσουμε πιο γρήγορα την αναζήτηση (ή δημιουργία) της στοίβας που θα τοποθετήσουμε την κάρτα.

Ο αλγόριθμος σίγουρα θα περάσει το μήκος της τράπουλας $n$. Στη χειρότερη περίπτωση όπου η τράπουλα θα είναι σε αύξουσα ακολουθία, τότε ο αλγόριθμος θα τρέξει ένα binary search για κάθε μήκος $k: 0 \leq k \leq n$. Οι εντολές απόθεσης και ανάκτησης μεταβλητών καθώς και τα boolean checks απαιτούν $\Theta(1)$ βήματα. Οπότε ο συνολικός χρόνος του αλγορίθμου θα είναι
$$T(n) = \log{1} + \log{2} + ... + \log{n} = \mathcal{O}(n\log{n})$$

2. Εφόσον με τον αλγόριθμο του (1) καταλήγουμε με μια λίστα από ταξινομημένες στοίβες, αρκεί να εκτελέσουμε \verb|stack[].length - 1| mergesort αλγορίθους και θα έχουμε ταξινομήσει την τράπουλα. Για να γίνει αποδοτικά θα πρέπει να κάνουμε merge τους πίνακες ανά δύο. Στη χειρότερη περίπτωση (όπου όπως και στο (1) θα έχουν δημιουργηθεί $n$ στοίβες) ο αλγόριθμος θα χρειαστεί
$$T(n) = 2\lfloor\frac{n}{2}\rfloor + 4\lfloor\frac{n}{4}\rfloor + ... = \mathcal{O}(n\log{n})$$
Εναλλακτικά, παρατηρούμε ότι στην περίπτωση που έχουν δημιουργηθεί $n$ στήλες τότε από το (ταξινομημένο) δέντρο με τις κορυφές των στοίβων έχουμε ήδη μια ταξινόμηση της τράπουλας. Θα μπορούσαμε λοιπόν να χρησιμοποιήσουμε έναν αλγόριθμο ο οποίος θα παίρνει ένα κλώνο του \verb|topCardTree| και να ταξινομεί σε χρόνο $T(\verb|topCardTree.length|)$ τα στοιχεία της στοίβας στο νέο δέντρο. Εδώ η χειρότερη περίπτωση είναι να έχουμε $n/2$ στοίβες όπου η καθεμία έχει 2 στοιχεία, οπότε και θα πρέπει να κάνουμε $n/2$ \verb|insert| στο δέντρο, και άρα ο χρόνος γίνεται πάλι
$$T(n) = \frac{n}{2}\log{(n/2)} = \mathcal{O}(n\log{n})$$

3. Με εισόδους $3, 2, 4, 7, 8, 1, 5, 6$ προκύπτει η διάταξη
$$\left[(3, 2, 1), (4), (7, 5), (8, 6)\right]$$
όπου προκύπτουν 4 στοίβες.

Επιπλέον, το μήκος της μέγιστης αύξουσας υπακολουθίας είναι επίσης $4$ (το οποίο εμφανίζεται σε μια υπακολουθία, την $[2, 4, 7, 8]$).

4. Για να δείξουμε ότι το πλήθος των στοιβών στις οποίες καταλήγουμε είναι πάντα μεγαλύτερο ή ίσο του μήκους της μέγιστης αύξουσας υπακολουθίας της εισόδου, αρκεί να δείξουμε ότι σε μια μέγιστη ακολουθία $α_1, α_2, ..., α_k$ ο κάθε όρος ανήκει σε διαφορετική στοίβα.

Με επαγωγή. Η επαγωγική υπόθεση είναι προφανής. Έστω τώρα ότι για $n \leq k$ ισχύει ότι κάθε όρος της ακολουθίας βρίσκεται σε διαφορετική στοίβα και τραβάμε τον $k+1$-όρο. Η κάθε στοίβα που ήδη περιέχει έναν (μικρότερο) όρο δεν θα είναι διαθέσιμη, άρα θα πρέπει να τοποθετήσουμε την κάρτα είτε σε άλλη στοίβα είτε σε καινούργια. Άρα και για $k+1$ στοιχεία η υπόθεση ισχύει.

5. Σε σχέση με το πρόβλημα της μέγιστης αύξουσας υπακολουθίας, το κορυφαίο στοιχείο της $k$-στής στοίβας είναι το στοιχείο για το οποίο θα πρέπει να υπολογίσουμε το \verb|max| όλων των υπακολουθιών του. Δεδομένου λοιπόν ότι ξέρουμε ότι τα προηγούμενα στοιχεία της ακολουθίας που είναι μικρότερά του βρίσκονται αποκλειστικά στις στοίβες στα δεξιά, και από τις κορυφές προς τα κάτω, μπορούμε να βρούμε γρήγορα τα στοιχεία αυτά και να υπολογίσουμε το \verb|max| των υπακολουθιών τους (είτε αναδρομικά είτε δυναμικά).

Σχετικά με το μήκος της μέγιστης φθίνουσας υπακολουθίας, παρατηρώ ότι η δομή που μας δίνει ο αλγόριθμος δεν μας δίνει κάποια πληροφορία για αυτό.

6. Έστω ότι ο αλγόριθμος του $(1)$ δεν δημιουργεί τουλάχιστον $n+1$ στοίβες, δηλαδή δημιουργεί το πολύ $n$. Θα δείξω ότι έχει μια στοίβα μεγέθους τουλάχιστον $m+1$. Έστω ότι δεν έχει. Οπότε κάθε στοίβα έχει το πολύ $m$ στοιχεία. Όμως τότε στις $n$ στοίβες θα χωράνε μόνο $nm$ στοιχεία. Άτοπο.

Αυτό συνδέεται με το θεώρημα του Περιστερώνα.

Η ακολουθία:
$$5, 4, 3, 2, 1, 10, 9, 8, 7, 6, 15, 14, 13, 12, 11, 20, 19, 18, 17, 16, 25, 24, 23, 22, 21$$
δίνει την εξής λίστα από στοίβες:
$$\left[(5, 4, 3, 2, 1), (10, 9, 8, 7, 6), (15, 14, 13, 12, 11), (20, 19, 18, 17, 16), (25, 24, 23, 22, 21)\right]$$

\end{document}

### 2019-12-16 algo/ask02.tex
Algorithms: Added ask02 tex file

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}
\usepackage{amsmath}

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}
\setlength{\parskip}{1em}

\newcommand\nlambda[1]{\ensuremath{\lambda #1.\,}}
\newcommand\nred{\ensuremath{\longrightarrow}}

% Main document
\begin{document}
\title{Αλγόριθμοι - 2η Σειρά Ασκήσεων}
\author{Θωμάς Παππάς}
\date{15 Δεκεμβρίου 2019}
\maketitle
\begin{center}ΑΜ: AL1180011\end{center}

\section*{Ασκηση 1: Μεταφορά Δεμάτων}
(α)

1. Η στοίβαξη με βάση το βάρος ΔΕΝ οδηγεί πάντα σε ασφαλή στοίβαξη.\\
Αντιπαράδειγμα: Έστω πως έχουμε τα πακέτα $(4, 8), (6, 2)$. Τότε ενώ υπάρξει ασφαλής στοίβαξη, η ${(4, 8), (6, 2)}$, αν τα στοιβάξουμε με βάση το βάρος τότε η στοίβαξη ${(6, 2) , (4, 8)}$ δεν είναι ασφαλής.

2. Η στοίβαξη με βάση την αντοχή ΔΕΝ οδηγεί πάντα σε ασφαλή στοίβαξη.\\
Αντιπαράδειγμα: Έστω πως έχουμε τα πακέτα $(3, 9), (10, 4)$. Τότε ενώ υπάρξει ασφαλής στοίβαξη, η ${(10, 4), (3, 9)}$, αν τα στοιβάξουμε με βάση το βάρος τότε η στοίβαξη ${(3, 9), (10, 4)}$ δεν είναι ασφαλής.

3. Η στοίβαξη με βάση το άθροισμα βάρους και αντοχής οδηγεί πάντα σε ασφαλή στοίβαξη. Για να το δείξουμε αυτό, θα δείξουμε ότι οποιαδήποτε ασφαλής σύνταξη είναι ισοδύναμη με μια η οποία έχει τα πακέτα στοιβαγμένα με βάση το άθροισμα βάρους και αντοχής (με το μεγαλύτερο στη βάση της στοίβας).

Έστω ότι για τα πακέτα $(w_1, d_1),...,(w_n, d_n)$ υπάρχει μια ασφαλής στοίβαξη $(1,...,n)$. Για λόγους απλότητας, έστω ${(w_1, d_1),..., (w_n, d_n)}$ αυτή η στοίβαξη. Έστω λοιπόν ότι για κάποιο $k$ στη στοίβαξη έχουμε $w_k + d_k \leq w_{k+1} + d_{k+1}$.

Ισχύει ότι $d_k \geq \sum_{i=k+1}^nw_i$ και άρα από την παραπάνω ανισότητα έχουμε
$$d_{k+1} \geq w_k + d_k - w_{k+1} \geq w_k + \sum_{i=k+1}^nw_i - w_{k+1} = w_k + \sum_{i=k+2}^nw_i$$
οπότε αν αλλάξουμε τη στοίβαξη σε
$$\{(w_1, d_1),...,(w_{k+1}, d_{k+1}), (w_k, d_k),...,(w_n, d_n)\}$$
τότε αυτή παραμένει ασφαλής αφού $d_{k+1} \geq w_k + \sum_{i=k+2}^nw_i$ και $d_k \geq \sum_{i=k+1}^nw_i \geq \sum_{i=k+2}^nw_i$.

Άρα αν επαναλάβουμε την παραπάνω διαδικασία σε όσες περιπτώσεις έχουμε $w_k + d_k \leq w_{k+1} + d_{k+1}$ μπορούμε να βρούμε μια ισοδύναμη ασφαλής στοίβαξη όπου $\forall k \leq n$ έχουμε $w_{k+1} + d_{k+1} \leq w_k + d_k$.

(β) Θα χρησιμοποιήσουμε DP. Ταξινομούμε τα πακέτα σύμφωνα με το άθροισμα βάρους και αντοχής. Έστω το εξής υποπρόβλημα $P$:
\begin{center}
  $P(i,w):$ το μέγιστο κόστος με $i$ πακέτα το πολύ βάρους $w$.
\end{center}
Άρα το πρόβλημά μας λύνεται ψάχνοντας το $P(n,W)$ όπου $W = \sum_{i=1}^nw_i$.

Παρατηρούμε τώρα ότι
$$P(i,w) =
  \begin{cases}
    0, & \text{$w < w_i$}\\
    max
    \begin{cases}
      P(i-1,w)\\
      p_i + P(i-1,min\{w-w_1, d_i\})
    \end{cases} & \text{$w \geq w_i$}
  \end{cases}$$
όπου το $min\{w-w_1, d_i\}$ μας εξασφαλίζει ότι το πακέτο $i$ θα μπορεί να στηρίξει τη στοίβα που δημιουργεί το συγκεκριμένο κόστος, αλλά και ότι το συνολικό βάρος δεν θα ξεπεράσει το $w$. Άρα φτιάχνοντας έναν πίνακα $W \times n$ και με τις αρχικές τιμές
$$P(1,w) =
  \begin{cases}
    0, & \text{$w < w_i$}\\
    p_i, & \text{$w \geq w_i$}
  \end{cases}$$
υπολογίζουμε τις τιμές του. Κρατάμε εν τω μεταξύ σε μια μεταβλητή την $max$ τιμή από όλα τα $P(i,w)$ και στο τέλος παίρνουμε την τιμή αυτή και το σημείο του πίνακα όπου βρίσκεται ώστε πηγαίνοντας προς τα πίσω να βρούμε όλα τα στοιχεία που αποτελούν αυτήν την ασφαλή στοίβαξη.

Πιο συγκεκριμένα, αν ξεκινήσουμε από το $P(n,W)$ τότε για κάθε $P(i,w)$ που "κοιτάμε", αν $P(i-1,w) < P(i,w)$ τότε το $i$ πακέτο ανήκει στη βέλτιστη λύση ενώ διαφορετικά προχωράμε στο στοιχείο $P(i-1,min\{w-w_1,d_i\})$.

Ο χρόνος εκτέλεσης του παραπάνω αλγορίθμου είναι $\mathcal{O}(nW)$.

\section*{Άσκηση 2: Αναμνηστικά}
Θα χρησιμοποιήσουμε DP. Έστω το εξής υποπρόβλημα $S$:
\begin{center}
  $P(i,c):$ Η μέγιστη συναισθηματική αξία που μπορούμε να συλλέξουμε πηγαίνοντας σε $i$ χώρες με κόστος το πολύ $c$.
\end{center}
Άρα το πρόβλημά μας λύνεται ψάχνοντας το $P(n,C)$.

Εφόσον έχουμε αρκετό προϋπολογισμό για το φθηνότερο αντικείμενο από κάθε χώρα μπορούμε να θεωρήσουμε το $C_{min}(i)$ ως εξής:
\begin{center}
  $C_{min}(i):$ το συνολικό κόστος των φθηνότερων αντικειμένων μέχρι και τη χώρα $i$
\end{center}

Θεωρούμε τώρα το $P_i(j)$ τη μέγιστη συναισθηματική αξία που συλλέγουμε από $i$ χώρες επιλέγοντας το $j$ αντικείμενο από τη χώρα $i$. Άρα
$$P_i(j) =
  \begin{cases}
    0, & \text{$C_{min}(i-1) > c-c_{ij}$}\\
    p_{ij} + P(i-1,c-c_{ij}), & \text{$C_{min}(i-1) \leq c-c_{ij}$}
  \end{cases}$$
και έχουμε λοιπόν ότι
$$P(i,c) = max\{P_i(j) | 1 \leq j \leq k_i\}$$
οπότε και φτιάχνουμε έναν $n \times C$ πίνακα (ξεκινάμε από το $C_{min}(n)$ για ευκολία) όπου θα κρατάει τη μέγιστη συναισθηματική αξία για $i$ χώρες με κόστος $c$ καθώς και το στοιχείο $j$ το οποίο χρησιμοποιήθηκε από τη χώρα $i$ για αυτήν την περίπτωση. Βάζουμε 0 όπου το $c$ δεν αρκεί για να πάρουμε ακόμα και τα φθηνότερα αναμνηστικά από κάθε χώρα.

Η αρχικοποίηση των τιμών θα γίνει θέτοντας $P(i,0) = 0, \forall i \leq n$.

Η απάντηση προκύπτει από το να πάρουμε το κελί με τη μέγιστη συναισθηματική αξία από το τέλος και πηγαίνοντας προς τα πίσω να πάρουμε τα στοιχεία $j$ που χρησιμοποιήθηκαν για κάθε περίπτωση.

Εφόσον ο πίνακας θα πρέπει να υπολογίσει τιμές για κάθε χώρα $i \leq n$ για όλα τα κόστη $c \leq C$ και να κάνει σε κάθε περίπτωση $k_i$ υπολογισμούς, ο χρόνος εκτέλεσης του αλγορίθμου θα είναι $\mathcal{O}(nCk_{max})$, όπου $k_{max} = max\{k_i | 1 \leq i \leq n\}$.

\section*{Άσκηση 3: Σοκολατάκια}
Θα χρησιμοποιήσουμε DP για να υπολογίσουμε το κόστος κάθε διαδρομής. Θεωρούμε 2 μετρητές $c_l, c_r$ για τα βήματα που κάνουμε από το αρχικό σημείο αριστερά και δεξιά αντίστοιχα. Για να φτάσουμε στο ζητούμενο θα πρέπει να υπολογίσουμε το χρόνο για όλες τις περιπτώσεις.

Στο σημείο $(i, j)$ μπορούμε να φτάσουμε με 2 περιπτώσεις, είτε από το το σημείο $(i-1, j)$ (από το δεξιό κουτί με κίνηση αριστερά) είτε από το $(i, j-1)$ (από το αριστερό κουτί με κίνηση δεξιά). Κρατάμε δύο πίνακες $n \times n$ με το χρόνο και την ποσότητα των σοκολάτων που έχουμε φάει. Για το χρόνο $C(i, j)$ έχουμε λοιπόν
$$C(i, j) = max
  \begin{cases}
    0, & \text{$q_{i-1} > q_i, q_{j-1} > q_j, t_i = t_{i-1}, t_j = t_{j-1}$}\\
    C(i-1, j)\\
    C(i, j-1)
  \end{cases}$$
με προφανώς αρχική τιμή $C(0,0) = 0$.

Για να γεμίσουμε τους παραπάνω πίνακες ο χρόνος εκτέλεσης που χρειαζόμαστε είναι $\mathcal{O}(n^2)$.

\end{document}

### 2020-01-27 algo/ask03.tex
Algorithms: Added ask03 tex file

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}
\usepackage{amsmath}

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}
\setlength{\parskip}{1em}

\newcommand\nlambda[1]{\ensuremath{\lambda #1.\,}}
\newcommand\nred{\ensuremath{\longrightarrow}}

% Main document
\begin{document}
\title{Αλγόριθμοι και Πολυπλοκότητα - 3η Σειρά Ασκήσεων}
\author{Θωμάς Παππάς}
\date{22 Ιανουαρίου 2020}
\maketitle
\begin{center}ΑΜ: AL1180011\end{center}

\section*{Ασκηση 1: Ο Άγιος Βασίλης και τα Χρυσά Κλειδιά}

Για αρχή παρατηρούμε ότι οι σχέσεις μεταξύ των κουτιών και τα κουτιά τα οποία ανοίγουν τα κλειδιά που έχουν μέσα τους, μπορεί να αναπαραστεί σε έναν κατευθυνόμενο γράφο $G$ όπου ένας κόμβος θα αναπαραστά ένα κουτί και μια ακμή $(u, v)$ θα σημαίνει ότι το κουτί $u$ περιέχει ένα κλειδί που ξεκλειδώνει το κουτί $v$.

Ξεκινώντας λοιπόν θα διαβάσουμε το input χρόνο και σε $\mathcal{O}(m)$ χρόνο θα κατασκευάσουμε το γράφο $G$ σε έναν πίνακα γειτνίασης μεγέθους $n \times n$, καθώς και τον ανάστροφό του $G^T$ (ο ανάστροφος πίνακα γειτνίασης του $G$). Επίσης θα δημιουργήσουμε δύο queues ακαιρέων \verb|boxToCrack| \verb|boxUnlockOrder| για να αποθηκεύσουμε τα κουτιά που θα σπάσουμε και τη σειρά με την οποία θα ξεκλειδώσουμε τα κουτιά αντίστοιχα.

Τώρα θα προχωρήσουμε με τα εξής βήματα:
\begin{itemize}
  \item Διαχείρηση Τετριμένων περιπτώσεων (όπου το κουτί δεν μπορεί να ξεκλειδωθεί)
  \item Εύρεση Ισχυρά Συνεκτικών Συνιστωσών (ΙΣΣ) και κατασκευή DAG γράφου $G_{DAG}$
  \item DFS στο $G_{DAG}$ και κατασκευή $max$ κουτιών που μπορεί να ξεκλειδώσει το κάθε κουτί
\end{itemize}

\subsection*{Τετριμένες περιπτώσεις}
Προφανώς αν ένας κόμβος-κουτι $u$ με εισερχόμενο βαθμό $deg(u) = 0$ ή $1$ με μοναδική ακμή την $(u, u)$ είναι κουτιά που δεν μπορούν να ξεκλειδωθούμε με κάποιο από τα κλειδιά και άρα θα πρέπει να τα σπάσουμε.

Κατά τη διάρκεια που διαβάζουμε το input μπορούμε να κρατήσουμε αυτούς τους κόμβους σε ένα stack/queue, έτσι ώστε μετά να κάνουμε DFS στον καθένα τους. Δηλαδή για κάθε κόμβο $u$ με την παραπάνω ιδιότητα κάνουμε \verb|boxCrack.push(u)| και μετά κάνοντας ΒFS στο $u$ τοποθετούμε κάθε κόμβο που επισκεπτόμαστε σε σειρά χρόνων αφίξεως στο \verb|boxUnlockOrder|.

Τους κόμβους που επισκεφθήκαμε μπορούμε να τους βγάλουμε από το γράφο $G$. Σπάσαμε τα κουτιά που δεν είχαμε άλλη επιλογή, ανοίξαμε όσα κουτιά μας επέτρεψαν αυτά, και άρα οποιαδήποτε άλλη σύνδεση με τα υπόλοιπα κουτιά είναι αδιάφορη.

\subsection*{ΙΣΣ και DAG}
Ο γράφος $G$ ενδεχομένως να αποτελείται από υπογράφους ξένους μεταξύ τους. Για τα παρακάτω βήματα, θα πάρουμε έναν τυχαίο κόμβο (τον επόμενο που δεν έχουμε επισκεφθεί),θα δουλέψουμε πάνω στους κόμβους με τους οποίους συνδέεται, και μετά θα επαναλάβουμε τα βήματα μέχρι να έχουμε επισκεφθεί όλους τους κόμβους.

Χρησιμοποιύμε τον αλγόριθμο Kosaraju στον $G$. Πρώτα φτιάχνουμε μια λίστα από λίστες ακαιρέων \verb|sccs| για να κρατήσουμε τα σύνολα των ΙΣΣ που θα συναντήσουμε. Παίρνουμε λοιπόν έναν τυχαίο αρχικό κόμβο $u$ και κάνουμε DFS κρατώντας τους χρόνους αναχώρησης $f(u)$ σε κάθε βήμα, ώστε εντέλει να πάρουμε την Τοπολογική Διάταξη των κόμβων. Κρατάμε λοιπόν σε ένα stack \verb|topologicalOrder| τους κόμβους που περνάμε με τη σειρά των χρόνων αναχώρησης.

Σε αυτό το σημείο μπορούμε να πούμε ότι τα παραπάνω DFS μαζί με όσα ΒFS κάναμε στις τετριμμένες περιπτώσεις, έχουμε χρησιμοποιήσει συνολικά χρόνο $\mathcal{O}(m+n)$.

Τώρα χρησιμοποιώντας τον πίνακα $G^T$, κάνουμε σε χρόνο $\mathcal{O}(m+n)$ DFS στους κόμβους με τη σειρά της Τοπολογικής Διάταξης (παίρνοντας δηλαδή τα στοιχεία από το stack \verb|topologicalOrder|). Κάθε φορά που το DFS τελειώνει τότε αποθηκεύουμε τα στοιχεία που επισκεφθήκαμε σε μια λίστα μέσα στον \verb|sccs|, αφού αυτά τα στοιχεία αποτελούν μια ΙΣΣ του $G^T$ (και άρα και του $G$).

Μετά διαβάζουμε τη λίστα \verb|scc| και φτιάχνουμε ένα γράφο $G_{DAG}$ όπου κάθε κόμβος αντιστοιχεί σε ένα στοιχείο του \verb|sccs| και κατασκευάζουμε τις ακμές διαβάζοντας σε χρόνο $matcal{0}(m)$ τις ακμές του $G$ από τη μια ΙΣΣ στην άλλη. Δηλαδή
\begin{verbatim}
for scc in sccs:
  dag_node = GT.addOrGet(scc)
  for box in scc:
    for (edges from box as edge):
      if edge.to not in scc:
        scc' = find(edge.to in sccs[])
        dag_node' = GT.addOrGetNode(scc')
        GT.createEdge(dag_node, dag_node')
        break      
\end{verbatim}

\subsection*{Μέτρηση max κουτιών στον DAG}
Κάνουμε σε χρόνο $\mathcal{O}(m+n)$ ένα DFS πάνω στον $G^T$ και με τη σειρά των χρόνων αναχώρησης κατασκευάζουμε μια λίστα ακεραίων \verb|maxBoxesToUnlock| όπου θα κρατήσουμε το πόσα κουτιά μπορεί να ξεκλειδώσει ο κάθε κόμβος-κουτί. Εδώ παρατηρούμε ότι αυτό δουλεύει διότι για κάθε κόμβο $u$ και $v$ με $u, v$ στην ίδια ΙΣΣ θα ισχύει \verb|maxBoxesToUnlock[u] = maxBoxesToUnlock[v]|, και άρα μπορούμε να κρατήσουμε μόνο μια φορά αυτόν τον αριθμό, με τον καθένα να αντιστοιχεί στον αντίστοιχο κόμβο του $G^T$ που αντιπροσωπεύει την αντίστοιχη ΙΣΣ. Ο αριθμός αυτός θα είναι όσο το πλήθος των στοιχείων της ΙΣΣ + το αθροισμα των \verb|maxBoxesToUnlock[u]| αριθμών των απογόνων του.

Κρατάμε το $max$ και κάνοντας BFS ξεκινώντας από έναν τυχαίο αντιπρόσωπο της αντίστοιχης ΙΣΣ κάνουμε \verb|boxCrack.push(u)| για την πρώτη περίπτωση και \verb|boxUnlockOrder.push(u)| για κάθε κόμβο $u$ που επισκεπτόμαστε στη συνέχεια. Συνεχίζουμε μέχρι να σπάσουμε/επισκεφθούμε όλους τους κόμβους.

Η απάντηση στο πρόβλημα είναι η ουρες \verb|boxCrack.push(u)| και \verb|boxUnlockOrder| και ο συνολικός χρόνος που θα χρειαστεί είναι $\mathcal{O}(m+n)$.

\section*{Άσκηση 2: Μακρύτερο Μονοπάτι σε Δέντρο}
Εδώ εφόσον πρόκειται για δέντρο, η πολυπλοκότητα οποιοδήποτε BFS/DFS πραγματοποιήσουμε θα μας πάρει $\Theta(n+(n-1)) = \Theta(n)$.

Δημιουργούμε λοιπόν έναν ακέραιο \verb|maxWeight| και μια λίστα \verb|path| για να αποθηκεύσουμε τα ζητούμενα. Παρατηρούμε τώρα ότι αρκεί να υπολογίσουμε τα μονοπάτια που ξεκινάνε από έναν κόμβο προς τους απογόνους του, διότι εάν υπάρχει ένα μονοπάτι μέγιστου συνολικού βάρους με το κόμβο και τον γονέα του, τότε αυτό το νούμερο θα εμφανιστεί όταν το υπολογίσου για το δικό του υποδέντρο (του γονέα). Άρα το μόνο που μένει να δούμε αν ο κόμβος συμμετέχει στην optimal λύση ως άκρη (και άρα υπολογίζουμε την τιμή του από το $max$ των αντίστοιχων τιμών στα παιδιά του) ή ως μέσο (και άρα υπολογίζουμε την τιμή του από το $max$ άθροισμα δύο -διαφορετικών- παιδιών του).

Πραγματοποιούμε λοιπόν DFS στο δέντρο ξεκινώντας από τη ρίζα και κρατώντας δύο στοιχεία για κάθε κόμβο $u$ που εξερευνούμε, το $max$ βάρος $w_e(u)$ που έχει ο κόμβος ως η άκρη ενός μονοπατιού και το $max$ βάρος $w_m(u)$ που έχει ο κόμβος όταν ΔΕΝ είναι η άκρη ενός μονοπατιού. Έτσι, εφόσον μέσω του DFS εξερευνούμε (και άρα ξεκινάμε να υπολογίσουμε) είτε φύλλα είτε κόμβους που έχουμε ήδη υπολογίζει τα αντίστοιχα βάρη όλων των παιδιών του \verb|children(u)|, ο υπολογισμός γίνεται ως εξής:
$$w_e(u) =
  \begin{cases}
    0, & \text{$w(u) \leq 0$}\\
    w(u) + max\{w_e(v) | v \in \verb|children(u)|\}, & \text{διαφορετικά}
  \end{cases}$$
$$w_m(u) = w(u) + max\{w_e(v_1) + w_e(v_2)| v_1 \neq v_2, v_1, v_2 \in \verb|children(u)|\}$$
Επίσης ενώ τρέχουμε τους από πάνω υπολογισμούς, κρατάμε και τους κόμβους $v, v_1, v_2$ που επιλέξαμε για κάθε κόμβο $u$ (πχ. σε μια λίστα με 3-άδες $(v, v_1, v_2)$) έτσι ωστε μετά να μπορέσουμε να ανατρέξουμε στο μονοπάτι που θέλουμε.

Για τις περιπτώσεις που ο κόμβος έχει μη θετικό βάρος τότε ξέρουμε ότι δεν πρόκειται να ανήκει ως άκρη σε μονοπάτι μέγιστου συνολικού βάρους αφού το μονοπάτι χωρίς αυτόν τον κόμβο θα έχει σίγουρα μεγαλύτερο ή ίσο συνολικό βάρος.

Ενώ τρέχουμε τους παραπάνω υπολογισμούς συγκρίνουμε τα $w_e, w_m$ και κρατάμε το μεγαλύτερο στο \verb|maxWeight|. Στο τέλος η τιμή του \verb|maxWeight| καθώς και το μονοπάτι που έχει αυτήν την τιμή (το οποίο αποθηκεύουμε στο \verb|path| μέσω των 3-άδων που ορίσαμε παραπάνω).

Για να υπολογίσουμε την πολυπλοκότητα του αλγορίθμου, αρκεί να παρατηρήσουμε ότι ενώ τρέχει το DFS τότε ο κάθε κόμβος θα υπολογιστεί μια φορά και θα συγκριθεί από μια φορά (όταν φτάσει η στιγμή να υπολογιστεί ο γονέας του). Οπότε ο συνολικός χρόνος εκτέλεσης θα παραμείνει $\Theta(n)$.

\section*{Άσκηση 3: Κλέφτες και Αστυνόμοι}

Πρώτον παρατηρούμε ότι μπορούμε να αναπαραστήσουμε τις πιθανές κινήσεις του Κώστα και του Ανδρέα σε έναν γράφο $G_{game}(V \times V \times \{K, A\}, E')$ όπου κάθε κορυφή θα αναπαριστά μια κατάσταση του παιχνιδιού, ενώ οι ακμές τις πιθανές κινήσεις από τη μια στην άλλη. Ο κάθε κόμβος θα συνδέεται με μια 3-άδα $(u, v, P)$ όπου το $u$ είναι η κορυφή που βρίσκεται ο Κώστας, $v$ η κορυφή που βρίσκεται ο Αντρέας και το $P$ τον παίκτη Α ή Κ που είναι η σειρά του να παίξει. Συνεπώς για κάθε ακμή $(u, v)$ του $G$ έχουμε ότι $\forall w \in V$ οι $((u, w, K), (v, w, A))$ και $((w, u, A), (w, v, K))$ είναι ακμή του $G_{game}$.

Προφανώς αποκλείουμε τους κόμβους όπου ο Αλέξης βρίσκεται στην κορυφή-καταφύγιο. Θα μαρκάρουμε τώρα τον κάθε κόμβο στο $G_{game}$ με το αν από αυτήν την κατάσταση θα νικήσει σίγουρα ο Κώστας ή ο Αντρέας. Προφανώς για κάθε κόμβο $(u, v, P)$ όπου $u$ το καταφύγιο τότε νικάει ο Κώστας, ενώ για κάθε $(u, u, P)$ νικάει ο Αντρέας. Τώρα αν ο Κώστας έχει κάποια κατάσταση γύρω του που νικάει τότε νικάει και σε αυτή που βρίσκεται, ενώ αν παντού νικάει ο Αντρέας τότε νικάει και εκεί που είναι. Αντίστροφα για τον Αντρέα.

Πραγματοποιούμε μια τοπολογική κατανομή στις ακμές (ώστε να σιγουρευτούμε ότι το καταφύγιο θα είναι τελευταίο) και πραγματοποιούμε ένα DFS και υπολογίζουμε τις βέλτιστες κινήσεις από κάθε κατάσταση.

Ο χρόνος εκτέλεσης αποτελείται από την κατασκευή του $n \times n \times 2$ γράφου $G_{game}$ καθώς και από το DFS που πραγματοποιήθηκε σε αυτόν. Συνεπώς συνολικά έχουμε πολυπλοκότητα $\mathcal{O}(n^2) + \mathcal{O}(n^2) = \mathcal{O}(n^2)$.

\end{document}

### 2020-02-15 algo/ask04.tex
Algorithms: ask01: Added tex file with exercise 1

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}
\usepackage{amsmath}

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}
\setlength{\parskip}{1em}

\newcommand\nlambda[1]{\ensuremath{\lambda #1.\,}}
\newcommand\nred{\ensuremath{\longrightarrow}}

% Main document
\begin{document}
\title{Αλγόριθμοι και Πολυπλοκότητα - 4η Σειρά Ασκήσεων}
\author{Θωμάς Παππάς}
\date{16 Φεβρουαρίου 2020}
\maketitle
\begin{center}ΑΜ: AL1180011\end{center}

\section*{Ασκηση 1: Επιβεβαίωση και Αναπροσαρμογή Συντομότερων Μονοπατιών}

\subsection*{(α)}
Δεδομένου ότι έχουμε έναν (ενδεχομένως λάθος) ισχυρισμό για όλα τα συντομότερα μονοπάτια από μια κορυφή $u_1$, μπορούμε να χρησιμοποιήσουμε αυτήν την πληροφορία για να υπολογίσουμε το Δέντρο Συντομότερων Μονοπατιών από το $u_1$ σε γραμμικό χρόνο.

Αν ο ισχυρισμός είναι λάθος, τότε θα υπάρχει ένα μονοπάτι $(u_1, u_i)$ τέτοιο ώστε $d(u_1, u_i) \neq \delta_i$, και προχωρώντας επαγωγικά στις κορυφές αυτού του μονοπατιού μπορούμε να βρούμε το μικρότερο $j$ για το οποίο $d(u_1, u_j) \neq \delta_j$. Παρατηρούμε ότι εφόσον μας αρκεί ένα λάθος για να ξέρουμε ότι ο αρχικός ισχυρισμός είναι εσφαλμένος, τότε αρκεί να ελέγξουμε μόνο την τελευταία ακμή ενός μονοπατιού, με το δεδομένο ότι η απόσταση του γονέα του με το $u_1$ είναι η ισχυριζόμενη. Τέλος μένει να κρατήσουμε σε έναν πίνακα ποιες κορυφές έχουν επιβεβαιωμένες τις αποστάσεις τους, ώστε στο τέλος θα μπορούμε να αποφανθούμε αν είναι όλες σωστές.

Ξεκινώντας λοιπόν φτιάχνουμε μια integer λίστα \verb|parents[]| $n$ μεγέθους όπου θα κρατάμε τους γονείς των κορυφών που έχουν επιβεβαιώσει την απόστασή τους $d(u_1, u_i) = \delta_i$. Αρχικοποιούμε τη λίστα βάζοντας παντού $-1$.

Από την κορυφή $u_1$ Θα τρέξουμε BFS (σε χρόνο $\mathcal{O}(|G|+|V|)$) και σε κάθε αναδρομή μιας κορυφής $u_p$ θα συγκρίνουμε για κάθε παιδί $u_c$ τις τιμές $\delta_c$ και $\delta_p + w(u_p,u_c)$ ως εξής:
\begin{itemize}
  \item Αν $\delta_c > \delta_p + w(u_p,u_c)$, τότε έχουμε βρει συντομότερο μονοπάτι από το ισχυριζόμενο, άρα τερμάτισε και επέστρεψε \verb|false|
  \item Αν $\delta_c = \delta_p + w(u_p,u_c)$, τότε σημειώνουμε \verb|parents[c] = p| και συνεχίζουμε
  \item Αν $\delta_c < \delta_p + w(u_p,u_c)$, τότε δεν κάνουμε τίποτα και συνεχίζουμε
\end{itemize}
Στο τέλος ελέγχουμε αν για τη λίστα \verb|parents| υπάρχει κάποιο στοιχείο $k$ τέτοιο ώστε \verb|parents[k] = -1|. Αν υπάρχει, τότε τερματίζουμε και επιστρέφουμε \verb|false|. Αν όχι τότε σημαίνει ότι όλες οι αποστάσεις $\delta_1, ..., \delta_n$ έχουν επιβεβαιωθεί ως σωστές και άρα επιστρέφουμε τον πίνακα \verb|parents| ο οποίος αποτελεί την περιγραφή του ΔΣΜ με ρίζα την κορυφή $u_1$.

Τα operations που τρέχουμε σε κάθε αναδρομή του BFS είναι χρόνου $\Theta(1)$ ενώ ο τελευταίος έλεγχος της λίστας \verb|parents| θα πάρει το πολύ $\mathcal{O}(n)$. Άρα συνολικά ο χρόνος που απαιτείται για τον παραπάνω αλγόριθμο είναι $\mathcal{O}(|G|+|E|)$.

\subsection*{(β)}
Παρατηρούμε ότι για να αναπροσαρμόσουμε τις ελάχιστες αποστάσεις μεταξύ όλων των κορυφών σε νέες τιμές $d^\prime(u_i,u_j)$, αρκεί να ελέγξουμε τα μονοπάτια στα οποία συμμετέχει η ακμή $e$. Αν η ακμη $e = (x,y)$ συμμετέχει σε ένα τέτοιο μονοπάτι (και εφόσον δεν έχουμε κύκλους αρνητικού μήκους) τότε αυτό θα έχει απόσταση
$$d_e^\prime(u_i,u_j) = d(u_i,x) + w^\prime(x,y) + d(y,u_j)$$

Επίσης από την τριγωνική ανισότητα ξέρουμε ότι για κάθε (καινούργιο) συντομότερο μονοπάτι ισχύει ότι
$$d(u_i,u_j) \leq d(u_i,x) + w(x,y) + d(y,u_j)$$
ενώ επίσης
$$d^\prime(u_i,u_j) \leq d(u_i,x) + w^\prime(x,y) + d(y,u_j)$$
με τις ισότητες να ισχύουν όταν η ακμή $e$ είναι μέρος του συντομότερου μονοπατιού. Προφανώς ισχύει ότι $d^\prime(u_i,u_j) \leq d(u_i,u_j)$.

Διακρίνουμε λοιπόν τις εξής περιπτώσεις:
\begin{itemize}
  \item Αν $d(u_i,u_j) < d_e^\prime(u_i,u_j)$ τότε το αρχικό συντομότερο μονοπάτι δεν χρησιμοποιούσε την ακμή $e$ και εφόσον παραμένει μικρότερο τότε παίρνουμε $d^\prime(u_i,u_j) = d(u_i,u_j)$
  \item Αν $d(u_i,u_j) \geq d_e^\prime(u_i,u_j)$ τότε το μονοπάτι με την ακμή $e$ έχει συντομότερη ή ίση απόσταση από πριν, και άρα παίρνουμε $d^\prime(u_i,u_j) = d_e^\prime(u_i,u_j)$
\end{itemize}

Οι πράξεις που κάνουμε για κάθε ζευγάρι απαιτούν χρόνο $\Theta(1)$ και εφόσον ελέγχουμε για κάθε κορυφή σε κάθε άλλη κορυφή, άρα ο συνολικός απαιτούμενος χρόνος είναι $\mathcal{O}(n^2)$.

\subsection*{(γ)}
Αν το μήκος μιας ακμής $e = (x,y)$ αυξηθεί σε $w^\prime(x,y) > w(x,y)$ τότε ΔΕΝ μπορούμε να επεκτείνουμε τον αλγόριθμο του (β) για να βρούμε τις νέες αποστάσεις. Ο λόγος είναι ότι δεν έχουμε κάποιο κάτω φράγμα για το $d^\prime(u_i,u_j)$ (όπως είχαμε πριν άνω φράγμα με την τριγωνική ανισότητα).

Πιο συγκεκριμένα, εφόσον η ακμή $e$ αυξήθηκε, τότε έχουμε πάντα
$d(u_i,u_j) < d_e^\prime(u_i,u_j)$ χωρίς να ξέρουμε σε ποια περίπτωση του αλγορίθμου βρισκόμαστε. Ακόμα και αν ξέραμε ότι η ακμή $e$ συμμετείχε στο μονοπάτι με $d(u_i,u_j)$ και πάλι δεν μπορούμε να γνωρίζουμε αν με την επαυξημένη ακμή θα υπάρχει άλλο μονοπάτι με $d(u_i,u_j) < d^\prime(u_i,u_j) < d_e^\prime(u_i,u_j)$, και άρα ο αλγόριθμος δεν μπορεί να δουλέψει.

\end{document}

### 2020-02-17 algo/ask04.tex
Algorithms: ask04: Added exercise 2

@@
 
+\section*{Ασκηση 2: Σύστημα Ανισοτήτων}
+
+Αρχικά παρατηρούμε ότι μπορούμε να δούμε το σύστημα ανισωτήτων $S$ ως έναν γράφο $G(V,E)$ με $|V| = n, |E| = m$, ο οπου για κορυφές τοποθετούμε τις $x_i$ μεταβλητές, ενώ από κάθε ανισότητα $x_i-x_j\leq b_{ij}$ βάζουμε την ακμή $(x_j, x_i)$ με βάρος $w(x_j, x_i) = b_{ij}$.
+
+Επίσης παρατηρούμε ότι ένα μονοπάτι από $k$ κορυφές $(x_{i_1},...,x_{i_k})$ αντιστοιχεί στην ανισότητα που προκύπτει αν προσθέσουμε κατά μέλη τις $k-1$ ανισότητες που αντιστοιχούν στις ακμές του μονοπατιού
+$$x_{i_2}-x_{i_1}\leq b_{i_2i_1}$$
+$$x_{i_3}-x_{i_2}\leq b_{i_3i_2}$$
+$$...$$
+$$x_{i_k}-x_{i_{k-1}}\leq b_{i_ki_{k-1}}$$
+από τις οποίες και παίρνουμε
+$$x_{i_k}-x{i_1}\leq \sum_{j=1}^{k-1}b_{i_{j+1}i_j}$$
+όπου $\sum_{j=1}^{k-1}b_{i_{j+1}i_j}$ είναι και το άθροισμα των ακμών του μονοπατιού.
+
+\subsection*{(α)}
+Χρησιμοποιώντας τον γράφο $G$ μπορούμε να δούμε το εξής: Το σύστημα S είναι ικανοποιήσιμο αν και μόνον αν ο γράφος $G$ δεν περιέχει κύκλο αρνητικού μήκους.
+
+\subsubsection*{Απόδειξη}
+Έστω ότι το σύστημα $S$ είναι ικανοποιήσιμο.
+Θα δείξουμε ότι ο γράφος $G$ δεν μπορεί να περιέχει κύκλο αρνητικού μήκους.
+Αν υποθέσουμε ότι έχει, τότε αυτό σημαίνει ότι υπάρχει κύκλος από $k$ κουρφές $(x_{i_1},...,x_{i_k},x_{i_1})$ για τον οποίο ισχύει ότι το άθροισμα των ακμών του είναι αρνητικό.
+Με την παρατήρηση για το άθροισμα των ακμών ενός μονοπατιού από προηγουμένως παίρνουμε $x_{i_1}-x{i_1} < 0 \Rightarrow 0 < 0$, το οποίο προφανώς και είναι αδύνατον.
+Άρα ο γράφος $G$ δεν περιέχει κύκλους αρνητικού μήκους.
+
+Έστω τώρα ότι ο γράφος $G$ δεν περιέχει κύκλους αρνητικού μήκους.
+Θα δείξουμε ότι το σύστημα $S$ είναι ικανοποιήσιμο.
+Εφόσον o $G$ δεν περιέχει κύκλους αρνητικού μήκους, τότε μπορώ να βρω τα συντομότερα μονοπάτια από μια κορυφή $s$.
+Για να σιγουρευτούμε ότι θα φτάσουμε σε όλες τις μεταβλητές, προσθέτουμε μια κορυφή $x_0$ την οποία και συνδέουμε με όλες τις άλλες κορυφές με ακμή $(x_0,x_i)$ όπου $w(x_0,x_i) = 0$.
+Τότε μια λύση του συστήματος είναι η $(d(x_0,x_1),d(x_0,x_2),...,d(x_0,x_n))$.
+
+Όντως εφόσον $d(x_0,x_i)$ το συντομότερο μονοπάτι από το $x_0$ στο $x_i$, τότε για κάθε ακμή $(x_i,x_j)$ παίρνουμε από την τριγωνική ανισότητα ότι
+$$d(x_0,x_j) \leq d(x_0,x_i) + w(x_i,x_j) \Rightarrow x_j - x_i \leq b_{ji}$$
+που σημαίνει ότι ο αντίστοιχος περιορισμός ισχύει.
+
+\subsubsection*{Αλγόριθμος}
+Αρχικά θα κατασκευάσουμε το γράφο $G$ σε χρόνο $\Theta(n+m)$.
+Για την εύρεση κύκλου αρνητικού μήκους θα τρέξουμε τον Αλγόριθμο Bellman-Fort για τον επαυξημένο γράφο $G(V\cup\{x_0\}, E\cup\{(x_0,x_i) | x_i \in E\})$.
+Όμως εφόσον θέτουμε $w(x_0,x_i)=0, \forall x_i\in E$ και γνωρίζουμε ότι η κορυφή $x_0$ δεν έχει εξερχόμενες ακμές (και άρα ούτε συμμετέχει σε κύκλο αρνητικού μήκους) άρα μπορούμε να αγνοήσουμε την επαυξημένη κορυφή και τις ακμές της.
+
+Η πολυπλοκότητα του Bellman-Ford για γράφο με $n$ κορυφές και $m$ ακμές είναι $\Theta(nm)$, η οποία είναι και η συνολική πολυπλοκότητα του αλγορίθμου μας.
+
+\subsection*{(β)}
+\subsubsection*{Εύρεση τιμών}
+Για την εύρεση τιμών ο προηγούμενος αλγόριθμος αρκεί να επιστρέφει τη λίστα με τα συντομότερα μονοπάτια όταν δεν βρίσκει κύκλο αρνητικού μήκους.
+Έτσι όπως δείξαμε τα συντομότερα μονοπάτια $(d(x_0,x_1),d(x_0,x_2),...,d(x_0,x_n))$ αποτελούν μια λύση του συστήματος $S$.
+Η πολυπλοκότητα του αλγορίθμου παραμένει στο $\Theta(nm)$.
+
+\subsubsection*{Ελάχιστο μη ικανοποιήσιμο σύστημα}
+Για να υπολογίσουμε το ελάχιστο μη ικανοποιήσιμο σύστημα $S^\prime$ θα πρέπει να βρούμε τον ελάχιστο κύκλο αρνητικού μήκους που καθιστά το $S$ μη ικανοποιήσιμο.
+
+Φτιάχνουμε δύο λίστες $n$ μεγέθους \verb|degree[]| και \verb|pathSum[]|, αρχικοποιημένες με όλα τα στοιχεία τους ίσα με $0$).
+Επίσης φτιάχνουμε και μια λίστα από λίστες αγνώστου μεγέθους |\verb|negCyclePaths| όπου θα κρατάμε τους κύκλους αρνητικού μεγέθους που βρίσκουμε.
+Ο έλεγχος για κύκλους αρνητικού μήκους \verb|D[u] > D[v] + w(v,u)| μας δίνει την πληροφορία ότι η κορυφή $v$ ανήκει σε τουλάχιστον έναν κύκλο αρνητικού μήκους.
+Για να βρούμε τις ακμές του, θα τρέξουμε BFS από την $v$, και σε κάθε αναδρομή για την ακμή $(x_i, x_j)$ αυξάνουμε το βαθμό των κορυφών που βρίσκουμε κατά $1$ (\verb|degree[j]++|) και ενημερώνουμε τo άθροισμα του μονοπατιού (\verb|pathSum[j] = pathSum[i] + w(xi,xj)|).
+Όταν φτάσουμε σε κορυφή $x_i$ που έχουμε ήδη επισκευθεί, τότε αρχικά ελέγχουμε αν το μονοπάτι είναι αρνητικού μήκους.
+Αν όχι συνεχίζουμε, αν ναι τότε αν \verb|degr| είναι ο βαθμός της αναδρομής που βρισκόμαστε τότε ο κύκλος έχει μήκος \verb|degr-degree[i]|.
+Αποθηκεύουμε το μονοπάτι στο \verb|negCyclePaths| και συνεχίζουμε.
+
+Αφού ελέγξουμε όλες τις κορυφές που ανήκουν σε κύκλο αρνητικού μήκους, επιστρέφουμε τους περιορισμούς που αντιστοιχούν στο μονοπάτι με το μικρότερο μήκος.
+
+Για να βελτιώσουμε την πολυπλοκότητα του αλγορίθμου μας, μπορούμε να κρατήσουμε έναν global πίνακα \verb|visited| για όσα BFS χρειαστεί να τρέξουμε.
+Έτσι, αν έχουμε πολλαπλούς κύκλους αρνητικού μήκους στο $G$ τότε αυτές οι κορυφές θα εξεταστούν μια φορά η καθεμιά.
+Άρα στη χειρότερη περίπτωση όπου θα χρειαστεί να ελέγξουμε όλες τις κορυφές θα χρειαστούμε χρόνο $\Theta(n+m)$, και άρα ο συνολικός χρόνος για τον παραπάνω αλγόριθμο είναι $\Theta(nm+n+m)=\Theta(nm)$.
+
+\subsubsection*{(γ)}
+Τροποποιώντας το αλγόριθμο του υποερωτήματος (β), μπορούμε να προσθέσουμε τη λίστα $n$ μεγέθους \verb|weightSum| όπου θα αποθηκεύουμε το συνολικό βάρος ενός μονοπατιού.
+Ενώ τρέχουμε το BFS λοιπόν σε κάθε βήμα για μια ακμή $(x_i, x_j)$ εκτελούμε \verb|weightSum[j] = weightSum[i] + w[i][j]| όπου \verb|w| ο $n\times n$ πίνακας με τα βάρη των ακμών.
+Όταν από κορυφή $x_i$ βρίσκουμε κορυφή $x_j$ που έχουμε ήδη επισκευθεί τότε το συνολικό βάρος του μονοπατιού είναι \verb|weight[i]+w[i][j]-weight[j]|.
+Στο τέλος επιστρέφουμε το μονοπάτι με το μικρότερο συνολικό βάρος.
+
+Εφόσον απλά προσθέσαμε κάποιες $\Theta(1)$ πράξεις στον αλγόριθμο του (β), η πολυπλοκότητα του αλγορίθμου παραμένει στο $\Theta(nm)$.
+
+\subsection*{(δ)}
+Το πρόβλημα του υποερωτήματος (γ) διατυπώνεται ως πρόβλημα απόφασης $C(S,K)$ ως εξής:
+Για το σύστημα ανισώσεων $S$ και έναν αριθμό $Κ$, υπάρχει υποσύστημα $S^\prime$ βάρους το πολύ $K$ τέτοιο ώστε το $S^\prime$ μη ικανοποιήσιμο;
+
+Για να λύσουμε το πρόβλημα για ένα συγκεκριμένο αριθμό $K$, χρειάζόμαστε χρόνο $\Theta(nm)$, αλλά αφού $m\leq n(n-1)$ τότε ο χρόνος αυτός είναι το πολύ $\mathcal{O}(n^3)$. Άρα $C \in P$.
+
+Για να λύσουμε το πρόβλημα γενικά, αρχικά το λύνουμε για το άθροισμα $W$ όλων των βαρών των περιορισμών, δηλαδή για $W = \sum_{1 \leq i,j \leq n} w_{ij}$ (θεωρούμε $w_{ij}=0$ αν δεν υπάρχει περιορισμός $x_i-x_j$).
+Αν η απάντηση είναι \verb|false| (όπου σημαίνει ότι το $S$ είναι ικανοποιήσιμο) τότε επιστρέφουμε \verb|false|.
+Διαφορετικά ψάχνουμε με δυαδική αναζήτηση αριθμό $w$ τέτοιο ώστε $P(S,w) = \verb|true|$ και $P(S,w-1) = \verb|false|$.
+Αυτό σημαίνει ότι ο αλγόριθμος του (γ) θα τρέξει το πολύ $log(W)$ φορές, η οποία τιμή έχει ρυθμό ανάπτυξης μικρότερο του πολυωνυμικού, και άρα το πρόβλημα παραμένει στο $P$.
+
 \end{document}

### 2020-02-17 algo/ask04.tex
Algorithms: ask04: Added exercise 3a

@@
 \usepackage{amsmath}
+
+\usepackage{listings}% http://ctan.org/pkg/listings
+\lstset{
+  basicstyle=\ttfamily,
+  mathescape
+}
 
@@
 
+\section*{Άσκηση 3: Ταξιδεύοντας με Ηλεκτρικό Αυτοκίνητο}
+
+\subsection*{(α)}
+Εφόσον οι ακμές του δικτύου έχουν θετικά μήκη μπορούμε να βρούμε το συντομότερο $s-t$ μονοπάτι με τον αλγόριθμο του Dijkstra.
+Για να σιγουρευτούμε όμως ότι θα περάσουμε από τουλάχιστον $1$ πόλη με σταθμό φόρτισης, για κάθε κορυφή $u$ θα κρατάμε το $D_0[u]$, το συντομότερο μονοπάτι από το $s$ στο $u$ με κανένα σταθμό φόρτισης, καθώς και το $D_1[u]$, το συντομότερο μονοπάτι από το $s$ στο $u$ με τουλάχιστον $1$ σταθμό φόρτισης.
+Ομοίως και για τις λίστες $p_0$ και $p_1$ για να κρατάμε τους γονείς των κορυφών στα συντομότερα μονοπάτια.
+
+Αρχικοποιούμε τις λίστες $D_0$ και $D_1$ με άπειρο σε όλα τα στοιχεία εκτός από το $D_0[s]$ το οποίο και αρχικοποιούμε με $0$.
+Επίσης αρχικοποιούμε τις λίστες $p_0$ και $p_1$ με \verb|NULL| σε όλα τους τα στοιχεία.
+Τρέχουμε τον αλγόριθμο Dijkstra. Για καθε ακμή $u$ που επισκέφθεται ο αλγόριθμος:
+\begin{lstlisting}
+for all v $\in$ AdjList[u] do
+  if hasChargeStation(v) do
+    minD = min($D_0$[u],$D_1$[u])
+    if $D_1$[v] > minD + w(u,v) do
+      $D_1$[v] = minD + w(u,v)
+      $p_1$[v] = u
+  else
+    if $D_0$[v] > $D_0$[u] + w(u,v) do
+      $D_0$[v] = $D_0$[u] + w(u,v)
+      $p_0$[v] = u;
+    if $D_1$[v] > $D_1$[u] + w(u,v) do
+      $D_1$[v] = $D_1$[u] + w(u,v) 
+      $p_1$[v] = u; 
+\end{lstlisting}
+
+Αφού ο αλγόριθμος ξεκινάει από το $s$ με $D_0[s]=0$ και $D_1[s]=\infty$ τότε για κάθε επόμενη κορυφή $v$ που δεν έχει σταθμό φόρτισης το $D_0[v]$ ανανεώνεται όπως και στην κλασική έκδοση του αλγορίθμου, και το $D_1[v]$ παραμένει άπειρο.
+Όταν συναντήσουμε την πρώτη κορυφή με σταθμό φόρτισης, τότε ο αλγόριθμος ελέγχει αν το μονοπάτι από το $D_0$ ή το $D_1$ είναι το πιο σύντομο και επιλέγει αυτό για να υπολογίσει το $D_1[v]$, ενώ το $D_0[v]$ παραμένει άπειρο, αφού δεν υπάρχει μονοπάτι με $0$ σταθμούς φόρτισης που να περνάει από εκεί.
+Απο εδώ και πέρα αν ξανασυναντήσουμε κορυφή χωρίς σταθμό φόρτισης τότε ο κάθε έλεγχος στα $D_0$ και $D_1$ μας διαβεβαιώνει ότι και η $u$ έχει μονοπάτι με $0$ ΄$1$ σταθμούς φόρτισης αντίστοιχα (ή και τα δύο) και ανανεώνει τους πίνακες αναλόγως.
+Σε όλα τα παραπάνω βήματα οι πίνακες $p_0$ και $p_1$ συμπληρώνονται αντίστοιχα μόνο αν υπάρχει το αντίστοιχο μονοπάτι που περνάει από την ακμή $(u,v)$.
+
+Το ελάχιστο μονοπάτι προκύπτει αν ξεκινήσουμε από την κορυφή $u$ που έχει την ελάχιστη τιμή στο $D_1$, η οποία ξέρουμε ότι δεν μπορεί να είναι άπειρο αφού $|C|\geq 3$, και πάρουμε αναδρομικά τους προγόνους της κορυφής από τις λίστες $p_0$ και $p_1$.
+Ξεκινάμε με το $p_1$ της κορυφής και μετά για κάθε γονέα κορηφής $p$ ελέγχουμε αν $D_0[p] < D_1[p]$.
+Αν είναι αληθής για συνέχεια του μονοπατιού παίρνουμε το $p_0[p]$ και συνεχίζουμε με την $p_0$ μέχρι τέλους.
+Αν δεν είναι αληθής τότε παίρνουμε το $p_1[p]$ και στη συνέχεια επαναλαμβάνουμε τη διαδικασία (με τον έλεγχο) ξανά για αυτό το στοιχείο.
+
+Εάν χρησιμοποιήσουμε Fibonacci heap για την εκτέλεση του Dijkstra τότε επιτυγχάνουμε χρόνο εκτέλεσης $\mathcal{O}(m+nlogn)$.
+Οι επιπλέον πράξεις που προσθέσαμε είναι χρόνου $\Theta(1)$ ενώ το τελευταίο κομμάτι που κατασκευάζει το μονοπάτι χρειάζεται χρόνο $\Theta(n)$, άρα ο συνολικός χρονος εκτέλεσης του αλγορίθμου μας είναι $\mathcal{O}(m+nlogn)$.
+
 \end{document}

### 2020-03-05 algo/presentation_algorithms_in_git.tex
Algorithms: Presentation: Added tex file for 'Algorithms in Git' presentation slides

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass{beamer}
\usetheme{Madrid}
\centering

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}

% Main document
\begin{document}
\title{Algorithms in Git}
\author{Thomas Pappas}
%\date{4 March 2020}
\maketitle

% These three lines create an automatically generated table of contents.
\begin{frame}{Outline}
  \tableofcontents
\end{frame}

\begin{frame}
  \begin{block}{Disclaimer}
    This presentation contains a simplified, for introductory purposes, representation of how the Git framwork functions.
    The actual models of a Git repo, commit, branch etc. are more complex than described here.
    For more info check the references.
  \end{block}
\end{frame}

\section{What is Git?}

\begin{frame}{What is Git?}
  \begin{block}{Git is a decentralised VCS}
    \begin{itemize}
    \item Version Control System (VCS)
      \begin{itemize}
        \item tracks and keeps a history of changes in a directory tree of text files\\(code in most cases)
        \item facilitates collaborative development
        \item allows sharing code
        \item versioning
        \item etc.
      \end{itemize}
    \item Decentralised: Every user has a full copy of the repository (repo)
    \item Created by Linus Torvalds in 2005 for development of the Linux kernel
  \end{itemize}
  \end{block}
\end{frame}

\subsection{Git commits}

\begin{frame}{Git commits}
  \begin{block}{What are Commits?}
    Commits are the basic units of a Git repo.
    It contains information about
    \begin{itemize}
      \item Hash (for unique identification)
      \item For each file, two file states $a$ (before) and $b$ (after) to track changed
      \begin{itemize}
        \item Name
        \item Lines (in blobs)
        \item Meta-data
      \end{itemize}
      \item Commit message
      \item Meta-data (author, commiter, date)
      \item Parent(s) commit hash
    \end{itemize}
    A Git commit captures the full state of the file directory tree the moment the commit was created.
  \end{block}
\end{frame}

\begin{frame}{Git commits}
  \begin{block}{Diff blobs}
    When viewing a diff, a "blob" is the file section where the line changes are shown. For the two file state $a$ and $b$ the following are shown:
    \begin{itemize}
      \item line start and length (for the blob size)
      \item lines "removed" from $a$ to $b$ appended with "$-$"
      \item lines "added" from $a$ to $b$ appended with "$+$"
    \end{itemize}
  \end{block}
  \begin{block}{Commits as Nodes}
    We can thus see the Git repo as a graph with the commits as its nodes. A commit without a parent commit hash is called a "root" commit. 
  \end{block}
\end{frame}

% TODO: Add an example
%\begin{frame}{Git commit Example}

%\end{frame}

\subsection{Branches}

\begin{frame}{Git branches}
  \begin{block}{What are Branches?}
    Branches are "pointers" to commits. In practice, though, a branch is the subgraph that has all the ancestor commits of that commit.
  \end{block}
  \begin{block}{Some properties}
    \begin{itemize}
      \item One commit can belong to multiple branches
      \item The Git repo keeps a "current" branch in a HEAD variable
      \item When a commit is created, the branch's "tip" becomes that commit
      \item Benefit: Branches can facilitate independent feature development
    \end{itemize}
  \end{block}
\end{frame}

\section{Merging branches}

\begin{frame}{Merging branches}
  \begin{block}{What is a Merge?}
    Incorporates changes from the named commits (since the time their histories diverged from the current branch) into the current branch.
  \end{block}
  \begin{block}{(Common) Merge types}
    \begin{itemize}
      \item Fast Forward Merge
      \item 3-way Merge
    \end{itemize}
  \end{block}
  \begin{block}{Fast Forward Merge}
    Trivial case where the tip commit in the current branch is an ancestor of the named commit. Simply move the tip of the current branch to the named commit.
  \end{block}
\end{frame}

\begin{frame}{Merging branches}
  \begin{block}{3-way Merge: Algorithm}
    Given I currently am at "branchA" and I merge with "branchB", or in other words: Given the hashes of the two commits A and B on the branches' tips.
    \begin{itemize}
      \item Find a merge base C, the best common ancestor of commits A and B (LCA)
      \item Create a diff $D_A$ with the combined commits from C to A\\(and $D_B$ from C to B respectively)
      \item For each changed file, compare the blocks between the two diffs:
      \begin{itemize}
        \item If they apply changes to different blocks of the file, apply all changes
        \item If they apply changes to the same block and the change is the same, apply that change
        \item If they apply changes to the same block and the change is NOT the same, return a conflict
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\section{Constructing the Git Commit Graph}

\begin{frame}{Constructing the Git Commit Graph}
  \begin{block}{Topological Order}
    In order to construct the Git Commit Graph we need to have the commits in an order when no commit will appear after its parent, ie. in topological order.
  \end{block}
\end{frame}
\begin{frame}[fragile]
  \frametitle{Constructing the Git Commit Graph}
  \begin{block}{Kahn's algorithm, Kahn, Arthur B. (1962)}
    \begin{verbatim}
    L ← Empty list that will contain the sorted elements
    S ← Set of all nodes with no incoming edge

    while S is non-empty do
        remove a node n from S
        add n to tail of L
        for each node m with an edge e from n to m do
            remove edge e from the graph
            if m has no other incoming edges then
                insert m into S

    if graph has edges then
        return error   (graph has at least one cycle)
    else
        return L   (a topologically sorted order)
    \end{verbatim}
  \end{block}
\end{frame}
\begin{frame}{Constructing the Git Commit Graph}
  \begin{block}{Topological Sorting in Git}
    The standard algorithm for topological sorting is Kahn’s Algorithm.
    \begin{itemize}
      \item We first initialise $S$ with the 1 node: the current branch tip commit
      \item We consider the graph with the edges inverted (since we want to start from a graph leaf)
    \end{itemize}
    The basic way this algorithm works is by walking the commit graph in two passes:
    \begin{enumerate}
      \item The first pass computes the “in-degree” of each commit: how many commits have this commit as a parent? (This in-degree only cares about commits reachable from our starting position.)
      \item Walk the commit graph by selecting a commit with in-degree zero and decrementing the in-degree of its parents.
    \end{enumerate}
  \end{block}
\end{frame}

\begin{frame}{Constructing the Git Commit Graph}
  \begin{block}{Generation Numbers}
    We define the generation number of a commit as follows:
    \begin{itemize}
      \item If a commit has no parents, then its generation number is 1
      \item Otherwise, the generation number is the maximum generation number of its parents $+1$
    \end{itemize}
    Can be easily implemented using $DFS$.\\
    Note that the generation numbers of a commit and its parent can have a big difference.
  \end{block}
  \begin{block}{Property}
    Suppose A and B are commits with generation numbers gen(A) and gen(B). If gen(A) < gen(B) then A cannot reach B.
  \end{block}
\end{frame}

\begin{frame}{Constructing the Git Commit Graph}
  \begin{block}{Generation Number usages}
    Improvements in algorithms for
    \begin{itemize}
      \item “Can X Reach Y?” Questions
      \item Merge-Base Questions
      \item Topological Sorting
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Constructing the Git Commit Graph}
  \begin{block}{Practical issue with the Topological Sorting}
    In practice, when viewing the branch history, we only need the last few commits.
    The problem is, we need to walk the entire graph in order to guarantee the in-degree of a commit is zero ($\mathcal{O}(m+n)$).
  \end{block}
  \begin{block}{Generation Numbers to the rescue}
    The trick is to keep two commit walks going at the same time.
    One walk is in charge of computing in-degrees while the other is for walking the commits in topological order. Then the following applies:
    \begin{itemize}
      \item For each visited commit, store its Generation Number (in a priority queue)
      \item The in-degree walk only needs to advance when the topological order walk considers a commit for the next selection
      \item The in-degree walk advances by selecting a commit of maximum generation number
    \end{itemize}
    This way we can detect in constant time if we need to advance that walk.
  \end{block}
\end{frame}

\section{References}

\begin{frame}{References}
  \begin{itemize}
    \item \href{https://www.oreilly.com/library/view/version-control-with/9781449345037/ch04.html}{Version Control with Git, 2nd Edition\\Chapter 4: Basic Git Concepts} (O'Reilly)
    \item \href{https://git-scm.com/docs/git-merge}{git-merge} (Git documentation)
    \item \href{https://git-scm.com/docs/git-merge-base}{git-merge-base} (Git documentation)
    \item \href{https://stackoverflow.com/questions/14961255/how-does-git-merge-work-in-details}{Stack Overflow question: How does 'git merge' work in details?}
    \item \href{https://www.atlassian.com/git/tutorials/using-branches/git-merge}{Atlassian Git Tutorial: Git Merge}
    \item \href{https://devblogs.microsoft.com/devops/supercharging-the-git-commit-graph-iii-generations/}{Supercharging the Git Commit Graph III: Generations and Graph Algorithms} (Azure DevOps Blog)
    \item Kahn, Arthur B. (1962), "Topological sorting of large networks", Communications of the ACM, 5 (11): 558–562, doi:\href{https://doi.org/10.1145\%2F368996.369025}{10.1145/368996.369025}.
  \end{itemize}
\end{frame}

\end{document}

### 2020-03-05 complexity/presentation_sharp3sat_in_ip.tex
Complexity: Presentation: Included tex file for the presentation '#3SAT in IP'

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass{beamer}
\usetheme{Madrid}
\centering

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}

% Main document
\begin{document}
\title{\#3SAT $\in$ IP (Proof sketch)}
\author{Thomas Pappas}
%\date{4 March 2020}
\maketitle

% These three lines create an automatically generated table of contents.
\begin{frame}{Outline}
  \tableofcontents
\end{frame}

\section{Constructing the boolean polynomial}

\begin{frame}{Constructing the "boolean" polynomial}
  \begin{block}{Technique by Example}
    Let $\phi = (\neg x_1 \vee x_2 \vee x_3) \wedge (x_1 \vee x_2 \vee \neg x_3).$\\
    We consider a polynomial $q(x_1,x_2,x_3)$ such that if $(x_1^\prime,x_2^\prime,x_3^\prime)$ is a truth assignment for $\phi$ then $q(x_1^\prime,x_2^\prime,x_3^\prime)=1$ and $=0$ otherwise.
    For the example $\phi$ we get
    $$q(x_1,x_2,x_3)=[1-x_1(1-x_2)(1-x_3)][1-(1-x_1)(1-x_2)x_3]$$
    $$deg(q) \leq 3m$$
  \end{block}
  \begin{block}{Equivalence}
    We see that $\phi \in \#3SAT$ for a constant $K$ iff
    $$\sum_{b_1=0}^1 \sum_{b_2=0}^1 \sum_{b_3=0}^1 q(b_1,b_2,b_3) = K$$
  \end{block}
\end{frame}

\begin{frame}{Constructing the single variable "boolean" polynomial}
  \begin{block}{To avoid exponential computations}
    Since the $n$ variables and $m$ clauses could cause exponential calculatios, we observe that given a large enough prime number $p$
    $$\sum_{b_1=0}^1 \sum_{b_2=0}^1 \sum_{b_3=0}^1 q(b_1,b_2,b_3) = K$$ iff $$\sum_{b_1=0}^1 \sum_{b_2=0}^1 \sum_{b_3=0}^1 q(b_1,b_2,b_3) = K modp$$
  \end{block}
  \begin{block}{But why a prime number?}
    By selecting a prime number for this task, we achieve that the resulting ring is a field.
  \end{block}
\end{frame}

\section{Constructing the single variable boolean polynomial}

\begin{frame}{Constructing the single variable "boolean" polynomial}
  \begin{block}{}
    Now consider the following single variable polynomial
    $$r(X_1) = \sum_{b_2=0}^1 \sum_{b_3=0}^1 q(x_1,b_2,b_3)$$
    $$deg(r) \leq 3m$$
    It follows that $r(0)+r(1)=K$.
  \end{block}
\end{frame}

\section{Prover-Verifier Interaction}

\begin{frame}{Prover-Verifier Interaction}
  \begin{block}{}
    For a Prover $P$ and a Verifier $V$:
    \begin{itemize}
      \item $P$ and $V$ both construct the polynomial $q$
      \item $P$ sends a prime number $p$ of $2n$ bits
      \item $P$ sends the $r(X_1)$ to $V$
      \item $V$ starts the verification
        \begin{itemize}
          \item if $r(0)+r(1)=K modp$ then check if $r(\alpha) = q(\alpha,b_2,b_3) modp$ for an $\alpha \neq 0,1$ and accept/reject accordingly with probability of success $\frac{3m}{2^{2n}}$
          \item if $r(0)+r(1)\neq K modp$ then reject
        \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\section{References}

\begin{frame}{References}
  \begin{itemize}
    \item LUND, C., FORTNOW, L., KARLOFF, H., AND NISAN, N. 
      \href{https://users.cs.fiu.edu/~giri/teach/5420/f01/LundIPS.pdf}{Algebraic methods for interactive proof systems},
      In Proceedings of 31st Symposium on Fottndations of Computer Science (EEE, New York, 1990, pp. 2-90)
    \item \href{https://www.youtube.com/watch?v=yS9WrISP_Ug&list=PLm3J0oaFux3YL5vLXpzOyJiLtqLp6dCW2&index=26}{Undergrad Complexity at CMU - Lecture 25: Interactive Proofs: IP=PSPACE}
  \end{itemize}
\end{frame}

\end{document}

### 2020-04-05 typesys/exer01.tex
TypeSys: Exer01: Included all exercises but 1.6
Draft solutions, they need vetting

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}

% More packages and macros
\usepackage[inference]{semantic}

\newcommand\nlambda[1]{\ensuremath{\lambda #1.\,}}
\newcommand\nred{\ensuremath{\longrightarrow}}

% Main document
\begin{document}
\title{1η Σειρά Ασκήσεων}
\author{Θωμάς Παππάς}
\date{28 Δεκεμβρίου 2019}
\maketitle

\section{Λάμβδα λογισμός χωρίς τύπους}

\subsection*{Άσκηση 1.1  Αναπαράσταση λιστών}

Αρχικά παρατηρούμε ότι μια λίστα $t$, πχ με $3$ στοιχεία $[x, y, z]$ είναι της μορφής
$$t = \nlambda{c} \nlambda{n} c x (c y (c z n))$$

\subsubsection*{nil}
Για την αναπαράσταση του \verb|nil| θα θέλουμε η συνάρτηση $c$ να μην εφαρμοστεί καθόλου οπότε παίρνουμε
$$\verb|nil| = \nlambda{c} \nlambda{n} n$$
το οποίο και είναι το ίδιο "pun" με το \verb|false| στα Church booleans και το $c_0$ στα Church numerals.

\subsubsection*{cons}
Για να προσθέσουμε ένα στοιχείο $h$ σε μια λίστα $t$, τότε αρκεί να καλέσουμε τη συνάρτηση $c$ της $t$ με τη λίστα $t$ και το στοιχείο $h$. Δηλαδή
$$\verb|cons| = \nlambda{t} \nlambda{h} \nlambda{c} \nlambda{n} c\ h\ (t\ c\ n)$$

\subsubsection*{isnil}
Για την υλοποίηση του \verb|isnil| θα χρησιμοποιήσουμε ένα ανάλογο κόλπο με αυτό του \verb|iszro| για τα Church numerals. Η συνάρτηση θα πρέπει να επιστρέφει \verb|true| όταν η συνάρτηση \verb|c| δεν τρέξει καθόλου, και \verb|false| όταν τρέξει έστω και μία φορά.
$$\verb|isnil| = \nlambda{t} t\ (\nlambda{x} \nlambda{y} \verb|false|)\ \verb|true|$$

\subsubsection*{head}
Εδώ για να πάρουμε το πρώτο στοιχείο του πίνακα, αρκεί να εφαρμόσουμε τη συνάρτηση $c= \verb|true|$ στη λίστα (με αδιάφορο το \verb|n|, εδώ θα βάλουμε τυχαία \verb|false|) και αυτή θα επιστρέψει το πρώτο της στοιχείο.
$$\verb|head| = \nlambda{t} t\ \verb|true|\ \verb|false|$$
Ερώτηση (TODO): Εδώ αυτό λειτουργεί διότι δεν είμαστε σε typed λ-calculus, σωστά; Διαφορετικά (όπως στη Haskell) για \verb|n| θα πρέπει να δώσουμε ένα στοιχείο στον ίδιο τύπο με τον τύπο των στοιχείων της λίστας.

\subsubsection*{tail}
Όπως συμβουλεύει και η υπόδειξη στην άσκηση, θα θεωρήσουμε μια συνάρτηση που θα φτιάχνει ζευγάρια (\verb|pair|) λιστών τα οποία θα αυξάνονται κατά ένα κάθε φορά (με κάθε κλήση της συνάρτησης στη λίστα), και στο τέλος θα πάρω το πρώτο στοιχείο του \verb|pair| όπου θα βρίσκεται η λίστα της προηγούμενης κλήσης της συνάρτησης. Δηλαδή έχουμε:
\[\verb|nn = pair nil nil|\]
\[\verb|cc| = \nlambda{x} \nlambda{p} \verb|pair (snd p) (cons x (snd p))|\]
και οπότε
\[\verb|tail| = \nlambda{t} \verb|fst (t cc nn)|\]

\subsection*{Άσκηση 1.2 Λίστες και σταθερά σημεία}

Για να φτιάξουμε τη συνάρτηση \verb|sumarise| που αθροίζει τα στοιχεία μιας λίστας \verb|t|, αρκεί να γράψουμε μια αναδρομική συνάρτηση που να το υπολογίζει και να χρησιμοποιήσουμε τη συνάρτηση \verb|fix| για να την υλοποιήσουμε. Οπότε αν
\[\verb|s| = \nlambda{sum} \nlambda{t} \verb|if isnil t then c|_0\verb| else plus (head t) (sum (tail t))|\]
τότε έχουμε
\[\verb|summary| = \verb|fix s|\]

TODO: Να δείξω και το πώς δουλεύει η λούπα ή το παραπάνω αρκεί;

\subsection*{Άσκηση 1.3 Διαφορετικές στρατηγικές αποτίμησης}
Οι κανόνες αποτίμησης του Figure 5-3 στη σελίδα 72 του βιβλίου του Pierce θα πρέπει να προσαρμοστούν ως εξής για την κάθε στρατηγική που θα επιλέξουμε:

Ερώτηση (TODO): "values are possible results for our evaluation", οπότε δεν χρειάζεται να αλλάξουμε τον ορισμό των values για να επιτρέψουμε αποτιμήσεις στα λ-abstractions, σωστά;\\
Αν όχι τότε αλλάζω τα values ως εξής: $\verb|v := |\nlambda{x} \verb|v|$

\subsubsection*{full beta reduction}
Εδώ αρκεί να προσθέσουμε τους εξής κανόνες
\[
  \inference[E-APP3: ]{%
    t_2 \nred t'_2
  }{%
    t_1 t_2 \nred t_1 t'_2
  }
\]
\[
  \inference[E-APP4: ]{%
    t_1 \nred t'_1
  }{%
    \nlambda{x} t_1 \nred \nlambda{x} t'_1
  }
\]
και μπορούμε μετά να αφαιρέσουμε τον \verb|E-APP2| δεδομένου ότι ο δεύτερος κανόνας από τους παραπάνω καλύπτει και την περίπτωση $\verb|v|_1\verb|t|_1$.

\subsubsection*{normal-order}
Εδώ θα χρειαστούμε πάλι τον \verb|E-APP3| αλλά μετά θα πρέπει να αφαιρέσουμε τον \verb|E-APP2| έτσι ώστε να απαγορεύσουμε αποτιμήσεις από τα δεξιά.

\subsubsection*{lazy evaluation}
Εδώ (λογικά) θα αρκεί να προσθέσουμε στους κανόνες του Figure 5-3 το \verb|E-APP4| και είμαστε έτοιμοι.

\subsection*{Άσκηση 1.4 Μέγιστος κοινός διαιρέτης}

\begin{verbatim}
/* Exer01-1.4 OCaml implementation. */

fix = lambda f.(lambda x.f (lambda y.x x y)) (lambda x.f (lambda y.x x y));

/* Recurcive function for subtracting two numerals. */
subr = lambda sub.lambda m.lambda n.if iszero n then m else sub (pred m) (pred n);
sub = fix subr;

/* Recurcive function MOD of two numerals. */
modr = lambda mod.lambda m.lambda n.if iszero (sub m n) then
  (if iszero (sub n m) then 0 else m) else mod (sub m n) n;
mod = fix modr;

/* The GCD function! */
gcdr = lambda gcd.lambda m.lambda n.if iszero n then m else gcd n (mod m n);
gcd = fix gcdr;

/* Print the examples. */
gcd 24 42;
gcd 42 17;
gcd 714 630;
gcd 85 204;
\end{verbatim}

\section{Απλοί τύποι}

\subsection*{Άσκηση 1.5 Subject expansion}

\subsubsection*{1. Γλώσσα αριθμητικών εκφράσεων}
Για τη γλώσσα των αριθμητικών εκφράσεων ΔΕΝ ισχύει το Subject expansion.
Αν θέσουμε
$$t = \verb|if true then 0 else false|$$
$$t^\prime = \verb|0|$$
τότε βλέπουμε ότι $t \nred t^\prime$ με $t^\prime:\verb|Bool|$ ενώ το $t$ δεν είναι well-typed.

\subsubsection*{2. $\lambda$-λογισμός με απλούς τύπους}
Αρχικά παρατηρούμε ότι αν ο $t$ είναι well-typed τότε παίρνουμε το ζητούμενο, αφού αν $\Gamma \vdash t:T^\prime$ με $T^\prime \neq T$ τότε από το Preservation theorem παίρνουμε ότι $\Gamma \vdash t^\prime:T^\prime$ το οποίο είναι άτοπο.
Αρκεί λοιπόν να δείξουμε ότι όλοι οι όροι του συναρτισιακού $\lambda$-λογισμού είναι well-typed.

Προφανώς ο $t$ δεν γίνεται να είναι value εφόσον τότε δεν υπάρχει κάποιο $t^\prime$ τέτοιο ώστε $t\nred t^\prime$.
Εάν τώρα ο $t$ είναι κάποιος base term του $\Gamma$ (που δεν περιέχει conditional expressions) τότε είτε $t:\verb|Bool|$ είτε $t:\verb|Nat|$ και άρα είναι well-typed.
Αυτό διότι οποιοσδήποτε άλλος ill-typed όρος (πχ. \verb|succ false|) πάλι δεν μπορεί να γίνει evaluate σε κάποιο $t^\prime$.

\vspace{5mm}

Question: Τι context έχουμε εδώ;

\vspace{5mm}

Για την περίπτωση που $t$ είναι application term της μορφής $t_1 t_2$, θα δείξουμε το ζητούμενο με επαγωγή. Έστω λοιπόν ότι το Subject expansion ισχύει για κάθε υποόρο του $t$, δηλαδή και για για τα $t_1,t_2$.

Αν για το evaluation χρησιμοποιήσαμε τον κανόνα \textsc{E-App1} τότε υπάρχει ένα $t_1^\prime$ τέτοιο ώστε $t^\prime=t_1^\prime t_2$ και άρα από το Inversion lemma (3) παίρνουμε ότι υπάρχει τύπος $T_{11}$ τέτοιος ώστε\\$\Gamma \vdash t_1^\prime:T_{11} \rightarrow T$ και $\Gamma \vdash t_2:T_{11}$.
Από τον πρώτο κανόνα και την επαγωγική υπόθεση παίρνουμε ότι $\Gamma \vdash t_1:T_{11}$ και άρα (αφού $\Gamma \vdash t_2:T_{11}$ και χρησιμοποιώντας τον \textsc{T-App}) έχουμε $\Gamma \vdash t:T$.

Ομοίως για την περίπτωση που για το evaluation χρησιμοποιήσαμε τον κανόνα \textsc{E-App2}.

Έστω τώρα ότι για το evaluation χρησιμοποιήσαμε τον κανόνα \textsc{E-AppAbs}, δηλαδή $t_1 = \lambda x:T_{11}.t_{12}$ και $t_2$ είναι value με $\Gamma \vdash t_2:T_{11}$.
Τότε θα πρέπει $\Gamma \vdash t_{12}:T$ αφού έχουμε ότι $t^\prime = [x \mapsto t_2]t_{12}$ και $\Gamma \vdash t^\prime:T$, και άρα αν ο $t{12}$ έχει άλλο τύπο ή δεν είναι well-typed τότε φτάνουμε σε άτοπο. Οπότε έχουμε $\Gamma \vdash t_1:T_{11} \rightarrow T, t_2:T_{11}$ και από τον \textsc{E-App1} παίρνουμε $\Gamma \vdash T$.

\vspace{5mm}

Άρα σε κάθε περίπτωση το Subject expansion ισχύει.

\subsection*{Άσκηση 1.6 Κατάσταση σφάλματος}

\end{document}

### 2020-04-05 typesys/exer02.tex
TypeSys: Exer02: Included exercise 2.1

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}

% More packages and macros
\usepackage[inference]{semantic}

\newcommand\nlambda[1]{\ensuremath{\lambda #1.\,}}
\newcommand\nred{\ensuremath{\longrightarrow}}

% Main document
\begin{document}
\title{2η Σειρά Ασκήσεων}
\author{Θωμάς Παππάς}
\date{12 Ιανουαρίου 2020}
\maketitle

\section{Επεκτάσεις}

\subsection*{Άσκηση 2.1  Ascription}

\subsubsection*{(1)}
Θέτουμε λοιπόν την derived form του \verb|Ascription| ως εξής: ένας όρος $t\verb| as |T$ μπορεί να γραφτεί ως $(\lambda x:T.x)t$.
Θα δείξουμε τώρα ότι οι κανόνες evaluation και typing στα δύο type systems είναι ισοδύναμα.
Προφανώς αν ο όρος $t$ δεν είναι τύπου $T$ τότε ο typechecker θα επιστρέψει error και στις δύο περιπτώσεις.

Εστω λοιπόν $\lambda^E, \lambda^I, e$ η εξωτερική γλώσσα (με το \verb|Ascription|), η εσωτερική γλώσσα (το simply typed $\lambda$-calculus) και την elaboration function που μετατρέπει τους ascription όρους στην derived form τους.
Παρατηρούμε ότι (επαγωγική υπόθεση)
\begin{itemize}
  \item Αν $t = v_1\verb| as |T$, όπου $v_1$ value τότε
    \begin{itemize}
      \item $t = v_1\verb| as |T \nred_E v_1$
      \item $e(t) = (\lambda x:T.x)v_1 \nred_I v_1$
    \end{itemize}
  \item Αν $t = t_1\verb| as |T$ με $t_1 \nred_E t_1^\prime$ για κάποιους όρους $t_1,t_1^\prime$ που ΔΕΝ περιέχουν ascription (άρα και $t_1 \nred_I t_1^\prime$) τότε
    \begin{itemize}
      \item $t \nred_E t^\prime$ όπου $t^\prime = t_1^\prime\verb| as |T$ (από τον \textsc{E-Ascribe1})
      \item $e(t) = (\lambda x:T.x)t_1 \nred_I (\lambda x:T.x)t_1^\prime = e(t^\prime)$
    \end{itemize}
\end{itemize}
Και άρα για έναν τυχαίο τύπο $t$ μπορούμε με τα παραπάνω να κάνουμε επαγωγή στους υποτύπους του και να πάρουμε ότι $t \nred_E t^\prime$ iff $e(t) \nred_I e(t^\prime)$.

Επίσης βλέπουμε ότι $\Gamma \vdash^E t:T$ ανν $\Gamma \vdash^I e(t):T$ αφού $\Gamma \vdash^I (\lambda x:T.x): T \rightarrow T$, και άρα το \verb|Ascription| είναι derived form.

\subsubsection*{(2)}
Με τον κανόνα \textsc{E-AscribeEager} το \verb|Ascription| ΔΕΝ μπορεί να είναι derived form από τον simply $\lambda$-calculus. Αυτό διότι αν θέσουμε οποιοδήποτε όρο που να συμπεριλαμβάνει τον $t$ τότε θα πρέπει να κάνουμε πρώτα αυτόν evaluate με τον $t$ χωρίς να έχει γίνει ο ίδιος evaluate, το οποίο δεν υπάρχει σε κάποιο υπάρχον evaluation rule, και άρα θα έχουμε μια καινούργια συμπεριφορά στο type system μας.

\end{document}

### 2020-04-11 typesys/exer01.tex
TypeSys: Exer01: Addded exercise 1.6 and made improvements to all of them

@@
 $$\verb|nil| = \nlambda{c} \nlambda{n} n$$
-το οποίο και είναι το ίδιο "pun" με το \verb|false| στα Church booleans και το $c_0$ στα Church numerals.
+το οποίο και είναι το ίδιο ``pun'' με το \verb|false| στα Church booleans και το $c_0$ στα Church numerals.
 
@@
 $$\verb|head| = \nlambda{t} t\ \verb|true|\ \verb|false|$$
-Ερώτηση (TODO): Εδώ αυτό λειτουργεί διότι δεν είμαστε σε typed λ-calculus, σωστά; Διαφορετικά (όπως στη Haskell) για \verb|n| θα πρέπει να δώσουμε ένα στοιχείο στον ίδιο τύπο με τον τύπο των στοιχείων της λίστας.
 
@@
 
-TODO: Να δείξω και το πώς δουλεύει η λούπα ή το παραπάνω αρκεί;
-
 \subsection*{Άσκηση 1.3 Διαφορετικές στρατηγικές αποτίμησης}
@@
 
-Ερώτηση (TODO): "values are possible results for our evaluation", οπότε δεν χρειάζεται να αλλάξουμε τον ορισμό των values για να επιτρέψουμε αποτιμήσεις στα λ-abstractions, σωστά;\\
-Αν όχι τότε αλλάζω τα values ως εξής: $\verb|v := |\nlambda{x} \verb|v|$
-
 \subsubsection*{full beta reduction}
-Εδώ αρκεί να προσθέσουμε τους εξής κανόνες
+Αρχικά θα κρατήσουμε τον \textsc{E-App1} θα αντικαταστήσουμε τους \textsc{E-App2} και \textsc{E-AppAbs} με πιο τους πιο γενικούς κανόνες
 \[
-  \inference[E-APP3: ]{%
+  \inference[\textsc{E-App2-Gen}: ]{%
     t_2 \nred t'_2
@@
 \[
-  \inference[E-APP4: ]{%
+  \textsc{E-AppAbs-Gen}: (\nlambda{x} t_{12}) t_2 \nred [x \mapsto t_2] t_{12}
+\]
+και τέλος θα επιτρέψουμε τις αποτιμήσεις μέσα στα abstractions.
+\[
+  \inference[\textsc{E-App3}: ]{%
     t_1 \nred t'_1
@@
 \]
-και μπορούμε μετά να αφαιρέσουμε τον \verb|E-APP2| δεδομένου ότι ο δεύτερος κανόνας από τους παραπάνω καλύπτει και την περίπτωση $\verb|v|_1\verb|t|_1$.
+Επίσης λόγω του \textsc{E-App3} θα πρέπει να περιορίσουμε τα values στα abstractions που επιστρέφουν όρους με είτε μόνο μεταβλητές είτε values είτε ένα συνδιασμό των δύο.
+Αν θέσουμε ως $\verb|t|_{\verb|v|}$ έναν τέτοιο όρο τότε έχουμε
+\[
+  \verb|v| := \nlambda{x} \verb|t|_{\verb|v|}
+\]
+% Question: Το από πάνω δεν ορίζει αυστηρά το "είτε μόνο μεταβλητές είτε values είτε ένα συνδιασμό των δύο"; Μάλλον όχι...
 
 \subsubsection*{normal-order}
-Εδώ θα χρειαστούμε πάλι τον \verb|E-APP3| αλλά μετά θα πρέπει να αφαιρέσουμε τον \verb|E-APP2| έτσι ώστε να απαγορεύσουμε αποτιμήσεις από τα δεξιά.
+Εδώ θα κρατήσουμε τους κανόνες \textsc{E-App1} και \textsc{E-App2} αλλά θα αντικαταστήσουμε τον \textsc{E-AppAbs} με τον ``αντίστροφο'' (σχετικά με το ποιος όρος πρέπει να είναι value και ποιος όχι)
+\[
+  \textsc{E-AppAbs-Rev}: (\nlambda{x} \verb|v|_{12}) t_2 \nred [x \mapsto t_2] \verb|v|_{12}
+\]
+και τέλος θα πάρουμε και τον \textsc{E-App3} και τον ορισμό των values από το προηγούμενο ερώτημα ώστε να επιτρέψουμε αποτιμήσεις μέσα στα abstractions.
 
-\subsubsection*{lazy evaluation}
-Εδώ (λογικά) θα αρκεί να προσθέσουμε στους κανόνες του Figure 5-3 το \verb|E-APP4| και είμαστε έτοιμοι.
+\subsubsection*{lazy evaluation (call by name)}
+Ομοίως με το προηγούμενο χωρίς τον \textsc{E-App3}, οπότε κρατάμε μόνο τους κανόνες \textsc{E-App1}, \textsc{E-App2} και \textsc{E-AppAbs-Rev} καθώς και τον αρχικό ορισμό για τα values (από το Figure 5-3).
 
@@
 
+\pagebreak
+
 \section{Απλοί τύποι}
@@
 $$t = \verb|if true then 0 else false|$$
-$$t^\prime = \verb|0|$$
-τότε βλέπουμε ότι $t \nred t^\prime$ με $t^\prime:\verb|Bool|$ ενώ το $t$ δεν είναι well-typed.
+$$t' = \verb|0|$$
+τότε βλέπουμε ότι $t \nred t'$ με $t':\verb|Bool|$ ενώ το $t$ δεν είναι well-typed.
 
 \subsubsection*{2. $\lambda$-λογισμός με απλούς τύπους}
-Αρχικά παρατηρούμε ότι αν ο $t$ είναι well-typed τότε παίρνουμε το ζητούμενο, αφού αν $\Gamma \vdash t:T^\prime$ με $T^\prime \neq T$ τότε από το Preservation theorem παίρνουμε ότι $\Gamma \vdash t^\prime:T^\prime$ το οποίο είναι άτοπο.
+Αρχικά παρατηρούμε ότι αν ο $t$ είναι well-typed τότε παίρνουμε το ζητούμενο, αφού αν $\Gamma \vdash t:T'$ με $T' \neq T$ τότε από το Preservation theorem παίρνουμε ότι $\Gamma \vdash t':T'$ το οποίο είναι άτοπο.
 Αρκεί λοιπόν να δείξουμε ότι όλοι οι όροι του συναρτισιακού $\lambda$-λογισμού είναι well-typed.
 
-Προφανώς ο $t$ δεν γίνεται να είναι value εφόσον τότε δεν υπάρχει κάποιο $t^\prime$ τέτοιο ώστε $t\nred t^\prime$.
+Προφανώς ο $t$ δεν γίνεται να είναι value εφόσον τότε δεν υπάρχει κάποιο $t'$ τέτοιο ώστε $t\nred t'$.
 Εάν τώρα ο $t$ είναι κάποιος base term του $\Gamma$ (που δεν περιέχει conditional expressions) τότε είτε $t:\verb|Bool|$ είτε $t:\verb|Nat|$ και άρα είναι well-typed.
-Αυτό διότι οποιοσδήποτε άλλος ill-typed όρος (πχ. \verb|succ false|) πάλι δεν μπορεί να γίνει evaluate σε κάποιο $t^\prime$.
-
-\vspace{5mm}
-
-Question: Τι context έχουμε εδώ;
+Αυτό διότι οποιοσδήποτε άλλος ill-typed όρος (πχ. \verb|succ false|) πάλι δεν μπορεί να γίνει evaluate σε κάποιο $t'$.
 
@@
 Για την περίπτωση που $t$ είναι application term της μορφής $t_1 t_2$, θα δείξουμε το ζητούμενο με επαγωγή.
-Έστω λοιπόν ότι το Subject expansion ισχύει για κάθε υποόρο του $t$, δηλαδή και για για τα $t_1,t_2$.
+Έστω λοιπόν ότι το Subject expansion ισχύει για κάθε υποόρο του $t$, δηλαδή και για τα $t_1,t_2$.
 
-Αν για το evaluation χρησιμοποιήσαμε τον κανόνα \textsc{E-App1} τότε υπάρχει ένα $t_1^\prime$ τέτοιο ώστε $t^\prime=t_1^\prime t_2$ και άρα από το Inversion lemma (3) παίρνουμε ότι υπάρχει τύπος $T_{11}$ τέτοιος ώστε\\$\Gamma \vdash t_1^\prime:T_{11} \rightarrow T$ και $\Gamma \vdash t_2:T_{11}$.
+Αν για το evaluation χρησιμοποιήσαμε τον κανόνα \textsc{E-App1} τότε υπάρχει ένα $t_1'$ τέτοιο ώστε $t'=t_1' t_2$ και άρα από το Inversion lemma (3) παίρνουμε ότι υπάρχει τύπος $T_{11}$ τέτοιος ώστε\\$\Gamma \vdash t_1':T_{11} \rightarrow T$ και $\Gamma \vdash t_2:T_{11}$.
 Από τον πρώτο κανόνα και την επαγωγική υπόθεση παίρνουμε ότι $\Gamma \vdash t_1:T_{11}$ και άρα (αφού $\Gamma \vdash t_2:T_{11}$ και χρησιμοποιώντας τον \textsc{T-App}) έχουμε $\Gamma \vdash t:T$.
@@
 Έστω τώρα ότι για το evaluation χρησιμοποιήσαμε τον κανόνα \textsc{E-AppAbs}, δηλαδή $t_1 = \lambda x:T_{11}.t_{12}$ και $t_2$ είναι value με $\Gamma \vdash t_2:T_{11}$.
-Τότε θα πρέπει $\Gamma \vdash t_{12}:T$ αφού έχουμε ότι $t^\prime = [x \mapsto t_2]t_{12}$ και $\Gamma \vdash t^\prime:T$, και άρα αν ο $t{12}$ έχει άλλο τύπο ή δεν είναι well-typed τότε φτάνουμε σε άτοπο.
-Οπότε έχουμε $\Gamma \vdash t_1:T_{11} \rightarrow T, t_2:T_{11}$ και από τον \textsc{E-App1} παίρνουμε $\Gamma \vdash T$.
+Τότε θα πρέπει $\Gamma \vdash t_{12}:T$ αφού έχουμε ότι $t' = [x \mapsto t_2]t_{12}$ και $\Gamma \vdash t':T$, και άρα αν ο $t_{12}$ έχει άλλο τύπο ή δεν είναι well-typed τότε φτάνουμε σε άτοπο.
+Οπότε έχουμε $\Gamma \vdash t_1:T_{11} \rightarrow T, t_2:T_{11}$ και από τον \textsc{T-App1} παίρνουμε $\Gamma \vdash t:T$.
 
@@
 
+\subsubsection*{Περιγραφή της γλώσσας}
+Για τη γλώσσα που προκύπτει από το συνδυασμό της απλής αριθμητικής και του $\lambda$-λογισμού με απλούς τύπους, θα επεκτείνουμε τους ορισμούς στα Figures 8.2 και 9.1 του βιβλίου.
+
+\pagebreak
+
+\paragraph*{Σύνταξη}:
+Επεκτείνουμε τους όρους (terms), values και Types αντίστοιχα ως εξής
+
+\verb|t ::=|
+
+\begin{tabular}{l r}
+  \verb|wrong| & \textit{constant wrong}
+\end{tabular}
+
+\verb|v ::=|
+
+\begin{tabular}{l r}
+  \verb|wrong| & \textit{wrong value}
+\end{tabular}
+
+\verb|Τ ::=|
+
+\begin{tabular}{l r}
+  \verb|Wrong| & \textit{wrong type}
+\end{tabular}
+
+\paragraph*{Λειτουργική Σημασιολογία}:
+\[
+  \verb|if 0 then | t_1 \verb| else | t_2 \nred \verb|wrong|
+\]
+\[
+  \verb|if (succ | t_1 \verb|) then | t_2 \verb| else | t_3 \nred \verb|wrong|
+\]
+\[
+  \verb|if (pred | t_1 \verb|) then | t_2 \verb| else | t_3 \nred \verb|wrong|
+\]
+\[
+  \verb|if (| \nlambda{x} t_1 \verb|) then | t_2 \verb| else | t_3 \nred \verb|wrong|
+\]
+\[
+  \verb|if wrong then | t_1 \verb| else | t_2 \nred \verb|wrong|
+\]
+\[
+  \verb|succ true| \nred \verb|wrong|, \;
+  \verb|pred true| \nred \verb|wrong|, \;
+  \verb|iszero true| \nred \verb|wrong|
+\]
+\[
+  \verb|succ false| \nred \verb|wrong|, \;
+  \verb|pred false| \nred \verb|wrong|, \;
+  \verb|iszero false| \nred \verb|wrong|
+\]
+\[
+  \verb|succ(| \nlambda{x} t \verb|)| \nred \verb|wrong|, \;
+  \verb|pred(| \nlambda{x} t \verb|)| \nred \verb|wrong|, \;
+  \verb|iszero(| \nlambda{x} t \verb|)| \nred \verb|wrong|
+\]
+\[
+  \verb|succ wrong| \nred \verb|wrong|, \;
+  \verb|pred wrong| \nred \verb|wrong|, \;
+  \verb|iszero wrong| \nred \verb|wrong|
+\]
+
+\paragraph*{Σύστημα Τύπων}:
+\[
+  \inference{
+    \Gamma \vdash t_1:\texttt{Nat} & \Gamma \vdash t_2:T_1 & \Gamma \vdash t_3:T_2
+  }{
+    \Gamma \vdash \texttt{if } t_1 \texttt{ then } t_2 \texttt{ else } t_3: \texttt{Wrong}
+  }
+\]
+\[
+  \inference{
+    \Gamma \vdash t_1:T_{11} \rightarrow T_{12} & \Gamma \vdash t_2:T_1 & \Gamma \vdash t_3:T_2
+  }{
+    \Gamma \vdash \texttt{if } t_1 \texttt{ then } t_2 \texttt{ else } t_3: \texttt{Wrong}
+  }
+\]
+\[
+  \inference{
+    \Gamma \vdash t_1:\texttt{Wrong} & \Gamma \vdash t_2:T_1 & \Gamma \vdash t_3:T_2
+  }{
+    \Gamma \vdash \texttt{if } t_1 \texttt{ then } t_2 \texttt{ else } t_3: \texttt{Wrong}
+  }
+\]
+\[
+  \inference{
+    \Gamma \vdash t_1:\texttt{Bool}
+  }{
+    \Gamma \vdash \texttt{succ } t_1: \texttt{Wrong}
+  },
+  \inference{
+    \Gamma \vdash t_1:\texttt{Bool}
+  }{
+    \Gamma \vdash \texttt{pred } t_1: \texttt{Wrong}
+  },
+  \inference{
+    \Gamma \vdash t_1:\texttt{Bool}
+  }{
+    \Gamma \vdash \texttt{iszero } t_1: \texttt{Wrong}
+  }
+\]
+\[
+  \inference{
+    \Gamma \vdash t_1:T_{11} \rightarrow T_{12}
+  }{
+    \Gamma \vdash \texttt{succ } t_1: \texttt{Wrong}
+  },
+  \inference{
+    \Gamma \vdash t_1:T_{11} \rightarrow T_{12}
+  }{
+    \Gamma \vdash \texttt{pred } t_1: \texttt{Wrong}
+  },
+  \inference{
+    \Gamma \vdash t_1:T_{11} \rightarrow T_{12}
+  }{
+    \Gamma \vdash \texttt{iszero } t_1: \texttt{Wrong}
+  }
+\]
+\[
+  \inference{
+    \Gamma \vdash t_1:\texttt{Wrong}
+  }{
+    \Gamma \vdash \texttt{succ } t_1: \texttt{Wrong}
+  },
+  \inference{
+    \Gamma \vdash t_1:\texttt{Wrong}
+  }{
+    \Gamma \vdash \texttt{pred } t_1: \texttt{Wrong}
+  },
+  \inference{
+    \Gamma \vdash t_1:\texttt{Wrong}
+  }{
+    \Gamma \vdash \texttt{iszero } t_1: \texttt{Wrong}
+  }
+\]
+\[
+  \inference{
+    \Gamma \vdash t_1:T_{11} \rightarrow T_{12} & \Gamma \vdash t_2:T_2, T_{11} \neq T_2
+  }{
+    \Gamma \vdash t_1 t_2: \texttt{Wrong}
+  }
+\]
+
+\subsubsection*{Type Safety}
+Με τους παραπάνω κανόνες καταλήγουμε σε ένα σύστημα όπου δεν υπάρχουν ``stuck'' όροι, και άρα η ιδιότητα \textit{Progress} δεν μας προσφέρει κάτι.
+Ο ορισμός του \textit{Preservation} τώρα μπορεί να προσαρμοστεί ως εξής
+\begin{center}
+ \textit{Preservation:} Ένας όρος που ΔΕΝ έχει type \verb|Wrong| και κάνει ένα evaluation βήμα, τότε και ο όρος που θα επιστραφεί επίσης ΔΕΝ θα έχει type \verb|Wrong|
+\end{center}
+
 \end{document}

### 2020-04-19 typesys/exer02.tex
TypeSys: Exer02: Added exercises 2.3 and 2.4 and the OCaml implementation of the first
2.3 is most certainly false, but that's how far I managed to get

@@
 \usepackage[inference]{semantic}
+\usepackage{listings}% http://ctan.org/pkg/listings
+\lstset{
+  basicstyle=\ttfamily,
+  mathescape
+}
 
@@
 \subsubsection*{(1)}
-Θέτουμε λοιπόν την derived form του \verb|Ascription| ως εξής: ένας όρος $t\verb| as |T$ μπορεί να γραφτεί ως $(\lambda x:T.x)t$.
+Θέτουμε λοιπόν την derived form του \verb|Ascription| ως εξής: ένας όρος $t\verb| as |T$ μπορεί να γραφτεί ως $(\nlambda{x:T} x)t$.
 Θα δείξουμε τώρα ότι οι κανόνες evaluation και typing στα δύο type systems είναι ισοδύναμα.
@@
       \item $t = v_1\verb| as |T \nred_E v_1$
-      \item $e(t) = (\lambda x:T.x)v_1 \nred_I v_1$
+      \item $e(t) = (\nlambda{x:T} x)v_1 \nred_I v_1$
     \end{itemize}
-  \item Αν $t = t_1\verb| as |T$ με $t_1 \nred_E t_1^\prime$ για κάποιους όρους $t_1,t_1^\prime$ που ΔΕΝ περιέχουν ascription (άρα και $t_1 \nred_I t_1^\prime$) τότε
+  \item Αν $t = t_1\verb| as |T$ με $t_1 \nred_E t_1'$ για κάποιους όρους $t_1,t_1'$ που ΔΕΝ περιέχουν ascription (άρα και $t_1 \nred_I t_1'$) τότε
     \begin{itemize}
-      \item $t \nred_E t^\prime$ όπου $t^\prime = t_1^\prime\verb| as |T$ (από τον \textsc{E-Ascribe1})
-      \item $e(t) = (\lambda x:T.x)t_1 \nred_I (\lambda x:T.x)t_1^\prime = e(t^\prime)$
+      \item $t \nred_E t'$ όπου $t' = t_1'\verb| as |T$ (από τον \textsc{E-Ascribe1})
+      \item $e(t) = (\nlambda{x:T} x)t_1 \nred_I (\nlambda{x:T} x)t_1' = e(t')$
     \end{itemize}
 \end{itemize}
-Και άρα για έναν τυχαίο τύπο $t$ μπορούμε με τα παραπάνω να κάνουμε επαγωγή στους υποτύπους του και να πάρουμε ότι $t \nred_E t^\prime$ iff $e(t) \nred_I e(t^\prime)$.
+Και άρα για έναν τυχαίο τύπο $t$ μπορούμε με τα παραπάνω να κάνουμε επαγωγή στους υποτύπους του και να πάρουμε ότι $t \nred_E t'$ iff $e(t) \nred_I e(t')$.
 
-Επίσης βλέπουμε ότι $\Gamma \vdash^E t:T$ ανν $\Gamma \vdash^I e(t):T$ αφού $\Gamma \vdash^I (\lambda x:T.x): T \rightarrow T$, και άρα το \verb|Ascription| είναι derived form.
+Επίσης βλέπουμε ότι $\Gamma \vdash^E t:T$ ανν $\Gamma \vdash^I e(t):T$ αφού $\Gamma \vdash^I (\nlambda{x:T} x): T \rightarrow T$, και άρα το \verb|Ascription| είναι derived form.
 
@@
 
+\subsection*{Άσκηση 2.2  Αθροίσματα και λογικές τιμές}
+
+Ορίζουμε τους όρους \verb|true|, \verb|false| και \verb|if| ως εξής:
+\begin{itemize}
+  \item $\verb|true| := \verb|inl unit as Unit+Unit|$
+  \item $\verb|false| := \verb|inr unit as Unit+Unit|$
+  \item $\verb|if | t_1 \verb| then | t_2 \verb| else | t_3 := \verb|case | t_1 \verb| as Unit+Unit of inl | x \Rightarrow t_2 | \verb|inr | x \Rightarrow t_3$
+\end{itemize}
+Όπου στην περίπτωση του \verb|case| θα πρέπει οι μεταβλητές να είναι ελεύθερες σε σχέση με τις μεταβλητές των $t_2$ και $t_3$, δηλαδή $x \notin FV(t_2), x \notin FV(t_3)$, το οποίο και πετυχαίνουμε με τα κατάλληλα renames στις μεταβλητές.
+
+\section{Αναφορές}
+
+\subsection*{Άσκηση 2.3 Τελεστής σταθερού σημείου}
+
+Κοιτάζοντας τις ασκήσεις 13.1.2, σελ. 158, και 13.5.8, σελ. 169 του βιβλίου βλέπουμε ότι μπορούμε να λύσουμε την τελευταία ως εξής (ελεγμένη και στην OCaml):
+\begin{lstlisting}
+  factorial = $\nlambda{n:Nat}$
+    let $f =$ ref $(\nlambda{m:Nat} 0)$ in
+      $f$ := $(\nlambda{m:Nat}$ if iszero $m$ then $1$ else times $(!f \; ($pred $m)) \; m)$; $!f \; n$
+\end{lstlisting}
+Παρόλα αυτά αυτός ο όρος δεν μπορεί να γενικευθεί για κάθε τύπο $T_1 \rightarrow T_2$ διότι για τον $T_2$ θα πρέπει να δώσουμε μια τυχαία αρχική τιμή (πχ.
+στο παραπάνω βάλαμε το $0$ για να αρχικοποιήσουμε την $f:Ref \; Nat \rightarrow Nat$).
+Θα μπορούσαμε να ορίσουμε πχ. την FixBool ως εξής:
+\begin{lstlisting}
+  fixBool = $\nlambda{f:(T_1 \rightarrow Bool) \rightarrow (T_1 \rightarrow Bool)} \nlambda{x:T_1}$
+    let $r =$ ref $(\nlambda{y:T_1}$ true $)$ in
+      $r$ := $(\nlambda{y:T_1} f \; !r \; y)$; $!r \; x$
+\end{lstlisting}
+
+\subsubsection*{Συνάρτηση even}
+
+Με το παραπάνω η υλοποίηση της συνάρτησης \verb|even| (στην OCaml) θα είναι ως εξής:
+\begin{verbatim}
+/* Exer02-2.3 OCaml implementation. */
+
+fixNatBool = lambda f:(Nat->Bool)->(Nat->Bool). lambda x:Nat.
+  let r = ref (lambda y:Nat. true) in
+    (lambda u:Unit. !r x) (r := (lambda y:Nat. f (!r) y));
+
+evenr = lambda ie:Nat->Bool. lambda n:Nat.
+  if iszero n then true
+    else if iszero (pred n) then false
+    else ie (pred (pred n));
+
+even = fixNatBool evenr;
+\end{verbatim}
+
+\subsection*{Άσκηση 2.4  Μοναδικότητα τύπων μνήμης}
+
+Παρατηρούμε ότι στην περίπτωση που έχουμε κύκλους τότε υπάρχουν παραπάνω από ένας τρόπος να έχουμε well typed όρους.
+Οπότε θα πάρουμε ένα context $\Gamma$ στο οποίο υπάρχει ο όρος \\ $\Gamma \vdash t = \nlambda{x:Nat} (!l) \; x$ και το store $\mu$ όπου $\mu = (l \rightarrow t)$.
+Τότε στη συνέχεια μπορούμε να πάρουμε τα εξής δύο stores $\Sigma_1, \Sigma_2$ στα οποία:
+\[ \Sigma_1(l) = Nat \rightarrow Nat \]
+\[ \Sigma_2(l) = Nat \rightarrow Bool \]
+και για τα οποία βλέπουμε ότι $\Gamma \; | \; \Sigma_1 \vdash \mu$ και $\Gamma \; | \; \Sigma_2 \vdash \mu$ ταυτόχρονα.
+
 \end{document}

### 2020-04-19 typesys/exer02_2_3.f

@@ -1,0 +1,48 @@
+/* Factorial implementation, Exercise 13.5.8 */
+
+sumr = lambda sum:Nat->Nat->Nat. lambda n:Nat. lambda m:Nat. if iszero m then n else sum (succ n) (pred m);
+sum = fix sumr;
+
+times = lambda n:Nat. lambda m:Nat.
+  let p = ref (lambda mm:Nat. 0) in
+    (lambda x:Unit. !p m) (p := (lambda mm:Nat. if iszero mm then 0 else sum (!p (pred mm)) n));
+
+fact = lambda n:Nat.
+  let f = ref (lambda m:Nat. 0) in
+    (lambda x:Unit. !f n) (f := (lambda m:Nat. if iszero m then 1 else times (!f (pred m)) m));
+/*fact 3;*/
+
+/* Failed attempt to define a generic fix combinator. */
+/*let r = ref (lambda z:T1. f (lambda y:T1->T2. f y z)) in !r x;
+f = lambda f:(T1->T2)->(T1->T2). lambda x:T1.
+  let r = ref (lambda y:T1->T2. f y z) in
+    (lambda u:Unit. !r x) (r := (lambda z:T1. f (!r) z));*/
+
+fixBool = lambda f:(T1->Bool)->(T1->Bool). lambda x:T1.
+  let r = ref (lambda y:T1. true) in
+    (lambda u:Unit. !r x) (r := (lambda y:T1. f (!r) y));
+
+/* The following has the same type as fixBool but does pass down any variable so it's not functioning. */
+fixBoolAlt = lambda f:(T1->Bool)->(T1->Bool).
+  let r = ref (lambda x:T1. f (lambda y:T1. true) x) in
+    (lambda u:Unit. !r) (r := f (!r));
+
+
+/* Exer02-2.3 OCaml implementation. */
+
+fixNatBool = lambda f:(Nat->Bool)->(Nat->Bool). lambda x:Nat.
+  let r = ref (lambda y:Nat. true) in
+    (lambda u:Unit. !r x) (r := (lambda y:Nat. f (!r) y));
+
+evenr = lambda ie:Nat->Bool. lambda n:Nat.
+  if iszero n then true
+    else if iszero (pred n) then false
+    else ie (pred (pred n));
+
+even = fixNatBool evenr;
+
+even 12;
+even 9;
+even 1;
+even 23;
+even 42;

### 2020-04-19 typesys/exer01_1_4.f
TypeSys: Exer01: Included the OCaml implementation file for exercise 1.4

@@ -1,0 +1,21 @@
+/* Exer01-1.4 OCAml implementation.  */
+
+fix = lambda f.(lambda x.f (lambda y.x x y)) (lambda x.f (lambda y.x x y));
+
+/* Recurcive function for subtracting two numerals. */
+subr = lambda sub.lambda m.lambda n.if iszero n then m else sub (pred m) (pred n);
+sub = fix subr;
+
+/* Recurcive function MOD of two numerals. */
+modr = lambda mod.lambda m.lambda n.if iszero (sub m n) then (if iszero (sub n m) then 0 else m) else mod (sub m n) n;
+mod = fix modr;
+
+/* The GCD function! */
+gcdr = lambda gcd.lambda m.lambda n.if iszero n then m else gcd n (mod m n);
+gcd = fix gcdr;
+
+/* Print the examples. */
+gcd 24 42;
+gcd 42 17;
+gcd 714 630;
+gcd 85 204;

### 2020-04-26 stuctbio/assignment2.tex
StuctBio: Assignment2: First attempt at the excercise along with the python script used for it

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}

% More packages and macros
\usepackage[inference]{semantic}
\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{amsmath}
\usepackage[margin=2cm]{geometry}

\newcommand\nlambda[1]{\ensuremath{\lambda #1.\,}}
\newcommand\nred{\ensuremath{\longrightarrow}}

% Main document
\begin{document}
\title{Assignment 2}
\author{Thomas Pappas}
\maketitle

\section*{a}

Using the USCF Chimera software and after superimposing the the 6FAT and 1UWC proteins we get the following figures

\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{superimposed}
\caption{The superimposed 3D structures}
\end{figure}
\begin{figure}[h]
\centering
\includegraphics[width=0.4\textwidth]{superimposed_CA}
\caption{The superimposed 3D structures giving emphasis on the calcium binding site}
\end{figure}

% Reply log: RMSD between 20 pruned atom pairs is 1.037 angstroms; (across all 234 pairs: 22.983)
The c-RMSD as calculated by Chimera after superposition is $1.037$ \AA

\section*{b}

How to calculate the c-RMSD between two structures of different length? Homology? Alignment?

\section*{c}

We take the coodinates for each residue's backbone atoms from the \verb|.pdb| file and we calculate the Caley-Menger (border) matrix $B$. We get:

\begin{small}
  \[B =\]
  \[\begin{pmatrix}
    0 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1 & 1\\
    1 & 0 & 1.077665 & 3.000898 & 5.4746245 & 10.628379 & 15.5881445 & 16.357075 & 23.977149 & 31.7466575\\
    1 & 1.077665 & 0 & 1.173865 & 2.9497055 & 7.310758 & 10.1919535 & 10.845074 & 16.593745  & 24.1580125\\
    1 & 3.000898 & 1.173865 & 0 & 0.8908105 & 3.025239 & 5.0428305 & 5.417763 & 10.345519  & 15.9237015\\
    1 & 5.4746245 & 2.9497055 & 0.8908105 & 0 & 1.0730015 & 3.03894 & 4.8417535 & 9.9602605 & 15.778275\\
    1 & 10.628379 & 7.310758 & 3.025239 & 1.0730015 & 0 & 1.1697375 & 2.939012 & 7.337819 & 11.4252685\\
    1 & 15.5881445 & 10.1919535 & 5.0428305 & 3.03894 & 1.1697375 & 0 & 0.8883295 & 3.0552225 & 6.377039\\
    1 & 16.357075 & 10.845074 & 5.417763 & 4.8417535 & 2.939012 & 0.8883295 & 0 & 1.084853 & 3.1626245\\
    1 & 23.977149 & 16.593745 & 10.345519 & 9.9602605 & 7.337819 & 3.0552225 & 1.084853 & 0 & 1.1833645\\
    1 & 31.7466575 & 24.1580125 & 15.9237015 & 15.778275 & 11.4252685 & 6.377039 & 3.1626245 & 1.1833645 & 0
  \end{pmatrix}\]
\end{small}

\section*{d}

By running the Python code \verb|numpy.linalg.matrix_rank(B)| we verify that the $rank(B) = 5$

Now in order to calculate the Gram matrix $G$, use the formula
\[
  G[i,j] := \frac{d_{i0}^2 - d_{ij}^2 + d_{j0}^2}{2}
\]
and while we can use the $B$ matrix for $\frac{d_{ij}^2}{2}$, in order to calculate $d_{i0}, d_{j0}$ we'll need to use the original coordinates. We therefore get
\begin{footnotesize}
  \[G =\]
  \[
    \begin{pmatrix}
      5199.442025 & 5188.332704 & 5287.185963 & 5326.089175 & 5419.655414 & 5410.547521 & 5409.324072 & 5401.249837 & 5487.240252\\
      5188.332704 & 5179.378713 & 5278.98134 & 5318.582438 & 5412.941379 & 5405.912056 & 5404.804417 & 5398.601585 & 5484.797241\\
      5287.185963 & 5278.98134 & 5380.931697 & 5421.417825 & 5518.00339 & 5511.837671 & 5511.00822 & 5505.626303 & 5593.808044\\
      5326.089175 & 5318.582438 & 5421.417825 & 5463.685574 & 5561.332566 & 5555.2185 & 5552.961168 & 5547.3885 & 5635.330409\\
      5419.655414 & 5412.941379 & 5518.00339 & 5561.332566 & 5661.125561 & 5655.807696 & 5653.583903 & 5648.730935 & 5738.403409\\
      5410.547521 & 5405.912056 & 5511.837671 & 5555.2185 & 5655.807696 & 5652.829306 & 5651.486458 & 5648.865404 & 5739.303511\\
      5409.324072 & 5404.804417 & 5511.00822 & 5552.961168 & 5653.583903 & 5651.486458 & 5651.920269 & 5650.381255 & 5742.063407\\
      5401.249837 & 5398.601585 & 5505.626303 & 5547.3885 & 5648.730935 & 5648.865404 & 5650.381255 & 5651.011947 & 5743.588506\\
      5487.240252 & 5484.797241 & 5593.808044 & 5635.330409 & 5738.403409 & 5739.303511 & 5742.063407 & 5743.588506 & 5838.531794
    \end{pmatrix}
  \]
\end{footnotesize}

and by using SVD we get the new coordinates
\begin{center}
  \[
    \begin{pmatrix}
      -0.720239668 & -3.29505773 & -1.06434145\\
      -0.719397583 & -1.95848694 & -0.462828815\\
      -0.733414994 & -1.34469699 & -0.384638014\\
      -0.739000952 & -1.33290190 & 0.827571807\\
      -0.752286576 & -0.772197814 & 1.08551735\\
      -0.751728771 & 0.755384109 & 1.13896831\\
      -0.751667006 & 1.37317774 & -0.0421124995\\
      -0.751193862 & 2.83776829 & -0.191918550\\
      -0.763282291 & 3.40972451 & -0.952375000
    \end{pmatrix}
  \]
\end{center}

thus achieving a c-RMSD with the initial coordinates (over all atoms) of $3.379948495065777 \times 10^{-13}$ \AA, which practically means the two structures are the same.

\vspace{5mm}

\textit{Note: Intuitively it seems it would make more sense to calculate $G$ using only the values from $B$. However when taking $d_{i0} = 1$ the c-RMSD becomes $\sim 5$.}

\section*{e}

We implement the perturbation by increasing all values in $B$ by a percentage.
Then we recalculate $G$, run SVD to get the $U$ and $\Sigma$ values, take the $S$ to be the $(3 \times 3)$ diagonal array with the three greatest values from $\Sigma$, and check the c-RMSD between the original cooredinates and the points from $\sqrt{S}U^T$.

The algorithm tried multiple points between $100\%$ and $200\%$ and then run again in the space where the c-RMSD would go over $1$. The conclusion was the the max percentage of perturbation for c-RMSD to be $< 1$ is $88.61\%$.

\section*{f}

Here for calculating the c-RMSD we will take only the distances that are less than a number $T$.
For the rest of the points we will assume that the distance is $0$ in order for it not to affect the final result.
We will also keep $R = 1$ \AA.

\end{document}

### 2020-04-26 stuctbio/assignment2.py

@@ -1,0 +1,88 @@
+import numpy as np
+
+
+# Helper functions
+
+# Calculate the c-RMSD between two coordinate sets.
+def c_rmsd(x, y):
+    # calculates c-RMSD for x,y sets of 3D coordinates.
+    n = np.shape(x)[0]
+    x_c = np.mean(x, axis=0)
+    y_c = np.mean(y, axis=0)
+    x = x - x_c
+    y = y - y_c
+    u, sig, vt = np.linalg.svd(x.transpose() @ y)
+    q = u @ vt
+    if np.linalg.det(q) < 0:
+        q = np.array([u[:, 0], u[:, 1], -u[:, 2]]) @ vt
+    return np.linalg.norm((x @ q) - y) / np.sqrt(n)
+
+
+# Calculate the Gram matrix G from a set of coordinates and a distant matrix.
+def gram(x, dist):
+    g = np.full((9, 9), 0.0)
+    for i in range(9):
+        for j in range(9):
+            g[i, j] = (np.linalg.norm(x[i]) ** 2 + np.linalg.norm(x[j]) ** 2) / 2 - dist[i + 1, j + 1]
+    # Similar way of calculating G using only the coordinates.
+    # for i in range(9):
+    #     for j in range(9):
+    #         g[i, j] = x[i].transpose() @ x[j]
+    return g
+
+
+def get_three_max(array):
+    a = np.sort(array)
+    return np.array([a[-1], a[-2], a[-3]])
+
+
+# Exercise C
+
+# Take the coordinates from the 3 backbone atoms (N - CA - C)
+# of the three residues of the calcium binding site, i.e. Val276-Ala277-Asp278.
+coord = np.array([
+    [19.456, 43.867, 53.820],  # ATOM   1818  N   VAL A 276
+    [19.120, 44.932, 52.867],  # ATOM   1819  CA  VAL A 276
+    [19.180, 46.289, 53.576],  # ATOM   1820  C   VAL A 276
+    [20.251, 47.037, 53.302],  # ATOM   1825  N   ALA A 277
+    [20.462, 48.366, 53.881],  # ATOM   1826  CA  ALA A 277
+    [19.599, 49.411, 53.172],  # ATOM   1827  C   ALA A 277
+    [18.326, 49.468, 53.563],  # ATOM   1830  N   ASP A 278
+    [17.345, 50.411, 52.999],  # ATOM   1831  CA  ASP A 278
[…]

### 2020-04-26 stuctbio/assignment2.tex
StuctBio: Assignment2: Included exercise question f and related python code, plus text improvements

@@
 % Reply log: RMSD between 20 pruned atom pairs is 1.037 angstroms; (across all 234 pairs: 22.983)
-The c-RMSD as calculated by Chimera after superposition is $1.037$ \AA
+The c-RMSD as calculated by Chimera after superposition is
+\begin{itemize}
+  \item $1.037$ \AA \; between 20 pruned atom pairs
+  \item $22.983$ \AA \; across all 234 pairs
+\end{itemize}
 
-\section*{b}
-
-How to calculate the c-RMSD between two structures of different length? Homology? Alignment?
+%\section*{b}
+%How to calculate the c-RMSD between two structures of different length? Homology? Alignment?
 
@@
 
-We take the coodinates for each residue's backbone atoms from the \verb|.pdb| file and we calculate the Caley-Menger (border) matrix $B$. We get:
+We will take the coodinates for each residue's backbone atoms from the \verb|6FAT.pdb| file and we'll calculate the Caley-Menger (border) matrix $B$. We get:
 
@@
 
-By running the Python code \verb|numpy.linalg.matrix_rank(B)| we verify that the $rank(B) = 5$
-
-Now in order to calculate the Gram matrix $G$, use the formula
+By running the Python code for $B$ \verb|numpy.linalg.matrix_rank(B)| we verify that $rank(B) = 5$.\\
+Now in order to calculate the Gram matrix $G$, we will use the formula
 \[
@@
 \]
-and while we can use the $B$ matrix for $\frac{d_{ij}^2}{2}$, in order to calculate $d_{i0}, d_{j0}$ we'll need to use the original coordinates. We therefore get
+and while we can use the $B$ matrix to get $\frac{d_{ij}^2}{2}$, in order to calculate $d_{i0}$ and $d_{j0}$ we'll need to use the original coordinates. We therefore get:
 \begin{footnotesize}
@@
 
-and by using SVD we get the new coordinates
+and by using SVD we get the new coordinates:
 \begin{center}
@@
 
-\textit{Note: Intuitively it seems it would make more sense to calculate $G$ using only the values from $B$. However when taking $d_{i0} = 1$ the c-RMSD becomes $\sim 5$.}
+%\textit{Note: Intuitively it seems it would make more sense to calculate $G$ using only the values from $B$. However when taking $d_{i0} = 1$ the c-RMSD becomes $\sim 5$.}
 
@@
 We implement the perturbation by increasing all values in $B$ by a percentage.
-Then we recalculate $G$, run SVD to get the $U$ and $\Sigma$ values, take the $S$ to be the $(3 \times 3)$ diagonal array with the three greatest values from $\Sigma$, and check the c-RMSD between the original cooredinates and the points from $\sqrt{S}U^T$.
+Then we recalculate $G$, run SVD to get the $U$ and $\Sigma$ values, take $S$ to be the $(3 \times 3)$ diagonal array with the three greatest values from $\Sigma$, and then check the c-RMSD between the original cooredinates and the points from $\sqrt{S}U^T$.
 
-The algorithm tried multiple points between $100\%$ and $200\%$ and then run again in the space where the c-RMSD would go over $1$.
-The conclusion was the the max percentage of perturbation for c-RMSD to be $< 1$ is $88.61\%$.
+The algorithm tried 100 points between $1\%$ and $100\%$ (with a step of $1\%$) which was the incease applied to all values of $B$, and then run again for 10 more points in the space where the c-RMSD would go over $1$ to increase accuracy.
+
+The conclusion was the max percentage of perturbation for c-RMSD to be less than $R = 1$ is around $88.61\%$.
 
@@
 Here for calculating the c-RMSD we will take only the distances that are less than a number $T$.
-For the rest of the points we will assume that the distance is $0$ in order for it not to affect the final result.
+For the rest of the points we will assume that the distance is $0$.
 We will also keep $R = 1$ \AA.
 
+\begin{center}
+  \begin{tabular}{ ||c|c|| }
+    \hline
+    $T$ & c-RMSD\\
+    \hline \hline
+    30 & 4.848773458134514\\
+    20 & 1.2941487875701954\\
+    15 & 5.004258253300996\\
+    10 & 5.243758773056963\\
+    5 & 1.360263291246221\\
+    4 & 1.3621607241108677\\
+    3 & 1.3643224342718143\\
+    2 & 1.15262288363306\\
+    1 & 0.2292140768425968\\
+    \hline
+  \end{tabular}
+\end{center}
+
+And therefore for $T = 1$ we get the c-RMSD to be less than $R = 1$ \AA.
+
 \end{document}

### 2020-04-26 stuctbio/assignment2.py

@@ -31,6 +31,18 @@ def gram(x, dist):
     return g
 
 
+# Calculate the Gram matrix G from a set of coordinates and a distant matrix.
+def gram_cutoff(x, dist, t):
+    g = np.full((9, 9), 0.0)
+    d = 0
+    for i in range(9):
+        for j in range(9):
+            if dist[i + 1, j + 1] > t:
+                d = dist[i + 1, j + 1]
+            g[i, j] = (np.linalg.norm(x[i]) ** 2 + np.linalg.norm(x[j]) ** 2) / 2 - d
+    return g
+
+
 def get_three_max(array):
     a = np.sort(array)
     return np.array([a[-1], a[-2], a[-3]])
@@ -86,3 +98,11 @@ for pert in np.linspace(0.0, 1.0, 101):
     new_coord = np.sqrt(np.diag(s)) @ vh[:3, :]
     print('For perturbation ', pert, ' we get c-RMSD: ', c_rmsd(coord, new_coord.transpose()))
 # c-RMSD < 1 is achieved for max perturbation ~88,61%.
+
+# Exercise F
+for T in [30, 20, 15, 10, 5, 4, 3, 2, 1]:
+    G = gram_cutoff(coord, B, T)
+    v, sigma, vh = np.linalg.svd(G)
+    s = get_three_max(sigma)
+    new_coord = np.sqrt(np.diag(s)) @ vh[:3, :]
+    print('For cutoff ', T, ' we get c-RMSD: ', c_rmsd(coord, new_coord.transpose()))

### 2020-05-18 stuctbio/Project/progress_report_1.tex
StructBio: Project: Incuded Project Progress report 1 & 2

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass{beamer}
\usetheme{Madrid}
\centering

% Greek fonts
\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}

\usepackage{graphicx}
\graphicspath{ {./pr1_figures/} }

% Main document
\begin{document}
\title{DeepSite}
\subtitle{Algorithms in Structural Bioinformatics - Project progress report 1}
\author{Thomas Pappas}
%\date{4 March 2020}
\maketitle

\section{What is the project about?}

\begin{frame}{What is the project about?}
  \begin{block}{DeepSite}
    Protein-binding site predictor using 3D-convolutional neural networks
    \begin{itemize}
      \item Deep Convolutional Neural Network (DCNN)
      \item Trained by 7622 proteins from scPDB
      \item Superior performance to two other competitive algorithmic strategies
      \item Available online at\\ \url{https://www.playmolecule.com/deepsite/}
  \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Example of a 6FAT protein}
  \begin{figure}[h]
    \includegraphics[width=1\textwidth]{deepsite_6fat_result}
    \caption{The 6FAT protein submitted in the \href{https://www.playmolecule.com/deepsite/}{DeepSite web app}}
  \end{figure}
\end{frame}

\subsection{What has happened?}

\begin{frame}{What has happened?}
  \begin{block}{Research}
    \begin{itemize}
      \item Neural Networks
      \item Convolutional Neural Networks
    \end{itemize}
  \end{block}
  \begin{block}{Analysis}
    DCNN for protein binding site prediction
    \begin{itemize}
      \item Treat the 3D protein molecular structure like a 3D image
      \begin{itemize}
        \item $1$ voxel = $1 \times 1 \times 1 $ \AA$^3$
      \end{itemize}
      \item Apply atom properties (hydrophobic, aromatic, etc.) as filters
      \item 10-fold cross-validation
      \item Network design
      \item Evaluation using DCC and DVO (with Jaccard Index)
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{The protein property filters}
  \begin{figure}[h]
    \includegraphics[width=0.4\textwidth]{deepsite_protein_property_filters}
    \caption{The 8 protein properties that contitute the filters of the DCNN.\\\hspace{1mm}
      From the DeepSite 2017 paper, 10.1093/bioinformatics/btx350}
  \end{figure}
\end{frame}

\subsection{What will happen?}

\begin{frame}{What will happen?}
  \begin{block}{Problems}
    The paper does NOT provide the full algorithm, therefore no easy tweaking can take place
  \end{block}
  \begin{block}{More Research}
    \begin{itemize}
      \item DCNN design choices
      \item NN - Binding site problem relation
    \end{itemize}
  \end{block}
  \begin{block}{Investigation suggestions}
    \begin{itemize}
      \item Protein sample submission to online application
      \begin{itemize}
        \item Visualisation
        \item Modify propability threshold
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\subsection{Contact details}

\begin{frame}{Contact details}
  \begin{center}
    Thomas Pappas\\
    \href{mailto:thpappas@di.uoa.gr}{thpappas@di.uoa.gr}
  \end{center}
\end{frame}

\end{document}

### 2020-05-18 stuctbio/Project/progress_report_2.tex
StructBio: Project: Incuded Project Progress report 1 & 2

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass{beamer}
\mode<presentation>
{
  \usetheme[progressbar=foot,numbering=fraction,background=light]{metropolis} 
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
  %\setbeamertemplate{frame footer}{My custom footer}
}
\centering

\usepackage{graphicx}
\graphicspath{ {./pr2_figures/} }

% Main document
\begin{document}
\title{DeepSite}
\subtitle{Algorithms in Structural Bioinformatics \\ Project progress report 2}
\author{Thomas Pappas}
%\date{4 March 2020}
\maketitle

\begin{frame}{Outline}
  \tableofcontents
\end{frame}

\section{What is the project about?}

\begin{frame}{What is DeepSite?}
  \begin{block}{DeepSite}
    Protein-binding site \emph{predictor} using 3D-convolutional neural networks
    \begin{itemize}
      \item Using DCNN due to an existing database of 7622 proteins from scPDB to train the NN
      \item Superior performance to two other competitive algorithmic strategies
      \item Available online at \url{https://www.playmolecule.com/deepsite/}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{DeepSite Algorithm summary}
  \begin{block}{Algorithm summary}
    \begin{itemize}
      \item Takes as input a protein ID or a PDB file
      \item Translates the molecular structures to 8 grids representing molecular properties
      \begin{itemize}
        \item The 8 grids are basically channels that NNs take as input
      \end{itemize}
      \item Takes $16 \times 16 \times 16$ \AA$^3$ subgrids from the 8 channels as input for the Deep Convolutional Neural Network (DCNN)
      \item Returns a list of predicted points to be binding-sites, along with their success score
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Example of a 6FAT protein}
  \begin{figure}[h]
    \includegraphics[width=1\textwidth]{deepsite_6fat_result}
    \caption{The 6FAT protein submitted in the \href{https://www.playmolecule.com/deepsite/}{DeepSite web app}}
  \end{figure}
\end{frame}

\section{Translating PDB to NN channels}

\begin{frame}{Translating PDB to NN channels}
  \begin{block}{Parsing the PDB data}
    \begin{itemize}
      \item Parse the atom coordinates from the PDB data
      \begin{itemize}
        \item Use of the HTMDs (Doerr et al., 2016) Python package
      \end{itemize}
      \item Use the AutoDock 4 tables (Tables \ref{table:1} \& \ref{table:2}) and create 8 \emph{filtered set of atoms}, one for each protein property
      \item Consider the space grid containing the protein
      \begin{itemize}
        \item Grid is split to $1 \times 1 \times 1 $ \AA$^3$ voxels
        \item $+8$\AA \;for the cases where the binding pockets are on the edge
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{AutoDock 4 tables}
  \begin{columns}
    \begin{column}{.4\textwidth}
      \begin{tiny}
      \begin{table}
      \caption{Atom types}
      \label{table:1}
      \begin{tabular}{ l l }
        \hline
        Element & Description \\
        \hline
        C & Non H-bonding aliphatic carbon \\
        A & Non H-bonding aromatic carbon \\
        NA & Acceptor 1 H-bond nitrogen \\
        NS & Acceptor S Spherical nitrogen \\
        OA & Acceptor 2 H-bonds oxygen \\
        OS & Acceptor S Spherical oxygen \\
        SA & Acceptor 2 H-bonds sulfur \\
        HD & Donor 1 H-bond hydrogen \\
        HS & Donor S Spherical hydrogen \\
        MG & Non H-bonding magnesium \\
        ZN & Non H-bonding zinc \\
        MN & Non H-bonding manganese \\
        CA & Non H-bonding calcium \\
        FE & Non H-bonding iron \\
        \hline
      \end{tabular}
      \end{table}
      \end{tiny}
    \end{column}
    \begin{column}{.6\textwidth}
      \begin{tiny}
      \begin{table}
      \caption{Property-atom type correspondence}
      \label{table:2}
      \begin{tabular}{ l l }
        \hline
        Property & Rule \\
        \hline
        Hydrophobic & atom type C or A \\
        Aromatic & atom type A \\
        Hydrogen bond acceptor & atom type NA or NS or OA or OS or SA \\
        Hydrogen bond donor & atom type HD or HS with O or N partner \\
        Positive ionizable & atom with positive charge \\
        Negative ionizable & atom with negative charge \\
        Metal & atom type MG or ZN or MN or CA or FE \\
        Excluded volume & all atom types \\
      \end{tabular}
      \end{table}
      \end{tiny}
    \end{column}
  \end{columns}
  Table 1, Table 2, 10.1093/bioinformatics/btx350
\end{frame}

\begin{frame}{Translating PDB to NN channels}
  \begin{block}{Atom occupancy}
    We calculate the probability of an atom to exist near the center of a voxel by using the pair correlation function
    \[
      g(r) = exp(-\beta V(r))
    \]
    where $V(r) = \epsilon (r_{vdw}/r)^{12}$ and by taking $\epsilon = \beta^{-1}$ we get the \emph{single atom occupancy estimate} to be
    \[
      n(r) = 1 - exp(-(r_{vdw}/r)^{12})
    \]
  \end{block}
  \begin{block}{Building the NN channels}
    Create a channel (3D matrix) for each of the 8 atom sets, and for each voxel assign the probability of the voxel having an atom of that property (Figure 2)
  \end{block}
\end{frame}

\begin{frame}{Translating PDB to NN channels}
  \begin{figure}[h]
    \includegraphics[width=1\textwidth]{deepsite_protein_property_channels}
    \caption{Visual representations of descriptor channels (3/8) for PDB ID 4NIE, Figure S2, 10.1093/bioinformatics/btx350}
  \end{figure}
\end{frame}

\section{NN design}

\begin{frame}{NN design}
  \begin{figure}[h]
    \includegraphics[width=1\textwidth]{deepsite_dcnn_architecture}
    \caption{DeepSite’s internal DCNN architecture, Fig. 2, 10.1093/bioinformatics/btx350}
  \end{figure}
\end{frame}

\begin{frame}{NN design}
  \begin{block}{Training}
    \begin{itemize}
      \item Input subgrids of $16 \times 16 \times 16$ \AA$^3$
      \item Step of 4 voxels
    \end{itemize}
  \end{block}
  \begin{block}{Success criteria for a subgrid}
    Geometric center is closer than 4 Å to the pocket geometric center
  \end{block}
\end{frame}

\section{Evaluating the NN model}

\begin{frame}{10-fold cross-validation}
  Dataset of 7622 scPDB structures
  \begin{block}{Steps}
    \begin{itemize}
      \item Split the training dataset to 10 (equal size) sets
      \item Consider one as a testing set and the rest as training ones and evaluate its success
      \item Cycle through each set and repeat the evaluation
      \item Final result is the average of all above evaluations
    \end{itemize}
  \end{block}
  \begin{block}{Why $k$-fold cross validation?}
    \begin{itemize}
      \item Common practice for validating NN models
      \item Limits the possibility of over-fitting
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Evaluation metrics}
  \begin{block}{Distance to the center of the binding site (DCC)}
    A prediction is successful is closer than a given threshold to the real-binding site
    \begin{itemize}
      \item Values uses range from 4 to 20 \AA
      \item Ignores the shape of the predicted pocket
    \end{itemize}
  \end{block}
  \begin{block}{Discretized volumetric overlap (DVO)}
    Discretize protein space to $1 \times 1 \times 1$ \AA$^3$ voxels and calculate the Jaccard index
    \[
      J = \frac{\#|V_r \cap V_p|}{\#|V_r \cup V_p|}
    \]
    $V_r$: set of voxels in real binding pocket\\
    $V_p$: set of voxels in predicted binding pocket
    \begin{itemize}
      \item Takes into account the shape of the predicted pocket
    \end{itemize}
  \end{block}
\end{frame}

\section{Next Steps}

\begin{frame}{Next Steps}
  \begin{block}{Neural Network design analysis}
  \end{block}
  \begin{block}{Compare results with fPocket and Concavity algorithms}
  \end{block}
\end{frame}

\begin{frame}{Contact details}
  \begin{center}
    Thomas Pappas\\
    \href{mailto:thpappas@di.uoa.gr}{thpappas@di.uoa.gr}
  \end{center}
\end{frame}

\end{document}

### 2020-05-18 stuctbio/Project/deepsite.py
StructBio: Project: Included Python scripts for a NNet and for the DeepSite algorithm

@@ -1,0 +1,37 @@
+from htmd.ui import *
+from keras.models import Sequential
+from keras.layers import Convolution3D, MaxPooling3D, Dropout, Flatten, Dense, Activation
+from keras.layers.advanced_activations import ELU
+from keras.optimizers import Adam
+
+# Parse the PDB data
+mol = Molecule('4NIE')
+print(mol)
+
+# The DeepSite DCNN
+boxsize = 16
+model = Sequential()
+model.add(Convolution3D(32, (8, 8, 8), padding='same',
+                        input_shape=(boxsize, boxsize, boxsize, 8)))
+model.add(ELU())
+model.add(Convolution3D(48, (4, 4, 4)))
+model.add(ELU())
+model.add(MaxPooling3D(pool_size=(2, 2, 2)))
+model.add(Dropout(0.25))
+
+model.add(Convolution3D(64, (4, 4, 4), padding='same'))
+model.add(ELU())
+model.add(Convolution3D(96, (4, 4, 4)))
+model.add(ELU())
+model.add(MaxPooling3D(pool_size=(2, 2, 2)))
+model.add(Dropout(0.25))
+
+model.add(Flatten())
+model.add(Dense(256))
+model.add(ELU())
+model.add(Dropout(0.5))
+model.add(Dense(1))
+model.add(Activation('sigmoid'))
+
+opt = Adam()
+model.compile(loss='binary_crossentropy', optimizer=opt, metrics=['accuracy'])

### 2020-05-18 stuctbio/Project/nnet.py

@@ -1,0 +1,83 @@
+import numpy as np
+
+
+def sigmoid(x):
+    # Our activation function: f(x) = 1 / (1 + e^(-x))
+    return 1 / (1 + np.exp(-x))
+
+
+def deriv_sigmoid(x):
+    # Derivative of sigmoid: f'(x) = f(x) * (1 - f(x))
+    fx = sigmoid(x)
+    return fx * (1 - fx)
+
+
+def mse_loss(y_true, y_pred):
+    # y_true and y_pred are numpy arrays of the same length.
+    return ((y_true - y_pred) ** 2).mean()
+
+
+class Neuron:
+    def __init__(self, weights, bias):
+        self.weights = weights
+        self.bias = bias
+
+    def get_total(self, inputs):
+        # Weight inputs, add bias.
+        return (self.weights @ inputs) + self.bias
+
+    def feedforward(self, total):
+        # Use the activation function
+        return sigmoid(total)
+
+    def train(self, y_pred):
+        self.weights = np.array([])
+
+
+class OurNeuralNetwork:
+    """
+    A neural network with:
+    - 2 inputs
+    - a hidden layer with 2 neurons (h1, h2)
+    - an output layer with 1 neuron (o1)
+    Each neuron has the same weights and bias:
+    - w = [0, 1]
+    - b = 0
+    """
+    def __init__(self):
+        self.h1 = Neuron(np.array([np.random.normal(), np.random.normal()]), np.random.normal())
+        self.h2 = Neuron(np.array([np.random.normal(), np.random.normal()]), np.random.normal())
+        self.o1 = Neuron(np.array([np.random.normal(), np.random.normal()]), np.random.normal())
+        learn_rate = 0.1
+
+    def feedforward(self, x):
+        sum_h1 = self.h1.get_total(x)
+        out_h1 = self.h1.feedforward(sum_h1)
+        sum_h2 = self.h2.get_total(x)
+        out_h2 = self.h2.feedforward(sum_h2)
+        sum_o1 = self.o1.get_total(np.array([out_h1, out_h2]))
+        return self.o1.feedforward(sum_o1)
+
+    def train(self, data, all_y_trues):
+        """
+        - data is a (n x 2) numpy array, n = # of samples in the dataset.
+        - all_y_trues is a numpy array with n elements.
+          Elements in all_y_trues correspond to those in data.
+        """
+        epochs = 1000  # number of times to loop through the entire dataset
+
+        for epoch in range(epochs):
[…]

### 2020-07-13 stuctbio/Project/final_presentation.tex
StrucBio: Project: Included the final presentation of the project (presented on 25/06/2020)

--- 2020-05-18 stuctbio/Project/progress_report_2.tex
@@
 \usepackage{graphicx}
-\graphicspath{ {./pr2_figures/} }
+\graphicspath{ {./fp_figures/} }
+\usepackage{hyperref,xcolor}
+\newcommand{\link}[2]{\href{#1}{\textcolor{blue}{\underline{#2}}}}
 
@@
 \begin{document}
-\title{DeepSite}
-\subtitle{Algorithms in Structural Bioinformatics \\ Project progress report 2}
+\title{DeepSite: NNets for binding site prediction}
+\subtitle{Algorithms in Structural Bioinformatics}
 \author{Thomas Pappas}
@@
 
-\begin{frame}{Outline}
-  \tableofcontents
+\begin{frame}{Agenda}
+  \tableofcontents[hideallsubsections]
 \end{frame}
@@
     \begin{itemize}
-      \item Using DCNN due to an existing database of 7622 proteins from scPDB to train the NN
+      \item Using DCNN due to an existing database of 7622 proteins from scPDB to train the NNet
       \item Superior performance to two other competitive algorithmic strategies
-      \item Available online at \url{https://www.playmolecule.com/deepsite/}
+      \item Available online at \link{https://www.playmolecule.com/deepsite/}{https://www.playmolecule.com/deepsite/}
     \end{itemize}
@@
 \end{frame}
+
+\begin{frame}{Aim and objectives}
+  \begin{block}{Review}
+    How does DeepSite takes a PDB structure and implements a DCNN on it to predict binding sites?
+  \end{block}
+  \begin{block}{Confirm}
+    Test the algorithm with more recent available data.
+  \end{block}
+  \begin{block}{Compare}
+    See the algorithm's performance compared to other binding site prediction ones, i.e. fpocket
+  \end{block}
+\end{frame}
+
+\section{The DeepSite algorithm}
 
@@
       \item Takes $16 \times 16 \times 16$ \AA$^3$ subgrids from the 8 channels as input for the Deep Convolutional Neural Network (DCNN)
-      \item Returns a list of predicted points to be binding-sites, along with their success score
+      \item Returns a list of predicted points to be binding sites, along with their success score
     \end{itemize}
@@
     \includegraphics[width=1\textwidth]{deepsite_6fat_result}
-    \caption{The 6FAT protein submitted in the \href{https://www.playmolecule.com/deepsite/}{DeepSite web app}}
+    \caption{The 6FAT protein submitted in the \link{https://www.playmolecule.com/deepsite/}{DeepSite web app}}
   \end{figure}
@@
 
-\section{Translating PDB to NN channels}
+\subsection{Translating PDB to NNet channels}
 
@@
 
-\section{NN design}
+\subsection{NNet design}
 
-\begin{frame}{NN design}
+\begin{frame}{NNet design}
   \begin{figure}[h]
@@
 
-\begin{frame}{NN design}
+\begin{frame}{NNet training}
   \begin{block}{Training}
@@
 
-\section{Evaluating the NN model}
+\begin{frame}{NNet properties}
+  \begin{block}{Layers}
+    \begin{itemize}
+      \item 4 Convolutional Layers
+      \item Max Pooling and Dropout layers after each 2
+      \item Sigmoid activation function at the end to get a probability value
+    \end{itemize}
+  \end{block}
+  \begin{block}{But why?}
+    \begin{itemize}
+      \item Common practices in the ML community
+      \item Simplified model due to scarcity of data
+    \end{itemize}
+  \end{block}
+  \begin{block}{Issues?}
+    \begin{itemize}
+      \item Class imbalance problem (many 0 cases)
+      \begin{itemize}
+        \item Undersampling of dataset
+      \end{itemize}
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\begin{frame}{NNet end result}
+  The algorithm will run for all subgrids and will output a full probability map for all voxels.
+  So for a protein
+  \begin{itemize}
+    \item returns a volumetric map of predicted binding sites
+    \item uses the Mean-Shift clustering algorithm to distinguish different binding sites in that protein
+  \end{itemize}
+\end{frame}
+
+\subsection{Evaluating the NNet model}
 
@@
     \begin{itemize}
-      \item Common practice for validating NN models
+      \item Common practice for validating NNet models
       \item Limits the possibility of over-fitting
@@
   \begin{block}{Distance to the center of the binding site (DCC)}
-    A prediction is successful is closer than a given threshold to the real-binding site
+    A prediction is successful is closer than a given threshold to the real binding site
     \begin{itemize}
@@
 
-\section{Next Steps}
+\section{Confirming for old and new data}
 
-\begin{frame}{Next Steps}
-  \begin{block}{Neural Network design analysis}
+\begin{frame}{Method}
+  \begin{block}{sc-PDB}
+    When DeepSite was published, sc-PDB contained 9283 entries;\\
+    as of today it has 16034
   \end{block}
-  \begin{block}{Compare results with fPocket and Concavity algorithms}
+  \begin{block}{Steps for evaluating results (for a protein)}
+    \begin{itemize}
+      \item Download the sc-PDB entries
+      \begin{itemize}
+        \item (Real) Binding site atom info contained in "site.mol2" file
+      \end{itemize}
+      \item Run the DeepSite algorithm from the \link{https://www.playmolecule.com/deepsite/}{online web app} using the PDB ID and the chain from the sc-PDB info
+      \item Calculate the geometric center of the real binding site and its distance from the DeepSite output
+      \begin{itemize}
+        \item In case of multiple ouputs, keep the one with min distance
+        \item Distance should be $<20$\AA
+      \end{itemize}
+    \end{itemize}
+    Test the method with proteins from the training set, and then evaluate with the newer additions
+  \end{block}
+\end{frame}
+
+\begin{frame}{Testing for proteins from the training set}
+  \begin{tiny}
+  \begin{table}
+  \caption{Success evaluation for proteins in the training set}
+  \label{table:3}
+  \begin{tabular}{ c | c | c | c | c }
+    PDB ID (chain) & scPDB ID & DeepSite site prediction & DeepSite score & distance to real (\AA) \\
+    \hline
+    2GQ3 (A) & 2gq3\_1 & $(39.08, 40.04, 83.57)$ & $0.999$ & $18.86$ \\
+    1HT2 (H) & 1ht2\_4 & $(100.75, 84.69, 105.11)$ & $0.999$ & $2.98$ \\
+    3AHN (A) & 3ahn\_1 & $(18.3, -0.36, 4.47)$ & $0.999$ & $4.02$ \\
+    1RBQ (B) & 1rbq\_2 & $(-42.67, 44.16, 11.63)$ & $0.997$ & $4.02$ \\
+    %1NLY (A) & 1nly\_1
+    %1OO6 () & 1oo6_1
+    1RJ9 (A) & 1rj9\_1 & $(30.88, 8.67, 27.27)$ & $0.995$ & $2.83$ \\
+  \end{tabular}
+  \end{table}
+  \end{tiny}
+\end{frame}
+
+\begin{frame}{Testing for newer additions to the sc-PDB}
+  \begin{tiny}
+  \begin{table}
+  \caption{Success evaluation for newer proteins}
+  \label{table:4}
+  \begin{tabular}{ c | c | c | c | c }
+    PDB ID (chain) & scPDB ID & DeepSite site prediction & DeepSite score & distance to real (\AA) \\
+    \hline
+    10MH (A) & 10mh\_1 & $(-23.23, 45.71, 89.51)$ & $0.99$ & $17.91$ \\
+    2QJP (G) & 2qjp\_6 & $(73.90, 28.70, 35.20)$ & $0.99$ & $3.87$ \\
+    2QJP (J) & 2qjp\_7 & $(75.51, -12.29, 33.10)$ & $0.99$ & $5.27$ \\
+    4YLH (K) & 4ylh\_11 & $(64.01, 100.21, -24.34)$ & $0.999$ & $4.016$
+  \end{tabular}
+  \end{table}
+  \end{tiny}
+\end{frame}
+
+\section{Comparing with fpocket}
+
+\begin{frame}{Method}
+  \begin{block}{fpocket}
+    fpocket is a very fast open source protein pocket detection algorithm based on Voronoi tessellation
+    \begin{itemize}
+      \item \link{https://github.com/Discngine/fpocket}{fpocket GitHub repo}
+    \end{itemize}
+  \end{block}
+  \begin{block}{Steps for evaluating results (for a protein)}
+    \begin{itemize}
+      \item Download the PDB file
+      \item Run the fpocket command for the above PDB file
+      \begin{itemize}
+        \item Default script options
+      \end{itemize}
+      \item Take the 1st pocket result (highest score)
+      \item Calculate geometric center and distance from real binding site as before
+    \end{itemize}
+  \end{block}
+\end{frame}
+
+\begin{frame}{Comparing prediction results}
+  \begin{tiny}
+  \begin{table}
+  \caption{Comparison of DeepSite and fpocket algorithms}
+  \label{table:5}
+  \begin{tabular}{ c | c | c | c | c }
+    PDB ID & sc-PDB ID & fpocket pocket & fpocket score & distance to real (\AA) \\
+    \hline
+    2GQ3 & 2gq3\_1 & $(49.60, 27.14, 84.73)$ & $0.99$ & $4.22$ \\
+    1RJ9 & 1rj9\_1 & $(32.63, 5.71, 33.32)$ & $0.99$ & $4.62$ \\
+    10MH & 10mh\_1 & $(-15.86, 31.04, 91.05)$ & $0.263$ & $6.78$ \\
+    2QJP & 2qjp\_7 & $(71.70, -16.21, 32.28)$ & $0.984$ & $1.15$
+  \end{tabular}
+  \end{table}
+  \end{tiny}
+\end{frame}
+
+\section{Comments}
+
+\begin{frame}{Comments}
+  Overall: \textbf{It works!}
+
+  \begin{block}{However}
+    \begin{itemize}
+      \item Not all results can be verified
+      \begin{itemize}
+        \item e.g. protein 2QJP has $10+$ predicted pockets but only $2$ can be verified by sc-PDB
+      \end{itemize}
+    \end{itemize}
+  \end{block}
+
+  \begin{block}{Comparison to fpocket}
+    \begin{itemize}
+      \item The DeepSite algorithm seems to indeed score much better in most proteins
+      \item Regarding the distance from the real binding site, however, fpocket seems to perform better
+    \end{itemize}
   \end{block}
@@
     Thomas Pappas\\
-    \href{mailto:thpappas@di.uoa.gr}{thpappas@di.uoa.gr}
+    \link{mailto:thpappas@di.uoa.gr}{thpappas@di.uoa.gr}
   \end{center}

### 2020-07-17 stuctbio/Project/final_report.tex
StrucBio: Project: Included the final report of the project
Also included the helper python script to calculate protein geometric centers and distances

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass{beamer}
\mode<presentation>
{
  \usetheme[progressbar=foot,numbering=fraction,background=light]{metropolis} 
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
  %\setbeamertemplate{frame footer}{My custom footer}
}
\centering

\usepackage{graphicx}
\graphicspath{ {./fr_figures/} }
\usepackage{hyperref,xcolor}
\newcommand{\link}[2]{\href{#1}{\textcolor{blue}{\underline{#2}}}}

% Main document
\begin{document}
\title{DeepSite: NNets for binding site prediction}
\subtitle{Algorithms in Structural Bioinformatics}
\author{Thomas Pappas}
%\date{4 March 2020}
\maketitle

\begin{frame}{Agenda}
  \tableofcontents[hideallsubsections]
\end{frame}

\section{What is the project about?}

\begin{frame}{What is DeepSite?}
  \begin{block}{DeepSite}
    Protein-binding site \emph{predictor} using 3D-convolutional neural networks
  \end{block}
  \begin{block}{}
    DeepSite is an algorithm that given a protein it returns predictions about its binding pockets.
    It uses a Deep Convolutional Neural Network (DCNN) which is trained from an existing database of 7622 protein-binding sites (scPDB).
      %\item Superior performance to two other competitive algorithmic strategies
  \end{block}
  \begin{block}{}
      DeepSite is available online at \link{https://www.playmolecule.com/deepsite/}{https://www.playmolecule.com/deepsite/}
  \end{block}
\end{frame}

\begin{frame}{Aim and objectives of the project}
  \begin{block}{}
    In this project we will be focusing on the following:
  \end{block}
  \begin{block}{Review}
    First we will analyse how the algorithm works, i.e. how it converts a protein structure into an input for the DCNN, how is the later structured and how it uses its results to make predictions about the protein's binding sites?
  \end{block}
  \begin{block}{Confirm}
    % TODO: Add the new number of scPDB available data to date.
    The algorithm's DCNN was trained using the scPDB data available in 2017. Since then scPDB has gathered more data which gives us a great dataset to test and verify the accuracy of the algorithm.
  \end{block}
  \begin{block}{Compare}
    Investigate the algorithm's results and performance compared to other binding site prediction ones, and more specifically with the fpocket algorithm.
  \end{block}
\end{frame}

\begin{frame}{Challenges}
  \begin{block}{}
    Most of the challenges for this project derive from the fact that the algorithm was not reconstructed.
    While parts of the algorithm are included in the paper, due to lack or time, resources and expertise of the author, re-implementation was not possible.

    For this reason the \link{https://www.playmolecule.com/deepsite/}{DeepSite web app} was used to get the algorithm's output for a given protein.
  \end{block}
  \begin{block}{}
    Therefore
    \begin{itemize}
      \item The DCNN training and performance couldn't be evaluated
      \item In the review and comparison sections, the volumentric map of the binding site could not be utilised and thus focus has been put on the center $3D$ coordinates of the pocket
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Challenges}
  \begin{block}{}
    Another challenge in reviewing comes from the fact that the sc-PDB database provides very few binding site pocket for a given protein. Since the DeepSite algorithm can return multiple pocket predictions, we can only validate those available using the scPDB data.
  \end{block}
\end{frame}

\section{The DeepSite algorithm}

\begin{frame}{The DeepSite Algorithm}
  \begin{block}{I/O Overview}
    \begin{itemize}
      \item Input: A protein ID or a PDB file
      \item Output: A list of pocket predictions
      \begin{enumerate}
        \item Volumetric map of the protein's probability to have a pocket in a specific voxel, clustered in the different predictions
        \item 3D coordinates of the voxel with the highest probability in each cluster
        \item Prediction score
      \end{enumerate}
    \end{itemize}
  \end{block}
  \begin{block}{I/O Example}
    \begin{itemize}
      \item Input: "6FAT" (protein ID)
      \item Output (Volumetric map not utilised):
      \begin{enumerate}
        \item $\left[-1.4, 61.0, 69.6\right], 1.0$
        \item $\left[4.6, 37.0, 49.6\right], 0.94$
      \end{enumerate}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Example of a 6FAT protein}
  \begin{figure}[h]
    \includegraphics[width=1\textwidth]{deepsite_6fat_result}
    \caption{The 6FAT protein submitted in the \link{https://www.playmolecule.com/deepsite/}{DeepSite web app}}
  \end{figure}
\end{frame}

\begin{frame}{The DeepSite Algorithm}
  \begin{block}{Algorithm steps (summary)}
    \begin{enumerate}
      \item Take as input a protein ID or a PDB file and parse the DB atom coordinates to a grid
      \item Create 8 more grids, one for each protein property
      \begin{itemize}
        \item Each property grid is a probability map i.e. each voxel contains the probability of an atom of that property to be within it
        \item Each property grid is a Neural Network (NNet) channel
      \end{itemize}
      \item Take all $16 \times 16 \times 16$ \AA$^3$ subgrids from the 8 channels and give it as input to the DCNN
      \begin{itemize}
        \item The DCNN will return the probability for the center of the input subgrid to be in a binding site pocket
        \item Creates a probability map for all voxels of the protein
      \end{itemize}
    \end{enumerate}
  \end{block}
\end{frame}

\begin{frame}{The DeepSite Algorithm}
  \begin{block}{Algorithm steps (summary)}
    \begin{enumerate}
      \setcounter{enumi}{3}
      \item Use the Mean Shift (Comaniciu and Meer, 2002) clustering algorithm to distinquish the different binding site pockets
      \item Take the voxel with the max probability from each cluster and return its coordinates and its score
    \end{enumerate}
  \end{block}
\end{frame}

\subsection{Steps 1 & 2: Translating PDB to NNet channels}

\begin{frame}{Translating PDB to NNet channels}
  \begin{block}{Step 1: Parse the PDB data}
    \begin{itemize}
      \item Parse the atom coordinates from the PDB data
      \begin{itemize}
        \item Use of the HTMDs (Doerr et al., 2016) Python package
      \end{itemize}
      \item Consider the space grid containing the protein
      \begin{itemize}
        \item Grid is split to $1 \times 1 \times 1 $ \AA$^3$ voxels
        \item $+8$\AA \;for the cases where the binding pockets are on the edge
      \end{itemize}
    \end{itemize}
  \end{block}
%\end{frame}

%\begin{frame}{Translating PDB to NN channels}
  \begin{block}{Step 2: Generate the 8 protein-property grids/channels}
  Using the AutoDock 4 tables (Tables \ref{table:1} \& \ref{table:2}), for each of the 8 protein properties we do the following:
    \begin{itemize}
      \item Filter the atoms that have that property
      \item Create a grid and for each voxel calculate the atom occupancy, i.e. the probability for the voxel to contain an atom of that property
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{AutoDock 4 tables}
  \begin{columns}
    \begin{column}{.4\textwidth}
      \begin{tiny}
      \begin{table}
      \caption{Atom types}
      \label{table:1}
      \begin{tabular}{ l l }
        \hline
        Element & Description \\
        \hline
        C & Non H-bonding aliphatic carbon \\
        A & Non H-bonding aromatic carbon \\
        NA & Acceptor 1 H-bond nitrogen \\
        NS & Acceptor S Spherical nitrogen \\
        OA & Acceptor 2 H-bonds oxygen \\
        OS & Acceptor S Spherical oxygen \\
        SA & Acceptor 2 H-bonds sulfur \\
        HD & Donor 1 H-bond hydrogen \\
        HS & Donor S Spherical hydrogen \\
        MG & Non H-bonding magnesium \\
        ZN & Non H-bonding zinc \\
        MN & Non H-bonding manganese \\
        CA & Non H-bonding calcium \\
        FE & Non H-bonding iron \\
        \hline
      \end{tabular}
      \end{table}
      \end{tiny}
    \end{column}
    \begin{column}{.6\textwidth}
      \begin{tiny}
      \begin{table}
      \caption{Property-atom type correspondence}
      \label{table:2}
      \begin{tabular}{ l l }
        \hline
        Property & Rule \\
        \hline
        Hydrophobic & atom type C or A \\
        Aromatic & atom type A \\
        Hydrogen bond acceptor & atom type NA or NS or OA or OS or SA \\
        Hydrogen bond donor & atom type HD or HS with O or N partner \\
        Positive ionizable & atom with positive charge \\
        Negative ionizable & atom with negative charge \\
        Metal & atom type MG or ZN or MN or CA or FE \\
        Excluded volume & all atom types \\
      \end{tabular}
      \end{table}
      \end{tiny}
    \end{column}
  \end{columns}
  Table 1, Table 2, 10.1093/bioinformatics/btx350
\end{frame}

\begin{frame}{Translating PDB to NNet channels}
  \begin{block}{Atom occupancy}
    We calculate the probability of an atom of distance $r$ to the center of a voxel by using the pair correlation function.
    \[
      g(r) = exp(-\beta V(r))
    \]
    where $V(r) = \epsilon (r_{vdw}/r)^{12}$ and by taking $\epsilon = \beta^{-1}$ we get the \emph{single atom occupancy estimate} to be
    \[
      n(r) = 1 - exp(-(r_{vdw}/r)^{12})
    \]
  \end{block}
  \begin{block}{Building the NNet channels}
    For each channel we through each voxel and for each we calculate $n(r)$ for all atoms in the protein and assign to it the max value. This way we end up with 8 3D matrices where each voxel has the probability of having an atom of that property in them (Figure 2)
  \end{block}
\end{frame}

\begin{frame}{Translating PDB to NNet channels}
  \begin{figure}[h]
    \includegraphics[width=1\textwidth]{deepsite_protein_property_channels}
    \caption{Visual representations of descriptor channels (3/8) for PDB ID 4NIE, Figure S2, 10.1093/bioinformatics/btx350}
  \end{figure}
\end{frame}

\subsection{DCNN design}

\begin{frame}{DCNN design}
  \begin{block}{}
    Before we move on to Step 3., let's take a look at the DCNN design and architecture.

    The DCNN takes as input $8$ 3D matrices of size $16 \times 16 \times 16$ and outputs a value between $0$ and $1$ (probability).

    In context (after it is trained), it takes subgrids of the 8 protein property channels and then calculates the probability of the center voxel of that subgrid to be a binding site pocket.
  \end{block}
\end{frame}

\begin{frame}{DCNN design}
  \begin{figure}[h]
    \includegraphics[width=1\textwidth]{deepsite_dcnn_architecture}
    \caption{DeepSite’s internal DCNN architecture, Fig. 2, 10.1093/bioinformatics/btx350}
  \end{figure}
\end{frame}

\begin{frame}{DCNN properties}
  \begin{block}{Layers}
    \begin{itemize}
      \item 4 Convolutional Layers
      \item Max Pooling and Dropout layers after each 2
      \item Sigmoid activation function at the end to get a probability
    \end{itemize}
  \end{block}
  \begin{block}{But why such a structure was chosen?}
    \begin{itemize}
      \item Common practices in the ML community
      \item Simplified model due to scarcity of data
      \item Variations have been attempted with no apparent differences
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{DCNN properties}
  \begin{block}{Issues}
    \begin{itemize}
      \item Class imbalance problem since most protein subgrids are not close to a binding site
      \begin{itemize}
        \item Tackled by undersampling of dataset
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{DCNN training}
  \begin{block}{}
    To understand better how the DCNN returns the probability for the center of the subgrid to be a binding site pocket, we should examine how it was trained.
    To do so the sc-PDB data was used which contain the binding site pockets for a given protein.
  \end{block}
  \begin{block}{Training}
    \begin{itemize}
      \item Input subgrids of $16 \times 16 \times 16$ \AA$^3$
      \item Step of 4 voxels
      \item Success criteria: Geometric center is closer than 4 \AA\;to the actual pocket geometric center
    \end{itemize}
  \end{block}
  \begin{block}{}
    The NNet is therefore tuned to predict if the center of the subgrid is close to a pocket.
  \end{block}
\end{frame}

\begin{frame}{DCNN training}
  To evaluate the accuracy of the DCNN, the 10-fold cross-validation method was used
  \begin{block}{Steps}
    \begin{itemize}
      \item Split the training dataset (7622 scPDB structures) to 10 (equal size) sets
      \item Consider one as a testing set and the rest as training ones and evaluate its success
      \item Cycle through each set and repeat the evaluation
      \item Final success result is the average of all above evaluations
    \end{itemize}
  \end{block}
  \begin{block}{Why $k$-fold cross validation?}
    \begin{itemize}
      \item Common practice for validating NNet models
      \item Limits the possibility of over-fitting
    \end{itemize}
  \end{block}
\end{frame}

\subsection{Step 3-4: The probability map and returned values}

\begin{frame}{Steps 3: The probability map}
  \begin{block}{}
    Getting back to the algorithm now with a trained DCNN, in Step $3.$ it will run it for all subgrids and will output a full probability map for all voxels of the protein.

    Each number represents the probability of the voxel to be close to a binding site pocket.
  \end{block}
\end{frame}

\begin{frame}{Step 4-5: The returned values}
  \begin{block}{}
    Then in Step $4.$ it uses the Mean-Shift (Comaniciu and Meer, 2002) clustering algorithm to distinguish different binding sites in that protein.

    Finally, in Step $5.$ it takes the maximum probability voxel out of each cluster and retuns its coordinates and score.
  \end{block}
\end{frame}

\section{Confirming for old and new sc-PDB data}

\begin{frame}{Evaluation metrics}
  To evaluate the accuracy of the DeepSite predictions \\
  the following metrics are suggested
  \begin{block}{Distance to the center of the binding site (DCC)}
    A prediction is successful if it's center is closer than a threshold of  4 to 20 \AA\;to the real binding site geometric center
    \begin{itemize}
      \item Ignores the shape of the predicted pocket
    \end{itemize}
  \end{block}
  \begin{block}{Discretized volumetric overlap (DVO)}
    Discretize protein space to $1 \times 1 \times 1$ \AA$^3$ voxels and calculate the Jaccard index
    \[
      J = \frac{\#|V_r \cap V_p|}{\#|V_r \cup V_p|}
    \]
    $V_r$: set of voxels in real binding pocket\\
    $V_p$: set of voxels in predicted binding pocket
    \begin{itemize}
      \item Takes into account the shape of the predicted pocket
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Evaluation metrics}
  \begin{block}{}
    As mentioned before, since the predicted binding site space is not utilised, DVO cannot be utilised either.
  We will therefore focus on DCC for our evaluations.
  \end{block}
  \begin{block}{sc-PDB}
    When DeepSite was published, sc-PDB contained 9283 entries;\\
    as of today it has 16034
  \end{block}
  \begin{block}{}
    The above allows us to test with binding pocket data existing both when the algorithm was published, but also afterwards.
  \end{block}
\end{frame}

\begin{frame}{Evaluation metrics}
  \begin{block}{Steps for evaluating results for a protein in sc-PDB}
    To evalulate a prediction for a protein for which we have the actual pocket data in sc-PDB we do the following
    \begin{enumerate}
      \item Find and download the sc-PDB entry using the \link{http://bioinfo-pharma.u-strasbg.fr/}{sc-PDB website}
      \begin{itemize}
        \item (Real) Binding site atom info contained in "site.mol2" file
        \item Alternatively one can download the entire sc-PDB database and find afterwards any protein data locally
      \end{itemize}
      \item Run the DeepSite algorithm from the \link{https://www.playmolecule.com/deepsite/}{online web app} using the PDB ID and the chain from the sc-PDB info
      \begin{itemize}
        \item Download the results, i.e. the center coordinates of all the binding site pocket predictions
      \end{itemize}
    \end{enumerate}
  \end{block}
\end{frame}

\begin{frame}{Evaluation metrics}
  \begin{block}{Steps for evaluating results for a protein in sc-PDB (cont.)}
    \begin{enumerate}
      \setcounter{enumi}{2}
      \item Calculate the geometric center of the real binding site
      \item Calculate the distance (norm) between the center of the real binding site and the DeepSite predictions
      \begin{itemize}
        \item Distance for exactly one of them should be $<20$\AA
      \end{itemize}
    \end{enumerate}
    The reason for the last criteria is that if two prediction centers are both closer than 20 \AA\; to another point, they would have already been clustered as belonging to the same pocket.
    Therefore we shouldn't expect more than one prediction to be that close to the real pocket center.
  \end{block}
\end{frame}

\begin{frame}{Confirm the old sc-PDB data}
  \begin{block}{}
    To begin with we will first try to confirm that the algorithm works for the proteins it was trained with.
    This might at first seem redundant but as a first step we can confirm its accuracy for some trivial predictions, while the measurement can also serve as a control group for our evaluation metric.
  \end{block}
\end{frame}

\begin{frame}{Confirm for old sc-PDB data}
  \begin{tiny}
  \begin{table}
  \caption{Success evaluation for proteins in the training set}
  \label{table:3}
  \begin{tabular}{ c | c | c | c | c }
    PDB ID (chain) & DeepSite site prediction & sc-PDB ID & sc-PDB site (geom. c) & distance (\AA) \\
    \hline
    2GQ3 (A) & $(39.08, 40.04, 83.57)$ & 2gq3\_1 & $(48.99, 24.08, 81.9)$ & $18.86$ \\
    1HT2 (H) & $(100.75, 84.69, 105.11)$ & 1ht2\_4 & $(102.76, 82.49, 105.04)$ & $2.98$ \\
    3AHN (A) & $(18.3, -0.36, 4.47)$ & 3ahn\_1 & $(16.48, -0.38, 0.89)$ & $4.02$ \\
    1RBQ (B) & $(-42.67, 44.16, 11.63)$ & 1rbq\_2 & $(-46.8, 33.06, 10.98)$ & $4.02$ \\
    2G20 (A) & $(13.12, 45.87, 106.54)$ & 2g20\_1 & $(9.54, 43.78, 105.38)$ & $4.30$ \\
    %1OO6 () & 1oo6_1
    1RJ9 (A) & $(30.88, 8.67, 27.27)$ & 1rj9\_1 & $(32.28, 6.8, 28.85)$ & $2.83$ \\
  \end{tabular}
  \end{table}
  \end{tiny}
  To ensure the proteins selected will not have the same protein pocket, each was selected from a different set used in the 10-fold cross-validation
\end{frame}

\begin{frame}{Confirm for old sc-PDB data}
  \begin{block}{Notes}
    Thefore the following points should be noted:
    \begin{itemize}
      \item Not all results can be verified
      \begin{itemize}
        \item e.g. protein 2QJP has $10+$ predicted pockets but only $2$ can be verified by sc-PDB
      \end{itemize}
      \item Out of all the predictions, all of them were compared with the actual pocket center and only one of them had a distance less than $20$ \AA
      \item So for the "old" data the numbers are as expected.
      Also most of them are very close to the real pocket ($\sim 4$ \AA)
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Confirm for newer additions to the sc-PDB}
  \begin{block}{}
    Now let's move on to testing from data that were not included in the DCNN's training.
  \end{block}
  \begin{tiny}
  \begin{table}
  \caption{Success evaluation for newer proteins}
  \label{table:4}
  \begin{tabular}{ c | c | c | c | c }
    PDB ID (chain) & DeepSite site prediction & sc-PDB ID & sc-PDB site (geom. c) & distance (\AA) \\
    \hline
    10MH (A) & $(-23.23, 45.71, 89.51)$ & 10mh\_1 & $(-16.32, 30.01, 84.37)$ & $17.91$ \\
    2QJP (G) & $(73.90, 28.70, 35.20)$ & 2qjp\_6 & $(73.16, 25.08, 36.36)$ & $3.87$ \\
    2QJP (J) & $(75.51, -12.29, 33.10)$ & 2qjp\_7 & $(71.24, -15.37, 32.92)$ & $5.27$ \\
    4YLH (K) & $(64.01, 100.21, -24.34)$ & 4ylh\_11 & $(71.7, 97.15, -21.56)$ & $4.016$
  \end{tabular}
  \end{table}
  \end{tiny}
  Same notes apply as before
\end{frame}

\section{Comparing with fpocket}

\begin{frame}{Method}
  \begin{block}{fpocket}
    fpocket is a very fast open source protein pocket detection algorithm based on Voronoi tessellation
    \begin{itemize}
      \item \link{https://github.com/Discngine/fpocket}{fpocket GitHub repo}
    \end{itemize}
  \end{block}
  \begin{block}{Steps for evaluating results (for a protein)}
    \begin{enumerate}
      \item Download the PDB file
      \item Run the fpocket command for the above PDB file
      \begin{itemize}
        \item Default script options
      \end{itemize}
      \item Take the 1st pocket result (highest score)
      \item Calculate geometric center and distance from real binding site as before
    \end{enumerate}
  \end{block}
\end{frame}

\begin{frame}{Comparing prediction results}
  \begin{tiny}
  \begin{table}
  \caption{Success evaluation for the fpocket algorithm}
  \label{table:5}
  \begin{tabular}{ c | c | c | c | c | c }
    PDB ID & fpocket pocket & fpocket score & sc-PDB ID & sc-PDB site (geom. c) & distance (\AA) \\
    \hline
    2GQ3 & $(49.60, 27.14, 84.73)$ & $1.208$ & 2gq3\_1 & $(48.99, 24.08, 81.9)$ & $4.22$ \\
    1HT2 & $(115.54, 54.79, 99.14)$ & $0.627$ & 1ht2\_4 & $(102.76, 82.49, 105.04)$ & $31.07$ \\
    3AHN & $(18.74, -1.0, 4.64)$ & $0.621$ & 3ahn\_1 & $(16.48, -0.38, 0.89)$ & $4.42$ \\
    1RBQ & $(-45.78, 34.1, 9.79)$ & $0.723$ & 1rbq\_2 & $(-46.8, 33.06, 10.98)$ & $1.88$ \\
    2G20 & $(11.64, 41.15, 107.19)$ & $0.713$ & 2g20\_1 & $(9.54, 43.78, 105.38)$ & $3.82$ \\
    1RJ9 & $(32.63, 5.71, 33.32)$ & $1.084$ & 1rj9\_1 & $(32.28, 6.8, 28.85)$ & $4.62$ \\
    10MH & $(-15.86, 31.04, 91.05)$ & $0.441$ & 10mh\_1 & $(-16.32, 30.01, 84.37)$ & $6.78$ \\
    2QJP & $(71.70, -16.21, 32.28)$ & $1.025$ & 2qjp\_6 & $(73.16, 25.08, 36.36)$ & $41.51$ \\
    2QJP & $(71.70, -16.21, 32.28)$ & $1.025$ & 2qjp\_7 & $(71.24, -15.37, 32.92)$ & $1.15$ \\
    4YLH & $(72.96, 90.19, -23.0)$ & $0.617$ & 4ylh\_11 & $(71.7, 97.15, -21.56)$ & $7.22$
  \end{tabular}
  \end{table}
  \end{tiny}
\end{frame}

\begin{frame}{Comparing prediction results}
  \begin{block}{Parameters for the fpocket comparison}
    The following should be considered when viewing the above:
    \begin{itemize}
      \item fpocket does not separate its predictions per chain
      \item The pocket prediction used is the one with the highest score which means that other ones could perform better \\
      e.g. for protein 1HT2 there are 170 pocket predictions with the 4th having a distance of $2.24$ \AA\; to the real one, though with a score of $0.195$
      \begin{itemize}
        \item Could be related to the point about the different chains, since as we can see for protein 2QJP where we have data for both chains $G$ and $J$, they have distances $41.51$ and $1.15$ respectively
      \end{itemize}
      \item fpocket provides a "Score" and a "Druggability Score" in its results. The first has been used and the prediction with the highest value was picked
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Comparing prediction results}
  \begin{tiny}
  \begin{table}
  \caption{Comparison of DeepSite and fpocket algorithms}
  \label{table:6}
  \begin{tabular}{ c | c | c }
    PDB ID & DeepSite distance (\AA) & fpocket distance (\AA) \\
    \hline
    2GQ3 & $18.86$ & $4.22$ \\
    1HT2 & $2.98$ & $31.07$ \\
    3AHN & $4.02$ & $4.42$ \\
    1RBQ & $4.02$ & $1.88$ \\
    2G20 & $4.30$ & $3.82$ \\
    1RJ9 & $2.83$ & $4.62$ \\
    10MH & $17.91$ & $6.78$ \\
    2QJP (G) & $3.87$ & $41.51$ \\
    2QJP (J) & $5.27$ & $1.15$ \\
    4YLH & $4.016$ & $7.22$
  \end{tabular}
  \end{table}
  \end{tiny}
\end{frame}

\begin{frame}{Comparing prediction results}
  \begin{block}{Observations}
    \begin{itemize}
      \item In terms of approaching the real pocket (chain parameters considered) it seems in most cases DeepSite can make bigger errors but it will not miss it (i.e. distance $> 20$ \AA) as much
      \item In terms of score (if comparable), DeepSite's predictions has always a score $\sim 0.9$ while fpocket has $\sim 0.7$
      \item (And a general observation) Obviously DeepSite is a much slower algorithm since it uses a DCNN
    \end{itemize}
  \end{block}
\end{frame}

\section{Final Comments}

\begin{frame}{Final Comments}
  \begin{block}{}
    Even though it seems quite clear that the DeepSite algorithm has superior performance compared to fpocket, the above analysis is obviously far from thorough to verify so.

    Also while the volumetric map of the clustered binding site pockets was not utilised, the DeepSite web app does provide a "Cube" file which could potentially be used to extrapolate that data.
    This possibility has not been explored in this project.

    In the least, hopefully the comments and flags that were raised throught this presentation can compensate for the above and give a clearer picture of DeepSite's behavior and performance.
  \end{block}
\end{frame}

\begin{frame}{Contact details}
  \begin{center}
    Thomas Pappas\\
    \link{mailto:thpappas@di.uoa.gr}{thpappas@di.uoa.gr}
  \end{center}
\end{frame}

\end{document}

### 2020-07-17 stuctbio/Project/calculateDist.py

@@ -1,0 +1,52 @@
+from pathlib import Path
+from htmd.ui import *
+import numpy as np
+
+
+def get_real_binding_site_geo_center(scpdb_id):
+    # Calculate the distance of the predicted point to the real binding site.
+    local_path_to_scpdb = '/.../Project/scPDB/'
+    mol = Molecule(local_path_to_scpdb + scpdb_id + '/site.mol2')
+    coords = mol.get('coords')
+    return np.mean(coords, axis=0)
+
+
+def check_deepsite(scpdb_id, prediction):
+    return np.linalg.norm(prediction - get_real_binding_site_geo_center(scpdb_id))
+
+
+def check_fpocket(scpdb_id):
+    pdb_id = scpdb_id.split('_')[0]
+
+    # In case we need to iterate though all pockets.
+    pathlist = Path('/.../Project/PD/'
+                    + pdb_id + '/' + pdb_id + '_out/pockets').glob('*.pdb')
+    for path in pathlist:
+        mol = Molecule(str(path))
+        coords = mol.get('coords')
+        c = np.mean(coords, axis=0)
+        d = np.linalg.norm(c - get_real_binding_site_geo_center(scpdb_id))
+        if d < 20:
+            print('Path', path, 'Center', c, 'distance', d)
+
+    # Parse the PDB data
+    mol = Molecule('/.../Project/PD/'
+                   + pdb_id + '/' + pdb_id + '_out/pockets/pocket1_atm.pdb')
+    coords = mol.get('coords')
+    c = np.mean(coords, axis=0)
+    return [c, np.linalg.norm(c - get_real_binding_site_geo_center(scpdb_id))]
+
+
+# DeepSite
+scpdb = '4ylh_11'
+point = np.array([13.12000084, 45.86599922, 106.54499817])
+
+# real = get_real_binding_site_geo_center(scpdb)
+# print('(' + str(round(real[0], 2)) + ', ' + str(round(real[1], 2)) + ', ' + str(round(real[2], 2)) + ')')
+# print(scpdb.split('_')[0].upper(), '&', scpdb,
+#       '$(' + str(round(point[0], 2)) + ', ' + str(round(point[1], 2)) + ', ' + str(round(point[2], 2)) + ')$',
+#       '&', '$' + str(check_deepsite(scpdb, point)) + '$', '\\\\')
+# fpocket
+# fp = check_fpocket('4ylh_11')
[…]

### 2020-11-04 geodata/project1/project1.tex
Geodata: Added project1
Tex file plus the figure

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass{beamer}
\mode<presentation>
{
  \usetheme[progressbar=foot,numbering=fraction,background=light]{metropolis} 
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
  %\setbeamertemplate{frame footer}{My custom footer}
}
\centering

\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{hyperref,xcolor}
\newcommand{\link}[2]{\href{#1}{\textcolor{blue}{\underline{#2}}}}

% Main document
\begin{document}
\title{Convergence diagnostics for Markov chain Monte Carlo}
\subtitle{Geometric Data Analysis}
\author{Thomas Pappas}
%\date{4 March 2020}
\maketitle

\begin{frame}{Agenda}
  \tableofcontents[hideallsubsections]
\end{frame}

\section{What are Convergence Diagnostics?}

\begin{frame}{What are Convergence Diagnostics?}
  \begin{block}{}
    Determining convergence of the underlying Markov chain to stationarity and convergence of Monte Carlo estimators to population quantities, respectively.
  \end{block}
  \begin{block}{Answering the following questions}
    \begin{itemize}
      \item When to start the algorithm? ($n^\prime$)
        \begin{itemize}
          \item Remove first results to improve the sample, especially when the initial value is not in a high-density region
          \item Called "burn-in"
        \end{itemize}
      \item When to end the algorithm? ($n^*$) (in relation to the step $\epsilon$)
        \begin{itemize}
          \item Use of $E_\pi g, \bar{g}_{n^\prime,n}$ where $g$ a real-value function of what we need to estimate
        \end{itemize}
      %\item What is the overall convergence assessment of the Markov chain to the stationary distribution?
    \end{itemize}
  \end{block}
\end{frame}

\section{MCMC Diagnostics}

\begin{frame}{Honest MCMC}
  Method for finding $n^\prime$ and $n^*$
  \begin{block}{Honest value for burn-in}
    For a Markov chain estimator $X_n$ and $f_n$ its density, we know that $X_n$ converges in the total variation (TV) norm for $\pi$, i.e.
    \[
      \frac{1}{2}\int_\chi|f_n(x)-\pi(x)|dx \downarrow 0 \textrm{ as } n \rightarrow \infty
    \]
    Therefore we can take an arbitrary cutoff value (here $0.01$) and find the smallest number $n^\prime$ such that
    \[
      \frac{1}{2}\int_\chi|f_{n^\prime}(x)-\pi(x)|dx < 0.01
    \]
    TV norm generally not available, use of \textit{drift} and \textit{minorization} (d\&m) technique to construct a quantitative bound.
  \end{block}
\end{frame}

\begin{frame}{Honest MCMC}
  \begin{block}{Honest stopping rule - Background}
    Let $g$ be a real value function so that $E_\pi g$ becomes a particular feature of the target density. From the strong law of large numbers we get
    \[
      \bar{g}_{n^\prime,n} \equiv \sum_{i=n^\prime}^n g(X_i)/(n-n^\prime) \rightarrow E_\pi g \textrm{ as } n \rightarrow \infty
    \]
    We take $n^\prime = 0$ and we write $\bar{g}_n$ for $\bar{g}_{0,n}$.
  \end{block}
\end{frame}

\begin{frame}{Honest MCMC}
  \begin{block}{Honest way to stop the chain - Background}
    Now if a central limit theorem (CLT) is available for $\bar{g}_n$ , we get
    \[
      \sqrt{n}(\bar{g}_n-E_\pi g) \rightarrow^d N(0,\sigma_g^2) \textrm{ as } n \rightarrow \infty
    \]
    where
    \[
      \sigma_g^2 \equiv Var_\pi(g(X_0))+2\sum_{i=1}^\infty Cov_\pi(g(X_0),g(X_i)) < \infty
    \]
    If $\widehat{\sigma}_{g,n}$ is a consistent estimator of $\sigma_g$, then an estimator of the standard error of $\bar{g}_n$ is $\widehat{\sigma}_{g,n}/\sqrt{n}$.
  \end{block}
\end{frame}

\begin{frame}{Honest MCMC}
  \begin{block}{Honest way to stop the chain - fixed-width stopping rule (FWST)}
    To achieve the confidence interval to fall under a threshold $\epsilon$, we terminate the simulation, first after $\tilde{n}$ iterations, and then when
    \[
      t_*\frac{\widehat{\sigma}_{g,n}}{\sqrt{n}}+\frac{1}{n} \leq \epsilon
    \]
    Note that:
    \begin{itemize}
      \item We execute $\tilde{n}$ iterations to avoid early stop due to poor estimate of $\widehat{\sigma}_{g,n}$
        \begin{itemize}
          \item Value should depend on the complexity of the problem
          \item $\tilde{n} = 10^4$ works well in practice
        \end{itemize}
      \item $t_*$ is an appropriate quantile
        \begin{itemize}
          \item In relation with the confidence interval $100(1-\alpha)\%$
        \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Graphical methods}
  Methods for MCMC convergence diagnosis
  \begin{block}{Trace plot}
    Time series plat that shows the realisations of the Markov chain at each iteration against the iteration numbers.
    \begin{itemize}
      \item Visualise the movement in the state space
      \item If the chain is "stuck" then it shows flat bits
        \begin{itemize}
          \item e.g. if in Metropolis-Hasting (MH) we have many consecutive rejections or acceptances
        \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Graphical methods}
  \begin{block}{lag-$k$ autocorrelation}
    The correlation between the samples $k$ steps apart. Shows values of the lag-$k$ autocorrelation function (ACF) against increasing $k$ values.
    \begin{itemize}
      \item For fast-mixing Markov chains, ACF should quickly drop to $0$
    \end{itemize}
  \end{block}
  \begin{block}{Running mean plot}
    Shows the Monte Carlo time average estimates against the iterations.
    \begin{itemize}
      \item Line plot should stabilise to a fixed number
      \item Used to decide stopping times
      \item Has faced criticism
    \end{itemize}
  \end{block}
  %In the multivariant case, all above methods are made by using marginal chains
\end{frame}

%\begin{frame}{Two spectral density-based methods?}
%
%\end{frame}
%
%\begin{frame}{Effective sample size?}
%
%\end{frame}

\section{Examples}

\begin{frame}{An exponential target distribution}
  \begin{block}{}
    \begin{itemize}
      \item Target distribution: $Exp(1)$
      \item Target density: $\pi(x) = exp(-x), x > 0$
      \item Independence Metropolis sampler $Exp(\theta)$
        \begin{itemize}
          \item density: $q(x) = \theta exp(-\theta x), x > 0$
        \end{itemize}
      \item We study the independence chain corresponding to\\
        $\theta = 0.5$ and $\theta = 5$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{An exponential target distribution}
  \begin{block}{Graphical methods}
    \begin{itemize}
      \item We run for 1,000 iterations
      \item $X_0 = 0.1$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{An exponential target distribution}
  \begin{block}{Trace and autocorrelation plots}
    \begin{figure}[h]
      \includegraphics[width=0.8\textwidth]{example1_trace_autocorrellation_plot}
      \caption{Trace and autocorrelation function plots. Top row, $\theta = 0.5$; bottom row, $\theta = 5$.}
    \end{figure}
  \end{block}
\end{frame}

\begin{frame}{An exponential target distribution}
  \begin{block}{Trace and autocorrelation plots}
    \begin{itemize}
      \item For $\theta = 0.5$ the chain mixes well but for $\theta = 5$ the chain needs to be run longer
      \item $\theta = 0.5$ seems to require no burn-in in contrast with $\theta = 5$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{An exponential target distribution}
  \begin{block}{Honest burn-in}
    For $\theta < 1$, we get that
    \[
      \pi(x) / q(x) = \theta^{-1}exp(x(\theta-1)) \leq \theta^{-1}, x > 0
    \]
    and therefore (according to Mengersen and Tweedie (1996))
    \[
      \frac{1}{2}\int_{\chi}|f_n(x)-\pi(x)|dx \leq (1-\theta)^n
    \]
    which is an analytical upper bound of the TV norm. So for $\theta = 0.5$ if $n^\prime = \lceil log(0.01)/log(0.5)\rceil = 7$ can be an appropriate burn-in.\\
    For $\theta = 5$ the upper bound can't be used.
  \end{block}
  % For $\theta = 5$ the independence chain becomes subgeometric and...
\end{frame}

\begin{frame}{An exponential target distribution}
  \begin{block}{Honest way to stop the chain}
    We consider estimation of the mean of the stationary distribution, i.e. $E_\pi X = 1$.
    \begin{itemize}
      \item We apply FWSR for $\epsilon = 0.005$ and $\alpha = 0.05$
        \begin{itemize}
          \item Which makes $t_* = 1.96$
        \end{itemize}
    \end{itemize}
    \begin{itemize}
      \item For $\theta = 0.5$
        \begin{itemize}
          \item Starting at $X_s = 0.1545$
          \item $n^* = 323,693$ iterations
        \end{itemize}
      \item For $\theta = 5$
        \begin{itemize}
          \item Starting at $X_0 = 0.1$
          \item $n^* = 323,700$ iterations
          \item No CLT function available so can't compute asymptotic confidence intervals
        \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{An exponential target distribution}
We run mean estimates to evaluate the results
  \begin{figure}[h]
    \includegraphics[width=1\textwidth]{example1_mean_estimates}
    \caption{Running mean estimates, on the left for $\theta = 0.5$ with confidence intervals, on the right for $\theta = 5$ without. The horizontal line denotes the truth.}
  \end{figure}
  Conclusions are the same as before
\end{frame}

%\begin{frame}{A Bayesian logistic model?}
%
%\end{frame}

\begin{frame}{Contact details}
  \begin{center}
    Thomas Pappas\\
    \link{mailto:thpappas@di.uoa.gr}{thpappas@di.uoa.gr}
  \end{center}
\end{frame}

\end{document}

### 2020-11-09 logic/presentation_2-4_2020-11-06.tex
Logic: First version of the presentation on chapter 2.4 for Friday 06/11/2020

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass{beamer}
\mode<presentation>
{
  \usetheme[progressbar=foot,numbering=fraction,background=light]{metropolis} 
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
  %\setbeamertemplate{frame footer}{My custom footer}
}
\centering

% Greek fonts
\usepackage{fontspec}
%\RequirePackage[cm-default]{fontspec}
\defaultfontfeatures{Mapping=tex-text}
  % you may want to try: {FreeSerif} or {Times New Roman}
%\setmainfont{Liberation Serif}
  % you may want to try: {FreeSans} or {Arial}
\setsansfont[Scale=MatchLowercase]{Liberation Sans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{Liberation Mono}

\usepackage{graphicx}
\graphicspath{ {./figures/} }
\usepackage{hyperref,xcolor}
\newcommand{\link}[2]{\href{#1}{\textcolor{blue}{\underline{#2}}}}

% Main document
\begin{document}
\title{Κατηγορηματικός Λογισμός}
\subtitle{Μαθηματική Λογική}
\author{Θωμάς Παππάς}
\date{Παρασκευή 6 Νοεμβρίου 2020}
\maketitle

\begin{frame}{Agenda}
  \tableofcontents[hideallsubsections]
  %\tableofcontents
\end{frame}

%\AtBeginSection{}

\section{Τυπικές αποδείξεις και Μεταθεωρήματα}

\subsection{Κανόνας $T$}

\begin{frame}{Κανόνας $T$}
  Αν $\Gamma \vdash \alpha_1, \ldots, \Gamma \vdash \alpha_n$ και $\{\alpha_1, \ldots, \alpha_n\} \models^{\textrm{T}\Sigma} \beta$, τότε $\Gamma \vdash \beta$.
  \begin{block}{Απόδειξη}
    Ο τύπος $\alpha_1 \rightarrow \cdots \rightarrow \alpha_n \rightarrow \beta$ είναι ταυτολογία και άρα Λογικό Αξίωμα.
    Εφαρμόζουμε Modus Ponens $n$ φορές.
  \end{block}
\end{frame}

\subsection{Μεταθεώρημα Συναγωγής}

\begin{frame}{Μεταθεώρημα Συναγωγής}
  Αν $\Gamma ; \gamma \vdash \phi$ τότε $\Gamma \vdash (\gamma \rightarrow \phi)$.\\
  \begin{small}Το αντίστροφο είναι το Modus Ponens\end{small}
  \begin{block}{1η Απόδειξη}
    Έχουμε ότι $\Gamma ; \gamma \vdash \phi$
    \begin{itemize}
      \item[] ανν $(\Gamma ; \gamma) \cup \Lambda \models^{\textrm{T}\Sigma} \phi$
      \item[] ανν $\Gamma \cup \Lambda \models^{\textrm{T}\Sigma} (\gamma \rightarrow \phi)$
      \item[] ανν $\Gamma \vdash (\gamma \rightarrow \phi)$
    \end{itemize}
  \end{block}
\end{frame}
\begin{frame}{Μεταθεώρημα Συναγωγής}
  Αν $\Gamma ; \gamma \vdash \phi$ τότε $\Gamma \vdash (\gamma \rightarrow \phi)$.
  \begin{block}{2η Απόδειξη}
    Θα δείξουμε με επαγωγή ότι για κάθε $\phi$ θεώρημα του $\Gamma ; \gamma$, ο τύπος $(\gamma \rightarrow \phi)$ είναι επίσης θεώρημα του $\Gamma$
    \begin{itemize}
      \item Περίπτωση 1: $\phi = \gamma$. Τότε προφανώς $\vdash (\gamma \rightarrow \phi)$
      \item Περίπτωση 2: $\phi$ λογικό αξίωμα ή μέλος του $\Gamma$.
        Τότε $\Gamma \vdash \phi$ και αφού $\phi \models^{\textrm{T}\Sigma} (\gamma \rightarrow \phi)$ τότε από τον κανόνα $T$ παίρνουμε $\Gamma \vdash (\gamma \rightarrow \phi)$.
      \item Περίπτωση 3: $\phi$ είναι από Modus Ponens στις $\psi$ και $(\psi \rightarrow \phi)$.\\
        Από επαγωγική υπόθεση $\Gamma \vdash (\gamma \rightarrow \psi)$ και $\Gamma \vdash (\gamma \rightarrow (\psi \rightarrow \phi))$.\\
        Τέλος, εφόσον $\{\gamma \rightarrow \psi, \gamma \rightarrow (\psi \rightarrow \phi)\} \models^{\textrm{T}\Sigma} \gamma \rightarrow \phi$ τότε από τον κανόνα $T$ παίρνουμε $\Gamma \vdash (\gamma \rightarrow \phi)$
    \end{itemize}
  \end{block}
\end{frame}

\subsection{Μεταθεώρημα Αντιθετοαναστροφής}

\begin{frame}{Μεταθεώρημα Αντιθετοαναστροφής}
  $\Gamma ; \phi \vdash \neg\psi$ ανν $\Gamma ; \psi \vdash \neg\phi$
  \begin{block}{Απόδειξη}
    \begin{itemize}
      \item[] $\Gamma ; \phi \vdash \neg\psi$ ανν $\Gamma \vdash \phi \rightarrow \neg\psi$ από το Μεταθεώρημα Συναγωγής
      \item[] ανν $\Gamma \vdash \psi \rightarrow \neg\phi$ από τον κανόνα $T$, αφού $\{\phi \rightarrow \neg\psi\} \models^{\textrm{T}\Sigma} (\psi \rightarrow \neg\phi)$
      \item[] ανν $\Gamma ; \psi \vdash \neg\phi$ από Modus Ponens
    \end{itemize}
  \end{block}
\end{frame}

\subsection{Μεταθεώρημα εις άτοπον απαγωγής}

\begin{frame}{Μεταθεώρημα εις άτοπον απαγωγής}
  \begin{block}{Ορισμός}
    Ένα σύνολο από τύπους $\Sigma$ θα λέγεται \textit{αντιφατικό} ανν για κάποιο τύπο $\beta$  ισχύει ότι $\Sigma \vdash \beta$ και $\Sigma \vdash \neg\beta$
  \end{block}

  \begin{block}{Μεταθεώρημα εις άτοπον απαγωγής}
    Αν $\Gamma ; \phi$ είναι αντιφατικό τότε $\Gamma \vdash \neg\phi$.
  \end{block}

  \begin{block}{Απόδειξη}
    Αφού $\Gamma ; \phi$ αντιφατικό τότε υπάρχει τύπος $\beta$ τέτοιος ώστε $\Sigma \vdash \beta$ και $\Sigma \vdash \neg\beta$.\\
    Απο Μεταθεώρημα Συναγωγής παίρνουμε $\Gamma \vdash (\phi \rightarrow \beta)$ και $\Gamma \vdash (\phi \rightarrow \neg\beta)$\\
    Επίσης $\{\phi \rightarrow \beta, \phi \rightarrow \neg\beta\} \models^{\textrm{T}\Sigma} \neg\phi$ και άρα από τον κανόνα $T$ παίρνουμε $\Gamma \vdash \neg\phi$.
  \end{block}
\end{frame}

\begin{frame}{Παράδειγμα}
  \begin{block}{}
    Θα δείξουμε ότι $\vdash \exists x \forall y \phi \rightarrow \forall y \exists x \phi$.
    \begin{itemize}
      \item[] από Μεταθεώρημα Συναγωγής, αρκεί ν.δ.ο. $\exists x \forall y \phi \vdash \forall y \exists x \phi$
      \item[] από Μεταθεώρημα Γενίκευσης, αρκεί ν.δ.ο. $\exists x \forall y \phi \vdash \exists x \phi$
      \item[] ισοδύναμα, αρκεί ν.δ.ο. $\neg\forall x \neg\forall y \phi \vdash \neg\forall x \neg\phi$
      \item[] από το Μεταθεώρημα Αντιθετοαναστροφής, αρκεί ν.δ.ο. $\forall x \neg\phi \vdash \forall x \neg\forall y \phi$
      \item[] από το Μεταθεώρημα Γενίκευσης, αρκεί ν.δ.ο. $\forall x \neg\phi \vdash \neg\forall y \phi$
      \item[] από το Μεταθεώρημα της εις άτοπον απαγωγής, αρκεί ν.δ.ο. το $\{\forall x \neg\phi, \forall y \phi\}$ είναι αντιφατικό
      \begin{itemize}
        \item $\forall x \neg\phi \vdash \neg\phi$ από το Αξίωμα 2 και Modus Ponens
        \item $\forall y \phi \vdash \phi$ για τον ίδιο λόγο
      \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\section{Στρατηγικές Τυπικών Αποδείξεων και Παραδείγματα}

\begin{frame}{Στρατηγικές Τυπικών Αποδείξεων}
  \begin{block}{}
    Θα δούμε στρατηγικές για να κατασκευάζουμε τυπικές αποδείξεις προτάσεων.
  \end{block}
  \begin{block}{}
    Αν ένας τύπος $\phi$ είναι της μορφής
    \begin{itemize}
      \item $(\psi \rightarrow \theta)$, τότε αρκεί ν.δ.ο. $\Gamma ; \psi \vdash \theta$
      \item $\forall x \psi$
        \begin{itemize}
          \item Αν η $x$ δεν εμφανίζεται ελεύθερη στον $\psi$ τότε αρκεί ν.δ.ο. $\Gamma \vdash \psi$
          \item Διαφορετικά, θα υπάρχει πάντα μια μεταβλητή $y$ τέτοια ώστε $\Gamma \vdash \forall y \psi_y^x$ και $\forall y \psi_y^x \vdash \forall x \psi$
        \end{itemize}
      \item άρνησης ενός τύπου της μορφής
        \begin{itemize}
          \item $\neg(\psi \rightarrow \theta)$, τότε αρκεί ν.δ.ο. $\Gamma \vdash \psi$ και $\Gamma \vdash \neg\theta$
          \item $\neg\neg\psi$, τότε αρκεί ν.δ.ο. $\Gamma \vdash \psi$
          \item $\neg\forall x \; \psi$, τότε αρκεί ν.δ.ο. $\Gamma \vdash \neg\psi_t^x$ όπου $t$ όρος.
            \begin{itemize}
              \item Όχι πάντα δυνατό, πχ. $\Gamma = \emptyset, \psi = \neg(Px \rightarrow \forall y Py)$.
          \item (Στο παραπάνω έχουμε $\neg\forall x \; \psi = \exists x (Px \rightarrow \forall y Py)$).
            \end{itemize}
        \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Παράδειγμα 1}
  \begin{block}{}
    Αν η $x$ δεν εμφανίζεται ελεύθερη στον $\alpha$ τότε
    \[
      \vdash (\alpha \rightarrow \forall x \beta) \leftrightarrow \forall x (\alpha \rightarrow \beta)
    \]
    Για να το αποδείξω αρκεί ν.δ.ο. (από κανόνα $T$)
    \[
      \vdash (\alpha \rightarrow \forall x \beta) \rightarrow \forall x (\alpha \rightarrow \beta)
    \]
    και
    \[
      \vdash \forall x (\alpha \rightarrow \beta) \rightarrow (\alpha \rightarrow \forall x \beta)
    \]
  \end{block}
\end{frame}

\begin{frame}{Παράδειγμα 1}
  \begin{block}{}
    \[
      \vdash (\alpha \rightarrow \forall x \beta) \rightarrow \forall x (\alpha \rightarrow \beta)
    \]
    Για την πρώτη περίπτωση, αρκεί ν.δ.ο.
    \begin{itemize}
      \item $\{\alpha \rightarrow \forall x \beta\} \vdash \forall x (\alpha \rightarrow \beta)$ (Μεταθεώρημα Συναγωγής)
      \item $\{\alpha \rightarrow \forall x \beta\} \vdash (\alpha \rightarrow \beta)$ (Μεταθεώρημα Γενίκευσης)
      \item $\{\alpha \rightarrow \forall x \beta, \alpha\} \vdash \beta$ (Μεταθεώρημα Συναγωγής)
    \end{itemize}
    Το οποίο ισχύει αφού $\{\alpha \rightarrow \forall x \beta, \alpha\} \vdash \forall x \beta$ (MP)\\
    και επίσης $(\forall x \beta \rightarrow \beta)$ είναι αξίωμα.
  \end{block}
\end{frame}

\begin{frame}{Παράδειγμα 1}
  \begin{block}{}
    \[
      \vdash \forall x (\alpha \rightarrow \beta) \rightarrow (\alpha \rightarrow \forall x \beta)
    \]
    Για τη δεύτερη περίπτωση, αρκεί ν.δ.ο.
    \begin{itemize}
      \item $\{\forall x (\alpha \rightarrow \beta)\} \vdash (\alpha \rightarrow \forall x \beta)$ (Μεταθεώρημα Συναγωγής)
      \item $\{\forall x (\alpha \rightarrow \beta), \alpha\} \vdash \forall x \beta$ (Μεταθεώρημα Συναγωγής)
      \item $\{\forall x (\alpha \rightarrow \beta), \alpha\} \vdash \beta$ (Μεταθεώρημα Γενίκευσης)
    \end{itemize}
    το οποίο ισχύει αφού $\forall x (\alpha \rightarrow \beta) \rightarrow (\alpha \rightarrow \beta)$ λογικό αξίωμα και άρα
    \[
      \{\forall x (\alpha \rightarrow \beta), \alpha\} \vdash (\alpha \rightarrow \beta)
    \]
    και με άλλο ένα Modus Ponens παίρνουμε το ζητούμενο.
  \end{block}
\end{frame}

\begin{frame}{Συντομογραφίες (συμβολισμός)}
  \begin{block}{}
    Οι τύποι θα τοποθετούνται σε μια αριθμημένη λίστα, ο καθένας με μια αιτιολογήση ως προς το πώς προέκυψε
    \begin{itemize}
      \item Αξ 1: Λογικό Αξίωμα 1
      \item $1,2$·$T$: κανόνας $T$ στους τύπους των γραμμών $1,2$
      \item $1,2$·MP: Μodus Ponens στους τύπους των γραμμών $1,2$
      \item $1$·γεν: Μεταθεώρημα Γενίκευσης στον τύπο της γραμμής $1$
      \item $1$·γεν$^2$: Μεταθεώρημα Γενίκευσης 2 φορές στον τύπο της γραμμής $1$
      \item $1$·συναγ: Μεταθεώρημα Συναγωγής στον τύπο της γραμμής $1$
      \item $1$·ΑΣΑ: Μεταθεώρημα Απαγωγής Σε Άτοπο στον τύπο της γραμμής $1$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Παράδειγμα 2}
  \begin{block}{}
  Δείξτε ότι
    \[
      \forall x \forall y (x = y \rightarrow y = x)
    \]
  \end{block}
  \begin{block}{Απόδειξη}
    \begin{itemize}
      \item[1.] $\vdash x = y \rightarrow x = x \rightarrow y = x$, Αξ 6
      \item[2.] $\vdash x = x$, Αξ 5
      \item[3.] $\vdash x = y \rightarrow y = x$, $1,2;T$
      \item[4.] $\vdash \forall x \forall y (x = y \rightarrow y = x)$, $3;$γεν$^2$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Παράδειγμα 3}
  \begin{block}{}
  Δείξτε ότι
    \[
      \vdash x = y \rightarrow \forall z \; Pxz \rightarrow \forall z \; Pyz
    \]
  \end{block}
  \begin{block}{Απόδειξη}
    \begin{itemize}
      \item[1.] $\vdash x = y \rightarrow (Pxz \rightarrow Pyz)$, Αξ 6
      \item[2.] $\vdash \forall z \; Pxz \rightarrow Pxz$, Αξ 2
      \item[3.] $\vdash x = y \rightarrow (\forall z \; Pxz \rightarrow Pyz)$, $1,2;T$
      \item[4.] $\{x = y, \forall z \; Pxz\} \vdash Pyz$, $3$·MP$^2$
      \item[5.] $\{x = y, \forall z \; Pxz\} \vdash \forall z Pyz$, $4$·γεν$^2$
      \item[6.] $\vdash x = y \rightarrow \forall z \; Pxz \rightarrow \forall z \; Pyz$, $5$·συναγ$^2$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Παράδειγμα 4}
  \begin{block}{}
  Έστω $f$ μια διμελής συνάρτηση. Τότε
    \[
      \vdash \forall x_1 \forall x_2 \forall y_1 \forall y_2 (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)
    \]
  \end{block}
  \begin{block}{Απόδειξη}
    \begin{itemize}
      \item[1.] $\vdash x_1 = y_1 \rightarrow fx_1x_2 = fx_1x_2 \rightarrow fx_1x_2 = fy_1x_2$, Αξ 6
      \item[2.] $\vdash x_2 = y_2 \rightarrow fx_1x_2 = fy_1x_2 \rightarrow fx_1x_2 = fy_1y_2$, Αξ 6
      \item[3.] $\vdash fx_1x_2 = fx_1x_2$, Αξ 5
      \item[4.] $\vdash (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)$, $1,2,3$·$T$
      \item[5.] $\vdash \forall x_1 \forall x_2 \forall y_1 \forall y_2 (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)$, $1,2,3$·γεν$^4$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Μεταθεώρημα Γενίκευσης Σταθερών}
  \begin{block}{}
    Έστω $\Gamma \vdash \phi$ και $c$ μια σταθερά που δεν εμφανίζεται στο $\Gamma$. Τότε υπάρχει μεταβλητή $y$ που δεν εμφανίζεται στον $\phi$ τέτοια ώστε $\Gamma \vdash \forall y \; \phi_y^c$.\\
    Επιπλέον, υπάρχει τυπική απόδειξη του $\forall y \; \phi_y^c$ από το $\Gamma$ στην οποία η $c$ δεν εμφανίζεται.
  \end{block}
  \begin{block}{Απόδειξη}
    Έστω $\langle \alpha_0, \ldots, \alpha_n \rangle$ τυπική απόδειξη του $\phi$ από το $\Gamma$. (άρα $\alpha_n= \phi$)\\
    Έστω $y$ μεταβλητή που δεν εμφανίζεται σε κανένα από τα $\alpha_i$.\\
    Ισχυριζόμαστε ότι η
    \begin{equation}
      \label{q-def}
      \langle(\alpha_0)_y^c, \ldots, (\alpha_n)_y^c \rangle
    \end{equation}
    είναι τυπική απόδειξη της $\phi_y^c$ στο $\Gamma$
  \end{block}
\end{frame}

\begin{frame}{Μεταθεώρημα Γενίκευσης Σταθερών}
  \begin{block}{Απόδειξη (συν.)}
  Θα χρησιμοιήσουμε επαγωγή
  \begin{itemize}
    \item Περίπτωση 1: $\alpha_k \in \Gamma$. Τότε $(\alpha_k)_y^c = \alpha_k$
    \item Περίπτωση 2: $\alpha_k$ Λογικό Αξίωμα. Τότε και $(\alpha_k)_y^c$ Λογικό Αξίωμα
    \item Περίπτωση 3: $\alpha_k$ είναι από MP στις $\alpha_i$ και $\alpha_j$, για $i,j \leq k$\\
      και όπου $\alpha_j = (\alpha_i \rightarrow \alpha_k)$.\\
      Βλέπουμε ότι $(\alpha_j)_y^c = (\alpha_i \rightarrow \alpha_k)_y^c = ((\alpha_i)_y^c \rightarrow (\alpha_k)_y^c)$.\\
      Η $(\alpha_k)_y^c$ προκύπτει από MP στις $(\alpha_i)_y^c$ και $(\alpha_j)_y^c$.
  \end{itemize}
  Άρα η \eqref{q-def} είναι τυπική απόδειξη της $\phi_y^c$.
  \end{block}
\end{frame}

\begin{frame}{Μεταθεώρημα Γενίκευσης Σταθερών}
  \begin{block}{Απόδειξη (συν.)}
  \end{block}
  \begin{block}{}
    Έστω $\Phi$ το (πεπερασμένο) υποσύνολο του $\Gamma$ το οποίο χρησιμοποιήθηκε στην \eqref{q-def}. Τότε η \eqref{q-def} είναι τυπική απόδειξη της $\phi_y^c$ από το $\Phi$ στο οποίο η $y$ δεν εμφανίζεται. Από το Μεταθεώρημα Γενίκευσης παίρνουμε $\Phi \vdash \forall y \; \phi_y^c$.
  \end{block}
  \begin{block}{}
  Επιπλέον, υπάρχει τυπική απόδειξη της $\forall y \; \phi_y^c$ από το $\Phi$ όπου η $c$ δεν εμφανίζεται, διότι στην απόδειξη του Μεταθεωρήματος Γενίκευσης δεν εισάγαμε κάποιο νέο σύμβολο.
  \end{block}
\end{frame}

\begin{frame}{Πόρισμα 1}
  \begin{block}{}
    Έστω $\Gamma \vdash \phi_c^x$ όπου η $c$ δεν εμφανίζεται στο $\Gamma$ ή στον $\phi$.\\
    Τότε $\Gamma \vdash \forall x \; \phi$ και υπάρχει τυπική απόδειξη από το $\Gamma$ όπου η $c$ δεν εμφανίζεται.
  \end{block}
  \begin{block}{Απόδειξη}
    Εφόσον $\Gamma \vdash \phi_c^x$, από το Μεταθεώρημα Γενίκευσης Σταθερών παίρνουμε $\Gamma \vdash \forall y \; (\phi_c^x)_y^c$. Αλλά αφού η $c$ δεν εμφανίζεται στον $\phi$ τότε
    \[
      (\phi_c^x)_y^c = \phi_y^x
    \]
    Άρα αρκεί ν.δ.ο. $\forall y \; \phi_y^x \vdash \forall x \; \phi$.\\
    Από το Λογικό Αξίωμα 3 παίρνουμε $\forall y \; \phi_y^x \rightarrow (\phi_y^x)_x^y$.\\
    Όμως $(\phi_y^x)_x^y = \phi$ και άρα παίρνουμε το ζητούμενο.
  \end{block}
\end{frame}

\begin{frame}{Πόρισμα 2 (Κανόνας EI)}
  \begin{block}{}
    Έστω σταθερά $c$ που δεν εμφανίζεται στους $\phi, \psi$ ή στο $\Gamma$ και ότι $\Gamma ; \phi_c^x \vdash \psi$.\\
    Τότε $\Gamma ; \exists x \; \phi \vdash \psi$ και υπάρχει τυπική απόδειξη της $\psi$ από το $\Gamma$ όπου η $c$ δεν εμφανίζεται.
  \end{block}
  \begin{block}{Απόδειξη}
    Από το Μεταθεώρημα Αντιθετοαναστροφής παίρνουμε $\Gamma ; \neg\psi \vdash \neg\phi_c^x$.\\
    Από το Πόρισμα 1 παίρνουμε $\Gamma ; \neg\psi \vdash \forall x \; \neg\phi$\\
    Από το Μεταθεώρημα Αντιθετοαναστροφής παίρνουμε $\Gamma ; \neg(\forall x \; \neg\phi) \vdash \psi$ από το οποίο και καταλήγουμε στο $\Gamma ; \exists x \; \phi \vdash \psi$.
  \end{block}
\end{frame}

\begin{frame}{Παράδειγμα 5}
  \begin{block}{}
    Δείξτε ότι
    \[
      \vdash \exists x \forall y \; \phi \rightarrow \forall y \exists x \; \phi
    \]
  \end{block}
  \begin{block}{Απόδειξη}
    Αρκεί ν.δ.ο.
    \begin{itemize}
      \item $\exists x \forall y \; \phi \vdash \forall y \exists x \; \phi$ (Μεταθεώρημα Συναγωγής)
      \item $\forall y \; \phi_c^x \vdash \forall y \exists x \; \phi$ (Κανόνας EI)
      \item $\forall y \; \phi_c^x \vdash \exists x \; \phi$ (Μεταθεώρημα Γενίκευσης)
      \item $\phi_c^x \vdash \exists x \; \phi$ (εφόσον $\forall y \; \phi_c^x \vdash \phi_c^x$)
      \item $\forall x \; \neg\phi \vdash \neg\phi_c^x$ (Μεταθεώρημα Αντιθετοαναστροφής)
    \end{itemize}
    το οποίο και προκύπτει από Modus Ponens στον $(\forall x \; \neg\phi \rightarrow (\neg\phi)_c^x)$\\
    (Λογικό Αξίωμα 2).
  \end{block}
\end{frame}

\section{Αλφαβητικές Παραλλαγές}

\begin{frame}{Μεταθεώρημα Ύπαρξης Αλφαβητικών Παραλλαγών}
  \begin{block}{}
    Έστω τύπος $\phi$, όρος $t$ και μεταβλητή $x$.\\
    Τότε μπορούμε να βρούμε έναν τύπο $\phi^\prime$ που διαφέρει από τον $\phi$ μόνο στην επιλογή των ποσοδεικτών, τέτοιο ώστε
    \begin{itemize}
      \item[(a)] $\phi \vdash \phi^\prime$ και $\phi^\prime \vdash \phi$
      \item[(b)] $t$ είναι αντικαταστάσιμος στον $\phi^\prime$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Μεταθεώρημα Ύπαρξης Αλφαβητικών Variants}
  \begin{block}{Απόδειξη}
  %\end{block}
  %\begin{block}{}
    Σταθεροποιούμε τα $t,x$ και κατασκευάζουμε τον $\phi^\prime$ αναδρομικά:
    \begin{itemize}
      \item Αν $\phi$ ατομικός τύπος, τότε $\phi^\prime = \phi$
      \item $(\neg\phi)^\prime = (\neg\phi^\prime)$
      \item $(\phi \rightarrow \psi)^\prime = (\phi^\prime \rightarrow \psi^\prime)$
    \end{itemize}
    Για την περίπτωση $(\forall y \; \phi)^\prime$ επιλέγουμε μεταβλητή $z$ που δεν εμφανίζεται στα $\phi^\prime, t, x$. Ορίζουμε $(\forall y \; \phi)^\prime = \forall z (\phi^\prime)_z^y$.\\
    Από επαγωγική υπόθεση έχουμε ότι $t$ αντικαταστάσιμος για τη $x$ στον $\phi^\prime$ και αφού $x \neq z$ τότε $t$ αντικαταστάσιμος για τη $x$ στον $(\phi^\prime)_z^y$. Άρα το (b) ισχύει.
  \end{block}
  \begin{block}{}
    Μένει ν.δ.ο. ισχύει και το (a) για την περίπτωση $(\forall y \; \phi)^\prime$, δηλαδή\\
    $\forall y \; \phi \vdash \forall z (\phi^\prime)_z^y$ και $\forall z (\phi^\prime)_z^y \vdash \forall y \; \phi$.
  \end{block}
\end{frame}

\begin{frame}{Μεταθεώρημα Ύπαρξης Αλφαβητικών Variants}
  \begin{block}{Απόδειξη (συν.)}
    Για το πρώτο έχουμε
    \begin{itemize}
      \item[1.] $\phi \vdash \phi^\prime$ από επαγωγική υπόθεση και άρα $\forall y \; \phi \vdash \forall y \; \phi^\prime$
      \item[2.] $\forall y \; \phi^\prime \vdash (\phi^\prime)_z^y$ από Αξ 2 αφού η $z$ δεν εμφανίζεται στον $\phi^\prime$
      \item[3.] $\forall y \; \phi^\prime \vdash \forall z (\phi^\prime)_z^y$ από το Μεταθεώρημα Γενίκευσης στον $2$
      \item[4.] $\forall y \; \phi \vdash \forall z (\phi^\prime)_z^y$ από $1,3$
    \end{itemize}
    Για το δεύτερο έχουμε
    \begin{itemize}
      \item[1.] $\forall z (\phi^\prime)_z^y \vdash ((\phi^\prime)_z^y)_y^z$ από Αξ 2 ενώ επίσης $((\phi^\prime)_z^y)_y^z = \phi^\prime$
      \item[2.] $\phi^\prime \vdash \phi$ από επαγωγική υπόθεση
      \item[3.] $\forall z (\phi^\prime)_z^y \vdash \phi$ από $1,2$
      \item[4.] $\forall z (\phi^\prime)_z^y \vdash \forall y \; \phi$ από Μεταθεώρημα Γενίκευσης στον $3$
    \end{itemize}
  \end{block}
\end{frame}

\section{Ισότητα}

\begin{frame}{Ισότητα}
  \begin{block}{}
    Εδώ κάποιες ισότητες που θα χρειαστούμε αργότερα:
    \begin{itemize}
      \item Eq1: $\vdash \forall x \; x = x$
      \item Eq2: $\vdash \forall x \forall y (x = y \rightarrow y = x)$
      \item Eq3: $\vdash \forall x \forall y \forall z (x = y \rightarrow y = z \rightarrow x = z)$
      \item Eq4: $\vdash \forall x_1 \forall x_2 \forall y_1 \forall y_2 (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow Px_1x_2 = Py_1y_2)$
        \begin{itemize}
          \item $P$ διμελές κατηγορηματικό σύμβολο
          \item ομοίως για $n$-μελή κατηγορηματικά σύμβολα
        \end{itemize}
      \item Eq5: $\vdash \forall x_1 \forall x_2 \forall y_1 \forall y_2 (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)$
        \begin{itemize}
          \item $f$ διμελής συνάρτηση
          \item ομοίως για $n$-μελείς συναρτήσεις
        \end{itemize}
    \end{itemize}
  \end{block}
\end{frame}

\end{document}

### 2020-11-09 logic/presentation_2-4_2020-11-06.tex
Logic: Presentation: Removed slides not presented in class, added missing proof and made latex improvements

@@
 
-\begin{frame}{Μεταθεώρημα εις άτοπον απαγωγής}
+\begin{frame}{Μεταθεώρημα Απαγωγής σε άτοπο}
   \begin{block}{Ορισμός}
@@
 
-  \begin{block}{Μεταθεώρημα εις άτοπον απαγωγής}
+  \begin{block}{Μεταθεώρημα Απαγωγής σε άτοπο}
     Αν $\Gamma ; \phi$ είναι αντιφατικό τότε $\Gamma \vdash \neg\phi$.
@@
       \item[] από το Μεταθεώρημα Γενίκευσης, αρκεί ν.δ.ο. $\forall x \neg\phi \vdash \neg\forall y \phi$
-      \item[] από το Μεταθεώρημα της εις άτοπον απαγωγής, αρκεί ν.δ.ο. το $\{\forall x \neg\phi, \forall y \phi\}$ είναι αντιφατικό
+      \item[] από το Μεταθεώρημα Απαγωγής σε άτοπο, αρκεί ν.δ.ο. το $\{\forall x \neg\phi, \forall y \phi\}$ είναι αντιφατικό
       \begin{itemize}
@@
             \begin{itemize}
-              \item Όχι πάντα δυνατό, πχ. $\Gamma = \emptyset, \psi = \neg(Px \rightarrow \forall y Py)$.
-          \item (Στο παραπάνω έχουμε $\neg\forall x \; \psi = \exists x (Px \rightarrow \forall y Py)$).
+              \item Όχι πάντα δυνατό, πχ. $\Gamma = \emptyset, \psi = \neg(Px \rightarrow \forall y Py)$.\\
+              (Άρα $\phi = \neg\forall x \; \psi = \exists x (Px \rightarrow \forall y Py)$)
             \end{itemize}
@@
     \end{itemize}
+  \end{block}
+\end{frame}
+
+\begin{frame}{Αντιπαράδειγμα $\neg\forall x \; \psi$ (Drinker's principle)}
+  \begin{block}{}
+  Δείξτε ότι
+  \[
+    \vdash \exists x (Px \rightarrow \forall y Py)
+  \]
+  \end{block}
+  \begin{block}{Απόδειξη}
+    \begin{enumerate}
+      \item $\forall x Px \vdash \exists x (Px \rightarrow \forall y Py)$, $T$ αφού $\forall x Px \models^{\textrm{T}\Sigma} \exists x (Px \rightarrow \forall y Py)$
+      \item $\neg\forall x Px \vdash \exists x (Px \rightarrow \forall y Py)$, $T$ αφού $\neg\forall x Px \models^{\textrm{T}\Sigma} \exists x (Px \rightarrow \forall y Py)$
+      \item $\neg\exists x (Px \rightarrow \forall y Py) \vdash \neg\forall x Px$ (Μεταθεώρημα Αντ. στο $1$)
+      \item $\neg\exists x (Px \rightarrow \forall y Py) \vdash \forall x Px$ (Μεταθεώρημα Αντ. στο $2$)
+    \end{enumerate}
+    Άρα $\{\neg\exists x (Px \rightarrow \forall y Py)\}$ αντιφατικό λόγω $3,4$ και από το Μεταθεώρημα της Απαγωγής σε άτοπο παίρνουμε το ζητούμενο.
   \end{block}
@@
   \begin{block}{Απόδειξη}
-    \begin{itemize}
-      \item[1.] $\vdash x = y \rightarrow x = x \rightarrow y = x$, Αξ 6
-      \item[2.] $\vdash x = x$, Αξ 5
-      \item[3.] $\vdash x = y \rightarrow y = x$, $1,2;T$
-      \item[4.] $\vdash \forall x \forall y (x = y \rightarrow y = x)$, $3;$γεν$^2$
-    \end{itemize}
+    \begin{enumerate}
+      \item $\vdash x = y \rightarrow x = x \rightarrow y = x$, Αξ 6
+      \item $\vdash x = x$, Αξ 5
+      \item $\vdash x = y \rightarrow y = x$, $1,2;T$
+      \item $\vdash \forall x \forall y (x = y \rightarrow y = x)$, $3;$γεν$^2$
+    \end{enumerate}
   \end{block}
@@
   \begin{block}{Απόδειξη}
-    \begin{itemize}
-      \item[1.] $\vdash x = y \rightarrow (Pxz \rightarrow Pyz)$, Αξ 6
-      \item[2.] $\vdash \forall z \; Pxz \rightarrow Pxz$, Αξ 2
-      \item[3.] $\vdash x = y \rightarrow (\forall z \; Pxz \rightarrow Pyz)$, $1,2;T$
-      \item[4.] $\{x = y, \forall z \; Pxz\} \vdash Pyz$, $3$·MP$^2$
-      \item[5.] $\{x = y, \forall z \; Pxz\} \vdash \forall z Pyz$, $4$·γεν$^2$
-      \item[6.] $\vdash x = y \rightarrow \forall z \; Pxz \rightarrow \forall z \; Pyz$, $5$·συναγ$^2$
-    \end{itemize}
+    \begin{enumerate}
+      \item $\vdash x = y \rightarrow (Pxz \rightarrow Pyz)$, Αξ 6
+      \item $\vdash \forall z \; Pxz \rightarrow Pxz$, Αξ 2
+      \item $\vdash x = y \rightarrow (\forall z \; Pxz \rightarrow Pyz)$, $1,2;T$
+      \item $\{x = y, \forall z \; Pxz\} \vdash Pyz$, $3$·MP$^2$
+      \item $\{x = y, \forall z \; Pxz\} \vdash \forall z Pyz$, $4$·γεν$^2$
+      \item $\vdash x = y \rightarrow \forall z \; Pxz \rightarrow \forall z \; Pyz$, $5$·συναγ$^2$
+    \end{enumerate}
   \end{block}
@@
   \begin{block}{Απόδειξη}
-    \begin{itemize}
-      \item[1.] $\vdash x_1 = y_1 \rightarrow fx_1x_2 = fx_1x_2 \rightarrow fx_1x_2 = fy_1x_2$, Αξ 6
-      \item[2.] $\vdash x_2 = y_2 \rightarrow fx_1x_2 = fy_1x_2 \rightarrow fx_1x_2 = fy_1y_2$, Αξ 6
-      \item[3.] $\vdash fx_1x_2 = fx_1x_2$, Αξ 5
-      \item[4.] $\vdash (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)$, $1,2,3$·$T$
-      \item[5.] $\vdash \forall x_1 \forall x_2 \forall y_1 \forall y_2 (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)$, $1,2,3$·γεν$^4$
-    \end{itemize}
+    \begin{enumerate}
+      \item $\vdash x_1 = y_1 \rightarrow fx_1x_2 = fx_1x_2 \rightarrow fx_1x_2 = fy_1x_2$, Αξ 6
+      \item $\vdash x_2 = y_2 \rightarrow fx_1x_2 = fy_1x_2 \rightarrow fx_1x_2 = fy_1y_2$, Αξ 6
+      \item $\vdash fx_1x_2 = fx_1x_2$, Αξ 5
+      \item $\vdash (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)$, $1,2,3$·$T$
+      \item $\vdash \forall x_1 \forall x_2 \forall y_1 \forall y_2 (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)$, $1,2,3$·γεν$^4$
+    \end{enumerate}
   \end{block}
@@
 
-\section{Αλφαβητικές Παραλλαγές}
-
-\begin{frame}{Μεταθεώρημα Ύπαρξης Αλφαβητικών Παραλλαγών}
-  \begin{block}{}
-    Έστω τύπος $\phi$, όρος $t$ και μεταβλητή $x$.\\
-    Τότε μπορούμε να βρούμε έναν τύπο $\phi^\prime$ που διαφέρει από τον $\phi$ μόνο στην επιλογή των ποσοδεικτών, τέτοιο ώστε
-    \begin{itemize}
-      \item[(a)] $\phi \vdash \phi^\prime$ και $\phi^\prime \vdash \phi$
-      \item[(b)] $t$ είναι αντικαταστάσιμος στον $\phi^\prime$
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\begin{frame}{Μεταθεώρημα Ύπαρξης Αλφαβητικών Variants}
-  \begin{block}{Απόδειξη}
-  %\end{block}
-  %\begin{block}{}
-    Σταθεροποιούμε τα $t,x$ και κατασκευάζουμε τον $\phi^\prime$ αναδρομικά:
-    \begin{itemize}
-      \item Αν $\phi$ ατομικός τύπος, τότε $\phi^\prime = \phi$
-      \item $(\neg\phi)^\prime = (\neg\phi^\prime)$
-      \item $(\phi \rightarrow \psi)^\prime = (\phi^\prime \rightarrow \psi^\prime)$
-    \end{itemize}
-    Για την περίπτωση $(\forall y \; \phi)^\prime$ επιλέγουμε μεταβλητή $z$ που δεν εμφανίζεται στα $\phi^\prime, t, x$. Ορίζουμε $(\forall y \; \phi)^\prime = \forall z (\phi^\prime)_z^y$.\\
-    Από επαγωγική υπόθεση έχουμε ότι $t$ αντικαταστάσιμος για τη $x$ στον $\phi^\prime$ και αφού $x \neq z$ τότε $t$ αντικαταστάσιμος για τη $x$ στον $(\phi^\prime)_z^y$. Άρα το (b) ισχύει.
-  \end{block}
-  \begin{block}{}
-    Μένει ν.δ.ο. ισχύει και το (a) για την περίπτωση $(\forall y \; \phi)^\prime$, δηλαδή\\
-    $\forall y \; \phi \vdash \forall z (\phi^\prime)_z^y$ και $\forall z (\phi^\prime)_z^y \vdash \forall y \; \phi$.
-  \end{block}
-\end{frame}
-
-\begin{frame}{Μεταθεώρημα Ύπαρξης Αλφαβητικών Variants}
-  \begin{block}{Απόδειξη (συν.)}
-    Για το πρώτο έχουμε
-    \begin{itemize}
-      \item[1.] $\phi \vdash \phi^\prime$ από επαγωγική υπόθεση και άρα $\forall y \; \phi \vdash \forall y \; \phi^\prime$
-      \item[2.] $\forall y \; \phi^\prime \vdash (\phi^\prime)_z^y$ από Αξ 2 αφού η $z$ δεν εμφανίζεται στον $\phi^\prime$
-      \item[3.] $\forall y \; \phi^\prime \vdash \forall z (\phi^\prime)_z^y$ από το Μεταθεώρημα Γενίκευσης στον $2$
-      \item[4.] $\forall y \; \phi \vdash \forall z (\phi^\prime)_z^y$ από $1,3$
-    \end{itemize}
-    Για το δεύτερο έχουμε
-    \begin{itemize}
-      \item[1.] $\forall z (\phi^\prime)_z^y \vdash ((\phi^\prime)_z^y)_y^z$ από Αξ 2 ενώ επίσης $((\phi^\prime)_z^y)_y^z = \phi^\prime$
-      \item[2.] $\phi^\prime \vdash \phi$ από επαγωγική υπόθεση
-      \item[3.] $\forall z (\phi^\prime)_z^y \vdash \phi$ από $1,2$
-      \item[4.] $\forall z (\phi^\prime)_z^y \vdash \forall y \; \phi$ από Μεταθεώρημα Γενίκευσης στον $3$
-    \end{itemize}
-  \end{block}
-\end{frame}
-
-\section{Ισότητα}
-
-\begin{frame}{Ισότητα}
-  \begin{block}{}
-    Εδώ κάποιες ισότητες που θα χρειαστούμε αργότερα:
-    \begin{itemize}
-      \item Eq1: $\vdash \forall x \; x = x$
-      \item Eq2: $\vdash \forall x \forall y (x = y \rightarrow y = x)$
-      \item Eq3: $\vdash \forall x \forall y \forall z (x = y \rightarrow y = z \rightarrow x = z)$
-      \item Eq4: $\vdash \forall x_1 \forall x_2 \forall y_1 \forall y_2 (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow Px_1x_2 = Py_1y_2)$
-        \begin{itemize}
-          \item $P$ διμελές κατηγορηματικό σύμβολο
-          \item ομοίως για $n$-μελή κατηγορηματικά σύμβολα
-        \end{itemize}
-      \item Eq5: $\vdash \forall x_1 \forall x_2 \forall y_1 \forall y_2 (x_1 = y_1 \rightarrow x_2 = y_2 \rightarrow fx_1x_2 = fy_1y_2)$
-        \begin{itemize}
-          \item $f$ διμελής συνάρτηση
-          \item ομοίως για $n$-μελείς συναρτήσεις
-        \end{itemize}
-    \end{itemize}
-  \end{block}
-\end{frame}
-
 \end{document}

### 2020-11-13 logic/presentation_2-4_2020-11-06.tex
Logic: Presentation: Included missing proof and added slides for the 12/11/2020 lecture

@@
 \newcommand{\link}[2]{\href{#1}{\textcolor{blue}{\underline{#2}}}}
+\usepackage{soul}
 
@@
 
-\begin{frame}{Αντιπαράδειγμα $\neg\forall x \; \psi$ (Drinker's principle)}
+\begin{frame}{Αντιπαράδειγμα $\neg\forall x \psi$ (Drinker's principle)}
   \begin{block}{}
@@
   \end{block}
-  \begin{block}{Απόδειξη}
+  \begin{block}{Απόδειξη (ελλειπής)}
     \begin{enumerate}
-      \item $\forall x Px \vdash \exists x (Px \rightarrow \forall y Py)$, $T$ αφού $\forall x Px \models^{\textrm{T}\Sigma} \exists x (Px \rightarrow \forall y Py)$
-      \item $\neg\forall x Px \vdash \exists x (Px \rightarrow \forall y Py)$, $T$ αφού $\neg\forall x Px \models^{\textrm{T}\Sigma} \exists x (Px \rightarrow \forall y Py)$
+      \item $\forall x Px \vdash \exists x (Px \rightarrow \forall y Py)$, \st{$T$ αφού $\forall x Px \models^{\textrm{T}\Sigma} \exists x (Px \rightarrow \forall y Py)$}
+      \item $\neg\forall x Px \vdash \exists x (Px \rightarrow \forall y Py)$, \st{$T$ αφού $\neg\forall x Px \models^{\textrm{T}\Sigma} \exists x (Px \rightarrow \forall y Py)$}
       \item $\neg\exists x (Px \rightarrow \forall y Py) \vdash \neg\forall x Px$ (Μεταθεώρημα Αντ. στο $1$)
@@
     Άρα $\{\neg\exists x (Px \rightarrow \forall y Py)\}$ αντιφατικό λόγω $3,4$ και από το Μεταθεώρημα της Απαγωγής σε άτοπο παίρνουμε το ζητούμενο.
+  \end{block}
+\end{frame}
+
+\begin{frame}{Αντιπαράδειγμα $\neg\forall x \psi$ (Drinker's principle)}
+  Τώρα θα δείξουμε ότι για κάθε όρο $t$
+  \[
+    \nvdash (Px \rightarrow \forall y Py)^x_t
+  \]
+  \begin{block}{Απόδειξη (μη φορμαλιστική)}
+    Έστω για έναν τυχαίο όρο $t$ ότι $\vdash (Px \rightarrow \forall y Py)_t^x$.
+Βλέπουμε ότι μπορούμε να θεωρήσουμε μια αυθαίρετη δομή $\mathfrak{A}$ (πχ.
+όπου $\neg Pt$ για κάθε $t$) στην οποία και θα έχουμε $\not\models_\mathfrak{A} (Px \rightarrow \forall y Py)_t^x$.\\
+    Άρα έχουμε ότι $\not\models (Px \rightarrow \forall y Py)_t^x$ και από το Μεταθεώρημα Αξιοπιστίας παίρνουμε το ζητούμενο.
   \end{block}

### 2020-12-02 geodata/project2/project2.tex
Geodata: Included project2 tex and java code written for it

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass{beamer}
\mode<presentation>
{
  \usetheme[progressbar=foot,numbering=fraction,background=light,block=fill]{metropolis} 
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
  %\setbeamertemplate{frame footer}{My custom footer}
}
\centering

% Commands for tansparent block and to correct the small line space with the title.
% \metroset{block=transparent}
% \vspace{0pt}

\usepackage{graphicx,pgfplots,tikz,tikz-3dplot}
\graphicspath{ {./figures/} }
\usepackage{hyperref,xcolor}
\newcommand{\link}[2]{\href{#1}{\textcolor{blue}{\underline{#2}}}}

% Main document
\begin{document}
\title{Road segmentation and alignment}
\subtitle{Geometric Data Analysis}
\author{Thomas Pappas\\ \link{mailto:thpappas@di.uoa.gr}{thpappas@di.uoa.gr}}
\date{November 26, 2020}
\maketitle

\begin{frame}{Agenda}
  \tableofcontents[hideallsubsections]
\end{frame}

\section{Road segmentation}

\subsection{Introduction}

\begin{frame}{Road segmentation}
  \begin{block}{What is Road segmentation?}
    Partitioning of roads into segments in order to represent and compare map information in a more meaningful and easier to analyse way\\
    (various applications e.g. traffic analysis, anomaly detection)
    \begin{itemize}
      \item A segment consists of two or more nodes
      \item Line segment is a segment consisting of two nodes
    \end{itemize}
  \end{block}

  \begin{block}{Types of road segmentation}
    \begin{itemize}
      \item Segmentation by junction
      \item Segmentation by curvature
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Road segmentation}
  \begin{block}{Highways}
    \begin{itemize}
      \item High-performance roads
        \begin{itemize}
          \item Motorway
          \item Trunk
          \item Primary
          \item Secondary
          \item Tertiary
        \end{itemize}
      \item Low-performance roads
        \begin{itemize}
          \item Residential
          \item Unclassified
          \item Service
        \end{itemize}
      \item Link roads
    \end{itemize}
  \end{block}
\end{frame}

\subsection{Segmentation by curvature}

\begin{frame}{Segmentation by curvature}
  \begin{block}{Curve radius}
    Every set of three points defines a triangle. We call curve radius the radius of the triange's circumcircle.
  \end{block}

  \begin{block}{Curvature}
    The curvature of a line segment is the mean of the curve radius of the sets its two points participate. (Figure 1)
  \end{block}

  \begin{block}{When to create a segment?}
    We keep the minumum curvature of the segment under construction. We create a new segment when we occur a line segment with a curvature with high augmentation compared to the min curvature.
  \end{block}
\end{frame}

\begin{frame}{Curvature}
  \begin{figure}[h]
    \includegraphics[width=0.8\textwidth]{line_segment_curvature}
    \caption{The curvature of the line segment $B\Gamma$ is $(r_1+r_2)/2$.}
  \end{figure}
\end{frame}

\begin{frame}{Formula for regulated segmentation}
  \metroset{block=transparent}
  \begin{block}{}
    If we define
    \begin{itemize}
      \item $P$ the set of points in the highway
      \item $H$ the set of points in the highway that have been divided to segments
      \item $\rho$ a minor positive number (e.g. $\rho = 8$)
      \item $\lambda$ the length of the under construction segment
      \item $\mu$ the mean length of all the highways of the same category
    \end{itemize}
    then when
    \[
      |P| > (|H|/(|H|/\rho + 1)) \textrm{ and } (\lambda > \mu)
    \]
    are both true, create a new segment.\\
    Note: Invented through experimental processes.
  \end{block}
\end{frame}

\begin{frame}{Segmentation by curvature}
  \begin{block}{Algorithm}
    Input: A set of points $P$\\
    Output: A set of segments (set of points from $P$)
    \begin{enumerate}
      \item If $|P| < 3$, create a single segment and exit
      \item Initialise min-curvature to $0$
      \item Iterate through the line segments
        \begin{enumerate}
          \item If first segment, initialise a segment, set min-curvature equal to the current one and continue
          \item If last segment, add the last point to the segment and finalise it
          \item If the curvature has high augmentation compared to the min-curvature, finalise the segment under construction and intiate a new one with the current line segment;\\
          set min-curvature as the current one
          \item Else add the second point to the segment, update min-curvature (if needed) and continue
        \end{enumerate}
    \end{enumerate}
  \end{block}
%  \begin{block}{Complexity}
%    $\mathcal{O}(n)$
%  \end{block}
\end{frame}

\begin{frame}{Segmentation by curvature - Example}
  Curvature segment criteria: $|currentCurve - minCurve| > minCurve$
  \begin{scriptsize}
    \begin{table}
      \caption{Segmentation by curvature, New York (Brooklyn)}
      \label{table:1}
      \begin{tabular}{ l | c c c c }
        \hline
        Highway type & \# & \#segments & \#segments (with formula) & mean length\\
        \hline
        Unclassified & $5$ & $10$ & $11$ & $108.17$\\
        Primary link & $6$ & $6$ & $6$ & $67.64$\\
        Tertiary & $45$ & $79$ & $83$ & $411.60$\\
        Motorway link & $20$ & $26$ & $27$ & $128.99$\\
        Motorway & $7$ & $15$ & $17$ & $663.07$\\
        Secondary & $275$ & $344$ & $348$ & $139.34$\\
        Residential & $756$ & $1069$ & $1109$ & $331.72$\\
        Service & $108$ & $219$ & $227$ & $146.47$\\
        Unused & $543$ & $1158$ & $1204$ & $112.82$\\
        Secondary link & $2$ & $2$ & $2$ & $27.81$\\
        Primary & $240$ & $285$ & $286$ & $110.53$
      \end{tabular}
    \end{table}
  \end{scriptsize}
\end{frame}

\section{Road alignment with Descrete Fréchet Distance}

\begin{frame}{Descrete Fréchet Distance (DFD)}
  Distance measure for matching two geometric objects in $2D$ or $3D$.
  \begin{block}{For reference}
    For two polygonal curves $P$ and $Q$ and the set of all possible travesals $T$
    \[
      d_F(P,Q) = \min_T \max_{(i_k,j_k) \in T} d(p_{i_k}, q_{j_k})
    \]
    Computed using dynamic programming.
  \end{block}
\end{frame}

\subsection{Calculating DFD with translation and rotation}

\begin{frame}{Calculating DFD with translation and rotation $2D$}
  \begin{block}{Problem}
    For  two polygonal curves $P$ and $Q$ find the minimum DFD value for all possible translations and rotations.
  \end{block}

%  \begin{block}{Solution for 2D}
%    Long story
%  \end{block}

  \begin{block}{Theorem 2\footnotemark}
    For minimizing the discrete Fréchet distance between two $2D$ polyg-onal chains under translation and rotation, we have an $\mathcal{O}(m^4n^4\log{}(1/\epsilon))$ time $1+\epsilon$ approximation algorithm and an $\mathcal{O}(m^4n^4\log{}(m+n))$ time exact algorithm.
  \end{block}
  \footnotetext[1]{Jiang M, Xu Y, Zhu B. Protein structure-structure alignment with discrete Fréchet distance. J Bioinform Comput Biol. 2008 Feb;6(1):51-64. doi: 10.1142/s0219720008003278. PMID: 18324745.}
\end{frame}

\begin{frame}{Calculating DFD with translation and rotation $2D$}
  \begin{block}{The idea behind Theorem 2}
    \begin{itemize}
      \item Runtime to check the DFD for an arbitrary translation: $\mathcal{O}(mn)$
      \item Solve the decision problem for $\epsilon > 0$
        \begin{itemize}
          \item Check transformations for every $4$ (at most) vertices
          \item i.e. hold $3$ vertices of reference, so runtime becomes $\mathcal{O}((mn)m^3n^4) = \mathcal{O}(m^4n^4)$
        \end{itemize}
      \item Either use binary search to approximate the min DFD\\
        $1+\epsilon$ approximation algorithm
      \item Or use Cole’s sorting trick\footnotemark$^,$\footnotemark\\
        $\mathcal{O}(m^4n^4\log{}(m+n))$ time exact algorithm
    \end{itemize}
    \footnotetext[2]{Alt H, Knauer C, Wenk C, Matching polygonal curves with respect to the Fréchet
distance, in Proceedings of the 18th Annual Symposium on Theoretical Aspects of
Computer Science (STACS’01), pp. 63–74, 2001.}
    \footnotetext[3]{Cole R, Slowing down sorting networks to obtain faster sorting algorithms, J ACM 34:200–208, 1987.}
  \end{block}
\end{frame}

\begin{frame}{Calculating DFD with translation and rotation $3D$}
  \begin{block}{Algorithm for $3D$}
    If we apply the same idea for $3D$ then we need $6$ vertices of reference and we therefore get an algorithm of complexity $\mathcal{O}((mn)^7)$ (ignoring the log factors) for transformations under translation and rotation.\\
    We will instead present a faster intuitive heuristic.
  \end{block}
\end{frame}

\begin{frame}{Calculating DFD with translation and rotation $3D$}
  \begin{block}{Observations}
    \begin{itemize}
      \item Given $3D$ chain $C$ of $n$ vertices, each vertex $c_i$ is a $3D$ vector $\vec{c_i}$
      \item The center $c$ is the vector $\vec{c} = \frac{\sum_i \vec{c_i}}{n}$
    \end{itemize}
    For two polygonal chains $A,B$ where\\
    $A = \langle \alpha_1,\alpha_2,\cdots,\alpha_m \rangle$ and $B = \langle b_1,b_2,\cdots,b_n \rangle$
    \begin{itemize}
      \item if $d_F(A,B) = \epsilon$ then $d(\alpha_1,b_1) \leq \epsilon$ and $d(\alpha_m,b_n) \leq \epsilon$
      \item If $\epsilon < \frac{1}{2}\min_{i < m} |\alpha_{i+1}-\alpha_i|$ or $\epsilon < \frac{1}{2}\min_{i < n} |b_{i+1}-b_i|$, then the Fréchet alignment of $A$ and $B$ must contain only $1-1$ matches, i.e $m = n$ and for $0 \leq i \leq n$ we have $d(\alpha_i,b_i) \leq \epsilon$.\\
      Therefore for $\alpha,b$ the centers of $A,B$ respectively, $d(\alpha, b) \leq \epsilon$
    \end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Calculating DFD with translation and rotation $3D$}
  \begin{block}{Heuristic for $3D$}
    From the above observations, we see we can use the three points (endvertices and center) as reference points.
    \begin{enumerate}
      \item Translate $B$ such that the centers $\alpha$ and $b$ coincide
      \item Rotate $B$ around $b$ such that $\vartriangle \alpha\alpha_1\alpha_m$ and $\vartriangle bb_1b_n$ are coplanar
        \begin{itemize}
          \item Also such that $\frac{\vec{\alpha_1}+\vec{\alpha_m}}{2}-\vec{\alpha}$ and $\frac{\vec{b_1}+\vec{b_n}}{2}-\vec{b}$ have the same direction
        \end{itemize}
      \item Randomly select two vertices from $B$. Rotate $B$ for a small angle around the axis through the two vertices; if DFD does not decrease, rotate back
      \item Repeat step $3$ (tuning) for a number of times
    \end{enumerate}
  \end{block}
\end{frame}

\begin{frame}{Examples}
  \begin{small}
    \begin{table}
      \caption{DFD comparison of two highways from each category with the highest same size. We compute the DFD under translation $d_F$ (tr), DFD under translation and rotation $\min d_F$ and the c-RMSD.}
      \label{table:2}
      \begin{tabular}{ l | c c c c c }
        Highway type & $|A|$ & $|B|$ & $d_F (tr)$ & $\min d_F$ & c-RMSD\\
        \hline
        Unclassified & $10$ & $10$ & $129.05$ & $60.61$ & $40.45$\\
        Primary link & $2$ & $2$ & $67.05$ & $54.37$ & $54.37$\\
        Tertiary & $11$ & $11$ & $210.24$ & $63.06$ & $53.77$\\
        Motorway link & $5$ & $5$ & $24.83$ & $21.28$ & $17.52$\\
        Motorway & $9$ & $9$ & $168.15$ & $90.05$ & $53.28$\\
        Secondary & $14$ & $14$ & $205.50$ & $177.13$ & $81.54$\\
        Residential & $27$ & $27$ & $887.77$ & $645.15$ & $366.53$\\
        Service & $28$ & $28$ & $171.24$ & $56.25$ & $41.71$\\
        Unused & $37$ & $37$ & $186.84$ & $133.62$ & $59.36$\\
        Secondary link & $3$ & $3$ & $23.95$ & $6.87$ & $5.90$\\
        Primary & $11$ & $11$ & $415.89$ & $199.93$ & $129.75$\\
      \end{tabular}
    \end{table}
  \end{small}
\end{frame}

\begin{frame}{Examples}
  \begin{block}{Some conclusions}
    \begin{itemize}
      \item Translation only DFD can be a lot larger than if we also allow rotation
      \item c-RMSD seems to have better results for alligning the two lines
    \end{itemize}
  \end{block}
\end{frame}

%\begin{frame}{Examples}
%  \begin{figure}
%    \begin{tikzpicture}
%    \begin{axis}
%    [   view={-45}{60},
%      xmin=0,xmax=5,
%      ymin=0,ymax=5,
%      zmin=0, zmax=5,
%    ]
%    \addplot3[
%      surf,color=red
%    ] 
%    coordinates {
%      (0,0,0) (0,1,0) (0,2,0)
%      (1,0,0) (1,1,0.6) (1,2,0.7)
%      (2,0,0) (2,1,0.7) (2,2,1.8)
%    };
%    \end{axis}
%
%    \end{tikzpicture}
%  \end{figure}
%\end{frame}

%\section{Bibliography}

\begin{frame}{Bibliography}
  \begin{itemize}
    \item Dimitrios - Nikolaos Konstantakis, Geometrical Road Segmentation and Clustering, BSc Thesis, National and Kapodistrian University of Athens, Department of Informatics and Telecommunications, 2018 April
    \item Jiang M, Xu Y, Zhu B. Protein structure-structure alignment with discrete Fréchet distance. J Bioinform Comput Biol. 2008 Feb;6(1):51-64. doi: 10.1142/s0219720008003278. PMID: 18324745.
  \end{itemize}
\end{frame}

\end{document}

### 2020-12-02 geodata/project2/Segmenation/src/osm/Main.java

@@ -1,0 +1,128 @@
+/**
+ * 
+ * This class is an adjustment of the original Main class from the BSc Thesis of Dimitrios - Nikolaos Kostantakis
+ *   Code style has followed the original one.
+ *   Custom code includes the 'bucketLookup' method plus the 'Custom code' block in the main one.
+ * 
+ * @author Thomas Pappas
+ * @see Dimitrios - Nikolaos Konstantakis, Geometrical Road Segmentation and Clustering, BSc Thesis
+ *   National and Kapodistrian University of Athens, Department of Informatics and Telecommunications, 2018 April
+ */
+package osm;
+
+import java.io.File;
+import java.io.IOException;
+import java.util.ArrayList;
+import java.util.Collections;
+import java.util.HashMap;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+
+import org.xml.sax.SAXException;
+
+import info.pavie.basicosmparser.model.Element;
+import osm.segmentation.Bucket;
+import osm.segmentation.OsmParser;
+import osm.segmentation.Segment;
+//import osm.segmentation.SegmentationSystem;
+import osm.segmentation.SegmentationSystem2;
+import osm.segmentation.clustering.Clustering2;
+import osm.segmentation.clustering.SimplePoint;
+
+public class Main {
+	/**
+	 * For a given bucket, find the two highways with the same max size.
+	 * 
+	 * @param bucket
+	 * @return
+	 *   The integer?
+	 */
+	public static List<Segment> bucketLookup(Bucket bucket) {
+		// Initialise an empty Segment list to store the max same size buckets.
+		List<Segment> bucketsMaxSameSize = new ArrayList<Segment>();
+		List<Segment> highways = bucket.getHighways();
+		List<Integer> sizes = new ArrayList<Integer>();
+		
+		// Sort the sizes (descending) and look for the max value that occurs at least twice.
+		for (Iterator<Segment> iterator = bucket.getHighways().iterator(); iterator.hasNext();) {
+			Segment highway = iterator.next();
+			sizes.add(highway.getCurve().size());
+		}
+		List<Integer> sizesOrd = new ArrayList<Integer>(sizes);
+		Collections.sort(sizesOrd, Collections.reverseOrder());
+		int maxSameSize = sizesOrd.get(0);
+		Boolean found = false;
[…]

### 2020-12-02 geodata/project2/Segmenation/src/osm/segmentation/SegmentationSystem2.java

@@ -1,0 +1,67 @@
+/**
+ * 
+ * Class extending the functionality of the SegmentationSystem class from the BSc Thesis of Dimitrios - Nikolaos Kostantakis
+ *   Code style has followed the original one.
+ *   Most methods are variations of the original ones, usually simply adjusted to different inputs.
+ * 
+ * @author Thomas Pappas
+ * @see Dimitrios - Nikolaos Konstantakis, Geometrical Road Segmentation and Clustering, BSc Thesis
+ *   National and Kapodistrian University of Athens, Department of Informatics and Telecommunications, 2018 April
+ */
+package osm.segmentation;
+
+import java.io.FileNotFoundException;
+import java.io.PrintWriter;
+import java.io.UnsupportedEncodingException;
+import java.util.Iterator;
+import java.util.List;
+import java.util.Map;
+
+import info.pavie.basicosmparser.model.Element;
+
+public class SegmentationSystem2 extends SegmentationSystem {
+
+	public SegmentationSystem2(Map<String, Element> osmResult) {
+		super(osmResult);
+	}
+
+	public void menu() {
+		super.menu();
+		
+		//Print the mean length from each bucket.
+		for (Map.Entry<String, Bucket> entry : this.getHashtable().entrySet()) {
+			Bucket bucket = entry.getValue();
+			System.out.println("Mean length: "+bucket.getMeanlength()+"\t for Bucket \""+bucket.getRoadtype()+"\"");
+		}
+	}
+
+
+	public void segmentation(Bucket bucket) {
+		for (Iterator<Segment> iterator = bucket.getHighways().iterator(); iterator.hasNext();) {
+			Segment highway = iterator.next();
+			this.segmentationByCurvature(highway);
+		}
+	}
+	
+	public void createDataset() throws FileNotFoundException, UnsupportedEncodingException {
+		PrintWriter writer = new PrintWriter("", "UTF-8");	
+		for (Map.Entry<String, Bucket> entry : this.getHashtable().entrySet()) {
+			Bucket bucket = entry.getValue();
+			
+			List<Segment> segments = bucket.getSegments();
+			Iterator<Segment> iterator = segments.iterator();
+			while(iterator.hasNext()) {
+				Segment segment = iterator.next();
+				writer.print(segment.getId()+"\t"+segment.getWay().getId()+"\t"+segment.getCurve().size()+"\t");
+				
[…]

### 2020-12-02 geodata/project2/Segmenation/src/osm/segmentation/clustering/Clustering2.java

@@ -1,0 +1,125 @@
+/**
+ * 
+ * Class extending the functionality of the Clustering class from the BSc Thesis of Dimitrios - Nikolaos Kostantakis
+ *   Code style has followed the original one.
+ *   Most methods are variations of the original ones, usually simply adjusted to different inputs.
+ * 
+ * @author Thomas Pappas
+ * @see Dimitrios - Nikolaos Konstantakis, Geometrical Road Segmentation and Clustering, BSc Thesis
+ *   National and Kapodistrian University of Athens, Department of Informatics and Telecommunications, 2018 April
+ */
+package osm.segmentation.clustering;
+
+import java.util.ArrayList;
+import java.util.Iterator;
+import java.util.List;
+
+import Jama.Matrix;
+import Jama.SingularValueDecomposition;
+import osm.segmentation.Bucket;
+import osm.segmentation.Segment;
+import osm.segmentation.curves.SegmentPoint;
+
+public class Clustering2 extends Clustering {
+
+	public Clustering2(Bucket bucket, int k) {
+		super(bucket, k);
+	}
+	
+	public double cRMSD_distance(List<SegmentPoint> curveA, List<SegmentPoint> curveB) {
+		Matrix Q, U, VTransposed;
+
+		Matrix matrixX = new Matrix(get_normalized_matrix_from_curve(curveA));
+		Matrix matrixY = new Matrix(get_normalized_matrix_from_curve(curveB));
+
+		SingularValueDecomposition svd = new SingularValueDecomposition((matrixX.transpose()).times(matrixY));
+		// singular = svd.getSingularValues(); //double[] singular;
+
+		U = svd.getU();
+		VTransposed = (svd.getV()).transpose();
+
+		Q = U.times(VTransposed);
+		if (Q.det() < 0) {
+			for (int i = 0; i < U.getRowDimension(); i++)
+				U.set(i, 2, U.get(i, 2) * (-1));
+			Q = U.times(VTransposed);
+		}
+
+		return (((matrixX.times(Q)).minus(matrixY)).normF() / Math.sqrt(matrixX.getRowDimension()));
+	}
+
+	public double[][] get_normalized_matrix_from_curve(List<SegmentPoint> curveA) {
+		double meanX = 0, meanY = 0, meanZ = 0;
+		double[][] matrix = new double[curveA.size()][3];
+
+		if (curveA.isEmpty())
+			return null;
+
[…]

### 2021-02-13 geodata/project3/project3.tex
Geodata: Included project3 tex code and figures

\documentclass{beamer}

\mode<presentation>
{
  \usetheme[compress]{Berlin}
  \usecolortheme{default}
  %\usefonttheme{serif}
  %\usepackage{fontspec}
  %\setmainfont{Liberation Serif}
  %\usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  %\usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
} 
\addtobeamertemplate{navigation symbols}{}{%
    \usebeamerfont{footline}%
    \usebeamercolor[fg]{footline}%
    \hspace{1em}%
    \insertframenumber/\inserttotalframenumber
}
\usepackage{multicol}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{parskip}
\usepackage{array}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{nccmath}
\usepackage{biblatex}
\graphicspath{ {./figures/} }
\usepackage{longtable}
\usepackage[dvipsnames]{xcolor}
\usepackage{graphicx} 
\usepackage{xmpmulti}
\usepackage{booktabs} 
\let\lemma\relax
\newtheorem{lemma}[theorem]{\gr Λήμμα}
\newtheorem{mycorollary}[theorem]{Corollary}
\newtheorem{myprop}[theorem]{Proposition}
\theoremstyle{definition}
\newcommand{\en}{\selectlanguage{english}}
\newcommand{\gr}{\selectlanguage{greek}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\STRUCT}{\text{STRUCT}}

\title[]{Graph attention networks and expressiveness}
\author[Georgiadou, Pappas]{Ilektra Styliani Georgiadou, Thomas Pappas}
\institute[ALMA]{}
\date{\today}

\begin{document}
\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

\begin{frame}[plain]
  \titlepage
  \begin{columns}
\column{0.4\textwidth}
    \begin{figure}
      \centering
      \includegraphics[scale=0.6]{alma_logo.png}
    \end{figure}
\column{0.5\textwidth}
ALMA \\
\tiny{INTER-INSTITUTIONAL GRADUATE PROGRAM \\
"ALGORITHMS, LOGIC AND DISCRETE MATHEMATICS"}
\end{columns}
\end{frame}

\begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[hideallsubsections]
\end{frame}

\section{Graph Attention Networks}

\begin{frame}{Past GNN approaches}
    Past GNN attempts include spectral and non-spectral approaches
    \begin{itemize}
        \item Spectral: Compute and depend on the Laplacian eigenvalues
            \begin{itemize}
                \item computation is demanding, though it has been improved over time
                \item dependant on the graph structure
            \end{itemize}
        \item Non-spectral: define convolutions directly on the graph
            \begin{itemize}
                \item dependent on the neighborhood size (learn for each node degree)
                \item or learn on a fixed neighborhood size (GraphSAGE)
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Graph Convolutional Neural Networks}
    \textbf{GCN} is a type of convolutional neural network that can work directly on graphs and take advantage of their structural information.\\
    \bigskip \pause
    \begin{block}{In General}
        For each node, we get the feature information from all its neighbors and itself. We will use the same function for all the nodes. Finally, we feed the result values into a neural network. We can also stack more layers on top of each other to get a deeper GCN. The output of a layer will be treated as the input for the next layer.
    \end{block} \pause
    The way GCN aggregates messages is structure-dependent, which may hurt its generalizability.
\end{frame}

\begin{frame}{Graph Attention Networks}
    GAT introduces the attention mechanism as a substitute for the statically normalized convolution operation.
    \begin{block}{Attention Strategy}
        Compute the hidden representations of each node in the graph, by attending over its neighbours, following a self-attention strategy, which will be: 
        \begin{enumerate}
            \item Efficient (parallelizable)
            \item Applied to nodes of different degrees
            \item Applicable to inductive learning problems
        \end{enumerate}
    \end{block} \pause
    Given as input a set of node features \(h=\{\vec{\rm h_{1}},\dots,\vec{\rm h_{N}}\},\;\vec{\rm h_{i}}\in \mathbb{R}^{F}\), produce a new set of node features \(h'=\{\vec{\rm h'_{1}},\dots,\vec{\rm h'_{N}}\},\;\vec{\rm h'_{i}}\in \mathbb{R}^{F'}\)
\end{frame}

\begin{frame}{Graph Attentional Layer}
    \begin{block}{Single layer Algorithm}
    \textbf{Input:} set of node features \(h=\{\vec{\rm h_{1}},\dots,\vec{\rm h_{N}}\}\), weight matrix \(W\in \mathbb{R}^{F'\times F}\) (learnable), shared attentional mechanism \(\alpha: \mathbb{R}^{F'}\times\mathbb{R}^{F'}\rightarrow \mathbb{R}\), nonlinearity function \(\sigma\)
    \begin{itemize}
        \item Compute attention coefficients for nodes \(j\in \mathcal{N}_{i}\) as \(e_{ij}=\alpha(\textbf{W}\vec{\rm h_{i}},\textbf{W}\vec{\rm h_{j}})\), the importance of node \(j\)'s features to \(i\)
            \begin{itemize}
                \item Can be done across all nodes or only within the neighborhood (masked attention)
            \end{itemize}
        \item Normalize them as \(\alpha_{ij}=softmax_{j}(e_{ij})=\frac{exp(e_{ij})}{\sum_{k\in\mathcal{N}_{i}}exp(e_{ik})}\)
        \item Compute linear combination and (potentially) apply a nonlinearity \(\sigma\), \(\vec{\rm h'_{i}}=\sigma\left(\sum_{j\in\mathcal{N}_{i}}\alpha_{ij}\textbf{W}\vec{\rm h_{j}}\right)\)
    \end{itemize}
    \end{block}

\end{frame}

\begin{frame}{Multi-head attention}
    To stabilize the learning process, we employ multi-head attention, so we execute the last step of the Algorithm for \(K\) independent attention mechanisms and their features are concatenated.\\
    \bigskip \pause
    Performing multi-head attention on the final layer, taking averages and nonlinearity function \(\sigma\), so:
    \[\vec{\rm h'_{i}}=\sigma\left(\frac{1}{K}\sum_{k=1}^{K}\sum_{j\in\mathcal{N}_{i}}\alpha_{ij}^k\textbf{W}^k\vec{\rm h_{j}}\right)\]
\end{frame}

\begin{frame}{Illustrations}
    \begin{multicols}{2}
        \begin{figure}
            \centering
            \includegraphics[scale=0.4]{GAT1.png}
            \caption{The attention mechanism \(\alpha(\textbf{W}\vec{\rm h_{i}},\textbf{W}\vec{\rm h_{j}})\) parametrized by a weight vector \(\vec{\rm a}\)}
        \end{figure}
        \begin{figure}
            \centering
            \includegraphics[scale=0.40]{GAT2.png}
            \caption{Multi-head attention where different arrow colors denote independent attention computations}
        \end{figure}
    \end{multicols}
\end{frame}

\begin{frame}{Effectiveness}
    Parallelization of computations
    \begin{itemize}
        \item Self-attentional layer // across all edges
        \item Output features // across all nodes
    \end{itemize} \pause
    \begin{block}{Time Complexity}
        Time needed in a single GAT attention head computing \(F'\) features and \(F\) input features for graph \(G(V,E)\) is:
        \begin{center}
            \(\mathcal{O}(\;|V|FF'+|E|F'\;)\)
        \end{center}
    \end{block} \pause
    Applying multi-head attention multiplies the storage and parameter requirements by a factor of \(K\). The individual heads’ computations are fully independent.
\end{frame}

\begin{frame}{Benefits}
    \begin{itemize}
        \item Allows assigning different importances to nodes of the same neighborhood
        \item Analyzing the learned attentional weights may lead to benefits in interpretability (e.g. in the machine translation domain)
        \item Applied in a shared manner to all edges in the graph, without upfront access to the global graph structure, so:
        \begin{itemize}
            \item there is no need for undirected graphs
            \item it is directly applicable to inductive learning
        \end{itemize}
        \item Works with the entirety of the neighborhood and does not assume any ordering within it
        \begin{itemize}
            \item Opposite to previous inductive methods with fixed-sized neighborhoods and the existence of a sequential node ordering across neighborhoods (GraphSAGE)
        \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Evaluation}
    In all experiments
    \begin{itemize}
        \item Masked attention has been applied on first-order neighbors
        \item The attention mechanism \(\alpha\) is a single-layer  feedforward  neural  network
            \begin{itemize}
                \item parametrized by a weight vector \(\vec{\rm{a}}\in \mathbb{R}^{2F^\prime}\)
                \item LeakyReLU nonlinearity (with negative input slope \(\alpha = 0.2\)) is applied
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Test: Transductive learning}
    \begin{block}{Dataset}
        Three standard  citation  network  benchmark  datasets were utilised: Cora, Citeseer and Pubmed. Nodes correspond to documents and edges to (undirected) citations.  Node features correspond to elements of a bag-of-words representation of a document.
    \end{block} \pause
    \begin{block}{Methods}
        Comparison is done against the approaches specified in Kipf \& Welling (2017).
        \begin{itemize}
            \item Same metrics were used
            \item Maximum performance is reported
            \item Also included GCN-64, a GCN model that computes 64 hidden features using ReLU or ELU activation
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Test: Transductive learning}
    \begin{block}{Setup}
        Two-layer GAT model
        \begin{itemize}
            \item First layer
                \begin{itemize}
                    \item \(K=8\) attention heads
                    \item \(F^\prime = 8\) features each
                    \item ELU nonlinearity
                \end{itemize}
            \item Second layer: Classification
                \begin{itemize}
                    \item Single attention head (\(8\) for Pubmed)
                    \item \(C\) features (number of classes)
                    \item Softmax activation
                \end{itemize}
        \end{itemize}
        Due to low number of training nodes (\(140, 120, 60\) respectively)\\
        \(L_2\) regularisation is applied with \(\lambda = 0.0005\) (\(0.001\) for Pubmed) and dropout \(p = 0.6\) to all inputs and attention coefficients.
    \end{block}
\end{frame}

\begin{frame}{Test Results: Transductive learning}
    \begin{tiny}
    \begin{table}
      \caption{Transductive}
      \label{table:1}
      \begin{tabular}{ l l l l }
        \hline
        Method & Cora & Citeseer & Pubmed \\
        \hline
        MLP & $55.1\%$ & $46.5\%$ & $71.4\%$ \\
        ManiReg (Belkin et al., 2006) & $59.5\%$ & $60.1\%$ & $70.7\%$ \\
        SemiEmb (Weston et al., 2012) & $59.0\%$ & $59.6\%$ & $71.7\%$ \\
        LP (Zhu et al., 2003) & $68.0\%$ & $45.3\%$ & $63.0\%$ \\
        DeepWalk (Perozzi et al., 2014) & $67.2\%$ & $43.2\%$ & $65.3\%$ \\
        ICA (Lu \& Getoor, 2003) & $75.1\%$ & $69.1\%$ & $73.9\%$ \\
        Planetoid (Yang et al., 2016) & $75.7\%$ & $64.7\%$ & $77.2\%$ \\
        Chebyshev (Defferrard et al., 2016) & $81.2\%$ & $69.8\%$ & $74.4\%$ \\
        GCN (Kipf \& Welling, 2017) & $81.5\%$ & $70.3\%$ & $79.0\%$ \\
        MoNet (Monti et al., 2016) & $81.7\pm0.5\%$ & — & $78.8\pm0.3\%$ \\
        \hline
        GCN-64 & $81.4\pm0.5\%$ & $70.9\pm0.5\%$ & $79.0\pm0.3\%$ \\
        GAT (Velickovic et al., 2018) & $83.0\pm0.7\%$ & $72.5\pm0.7\%$ & $79.0\pm0.3\%$ \\
        \hline
      \end{tabular}
    \end{table}
    \end{tiny}
\end{frame}

\begin{frame}{Test: Inductive learning}
    \begin{block}{Dataset}
        A protein-protein interaction (PPI) dataset was utilised. Dataset consists of graphs corresponding to different human tissues.
    \end{block}
    \begin{block}{Methods}
        Comparison is done against four different super-vised GraphSAGE inductive methods presented in Hamilton et al. (2017).
    \end{block} \pause
    \begin{block}{Const-GAT}
        A variation Const-GAT is also provided with a constant attention mechanism \(\alpha(x,y) = 1\). This will assign the same weight to every neighbor and can be used to strictly evaluate the benefits of applying an attention mechanism (i.e. comparing with a near GCN-equivalent model).
    \end{block}
\end{frame}

\begin{frame}{Test: Inductive learning}
    \begin{block}{Setup}
        Three-layer GAT model
        \begin{itemize}
            \item First and Second layer
                \begin{itemize}
                    \item \(K = 4\) attention heads
                    \item \(F^\prime = 256\) features each
                    \item ELU nonlinearity
                \end{itemize}
            \item Third layer: Multi-label classification
                \begin{itemize}
                    \item \(K = 6\) attention heads
                    \item \(F^\prime = 121\) features each
                    \item Avaraged followed by Sigmoid activation
                \end{itemize}
        \end{itemize}
        No regularisation or dropout is required\\
        (\(44906\) training nodes from \(20\) graphs).
    \end{block}
\end{frame}

\begin{frame}{Test Results: Inductive learning}
    \begin{small}
    \begin{table}
      \caption{Inductive}
      \label{table:2}
      \begin{tabular}{ l l }
        \hline
        Method & PPI \\
        \hline
        Random & $0.396$ \\
        MLP & $0.422$ \\
        GraphSAGE-GCN (Hamilton et al., 2017) & $0.500$ \\
        GraphSAGE-mean (Hamilton et al., 2017) & $0.598$ \\
        GraphSAGE-LSTM (Hamilton et al., 2017) & $0.612$ \\
        GraphSAGE-pool (Hamilton et al., 2017) & $0.600$ \\
        \hline
        GraphSAGE & $0.768$ \\
        Const-GAT (Velickovic et al., 2018) & $0.934\pm0.006$ \\
        GAT (Velickovic et al., 2018) & $0.973\pm0.002$ \\
        \hline
      \end{tabular}
    \end{table}
    \end{small}
\end{frame}

\section{How Powerful are GNNs?}
\begin{frame}{Representational Power of GNNs}
    \begin{block}{Background}
    GNNs are widely used and have state-of-the-art results, but there is a lack of a theoretical framework to analyse their expressive power and what graph structures they can capture.
    \end{block} \pause
    \begin{block}{Key insight}
    Use the GNNs' similarities to the Weisfeiler-Lehman Isomorphism Test to evaluate their ability to distinguish graphs.
    \end{block}
\end{frame}

\begin{frame}{Background}
    \begin{block}{Multiset}
    A set that allows multiple instances.\\
    Formally $X$ is a multiset when $X = (S, m)$ where
    \begin{itemize}
        \item $S$ is the set of the distinct elements of $X$
        \item $m: S \rightarrow \mathbb{N}_{\geq1}$ the multiplicity of the elements
    \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Weisfeiler-Lehman Isomorphism Test}
    Test to evaluate weather two graphs are isomorphic.
    \begin{block}{Algorithm}
    For two Graphs $G_1, G_2$, for each node
    \begin{enumerate}
        \item Assign an initial label (same for all nodes)
        \item Create a multiset of the labels of all its neighbouring nodes
        \item Create a hash using its label and multiset and update its label with it 
        \item Repeat steps 2 - 3 until the labels' values stop changing
    \end{enumerate}
    If at any step the labels of the nodes between $G_1,G_2$ differ then they are not isomorphic.
    \end{block}
    A positive answer works well for most graphs.
\end{frame}

\begin{frame}
    \transduration<0-7>{0}
    \multiinclude[<+->][format=png, graphics={width=\textwidth}]{WL}
\end{frame}

\begin{frame}{Theoretical Framework}
    \begin{block}{Intuition}
    A maximally powerful GNN should map two nodes with different neighborhood structure to different locations. Therefore its aggregation scheme needs to be injective.
    \end{block}
\end{frame}

\begin{frame}{Conditions for Powerful GNNs (1/2)}
    \begin{block}{Lemma 2 (Xu et al. (2019))}
    Let \(G_{1}\) and \(G_{2}\) be any two non-isomorphic graphs. If a graph neural network \(\A : \mathcal{G} \rightarrow \mathbb{R}^d\) maps \(G_{1}\) and \(G_{2}\) to different embeddings, the Weisfeiler-Lehman graph isomorphism test also decides \(G_{1}\) and \(G_{2}\) are not isomorphic.
    \end{block}
\end{frame}

\begin{frame}{Conditions for Powerful GNNs (2/2)}
    \begin{block}{Theorem 3 (Xu et al. (2019))}
    Let \(\A: G \rightarrow \mathbb{R}^d\) be a GNN. With a sufficient number of GNN layers, \(\A\) maps any graphs \(G_1\) and \(G_2\) that the Weisfeiler-Lehman test of isomorphism decides as non-isomorphic, to different embeddings if the following conditions hold:
    \begin{enumerate}
        \item \(\A\) aggregates and updates node features iteratively with
            \[
                h_v^{(k)} = \phi\left(h_v^{(k-1)},f\left(\Big\{h_u^{(k-1)}:u\in \mathcal{N}(v)\Big\}\right)\right)
            \]
            where the functions \(f\), which operates on multisets, and \(\phi\) are injective.
        \item \(\A\)’s graph-level readout, which operates on the multiset of node features \(\Big\{h_v^{(k)}\Big\}\), is injective.
    \end{enumerate}
    \end{block}
\end{frame}

\begin{frame}{Graph Isomorphism Network}
    We will first see that sum aggregators can represent universal functions over multisets
    \begin{block}{Lemma 5 (Xu et al. (2019))}
    Assume \(\mathcal{X}\) is countable. There exists a function \(f:\mathcal{X} \rightarrow \mathbb{R}^n\) so that \(h(X) = \sum_{x\in X} f(x)\) is unique for each multiset \(X \subset \mathcal{X}\) of bounded size.  Moreover, any multiset function \(g\) can be decomposed as \(g(X) = \phi\left(\sum_{x\in X}f(x)\right)\) for some function \(\phi\).
    \end{block}
\end{frame}

\begin{frame}{Graph Isomorphism Network}
    \begin{footnotesize}
    The following aggregation scheme (among many other potential ones) will satisfy the condition \(1\) of the Theorem.
    \begin{block}{Corollary 6 (Xu et al. (2019))}
    Assume \(\mathcal{X}\) is countable.  There exists a function \(f:\mathcal{X} \rightarrow \mathbb{R}^n\) so that for infinitely many choices of \(\epsilon\), including all irrational numbers,
    \[
        h(c,X) = (1 + \epsilon) \cdot f(c) + \sum_{x\in X}f(x)
    \]
    is unique for each pair \((c,X)\), where \(c\in\mathcal{X}\) and \(X \subset \mathcal{X}\) is a multiset of bounded size. Moreover, any function \(\phi\) over such pairs can be decomposed as
    \[
        g(c,X) = \phi\left((1 + \epsilon) \cdot f(c) + \sum_{x\in X}f(x)\right)
    \]
    for some function \(\phi\). \(\epsilon\) can be either a learnable parameter or a fixed scalar.
    \end{block}
    \end{footnotesize}
\end{frame}

\begin{frame}{Graph Isomorphism Network}
    We can use multi-layer perceptrons (MLPs) to model and learn \(f\) and \(\phi\). Therefore GIN will update the node representations using
    \[
        h_v^{(k)} = MLP^{(k)}\left(\left(1+\epsilon^{(k)}\right) \cdot h_v^{(k-1)} + \sum_{u\in \mathcal{N}(v)}h_u^{(k-1)}\right)
    \]
    For graph classification, as features from earlier iterations may generalize better, we concatenate across all iterations/layers of GIN
    \[
        %h_G = CONCAT\left(READOUT\left(\Big\{h_v^{(k)}|v\in G\Big\}\right) | k = 0, 1, \dots , K\right)
        h_G = CONCAT\left(\sum_{v\in G}h_v^{(k)} \Big | k = 0, 1, \dots , K\right)
    \]
\end{frame}

\begin{frame}{Less Powerful GNNs}
    \begin{itemize}
        \item Mean aggregators (e.g. GCN)
            \begin{itemize}
                \item cannot distinguish some node structures, but captures the distribution
            \end{itemize}
        \item Max-pooling (e.g. GraphSAGE) or Min-pooling aggreagators
            \begin{itemize}
                \item even weaker, but can identify representative elements
                \item ignores multiplicities, i.e. reduces the multiset to a simple set
            \end{itemize}
    \end{itemize}
\end{frame}

\begin{frame}{Less Powerful GNNs}
    \begin{figure}
        \centering
        \includegraphics[scale=0.9]{expr_power_ranking.png}
        \caption{Ranking by expressive power for sum, mean and max aggregators over a multiset}
    \end{figure}
    \begin{figure}
        \centering
        \includegraphics[scale=0.9]{struc_fail_distinguish.png}
        \caption{Examples of graph structures that mean and max aggregators fail to distinguish.}
    \end{figure}
\end{frame}

\begin{frame}{Experiments}
    \begin{block}{Datasets}
        We use 9 graph classification benchmarks
        \begin{itemize}
            \item 4 bioinformatics datasets (MUTAG, PTC, NCI1, PROTEINS)
            \item 5 social network datasets (COLLAB, IMDB-BINARY, IMDB-MULTI, REDDIT-BINARY, REDDIT-MULTI5K)
        \end{itemize}
        We want the models to learn from network structure, so we put no features.
    \end{block}
\end{frame}

\begin{frame}{Experiments}
    \begin{block}{Models}
        \begin{itemize}
            \item GIN-\(\epsilon\): a GIN that learns \(\epsilon\)
            \item GIN-\(0\): a GIN where \(\epsilon = 0\)
            \item GIN-\(0\) with a 1-layer perceptron
            \item MLP with a MEAN aggregator
            \item GCN
            \item MLP with a MAX aggregator
            \item GraphSAGE
        \end{itemize}
    \end{block}
\end{frame}

\begin{frame}{Experimens}
    \begin{block}{Configuration}
        A \(10\)-fold cross-validation is performed and the average and standard deviation of validation accuracies is reported.\\
        \bigskip
        For all models
        \begin{itemize}
            \item 5 GNN layers (including input)
            \item MLPs have \(2\) layers
            \item Batch normalisation is applied
        \end{itemize}
    \end{block}
    \begin{block}{Training accuracy}
        Training accuracy is also reported (5 GNN layers) along with the WL subtree kernel (4 iterations comparable to the 5 GNN layers).
    \end{block}
\end{frame}

\begin{frame}{Experiments}
    \begin{figure}
        \centering
        \includegraphics[scale=1]{gins_training_set_perf.png}
        \caption{Training set performance of GINs, less powerful GNN variants and the WL subtree kernel}
    \end{figure}
\end{frame}

\begin{frame}{Experiments}
    \begin{tiny}
    \begin{table}
      \caption{Test set classification accuracies (\%) (social networks)}
      \label{table:3}
      \begin{tabular}{ l c c c c c }
        \hline
        Datasets & IMDB-B & IMDB-M & RDT-B & RDT-M5K & COLLAB \\
        \hline
        SUM–MLP (GIN-\(0\)) & $75.1\pm5.1$ & $52.3\pm2.8$ & $92.4\pm2.5$ & $57.5\pm1.5$ & $80.2\pm1.9$ \\
        SUM–MLP (GIN-\(\epsilon\)) & $74.3\pm5.1$ & $52.1\pm3.6$ & $92.2\pm2.3$ & $57.0\pm1.7$ & $80.1\pm1.9$ \\
        SUM–1-LAYER7 & $4.1\pm5.0$ & $52.2\pm2.4$ & $90.0\pm2.7$ & $55.1\pm1.6$ & $80.6\pm1.9$ \\
        MEAN–MLP & $73.7\pm3.7$ & $52.3\pm3.1$ & $50.0\pm0.0$ & $20.0\pm0.0$ & $79.2\pm2.3$ \\
        MEAN–1-LAYER (GCN) & $74.0\pm3.4$ & $51.9\pm3.8$ & $50.0\pm0.0$ & $20.0\pm0.0$ & $79.0\pm1.8$ \\
        MAX–MLP & $73.2\pm5.8$ & $51.1\pm3.6$ & – & – & – \\
        MAX–1-LAYER (GraphSAGE) & $72.3\pm5.3$ & $50.9\pm2.2$ & – & – & – \\
        \hline
      \end{tabular}
    \end{table}

    \begin{table}
      \caption{Test set classification accuracies (\%) (bioinformatics)}
      \label{table:4}
      \begin{tabular}{ l c c c c }
        \hline
        Datasets & MUTAG & PROTEINS & PTC & NCI1 \\
        \hline
        SUM–MLP (GIN-\(0\)) & $89.4\pm5.6$ & $76.2\pm2.8$ & $64.6\pm7.0$ & $82.7\pm1.7$ \\
        SUM–MLP (GIN-\(\epsilon\)) & $89.0\pm6.0$ & $75.9\pm3.8$ & $63.7\pm8.2$ & $82.7\pm1.6$ \\
        SUM–1-LAYER7 & $90.0\pm8.8$ & $76.2\pm2.6$ & $63.1\pm5.7$ & $82.0\pm1.5$ \\
        MEAN–MLP & $83.5\pm6.3$ & $75.5\pm3.4$ & $66.6\pm6.9$ & $80.9\pm1.8$ \\
        MEAN–1-LAYER (GCN) & $85.6\pm5.8$ & $76.0\pm3.2$ & $64.2\pm4.3$ & $80.2\pm2.0$ \\
        MAX–MLP & $84.0\pm6.1$ & $76.0\pm3.2$ & $64.6\pm10.2$ & $77.8\pm1.3$ \\
        MAX–1-LAYER (GraphSAGE) & $85.1\pm7.6$ & $75.9\pm3.2$ & $63.9\pm7.7$ & $77.7\pm1.5$ \\
        \hline
      \end{tabular}
    \end{table}
    \end{tiny}
\end{frame}

\begin{frame}{Experiments}
    \begin{block}{Results}
        \begin{itemize}
            \item WL subtree kernel is an upper bound, as predicted
            \item GINs achieve much higher performance that the other GNN variants
                \begin{itemize}
                    \item Followed by sum aggregators and then mean and max, again as predicted
                \end{itemize}
            \item GIN-\(0\) performs better than GIN-\(\epsilon\)
                \begin{itemize}
                    \item Probably due to its simplicity
                \end{itemize}
        \end{itemize}
    \end{block}
\end{frame}

\section{GCNs Loss of Expressive Power}
\begin{frame}{Intuition}
    \begin{block}{Goal}
        Theoretical analysis of the graph NN expressive power, by analyzing their asymptotic behaviors as the layer size goes to infinity.
    \end{block} \pause
    \begin{block}{General Approach}
        Using dynamical systems we will specialize to the GCNs, making use of a generalization of next Theorem. 
    \end{block}\pause
    \begin{block}{Theorem}
        If a finite and discrete Markov process is irreducible and aperiodic, it exponentially converges to a unique equilibrium and the eigenvalues of its transition matrix determine the convergence rate.
    \end{block}    
\end{frame}

\begin{frame}{Dynamical System}
    Definition of the problem:
    \begin{itemize}
        \item Function \(f_{l}:\mathbb{R}^{N\times C}\rightarrow\mathbb{R}^{N\times C}\) as \(f_{l}(X)=MLP_{l}(PX)=\sigma(\cdots\sigma(\sigma(PX)W_{l1})W_{l2}\cdots W_{lH_{l}})\), \\ the \(l-\)th multi-layer perceptron common to all nodes. 
        \begin{itemize}
            \item \(\sigma:\mathbb{R}^{N\times C}\rightarrow\mathbb{R}^{N\times C}\) is a ReLU function, \(P\in\mathbb{R}^{N\times N}\) is a symmetric matrix and \(W_{lh}\in\mathbb{R}^{C\times C}\)
        \end{itemize}
        \item Dynamics \(X^{(l+1)}=f_{l}(X^{(l)})\), with some initial value \(X^{(0)}\)
    \end{itemize}
    \bigskip
    We are interested in the asymptotic behavior of \(X^{(l)}\) as \(l\rightarrow\infty\).
\end{frame}

\begin{frame}{Dynamical System Results}
    Let \(U\) be a \(M-\)dimensional subspace of \(\mathbb{R}^{N}\)
    \begin{block}{Assumptions}
        \begin{enumerate}
            \item \(U\) has an orthonormal basis \((e_{m})_{m\in[M]}\) that consists of non-negative vectors.
            \item \(U\) is invariant under \(P\) , so if \(u \in U\) , then \(Pu \in U\).
        \end{enumerate}    
    \end{block} \pause
    Defining the subspace \(\mathcal{M}\) of \(\mathbb{R}^{N\times C}\) by \[\mathcal{M}=U\otimes\mathbb{R}^C=\{\sum_{m=1}^{M}e_{m}\otimes w_{m}|w_{m}\in \mathbb{R}^C\},\]  for \(X\in \mathbb{R}^{N\times C}\) denote distance between \(X\) and \(M\) by \(d_{\mathcal{M}}(X) := inf\{\|X-Y\|_{F} |\; Y \in \mathcal{M}\}\), the maximum singular value of \(W_{lh}\) by \(s_{lh}\) and \(\lambda:=\max_{n\in[N-M]}{|\lambda_{n}|}\), \(\lambda_{i}\) the eigenvalues of \(P\). 
\end{frame}

\begin{frame}{Dynamical System Results}
    \begin{block}{Theorem 1}
        Under Assumptions \(1\) and \(2\), we have 
        \begin{center}
            \(d_{\mathcal{M}}(f_{l}(X)) \leq s_{l}\lambda d_{\mathcal{M}}(X)\) for any \(X\in \mathbb{R}^{N\times C}\)  
        \end{center}
    \end{block}
    \begin{block}{Corollary 1}
        \(\mathcal{M}\) is invariant under \(f_{l}\) for any \(l\in\mathbb{N}_{+}\) , that is, if \(X\in\mathcal{M}\), then we have \(f_{l}(X)\in\mathcal{M}\).
    \end{block}
    \begin{block}{Corollary 2}
        Let \(s := \text{sup}_{l\in\mathbb{N}_{+}} s_{l}\). We have \(d_{\mathcal{M}}(X^{(l)}) = \mathcal{O}((s\lambda)^l)\). In particular, if \(s\lambda<1\), then \(X_{l}\) exponentially approaches \(\mathcal{M}\) as \(l\rightarrow\infty\) for any initial value \(X^{(0)}\).
    \end{block}
\end{frame}

\begin{frame}{Applications to GCNs}
    Let \(G=(V,E),\;|V|=N\) be an undirected graph, \(A\) be the adjacency matrix and \(D\) be the degree matrix of \(G\).\\
    \bigskip
    We define the augmented normalized Laplacian of \(G\) by \(\Delta:=I_{N}-(D+I_{N})^{-\frac{1}{2}}(A+I_{N})(D+I_{N})^{-\frac{1}{2}}\) and \(P:=I_{N}-\Delta\).\\
    \bigskip \pause
    For weights \(W_{l}\in \mathbb{R}^{C\times C}\), we define a GCN associated with \(G\) by \(f = f_{L}\circ\cdots\circ f_{1}\) where \(f_{l}:\mathbb{R}^{N\times C}\rightarrow\mathbb{R}^{N\times C}\) is defined by \(f_{l}(X) := \sigma(PXW_{l})\). \\
    \bigskip
    We are interested in the asymptotic behavior of the output \(X^{(L)}\) of the GCN as \(L \rightarrow\infty\).

\end{frame}

\begin{frame}{Applications to GCNs}
    For node classification tasks, we can interpret next result as the “information loss” of GCNs in the limit of infinite layers.
    \begin{block}{Theorem 2}
        For any initial value \(X^{(0)}\), the output of \(l-\)th layer \(X^{(l)}\) satisfies \(d_{\mathcal{M}}(X^{(l)})\leq(s\lambda)^{l}d_{\mathcal{M}}(X^{(0)})\). In particular, \(d_{\mathcal{M}}(X^{(l)})\) exponentially converges to \(0\) when \(s\lambda < 1\).
    \end{block} \pause
    For any \(X \in \mathcal{M}\), if two nodes \(i,j\in V\) are in a same connected component and their degrees are identical, then, the column vectors of \(X\) that correspond to nodes \(i\) and \(j\) are identical. \\
    \bigskip
    We cannot distinguish these nodes using X, so \(\mathcal{M}\) only has information about connected components and node degrees.
\end{frame}

\begin{frame}{Further Results for GCNs}
    \begin{block}{Theorem 3}
        Consider a GCN on the Erdős-Rényi graph \(G_{N,p}\) such that \(\frac{\log{N}}{N p} = o(1)\) as a function of \(N\). For any \(\epsilon > 0\), if the supremum \(s\) of the maximum singular values of weights in the GCN satisfies \(s < s_{0} := \frac{1}{7}\sqrt{\frac{Np-p+1}{\log{(4N/\epsilon)}}}\), then, for sufficiently large \(N\) , the GCN satisfies the condition of Theorem 2 with probability at least \(1-\epsilon\).
    \end{block} \pause
    The upper bound \(s_{0}\rightarrow\infty\) as \(N \rightarrow\infty\), so if the graph is sufficiently large and not extremely sparse, most GCNs suffer from information loss. For the dependence on the edge probability \(p, s_{0}\) is an increasing function of \(p\). \\
    \bigskip
    Theorem 3 implies that graph NNs perform poorly on dense NNs.
\end{frame}

% \begin{frame}{Experiments}

% \end{frame}

% \section{}
% \begin{frame}{Conclusion?}

% \end{frame}

\begin{frame}{Bibliography}
    \begin{itemize}
        \item Graph Attention Networks, by Petar Veličković, Guillem Cucurull, Arantxa Casanova, Adriana Romero, Pietro Liò and Yoshua Bengio
        \item How Powerful are Graph Neural Networks, by Keyulu Xu, Weihua Hu, Jure Leskovec and Stefanie Jegelka
        \item Graph Neural Networks Exponentially Lose Expressive Power for Node Classification, by Kenta Oono, Taiji Suzuki
        \item David Bieber, The Weisfeiler-Lehman Isomorphism Test
    \end{itemize}
\end{frame}

\begin{frame}{}
\centering
    \huge Thank you!
\end{frame}
\end{document}

### 2021-04-18 agt/ask01.tex
AGT: Exer01: First draft with exercises 1,2,3,4 and 6

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
  % you may want to try: {Liberation Serif} or {Times New Roman}
\setmainfont{FreeSerif}
  % you may want to try: {Liberation Sans} or {Arial}
\setsansfont[Scale=MatchLowercase]{FreeSans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{FreeMono}

\usepackage{amsmath}
% Required packages for plotting
\usepackage{pgfplots}
%\usepackage{pgfplotstable}
\pgfplotsset{compat=1.16}
%\usepackage{tikz}

\newcommand{\overeq}[1]{\stackrel{\text{#1}}{=}}
\newcommand{\vi}{\mathrm{v}}
\newcommand{\Supp}{\mathrm{Supp}}

% Main document
\begin{document}
\title{Αλγοριθμική Θεωρία Παιγνίων - 1η σειρά ασκήσεων}
\author{Θωμάς Παππάς}
%\date{}
\maketitle

\section*{Πρόβλημα 1}

\begin{enumerate}
	\item Ισχύει\\
	  $\forall t \in S^2$ έχουμε ότι $u_1(A,t)>u_1(C,t)$
	\item Δεν ισχύει\\
	  διότι έχουμε $u_2(D,W) < u_2(D,Z)$
	\item Ισχύει\\
	  $\forall t \in S^2$ έχουμε ότι $u_1(D,t) \geq u_1(B,t)$ με $u_1(D,W)>u_1(B,W)$
	\item Ισχύει\\
	  $\forall s \in S^1$ έχουμε ότι $u_2(W,s)>u_1(Y,s)$ που σημαίνει ότι η $W$ κυριαρχεί αυστηρά την $Y$, άρα και ασθενώς
	\item Ισχύει\\
	  βλέπουμε ότι $u_1(A,W) > \max\{u_1(B,W), u_1(C,W), u_1(D,W)\}$ που σημαίνει ότι η $A$ είναι η μοναδική υποψήφια κυρίαρχη στρατηγική.
	  Όμως $u_1(A,Z) = u_1(D,Z)$ οπότε η $A$ δεν είναι κυρίαρχη και άρα δεν υπάρχει καμία κυρίαρχη στρατηγική για τον παίκτη 1
	\item Δεν ισχύει\\
	  διότι $u_2(A,Y) > u_2(A,Z)$
	\item Ισχύει\\
	  αφαιρούμε τις στρατηγικές $B,C$ και $X,Y$ (κυριαρχούνται αυστηρά από τις $A$ και $W$ αντίστοιχα) και από τα υπόλοιπα σημεία το $(D,Z)$ είναι σημείο ισορροπίας αφού $u_1(D,Z) \geq u_1(A,Z), u_2(D,Z) \geq u_2(D,W)$ και το κοινωνικό όφελος είναι $u_1(D,Z) + u_2(D,Z) = 5+6<13$
\end{enumerate}

\section*{Πρόβλημα 2}

Για αρχή παρατηρούμε αν $a_1=50$ τότε ο π.1 θα πάρει σίγουρα $50$ ευρώ, αφού
\begin{itemize}
	\item αν $a_2 \leq 50$ τότε $u_1(50,a_2) = 50$ (από κανόνα $1$)
	\item αν $a_2 > 50$ τότε $u_1(50,a_2) = 50$ (από κανόνα $3$)
\end{itemize}
που σημαίνει ότι όλες οι στρατηγικές όπου $a_1<50$ κυριαρχούνται αυστηρά από την παραπάνω αφού αν $a_1<50$ τότε $\forall a_2: u_1(a_1,a_2) = a_1 < 50$.
\\
Ομοίως και για τον π.2, που σημαίνει ότι οι στρατηγικές $a_1<50$ και $a_2<50$ μπορούν να αφαιρεθούν με οποιαδήποτε σειρά και χωρίς να επηρεάσουν κάποιο σημείο ισορροπίας.
\newpage
Τώρα αν $a_1=100$ τότε πέρα από την περίπτωση $a_2=100$ όπου θα πάρουν και οι δύο $50$ ευρώ, αν $a_2 \in [51, 99]$ έχουμε $u_2(100,a_2)=a_2>50,u_1(100,a_2)=100-a_2<50$. Οπότε η στρατηγική $a_1=100$ είναι ασθενώς κυριαρχούμενη από την $a_1=50$ και μπορεί να αφαιρεθεί. Προφανώς ομοίως και για τον π.2.
\\[8pt]
Με την ίδια λογική βλέπουμε ότι και οι στρατηγικές $a_1=99$ και $a_2=99$ κυριαρχούνται ασθενώς από τις $a_1=50$ και $a_2=50$ αντίστοιχα (εφόσον έχουμε αφαιρέσει τις $a_1=100$ και $a_2=100$), και αναδρομικά ομοίως για όλες τις στρατηγικές $a_1,a_2 \in [52,100]$. Οπότε οι στρατηγικές που επιβιώνουν είναι οι
\begin{center}
	\begin{tabular}{c || c | c}
		& 50 & 51\\
		\hline\hline
		50 & 50 & 50\\
		51 & 50 & 50
	\end{tabular}
\end{center}
Βλέπουμε όμως ότι πριν αφαιρέσουμε κάποια από τις προηγούμενες ασθενώς κυριαρχούμενες στρατηγικές, έχουμε ότι η $a_1=50$ κυριαρχείται ασθενώς από την $a_1=51$ αφού $u_1(50,52) = 50 < 51 = u_1(51,52)$ (και πάλι ομοίως για τον π.2).
\\[8pt]
Άρα η μοναδική στρατηγική που θα επιβιώσει ανεξάρτητα από τη σειρά με την οποία θα αφαιρέσουμε τις ασθενώς κυριαρχούμενες στρατηγικές είναι η $(51,51)$.

\section*{Πρόβλημα 3}

\paragraph{(i)} Θα πρέπει να ισχύει $\vi_1=\vi_2$, οπότε έχουμε:
\begin{flalign}
  \vi_1=\vi_2 &\Rightarrow \mathrm{max}_i\mathrm{min}_j A_{ij} = \mathrm{min}_j\mathrm{max}_i A_{ij} &\nonumber\\
    &\Rightarrow \max\{\min\{a,5\},1,2\} = \min\{\max\{a,3\},6,7\} \label{eqv}
\end{flalign}
\begin{itemize}
	\item Αν $a > 5$ τότε \eqref{eqv} $\Rightarrow \max\{5,1,2\} = \min\{a,6,7\} \Rightarrow 5 = \min\{a,6\}$ που δεν γίνεται
	\item Αν $3 \leq a \leq 5$ τότε \eqref{eqv} $\Rightarrow \max\{a,1,2\} = \min\{a,6,7\} \Rightarrow a = a$ που ισχύει
	\item Αν $a < 3$ τότε \eqref{eqv} $\Rightarrow \max\{a,1,2\} = \min\{3,6,7\} \Rightarrow \max\{a,2\} = 3$ που δεν γίνεται
\end{itemize}
Οπότε το παίγνιο έχει σημείο ισορροπίας μόνο όταν $a \in [3,5]$.

\paragraph{(ii)} Η αναπαράσταση του παιγνίου είναι η εξής:
\begin{center}
	\begin{tabular}{c || c | c | c | c}
		& Δ1-Μ1 & Δ1-Μ2 & Δ2-Μ1 & Δ2-Μ2\\
		\hline\hline
		Δ1-Μ1 & $0$ & $2$ & $-3$ & $0$\\
		Δ1-Μ2 & $-2$ & $0$ & $0$ & $3$\\
		Δ2-Μ1 & $3$ & $0$ & $0 $& $-4$\\
		Δ2-Μ2 & $0$ & $-3$ & $4$ & $0$
	\end{tabular}
\end{center}
από το οποίο και βλέπουμε ότι αν οι παίκτες επιλέξουν οποιαδήποτε μικτή στρατηγική με Support μόνο τις αμιγείς στρατηγικές Δ1-Μ2 και Δ2-Μ1, τότε το συνολικό τους όφελος θα είναι $0$, και άρα δεν μπορεί να υπάρξει σημείο ισορροπίας σε αυτήν την περίπτωση.\\???

\section*{Πρόβλημα 4}

\paragraph{(i)} Σε ένα $2 \times 2$ παίγνιο, τα πιθανά σημεία ισορροπίας με αμιγείς στρατηγικές είναι τα\\
$(s_1,t_1),(s_1,t_2),(s_2,t_1),(s_2,t_2)$.
Χωρίς βλάβη της γενικότητας, έστω ότι τα $3$ σημεία ισορροπίας είναι τα $(s_1,t_1),(s_1,t_2),(s_2,t_1)$.
Δηλαδή έχουμε:
\begin{flalign}
	&u_1(s_1,t_1) \geq u_1(s, t_1) \forall s \in S \Rightarrow u_1(s_1,t_1) \geq u_1(s_2,t_1) \label{equil1}&\\
	&u_1(s_2,t_1) \geq u_1(s, t_1) \forall s \in S \Rightarrow u_1(s_2,t_1) \geq u_1(s_1,t_1) \label{equil2}\\
	&\eqref{equil1},\eqref{equil2} \Rightarrow u_1(s_1,t_1) = u_1(s_2,t_1) \label{equil3}
\end{flalign}
Τότε $\forall p \in (0,1)$, το προφίλ στρατηγικών $(s^\prime,t_1)$ όπου $s^\prime = (p, 1-p)$ μικτή στρατηγική, είναι επίσης σημείο ισορροπίας, αφού:
\begin{flalign*}
	u_1(s^\prime,t_1) &= p \cdot u_1(e_0,t_1) + (1-p) \cdot u_1(e_1,t_1) = p \cdot u_1(s_1,t_1) + (1-p) \cdot u_1(s_2,t_1) &\\
	  &\overeq{\eqref{equil3}} p \cdot u_1(s_1,t_1) + (1-p) \cdot u_1(s_1,t_1) = u_1(s_1,t_1)
\end{flalign*}
και άρα $u_1(s^\prime,t_1) \geq u_1(e_0,t_1)$ και $u_1(s^\prime,t_1) \geq u_1(e_1,t_1)$.
\\[8pt]
Ομοίως, χρησιμοποιώντας τα σημεία ισορροπίας $(s_1,t_1),(s_1,t_2)$ βρίσκουμε ότι και για τον παίκτη 2, $\forall p \in (0,1)$ το προφίλ στρατηγικών $(s_1,t^\prime)$ όπου $t^\prime = (p, 1-p)$ μικτή στρατηγική, είναι επίσης σημείο ισορροπίας.
\\[8pt]
Συνεπώς (και εφόσον και οποιοσδήποτε συνδυασμός των παραπάνω στρατηγικών επίσης αποτελεί σημείο ισορροπίας) και για τους δύο παίκτες υπάρχει άπειρο πλήθος από σημεία ισορροπίας με μεικτές στρατηγικές.

\paragraph{(ii)} Για αρχή αφαιρούμε την $s_3$ εφόσον κυριαρχείται αυστηρά από τις $s_1,s_2$ και άρα δεν πρόκειται να συμμετέχει σε οποιοδήποτε σημείο ισορροπίας.
\\[8pt]
Μετά κοιτώντας τις αμιγείς στρατηγικές, βλέπουμε ότι το $(s_2,t_1)$ είναι σημείο ισορροπίας, αφού
\[u_1(s_2,t_1) > u_1(s_1,t_1) \text{ και } u_2(s_2,t_1) > u_2(s_2,t_2) > u_2(s_2,t_3)\]
Τέλος για βρούμε αν υπάρχουν μικτές στρατηγικές, έστω $(p,q)$ προφίλ στρατηγικών σε σημείο ισορροπίας, με $p = (p_1,1-p_1)$ και $q = (q_1,q_2,1-q_1-q_2)$.
Οπότε θα πρέπει να ισχύει ότι:
\begin{flalign*}
  u_1(e^1,q) = u_2(e^1,q) &\Rightarrow 0q_1+5q_2+3(1-q_1-q_2) = 2q_1+3q_2+5(1-q_1-q_2) &\\
    &\Rightarrow 5q_2+3-3q_1-3q_2 = 2q_1+3q_2+5-5q_1-5q_2\\
    &\Rightarrow -3q_1-2q_1+5q_1+5q_2-3q_2-3q_2+5q_2 = 5-3\\
    &\Rightarrow 4q_2 = 2 \Rightarrow q_2 = \frac12
\end{flalign*}
\begin{flalign*}
  u_2(p,e^1) &= f_1(p_1) = 0p_1+4(1-p_1) = -4p_1+4 &\\
  u_2(p,e^2) &= f_2(p_1) = 2p_1+3(1-p_1) = -p_1+3\\
  u_2(p,e^3) &= f_3(p_1) = 3p_1+1(1-p_1) = 2p_1+1
\end{flalign*}
Στο τελευταίο κοιτάζουμε τις τιμές που παίρνουν οι $f_1,f_2,f_3$ για $p\in(0,1)$ και παίρνουμε τα σημεία των τομών τους πάνω στη $\max\{f_1,f_2,f_3\}$:

\centering
\begin{tikzpicture}
\begin{axis}[
  axis lines=left,
  xmax=1.2, ymax=5,
  xtick={1/3,2/3,1},
  xticklabels={$1/3$,$2/3$,$1$},
  xlabel=$p_1$
]

  % Add all the utility functions.
  \addplot[
    color=red,
    domain=0:1
  ]
  {-4*x+4};
  \addplot[
    color=blue,
    domain=0:1
  ]
  {-x+3};
  \addplot[
    color=brown,
    domain=0:1
  ]
  {2*x+1};
  %\node [fill=black,anchor=center] at (1/3,8/3) {};
  \draw [dashed,help lines] (0,8/3) -| (1/3,0);
  %\node [fill=black,anchor=center] at (2/3,7/3) {};
  \draw [dashed,help lines] (0,7/3) -| (2/3,0);
  \legend{$f_1$,$f_2$,$f_3$}
\end{axis}
\end{tikzpicture}

\raggedright
όπου στα σημεία τομής
\begin{flalign*}
  f_1(p_1) = f_2(p_1) &\Rightarrow -4p_1+4 = -p_1+3 \Rightarrow 3p_1 = 1 \Rightarrow p_1 = \frac13 &\\
  f_2(p_1) = f_3(p_1) &\Rightarrow -p_1+3 = 2p_1+1 \Rightarrow 3p_1 = 2 \Rightarrow p_1 = \frac23
\end{flalign*}
Στην πρώτη περίπτωση όπου $\Supp(q)=\{1,2\}$ έχουμε ότι $q = (1-q_2,q_2,0) \stackrel{q_2=1/2}{=} \left(\frac12,\frac12,0\right)$,\\
ενώ στη δεύτερη όπου $\Supp(q)=\{2,3\}$ έχουμε ότι $q = (0,q_2,1-q_2) \stackrel{q_2=1/2}{=} \left(0,\frac12,\frac12\right)$.
\\[10pt]
Οπότε εντέλει τα σημεία ισορροπίας στο παίγνιο είναι τα
\[(s_2,t_1) = (e^2,e^1), \left(\left(\frac13,\frac23\right),\left(\frac12,\frac12,0\right)\right), \left(\left(\frac23,\frac13\right),\left(0,\frac12,\frac12\right)\right)\]

\section*{Πρόβλημα 5}

Ορίζουμε...
\newpage

\section*{Πρόβλημα 6}

Θα δείξουμε ότι δεν ξέρουμε αν υπάρχει πολυωνυμικός αλγόριθμος για πεπερασμένα παίγνια μηδενικού αθροίσματος με $3$ παίκτες, δείχνοντας ότι ένας τέτοιος αλγόριθμος θα έλυνε και ένα γενικό παίγνιο με $2$ παίκτες.
\\[8pt]
Έστω λοιπόν $G_1$ ένα γενικό παίγνιο $2$ παικτών με στρατηγικές $S^1,S^2$ και utility functions $u_1, u_2$.
Κατασκευάσουμε τώρα ένα παίγνιο $G_2$ από το $G_1$ αλλά με $3$ παίκτες, στρατηγικές $S^1,S^2,S^3$ όπου $S^3 = \{r\}$ (δηλαδή ο π.3 έχει μόνο μία διαθέσιμη στρατηγική) και utility functions $u_1^\prime, u_2^\prime, u_3^\prime$ όπου:
\begin{align}
  u_1^\prime(p,q,r) &= u_1(p,q) \label{nash1}&\\
  u_2^\prime(p,q,r) &= u_2(p,q) \label{nash2}\\
  u_3^\prime(p,q,r) &= -u_1(p,q)-u_2(p,q) \nonumber
\end{align}
Τότε το $G_2$ είναι παίγνιο μηδενικού αθροίσματος με $3$ παίκτες και έχουμε ότι ένα προφίλ στρατηγικών $(p,q)$ είναι σημείο ισορροπίας για το $G_1$ αν και μόνον αν το $(p,q,r)$ είναι σημείο ισορροπίας στο $G_2$.
Όντως για ένα τέτοιο σημείο $(p,q,r)$ και $\forall p^\prime \in S^1, \forall q^\prime \in S^2$ έχουμε ότι:
\begin{itemize}
	\item $u_1(p,q) \geq u_1(p^\prime,q) \stackrel{\eqref{nash1}}{\Leftrightarrow} u_1^\prime(p,q,r) \geq u_1^\prime(p^\prime,q,r)$
	\item $u_2(p,q) \geq u_2(p,q^\prime) \stackrel{\eqref{nash2}}{\Leftrightarrow} u_2^\prime(p,q,r) \geq u_2^\prime(p,q^\prime,r)$
\end{itemize}
Ενώ για τον π.3 στο $G_2$ κάθε σημείο είναι ισορροπίας για αυτόν αφού $|S^3|=1$.
\\[8pt]
Από το παραπάνω βλέπουμε ότι ένα παίγνιο $2$ παικτών μπορεί να αναχθεί σε μια ειδική περίπτωση ενός παιγνίου μηδενικού αθροίσματος $3$ παικτών, και άρα το τελευταίο είναι τουλάχιστον όσο δύσκολο όσο το πρώτο.
Πιο συγκεκριμένα δηλαδή η επίλυση ενός παιγνίου μηδενικού αθροίσματος $3$ παικτών είναι PPAD-hard πρόβλημα, και άρα δεν γνωρίζουμε για την ύπαρξη πολυωνυμικού αλγορίθμου που να το επιλύνει.

\end{document}

### 2021-04-19 agt/ask01.tex
AGT: Exer01: Completed ex.4 and added ex.7 plus small fixes overall

@@
 \end{center}
-από το οποίο και βλέπουμε ότι αν οι παίκτες επιλέξουν οποιαδήποτε μικτή στρατηγική με Support μόνο τις αμιγείς στρατηγικές Δ1-Μ2 και Δ2-Μ1, τότε το συνολικό τους όφελος θα είναι $0$, και άρα δεν μπορεί να υπάρξει σημείο ισορροπίας σε αυτήν την περίπτωση.\\???
+Έστω τώρα $(p,q)$ προφίλ μικτών στρατηγικών με Support μόνο τις αμιγείς στρατηγικές Δ1-Μ2 και Δ2-Μ1, δηλαδή
+\[p=(0,p_1,1-p_1,0),q=(0,q_1,1-q_2,0)\]
+Κοιτάζουμε λοιπόν για σημείο ισορροπίας με αυτό το προφίλ
+\begin{flalign*}
+  w_1 &= \max_p \min_q u_1(p,q) &\\
+    &= \max_p \min \{u_1(p,e^1),u_1(p,e^2),u_1(p,e^3),u_1(p,e^4)\}\\
+    &= \max_{p_1} \min \{0 \cdot 0+2p_1-3(1-p_1)+0 \cdot 0,-2 \cdot 0+0p_1+0(1-p_1)+3 \cdot 0,\\
+      &\qquad\qquad\qquad 3 \cdot 0+0p_1+0(1-p_1)-4 \cdot 0,0 \cdot 0-3p_1+4(1-p_1)+0 \cdot 0\}\\
+    &= \max_{p_1} \min \{5p_1-3,0,0,-7p_1+4\}
+\end{flalign*}
+κοιτάζουμε λοιπόν τώρα τις τιμές για τις συναρτήσεις
+\[f_1(p_1)=5p_1-3,f_2(p_1)=0,f_3(p_1)=-7p_1+4\]
+(στα αριστερά μεγεθύνουμε στο σημείο ενδιαφέροντος)
+
+\centering
+\begin{tikzpicture}
+\begin{axis}[
+  width=220pt,
+  axis lines=center,
+  xmax=1, ymin=-3, ymax=5,
+  xlabel=$p_1/q_1$
+]
+
+  % Add all the utility functions.
+  \addplot[
+    color=brown,
+    domain=0:1
+  ]
+  {5*x-3};
+  \addplot[
+    color=red,
+    domain=0:1
+  ]
+  {0};
+  \addplot[
+    color=blue,
+    domain=0:1
+  ]
+  {-7*x+4};
+  \legend{$f_1$,$f_2$,$f_3$}
+\end{axis}
+\end{tikzpicture}
+\begin{tikzpicture}
+\begin{axis}[
+  width=220pt,
+  axis lines=center,
+  xmin=0.5, xmax=0.7, ymin=-0.2, ymax=0.2,
+  xtick={4/7,7/12,3/5},
+  xticklabels={$\frac47$,$\frac7{12}$,$\frac35$},
+  xlabel=$p_1/q_1$,
+  x tick label style={inner ysep=8pt,anchor=south},
+  % For some reason the 0 coordinates doesn't show the label, so we put it at 0.001.
+  ytick={-0.2,-1/12,0.001,0.2},
+  yticklabels={$-0.2$,$-\frac{1}{12}$,$0$,$0.2$}
+]
+
+  % Add all the utility functions.
+  \addplot[
+    color=brown,
+    domain=0:1
+  ]
+  {5*x-3};
+  \addplot[
+    color=red,
+    domain=0:1
+  ]
+  {0};
+  \addplot[
+    color=blue,
+    domain=0:1
+  ]
+  {-7*x+4};
+  \draw [dashed,help lines] (0,-1/12) -| (7/12,0);
+  \legend{$f_1$,$f_2$,$f_3$}
+\end{axis}
+\end{tikzpicture}
+
+\raggedright
+όπου βλέπουμε ότι η $\min\{f_1,f_2,f_3\}$ παίρνει τη $\max$ τιμή του στο σημείο $p_1=7/12$ όπου
+\[w_1 = f_1\left(\frac{7}{12}\right) = f_3\left(\frac{7}{12}\right) = 5 \cdot \frac{7}{12} - 3 = -\frac{1}{12}\]
+Τώρα για το $w_2$ λόγω συμμετρίας του προβλήματος, βλέπουμε ότι προκύπτουν οι ίδιες συναρτήσεις, οπότε χρησιμοποιώντας πάλι τις παραπάνω γραφικές παραστάσεις βλέπουμε ότι
+\begin{flalign*}
+w_2 &= \min_q \max_p u_2(p,q) = ... = \min_{q_1} \max \{5q_1-3,0,0,-7q_1+4\} = 0
+\end{flalign*}
+το οποίο ισχύει για οποιοδήποτε $q_1 \in \left[\frac47,\frac35\right]$.
+\\[8pt]
+Εφόσον $w_1 \neq w_2$, το $(p,q)$ δεν είναι σημείο ισορροπίας.
 
@@
 \begin{align}
-  u_1^\prime(p,q,r) &= u_1(p,q) \label{nash1}&\\
-  u_2^\prime(p,q,r) &= u_2(p,q) \label{nash2}\\
+  u_1^\prime(p,q,r) &= u_1(p,q) \label{nash61}\\
+  u_2^\prime(p,q,r) &= u_2(p,q) \label{nash62}\\
   u_3^\prime(p,q,r) &= -u_1(p,q)-u_2(p,q) \nonumber
@@
 \begin{itemize}
-	\item $u_1(p,q) \geq u_1(p^\prime,q) \stackrel{\eqref{nash1}}{\Leftrightarrow} u_1^\prime(p,q,r) \geq u_1^\prime(p^\prime,q,r)$
-	\item $u_2(p,q) \geq u_2(p,q^\prime) \stackrel{\eqref{nash2}}{\Leftrightarrow} u_2^\prime(p,q,r) \geq u_2^\prime(p,q^\prime,r)$
+	\item $u_1(p,q) \geq u_1(p^\prime,q) \stackrel{\eqref{nash61}}{\Leftrightarrow} u_1^\prime(p,q,r) \geq u_1^\prime(p^\prime,q,r)$
+	\item $u_2(p,q) \geq u_2(p,q^\prime) \stackrel{\eqref{nash62}}{\Leftrightarrow} u_2^\prime(p,q,r) \geq u_2^\prime(p,q^\prime,r)$
 \end{itemize}
@@
 
+\section*{Πρόβλημα 7}
+
+\paragraph{(i)} Έτσι ώστε το $(p,q)$ να είναι $\epsilon-$σημείο ισορροπίας θα πρέπει να ισχύει ότι
+\begin{align}
+  u_1(p,q) \geq u_1(e^1,q) - \epsilon \label{nash71}\\
+  u_1(p,q) \geq u_1(e^2,q) - \epsilon \label{nash72}\\
+  u_2(p,q) \geq u_2(p,e^1) - \epsilon \label{nash73}\\
+  u_2(p,q) \geq u_2(p,e^2) - \epsilon \label{nash74}
+\end{align}
+Υπολογίζουμε τις αντίστοιχες τιμές
+\begin{align*}
+  u_1(p,q) &= 1/2 \cdot 1/2 \left[(1/2-\delta)+0+\delta+(1/2-\delta)\right] = 1/4(1-\delta) = 1/4-\delta/4&\\
+  u_1(e^1,q) &= 1/2(1/2-\delta)+1/2 \cdot 0 = 1/4-\delta/2\\
+  u_1(e^2,q) &= 1/2\delta+1/2(1/2-\delta) = 1/4\\[3pt]
+  u_2(p,q) &= 1/2 \cdot 1/2 \left[\delta+(1/2-\delta)+(1/2-\delta)+\delta\right] = 1/4 \cdot 1 = 1/4\\
+  u_2(p,e^1) &= 1/2\delta+1/2(1/2-\delta) = 1/4\\
+  u_2(p,e^2) &= 1/2(1/2-\delta)+1/2\delta = 1/4\\
+\end{align*}
+Για τον π.2 βλέπουμε ότι οι \eqref{nash73} και \eqref{nash74} ισχύουν $\forall \epsilon \geq 0$.
+Για τον π.1 τώρα έχουμε:
+\begin{itemize}
+	\item $\eqref{nash71} \Rightarrow \epsilon \geq u_1(e^1,q)-u_1(p,q) = (1/4-\delta/2) - (1/4-\delta/4) = -\delta/4$\\
+	  που ισχύει πάντα αφού $-\delta/4 < 0$
+	\item $\eqref{nash72} \Rightarrow \epsilon \geq u_1(e^2,q)-u_1(p,q) = 1/4 - (1/4-\delta/4) = \delta/4$
+\end{itemize}
+Άρα το καλύτερο (μικρότερο) $\epsilon \geq 0$ ώστε το $(p,q)$ να είναι $\epsilon-$σημείο ισορροπίας είναι το
+\[\epsilon(\delta) = \frac{\delta}{4}\]
+
+\paragraph{(ii)} Αφού $p=(1/n,1/n,\dots,1/n)$ έχουμε ότι $\Supp(p) = \{1,2,\dots,n\}$, δηλαδή περιέχει όλες τις στρατηγικές του εκάστοτε παίκτη.
+Άρα αρκεί να δείξουμε ότι $\forall \epsilon \geq k/n$ και $\forall i,l$ με $1 \leq i,l \leq n$ ισχύει ότι
+\begin{align}
+  u_1(e^i,p) \geq u_1(e^l,p) - \epsilon \label{nash75}\\
+  u_2(p,e^i) \geq u_2(p,e^l) - \epsilon \label{nash76}
+\end{align}
+Εφόσον από την υπόθεση σε κάθε σειρά και στήλη έχουμε το πολύ $k$ μη μηδενικές τιμές, δηλαδή $\forall i, 1 \leq i \leq n$ ισχύει ότι $|\{j:u_1(s_i,t_j) \neq 0\}| \leq k$, τότε παρατηρούμε ότι
+\begin{flalign*}
+  u_1(e^i,p) &= \sum_{j=0}^n p_j \cdot u_1(s_i,t_j) = \frac{1}{n} \sum_{j=0}^n u_1(s_i,t_j) = \frac{1}{n} \sum_{j: u_1(s_i,t_j) \neq 0} u_1(s_i,t_j)&\\
+    & \leq \frac{1}{n} \sum_{j: u_1(s_i,t_j) \neq 0} 1 \stackrel{\text{υποθ.}}{\leq} \frac{1}{n} \cdot k = \frac{k}{n}
+\end{flalign*}
+και άρα η \eqref{nash75} ισχύει αφού $\forall i,l$ με $1 \leq i,l \leq n$
+\[u_1(e^l,p)-\epsilon \leq u_1(e^l,p)-\frac{k}{n} \leq 0 \leq u_1(e^i,p)\]
+Ομοίως δείχνουμε και την \eqref{nash76}.
+Άρα το προφίλ μεικτών στρατηγικών $(p,p)$ όντως αποτελεί $\epsilon-$σημείο ισορροπίας.
+
+\section*{Πρόβλημα 8}
+
+\paragraph{(i)}
+
 \end{document}

### 2021-04-20 agt/ask01.tex
AGT: Exer01: Added exercises 5 and 8

@@
 
-Ορίζουμε...
+\paragraph{(i)} Ορίζουμε ένα παίγνιο ως εξής:
+\begin{itemize}
+	\item παίκτης $i$ είναι ο φοιτητής $i$ που συμμετέχει στην ψηφοφορία
+	\item $S^i = S = \{\Pi_1,\Pi_2,\Pi_3,\Pi_4\}$
+\end{itemize}
+Τώρα πριν ορίσουμε τις συναρτήσεις χρησιμότητας, ορίζουμε τη συνάρτηση $w(s)$ η οποία δεδομένου ενός προφίλ στρατηγικών $s \in S^{50}$ επιστρέφει την παράταξη που νίκησε.
+Δηλαδή, αν συμβολίσουμε ως $|\Pi_i|_s$ το πλήθος των $\Pi_i$ στρατηγικών στο σύνολο $s$ τότε
+\[
+  w(s) =
+    \begin{cases}
+      \Pi_1, & |\Pi_1|_s \geq \max\{|\Pi_2|_s,|\Pi_3|_s,|\Pi_4|_s\}\\
+      \Pi_2, & |\Pi_2|_s \geq \max\{|\Pi_3|_s,|\Pi_4|_s\}\\
+      \Pi_3, & |\Pi_3|_s \geq |\Pi_4|_s\\
+      \Pi_4, & \text{διαφορετικά}
+    \end{cases}
+\]
+Οπότε τώρα ένας φοιτητής $i$ με σειρά προτίμησης των παρατάξεων $\Pi_1 > \Pi_2 > \Pi_3 > \Pi_4$ θα έχει συνάρτηση χρησιμότητας
+\[
+  u_i(s) =
+    \begin{cases}
+      3, & w(s) = \Pi_1\\
+      2, & w(s) = \Pi_2\\
+      1, & w(s) = \Pi_3\\
+      0, & w(s) = \Pi_4\\
+    \end{cases}
+\]
+και ομοίως αν είχε άλλη σειρά με την υψηλότερη προτίμηση να του δίνει $3$ μονάδες ωφέλειας μέχρι την τελευταία να του δίνει $0$.
+
+\paragraph{(ii)} Για κάθε στρατηγική $i \in S$ έχουμε ότι το $s = \{\Pi_i\}^{50}$ αποτελεί σημείο ισορροπίας όπου κερδίζει η παράταξη $\Pi_i$.
+Όντως αν ένας παίκτης $p$ αλλάξει την ψήφο του σε κάποια άλλη παράταξη $\Pi_j$ τότε στο $s^\prime = (\Pi_j,s_{-p})$ θα έχουμε $|\Pi_i|_p=49, |\Pi_j|_p=1$ (και $0$ για τις υπόλοιπες) και άρα $w(s^\prime) = w(s) = \Pi_i$, που σημαίνει $u_i(s^\prime) = u_i(s)$.
+
+\paragraph{(iii)} Για αρχή βλέπουμε ότι αν όλοι οι φοιτητές ψηφίσουν την πραγματική τους προτίμηση τότε $(|\Pi_1|,|\Pi_2|,|\Pi_3|,|\Pi_4|) = (20,10,20,0)$.
+Άρα έτσι ώστε να φτάσουμε σε σημείο όπου νικάει η $\Pi_2$ με τον ελάχιστο αριθμό αλλαγών, θα πρέπει να αλλάξουμε την ψήφο από αυτούς που ψήφισαν $\Pi_1$ και $\Pi_3$.
+Επιλέγουμε τα group φοιτητών 1-10 και 41-50 αντίστοιχα επειδή έχουν την $\Pi_2$ σαν δεύτερη προτίμηση.
+Επίσης παρατηρούμε ότι για να είμαστε σε σημείο ισορροπίας θα πρέπει $\Pi_2 > \Pi_1-1$ και $\Pi_2 > \Pi_3$, έτσι ώστε μια μεμονομένη αλλαγή ψήφου να μην μπορεί να αλλάξει το αποτέλεσμα.
+\\[8pt]
+Με τα παραπάνω βλέπουμε ότι αν $4$ άτομα από κάθε group ψηφίσουν $\Pi_2$ αντί για την αρχική τους προτίμηση τότε $(|\Pi_1|,|\Pi_2|,|\Pi_3|,|\Pi_4|) = (16,18,16,0)$ το οποίο είναι σημείο ισορροπίας όπου νικάει η $\Pi_2$.
+Πιο συγκεκριμένα, η κατάταξη των ψήφων είναι ως εξής:
+\begin{itemize}
+	\item 1-10: $6$ ψηφίζουν $\Pi_1$ (πρώτη επιλογή) και $4$ ψηφίζουν $\Pi_2$
+	\item 11-20: όλοι ψηφίζουν $\Pi_3$ (πρώτη επιλογή)
+	\item 21-30: όλοι ψηφίζουν $\Pi_1$ (πρώτη επιλογή)
+	\item 31-40: όλοι ψηφίζουν $\Pi_2$ (πρώτη επιλογή)
+	\item 41-50: $6$ ψηφίζουν $\Pi_3$ (πρώτη επιλογή) και $4$ ψηφίζουν $\Pi_2$
+\end{itemize}
+στην οποία βλέπουμε ότι αν αλλάξουμε την ψήφο σε κάποιον από αυτούς που δεν έχουν ψηφίσει την πρώτη τους επιλογή τότε το σημείο δεν είναι πια ισορροπίας.
+\\[8pt]
+Οπότε ο ελάχιστος αριθμός ψηφοφόρων που πρέπει να μην ψηφίσει την πραγματική του προτίμηση σε σημείο ισορροπίας με νικητή την παράταξη $\Pi_2$ είναι $8$.
+
 \newpage
@@
 
-\paragraph{(i)}
+\paragraph{(i)} Θα δείξουμε ότι το παρακάτω προφίλ στρατηγικών αποτελεί σημείο ισορροπίας
+\[b = (b_1,b_2,b_3,\dots,b_n) = (v_2,v_1,v_3,\dots,v_n)\]
+όπου ο π.1 δηλώνει $v_2$, ο π.2 δηλώνει $v_1$, και αφού $b_2 > b_1 > b_3 > \dots > b_n$ τότε ο νικητής είναι ο π.2 πληρώνοντας $b_1 = v_2$, και όχι ο π.1 που έχει την υψηλότερη αποτίμηση.
+\\[8pt]
+Αρκεί να δείξουμε ότι όλοι οι παραπάνω παίκτες έχουν την ίδια ωφέλεια με το αν δήλωναν την αποτίμησή τους, δηλαδή αρκεί να δείξουμε $\forall i, 1 \leq i \leq n$ ότι
+\[u_i(b) = u_i(v_i,b_{-i})\]
+Τότε εφόσον βρισκόμαστε σε truthful μηχανισμό και άρα $u_i(v_i,b_{-i}) \geq u_i(b^\prime,b_{-i})$ για κάθε $b^\prime \neq v_i$, παίρνουμε και ότι $u_i(b) \geq u_i(b^\prime,b{-i})$ για κάθε $b^\prime$, και άρα το προφίλ στρατηγικών $b$ θα είναι σημείο ισορροπίας.
+\\[8pt]
+Αρχικά προφανώς $i \geq 3$ έχουμε $b_i=v_i$ και άρα προφανώς $u_i(v_i,b_{-i}) = u_i(b)$.
+Για τους δύο πρώτους παίκτες υπολογίζουμε τις αντίστοιχες τιμές
+\begin{align*}
+  u_1(b) = 0 \qquad u_1(v_1,b_{-1}) = v_1 - b_1 = v_1 - v_1 = 0\\[3pt]
+  u_2(b) = v_2 - b_1 = v_2 - v_2 = 0 \qquad u_2(v_2,b_{-2}) = 0
+\end{align*}
+Άρα έχουμε όντως $u_i(b) = u_i(v_i,b_{-i}), \forall i, 1 \leq i \leq n$, και άρα με τον παραπάνω συλλογισμό, το $b$ αποτελεί σημείο ισορροπίας με νικητή τον π.2 ενώ $v_1>v_2$.
+
+\paragraph{(ii)} Θα δείξουμε ότι ο δεύτερος παίκτης μπορεί να πει ψέματα έτσι ώστε να αυξήσει την ωφέλειά του.
+\\[8pt]
+Δεδομένου λοιπόν ότι όλοι οι παίκτες εκτός του π.2 δηλώσουν προσφορές όσο η αποτίμησή τους, εάν ο π.2 κάνει και αυτός το ίδιο τότε δεν θα κερδίσει το αγαθό και θα έχει ωφέλεια $u_2(v_2,b_{-2}) = 0$.
+Εάν όμως επιλέξει να δηλώσει μια πιο μεγάλη προσφορά $b_2^\prime$ τέτοια ώστε $b_2^\prime > v_1 > v_2$ τότε θα κερδίσει το αγαθό και θα έχει ωφέλεια $u_2(b_2^\prime,b_{-2}) = v_2-v_3 > 0$.
+\\[8pt]
+Εφόσον έχουμε $u_2(v_2,b_{-2}) < u_2(b_2^\prime,b_{-2})$ έπεται ότι ο μηχανισμός δεν είναι φιλαλήθης.
 

### 2021-04-20 agt/ask01.tex
AGT: Exer01: Final fixes and improvements

@@
 \\[8pt]
-Άρα η μοναδική στρατηγική που θα επιβιώσει ανεξάρτητα από τη σειρά με την οποία θα αφαιρέσουμε τις ασθενώς κυριαρχούμενες στρατηγικές είναι η $(51,51)$.
+Άρα το μοναδικό προφίλ στρατηγικών που θα επιβιώσει ανεξάρτητα από τη σειρά με την οποία θα αφαιρέσουμε τις ασθενώς κυριαρχούμενες στρατηγικές είναι το $(51,51)$.
 
@@
 \raggedright
-όπου βλέπουμε ότι η $\min\{f_1,f_2,f_3\}$ παίρνει τη $\max$ τιμή του στο σημείο $p_1=7/12$ όπου
+όπου βλέπουμε ότι η $\min\{f_1,f_2,f_3\}$ παίρνει τη $\max$ τιμή της στο σημείο $p_1=7/12$ όπου
 \[w_1 = f_1\left(\frac{7}{12}\right) = f_3\left(\frac{7}{12}\right) = 5 \cdot \frac{7}{12} - 3 = -\frac{1}{12}\]
-Τώρα για το $w_2$ λόγω συμμετρίας του προβλήματος, βλέπουμε ότι προκύπτουν οι ίδιες συναρτήσεις, οπότε χρησιμοποιώντας πάλι τις παραπάνω γραφικές παραστάσεις βλέπουμε ότι
+Τώρα για το $w_2$, λόγω συμμετρίας του προβλήματος, βλέπουμε ότι προκύπτουν οι ίδιες συναρτήσεις, οπότε χρησιμοποιώντας πάλι τις παραπάνω γραφικές παραστάσεις βλέπουμε ότι
 \begin{flalign*}
@@
 \\[8pt]
-Εφόσον $w_1 \neq w_2$, το $(p,q)$ δεν είναι σημείο ισορροπίας.
+Εφόσον $w_1 \neq w_2$ συμπεραίνουμε ότι το $(p,q)$ δεν είναι σημείο ισορροπίας.
 
@@
 \begin{flalign*}
-	u_1(s^\prime,t_1) &= p \cdot u_1(e_0,t_1) + (1-p) \cdot u_1(e_1,t_1) = p \cdot u_1(s_1,t_1) + (1-p) \cdot u_1(s_2,t_1) &\\
+	u_1(s^\prime,t_1) &= p \cdot u_1(e^0,t_1) + (1-p) \cdot u_1(e^1,t_1) = p \cdot u_1(s_1,t_1) + (1-p) \cdot u_1(s_2,t_1) &\\
 	  &\overeq{\eqref{equil3}} p \cdot u_1(s_1,t_1) + (1-p) \cdot u_1(s_1,t_1) = u_1(s_1,t_1)
 \end{flalign*}
-και άρα $u_1(s^\prime,t_1) \geq u_1(e_0,t_1)$ και $u_1(s^\prime,t_1) \geq u_1(e_1,t_1)$.
+και άρα $u_1(s^\prime,t_1) \geq u_1(s, t_1) \forall s \in S$.
 \\[8pt]
@@
     &\Rightarrow 5q_2+3-3q_1-3q_2 = 2q_1+3q_2+5-5q_1-5q_2\\
-    &\Rightarrow -3q_1-2q_1+5q_1+5q_2-3q_2-3q_2+5q_2 = 5-3\\
+    &\Rightarrow (-3q_1-2q_1+5q_1) + (5q_2-3q_2-3q_2+5q_2) = 5-3\\
     &\Rightarrow 4q_2 = 2 \Rightarrow q_2 = \frac12
 \end{flalign*}
+καθώς και ότι:
 \begin{flalign*}
@@
 	\item παίκτης $i$ είναι ο φοιτητής $i$ που συμμετέχει στην ψηφοφορία
-	\item $S^i = S = \{\Pi_1,\Pi_2,\Pi_3,\Pi_4\}$
+	\item $S^i = \{\Pi_1,\Pi_2,\Pi_3,\Pi_4\} = S$
 \end{itemize}
@@
 \]
-και ομοίως αν είχε άλλη σειρά με την υψηλότερη προτίμηση να του δίνει $3$ μονάδες ωφέλειας μέχρι την τελευταία να του δίνει $0$.
+και αντίστοιχα αν είχε άλλη σειρά προτίμησης τότε ομοίως η υψηλότερη προτίμηση θα του δίνει $3$ μονάδες ωφέλειας κ.ο.κ.
 
 \paragraph{(ii)} Για κάθε στρατηγική $i \in S$ έχουμε ότι το $s = \{\Pi_i\}^{50}$ αποτελεί σημείο ισορροπίας όπου κερδίζει η παράταξη $\Pi_i$.
-Όντως αν ένας παίκτης $p$ αλλάξει την ψήφο του σε κάποια άλλη παράταξη $\Pi_j$ τότε στο $s^\prime = (\Pi_j,s_{-p})$ θα έχουμε $|\Pi_i|_p=49, |\Pi_j|_p=1$ (και $0$ για τις υπόλοιπες) και άρα $w(s^\prime) = w(s) = \Pi_i$, που σημαίνει $u_i(s^\prime) = u_i(s)$.
+Όντως αν ένας παίκτης $p$ αλλάξει την ψήφο του σε κάποια άλλη παράταξη $\Pi_j$ τότε στο $s^\prime = (\Pi_j,s_{-p})$ θα έχουμε $|\Pi_i|_p=49, |\Pi_j|_p=1$ (και $0$ για τις υπόλοιπες) και άρα $w(s^\prime) = w(s) = \Pi_i$ που σημαίνει $u_i(s^\prime) = u_i(s)$.
 
@@
 \\[8pt]
-Με τα παραπάνω βλέπουμε ότι αν $4$ άτομα από κάθε group ψηφίσουν $\Pi_2$ αντί για την αρχική τους προτίμηση τότε $(|\Pi_1|,|\Pi_2|,|\Pi_3|,|\Pi_4|) = (16,18,16,0)$ το οποίο είναι σημείο ισορροπίας όπου νικάει η $\Pi_2$.
-Πιο συγκεκριμένα, η κατάταξη των ψήφων είναι ως εξής:
+Με τα παραπάνω βλέπουμε ότι αν $4$ άτομα από κάθε group που επιλέξαμε ψηφίσουν $\Pi_2$ αντί για την αρχική τους προτίμηση τότε $(|\Pi_1|,|\Pi_2|,|\Pi_3|,|\Pi_4|) = (16,18,16,0)$ το οποίο είναι σημείο ισορροπίας όπου νικάει η $\Pi_2$.
+Πιο συγκεκριμένα, η κατάταξη των ψήφων είναι η εξής:
 \begin{itemize}
@@
 \end{itemize}
-στην οποία βλέπουμε ότι αν αλλάξουμε την ψήφο σε κάποιον από αυτούς που δεν έχουν ψηφίσει την πρώτη τους επιλογή τότε το σημείο δεν είναι πια ισορροπίας.
+στην οποία και βλέπουμε ότι αν αλλάξουμε την ψήφο από κάποιον από αυτούς που δεν έχουν ψηφίσει την πρώτη τους επιλογή στην πρώτη, τότε το σημείο δεν θα είναι πια ισορροπίας.
 \\[8pt]
@@
 \end{align}
-Τότε το $G_2$ είναι παίγνιο μηδενικού αθροίσματος με $3$ παίκτες και έχουμε ότι ένα προφίλ στρατηγικών $(p,q)$ είναι σημείο ισορροπίας για το $G_1$ αν και μόνον αν το $(p,q,r)$ είναι σημείο ισορροπίας στο $G_2$.
+Τότε το $G_2$ είναι παίγνιο μηδενικού αθροίσματος με $3$ παίκτες, ενώ επίσης έχουμε και ότι ένα προφίλ στρατηγικών $(p,q)$ είναι σημείο ισορροπίας για το $G_1$ αν και μόνον αν το $(p,q,r)$ είναι σημείο ισορροπίας στο $G_2$.
 Όντως για ένα τέτοιο σημείο $(p,q,r)$ και $\forall p^\prime \in S^1, \forall q^\prime \in S^2$ έχουμε ότι:
@@
 \end{itemize}
-Ενώ για τον π.3 στο $G_2$ κάθε σημείο είναι ισορροπίας για αυτόν αφού $|S^3|=1$.
+Ενώ για τον π.3 στο $G_2$ κάθε σημείο είναι ισορροπίας αφού $|S^3|=1$.
 \\[8pt]
@@
   u_1(e^1,q) &= 1/2(1/2-\delta)+1/2 \cdot 0 = 1/4-\delta/2\\
-  u_1(e^2,q) &= 1/2\delta+1/2(1/2-\delta) = 1/4\\[3pt]
+  u_1(e^2,q) &= 1/2 \cdot \delta+1/2(1/2-\delta) = 1/4\\[3pt]
   u_2(p,q) &= 1/2 \cdot 1/2 \left[\delta+(1/2-\delta)+(1/2-\delta)+\delta\right] = 1/4 \cdot 1 = 1/4\\
-  u_2(p,e^1) &= 1/2\delta+1/2(1/2-\delta) = 1/4\\
-  u_2(p,e^2) &= 1/2(1/2-\delta)+1/2\delta = 1/4\\
+  u_2(p,e^1) &= 1/2 \cdot \delta+1/2(1/2-\delta) = 1/4\\
+  u_2(p,e^2) &= 1/2(1/2-\delta)+1/2 \cdot \delta = 1/4\\
 \end{align*}
@@
 \end{align}
-Εφόσον από την υπόθεση σε κάθε σειρά και στήλη έχουμε το πολύ $k$ μη μηδενικές τιμές, δηλαδή $\forall i, 1 \leq i \leq n$ ισχύει ότι $|\{j:u_1(s_i,t_j) \neq 0\}| \leq k$, τότε παρατηρούμε ότι
+Εφόσον από την υπόθεση σε κάθε σειρά έχουμε το πολύ $k$ μη μηδενικές τιμές, δηλαδή $\forall i, 1 \leq i \leq n$ ισχύει ότι $|\{j:u_1(s_i,t_j) \neq 0\}| \leq k$, τότε παρατηρούμε ότι
 \begin{flalign*}
@@
 \[u_1(e^l,p)-\epsilon \leq u_1(e^l,p)-\frac{k}{n} \leq 0 \leq u_1(e^i,p)\]
-Ομοίως δείχνουμε και την \eqref{nash76}.
+Ομοίως δείχνουμε και την \eqref{nash76} εφόσον από υπόθεση η ιδιότητα για $k$ το πολύ μη μηδενικές τιμές ισχύει και για τις στήλες.
 Άρα το προφίλ μεικτών στρατηγικών $(p,p)$ όντως αποτελεί $\epsilon-$σημείο ισορροπίας.
@@
 \\[8pt]
-Αρχικά προφανώς $i \geq 3$ έχουμε $b_i=v_i$ και άρα προφανώς $u_i(v_i,b_{-i}) = u_i(b)$.
-Για τους δύο πρώτους παίκτες υπολογίζουμε τις αντίστοιχες τιμές
+Αρχικά $\forall i \geq 3$ έχουμε $b_i=v_i$ και άρα προφανώς $u_i(v_i,b_{-i}) = u_i(b)$.
+Για τους δύο πρώτους παίκτες τώρα υπολογίζουμε τις αντίστοιχες τιμές
 \begin{align*}

### 2021-05-23 stochastic/exer_set_03.tex
Stochastic: Exer Set 03: Added first draft with all excercises

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
  % you may want to try: {Liberation Serif} or {Times New Roman}
\setmainfont{FreeSerif}
  % you may want to try: {Liberation Sans} or {Arial}
\setsansfont[Scale=MatchLowercase]{FreeSans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{FreeMono}

\usepackage{mathtools}
\usepackage{tikz}

\newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
% Commands for wrapping properly common expressions.
\newcommand{\Exp}{\mathrm{Exp}}
\newcommand{\Expect}{{\rm I\kern-.3em E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}

% Main document
\begin{document}
\title{Στοχαστικές Ανελίξεις - 3ο πακέτο Ασκήσεων}
\author{Θωμάς Παππάς}
\date{}
\maketitle

\section*{Άσκηση 1}

Θα δείξω ότι
\[
	\pi_i = \sum_{j\in S} \pi_j p_{ji} \Leftrightarrow
	\sum_{j\in A} \sum_{i\in A^c} \pi_j p_{ji} = \sum_{i\in A^c} \sum_{j\in A} \pi_i p_{ij}
\]

\subsection*{$(\Leftarrow)$}
Αν πάρουμε για $A = \{j\}$ τότε οι εξισώσεις γενικευμένης ισορροπίας γίνονται:
\begin{align*}
	\sum_{j\neq i} \pi_j p_{ji} = \sum_{i\neq j} \pi_i p_{ij}
		&\Rightarrow \sum_{j\neq i} \pi_j p_{ji} + \pi_j p_{jj} = \sum_{i\neq j} \pi_i p_{ij} + \pi_j p_{jj} &\\
		&\Rightarrow \sum_{i\in S} \pi_j p_{ji} = \sum_{i\in S} \pi_i p_{ij}\\
		&\Rightarrow \pi_j \sum_{i\in S} p_{ji} = \sum_{i\in S} \pi_i p_{ij}\\
		&\Rightarrow \pi_j = \sum_{i\in S} \pi_i p_{ij}
\end{align*}

\subsection*{$(\Rightarrow)$}
Έστω ένα τυχαίο $A \subseteq S$. Τότε ξεκινώντας από το $\sum_{j\in A} \pi_j$ και εφαρμόζοντας τις εξισώσεις γενικής ισορροπίας έχουμε
\begin{align}
	\sum_{j\in A} \pi_j \cdot 1  &= \sum_{j\in A} \sum_{i\in S} \pi_i p_{ij}
		\Rightarrow \sum_{j\in A} \pi_j \sum_{i\in S} p_{ji}  = \sum_{j\in A} \sum_{i\in S} \pi_i p_{ij} \notag &\\
		&\Rightarrow \sum_{j\in A} \sum_{i\in S} \pi_j p_{ji}  = \sum_{i\in S} \sum_{j\in A} \pi_i p_{ij} \notag \\
		&\Rightarrow \sum_{j\in A} \left( \sum_{i\in A} \pi_j p_{ji} + \sum_{i\in A^c} \pi_j p_{ji} \right) = \sum_{i\in A} \sum_{j\in A} \pi_i p_{ij} + \sum_{i\in A^c} \sum_{j\in A} \pi_i p_{ij} \notag \\
		&\Rightarrow \sum_{j\in A} \sum_{i\in A} \pi_j p_{ji} + \sum_{j\in A} \sum_{i\in A^c} \pi_j p_{ji} = \sum_{i\in A} \sum_{j\in A} \pi_i p_{ij} + \sum_{i\in A^c} \sum_{j\in A} \pi_i p_{ij} \label{eqn:eqfulleq}
\end{align}
Όπου προφανώς ισχύει ότι
\[
	\sum_{j\in A} \sum_{i\in A} \pi_j p_{ji} = \sum_{i\in A} \sum_{j\in A} \pi_i p_{ij}
\]
άρα η προηγούμενη εξίσωση γίνεται
\[
	\eqref{eqn:eqfulleq} \Rightarrow \sum_{j\in A} \sum_{i\in A^c} \pi_j p_{ji} = \sum_{i\in A^c} \sum_{j\in A} \pi_i p_{ij}
\]
και εφόσον το $A$ ήταν τυχαίο άρα ισχύει για κάθε $A \subseteq S$.
\\[8pt]
Μια διαισθητική ερμηνεία για τις εξισώσεις γενικευμένης ισορροπίας είναι ότι ενώ η κατάσταση μιας Μ.Α.Δ.Χ αλλάζει, τότε μακροπρόθεσμα θα μπει σε ένα υποσύνολο του $S$ όσες φορές και θα βγει (αφού δεν μπορεί να \textit{ξαναμπεί} αν δεν \textit{βγει} πρώτα).

\section*{Άσκηση 2}

\paragraph{(α)}
Έχουμε ότι $\forall n \geq 0$ αν $X_0=i_0, X_1=i_1, \dots, X_n=i_n, i_k \in \{0,1,2,\dots,N\}$, τότε

\[
	P(X_{n+1} = j|X_n = i_n, X_{n-1} = i_{n-1}, \dots , X_0 = i_0) =
		\begin{cases}
			\frac{i_n}{N} \cdot q, & j = i_n-1\\
			\frac{i_n}{N} \cdot p + \frac{N-i_n}{N} \cdot q, & j = i_n\\
			\frac{N-i_n}{N} \cdot p, & j = i_n+1\\
			0, & \text{διαφορετικά}
		\end{cases}
\]
το οποίο είναι ανεξάρτητο του $n$ και των $i_0,i_1,\dots , i_{n-1}$ και άρα η $\{X_n, n \geq 0\}$ είναι Μ.Α.Δ.Χ με πίνακα πιθανοτήτων μετάβασης
\[
	P =
		\begin{pmatrix}
			q & p & 0 & \cdots & 0 & 0\\[1em]
			\frac{1}{N} q & \frac{1}{N}p + \frac{N-1}{N}q & \frac{N-1}{N} p & \cdots & 0 & 0\\[1em]
			0 & \frac{2}{N} q & \frac{2}{N}p + \frac{N-2}{N}q & \cdots & 0 & 0\\[1em]
			\vdots & \vdots & \vdots & \ddots & \vdots & \vdots\\[1em]
			0 & 0 & 0 & \cdots & \frac{N-1}{N}p + \frac{1}{N}q & \frac{1}{N} p\\[1em]
			0 & 0 & 0 & \cdots & q & p
		\end{pmatrix}
\]

\paragraph{(β)}
Έχουμε ότι $\forall i,j \in S$ θεωρώντας $i < j$ ισχύει ότι
\begin{align*}
	&p_{ij}^{(j-i)} \geq p_{i,i+1} \cdot p_{i+1,i+2} \cdot \dots \cdot p_{j-1,j} = \left(\frac{N-i}{N}p\right) \left(\frac{N-i-1}{N}p\right) \dots \left(\frac{N-j+1}{N}p\right) > 0\\
	&p_{ji}^{(j-i)} \geq p_{j,j-1} \cdot p_{j-1,j-2} \cdot \dots \cdot p_{i+1,i} = \left(\frac{j}{N}p\right) \left(\frac{j-1}{N}p\right) \dots \left(\frac{i+1}{N}p\right) > 0
\end{align*}
άρα η $\{X_n,n\geq 0\}$ είναι αδιαχώριστη.
Επίσης έχουμε $p_{ii} \geq 0, \forall i \in S$ άρα και απεριοδική.
\\[8pt]
Τέλος εφόσον η $\{X_n,n\geq 0\}$ είναι πεπερασμένη, αδιαχώριστη και απεριοδική τότε έχει στάσιμη κατανομή και άρα είναι και θετικά επαναληπτική.

\paragraph{(γ)}
Θεωρούμε $\forall i \in S$ το $A = \{0,1,2,\dots,i\}$, τότε από τις εξισώσεις γενικευμένης ισορροπίας παίρνουμε
\begin{flalign}
	\sum_{j\in A} \sum_{i\in A^c} \pi_j p_{ji} = \sum_{i\in A^c} \sum_{j\in A} \pi_i p_{ij}
		&\Rightarrow \pi_{i-1} p_{i-1,i} = \pi_{i} p_{i,i-1}
		\Rightarrow \pi_{i-1} \frac{N-i+1}{N} p = \pi_i \frac{i}{N} q \notag &\\
		&\Rightarrow \pi_{i-1} (N-i+1) p = \pi_i i (1-p) \notag\\
		&\Rightarrow \pi_i = \pi_{i-1}\frac{N-i+1}{i} \cdot \frac{p}{1-p} \notag\\
		&\Rightarrow \pi_i = \frac{(N-i+1)(N-i+2) \cdots N}{i (i-1) \cdots 1} \left(\frac{p}{1-p}\right)^i \pi_0 \notag\\
		&\Rightarrow \pi_i = \binom{N}{i} \left(\frac{p}{1-p}\right)^i \pi_0 \label{eqpr2}
\end{flalign}
Από την εξίσωση κανονικοποίησης τώρα έχουμε
\begin{align*}
	\sum_{i=0}^N \pi_i = 1 &\Rightarrow \pi_0 + \sum_{i=1}^N \pi_i = 1
		\stackrel{\eqref{eqpr2}}{\Rightarrow} \pi_0 + \sum_{i=1}^N \binom{N}{i} \left(\frac{p}{1-p}\right)^i \pi_0 = 1 &\\
		&\Rightarrow \pi_0 \left(1 + \sum_{i=1}^N \binom{N}{i} \left(\frac{p}{1-p}\right)^i \right) = 1
		\Rightarrow \pi_0 \sum_{i=0}^N \binom{N}{i} \left(\frac{p}{1-p}\right)^i = 1\\
		&\Rightarrow \pi_0 \left(1+\frac{p}{1-p}\right)^N = 1
		\Rightarrow \pi_0 \left(\frac{1}{1-p}\right)^N = 1\\
		&\Rightarrow \pi_0 = (1-p)^N
\end{align*}
και άρα η στάσιμη κατανομή είναι το διάνυσμα $[\pi_i]_{i=0,1,\dots,N}$ όπου
\[
	\pi_i = \binom{N}{i} \left(\frac{p}{1-p}\right)^i (1-p)^N = \binom{N}{i} p^i (1-p)^{N-i}
\]

\paragraph{(δ)}
Το μακροπρόθεσμο ποσοστό του χρόνου που υπάρχουν $i$ σφαιρίδια στην κάλπη $A$ είναι
\[
	\lim_{n \rightarrow \infty} \frac{\sum_{k=0}^{n-1} 1_{\{X_k=i\}}}{n} = \pi_i = \binom{N}{i} p^i (1-p)^{N-i}
\]

\section*{Άσκηση 3}

\paragraph{(α)}
Η Μ.Α.Δ.Χ. είναι αδιαχώριστη, αφού $p_{i,i+1} > 0$ και $p_{i-1}{i} > 0$.
\\[8pt]
Τώρα αν για $j=1,2,\dots$ θεωρήσουμε το $A_j = \{0,1,2,\dots,j-1\}$, τότε από τις εξισώσεις γενικευμένης ισορροπίας παίρνουμε
\[
	\pi_{j-1} p_{j-1} = \pi_j q_j \Rightarrow \pi_j = \frac{p_{j-1}}{q_j} \pi_{j-1}
\]
και άρα
\begin{equation}
	\pi_j = \frac{p_{j-1} p_{j-2} \dots p_0}{q_j q_{j-1} \dots q_1} \pi_0 \label{eqpr3}
\end{equation}
Από την εξίσωση κανονικοποίησης τώρα παίρνουμε
\begin{align*}
	\sum_{j=0}^\infty \pi_j = 1 &\Rightarrow \pi_0 + \sum_{j=1}^\infty \pi_j = 1
		\stackrel{\eqref{eqpr3}}{\Rightarrow} \pi_0 + \sum_{j=1}^\infty \frac{p_{j-1} p_{j-2} \dots p_0}{q_j q_{j-1} \dots q_1} \pi_0 = 1 &\\
		&\Rightarrow \pi_0 \left(1 + \sum_{j=1}^\infty \frac{p_{j-1} p_{j-2} \dots p_0}{q_j q_{j-1} \dots q_1} \right) = 1
\end{align*}
Θέτουμε $B^{-1} = 1 + \sum_{j=1}^\infty \frac{p_{j-1} p_{j-2} \dots p_0}{q_j q_{j-1} \dots q_1}$ και έχουμε
\begin{itemize}
	\item αν $B^{-1} < \infty$ τότε υπάρχει στάσιμη κατανομή και άρα η Μ.Α.Δ.Χ. είναι θετικά επαναληπτική με
		\[\pi_0=B, \pi_j = \frac{p_{j-1} p_{j-2} \dots p_0}{q_j q_{j-1} \dots q_1} B, j \geq 1\]
	\item αν $B^{-1} = \infty$ τότε $\pi_j = 0, \forall j = 0,1,2,\dots$ οπότε δεν υπάρχει στάσιμη κατανομή και άρα η αλυσίδα δεν είναι θετικά επαναληπτική
\end{itemize}
Άρα η $\{X_n,n\geq 0\}$ είναι θετικά επαναληπτική αν και μόνον αν $B < \infty$.

\paragraph{(β)}
Από το (α) υποερώτημα έχουμε ήδη ότι αν $B^{-1} < \infty$ τότε η στάσιμη κατανομή είναι το διάνυσμα $[\pi_i]_{i=0,1,2,\dots}$ όπου
\[\pi_0=B, \pi_j = \frac{p_{j-1} p_{j-2} \dots p_0}{q_j q_{j-1} \dots q_1} B, j \geq 1\]

\section*{Άσκηση 4}

\paragraph{(α)}
Αρχικά βλέπουμε ότι αν $p=1, q=0$ τότε $p_{ij} = 0, \forall i > j$ και άρα η $\{X_n,n\geq 0\}$ δεν είναι επαναληπτική.
Άρα απαιτούμε $p<1$, στη οποία περίπτωση η αλυσίδα είναι επαναληπτική αλλά και αδιαχώριστη.
Επίσης τότε η $\{X_n,n\geq 0\}$ και απεριοδική αφού $p_{00} = q > 0$.
\\[8pt]
Παίρνουμε τώρα τις εξισώσεις πλήρους ισορροπίας
\[
	\pi = \pi P \Rightarrow [\pi_0,\pi_1,\dots] = [\pi_0,\pi_1,\dots]
		\begin{pmatrix}
			q & p & 0 & 0 & \cdots\\
			q & 0 & p & 0 & \cdots\\
			q & 0 & 0 & p & \cdots\\
			\vdots & \vdots & \vdots & \vdots & \ddots
		\end{pmatrix}
		\Rightarrow
			\begin{cases}
				\pi_0 = \sum_{j=0}^\infty \pi_j q\\
				\pi_1 = p \cdot \pi_0\\
				\pi_2 = p \cdot \pi_1 \\
				\vdots
			\end{cases}
		\Rightarrow
			\begin{cases}
				\pi_0 = q\\
				\pi_1 = p \cdot q\\
				\pi_2 = p^2 \cdot q \\
				\vdots
			\end{cases}
\]
αφού από την εξίσωση κανονικοποίησης έχουμε $\sum_{j=0}^\infty \pi_j = 1$ και άρα
\[\pi_0 = \sum_{j=0}^\infty \pi_j q = q \sum_{j=0}^\infty \pi_j = q\]
Άρα υπάρχει στάσιμη κατανομή και η $\{X_n,n\geq 0\}$ είναι θετικά επαναληπτική αν και μόνον αν $p<1$.

\paragraph{(β)}
Από το (α) υποερώτημα έχουμε ήδη ότι αν $p<1$ τότε η στάσιμη κατανομή είναι το διάνυσμα $\pi = [\pi_i]_{i=0,1,2,\dots}$ όπου
\[\pi_j = p^i \cdot q\]

\section*{Άσκηση 5}

Έστω $Y_n$ το υποσύνολο του $A$ που έχει επισκεφθεί η αλυσίδα μέχρι το $n$-οστό βήμα.
Η $\{(X_n,Y_n,n\geq 0)\}$ είναι Μ.Α.Δ.Χ. και θεωρούμε ότι απορροφάται όταν επισκεφθεί κατάσταση με $X_n=0$ ή $Y_n=A$.
Δηλαδή οι πιθανότητες μετάβασης της νέας Μ.Α.Δ.Χ. είναι
\begin{align*}
	&P(X_{n+1}=0,Y_{n+1}=B|X_n=0,Y_n=B) = 1\\
	&P(X_{n+1}=i,Y_{n+1}=A|X_n=i,Y_n=A) = 1\\
	&P(X_{n+1}=j,Y_{n+1}=C|X_n=i,Y_n=B) = p_{ij}
\end{align*}
με
\[C = \begin{cases}
	B \cup \{j\}, & j \in A-B\\
	B & j \notin, A-B
\end{cases}\]
Για $B \subseteq A$ και $i \geq 1$ συμβολίζουμε με $p(i,B)$ την πιθανότητα η αλυσίδα να απορροφηθεί σε κατάσταση με $Y_n=A$ ξεκινώντας από την $(i,B)$.
Κάνοντας ανάλυση πρώτου βήματος παίρνουμε
\[
	\begin{dcases}
		p(i,B) = \sum_{j=0} p_{i_0} \cdot 0 + \sum_{j\in A-B} p_{ij} \cdot p(i,B\cup \{j\}) + \sum_{j\notin (A-B) \cup \{0\}} p_{ij} \cdot p(j,B)\\
		p(i,A) = 1
	\end{dcases}
\]
και αυτό $\forall i\in S \setminus \{0\}$ και $B \subseteq A$.
\\[8pt]
Αν $\pi^{(0)}$ η αρχική κατανομή τότε λύνοντας το παραπάνω σύστημα εξισώσεων παίρνουμε
\[
	f_A = \sum_{i\in A} \pi^{(0)}(i) \cdot p(i,\{i\}) + \sum_{i\notin A} \pi^{(0)}(i) \cdot p(i,\emptyset) + \pi^{(0)}(0) \cdot 0
\]

\end{document}

### 2021-05-23 stochastic/exer_set_03.tex
Stochastic: Exer Set 03: Included chain graphs and made final corrections and improvements

@@
 \subsection*{$(\Rightarrow)$}
-Έστω ένα τυχαίο $A \subseteq S$. Τότε ξεκινώντας από το $\sum_{j\in A} \pi_j$ και εφαρμόζοντας τις εξισώσεις γενικής ισορροπίας έχουμε
+Έστω ένα τυχαίο $A \subseteq S$. Τότε ξεκινώντας από το $\sum_{j\in A} \pi_j$ και εφαρμόζοντας τις εξισώσεις πλήρους ισορροπίας έχουμε
 \begin{align}
-	\sum_{j\in A} \pi_j \cdot 1  &= \sum_{j\in A} \sum_{i\in S} \pi_i p_{ij}
-		\Rightarrow \sum_{j\in A} \pi_j \sum_{i\in S} p_{ji}  = \sum_{j\in A} \sum_{i\in S} \pi_i p_{ij} \notag &\\
+	\sum_{j\in A} \pi_j \cdot 1  = \sum_{j\in A} \sum_{i\in S} \pi_i p_{ij}
+		&\Rightarrow \sum_{j\in A} \pi_j \sum_{i\in S} p_{ji}  = \sum_{j\in A} \sum_{i\in S} \pi_i p_{ij} \notag &\\
 		&\Rightarrow \sum_{j\in A} \sum_{i\in S} \pi_j p_{ji}  = \sum_{i\in S} \sum_{j\in A} \pi_i p_{ij} \notag \\
@@
 \end{align}
-Όπου προφανώς ισχύει ότι
+όπου προφανώς ισχύει ότι
 \[
@@
 \]
-άρα η προηγούμενη εξίσωση γίνεται
+και άρα η εξίσωση \eqref{eqn:eqfulleq} γίνεται
 \[
@@
 \]
-και εφόσον το $A$ ήταν τυχαίο άρα ισχύει για κάθε $A \subseteq S$.
+και εφόσον το $A$ ήταν τυχαίο άρα το παραπάνω ισχύει για κάθε $A \subseteq S$.
 \\[8pt]
@@
 			q & p & 0 & \cdots & 0 & 0\\[1em]
-			\frac{1}{N} q & \frac{1}{N}p + \frac{N-1}{N}q & \frac{N-1}{N} p & \cdots & 0 & 0\\[1em]
-			0 & \frac{2}{N} q & \frac{2}{N}p + \frac{N-2}{N}q & \cdots & 0 & 0\\[1em]
+			\frac{1}{N} q & \left(\frac{1}{N}p + \frac{N-1}{N}q\right) & \frac{N-1}{N} p & \cdots & 0 & 0\\[1em]
+			0 & \frac{2}{N} q & \left(\frac{2}{N}p + \frac{N-2}{N}q\right) & \cdots & 0 & 0\\[1em]
 			\vdots & \vdots & \vdots & \ddots & \vdots & \vdots\\[1em]
-			0 & 0 & 0 & \cdots & \frac{N-1}{N}p + \frac{1}{N}q & \frac{1}{N} p\\[1em]
+			0 & 0 & 0 & \cdots & \left(\frac{N-1}{N}p + \frac{1}{N}q\right) & \frac{1}{N} p\\[1em]
 			0 & 0 & 0 & \cdots & q & p
@@
 \end{align*}
-άρα η $\{X_n,n\geq 0\}$ είναι αδιαχώριστη.
+που σημαίνει ότι η $\{X_n,n\geq 0\}$ αδιαχώριστη.
 Επίσης έχουμε $p_{ii} \geq 0, \forall i \in S$ άρα και απεριοδική.
@@
 \paragraph{(γ)}
+\begin{center}
+	\begin{tikzpicture}[
+			node distance={15mm},
+			main/.style = {draw, circle, minimum size=23pt},
+			dots/.style = {minimum size=15pt}
+		]
+		\node[main] (1) {$0$};
+		\node[main] (2) [right of=1] {$1$};
+		\node[main] (3) [right of=2] {$2$};
+		\node[dots] (4) [right of=3] {$\dots$};
+		\node[main] (5) [right of=4] {$N$};
+		% For some reason using foreach doesn't align properly the edges on the \j node.
+		%\foreach \i [evaluate=\i as \j using \i+1] in {1,2,3}  {
+		%	\draw[->] (\i) to [out=120, in=60, looseness=4] (\i);
+		%	\draw[->] (\i) to [out=45, in=135] (\j);
+		%	\draw[->] (\j) to [out=225, in=315] (\i);
+		%}
+		\draw[->] (1) to [out=120, in=60, looseness=4] (1);
+		\draw[->] (1) to [out=45, in=135] (2);
+		\draw[->] (2) to [out=225, in=315] (1);
+		\draw[->] (2) to [out=120, in=60, looseness=4] (2);
+		\draw[->] (2) to [out=45, in=135] (3);
+		\draw[->] (3) to [out=225, in=315] (2);
+		\draw[->] (3) to [out=120, in=60, looseness=4] (3);
+		\draw[->] (3) to [out=45, in=135] (4);
+		\draw[->] (4) to [out=225, in=315] (3);
+		\draw[->] (4) to [out=45, in=135] (5);
+		\draw[->] (5) to [out=225, in=315] (4);
+		\draw[->] (5) to [out=120, in=60, looseness=4] (5);
+	\end{tikzpicture}
+\end{center}
 Θεωρούμε $\forall i \in S$ το $A = \{0,1,2,\dots,i\}$, τότε από τις εξισώσεις γενικευμένης ισορροπίας παίρνουμε
@@
 \]
+\pagebreak
 
@@
 \paragraph{(α)}
-Η Μ.Α.Δ.Χ. είναι αδιαχώριστη, αφού $p_{i,i+1} > 0$ και $p_{i-1}{i} > 0$.
+\begin{center}
+	\begin{tikzpicture}[
+			node distance={15mm},
+			main/.style = {draw, circle, minimum size=23pt, inner sep=0pt},
+			dots/.style = {minimum size=15pt}
+		]
+		\node[main] (1) {$0$};
+		\node[main] (1) {$0$};
+		\node[main] (2) [right of=1] {$1$};
+		\node[main] (3) [right of=2] {$2$};
+		\node[dots] (4) [right of=3] {$\dots$};
+		\node[main] (5) [right of=4] {$j-1$};
+		\node[main] (6) [right of=5] {$j$};
+		\node[main] (7) [right of=6] {$j+1$};
+		\node[dots] (8) [right of=7] {$\dots$};
+		\draw[->] (1) to [out=120, in=60, looseness=4] node[above] {$r_0$} (1);
+		\draw[->] (1) to [out=45, in=135] node[above] {$p_0$} (2);
+		\draw[->] (2) to [out=225, in=315] node[below] {$q_1$} (1);
+		\draw[->] (2) to [out=120, in=60, looseness=4] node[above] {$r_1$} (2);
+		\draw[->] (2) to [out=45, in=135] node[above] {$p_1$} (3);
+		\draw[->] (3) to [out=225, in=315] node[below] {$q_2$} (2);
+		\draw[->] (3) to [out=120, in=60, looseness=4] node[above] {$r_2$} (3);
+		\draw[->] (3) to [out=45, in=135] node[above] {$p_2$} (4);
+		\draw[->] (4) to [out=225, in=315] node[below] {$q_3$} (3);
+		\draw[->] (4) to [out=45, in=135] node[above] {$p_{j-2}$} (5);
+		\draw[->] (5) to [out=225, in=315] node[below] {$q_{j-1}$} (4);
+		\draw[->] (5) to [out=120, in=60, looseness=4] node[above] {$r_{j-1}$} (5);
+		\draw[->] (5) to [out=45, in=135] node[above] {$p_{j-1}$} (6);
+		\draw[->] (6) to [out=225, in=315] node[below] {$q_{j}$} (5);
+		\draw[->] (6) to [out=120, in=60, looseness=4] node[above] {$r_j$} (6);
+		\draw[->] (6) to [out=45, in=135] node[above] {$p_j$} (7);
+		\draw[->] (7) to [out=225, in=315] node[below] {$q_{j+1}$} (6);
+		\draw[->] (7) to [out=120, in=60, looseness=4] node[above] {$r_{j+1}$} (7);
+		\draw[->] (7) to [out=45, in=135] node[above] {$p_{j+1}$} (8);
+		\draw[->] (8) to [out=225, in=315] node[below] {$q_{j+2}$} (7);
+	\end{tikzpicture}
+\end{center}
+Η Μ.Α.Δ.Χ. είναι αδιαχώριστη αφού $p_{i,i+1} > 0$ και $p_{i-1,i} > 0, i = 1,2,\dots$.
 \\[8pt]
@@
 \paragraph{(α)}
-Αρχικά βλέπουμε ότι αν $p=1, q=0$ τότε $p_{ij} = 0, \forall i > j$ και άρα η $\{X_n,n\geq 0\}$ δεν είναι επαναληπτική.
-Άρα απαιτούμε $p<1$, στη οποία περίπτωση η αλυσίδα είναι επαναληπτική αλλά και αδιαχώριστη.
+\begin{center}
+	\begin{tikzpicture}[
+			node distance={15mm},
+			main/.style = {draw, circle, minimum size=23pt, inner sep=0pt},
+			dots/.style = {minimum size=15pt}
+		]
+		\node[main] (1) {$0$};
+		\node[main] (2) [right of=1] {$1$};
+		\node[main] (3) [right of=2] {$2$};
+		\node[main] (4) [right of=3] {$3$};
+		\node[dots] (5) [right of=4] {$\dots$};
+		\draw[->] (1) to [out=150, in=210, looseness=4] node[left] {$q$} (1);
+		\draw[->] (1) to [out=45, in=135] node[above] {$p$} (2);
+		\draw[->] (2) to [out=225, in=315] (1);
+		\draw[->] (2) to [out=45, in=135] node[above] {$p$} (3);
+		\draw[->] (3) to [out=225, in=315] (1);
+		\draw[->] (3) to [out=45, in=135] node[above] {$p$} (4);
+		\draw[->] (4) to [out=225, in=315] (1);
+		\draw[->] (4) to [out=45, in=135] node[above] {$p$} (5);
+		\draw[->] (5) to [out=225, in=315] node[near start, below right] {$q$} (1);
+	\end{tikzpicture}
+\end{center}
+Αρχικά βλέπουμε ότι αν $p=1 \Rightarrow q=0$ τότε $p_{ij} = 0, \forall i > j$ και άρα η $\{X_n,n\geq 0\}$ δεν είναι επαναληπτική.
+Άρα απαιτούμε $p<1 \Rightarrow q>0$, στη οποία περίπτωση η αλυσίδα είναι επαναληπτική αλλά και αδιαχώριστη.
+\\[8pt]
 Επίσης τότε η $\{X_n,n\geq 0\}$ και απεριοδική αφού $p_{00} = q > 0$.
@@
 \[
-	\pi = \pi P \Rightarrow [\pi_0,\pi_1,\dots] = [\pi_0,\pi_1,\dots]
+	\pi = \pi P \Rightarrow (\pi_0,\pi_1,\dots) = (\pi_0,\pi_1,\dots)
 		\begin{pmatrix}
@@
 		\Rightarrow
-			\begin{cases}
+			\begin{dcases}
 				\pi_0 = \sum_{j=0}^\infty \pi_j q\\
@@
 				\vdots
-			\end{cases}
+			\end{dcases}
 		\Rightarrow
@@
 Από το (α) υποερώτημα έχουμε ήδη ότι αν $p<1$ τότε η στάσιμη κατανομή είναι το διάνυσμα $\pi = [\pi_i]_{i=0,1,2,\dots}$ όπου
-\[\pi_j = p^i \cdot q\]
+\[\pi_i = p^i \cdot q\]
+
+\pagebreak
 
@@
 
-Έστω $Y_n$ το υποσύνολο του $A$ που έχει επισκεφθεί η αλυσίδα μέχρι το $n$-οστό βήμα.
+Έστω $Y_n$ το υποσύνολο του $A$ που έχει επισκεφθεί η αλυσίδα μέχρι το $n$-οστό βήμα.\\
 Η $\{(X_n,Y_n,n\geq 0)\}$ είναι Μ.Α.Δ.Χ. και θεωρούμε ότι απορροφάται όταν επισκεφθεί κατάσταση με $X_n=0$ ή $Y_n=A$.
@@
 	B \cup \{j\}, & j \in A-B\\
-	B & j \notin, A-B
+	B & j \notin A-B
 \end{cases}\]
@@
 \\[8pt]
-Αν $\pi^{(0)}$ η αρχική κατανομή τότε λύνοντας το παραπάνω σύστημα εξισώσεων παίρνουμε
+Η λύση του παραπάνω συστήματος μας δίνει τον υπολογισμό της $f_A$.
+Πιο συγκεκριμένα, αν $\pi^{(0)}$ η αρχική κατανομή τότε λύνοντας το σύστημα παίρνουμε
 \[

### 2021-05-28 stochastic/exer_set_04.tex
Stochastic: Exer Set 04: Added first draft with all excercises

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
% you may want to try: {Liberation Serif} or {Times New Roman}
\setmainfont{FreeSerif}
% you may want to try: {Liberation Sans} or {Arial}
\setsansfont[Scale=MatchLowercase]{FreeSans}
% you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{FreeMono}

\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{blkarray}

\newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
% Commands for wrapping properly common expressions.
\newcommand{\Exp}{\mathrm{Exp}}
\newcommand{\Expect}{{\rm I\kern-.3em E}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\mc}{Μ.Α.Σ.Χ. }

% Main document
\begin{document}
\title{Στοχαστικές Ανελίξεις - 3ο πακέτο Ασκήσεων}
\author{Θωμάς Παππάς}
\date{}
\maketitle

\section*{Άσκηση 1}

Η $\{X(t),t\geq 0\}$ είναι \mc με χώρο καταστάσεων $S = \{0,1,2,\dots\}$.
Τώρα $\forall i \in S$ έχουμε ότι $q_{i,i+1} = \lambda$ (άφιξη πελάτη), ενώ για $i \geq 1$ για τα $q_{i,i-1}$ έχουμε
\begin{itemize}
	\item αν $i=1$ τότε εξυπηρετείτε ένας πελάτης ο οποίος θα εξυπηρετηθεί με ρυθμό $q_{1,0}=\mu$
	\item αν $i \geq 2$ τότε είτε θα τελειώσει η εξυπηρέτηση ενός πελάτη με ρυθμό $\mu$ είτε θα τελειώσει η υπομονή ενός τυχαίου πελάτη στο χώρο αναμονής με ρυθμό $\theta$, δηλαδή
	\[p_{i,i-1} \sim min\{\Exp(\mu), \Exp(\theta)\} = \Exp(\mu+\theta)\]
	και άρα $q_{i,i-1}=\mu+\theta$
\end{itemize}
\begin{center}
	\begin{tikzpicture}[
			node distance={15mm},
			main/.style = {draw, circle, minimum size=23pt},
			dots/.style = {minimum size=15pt}
		]
		\node[main] (1) {$0$};
		\node[main] (2) [right of=1] {$1$};
		\node[main] (3) [right of=2] {$2$};
		\node[dots] (4) [right of=3] {$\dots$};
		\draw[->] (1) to [out=45, in=135] node[above] {$\lambda$} (2);
		\draw[->] (2) to [out=225, in=315] node[below] {$\mu$} (1);
		\draw[->] (2) to [out=45, in=135] node[above] {$\lambda$} (3);
		\draw[->] (3) to [out=225, in=315] node[below] {$\mu+\theta$} (2);
		\draw[->] (3) to [out=45, in=135] node[above] {$\lambda$} (4);
		\draw[->] (4) to [out=225, in=315] node[below] {$\mu+\theta$} (3);
	\end{tikzpicture}
\end{center}
Στη συνέχεια για να βρούμε τη στάσιμη κατανομή θα πάρουμε $\forall j \in S\setminus \{0\}$ το\\
$A_j = \{0,1,2,\dots,j-1\}$ και από τις εξισώσεις γενικευμένης ισορροπίας έχουμε
\begin{itemize}
	\item για $j=1$: $p_0 \cdot q_{01} = p_1 \cdot q_{10} \Rightarrow p_0 \lambda = p_1 \mu \Rightarrow p_1 = \frac{\lambda}{\mu} p_0$
	\item για $j>1$: $p_{j-1} \cdot q_{j-1,j} = p_j \cdot q_{j,j-1} \Rightarrow p_{j-1} \lambda = p_j (\mu+\theta) \Rightarrow p_j = \frac{\lambda}{\mu+\theta} p_{j-1}$
\end{itemize}
Για το τελευταίο βλέπουμε ότι
\[
	p_j = \frac{\lambda}{\mu+\theta} p_{j-1} = \left(\frac{\lambda}{\mu+\theta}\right)^2 p_{j-2} = \cdots = \left(\frac{\lambda}{\mu+\theta}\right)^{j-1} p_1 = \left(\frac{\lambda}{\mu+\theta}\right)^{j-1} \frac{\lambda}{\mu} p_0
\]
Από εξίσωση κανονικοποίησης τώρα έχουμε ότι
\begin{equation}
	\label{eqreg1}
	\sum_{j=0}^\infty p_j = 1 \Rightarrow p_0 + p_1 + \sum_{j=2}^\infty p_j = 1 \Rightarrow p_0 \left(1 + \frac{\lambda}{\mu} + \sum_{j=2}^\infty \left(\frac{\lambda}{\mu+\theta}\right)^{j-1} \frac{\lambda}{\mu} \right) = 1
\end{equation}
Θέτουμε $r = \lambda/(\mu+\theta)$ και υπολογίζουμε το άθροισμα για $r<1$.
\[
	\sum_{j=2}^\infty r^{j-1} \stackrel{k=j-2}{=}  \sum_{k=0}^\infty r^{k+1} = r \sum_{k=0}^\infty r^k = r \left(\frac{1}{1-r}\right) = \frac{\lambda}{\mu+\theta} \cdot \frac{\mu+\theta}{\mu+\theta-\lambda} = \frac{\lambda}{\mu+\theta-\lambda}
\]
Οπότε συνεχίζοντας
\[
	\eqref{eqreg1} \Rightarrow p_0 \left(1 + \frac{\lambda}{\mu} + \frac{\lambda}{\mu} \cdot \frac{\lambda}{\mu+\theta-\lambda} \right) = 1
\]
Θέτουμε $B^{-1} = 1 + \frac{\lambda}{\mu} + \frac{\lambda}{\mu} \cdot \frac{\lambda}{\mu+\theta-\lambda}$ και βλέπουμε ότι $B^{-1} > 0$ οπότε και παίρνουμε
\[p_0 = B\]
Άρα η $\{X(t),t\geq 0\}$ είναι θετικά επαναληπτική αν και μόνον αν $\frac{\lambda}{\mu+\theta} < 1 \Rightarrow \lambda < \mu+\theta$ και η στάσιμη κατανομή της είναι η
\[
	p = [p_j]_{j=0,1,2,\dots} = \left[B, B \cdot \frac{\lambda}{\mu}, B \cdot \frac{\lambda}{\mu} \cdot \frac{\lambda}{\mu+\theta}, B \cdot \frac{\lambda}{\mu} \cdot \left(\frac{\lambda}{\mu+\theta}\right)^2, \dots\right]
\]

\section*{Άσκηση 2}

Βλέπουμε ότι αν $X(t) = i$ για κάποιο $t \geq 0$ τότε η κατάσταση θα αλλάξει είτε με την εξυπηρέτηση μιας ζήτησης είτε με την άφιξη νέας παραγγελίας.
Εφόσον και οι δύο διαδικασίες είναι εκθετικές και ανεξάρτητες μεταξύ τους και από τις προηγούμενες καταστάσεις, τότε η $\{X(t),t\geq 0\}$ είναι \mc
\\[8pt]
Ο χώρος καταστάσεων της αλυσίδας είναι $S = \{0,1,2,\dots,K+R\}$.
\begin{center}
	\begin{tikzpicture}[
			node distance={20mm},
			shorten >=1pt,
			main/.style = {draw, circle, minimum size=32pt, inner sep=1pt},
			dots/.style = {minimum size=15pt}
		]
		\node[main] (1) {$0$};
		\node[main] (2) [right of=1] {$1$};
		\node[main] (3) [right of=2] {$2$};
		\node[dots] (d34) [right of=3] {$\dots$};
		\node[main] (4) [right of=d34] {$R-1$};
		\node[main] (5) [right of=4] {$R$};
		\node[main] (6) [right of=5] {$R+1$};
		\node[dots] (d6) [right of=6] {$\dots$};
		\node[dots] (drl) [below=10mm of 1, xshift=-15mm] {$\dots$};
		\node[main] (7) [right of=drl] {$K-1$};
		\node[main] (8) [right of=7] {$K$};
		\node[main] (9) [right of=8] {$K+1$};
		\node[dots] (dkr) [right of=9] {$\dots$};
		\node[main] (10) [right of=dkr] [align=center]{\scriptsize$K+R$ \\ \scriptsize$-1$};
		\node[main] (11) [right of=10] {$K+R$};
		% Draw the lambda edges.
		\draw[->] (1) to [out=150, in=210, looseness=4] node[left] {$\lambda$} (1);
		\draw[->] (2) to node[above] {$\lambda$} (1);
		\draw[->] (3) to node[above] {$\lambda$} (2);
		\draw[->] (d34) to node[above] {$\lambda$} (3);
		\draw[->] (4) to node[above] {$\lambda$} (d34);
		\draw[->] (5) to node[above] {$\lambda$} (4);
		\draw[->] (6) to node[above] {$\lambda$} (5);
		\draw[->] (d6) to node[above] {$\lambda$} (6);
		\draw[->] (7) to node[above] {$\lambda$} (drl);
		\draw[->] (8) to node[above] {$\lambda$} (7);
		\draw[->] (9) to node[above] {$\lambda$} (8);
		\draw[->] (dkr) to node[above] {$\lambda$} (9);
		\draw[->] (10) to node[above] {$\lambda$} (dkr);
		\draw[->] (11) to node[above] {$\lambda$} (10);
		% Draw the theta edges.
		\draw[->] (1) to [out=315, in=135] node[above] {$\theta$} (8);
		\draw[->] (2) to [out=315, in=135] node[above] {$\theta$} (9);
		\draw[->] (3) to [out=315, in=135] node[above] {$\theta$} (dkr);
		\draw[->] (4) to node[right] {$\theta$} (10);
		\draw[->] (5) to node[right] {$\theta$} (11);
	\end{tikzpicture}
\end{center}
Τέλος ο πίνακας ρυθμών μετάβασης είναι ο
\[
	\begin{blockarray}{rcccccccccccc}
		& 0 & 1 & \dots & R-1 & R & \dots & K-1 & K & K+1 & \dots & K+R-1 & K+R \\
		\begin{block}{r(cccccccccccc)}
			0 & \lambda & 0 & \dots & 0 & 0 & \dots & 0 & \theta & 0 & \dots & 0 & 0 \\
			1 & \lambda & 0 & \dots & 0 & 0 & \dots & 0 & 0 & \theta & \dots & 0 & 0 \\
			2 & 0 & \lambda & \dots & 0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
			\vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
			R-1 & 0 & 0 & \dots & 0 & 0 & \dots & 0 & 0 & 0 & \dots & \theta & 0 \\
			R & 0 & 0 & \dots & \lambda & 0 & \dots & 0 & 0 & 0 & \dots & 0 & \theta \\
			R+1 & 0 & 0 & \dots & 0 & \lambda & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
			\vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
			K-1 & 0 & 0 & \dots & 0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
			K & 0 & 0 & \dots & 0 & 0 & \dots & \lambda & 0 & 0 & \dots & 0 & 0 \\
			K+1 & 0 & 0 & \dots & 0 & 0 & \dots & 0 & \lambda & 0 & \dots & 0 & 0 \\
			\vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots \\
			K+R-1 & 0 & 0 & \dots & 0 & 0 & \dots & 0 & 0 & 0 & \dots & 0 & 0 \\
			K+R & 0 & 0 & \dots & 0 & 0 & \dots & 0 & 0 & 0 & \dots & \lambda & 0 \\
		\end{block}
	\end{blockarray}
\]

\section*{Άσκηση 3}

Αρχικά θεωρούμε ότι $Y(t)=0$ για την περίπτωση όπου δεν υπάρχει κανένας πελάτης στο σύστημα και άρα δεν εξυπηρετείται κανένας.
\\[8pt]
Επίσης όταν βρισκόμαστε στην κατάσταση $(0,0)$ τότε για να εξετάσουμε τον τύπο του επόμενου πελάτη που θα φθάσει θεωρούμε την εκλέπτυνση Bernoulli της $\{X(t),t\geq 0\}$ με πιθανότητα επιτυχίας $\alpha$ και $1-\alpha$ αντίστοιχα, οπότε
\begin{itemize}
	\item ρυθμός προσέλευσης πελάτη τύπου $1 \sim \Exp(\alpha \lambda)$
	\item ρυθμός προσέλευσης πελάτη τύπου $2 \sim \Exp((1-\alpha) \lambda)$
\end{itemize}
ενώ από την κατάσταση $(1,1)$ η εξυπηρέτηση του πελάτη γίνεται με ρυθμό $\mu_i$ όπου $i$ ο τύπος του πελάτη.
\\[8pt]
Μετά για $X(t)>1$ έχουμε προσέλευση πελατών με διαδικασία Poisson με παράμετρο $\lambda$ εφόσον μπορούμε να ελέγξουμε για τον τύπο πελάτη όταν φτάσει η στιγμή να εξυπηρετηθεί.
Θεωρούμε λοιπόν ομοίως την εκλέπτυνση Bernoulli της $\{Y(t),t\geq 0\}$ με πιθανότητα επιτυχίας $\alpha$ και $1-\alpha$, οπότε παίρνουμε
\begin{itemize}
	\item ρυθμός εξυπηρέτησης πελάτη τύπου $i$ με τον επόμενο πελάτη να είναι τύπου $1 \sim \Exp(\alpha \mu_i)$
	\item ρυθμός εξυπηρέτησης πελάτη τύπου $i$ με τον επόμενο πελάτη να είναι τύπου $2$\\
		$\sim \Exp((1-\alpha) \mu_i)$
\end{itemize}
Βλέπουμε λοιπόν ότι σε κάθε περίπτωση η μετάβαση από μια κατάσταση σε μια άλλη γίνεται σε χρόνους εκθετικούς και ανεξάρτητους μεταξύ τους και με τις προηγούμενες καταστάσεις, και άρα η $((X(t),Y(t),t\geq 0)$ είναι \mc
\\[8pt]
Ο χώρος καταστάσεων της αλυσίδας είναι $S = \{(0,0)\} \cup \{(i,j)|i=1,2,\dots, j=1,2\}$.
\begin{center}
	\begin{tikzpicture}[
			node distance={25mm},
			shorten >=1pt,
			main/.style = {draw, circle, minimum size=23pt, inner sep=1pt},
			dots/.style = {minimum size=15pt}
		]
		\node[main] (00) {$0,0$};
		\node[main] (11) [right of=00] {$1,1$};
		\node[main] (21) [right of=11] {$2,1$};
		\node[main] (31) [right of=21] {$3,1$};
		\node[dots] (d1) [right of=31] {$\dots$};
		\node[main] (12) [below of=11] {$1,2$};
		\node[main] (22) [right of=12] {$2,2$};
		\node[main] (32) [right of=22] {$3,2$};
		\node[dots] (d2) [right of=32] {$\dots$};
		% Draw the client type 1 cases.
		\draw[->] (00) to [out=45, in=135] node[above] {$\alpha \lambda$} (11);
		\draw[->] (11) to node[below] {$\mu_1$} (00);
		\draw[->] (11) to [out=45, in=135] node[above] {$\lambda$} (21);
		\draw[->] (21) to node[below] {$\alpha \mu_1$} (11);
		\draw[->] (21) to [out=45, in=135] node[above] {$\lambda$} (31);
		\draw[->] (31) to node[below] {$\alpha \mu_1$} (21);
		\draw[->] (31) to [out=45, in=135] node[above] {$\lambda$} (d1);
		\draw[->] (d1) to node[below] {$\alpha \mu_1$} (31);
		% Draw the client type 2 cases.
		\draw[->] (00) to [out=270, in=180] node[left] {$(1-\alpha) \lambda$} (12);
		\draw[->] (12) to node[below] {$\mu_2$} (00);
		\draw[->] (12) to [out=315, in=225] node[below] {$\lambda$} (22);
		\draw[->] (22) to node[above] {\scriptsize$(1-\alpha) \mu_2$} (12);
		\draw[->] (22) to [out=315, in=225] node[below] {$\lambda$} (32);
		\draw[->] (32) to node[above] {\scriptsize$(1-\alpha) \mu_2$} (22);
		\draw[->] (32) to [out=315, in=225] node[below] {$\lambda$} (d2);
		\draw[->] (d2) to node[above] {\scriptsize$(1-\alpha) \mu_2$} (32);
		% Draw the intersections
		\draw[->] (21) to node[below right, sloped, pos=0.5] {\scriptsize$(1-\alpha) \mu_2$} (12);
		\draw[->] (22) to node[above right, sloped, pos=0.25] {\scriptsize$\alpha \mu_1$} (11);
		\draw[->] (31) to node[below right, sloped, pos=0.5] {\scriptsize$(1-\alpha) \mu_2$} (22);
		\draw[->] (32) to node[above right, sloped, pos=0.25] {\scriptsize$\alpha \mu_1$} (21);
		\draw[->] (d1) to node[below right, sloped, pos=0.5] {\scriptsize$(1-\alpha) \mu_2$} (32);
		\draw[->] (d2) to node[above right, sloped, pos=0.25] {\scriptsize$\alpha \mu_1$} (31);
	\end{tikzpicture}
\end{center}
Τέλος ο πίνακας ρυθμών μετάβασης είναι ο
\[
	\begin{blockarray}{cccccccccc}
		& (0,0) & (1,1) & (2,1) & (3,1) & \dots & (1,2) & (2,2) & (3,2) & \dots \\
		\begin{block}{c(ccccccccc)}
			(0,0) & 0 & \alpha \lambda & 0 & 0 & \dots & (1-\alpha) \lambda & 0 & 0 & \dots \\
			(1,1) & \mu_1 & 0 & \lambda & 0 & \dots & 0 & 0 & 0 & \dots \\
			(2,1) & 0 & \alpha \mu_1 & 0 & \lambda & \dots & (1-\alpha) \mu_2 & 0 & 0 & \dots \\
			(3,1) & 0 & 0 & \alpha \mu_1 & 0 & \dots & 0 & (1-\alpha) \mu_2 & 0 & \dots \\
			\vdots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots \\
			(1,2) & \mu_2 & 0 & 0 & 0 & \dots & 0 & \lambda & 0 & \dots \\
			(2,2) & 0 & \alpha \mu_1 & 0 & 0 & \dots & (1-\alpha) \mu_2 & 0 & \lambda & \dots \\
			(3,2) & 0 & 0 & \alpha \mu_1 & 0 & \dots & 0 & (1-\alpha) \mu_2 & 0 & \dots \\
			\vdots & \vdots & \vdots & \vdots & \vdots & \ddots & \vdots & \vdots & \vdots & \ddots \\
		\end{block}
	\end{blockarray}
\]

\section*{Άσκηση 4}

Ορίζουμε την αλυσίδα $\{(X(t),Y(t),t\geq 0\}$ όπου η $X(t)$ ο αριθμός των εργασιών που βρίσκονται στον υπολογιστή τη χρονική στιγμή $t$, και $Y(t)=0 \text{ ή } 1$ ανάλογα με το αν ο υπολογιστής είναι λειτουργικός ή όχι τη χρονική στιγμή $t$.
\\[8pt]
Βλέπουμε ότι αν $(X(t),Y(t)) = (i,j)$ για κάποιο $t$ τότε
\begin{itemize}
	\item αν $j=0$ ο υπολογιστής είναι χαλασμένος (και άρα και $i=0$) και είτε θα επισκευαστεί με ρυθμό $b$ είτε θα έρθει μια νέα εργασία με ρυθμό $\lambda$ (η οποία και θα χαθεί αμέσως)
	\item αν $j=1$ τότε ο υπολογιστής είναι λειτουργικός με $i$ εργασίες οπότε
		\begin{itemize}
			\item είτε θα διεκπεραιώσει μια εργασία με ρυθμό $\mu$
			\item είτε θα έρθει νέα εργασία με ρυθμό $\lambda$
			\item είτε θα χαλάσει ο υπολογιστής με ρυθμό $a$
		\end{itemize}
\end{itemize}
Όλες οι διαδικασίες τρέχουν σε εκθετικούς χρόνους ανεξάρτητους μεταξύ τους και από τις προηγούμενες καταστάσεις, και άρα η $\{(X(t),Y(t),t\geq 0\}$ είναι \mc
\\[8pt]
Ο χώρος καταστάσεων της αλυσίδας είναι $S = \{(0,0)\} \cup \{(i,1)|i=0,1,2,\dots\}$.
Για ευκολία στο συμβολισμό θα γράφουμε $-1$ αντί για $(0,0)$ και $i$ αντί για $(i,1)$.
\begin{center}
	\begin{tikzpicture}[
		node distance={20mm},
		shorten >=1pt,
		main/.style = {draw, circle, minimum size=23pt, inner sep=0pt},
		dots/.style = {minimum size=15pt}
	]
	\node[main] (m1) {$-1$};
	\node[main] (z) [right of=m1] {$0$};
	\node[main] (1) [right of=z] {$1$};
	\node[main] (2) [right of=1] {$2$};
	\node[dots] (d) [right of=2] {$\dots$};
	\draw[->] (m1) to [out=150, in=210, looseness=4] node[left] {$\lambda$} (m1);
	\draw[->] (m1) to [out=45, in=135] node[above] {$b$} (z);
	\draw[->] (z) to [out=225, in=315] (m1);
	\draw[->] (z) to [out=45, in=135] node[above] {$\lambda$} (1);
	\draw[->] (1) to node[below] {$\mu$} (z);
	\draw[->] (1) to [out=225, in=315] (m1);
	\draw[->] (1) to [out=45, in=135] node[above] {$\lambda$} (2);
	\draw[->] (2) to node[below] {$\mu$} (1);
	\draw[->] (2) to [out=225, in=315] (m1);
	\draw[->] (2) to [out=45, in=135] node[above] {$\lambda$} (d);
	\draw[->] (d) to node[below] {$\mu$} (2);
	\draw[->] (d) to [out=225, in=315] node[near start, below right] {$a$} (m1);
	\end{tikzpicture}
\end{center}
Τέλος ο πίνακας ρυθμών μετάβασης είναι ο
\[
	\begin{blockarray}{cccccc}
		& -1 & 0 & 1 & 2 & \dots \\
		\begin{block}{c(ccccc)}
			-1 & \lambda & b & 0 & 0 & \dots \\
			0 & a & 0 & \lambda & 0 & \dots \\
			1 & a & \mu & 0 & \lambda & \dots \\
			2 & a & 0 & \mu & 0 & \dots \\
			\vdots & \vdots & \vdots & \vdots & \vdots & \ddots \\
		\end{block}
	\end{blockarray}
\]

\end{document}

### 2021-05-28 stochastic/exer_set_04.tex
Stochastic: Exer Set 04: Final text and math improvements, submitted version

@@
 \begin{document}
-\title{Στοχαστικές Ανελίξεις - 3ο πακέτο Ασκήσεων}
+\title{Στοχαστικές Ανελίξεις - 4ο πακέτο Ασκήσεων}
 \author{Θωμάς Παππάς}
@@
 Η $\{X(t),t\geq 0\}$ είναι \mc με χώρο καταστάσεων $S = \{0,1,2,\dots\}$.
-Τώρα $\forall i \in S$ έχουμε ότι $q_{i,i+1} = \lambda$ (άφιξη πελάτη), ενώ για $i \geq 1$ για τα $q_{i,i-1}$ έχουμε
+$\forall i \in S$ έχουμε ότι $q_{i,i+1} = \lambda$ (άφιξη πελάτη), ενώ για $i \geq 1$ για τα $q_{i,i-1}$ έχουμε
 \begin{itemize}
-	\item αν $i=1$ τότε εξυπηρετείτε ένας πελάτης ο οποίος θα εξυπηρετηθεί με ρυθμό $q_{1,0}=\mu$
+	\item αν $i=1$ τότε εξυπηρετείτε ένας πελάτης με ρυθμό $q_{1,0}=\mu$
 	\item αν $i \geq 2$ τότε είτε θα τελειώσει η εξυπηρέτηση ενός πελάτη με ρυθμό $\mu$ είτε θα τελειώσει η υπομονή ενός τυχαίου πελάτη στο χώρο αναμονής με ρυθμό $\theta$, δηλαδή
@@
 Στη συνέχεια για να βρούμε τη στάσιμη κατανομή θα πάρουμε $\forall j \in S\setminus \{0\}$ το\\
-$A_j = \{0,1,2,\dots,j-1\}$ και από τις εξισώσεις γενικευμένης ισορροπίας έχουμε
+$A_j = \{0,1,2,\dots,j-1\}$ και άρα από τις εξισώσεις γενικευμένης ισορροπίας έχουμε
 \begin{itemize}
 	\item για $j=1$: $p_0 \cdot q_{01} = p_1 \cdot q_{10} \Rightarrow p_0 \lambda = p_1 \mu \Rightarrow p_1 = \frac{\lambda}{\mu} p_0$
-	\item για $j>1$: $p_{j-1} \cdot q_{j-1,j} = p_j \cdot q_{j,j-1} \Rightarrow p_{j-1} \lambda = p_j (\mu+\theta) \Rightarrow p_j = \frac{\lambda}{\mu+\theta} p_{j-1}$
+	\item για $j \geq 2$: $p_{j-1} \cdot q_{j-1,j} = p_j \cdot q_{j,j-1} \Rightarrow p_{j-1} \lambda = p_j (\mu+\theta) \Rightarrow p_j = \frac{\lambda}{\mu+\theta} p_{j-1}$
 \end{itemize}
@@
 \end{equation}
-Θέτουμε $r = \lambda/(\mu+\theta)$ και υπολογίζουμε το άθροισμα για $r<1$.
+Θέτουμε $r = \lambda/(\mu+\theta)$ και υπολογίζουμε το άθροισμα για $r<1$
 \[
-	\sum_{j=2}^\infty r^{j-1} \stackrel{k=j-2}{=}  \sum_{k=0}^\infty r^{k+1} = r \sum_{k=0}^\infty r^k = r \left(\frac{1}{1-r}\right) = \frac{\lambda}{\mu+\theta} \cdot \frac{\mu+\theta}{\mu+\theta-\lambda} = \frac{\lambda}{\mu+\theta-\lambda}
+	\sum_{j=2}^\infty r^{j-1} \stackrel{k=j-2}{=\joinrel=\joinrel=\joinrel=\joinrel=}  \sum_{k=0}^\infty r^{k+1} = r \sum_{k=0}^\infty r^k = r \left(\frac{1}{1-r}\right) = \frac{\lambda}{\mu+\theta} \cdot \frac{\mu+\theta}{\mu+\theta-\lambda} = \frac{\lambda}{\mu+\theta-\lambda}
 \]
@@
 \\[8pt]
-Ο χώρος καταστάσεων της αλυσίδας είναι $S = \{0,1,2,\dots,K+R\}$.
+Ο χώρος καταστάσεων της αλυσίδας είναι ο $S = \{0,1,2,\dots,K+R\}$
 \begin{center}
@@
 \end{center}
-Τέλος ο πίνακας ρυθμών μετάβασης είναι ο
+και ο πίνακας ρυθμών μετάβασης είναι ο
 \[
+	Q=
 	\begin{blockarray}{rcccccccccccc}
@@
 \\[8pt]
-Επίσης όταν βρισκόμαστε στην κατάσταση $(0,0)$ τότε για να εξετάσουμε τον τύπο του επόμενου πελάτη που θα φθάσει θεωρούμε την εκλέπτυνση Bernoulli της $\{X(t),t\geq 0\}$ με πιθανότητα επιτυχίας $\alpha$ και $1-\alpha$ αντίστοιχα, οπότε
+Επίσης όταν βρισκόμαστε στην κατάσταση $(0,0)$ τότε για να εξετάσουμε τον τύπο του επόμενου πελάτη που θα φθάσει θεωρούμε το διαχωρισμό Bernoulli της $\{X(t),t\geq 0\}$ με πιθανότητα επιτυχίας $\alpha$ και $1-\alpha$ αντίστοιχα, οπότε
 \begin{itemize}
@@
 \end{itemize}
-ενώ από την κατάσταση $(1,1)$ η εξυπηρέτηση του πελάτη γίνεται με ρυθμό $\mu_i$ όπου $i$ ο τύπος του πελάτη.
+Μετά για $X(t)>0$ έχουμε προσέλευση πελατών με διαδικασία Poisson με παράμετρο $\lambda$.
+Δεν υπάρχει λόγος να διαχωρίσουμε τον τύπο του πελάτη που έφθασε εφόσον μπορούμε να το ελέγξουμε τη στιγμή της εξυπηρέτησης.
 \\[8pt]
-Μετά για $X(t)>1$ έχουμε προσέλευση πελατών με διαδικασία Poisson με παράμετρο $\lambda$ εφόσον μπορούμε να ελέγξουμε για τον τύπο πελάτη όταν φτάσει η στιγμή να εξυπηρετηθεί.
-Θεωρούμε λοιπόν ομοίως την εκλέπτυνση Bernoulli της $\{Y(t),t\geq 0\}$ με πιθανότητα επιτυχίας $\alpha$ και $1-\alpha$, οπότε παίρνουμε
+Από την κατάσταση $(1,1)$ τώρα, εφόσον δεν υπάρχει πελάτης στο χώρο αναμονής η εξυπηρέτηση γίνεται με ρυθμό $\mu_i$, όπου $i$ ο τύπος του πελάτη.
+Μετά για $X(t)>1$ θα πρέπει να δούμε τον τύπο του πελάτη που θα εξυπηρετηθεί μετά τον τωρινό.
+Αφού και η $\{Y(t),t\geq 0\}$ είναι επίσης ακολουθία εκθετικά κατανεμημένων χρόνων, θεωρούμε ομοίως σε αυτή το διαχωρισμό Bernoulli με πιθανότητα επιτυχίας $\alpha$ και $1-\alpha$, οπότε και παίρνουμε
 \begin{itemize}
@@
 \end{itemize}
-Βλέπουμε λοιπόν ότι σε κάθε περίπτωση η μετάβαση από μια κατάσταση σε μια άλλη γίνεται σε χρόνους εκθετικούς και ανεξάρτητους μεταξύ τους και με τις προηγούμενες καταστάσεις, και άρα η $((X(t),Y(t),t\geq 0)$ είναι \mc
+Βλέπουμε λοιπόν ότι σε κάθε περίπτωση η μετάβαση από μια κατάσταση σε μια άλλη γίνεται σε χρόνους εκθετικούς και ανεξάρτητους μεταξύ τους και με τις προηγούμενες καταστάσεις, και άρα η $\{(X(t),Y(t)),t\geq 0\}$ είναι \mc
 \\[8pt]
-Ο χώρος καταστάσεων της αλυσίδας είναι $S = \{(0,0)\} \cup \{(i,j)|i=1,2,\dots, j=1,2\}$.
+Ο χώρος καταστάσεων της αλυσίδας είναι ο $S = \{(0,0)\} \cup \{(i,j)|i=1,2,\dots, j=1,2\}$.
 \begin{center}
@@
 \end{center}
-Τέλος ο πίνακας ρυθμών μετάβασης είναι ο
+και ο πίνακας ρυθμών μετάβασης είναι ο
 \[
+	Q =
 	\begin{blockarray}{cccccccccc}
@@
 \\[8pt]
-Βλέπουμε ότι αν $(X(t),Y(t)) = (i,j)$ για κάποιο $t$ τότε
+Βλέπουμε ότι αν $(X(t),Y(t)) = (i,j)$ για κάποιο $t \geq 0$ τότε
 \begin{itemize}
 	\item αν $j=0$ ο υπολογιστής είναι χαλασμένος (και άρα και $i=0$) και είτε θα επισκευαστεί με ρυθμό $b$ είτε θα έρθει μια νέα εργασία με ρυθμό $\lambda$ (η οποία και θα χαθεί αμέσως)
-	\item αν $j=1$ τότε ο υπολογιστής είναι λειτουργικός με $i$ εργασίες οπότε
+	\item αν $j=1$ τότε ο υπολογιστής είναι λειτουργικός με $i$ εργασίες οπότε θα συμβεί ένα από τα παρακάτω
 		\begin{itemize}
@@
 Όλες οι διαδικασίες τρέχουν σε εκθετικούς χρόνους ανεξάρτητους μεταξύ τους και από τις προηγούμενες καταστάσεις, και άρα η $\{(X(t),Y(t),t\geq 0\}$ είναι \mc
-\\[8pt]
-Ο χώρος καταστάσεων της αλυσίδας είναι $S = \{(0,0)\} \cup \{(i,1)|i=0,1,2,\dots\}$.
+\pagebreak\\
+Ο χώρος καταστάσεων της αλυσίδας είναι ο $S = \{(0,0)\} \cup \{(i,1)|i=0,1,2,\dots\}$.
 Για ευκολία στο συμβολισμό θα γράφουμε $-1$ αντί για $(0,0)$ και $i$ αντί για $(i,1)$.
@@
 	\draw[->] (m1) to [out=45, in=135] node[above] {$b$} (z);
-	\draw[->] (z) to [out=225, in=315] (m1);
+	\draw[->] (z) to [out=225, in=315] node[near start, below right] {$a$} (m1);
 	\draw[->] (z) to [out=45, in=135] node[above] {$\lambda$} (1);
 	\draw[->] (1) to node[below] {$\mu$} (z);
-	\draw[->] (1) to [out=225, in=315] (m1);
+	\draw[->] (1) to [out=225, in=315] node[near start, below right] {$a$} (m1);
 	\draw[->] (1) to [out=45, in=135] node[above] {$\lambda$} (2);
 	\draw[->] (2) to node[below] {$\mu$} (1);
-	\draw[->] (2) to [out=225, in=315] (m1);
+	\draw[->] (2) to [out=225, in=315] node[near start, below right] {$a$} (m1);
 	\draw[->] (2) to [out=45, in=135] node[above] {$\lambda$} (d);
@@
 \end{center}
-Τέλος ο πίνακας ρυθμών μετάβασης είναι ο
+Τέλος ο πίνακας ρυθμών μετάβασης της αλυσίδας είναι ο
 \[
+	Q =
 	\begin{blockarray}{cccccc}

### 2021-05-31 agt/ask02.tex
AGT: Exer02: All exercises apart from 4ii and 6iii
Problem 6 not very well analysed

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
  % you may want to try: {Liberation Serif} or {Times New Roman}
\setmainfont{FreeSerif}
  % you may want to try: {Liberation Sans} or {Arial}
\setsansfont[Scale=MatchLowercase]{FreeSans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{FreeMono}

\usepackage{mathtools}
% Required packages for plotting
\usepackage{pgfplots}
%\usepackage{pgfplotstable}
\pgfplotsset{compat=1.16}
%\usepackage{tikz}

\newcommand{\overeq}[1]{\stackrel{\text{#1}}{=}}
\newcommand{\vi}{\mathrm{v}}
\newcommand{\Expect}{{\rm I\kern-.3em E}}

% Main document
\begin{document}
\title{Αλγοριθμική Θεωρία Παιγνίων - 2η σειρά ασκήσεων}
\author{Θωμάς Παππάς}
%\date{}
\maketitle

\section*{Πρόβλημα 1}

\paragraph{(i)}
Αν $b_1,b_2$ οι προσφορές του κάθε παίκτη έχουμε
\[
	u_1(b_1,b_2) =
	\begin{cases}
		K-b_1 & b_1>b_2\\
		K/2-b_1 & b_1=b_2\\
		-b_1 & b_1<b_2
	\end{cases}
	\quad\quad
	u_2(b_1,b_2) =
	\begin{cases}
		K-b_2 & b_2>b_1\\
		K/2-b_2 & b_2=b_1\\
		-b_2 & b_2<b_1
	\end{cases}
\]

\paragraph{(ii)}
Έστω $(b_1,b_2)$ μια στρατηγική του παιγνίου, θα δείξουμε ότι πάντα υπάρχει μια καλύτερη στρατηγική για τουλάχιστον έναν από τους δύο παίκτες.
\begin{itemize}
	\item αν $b_1<b_2$ τότε ο π.2 έχει καλύτερη στρατηγική την προσφορά $b_2^\prime=b_2-(b_2-b_1)/2$ αφού εφόσον $b_1<b_2^\prime<b_2$ άρα
		\[u_2(b_2,b_2)=K-b_2<K-b_2+\frac{b_2-b_1}{2}=K-b_2^\prime=u_2(b_1,b_2^\prime)\]
		Ομοίως και η περίπτωση $b_2<b_1$ για τον π.1 λόγω συμμετρικότητας του προβλήματος
	\item αν $b_1=b_2$ τότε για οποιονδήποτε παίκτη (εδώ θα πάρουμε τον π.1) διακρίνουμε τις εξής περιπτώσεις
		\begin{itemize}
			\item αν $b_1<K/2$ τότε για  $b_1^\prime=b_1+K/2$ έχουμε $b_1^\prime>b_1$ και $u_1(b_1^\prime,b_2) = K-b_1^\prime = K/2-b_1$ και άρα
				\[u_1(b_1,b_2)=K/2-b_1<K/2-b_1^\prime=u_1(b_1^\prime,b)\]
			\item αν $b_1>K/2$ τότε $u_1(b_1,b_2)=K/2-b_1<0$ και άρα για $b_1^\prime=0$ παίρνουμε
				\[u_1(b_1,b_2)<0=u_1(b_1^\prime,b_2)\]
		\end{itemize}
\end{itemize}
Συνεπώς το παίγνιο δεν έχει σημεία ισορροπίας.

\pagebreak

\section*{Πρόβλημα 2}

Ο αλγόριθμος που περιγράφει η άσκηση είναι μονότονος διότι αποτελείται από δύο διαδικασίες που η καθεμιά είναι μονότονη.
\\[8pt]
Στην 1η φάση η ανάθεση λειτουργεί όπως μια Knapsack δημοπρασία και άρα είναι μονότονη.
Το ίδιο ισχύει και για τη 2η φάση αν τη δούμε μεμονωμένα.
Τώρα αν ένας παίκτης που έχει κερδίσει στη 2η φάση αυξήσει την προσφορά του, τότε η μόνη αλλαγή που ενδέχεται να γίνει είναι να ανέβει στην κατάταξη του άπληστου αλγόριθμου και να κερδίσει στην 1η φάση, όπου και πάλι παραμένει κερδισμένος.
\\[8pt]
Άρα και στο σύνολό του ο αλγόριθμος είναι μονότονος.

\section*{Πρόβλημα 3}

Θα θέσουμε μηχανισμό όπου ο η εισφορά του κάθε δημότη θα είναι το κομμάτι της εκτίμησης τους που συνεισφέρει στο συνολικό άθροισμα να φτάσει το στόχο $C$, δηλαδή αν $b=(b_1,b_2,\dots,b_n)$ οι προσφορές από τους δημότες τότε
\[
	p_i =
	\begin{dcases}
		max\{C-\sum_{j\neq i}b_j,0\} & \sum_{i=1}^n b_i \geq C\\
		0 & \sum_{i=1}^n b_i < C
	\end{dcases}
\]
Θα δείξουμε ότι ο μηχανισμός αυτός είναι φιλαλήθης.
Αρχικά βλέπουμε ότι για ένα σύνολο προσφορών $b$ αν το πάρκο χτιστεί τότε $u_i(b)= \vi_i-p_i$ ενώ αν δεν χτιστεί τότε $u_i(b)=0$.
\\[8pt]
Στην περίπτωση που $\sum_{j\neq i}^n b_j \geq C$ τότε $\forall b_i$ το πάρκο θα χτιστεί με $p_i=0$ και $u_i(b) = u_i(\vi_i,b_{-i}) = \vi_i-0 = \vi_i$.
\\[8pt]
Τώρα αν $\sum_{j\neq i}^n b_j < C$ έχουμε
\begin{itemize}
	\item αν $\vi_i+\sum_{j\neq i}^n b_j < C$ τότε το πάρκο δεν θα χτιστεί με $b_i=\vi_i$, ενώ αν $b_i$ αρκετά μεγάλο ώστε το πάρκο να χτιστεί τότε
		\[u_i(b)=\vi_i-p_i=\vi_i-C+\sum_{j\neq i} b_j < 0 = u_i(\vi_i,b_{-i})\]
	\item αν $\vi_i+\sum_{j\neq i}^n b_j \geq C$ τότε το πάρκο θα χτιστεί με $b_i=\vi_i$ με
		\[u_i(\vi_i,b_{-i}) = \vi_i-p_i = \vi_i-C+\sum_{j\neq i} b_j > 0\]
		όπου $0$ είναι το $u_i$ στην περίπτωση που το $b_i$ είναι αρκετά μικρό ώστε το πάρκο να μην χτιστεί
\end{itemize}
Άρα σε κάθε περίπτωση η στρατηγική $(\vi_i,b_{-i})$ μεγιστοποιεί την ωφέλεια του $i$ παίκτη, και άρα ο μηχανισμός είναι φιλαλήθης.

\pagebreak

\section*{Πρόβλημα 4}

\paragraph{(i)}
Θα σχεδιάσουμε μηχανισμό όπου ο κάθε παίκτης θα κερδίζει ωφέλεια ανάλογα με το πόσο συνεισέφερε στο να ελαχιστοποιηθεί η συνολική αξία του ελάχιστου συνδετικού δέντρου σε σχέση με το αν δεν χρησιμοποιούσαμε την ακμή του.
Ορίζουμε λοιπόν ως $T_{-e}$ το ελάχιστο συνδετικό δέντρο που θα πάρουμε εάν δεν χρησιμοποιήσουμε την ακμή $e$.
Αυτό πάντα υπάρχει αφού το $G$ δεν έχει γέφυρες.
\\[8pt]
Επίσης για διευκόλυνση στους ορισμούς θέτουμε ως $u(S)$ την αξία ενός δέντρου, δηλαδή αν $S \subseteq E$ δέντρο τότε
\[u(S) = \sum_{e \in S} b_e\]
\\[8pt]
Οπότε για ένα σύνολο προσφορών $b=\{b_e\}_{e\in E}$ και ελάχιστο συνδετικό δέντρο $T$ ορίζουμε τις αμοιβές ως εξής
\[p_e = u(T_{-e}) - u(T \setminus \{e\})\]
Θα δείξουμε τώρα ότι ο αυτός ο μηχανισμός είναι φιλαλήθης.
Έστω ότι έχουμε $b=(c_e,b)$ σύνολο προσφορών όπου το παίκτης $A_e$ δηλώνει την πραγματική του αξία.
\\[8pt]
Στην περίπτωση που $e \notin T$ τότε έχουμε $p_e = 0$ αφού $T_{-e}=T$ και $T \setminus \{e\} = T$, και άρα $u_e(c_e,b_{-e}) = 0$.
Προφανώς το ίδιο ισχύει και για κάθε $b_e>c_e$.
Έστω τώρα ότι ο $A_e$ επέλεγε να δηλώσει $b_e<c_e$ έτσι ώστε $e\in T$.
Εφόσον αρχικά είχαμε $e \notin T$ αυτό σημαίνει ότι αν πάρουμε $T_e = \min_{u(T)}\{T|e\in T\}$ τότε έχουμε $u(T) \leq u(T_e)$ και με την $b_e$ δήλωση ο $A_e$ κερδίζει ωφέλεια
\begin{align*}
	u_e(b_e,b_{-e}) = p_e - c_e &= u(T_{-e}) - u(T_e \setminus\{e\}) -c_e = u(T) - u(T_e) \leq 0\\
		&\Rightarrow u_e(b_e,b_{-e}) \leq u_e(c_e,b_{-e})
\end{align*}
Μετά στην περίπτωση που $e\in T$ τότε
\[u_e(c_e,b_{-e}) = p_e - c_e = u(T_{-e}) - u(T\setminus \{e\}) - c_e = u(T_{-e}) - u(T)\]
και εφόσον $T$ ελάχιστο συνδετικό δέντρο τότε $u(T) \leq u(T_{-e})$ και άρα $u_e(c_e,b_{-e}) \geq 0$.
Προφανώς και για κάθε $b_e$ τέτοιο ώστε $e \in T$ η αμοιβή δεν αλλάζει αφού είναι ανεξάρτητη του $b_e$, ενώ για $b_e > c_e$ σε σημείο που $e \notin T$ τότε $u_e(b_e,b_{-e}) = 0 \leq u_e(c_e,b_{-e})$.
\\[8pt]
Άρα έχουμε πάντα $u_e(b_e,b_{-e}) \leq u_e(c_e,b_{-e})$ και άρα ο μηχανισμός είναι φιλαλήθης.

%\paragraph{(ii)}
%Η ιδιότητα που θα πρέπει να έχει το γράφημα $G$ ώστε ο παραπάνω αλγόριθμος να είναι φιλαλήθης είναι ότι καμία ακμή $e$ δεν είναι γέφυρα.

\paragraph{(iii)}
Αν οι παίκτες μπορεί να έχουν στην κατοχή τους περισσότερες από μία ακμές τότε γενικεύουμε τους ορισμούς ως εξής
\begin{itemize}
	\item ο παίκτης $A_S$ έχει ένα σύνολο ακμών $S \subseteq E$
	\item $T_S \subseteq S$ είναι το σύνολο ακμών του $A_S$ που συμμετέχουν στο $T$ 
		\begin{itemize}
			\item αν δεν συμμετέχει καμία τότε $T_S=\emptyset$
		\end{itemize}
	\item $T_{-S}$ είναι το ελάχιστο συνεκτικό δέντρο που θα πάρουμε αν δεν χρησιμοποιήσουμε κάποια ακμή από το $S$
\end{itemize}
Τότε η αμοιβή προσαρμόζεται ως εξής
\[p_S = u(T_{-S}) - u(T \setminus S) = u(T_{-S}) - u(T \setminus T_S)\]
και αντίστοιχα, εφόσον ο παίκτης θα χρεωθεί μόνο το κόστος των ακμών που συνεισέφεραν στο $T$, η ωφέλειά του γίνεται
\[u_S = p_S - \sum_{e\in T_S} c_e = u(T_{-S}) - u(T \setminus T_S) -  \sum_{e\in T_S} c_e = u(T_{-S}) - u(T)\]
Η ιδιότητα τώρα που πρέπει να έχει το γράφημα ώστε ο παραπάνω μηχανισμός να είναι φιλαλήθης, είναι ότι για κάθε $S$ σύνολο ακμών ενός παίκτη το $G(V,E \setminus S)$ θα πρέπει να παραμένει συνεκτικό.
Με άλλα λόγια δεν γίνεται ένας παίκτης να ελέγχει σύνολο ακμών που περιέχουν τουλάχιστον μια ακμή από κάθε δέντρο του γραφήματος.

\section*{Πρόβλημα 5}

\paragraph{Για δύο παίκτες} θα ξεκινήσουμε βρίσκοντας το $SW^*=\max SW$ για κάθε περίπτωση.
Για το συνολικό $SW$ εφόσον δεν μπορούμε να πετύχουμε θετική αποτίμηση και για τους δύο παίκτες τότε έχουμε $SW=1$ με τις εξής βέλτιστες αναθέσεις
\[
	S^1=(\{a,b\},\emptyset) \qquad S^2=(\emptyset,\{a,b\}) \qquad S^3=(\emptyset,\{a\})
\]
Μετά στις μεμονωμένες περιπτώσεις προφανώς πετυχαίνουμε $SWM$ δίνοντας όλα τα αντικείμενα στον εκάστοτε παίκτη, οπότε εντέλει έχουμε
\[
	SW^* = 1 \qquad SW^*_{-1} = 1 \qquad SW^*_{-2} = 1
\]
Τώρα υπολογίζουμε τις πληρωμές.
Θεωρούμε ότι έχουμε την ανάθεση $S^1=(\{a,b\},\emptyset)$.
Τότε
\[
	\begin{aligned}
		p_1 &= SW^*_{-1} - v_2(\emptyset)\\
			&= 1-0\\
			&= 1
	\end{aligned}
	\qquad\qquad
	\begin{aligned}
		p_2 &= SW^*_{-2} - v_1(\{a,b\})\\
			&= 1-1\\
			&= 0
	\end{aligned}
\]
Οι πληρωμές βγαίνουν αντίστροφα $p_1=0,p_2=1$ στις αναθέσεις $S^2,S^3$.

\paragraph{Για τρεις παίκτες} βλέπουμε ότι μπορούμε να πετύχουμε $SW^*=2$ με την ανάθεση $S=(\emptyset,\{a\},\{b\})$.
Μετά έχουμε
\begin{itemize}
	\item $SW^*_{-1} = 2$ με την ανάθεση $(\{a\},\{b\})$
	\item $SW^*_{-2} = 1$ αντίστοιχα με το προηγούμενο ερώτημα
	\item $SW^*_{-3} = 1$ από το προηγούμενο ερώτημα
\end{itemize}
και άρα οι πληρωμές γίνονται
\[
	\begin{aligned}
		p_1 &= SW^*_{-1} - v_2(\{a\}) - v_3(\{b\})\\
			&= 2-1-1\\
			&= 0
	\end{aligned}
	\qquad
	\begin{aligned}
		p_2 &= SW^*_{-2} - v_1(\emptyset) - v_3(\{b\})\\
			&= 1-0-1\\
			&= 0
	\end{aligned}
	\qquad
	\begin{aligned}
		p_3 &= SW^*_{-3} - v_1(\emptyset) - v_2(\{a\})\\
			&= 1-0-1\\
			&= 0
	\end{aligned}
\]
Τέλος για τις πληρωμές παρατηρούμε ότι ακόμα και οι παίκτες που συνεισφέρουν στο $SW^*$ καταλήγουν μην πληρώνουν τίποτα.
Αυτό διότι η συνεισφορά τους είναι ίση με την αποτίμηση που κερδίζουν.

\section*{Πρόβλημα 6}

Έτσι ώστε ο μηχανισμός να μεγιστοποιεί την κοινωνική ωφέλεια θα πρέπει να γίνεται βέλτιστη ανάθεση των κομματιών σοκολάτας στους παίκτες, οπότε ο αλγόριθμος ανάθεσης θα λειτουργεί ως εξής
\begin{itemize}
	\item ταξινομούμε τους παίκτες έτσι ώστε $b_{i_1}/w_{i_1} > b_{i_2}/w_{i_2} > \dots > b_{i_n}/w_{i_n}$
	\item λύνουμε το \textrm{Subset Sum} πρόβλημα για κάθε παίκτη με την παραπάνω σειρά για τα αντικείμενα που έχουν μείνει και του αναθέτουμε τη λύση
	\item συνεχίζουμε μέχρι να τελειώσουν τα αντικείμενα ή αν περάσουμε όλους τους παίκτες
\end{itemize}
Εφόσον το \textrm{Subset Sum} είναι NP-complete πρόβλημα τότε ο παραπάνω αλγόριθμος δεν είναι πολυωνυμικά αποδοτικός, εκτός κι αν τον προσεγγίζουμε πολυωνυμικά.
\\[8pt]
Για την πληρωμή τώρα, έστω $S$ η βέλτιστη ανάθεση και $S_{-i}$ η βέλτιστη ανάθεση χωρίς τον παίκτη $i$.
Οπότε έχουμε
\[p_i = u(S) - \sum_{j \neq i} b_j \cdot w_j\]
Ο μηχανισμός είναι φιλαλήθης με $u_i(\vi_i,b_{-i}) \geq 0 $ άρα για ο κάθε μεμονωμένος παίκτης έχει $u_i \geq 0$ και άρα ο μηχανισμός είναι και individually rational.

\paragraph{(ii)} Αν εφαρμόσουμε τη λύση του (i) στην παραλλαγή του προβλήματος εδώ τότε το \textrm{Subset Sum} θα επιστρέφει πάντα την greedy λύση.
Μπορούμε αντί αυτού να κοιτάζουμε απευθείας για κάθε παίκτη αν τα κομμάτια που έχουν μείνει είναι $\geq w_i$ και αν ναι να του αναθέτουμε $w_i$ κομμάτια.
Με αυτόν τον τρόπο κρατάμε τις ιδιότητες του προηγούμενου (φιλαλήθης, μεγιστοποίηση κοινωνικής ωφέλειας, individually rational) ενώ έχουμε αποδοτικό αλγόριθμο που να τον υπολογίζει.

\section*{Πρόβλημα 7}

\paragraph{(i)}
Θέτω τις εξής τυχαίες μεταβλητές
\begin{itemize}
	\item $X_1,X_2$: οι προσφορές του π.1 και π.2 αντίστοιχα, $X_1,X_2 \sim U(0,1)$
	\item $X_m = \min\{X_1,X_2\}$
	\item $R$ το κέρδος της δημοπρασίας
\end{itemize}
Προφανώς εδώ $R=X_m$, οπότε θα υπολογίσουμε την αναμενόμενη τιμή της $X_m$
\begin{align*}
	F_{X_m}(x) &= P(X_m \leq x) = 1-P(X_m \geq x)\\
		&= 1-P(X_1 \geq x) \cdot P(X_2 \geq x) &\\
		&=1-(1-P(X_1<x))(1-P(X_2<x)) = 1-(1-x)(1-x) = 2x-x^2\\
	f_{X_m}(x) &= \frac{d}{dx}F_{X_m}(x) = 2-2x\\
	\Expect[X_m] &= \int_0^1 x \cdot f_{X_m}(x) dx = \int_0^1 2x-2x^2 dx = \left[x^2-\frac23 x^3\right]_0^1 = 1-\frac23 = \frac13
\end{align*}
Άρα όντως το αναμενόμενο κέρδος από τη δημοπρασία Vickrey είναι $1/3$.

\paragraph{(ii)}
Θεωρούμε την τυχαία μεταβλητή $X_M = max\{X_1,X_2\}$.
Με reserve price το $1/2$ έχουμε ότι το αναμενόμενο κέρδος είναι η αναμενόμενη τιμή του $X_m$ όταν $X_m \geq 1/2$ και $1/2$ όταν $X_m<1/2$ και $X_M \geq 1/2$. Δηλαδή
\[
	\Expect[R] = \Expect \left[X_m|X_m \geq 1/2\right] \cdot P(X_m\geq 1/2)) + 1/2 \cdot P \left(X_M>1/2,X_m<1/2\right)
\]
Για το $\Expect[X_m|X_m \geq 1/2]$ μπορούμε να δούμε ότι με δεδομένο ότι $X_m\geq 1/2$ τότε το πείραμα επαναλαμβάνεται στο διάστημα $[1/2,1]$.
Οπότε αν ξεκινήσουμε από το $1/2$ τότε η αναμενόμενη τιμή θα είναι αναλογικά το $1/3$ του διαστήματος $[1/2,1]$, δηλαδή
\[
	\Expect \left[X_m|X_m \geq 1/2\right] = \frac12 + \frac13 \left(1-\frac12\right) = \frac12 + \frac16 = \frac23
\]
Για το δεύτερο μέρος τώρα έχουμε
\begin{align*}
	P \left(X_M>1/2,X_m<1/2\right) &= P(X_1>1/2,X_2<1/2) + P(X_2>1/2,X_1<1/2) &\\
		&\stackrel{X_1,X_2 \textrm{ ανεξ.}}{=\joinrel=\joinrel=\joinrel=\joinrel=} P(X_1>1/2) \cdot P(X_2<1/2) + P(X_2>1/2) \cdot P(X_1<1/2)\\
		&=\frac12 \cdot \frac12 + \frac12 \cdot \frac12 = \frac12
\end{align*}
Οπότε εφόσον επίσης $P(X_m\geq 1/2) = 1-P(X_m<1/2) = 1-2\cdot\frac12+(\frac12)^2 = 1/4$ εντέλει παίρνουμε
\[
	\Expect[R] = \frac23 \cdot \frac14 + \frac12 \cdot \frac12 = \frac5{12}
\]
Άρα το επιπλέον κέρδος που πήραμε χρησιμοποιώντας reserve price το $1/2$ είναι $\frac5{12}-\frac13=\frac1{12}$.

\paragraph{(iii)}
Θέτω $Y_2$ τ.μ. για τη μεσαία τιμή ανάμεσα στις $X_1,X_2,X_3$.
Για την $F_{Y_2}(y)$ τώρα αρκεί να παρατηρήσουμε ότι η μεσαία τιμή είναι $<y$ όταν είτε και οι τρεις προσφορές είναι $<y$ είτε είναι μόνο οι δύο από αυτές.
Εφόσον $X_1,X_2,X_3$ ανεξάρτητες τότε έχουμε
\begin{align*}
	&F_{Y_2}(y) &= P(Y_2 \leq y) = &P(X_1 \leq y,X_2 \leq y,X_3 \leq y) + P(X_1 \leq y,X_2 \geq y,X_3 > y) \\
		&&&+ P(X_1 \leq y,X_2 > y,X_3 \leq y) + P(X_1 > y,X_2 \geq y,X_3 \leq y)\\
		&&\stackrel{\textrm{ ανεξ.}}{=\joinrel=\joinrel=}& P(X_1 \leq y)P(X_2 \leq y)P(X_3 \leq y) + P(X_1 \leq y)P(X_2 \geq y)P(X_3 > y) \\
		&&&+ P(X_1 \leq y)P(X_2 > y)P(X_3 \leq y) + P(X_1 > y)P(X_2 \geq y)P(X_3 \leq y)\\
		&&=&y^3+3y^2(1-y) = -2y^3+3y^2
\end{align*}
\begin{align*}
	f_{Y_2}(y) &= \frac{d}{dy}F_{X_2}(y) = -6y^2+6y\\
	\Expect[Y_2] &= \int_0^1 y f_{Y_2}(y) dy = \int_0^1 y (-6y^2+6y) dy = \int_0^1 -6y^2+6y^2\\
		&= \left[-\frac64 y^4 + 2y^3\right]_0^1 = -\frac32 + 2 = \frac12
\end{align*}

\section*{Πρόβλημα 8}
Αρχικά έχουμε ότι
\[f(z) = \frac{d}{dz}F(z) = \frac1{(z+1)^{2c}}\]
οπότε και το virtual valuation function $\phi(z)$ θα είναι
\[\phi(z) = z - \frac{1-F(z)}{f(z))} = z - \frac{1/(z+1)^c}{1/(z+1)^{2c}} = z - (z+1)^c\]
Τώρα για να είναι η κατανομή αυτή regular θα πρέπει να είναι μη-φθίνουσα, δηλαδή
\[\frac{d}{dz}\phi(z) \geq 0, \forall z \in [0,\infty)\]
Έχουμε $\frac{d}{dz}\phi(z) = 1-c(z+1)^{c-1}$.
Για $z=0$ παίρνουμε
\[\frac{d}{dz}\phi(0) \geq 0 \Rightarrow 1 - c \cdot 1^{c-1} \geq 0 \Rightarrow 1-c \leq 0 \Rightarrow c \leq 1\]
Όντως αν $c\leq 1$ βλέπουμε ότι
\begin{align*}
	c \leq 1 &\Rightarrow c-1 \leq 0 \stackrel{z+1\geq 1}{=\joinrel=\joinrel=\joinrel\Rightarrow} (z+1)^{c-1} \leq (z+1)^0 \Rightarrow (z+1)^{c-1} \leq 1\\
		&\stackrel{c \geq 0}{=\joinrel\Rightarrow} c(z+1)^{c-1} \leq c \stackrel{c \leq 1}{=\joinrel=\joinrel\Rightarrow} c(z+1)^{c-1} \leq 1 \Rightarrow 1-c(z+1)^{c-1} \geq 0\\
		&\Rightarrow \frac{d}{dz}\phi(z) \geq 0
\end{align*}
Άρα όντως η κατανομή είναι φθίνουσα για $c \leq 1$.

\end{document}

### 2021-06-07 del/8_expressivity_pres.tex
DEL: Presentation: First presentable version of chapter 8, Expressivity
Also included .gitignore for latex generated files

\documentclass{beamer}
\mode<presentation>
{
	\usetheme[progressbar=foot,numbering=fraction,background=light,block=fill]{metropolis} 
	\usecolortheme{default} % or try albatross, beaver, crane, ...
	\usefonttheme{serif}  % or try serif, structurebold, ...
	\setbeamertemplate{navigation symbols}{}
	\setbeamertemplate{caption}[numbered]
	%\setbeamertemplate{frame footer}{My custom footer}
}

\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{stmaryrd}
\usepackage{tikz}

\setlist[itemize]{noitemsep, topsep=-2pt, label=\textbullet}
\graphicspath{ {./figures/} }

\newcommand{\lang}{\mathcal{L}}

% Main document
\begin{document}
\title{Expressivity}
\subtitle{Dynamic Epistemic Logic}
\author[Pappas]{Thomas Pappas}
%\date{}
\maketitle

\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{5pt}
\setlength{\abovedisplayshortskip}{0pt}
\setlength{\belowdisplayshortskip}{0pt}

%\begin{frame}{Agenda}
  %\tableofcontents[hideallsubsections]
  %\tableofcontents
%\end{frame}

%\AtBeginSection{}

\section{Expressive power}

\begin{frame}{Expressive power}
	We'll try to answer these questions
	\begin{itemize}
		\item Which properties can be expressed with which languages and which cannot be expressed?
		\item How are languages related wrt expressivity?
	\end{itemize}
\end{frame}

\begin{frame}{Equivalence}
	\begin{block}{Definition 8.1 (Equivalence)}
		Two formulas $\phi$ and $\psi$ are \textit{equivalent} iff they are true in the same states. We denote this as $\phi \equiv \psi$
	\end{block}
\end{frame}

\begin{frame}{Expressive power}
  \begin{block}{Definition 8.2 (Expressive power)}
  	Given two logical languages $\lang_1$ and $\lang_2$ that are interpreted in the same class of models
  	\begin{itemize}
  		\item $\lang_2$ is \textit{at least as expressive} as $\lang_1$ ($\lang_1 \preceq \lang_2$)\\
  			if and only if for every formula $\phi_1 \in \lang_1$ there is a formula $\phi_2 \in \lang_2$ such that $\phi_1 \equiv \phi_2$ \pause
  		\item $\lang_1$ and $\lang_2$ are equally expressive ($\lang_1 \equiv \lang_2$)\\
  			if and only if $\lang_1 \preceq \lang_2$ and $\lang_2 \preceq \lang_1$ \pause
  		\item $\lang_2$ is more expressive than $\lang_1$ ($\lang_1 \prec \lang_2$)\\
  			if and only if $\lang_1 \preceq \lang_2$ but $\lang_1 \not\equiv \lang_2$
  	\end{itemize}
  \end{block}
\end{frame}

\begin{frame}{Expressive power: Example 1}
	Given the following languages for a countable set of propositional variables $P$
	\begin{flalign*}
		\lang_{PL} &\\
			&\phi ::= p | \neg \phi | \left(\phi \wedge \phi\right) | \left(\phi \vee \phi\right) | \left(\phi \rightarrow \phi\right) | \left(\phi \leftrightarrow \phi\right)\\
		\lang_{NAND} &\\
			&\phi ::= p | \left(\phi \barwedge \phi\right)
	\end{flalign*}
	what relation do they have wrt Expressive power?
\end{frame}

\begin{frame}{Expressive power: Example 1}
	\begin{scriptsize}
	\begin{block}{\scriptsize Theorem 8.4}
		\[\lang_{PL} \equiv \lang_{NAND}\] \pause
		\textbf{Proof.}
		\begin{itemize}
			\item $\lang_{NAND} \preceq \lang_{PL}$
				\begin{align*}
					& & t(p) &= p\\
					\phi \barwedge \psi &\equiv \neg (\phi \wedge \psi) & t(\phi \barwedge \psi) &= \neg (t(\phi) \wedge t(\psi))
				\end{align*}
			\item $\lang_{PL} \preceq \lang_{NAND}$
				\begin{align*}
				& & t(p) &= p\\
					\neg \phi &\equiv (\phi \barwedge \psi) & t(\neg \phi) &= (t(\phi) \barwedge t(\psi))\\
					\phi \wedge \psi &\equiv (\phi \barwedge \psi) \barwedge (\phi \barwedge \psi) & t(\phi \wedge \psi) &= (t(\phi) \barwedge t(\psi)) \barwedge (t(\phi) \barwedge t(\psi))\\
					\phi \vee \psi &\equiv (\phi \barwedge \phi) \barwedge (\psi \barwedge \psi) & t(\phi \vee \psi) &= (t(\phi) \barwedge t(\phi)) \barwedge (t(\psi) \barwedge t(\psi))\\
					\phi \rightarrow \psi &\equiv \phi \barwedge (\psi \barwedge \psi) & t(\phi \rightarrow \psi) &= t(\phi) \barwedge (t(\psi) \barwedge t(\psi))\\
					\phi \leftrightarrow \psi &\equiv (\phi \barwedge \psi) \barwedge (\phi \barwedge \phi) \barwedge (\psi \barwedge \psi) & t(\phi \leftrightarrow \psi) &= \dots 
						%(t(\phi) \barwedge t(\psi)) \barwedge (t(\phi) \barwedge t(\phi)) \barwedge (t(\psi) \barwedge t(\psi))
				\end{align*}
		\end{itemize}
		Show that $\phi \equiv t(\phi)$ for every formula $\phi \in \lang_{PL}$ (and $\phi \in \lang_{NAND}$ respectively) by induction on $\phi$.
	\end{block}
	\end{scriptsize}
\end{frame}

\begin{frame}{Expressive power: Example 2}
	\begin{flalign*}
		\lang_{\text{even}} &\\
			&\phi ::= p | \left(\phi \triangledown \phi\right) | \left(\phi \leftrightarrow \phi\right)\\
		\lang_{\wedge\vee} &\\
			&\phi ::= p | \left(\phi \wedge \phi\right) | \left(\phi \vee \phi\right)
	\end{flalign*}
	\begin{block}{Theorem 8.5}
		$\lang_{\text{even}} \prec \lang_{PL}$
	\end{block}
	\begin{block}{Exercise 8.6}
		$\lang_{\text{even}} \not\preceq \lang_{\wedge\vee}$ and $\lang_{\wedge\vee} \not\preceq \lang_{\text{even}}$
	\end{block}
\end{frame}

\section*{Bisimulation}

\begin{frame}{Bisimulation}
	\begin{block}{Theorem 2.15}
		For all pointed models $(M,s)$ and $(M^\prime,s^\prime)$, if $(M,s) \leftrightarroweq (M^\prime,s^\prime)$, then $(M,s) \equiv_{\lang_K} (M^\prime,s^\prime)$
	\end{block} \pause
	Does the converse hold?
\end{frame}

\begin{frame}{Bisimulation: Countably Many Atoms}
	Given a countable set of atoms P, enumarated such that $p_n$ is the $n$-th atom,
	\begin{block}{$M^1 = \langle S^1,R^1,V^1 \rangle$}
		\begin{columns}
			\begin{column}{0.5\textwidth}
				\begin{itemize}
					\item $S^1 = \{s^1\} \cup \mathbb{N}$
					\item $R^1 = \{s^1\} \times \mathbb{N}$
					\item $V^1(p_n) = \{n\}$
				\end{itemize}
			\end{column}
			\begin{column}{0.5\textwidth}
				\begin{tikzpicture}[
						shorten >=1pt,
						main/.style = {draw, circle, inner sep=2pt}
					]
					\node[main,label=above:{$p_0$}] (z) {$0$};
					\node[main,label=above:{$p_1$}] (1) [right of=z] {$1$};
					\node[main,label=above:{$p_2$}] (2) [right of=1] {$2$};
					\node (d) [right of=2] {$\dots$};
					\node[main,inner sep=1pt] (s1) [below of=z] {$s^1$};
					\draw[->] (s1) to (z);
					\draw[->] (s1) to (1);
					\draw[->] (s1) to (2);
				\end{tikzpicture}
			\end{column}
		\end{columns}
	\end{block}
	\begin{block}{$M^2 = \langle S^2,R^2,V^2 \rangle$}
		\begin{columns}
			\begin{column}{0.5\textwidth}
				\begin{itemize}
					\item $S^2 = \{s^2,\omega\} \cup \mathbb{N}$
					\item $R^2 = \{s^2\} \times (\mathbb{N} \cup \{\omega\})$
					\item $V^2(p_n) = \{n\}$
				\end{itemize}
			\end{column}
			\begin{column}{0.5\textwidth}
				\begin{tikzpicture}[
						shorten >=1pt,
						main/.style = {draw, circle, inner sep=2pt}
					]
					\node[main,label=above:{$p_0$}] (z) {$0$};
					\node[main,label=above:{$p_1$}] (1) [right of=z] {$1$};
					\node[main,label=above:{$p_2$}] (2) [right of=1] {$2$};
					\node (d) [right of=2] {$\dots$};
					\node[main,inner sep=1pt] (s2) [below of=z] {$s^2$};
					\node[main] (om) [below of=2] {$\omega$};
					\draw[->] (s2) to (z);
					\draw[->] (s2) to (1);
					\draw[->] (s2) to (2);
					\draw[->] (s2) to (om);
				\end{tikzpicture}
			\end{column}
		\end{columns}
	\end{block}
\end{frame}

\begin{frame}{Bisimulation: Countably Many Atoms}
	$(M^1,s^1)$ and $(M^2,s^2)$ are not bisimilar (\textbf{back} is not satisfied),\\
	but $(M^1,s^1)$ and $(M^2,s^2)$ satisfy the same formulas. \pause
	%\begin{small}
	\begin{proof}
		Induction on formulas
		\begin{itemize}
			\item $s^1,s^2$ satisfy the same properties (none)
			\item negation and conjuction are easy
		\end{itemize} \pause
		Suppose $K\phi$ a formula that could distinguish $(M^1,s^1)$ and $(M^2,s^2)$, i.e. $(M^1,s^1) \models K\phi$ and $(M^2,s^2) \not\models K\phi$ (opposite is impossible).
		\begin{itemize}
			\item $\phi$ is true in all $\mathbb{N}$ states and false in $\omega$
			\item $\phi$ is finite so let $n_{\max} = \max \{n|p_n \text{ occurs in } \phi\}$\\
				then $(M^2,n_{\max}+1) \models \phi$ iff $(M^2,\omega) \models \phi$
		\end{itemize} \pause
		Contradiction. Therefore $(M^1,s^1) \equiv_{\lang_K} (M^2,s^2)$
	\end{proof}
	%\end{small}
\end{frame}

\begin{frame}{Hedgehogs}
	\begin{figure}[h]
		\includegraphics[width=1\textwidth]{figure_8_1_hedgehog_models}
		\caption{Left: Hedgehog with finite spines ($H_{fin}$), Right: Hedgehog with an infinite spine ($H_{inf}$).}
	\end{figure} \pause
	\begin{block}{Theorem 8.12}
		\[(H_{fin},s_{fin}) \not\leftrightarroweq (H_{inf},s_{inf})\] \pause
		\textbf{Proof.} For every $n \in \mathbb{N}$  there is a formula that distinguishes $(\omega,0)$ from $(n,0)$, i.e. the formula $(\hat{K}^n \top \wedge K^{n+1} \bot)$
	\end{block}
\end{frame}

\begin{frame}{Modal depth}
	\begin{block}{Definition 8.13 (Modal depth)}
		The modal depth of a formula is given by the function $d:\lang_K \rightarrow \mathbb{N}$ s.t.
		\begin{align*}
			d(p) &= 0\\
			d(\neg \phi) &= d(\phi)\\
			d(\phi \wedge \psi) &= \max(d(\phi),d(\psi))\\
			d(K_a\phi) &= 1 + d(\phi)
		\end{align*}
	\end{block}
\end{frame}

\begin{frame}{Hedgehogs}
	\begin{block}{Lemma 8.14}
		For the $H_{inf}$ model, for all $\phi$ s.t. $d(\phi)=n$ it is the case that\\
		$(n,0) \models \phi$ iff $(\omega,0) \models \phi$ and $(m,0) \models \phi$ for all $m>n$
	\end{block} \pause
	\begin{block}{Theorem 8.15}
		\[(H_{fin},s_{fin}) \equiv_{\lang_K} (H_{inf},s_{inf})\]
		\textbf{Proof.} Analogous to the respective proof for $(M^1,s^1),(M^2,s^2)$\\
		For $K \phi$ s.t. $(H_{fin},s_{fin}) \models K \phi$ and $(H_{inf},s_{inf}) \not\models K \phi$ we get again $(H_{inf},(\omega,0)) \not\models \phi$ and from Lemma 8.14 we get $(H_{inf},(n,0)) \not\models \phi$ where $n=d(\phi)$.
		Therefore also $(H_{fin},s_{fin} \not\models K \phi)$ which is a contradiction.
	\end{block}
\end{frame}

\begin{frame}{Finite models}
	A model is \textit{finite} iff it consists only of a finite number of states, i.e. for $M = \langle S,R,V \rangle$ then $|S| \in \mathbb{N}$.
	\begin{block}{Theorem 8.16}
		For $M=\langle S,R,V \rangle, M^\prime=\langle S^\prime,R^\prime,V^\prime \rangle$ finite models and states $s \in S, s^\prime \in S^\prime$, if $(M,s) \equiv_{\lang_K} (M^\prime,s^\prime)$ then $(M,s) \leftrightarroweq (M^\prime,s^\prime)$.
	\end{block}
\end{frame}

\begin{frame}{Finite models}
	\begin{block}{Proof.}
		Suppose $(M,s) \equiv_{\lang_K} (M^\prime,s^\prime)$, we will show the following is a bisimulation
		\[\mathfrak{R} = \{(t,t^\prime) | (M,t) \equiv_{\lang_K} (M^\prime,t^\prime)\}\]
		\begin{itemize}
			\item \textbf{atoms} Trivial
			\item \textbf{forth} For $(t,t^\prime) \in \mathfrak{R}$ and $(t,u) \in R_{\alpha}$ suppose there is\\
				no state $u^\prime$: $(t^\prime,u^\prime) \in R_{\alpha}^\prime$ and $(u,u^\prime) \in \mathfrak{R}$.\\
				Then for every such $u^\prime$ there is a formula $\phi_{u^\prime}$: $(M^\prime,u^\prime) \models \phi_{u^\prime}$ and $(M,u) \not\models \phi_{u^\prime}$.
				Now consider
				\[\phi = \bigvee_{(t^\prime,u^\prime)\in R_{\alpha}^\prime} \phi_{u^\prime}\]
			$\phi$ is finite, and we get $(M,t) \models \hat{K}_a \neg \phi$ and $(M^\prime,t^\prime) \models K_a \phi$\\
				which is a contradiction
			\item \textbf{back} Analogous to the proof for \textbf{forth}
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Finite degree}
	A model is said to have a \textit{finite degree} iff $\{t | (s,t) \in R_a\}$ is finite for every $s \in S$ and $\alpha \in A$, i.e. the set of accessible states is always finite.
	\begin{block}{Exercise 8.17}
		\begin{itemize}
			\item Show that there is a model of finite degree which is not a finite model.
			\item Show that Theorem 8.16 can be extended to the class of models of finite degree.
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{Expressivity - Bisimulation}
	Notes
	\begin{itemize}
		\item Modal languages cannot distinguish non-identical models
		\item Two bisimilar models might be indistinguishable
		\item The problem seems to be related to infinity
			\begin{itemize}
				\item Formulas are finite but models may be infinite
				\item Though a theory can capture some infinitary aspects of a model, it cannot capture the whole model
			\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
	\begin{figure}[h]
		\includegraphics[width=1\textwidth]{i_want_to_play_a_game_meme}
	\end{figure}
\end{frame}

\section*{Games}

\begin{frame}{Games}
	A game is played with two models by two players:
	\begin{itemize}
		\item \textbf{Spoiler}: Tries to show that the models are different
		\item \textbf{Duplicator}: Tries to show that the models are the same
	\end{itemize}
	Spoiler only has a finite amount of rounds, if they fail to show that the models are different by then, the duplicator wins.
	\\[8pt]
	The two models have the same theory iff the duplicator has a winning strategy.
\end{frame}

\begin{frame}{The $\lang_K(P)$ game}
	\begin{small}
	For models $M = \langle S,R,V \rangle, M^\prime = \langle S^\prime,R^\prime,V^\prime \rangle$ and states $s \in S, s^\prime \in S^\prime$, the $n$-round $\lang_K(P)$ \textit{game} between spoiler and duplicator on $(M,s)$ and $(M^\prime,s^\prime)$ is the following \pause
	\begin{itemize}
		\item If $n=0$ then spoiler wins if $s$ and $s^\prime$ differ in any atomic property in $P$, else duplicator wins \pause
		\item If $n>0$ then spoiler can play any of the following moves
			\begin{itemize}
				\item \textbf{forth-move}: choose $\alpha \in A, t \in S \text{ s.t. } (s,t) \in R_a$.\\
				Duplicator responds with state $t^\prime \in S^\prime$ s.t. $(s^\prime,t^\prime) \in R_a^\prime$
				\item \textbf{back-move}: choose $\alpha \in A, t^\prime \in S^\prime \text{ s.t. } (s^\prime,t^\prime) \in R_a^\prime$.\\
				Duplicator responds with state $t \in S$ s.t. $(s,t) \in R_a$
			\end{itemize}
			Output is $(t,t^\prime)$ \pause
		\item Game continues with the new output state
	\end{itemize} \pause
	If either player cannot perform an action, that player loses\\
	If the output states differ in their atomic properties in $P$, spoiler wins\\
	If spoiler hasn't won after $n$ rounds, duplicator wins
	\end{small}
\end{frame}

\begin{frame}{Enter $\lang_K^n$}
	One should think of the number of rounds in the game as the \textit{modal depth} of the formulas the players are concerned with. \pause
	\begin{block}{Definition 8.19 ($\lang_K^n$)}
		The language $\lang_K^n$ of formulas of depth less than or equal to $n$ is defined as such
		\begin{flalign*}
			\lang_K^0 &\\
				&\phi ::= p | \neg \phi | \left(\phi \wedge \phi\right)\\
			\lang_K^{n+1} &\\
				&\phi ::= \psi | K_a \psi | \neg \phi | \left(\phi \wedge \phi\right)
		\end{flalign*}
		where $\psi \in \lang_K^n$
	\end{block}
\end{frame}

\begin{frame}{The $\lang_K(P)$ game}
	\begin{block}{Lemma 8.20}
		Given a finite set of atoms $P$, for every $n$ there are only finitely many different propositions up to logical equivalence in $\lang_K^n(P)$.\\
		\textbf{Proof.} By induction on $n$
	\end{block} \pause
	\begin{block}{Theorem 8.21}
		For all $n \in \mathbb{N}$, all models $(M,s)$ and $(M^\prime,s^\prime)$ and all finite sets of atoms $P$: duplicator has a winning strategy for the $n$-round $\lang_K(P)$-game on $(M,s)$ and $(M^\prime,s^\prime)$ iff $(M,s) \equiv_{\lang_K^n} (M^\prime,s^\prime)$.
	\end{block}
\end{frame}

\begin{frame}{The $\lang_K(P)$ game}
	\setbeamercolor{block title}{bg=}
	\setbeamercolor{block body}{bg=}
	\begin{block}{Proof.}
		Induction on $n$
		\begin{itemize}
			\item For $n=0$ it follows from the definition of the game
			\item Suppose the Theorem holds for $n$. For $n+1$
				\begin{small}
				\begin{itemize}
					\item[$(\rightarrow)$] By induction on the formula of $\phi \in \lang_K^{n+1}$
					\item If $\phi=\psi, \psi \in \lang_K^n$ it follows from (first) induction hypothesis
					\item If $\phi=K_a \psi, \psi \in \lang_K^n$, suppose $(M,s) \models K_a \psi$\\
						then for any $t^\prime: (s^\prime,t^\prime) \in R_a^\prime$ that spoiler could select,\\
						duplicator has a winning strategy, i.e. can select a $t \in R_a$: has a winning strategy in the subgame on $(M,t),(M^\prime,t^\prime)$\\[4pt]
						By induction hypothesis $(M,t) \models \psi$ iff $(M^\prime,t^\prime) \models \psi$ and since $(M,s) \models K_a \psi$ then $(M,t) \models \psi$ and $(M^\prime,t^\prime) \models \psi$\\
						$t$ was arbitrary so it holds for all $t^\prime:(s^\prime,t^\prime) \in R_a^\prime$ and therefore $(M^\prime,s^\prime) \models K_a \psi$
					\item The induction step is trivial
				\end{itemize}
				\end{small}
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}{The $\lang_K(P)$ game}
	\setbeamercolor{block title}{bg=}
	\setbeamercolor{block body}{bg=}
	\begin{block}{Proof. (cont.)}
		$(\leftarrow)$ Suppose $(M,s) \equiv_{\lang_K^{n+1}} (M^\prime,s^\prime)$, we need to describe the duplicator's winning strategy, i.e. show that for all $t: (s,t) \in R_a$ that spoiler selects, there is a $t^\prime: (s^\prime,t^\prime) \in R_a^\prime: (M,t) \equiv_{\lang_K^n} (M^\prime,t^\prime)$\\
		Then by the first induction hypothesis duplicator has a winning strategy for the remaining subgame \pause
		\\[8pt]
		Suppose there is no such $t^\prime$, so for all $t: (s^\prime,t^\prime)$ spoiler has a winning strategy, i.e. (from first induction hypothesis) there is a formula $\phi_{t^\prime}: d(\phi) \leq n$ where $(M^\prime,t^\prime) \models \phi_{t^\prime}, (M,s) \not\models \phi_{t^\prime}$
	\end{block}
\end{frame}

\begin{frame}{The $\lang_K(P)$ game}
	\setbeamercolor{block title}{bg=}
	\setbeamercolor{block body}{bg=}
	\begin{proof}[Proof. (cont.)]
		From Lemma 8.20 the set $\{\phi_{t^\prime} | (s^\prime,t^\prime) \in R_a^\prime\}$ is finite wrt equivalence.
		If $f$ a function that chooses one formula from each equivalence class $[t^\prime]$, then
		\[ \phi = \bigvee_{(t^\prime,u^\prime)\in R_{\alpha}^\prime} f([t^\prime]) \]
		is finite with $d(\phi) \leq n$ \pause
		\\[4pt]
		We have $(M^\prime,s^\prime) \models K_a \phi$ but $(M,s) \not\models K_a \phi$ while $d(K_a \phi) \leq n+1$\\
		Contradiction due to initial assumtion that $(M,s) \equiv_{\lang_K^{n+1}} (M^\prime,s^\prime)$\\
	\end{proof}
\end{frame}

\begin{frame}{The $\lang_K(P)$ game}
	\begin{block}{Theorem 8.22}
		$(M,s) \equiv (M^\prime,s^\prime)$ iff for all $n \in \mathbb{N}$ duplicator has a winning strategy for the $n$-round $\lang_K$-game on $(M,s)$ and $(M^\prime,s^\prime)$
	\end{block} \pause
	Games are finite but there are infinite games
\end{frame}

\end{document}

### 2021-06-07 del/8_expressivity_pres.tex
DEL: Presentation: Final additions and fixes after presentation

@@
 		\begin{itemize}
-			\item $s^1,s^2$ satisfy the same properties (none)
+			\item $s^1,s^2$ satisfy the same atoms (none)
 			\item negation and conjuction are easy
@@
 			\begin{itemize}
-				\item \textbf{forth-move}: choose $\alpha \in A, t \in S \text{ s.t. } (s,t) \in R_a$.\\
+				\item \textbf{forth-move}: choose $a \in A, t \in S \text{ s.t. } (s,t) \in R_a$.\\
 				Duplicator responds with state $t^\prime \in S^\prime$ s.t. $(s^\prime,t^\prime) \in R_a^\prime$
-				\item \textbf{back-move}: choose $\alpha \in A, t^\prime \in S^\prime \text{ s.t. } (s^\prime,t^\prime) \in R_a^\prime$.\\
+				\item \textbf{back-move}: choose $a \in A, t^\prime \in S^\prime \text{ s.t. } (s^\prime,t^\prime) \in R_a^\prime$.\\
 				Duplicator responds with state $t \in S$ s.t. $(s,t) \in R_a$
@@
 		\\[8pt]
-		Suppose there is no such $t^\prime$, so for all $t: (s^\prime,t^\prime)$ spoiler has a winning strategy, i.e.
-(from first induction hypothesis) there is a formula $\phi_{t^\prime}: d(\phi) \leq n$ where $(M^\prime,t^\prime) \models \phi_{t^\prime}, (M,s) \not\models \phi_{t^\prime}$
+		Suppose there is no such $t^\prime$, so for all $t^\prime: (s^\prime,t^\prime)$ spoiler has a winning strategy, i.e.
+(from first induction hypothesis) there is a formula $\phi_{t^\prime}: d(\phi) \leq n$ where $(M^\prime,t^\prime) \models \phi_{t^\prime}, (M,t) \not\models \phi_{t^\prime}$
 	\end{block}
@@
 		If $f$ a function that chooses one formula from each equivalence class $[t^\prime]$, then
-		\[ \phi = \bigvee_{(t^\prime,u^\prime)\in R_{\alpha}^\prime} f([t^\prime]) \]
+		\[ \phi = \bigvee_{(s^\prime,t^\prime)\in R_{\alpha}^\prime} f([t^\prime]) \]
 		is finite with $d(\phi) \leq n$ \pause
@@
 	\end{block} \pause
-	Games are finite but there are infinite games
+	Games are finite but there are infinite games\\ \pause
+	Winning strategy for duplicator coincides with bisimulation only when we consider an $\lang_K(P)$ game with $\omega$ rounds (the first ordinal limit)
 \end{frame}

### 2021-06-08 del/8_expressivity_pres.tex
DEL: Presentation: Added remaining slides for day 2
Plus some general fixes

@@
 \newcommand{\lang}{\mathcal{L}}
+\newcommand{\Mpr}{M^\prime}
+\newcommand{\Spr}{S^\prime}
+\newcommand{\spr}{s^\prime}
+\newcommand{\tpr}{t^\prime}
 
@@
 
+\section*{\textit{S5}}
+
+\begin{frame}{Single-agent \textit{S5}}
+	For \textit{S5}-models for one agent
+	\begin{block}{Theorem 8.24}
+		Duplicator has a winning strategy for the $n$-round $\lang_K$-game on $(M,s)$ and $(M^\prime,s^\prime)$ for every $n \in \mathbb{N}$ iff duplicator has a winning strategy for the $1$-round $\lang_K$-game on $(M,s)$ and $(M^\prime,s^\prime)$
+	\end{block} \pause
+	From right to left holds because the set of $a$-accessible states is the same for all states that are $a$-accessible from $s$ or $s^\prime$,\\
+	i.e. after $1$ round the subgame is exactly the same.
+\end{frame}
+
+\begin{frame}{Single-agent \textit{S5}}
+	\begin{block}{Theorem 8.25}
+		\[(M,s) \equiv_{\lang_K} (M^\prime,s^\prime) \text{ iff } (M,s) \equiv_{\lang_K^1} (M^\prime,s^\prime)\]
+	\end{block} \pause
+	For a formula $\phi \in \lang_K(\{a\})$
+
+	\[\delta_s = \bigwedge \{p | p \in P(\phi) \text{ and } (M,s) \models p\}\]
+	\[
+		\psi = \bigvee_{(M,s) \in S5(\phi)} \left( \delta_s \wedge \bigwedge_{s \sim_a t} \hat{K} \delta_t \wedge K \bigvee_{s \sim_a t} \delta_t \right)
+	\] \pause
+
+	we have $\phi \equiv \psi$ where $d(\psi) = 1$
+\end{frame}
+
+\begin{frame}{Multi-agent \textit{S5}}
+	\begin{figure}[h]
+		\includegraphics[width=1\textwidth]{figure_8_2_spine_models}
+		\caption{(8.2) Three spine models: $Spine(6)$, $Spine(3)$ and $Spine(\omega)$.}
+	\end{figure} \pause
+	\begin{block}{Theorem 8.31}
+		\[(Spine(n),0) \not\leftrightarroweq (Spine(\omega),0)\]
+	\end{block}
+\end{frame}
+
+\begin{frame}{Multi-agent \textit{S5}}
+	\begin{proof}
+		Define $\phi_n$ inductively
+		\begin{flalign*}
+			\phi_0 &= \hat{K}_a p\\
+			\phi_1 &= \hat{K}_a \hat{K}_b p\\
+			\phi_{n+1} &= \hat{K}_a \hat{K}_b \phi_n
+		\end{flalign*}
+		We have $(Spine(n),0) \models \phi_n$ and $(Spine(\omega),0) \not\models \phi_n$ for every $n \in \mathbb{N}$.
+	\end{proof}
+\end{frame}
+
+\begin{frame}{Multi-agent \textit{S5}}
+	\begin{block}{Theorem 8.32}
+		For every $n \in \mathbb{N}$
+		\[(Spine(n),0) \equiv_{\lang_K^n} (Spine(\omega),0)\]
+	\end{block} \pause
+	There is no formula that distinguishes $(Spine(\omega),0)$ from the other spine models \pause
+	\begin{block}{Theorem 8.33}
+		There is no $\phi \in \lang_K$ such that $(Spine(\omega),0) \notin \llbracket \phi \rrbracket$ and $\{(Spine(n),0) | n \in \mathbb{N}\} \subseteq \llbracket \phi \rrbracket$.
+	\end{block} \pause
+	Multi-agent \textit{S5} expressive power is quite similar to general modal logic
+\end{frame}
+
+\section*{\textit{S5C}}
+
+\begin{frame}{\textit{S5C}}
+	\begin{block}{Theorem 8.34}
+		\[\lang_K \prec \lang_{KC}\] \pause
+		\textbf{Proof.} Obviously $\lang_K \preceq \lang_{KC}$.
+		Now consider
+		\[\phi = C_{ab} \neg p\]
+		$\phi$ is false in $(Spine(n),0)$ for every $n \in \mathbb{N}$\\
+		and true in $(Spine(\omega),0)$
+		\\[4pt]
+		From Theorem 8.33 there is no such formula in $\lang_K$
+	\end{block} \pause
+	But still cannot distinguish bisimilar models
+	\begin{block}{Theorem 8.35}
+		For all models $(M,s)$ and $(\Mpr,\spr)$, if $(M,s) \leftrightarroweq (\Mpr,\spr)$ then $(M,s) \equiv_{\lang_{KC}} (\Mpr,\spr)$.
+	\end{block}
+	Converse does not hold
+\end{frame}
+
+\begin{frame}{The $\lang_{KC}(P)$ game}
+	For models $M = \langle S,R,V \rangle, M^\prime = \langle S^\prime,R^\prime,V^\prime \rangle$ and states $s \in S, s^\prime \in S^\prime$, the $n$-round $\lang_{KC}(P)$ \textit{game} is the same as the $\lang_K$ game, but spoiler has the following extra moves \pause
+	\begin{itemize}
+		\item \textbf{$C$-forth-move}: choose group $B$, $t \in S$ s.t. $(s,t) \in R(B)^*$\\
+		Duplicator responds with state $\tpr$ s.t. $(\spr,\tpr) \in R^\prime(B)^*$
+		\item \textbf{$C$-back-move}: choose group $B$, $\tpr \in \Spr$ s.t. $(\spr,\tpr) \in R^\prime(B)^*$\\
+		Duplicator responds with state $t$ s.t. $(s,t) \in R(B)^*$
+	\end{itemize} \pause
+	Win conditions also remain the same \pause
+	\\[4pt]
+	\textit{Note:} the length of the B-paths selected by spoiler and duplicator can differ
+\end{frame}
+
+\begin{frame}{\textit{S5C}}
+	We similarly extend \textbf{Modal depth} ($d(C_B \phi) = 1 + d(\phi)$), $\lang_{KC}^n$ and with similar reasoning we get \pause
+	\begin{block}{Theorem 8.41}
+		For all $n \in \mathbb{N}$, all models $(M,s)$ and $(M^\prime,s^\prime)$ and all finite sets of atoms $P$: duplicator has a winning strategy for the $n$-round $\lang_{KC}(P)$-game on $(M,s)$ and $(M^\prime,s^\prime)$ iff $(M,s) \equiv_{\lang_{KC}^n} (M^\prime,s^\prime)$.
+	\end{block}
+\end{frame}
+
+\section*{\textbf{PA}}
+
+\begin{frame}{\textbf{PA}}
+	\begin{block}{Theorem 8.44}
+		\[\lang_K \equiv \lang_{K[]}\] \pause
+		\textbf{Proof.} Clearly $\lang_K \preceq \lang_{K[]}$\\
+		For $\lang_{K[]} \preceq \lang_K$ we use
+		\begin{itemize}
+			\item the translation $t: \lang_{K[]} \rightarrow \lang_K$ from Definition 7.20
+			\item Lemma 7.24 ($\vdash \phi \leftrightarrow t(\phi), \phi \in \lang_{K[]}$)
+			\item soundness of \textbf{PA}
+		\end{itemize}
+	 to eventually get
+		\[\phi \equiv t(\phi) \text{ for every } \phi \in \lang_{K[]}\]
+	\end{block}
+\end{frame}
+
+\section*{\textit{PAC}}
+
+\begin{frame}{\textit{PAC}}
+	Since $\lang_{KC}$ can distinguish the spine models (spoiler can \textit{leap} to the end of the finite model) we need a different class of models, where such a leap is a bad move \pause
+	\begin{figure}[h]
+		\includegraphics[width=0.6\textwidth]{figure_8_3_hairpin_model}
+		\caption{(8.3) A hairpin model ($Hairpin(n)$). $n$ is even.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{\textit{PAC}}
+	\begin{block}{Lemma 8.46}
+		For every $n \in \mathbb{N}$
+		\[(Hairpin(n),s_0) \equiv_{\lang_{KC}^n} (Hairpin(n),t_0)\]
+	\end{block} \pause
+	\begin{block}{Lemma 8.47}
+		There is no formula $\phi \in \lang_{KC}$ such that for all $n \in \mathbb{N}$\\
+		$(Hairpin(n),s_0) \models \phi$ and $(Hairpin(n),s_0) \not\models \phi$.
+	\end{block}
+\end{frame}
+
+\begin{frame}{\textit{PAC}}
+	\begin{block}{Theorem 8.44}
+		\[\lang_{KC} \prec \lang_{KC[]}\] \pause
+		\textbf{Proof.} Obviously $\lang_{KC} \preceq \lang_{KC[]}$.
+		Now consider
+		\[\phi = [\neg p \rightarrow K_a \neg p] C_{ab} \neg p\]
+		$\phi$ is false in $(Hairpin(n),s_0)$ but true in $(Hairpin(n),t_0)$ for every $n \in \mathbb{N}$
+		\\[4pt]
+		From Lemma 8.47 there is no such formula in $\lang_{KC}$
+	\end{block} \pause
+	But still cannot distinguish bisimilar models since public announcements preserve bisimilarity
+\end{frame}
+
+\begin{frame}
+	\begin{figure}[h]
+		\includegraphics[width=0.5\textwidth]{figure_8_3_hairpin_model_pa}
+		\caption{(8.3) A hairpin model before and after a public announcement. $n$ is even.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{The $\lang_{KC[]}(P)$ game}
+	For models $M = \langle S,R,V \rangle, M^\prime = \langle S^\prime,R^\prime,V^\prime \rangle$ and states $s \in S, s^\prime \in S^\prime$, the $n$-round $\lang_{KC[]}(P)$ \textit{game} is the same as the $\lang_{KC}$ game, but spoiler can also initiate the following scenario \pause
+	\\[4pt]
+	\textbf{$[\phi]$-move}: choose number $r<n$ and sets $T \subseteq S, T^\prime \subseteq \Spr$ with $s \in T, s^\prime \in T^\prime$
+	\begin{itemize}[label=]
+		\item \textbf{Stage 1}: Duplicator chooses states $t \in (T \cup T^\prime), \bar{t} \in (\overline{T} \cup \overline{T^\prime})$ and they play the $r$-round game for these states\\
+			\quad If duplicator wins this subgame, wins the $n$-round game
+		\item \textbf{Stage 2}: otherwise, game continues on $(M|T,s), (\Mpr|T^\prime,\spr)$ over $(n-r)-1$ rounds
+	\end{itemize} \pause
+	Remaining win conditions remain the same
+\end{frame}
+
+\begin{frame}{\textit{S5C}}
+	We similarly extend \textbf{Modal depth} ($d([\phi] \psi) = 1 + d(\phi) + d(\psi)$), $\lang_{KC[]}^n$ and with (not as much, but still) similar reasoning we get \pause
+	\begin{block}{Theorem 8.41}
+		For all $n \in \mathbb{N}$, all models $(M,s)$ and $(M^\prime,s^\prime)$ and all finite sets of atoms $P$: duplicator has a winning strategy for the $n$-round $\lang_{KC[]}(P)$-game on $(M,s)$ and $(M^\prime,s^\prime)$ iff $(M,s) \equiv_{\lang_{KC[]}^n} (M^\prime,s^\prime)$.
+	\end{block}
+\end{frame}
+
+\section*{\textbf{AM}}
+
+\begin{frame}{\textbf{AM}}
+	\begin{block}{Theorem 8.57}
+		\[\lang_K \equiv \lang_{K\otimes}\] \pause
+		\textbf{Proof.} Clearly $\lang_K \preceq \lang_{K\otimes}$\\
+		For $\lang_{K\otimes} \preceq \lang_K$ we use
+		\begin{itemize}
+			\item the translation $t: \lang_{K\otimes} \rightarrow \lang_K$ from Definition 7.37
+			\item Lemma 7.40 ($\vdash \phi \leftrightarrow t(\phi), \phi \in \lang_{K\otimes}$)
+			\item soundness of \textbf{AM}
+		\end{itemize}
+		to eventually get
+		\[\phi \equiv t(\phi) \text{ for every } \phi \in \lang_{K\otimes}\]
+	\end{block}
+\end{frame}
+
+\section*{Relativised Common Knowledge}
+
+\begin{frame}{Relativised Common Knowledge}
+	For the general modal case $\mathcal{K}$
+	\begin{block}{Theorem 8.58}
+		\[\lang_{K\;RC} \equiv \lang_{K\;RC[]}\]
+		\\[10pt]
+	\end{block} \pause
+	\begin{block}{Theorem 8.66}
+		\[\lang_{KC[]} \prec \lang_{K\;RC}\]
+		\\[10pt]
+	\end{block} \pause
+	It is unknown whether this holds for \textit{S5}
+\end{frame}
+
+\begin{frame}{Summary}
+	\begin{center}
+		\begin{tikzpicture}
+			\draw[very thick] (0,0) -- (10,0);
+			\draw (2,0) parabola bend (5,1.5) (8,0);
+			\node at (5,0.75) {$\lang_K \equiv \lang_{K[]} \equiv \lang_{K\otimes}$};
+			\draw (1.5,0) parabola bend (5,2.5) (8.5,0);
+			\node at (5,2) {$\lang_{KC}$};
+			\draw (1,0) parabola bend (5,3.5) (9,0);
+			\node at (5,3) {$\lang_{KC[]}$};
+			\draw (0.5,0) parabola bend (5,4.5) (9.5,0);
+			\node at (5,3.8) {$\lang_{K\;RC} \equiv \lang_{K\;RC[]}$};
+		\end{tikzpicture}
+	\end{center}
+	\[\lang_K \equiv \lang_{K[]} \equiv \lang_{K\otimes} \prec \lang_{KC} \prec \lang_{KC[]} \prec \lang_{K\;RC} \equiv \lang_{K\;RC[]}\]
+\end{frame}
+
 \end{document}

### 2021-07-01 del/final_exam.tex
DEL: Final Exam: Exercises 1 to 3, version delivered

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

\usepackage{amsmath,latexsym,amssymb}
\usepackage{graphicx}
\graphicspath{ {./figures_final_exam/} }
% Required packages for plotting
\usepackage{pgfplots}
%\usepackage{pgfplotstable}
\pgfplotsset{compat=1.16}
%\usepackage{tikz}

% Main document
\begin{document}
\title{Dynamic Epistemic Logic - Final Take Home Exam}
\author{Thomas Pappas}
%\date{}
\maketitle

\section*{Exercise 1}

\paragraph{(a)} Let $F=\left<S,R\right>$ be a frame.

\subparagraph{($\Leftarrow$)} Let $M=\left<S,R,V\right>$ for some $V$ such that the property holds.
Then
\begin{flalign}
	& M,w \models \Box \Box p \rightarrow \Box p \nonumber\\
	\Leftrightarrow & M,w \models \Box \Box p \Rightarrow M,w \models \Box p \nonumber\\
	\Leftrightarrow & (\forall s \in R[w])[M,s \models \Box p] \Rightarrow (\forall s \in R[w])[M,s \models p] \nonumber\\
	\Leftrightarrow & (\forall s \in R[w])\left[(\forall t \in R[s]) [M,t \models p]\right] \Rightarrow (\forall s \in R[w])[M,s \models p] \label{ex1arl}
\end{flalign}
From hypothesis we get that $(\forall s \in R[w])\exists u \in R[w]$ such that $s \in R[u]$ therefore the first part of \eqref{ex1arl} implies that $M,s \models p, \forall s \in R[w]$ and therefore implies the second.
Therefore it holds.

\subparagraph{($\Rightarrow$)} Let $\Box \Box p \rightarrow \Box p$ hold in $F$ and assume $R$ doesn't have the weak density property, i.e. $\exists s,t$ such that $t \in R[s]$ but $\nexists u$ such that $u \in R[s]$ and $t \in R[u]$.
Define $V(p) = R[t], \forall t \in R[s]$ and $V(q) = \emptyset, q \ne p$.
\begin{center}
	\begin{tikzpicture}[
			shorten >=1pt,
			main/.style = {inner sep=1pt}
		]
		\node[main] (s) {$s$};
		\node[main] (empty1) [above right of=s] {};
		\node[main] (p1) [above right of=empty1] {$p$};
		\node[main] (p2) [right of=empty1] {$p$};
		\draw[->] (s) to (empty1);
		\draw[->] (empty1) to (p1);
		\draw[->] (empty1) to (p2);
	\end{tikzpicture}
\end{center}
Then $M,s \models \Box  \Box p$ but $M,s \not\models \Box p$ which is absurd.

\paragraph{(b)} The formula that defines the property $\forall x \forall y (xRy \rightarrow xRx)$ is
\[\Diamond p \rightarrow (\Box p \rightarrow p)\]
\subparagraph{($\Leftarrow$)} Let $M=\left<S,R,V\right>$ for some $V$ such that the property holds.
Then
\begin{flalign*}
	& M,w \models \Diamond p \rightarrow (\Box p \rightarrow p) \nonumber\\
	\Leftrightarrow & M,w \models \Diamond p  \Rightarrow M,w \models (\Box p \rightarrow p)
\end{flalign*}
From hypothesis, for $w$ if we have $M,w \models \Diamond p$ then $\exists y (y \in R[w])$ and from the property we get that $w$ is reflective, and therefore $M,w \models \Box p \rightarrow p$ also holds.

\subparagraph{($\Rightarrow$)} Let $\Diamond p \rightarrow (\Box p \rightarrow p$ hold in $F$ and assume that $R$ does not have the above property.
Consider the model where $w \notin V(p)$ but $s \in V(p)$ for an $s \in R[w]$
\begin{center}
	\begin{tikzpicture}[
		shorten >=1pt,
		main/.style = {inner sep=1pt}
	]
	\node[main] (w) {$w$};
	\node[main] (p) [above right of=empty1] {$p$};
	\draw[->] (w) to (p);
	\end{tikzpicture}
\end{center}
Then we have $M,w \models \Diamond p, M,w \models \Box p$ but $M,w \not\models p$.
\\[8pt]
Therefore the above modal formula indeed defines the property $\forall x \forall y (xRy \rightarrow xRx)$.

\section*{Exercise 2}

\paragraph{(a)} We see the following cases
\begin{itemize}
	\item If I was holding two aces, then Bob would see 4 aces in total and would figure out he is holding two eights.
		Not true since Bob cannot determine his cards.
	\item If i was holding two eights, then Alice would see 4 eight in total and would figure out she is holding two eights.
		Not true since Alice cannot determine her cards.
\end{itemize}
Therefore I am holding an ace and an eight.

\paragraph{(b)} Since I see two eights from Alice and an ace and an eight from Bob, it means I either have two aces or an ace and an eight.
If I hade two aces, then Bob would be in the same position as myself in (a), and since he still cannot determine his cards it means that is not the case.
Therefore I hold an ace and an eight.

\paragraph{(c)} We see the following cases
\begin{itemize}
	\item If I had two eights, then Alice would be in the same position as myself in (b) and she would have figured out her cards in her second round.
	\item If I had two aces, then the same logic can be applied as in (b) and therefore Alice would again figure out her cards.
\end{itemize}
Therefore I hold an ace and an eight.

\paragraph{(d)} We denote as $A$ when a player holds an ace and $8$ when they hold an eight.
Considering all posible cases for three players, the possible words of the game are
\begin{itemize}
	\item $(AA,AA,88),(AA,88,AA),(88,AA,AA)$
	\item $(AA,88,88),(88,AA,88),(88,88,AA)$
	\item $(AA,A8,A8),(A8,AA,A8),(A8,A8,AA)$
	\item $(88,A8,A8),(A8,88,A8),(A8,A8,88)$
	\item $(AA,A8,88),(AA,88,A8),(A8,AA,88),(A8,88,A8),(88,AA,A8),(88,A8,AA)$
	\item $(A8,A8,A8)$
\end{itemize}

\paragraph{(e)}
\[\] % Added to make the figure show below the paragraph label.
\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{aces_eights_kripke}
	\caption{The Kripke structure describing the aces and eights game}
\end{figure}

\paragraph{(f)} Considering the situation described in part (a), when Alice and Bob say they cannot determine which cards they have, the structure becomes as such
\begin{figure}[h]
	\centering
	\includegraphics[width=0.5\textwidth]{aces_eights_kripke_f}
	\caption{The Kripke structure after Alice and Bob's turns}
\end{figure}

\section*{Exercise 3}

\subsection*{Exercise 4.20}

We will show that $M,s \models \left<\phi\right> K_a \psi$ iff $M,s \models (\phi \wedge K_a(\phi \rightarrow \left<\phi\right>\psi))$
\begin{flalign*}
	& M,s \models (\phi \wedge K_a(\phi \rightarrow \left<\phi\right>\psi))\\
	\Leftrightarrow & M,s \models \phi \text{ and } M,s \models K_a(\phi \rightarrow \left<\phi\right>\psi)\\
	\Leftrightarrow & M,s \models \phi \text{ and } (\forall t \in R[s]) [M,t \models \phi \rightarrow \left<\phi\right>\psi]\\
	\Leftrightarrow & M,s \models \phi \text{ and } (\forall t \in R[s]) [M,t \models \phi \text{ implies } M,t \models \left<\phi\right>\psi]\\
	\Leftrightarrow & M,s \models \phi \text{ and } (\forall t \in R[s]) [M,t \models \phi \text{ implies } (M,t \models \phi \text{ and } M|_\phi,t \models \psi)]\\
	\Leftrightarrow & M,s \models \phi \text{ and } (\forall t \in R[s]) [M,t \models \phi \text{ implies } M|_\phi,t \models \psi]\\
	\Leftrightarrow & M,s \models \phi \text{ and } (\forall t \in R[s]: M,t \models \phi) \text{ implies } M|_\phi,t \models \psi\\
	\Leftrightarrow & M,s \models \phi \text{ and } (\forall t \in R[s]|_\phi) \text{ implies } M|_\phi,t \models \psi\\
	\Leftrightarrow & M,s \models \phi \text{ and } M|_\phi,s \models K_a\psi\\
	\Leftrightarrow & M,s \models \left<\phi\right> K_a\psi
\end{flalign*}

\subsection*{Exercise 4.21}
In Example 4.1 from the book we can first see that the formula $\phi = \left<p \wedge \neg K_b p\right>\hat{K}_a\hat{K}_b \neg p$ is not valid for the $0$ world since
\[M,0 \not\models p \Rightarrow M,0 \not\models p \wedge \neg K_b p\]
Then for the $1$ world we have that $M,1 \models p$, but also $M,1 \models \neg K_b p$ since $\neg K_b p \leftrightarrow \hat{K}_b \neg p$ and indeed $b$ considers possible the $0$ world where $\neg p$ holds.
Then we see that $M,1 \models \hat{K}_a\hat{K}_b \neg p$, because
\begin{align*}
	& M,0 \models \neg p \\
	\Rightarrow & M,1 \models \hat{K}_b \neg p & \text{ (since } 0 \sim_b 1 \text{)}\\
	\Rightarrow & M,1 \models \hat{K}_a \hat{K}_b \neg p & \text{ (since } 1 \sim_a 1 \text{)}
\end{align*}
Therefore finally we have
\[M,1 \models p \text{ and } M,1 \models \neg K_b p \text{ and } M,1 \models \hat{K}_a\hat{K}_b \neg p \Rightarrow M,1 \models \left<p \wedge \neg K_b p\right>\hat{K}_a\hat{K}_b \neg p\]

\end{document}

### 2021-07-03 del/final_exam.tex
DEL: Final Exam: Exercises 4 to 6, version that was send after the deadline

@@
 %\usepackage{tikz}
+\usepackage{multicol}
+\usepackage{logicproof}
 
@@
 
-We will show that $M,s \models \left<\phi\right> K_a \psi$ iff $M,s \models (\phi \wedge K_a(\phi \rightarrow \left<\phi\right>\psi))$
+We will show that $M,s \models \left<\phi\right> K_a \psi$ iff $M,s \models (\phi \land K_a(\phi \rightarrow \left<\phi\right>\psi))$
 \begin{flalign*}
-	& M,s \models (\phi \wedge K_a(\phi \rightarrow \left<\phi\right>\psi))\\
+	& M,s \models (\phi \land K_a(\phi \rightarrow \left<\phi\right>\psi))\\
 	\Leftrightarrow & M,s \models \phi \text{ and } M,s \models K_a(\phi \rightarrow \left<\phi\right>\psi)\\
@@
 \subsection*{Exercise 4.21}
-In Example 4.1 from the book we can first see that the formula $\phi = \left<p \wedge \neg K_b p\right>\hat{K}_a\hat{K}_b \neg p$ is not valid for the $0$ world since
-\[M,0 \not\models p \Rightarrow M,0 \not\models p \wedge \neg K_b p\]
+In Example 4.1 from the book we can first see that the formula $\phi = \left<p \land \neg K_b p\right>\hat{K}_a\hat{K}_b \neg p$ is not valid for the $0$ world since
+\[M,0 \not\models p \Rightarrow M,0 \not\models p \land \neg K_b p\]
 Then for the $1$ world we have that $M,1 \models p$, but also $M,1 \models \neg K_b p$ since $\neg K_b p \leftrightarrow \hat{K}_b \neg p$ and indeed $b$ considers possible the $0$ world where $\neg p$ holds.
@@
 Therefore finally we have
-\[M,1 \models p \text{ and } M,1 \models \neg K_b p \text{ and } M,1 \models \hat{K}_a\hat{K}_b \neg p \Rightarrow M,1 \models \left<p \wedge \neg K_b p\right>\hat{K}_a\hat{K}_b \neg p\]
+\[M,1 \models p \text{ and } M,1 \models \neg K_b p \text{ and } M,1 \models \hat{K}_a\hat{K}_b \neg p \Rightarrow M,1 \models \left<p \land \neg K_b p\right>\hat{K}_a\hat{K}_b \neg p\]
+
+\section*{Exercise 4}
+
+We will use induction on the formula $\phi$.
+
+\paragraph{if $\phi = p$} then $\phi(p/\psi) = \psi$ and $\phi(p/\chi) = \chi$ and finally $\vdash \psi \leftrightarrow \chi$ from hypothesis
+
+\paragraph{if $\phi = \neg \phi^\prime$} then $\phi(p/\psi) = \neg \phi^\prime(p/\psi)$ and $\phi(p/\chi) = \neg \phi^\prime(p/\chi)$.
+So we have
+\begin{logicproof}{1}
+	\vdash \phi^\prime(p/\psi) \leftrightarrow \phi^\prime(p/\chi) & (induction hypothesis) \\
+	\vdash \neg \phi^\prime(p/\psi) \leftrightarrow \neg \phi^\prime(p/\chi) & (1, propositional) \\
+	\vdash \phi(p/\psi) \leftrightarrow \phi(p/\chi) &
+\end{logicproof}
+
+\paragraph{if $\phi = \phi_1 \land \phi_2$} then $\phi(p/\psi) = \phi_1(p/\psi) \land \phi_2(p/\psi)$ and $\phi(p/\chi) = \phi_1(p/\chi) \land \phi_2(p/\chi)$.\\
+So we have
+\begin{logicproof}{1}
+	\vdash \phi_1(p/\psi) \leftrightarrow \phi_1(p/\chi) & (induction hypothesis) \\
+	\vdash \phi_2(p/\psi) \leftrightarrow \phi_2(p/\chi) & (induction hypothesis) \\
+	\vdash \phi_1(p/\psi) \land \phi_2(p/\psi) \leftrightarrow \phi_1(p/\chi) \land \phi_2(p/\chi) & (1,2, propositional) \\
+	\vdash \phi(p/\psi) \leftrightarrow \phi(p/\chi) &
+\end{logicproof}
+
+\paragraph{if $\phi = K_a \phi^\prime$} then $\phi(p/\psi) = K_a \phi^\prime(p/\psi)$ and $\phi(p/\chi) = K_a \phi^\prime(p/\chi)$.\\
+So we have
+\begin{logicproof}{1}
+	\vdash \phi^\prime(p/\psi) \leftrightarrow \phi^\prime(p/\chi) & (induction hypothesis) \\
+	\vdash K_a(\phi^\prime(p/\psi) \leftrightarrow \phi^\prime(p/\chi)) & (1, necessitation of $K_a$) \\
+	\vdash K_a(\phi^\prime(p/\psi) \rightarrow \phi^\prime(p/\chi)) & (2, propositional) \\
+	\vdash K_a(\phi^\prime(p/\psi)) \rightarrow K_a(\phi^\prime(p/\chi)) & (3, distribution of $K_a$ over $\rightarrow$) \\
+	\vdash K_a(\phi^\prime(p/\chi) \rightarrow \phi^\prime(p/\psi)) & (2, propositional) \\
+	\vdash K_a(\phi^\prime(p/\chi)) \rightarrow K_a(\phi^\prime(p/\psi)) & (5, distribution of $K_a$ over $\rightarrow$) \\
+	\vdash K_a(\phi^\prime(p/\psi)) \leftrightarrow K_a(\phi^\prime(p/\chi)) & (4,6, propositional) \\
+	\vdash \phi(p/\psi) \leftrightarrow \phi(p/\chi) &
+\end{logicproof}
+
+\paragraph{if $\phi = [\phi_1]\phi_2$} then $\phi(p/\psi) = [\phi_1(p/\psi)]\phi_2(p/\psi)$ and $\phi(p/\chi) = [\phi_1(p/\chi)]\phi_2(p/\chi)$.
+\\[8pt]
+Here we will also use the following tautology (for arbitrary $\phi_1,\phi_2,\psi,\chi$)
+\begin{equation}
+	((\phi_1 \rightarrow \psi) \land (\phi_2 \rightarrow \chi) \land (\phi_1 \leftrightarrow \phi_2)) \rightarrow (\psi \leftrightarrow \chi) \label{t1}
+\end{equation}
+So we have
+\begin{logicproof}{1}
+	\vdash \phi_2(p/\psi) \rightarrow [\phi_1(p/\psi)]\phi_2(p/\psi) & (from $\phi$ follows $[\psi]\phi$) \\
+	\vdash \phi_2(p/\chi) \rightarrow [\phi_1(p/\chi)]\phi_2(p/\chi) & (from $\phi$ follows $[\psi]\phi$) \\
+	\vdash \phi_2(p/\psi) \leftrightarrow \phi_2(p/\chi) & (inductive hypothesis) \\
+	\vdash [\phi_1(p/\psi)]\phi_2(p/\psi) \leftrightarrow [\phi_1(p/\chi)]\phi_2(p/\chi) & (1,2,3, tautology \eqref{t1}, modus ponence) \\
+	\vdash \phi(p/\psi) \leftrightarrow \phi(p/\chi) &
+\end{logicproof}
+\newpage
+
+\section*{Exercise 5}
+
+We have the following models:
+\begin{multicols}{2}
+	\[M = (\text{Read};\text{Read}_b)=\left<S,\sim,\textbf{pre}\right>\]
+	\columnbreak
+	\begin{center}
+		\begin{tikzpicture}[
+				node distance={20mm},
+				shorten >=1pt,
+				shorten <=1pt,
+				main/.style = {draw, circle, inner sep=5pt}
+			]
+			\node[main, label={(np,npb)}, label=left:{$\neg p$}] (nn) {};
+			\node[main, label={(np,pb)}, label=right:{$\bot$}] (np) [right of=nn] {};
+			\node[main, label=below:{(p,npb)}, label=left:{$\bot$}] (pn) [below of=nn] {};
+			\node[main, label=below:{(p,pb)}, label=right:{$p$}] (pp) [right of=pn] {};
+			\draw[-] (nn) to node[above] {$a$} (np);
+			\draw[-] (nn) to node[left] {$b$} (pn);
+			\draw[-] (np) to node[right] {$b$} (pp);
+			\draw[-] (pn) to node[below] {$a$} (pp);
+		\end{tikzpicture}
+	\end{center}
+\end{multicols}
+\begin{multicols}{2}
+	\[M^\prime = (\text{Read};\text{Read}_b)^\prime=\left<S^\prime,\sim^\prime,\textbf{pre}^\prime\right>\]
+	\columnbreak
+	\begin{center}
+		\begin{tikzpicture}[
+				node distance={20mm},
+				shorten >=1pt,
+				shorten <=1pt,
+				main/.style = {draw, circle, inner sep=5pt}
+			]
+			\node[main, label={(np,npb)}, label=below:{$\neg p$}] (nn) {};
+			\node[main, label={(p,pb)}, label=below:{$p$}] (pp) [right of=nn] {};
+		\end{tikzpicture}
+	\end{center}
+\end{multicols}
+In order to show that $M$ is emulus to $M^\prime$ we will use the definition in footnote 4 from p.159 of the book.
+We consider the relation
+\[\mathfrak{E} = S \times S^\prime\]
+We will show that $\mathfrak{E}$ is an emulation between $(M,(\text{np,npb}))$ and $(M^\prime,(\text{np,npb}))$.
+We indeed have $\mathfrak{E}((\text{np,npb}),(\text{np,npb}))$
+
+\paragraph{Front}
+\begin{itemize}
+	\item For $\mathfrak{E}((\text{np,npb}),(\text{np,npb}))$ and $(\text{np,npb}) \sim_a (\text{np,pb})$ we have\\
+		$(\text{np,npb}) \sim^\prime_a (\text{np,npb})$ and $\mathfrak{E}((\text{np,npb}),(\text{np,pb}))$
+	\item For $\mathfrak{E}((\text{np,npb}),(\text{np,npb}))$ and $(\text{np,npb}) \sim_b (\text{p,npb})$ we have\\
+		$(\text{np,npb}) \sim^\prime_b (\text{np,npb})$ and $\mathfrak{E}((\text{np,npb}),(\text{p,npb}))$
+	\item For $\mathfrak{E}((\text{np,pb}),(\text{np,npb}))$ and $(\text{np,pb}) \sim_b (\text{p,pb})$ we have\\
+		$(\text{np,pb}) \sim^\prime_b (\text{np,npb})$ and $\mathfrak{E}((\text{np,npb}),(\text{p,pb}))$
+	\item For $\mathfrak{E}((\text{p,npb}),(\text{np,npb}))$ and $(\text{p,npb}) \sim_a (\text{p,pb})$ we have\\
+		$(\text{p,npb}) \sim^\prime_a (\text{np,npb})$ and $\mathfrak{E}((\text{np,npb}),(\text{p,pb}))$
+\end{itemize}
+
+\paragraph{Back}
+For each $\text{t}^\prime \in S^\prime$ we only have $\text{t}^\prime \sim^\prime_a \text{t}^\prime$ and $\text{t}^\prime \sim^\prime_b \text{t}^\prime$ so for $\mathfrak{E}(\text{t},\text{t}^\prime)$ we selecting $\text{t}$ again suffices since also $\text{t} \sim_a \text{t}$ and $\text{t} \sim_b \text{t}$
+
+\paragraph{Pre}
+For all $\mathfrak{E}(\text{t},(\text{np,npb})), \text{t} \in S$ iy holds that there are $(\text{np,npb}),(\text{p,pb}) \in S^\prime$ where
+\[\textbf{pre}(\text{t}) \models \textbf{pre}^\prime(\text{np,npb}) \lor \textbf{pre}^\prime(\text{p,pb}) \Rightarrow \textbf{pre}(\text{t}) \models p \lor \neg p \Rightarrow \textbf{pre}(\text{t}) \models \top\]
+which holds for all $\text{t} \in S$. For the reverse we only need to select t and (np,npb) and
+\[\textbf{pre}^\prime(\text{np,npb}) \models \text{pre(t)} \lor \textbf{pre}(\text{np,npb}) \Rightarrow \neg p \models \text{pre(t)} \lor \neg p\]
+which holds, and therefore $\mathfrak{E}$ is an emulation between $(M,(\text{np,npb}))$ and $(M^\prime,(\text{np,npb}))$.
+\\[8pt]
+Likewise we can show that $\mathfrak{E}$ is an emulation between $(M,(\text{p,pb}))$ and $(M^\prime,(\text{p,pb}))$ and therefore $\mathfrak{E}$ is a total emulation.
+
+\section*{Exercise 6}
+
+We will use the Example 6.38 of the book where $\vdash_{\textbf{AMC}} [\text{Read, p}]K_a p$.
+We also note that using the same logic we get $\vdash_{\textbf{AMC}} [\text{Read, np}]K_a \neg p$.\\
+So we have
+\begin{footnotesize}
+\begin{logicproof}{1}
+	\vdash_{\textbf{AMC}} [\text{Read, p}]K_a p & (Example 6.38) \\
+	\vdash_{\textbf{AMC}} [\text{Read, p}](K_a p \lor K_a \neg p) & (1, propositional) \\
+	\vdash_{\textbf{AMC}} K_b[\text{Read, p}](K_a p \lor K_a \neg p) & (2, necessitation of $K_b$) \\
+	\vdash_{\textbf{AMC}} p \rightarrow K_b[\text{Read, p}](K_a p \lor K_a \neg p) & (3, weakening) \\
+	\vdash_{\textbf{AMC}} [\text{Read, np}]K_a \neg p & (Example 6.38 for np) \\
+	\vdash_{\textbf{AMC}} [\text{Read, np}](K_a p \lor K_a \neg p) & (5, propositional) \\
+	\vdash_{\textbf{AMC}} K_b[\text{Read, p}](K_a p \lor K_a \neg p) & (6, necessitation of $K_b$) \\
+	\vdash_{\textbf{AMC}} p \rightarrow K_b[\text{Read, p}](K_a p \lor K_a \neg p) & (7, weakening) \\
+	\vdash_{\textbf{AMC}} [\text{Read, p}]K_b(K_a p \lor K_a \neg p) \leftrightarrow (p \rightarrow \bigwedge_{\text{s} \sim_b \text{t}} K_b[\text{Read, t}](K_a p \lor K_a \neg p)) & (pre(p) $=p$, action and knowledge) \\
+	\vdash_{\textbf{AMC}} [\text{Read, p}]K_b(K_a p \lor K_a \neg p) & ($[\text{p}]_{\sim_b} = \{\text{p,np}\}$, 4,8,9, propositional)
+\end{logicproof}
+\end{footnotesize}
 

### 2021-10-26 ml/Ergasia1.Rmd
ML: Ergasia1: Added Ask1 with testthat unit tests, which were added to renv.lock

% !TeX program = XeLaTeX
---
title: "Εργασία 1"
author: "Θωμάς Παππάς"
date: "26/10/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::read_chunk('R/ergasia1.R')
```

# Άσκηση 1
```{r ask1_nnk}
```

### 2021-10-26 ml/R/ergasia1.R

@@ -1,0 +1,34 @@
+## ---- ask1_nnk
+d2 = function(x, y)
+{
+  return(sqrt(sum((x-y)^2)))
+}
+
+nnk = function (X, y, k, x0)
+{
+  # First some input checking.
+  if (!is.matrix(X))
+  {
+    print("X needs to be a matrix.")
+    return(FALSE)
+  } else if (!is.vector(y))
+  {
+    print("y needs to be a vector")
+    return(FALSE)
+  } else if (!is.numeric(k))
+  {
+    print("k needs to be a number")
+    return(FALSE)
+  } else if (length(X[1,]) != length(x0))
+  {
+    print("X column and x0 length should be the same")
+    return(FALSE)
+  }
+  
+  # Now calculate the Nearest Neighbor.
+  xdist = apply(X, 1, d2, y=x0)
+  dsort = sort(xdist, index.return=TRUE)
+  Nk = dsort$ix[1:k]
+  f = mean(y[Nk])
+  return(f)
+}

### 2021-10-26 ml/tests/test_ergasia1.R

@@ -1,0 +1,21 @@
+source('../R/ergasia1.R')
+
+library(testthat)
+
+test_that("Euclidian distance", {
+  expect_equal(d2(9, 1), 8)
+  expect_equal(d2(c(1, 1), c(4, 5)), 5)
+})
+
+test_that("Nearest Neighbour (k)", {
+  X = rbind(
+    c(0, 0), c(1, 1), c(3, 4), c(4, 5)
+  )
+  y = c(4, 2, 11, 1)
+  Ey = mean(y)
+  expect_equal(nnk(X, y, 1, c(0, 0)), 4)
+  expect_equal(nnk(X, y, 1, c(3, 3)), 11)
+  expect_equal(nnk(X, y, 2, c(1.5, 1.5)), 3)
+  expect_equal(nnk(X, y, 4, c(2,2)), Ey)
+  expect_equal(nnk(X, y, 4, c(4,5)), Ey)
+})

### 2021-10-26 ml/Ergasia1.Rmd
ML: Ergasia1: Added Ask2 with ozone dataset (and unit tests)

@@
 # Άσκηση 1
+
 ```{r ask1_nnk}
 ```
+
+# Άσκηση 2
+
+Αρχικά φορτώνουμε τα δεδομένα.
+```{r}
+ozone = read.csv("data/ozone.data", sep="\t")
+```
+
+## Βήμα 1
+
+Πρώτα δημιουργούμε μια τυχαία μετάθεση των αριθμών 1-111 (μέχρι και τον συνολικό
+αριθμό των γραμμών των δεδομένων) έτσι ώστε να πάρουμε μια τυχαία διαμέριση.
+```{r}
+size = nrow(ozone)
+partition_index = 80
+
+sample_indexes = sample(size)
+train_set = ozone[sample_indexes[1:partition_index],]
+test_set = ozone[sample_indexes[(partition_index+1):size],]
+```
+
+## Βήμα 2
+
+Στη συνέχεια χωρίζουμε το κάθε dataset στις ανεξάρτητες και εξαρτημένες
+μεταβλητές αντίστοιχα
+```{r}
+m = ncol(train_set)
+X_train = data.matrix(train_set[, m-1])
+X_test = data.matrix(test_set[, m-1])
+y_train = train_set[, m]
+y_test = test_set[, m]
+```
+
+και ορίζουμε συνάρτηση που να υπολογίζει το μέσο τετραγωνικό σφάλμα.
+```{r ask1_epek}
+```
+
+και έτσι τώρα μπορούμε για ολα τα ζητούμενα k να εφαρμόσουμε το nnk και να
+υπολογίσουμε το μέσο τετραγωνικό σφάλμα της πρόβλεψής μας.
+```{r}
+k_values = c(1, 2, 5, 10, 15, 20, 30, 40)
+epe_values = rep(0, length(k_values))
+
+for (i in 1:length(k_values))
+{
+  y_pred = apply(X_test, 1, nnk, x=X_train, y=y_train, k=k_values[i])
+  epe_values[i] = epe(y_pred, y_test)
+}
+print(epe_values)
+```
+
+## Βήμα 3
+
+Τέλος το γράφημα του μέσου σφάλματος πρόβλεψης ως συνάρτησης του k.
+```{r}
+plot(k_values, epe_values)
+```
+
+όπου παρατηρούμε ότι όσο ανεβαίνει το k και άρα το bias μεγαλώνει τότε
+το variance πέφτει.

### 2021-10-26 ml/R/ergasia1.R

@@ -4,12 +4,12 @@ d2 = function(x, y)
   return(sqrt(sum((x-y)^2)))
 }
 
-nnk = function (X, y, k, x0)
+nnk = function (x, y, k, x0)
 {
   # First some input checking.
-  if (!is.matrix(X))
+  if (!is.matrix(x))
   {
-    print("X needs to be a matrix.")
+    print("x needs to be a matrix.")
     return(FALSE)
   } else if (!is.vector(y))
   {
@@ -19,16 +19,22 @@ nnk = function (X, y, k, x0)
   {
     print("k needs to be a number")
     return(FALSE)
-  } else if (length(X[1,]) != length(x0))
+  } else if (length(x[1,]) != length(x0))
   {
     print("X column and x0 length should be the same")
     return(FALSE)
   }
   
   # Now calculate the Nearest Neighbor.
-  xdist = apply(X, 1, d2, y=x0)
+  xdist = apply(x, 1, d2, y=x0)
   dsort = sort(xdist, index.return=TRUE)
   Nk = dsort$ix[1:k]
   f = mean(y[Nk])
   return(f)
+}
+
+## ---- ask1_epek
+epe = function(y_pred, y_test)
+{
+  return(sum((y_pred-y_test)^2) / length(y_pred))
 }

### 2021-10-26 ml/tests/test_ergasia1.R

@@ -2,20 +2,27 @@ source('../R/ergasia1.R')
 
 library(testthat)
 
+# Set some dummy data.
+X = rbind(
+  c(0, 0), c(1, 1), c(3, 4), c(4, 5)
+)
+y = c(4, 2, 11, 1)
+Ey = mean(y)
+
 test_that("Euclidian distance", {
   expect_equal(d2(9, 1), 8)
   expect_equal(d2(c(1, 1), c(4, 5)), 5)
 })
 
 test_that("Nearest Neighbour (k)", {
-  X = rbind(
-    c(0, 0), c(1, 1), c(3, 4), c(4, 5)
-  )
-  y = c(4, 2, 11, 1)
-  Ey = mean(y)
   expect_equal(nnk(X, y, 1, c(0, 0)), 4)
   expect_equal(nnk(X, y, 1, c(3, 3)), 11)
   expect_equal(nnk(X, y, 2, c(1.5, 1.5)), 3)
   expect_equal(nnk(X, y, 4, c(2,2)), Ey)
   expect_equal(nnk(X, y, 4, c(4,5)), Ey)
+})
+
+test_that("Expected Prediction Error", {
+  expect_equal(epe(y, y), 0)
+  expect_equal(epe(y, c(4, 0, 11, 1)), 1)
 })

### 2021-10-27 ml/Ergasia1.Rmd
ML: Ergasia1: Fixed nnk algorithm to take data frames and corrected train and test set definitions

@@
 ```{r}
-m = ncol(train_set)
-X_train = data.matrix(train_set[, m-1])
-X_test = data.matrix(test_set[, m-1])
-y_train = train_set[, m]
-y_test = test_set[, m]
+independent_vars = c("radiation", "temperature", "wind")
+X_train = train_set[, independent_vars]
+X_test = test_set[, independent_vars]
+y_train = train_set$ozone
+y_test = test_set$ozone
 ```

### 2021-10-27 ml/R/ergasia1.R

@@ -7,9 +7,9 @@ d2 = function(x, y)
 nnk = function (x, y, k, x0)
 {
   # First some input checking.
-  if (!is.matrix(x))
+  if (!is.matrix(x) && !is.data.frame(x))
   {
-    print("x needs to be a matrix.")
+    print("x needs to either be a matrix or a data frame.")
     return(FALSE)
   } else if (!is.vector(y))
   {
@@ -23,6 +23,12 @@ nnk = function (x, y, k, x0)
   {
     print("X column and x0 length should be the same")
     return(FALSE)
+  }
+  
+  # If X is a data frame, convert it to a matrix.
+  if (is.data.frame(x))
+  {
+    x = data.matrix(x)
   }
   
   # Now calculate the Nearest Neighbor.

### 2021-10-27 ml/tests/test_ergasia1.R

@@ -15,11 +15,18 @@ test_that("Euclidian distance", {
 })
 
 test_that("Nearest Neighbour (k)", {
+  # Test with X as matrix.
   expect_equal(nnk(X, y, 1, c(0, 0)), 4)
   expect_equal(nnk(X, y, 1, c(3, 3)), 11)
   expect_equal(nnk(X, y, 2, c(1.5, 1.5)), 3)
   expect_equal(nnk(X, y, 4, c(2,2)), Ey)
   expect_equal(nnk(X, y, 4, c(4,5)), Ey)
+  
+  # Repeat some of the tests with X as data frame.
+  X_df = data.frame(X)
+  expect_equal(nnk(X_df, y, 1, c(0, 0)), 4)
+  expect_equal(nnk(X_df, y, 2, c(1.5, 1.5)), 3)
+  expect_equal(nnk(X_df, y, 4, c(4,5)), Ey)
 })
 
 test_that("Expected Prediction Error", {

### 2021-10-27 ml/Ergasia1.Rmd
ML: Ergasia1: Added Ask3 with the 'neighbr' package

@@
 το variance πέφτει.
+
+# Άσκηση 3
+
+Θα χρησιμοποιήσουμε τη μέθοδο "knn" από το πακέτο "neighbr".
+Σε αυτή τη μέθοδο το training set χρειάζεται να έχει και την target στήλη ενώ
+το test set όχι.
+Οπότε για τα ίδια k επαναλαμβάνουμε
+```{r}
+epe_values_pack = rep(0, length(k_values))
+for (i in 1:length(k_values))
+{
+  y_pred_pack = neighbr::knn(
+    train_set=train_set,
+    test_set=X_test,
+    k=k_values[i],
+    comparison_measure="euclidean",
+    continuous_target="ozone"
+  )
+  # Now the predictions are in the "test_set_scores" column which is a
+  # data frame with the numbers in the "continuous_target" column.
+  y_pred_pack = y_pred_pack$test_set_scores$continuous_target
+  epe_values_pack[i] = epe(y_pred_pack, y_test)
+}
+print(epe_values_pack)
+```
+
+και τέλος κατασκευάζουμε και το γράφημα
+```{r}
+plot(k_values, epe_values_pack)
+```

### 2022-04-22 ads/2021/ask_s01.tex
ADS: Moved the 2021 ask_s01 to a directory

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
  % you may want to try: {Liberation Serif} or {Times New Roman}
\setmainfont{FreeSerif}
  % you may want to try: {Liberation Sans} or {Arial}
\setsansfont[Scale=MatchLowercase]{FreeSans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{FreeMono}

\usepackage{amsmath}

% Main document
\begin{document}
\title{Αλγοριθμική Επιστήμη Δεδομένων - 1η σειρά ασκήσεων}
\author{Θωμάς Παππάς}
%\date{}
\maketitle

\section*{Άσκηση 1}

\subsection*{Άσκηση 6.3.1}

\paragraph{(a)} Το support για τα μεμονωμένα αντικείμενα, κάνοντας ένα πέρασμα από τα δεδομένα, είναι
\begin{center}
	% Result printed: [4, 6, 8, 8, 6, 4]
	\begin{tabular}{| c | c | c | c | c | c |}
		\hline
		$1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\
		\hline
		$4$ & $6$ & $8$ & $8$ & $6$ & $4$ \\
		\hline
	\end{tabular}
\end{center}

ενώ για τα ζευγάρια αντικειμένων, χρησιμοποιώντας τη μέθοδο Triangular-Matrix βρίσκουμε ότι είναι
\begin{center}
	% Result printed: [2, 3, 2, 1, 0, 3, 4, 2, 1, 4, 4, 2, 3, 3, 2]
	\begin{tabular}{| c | c || c | c || c | c |}
		\hline
		$\{1,2\}$ & $2$ & $\{2,3\}$ & $3$ &$\{3,5\}$ & $4$ \\
		\hline
		$\{1,3\}$ & $3$ & $\{2,4\}$ & $4$ &$\{3,6\}$ & $2$ \\
		\hline
		$\{1,4\}$ & $2$ & $\{2,5\}$ & $2$ &$\{4,5\}$ & $3$ \\
		\hline
		$\{1,5\}$ & $1$ & $\{2,6\}$ & $1$ &$\{4,6\}$ & $3$ \\
		\hline
		$\{1,6\}$ & $0$ & $\{3,4\}$ & $4$ &$\{5,6\}$ & $2$ \\
		\hline
	\end{tabular}
\end{center}

\paragraph{(b)} Χρησιμοποιώντας τον κανόνα $\{i,j\} \rightarrow i \times j \bmod 11$ βρίσκουμε ότι τα ζευγάρια αντικειμένων αντιστοιχίζονται ως εξής:
\begin{center}
	\begin{tabular}{| c | c || c | c || c | c |}
		\hline
		$\{1,2\}$ & $2$ & $\{2,3\}$ & $6$ &$\{3,5\}$ & $4$ \\
		\hline
		$\{1,3\}$ & $3$ & $\{2,4\}$ & $8$ &$\{3,6\}$ & $7$ \\
		\hline
		$\{1,4\}$ & $4$ & $\{2,5\}$ & $10$ &$\{4,5\}$ & $9$ \\
		\hline
		$\{1,5\}$ & $5$ & $\{2,6\}$ & $1$ &$\{4,6\}$ & $2$ \\
		\hline
		$\{1,6\}$ & $6$ & $\{3,4\}$ & $1$ &$\{5,6\}$ & $8$ \\
		\hline
	\end{tabular}
\end{center}

% Hash support on first pass: [0, 5, 5, 3, 6, 1, 3, 2, 6, 3, 2]
\paragraph{(c)} Από τα buckets που φτιάξαμε από το hash table στο first pass, αυτά που είναι συχνά είναι (ξεκινώντας το μέτρημα από το $0$) τα $1,2,4,8$.

\paragraph{(d)} Τα ζευγάρια που θα μετρηθούν στο 2ο πέρασμα του αλγόριθμου PCY είναι αυτά στα οποία και τα δύο στοιχεία είναι συχνά, αλλά και το ζευγάρι αντιστοιχεί σε hash bucket που είναι συχνός.
Εφόσον όλα τα μονοσύνολα είναι συχνά, από τα hash buckets παίρνουμε ότι θα μετρηθούν τα:
\begin{itemize}
	\item $\{2,6\},\{3,4\}$ (hash bucket $1$)
	\item $\{1,2\},\{4,6\}$ (hash bucket $2$)
	\item $\{1,4\},\{3,5\}$ (hash bucket $4$)
	\item $\{2,4\},\{5,6\}$ (hash bucket $8$)
\end{itemize}

\subsection*{Άσκηση 6.3.2}

Τρέχουμε τον Multistage αλγόριθμο με τα ίδια στοιχεία και το νέο hash κανόνα.
% Hash support on second pass: [0, 3, 2, 2, 0, 2, 4, 4, 5]
Στο νέο hash table μόνο τα buckets $6,7,8$ γίνονται συχνά, άρα τα υποψήφια ζευγάρια όντως μειώνονται στα
\[\{2,4\},\{2,6\},\{3,4\},\{3,5\}\]

\subsection*{Άσκηση 6.4.2}

\paragraph{(a)} Τρέχοντας τον αλγόριθμο Toivonen στα προηγούμενα δεδομένα στο δείγμα\\ $\{1,2,3\},\{2,3,4\},\{3,4,5\},\{4,5,6\}$ με support $1$ βρίσκουμε τα παρακάνω συχνά σύνολα:
\begin{itemize}
	\item $\{1\},\{2\},\{3\},\{4\},\{5\},\{6\}$
	\item $\{1,2\},\{1,3\},\{2,3\},\{2,4\},\{3,4\},\{3,5\},\{4,5\},\{4,6\},\{5,6\}$
	\item $\{1,2,3\},\{2,3,4\},\{3,4,5\},\{4,5,6\}$
\end{itemize}

\paragraph{(b)} Το negative border του δείγματος είναι όλα τα ζευγάρια που δεν είναι συχνά (αφού όλα τα μονοσύνολα είναι συχνά), δηλαδή
\[\{1,4\},\{1,5\},\{1,6\},\{2,5\},\{2,6\},\{3,6\}\]
και κανένα από τα σύνολα με $3$ στοιχεία αφού αυτά που έχουν όλα τους τα υποσύνολα συχνά βρίσκονται ήδη στο δείγμα.

\paragraph{(c)} Εφόσον το negative border αποτελείται μόνο από ζευγάρια στοιχείων, βλέποντας τον πίνακα συχνών ζευγαριών από την άσκηση $6.3.1$-a βρίσκουμε ότι \textbf{κανένα} από τα στοιχεία του negative border δεν είναι συχνό σε ολόκληρο το σύνολο δεδομένων.

%\section*{Άσκηση 2}

\section*{Άσκηση 3}

\paragraph{(α)} Έστω τα στοιχεία $k_1,k_2 \in U$ με $k_1 \leq m$ και $k_2 = k_1+m \leq m^k$.
Προφανώς $k_1 \neq k_2$ και $k_1 \equiv k_2 \bmod m$.
Θα δείξουμε ότι $\forall a \in [m] \setminus 0, b \in [m]$ θα έχουμε $h_{a,b}(k_1) = h_{a,b}(k_2)$.
Όντως
\[k_1 \equiv k_2 \bmod m \Rightarrow ak_1+b \equiv ak_2+b \bmod m \Leftrightarrow h_{a,b}(k_1) = h_{a,b}(k_2)\]
και εφόσον αυτό ισχύει $\forall a$ άρα η πιθανότητα να έχουμε $h_{a,b}(k_1) = h_{a,b}(k_2)$ είναι $1 \geq \frac1{m}$, και άρα αυτή η οικογένεια συναρτήσεων κατακερματισμού δεν είναι καθολική.

\paragraph{(β)} Έστω $k_1,k_2 \in U$ με $k_1 \neq k_2$.
Θα δείξουμε ότι $h_{a,b}(k_1) \neq h_{a,b}(k_2), \forall h \in H$, ή αλλιώς ότι $\Pr_{h_{a,b} \in H}[h_{a,b}(k_1) = h_{a,b}(k_2)] = 0$.
\\[8pt]
Εφόσον $p$ πρώτος, τότε $\forall a \in [p] \setminus 0, \exists a^{-1} : a \cdot a^{-1} \equiv 1 \bmod p$.
Οπότε έστω ότι υπάρχουν $a,b$ τέτοια ώστε $h_{a,b}(k_1) = h_{a,b}(k_2)$.
Τότε έχουμε
\begin{flalign*}
	h_{a,b}(k_1) = h_{a,b}(k_2) &\Rightarrow ak_1+b \equiv ak_2+b \bmod p \Rightarrow ak_1 \equiv ak_2 \bmod p &\\
		&\Rightarrow a^{-1} \cdot ak_1 \equiv a^{-1} \cdot ak_2 \bmod p \Rightarrow k_1 \equiv k_2 \bmod p
\end{flalign*}
με $0 \leq k_1,k_2 \leq m^k < p$, και άρα $k_1 = k_2$, άτοπο.
\\[8pt]
Άρα έχουμε $h_{a,b}(k_1) \neq h_{a,b}(k_2), \forall h \in H$, ή αλλιώς
\[\Pr_{h_{a,b} \in H}[h_{a,b}(k_1) = h_{a,b}(k_2)] = 0 < \frac1{m}\]
και άρα η οικογένεια συναρτήσεων $H$ είναι καθολική.

\paragraph{(γ)} Θέτοντας $U=[p]$ παρατηρούμε ότι η παραπάνω απόδειξη παραμένει απαράλλαχτη, εφόσον για μια τυχαία επιλογή  $k_1,k_2 \in U$ έχουμε πάλι $h_{a,b}(k_1) = h_{a,b}(k_2) \Rightarrow k_1 \equiv k_2 \bmod p$, και αφού $0 \leq k_1,k_2 < p$ παίρνουμε πάλι $k_1 \equiv k_2 \bmod p \Rightarrow k_1 = k_2$.
\\[8pt]
Άρα με τον ίδιο συλλογισμό καταλήγουμε ότι η ιδιότητα της καθολικότητας διατηρείται.

%\section*{Άσκηση 4}

%\paragraph{(α)} Ο χρόνος εισαγωγής του $i$-οστού στοιχείου είναι ένα τυχαίο γεγονός που ακολουθεί την κατανομή Bernoulli($m-i/m$).
%Άρα ο αναμενόμενος αριθμός επαναλήψεων μέχρι την πρώτη επιτυχία είναι $m/m-i$ (εφόσον αυτό ακολουθεί Geom($m-i/m$)).
%\paragraph{(α)} Μετά από την εισαγωγή $n$ στοιχείων, η επιτυχής αναζήτηση .
%Άρα ο αναμενόμενος αριθμός επαναλήψεων μέχρι την πρώτη επιτυχία είναι $1/(1-a)$ (εφόσον αυτό ακολουθεί Geom($1-a$)).
%\\[8pt]
%Από την άλλη, με την ίδια λογική, ο χρόνος εισαγωγής του $i$-οστού στοιχείου είναι $m/m-i$, εφόσον εδώ η πιθανότητα επιτυχίας να βρεθεί κενή θέση είναι $m-i/m$.

\end{document}

### 2022-05-10 ads/ask_s01.tex
ADS: Exer01: Added tex file with ex.1 along with helping python code
Python code taken from 2021 solution, tex file also for overlapping exercises but improved

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
  % you may want to try: {Liberation Serif} or {Times New Roman}
\setmainfont{FreeSerif}
  % you may want to try: {Liberation Sans} or {Arial}
\setsansfont[Scale=MatchLowercase]{FreeSans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{FreeMono}

\usepackage{amsmath}
\usepackage{hhline}

% Main document
\begin{document}
\title{Αλγοριθμική Επιστήμη Δεδομένων - 1η Σειρά Ασκήσεων}
\author{Θωμάς Παππάς}
%\date{}
\maketitle

\section*{Άσκηση 1}

\subsection*{Άσκηση 6.3.1 (MMDS)}

\paragraph{(a)} Το support για τα μεμονωμένα αντικείμενα, κάνοντας ένα πέρασμα από τα δεδομένα, είναι
\begin{center}
	% Result printed: [4, 6, 8, 8, 6, 4]
	\begin{tabular}{| r || c | c | c | c | c | c |}
		\hline
		item & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\ \hline
		support & $4$ & $6$ & $8$ & $8$ & $6$ & $4$ \\ \hline
	\end{tabular}
\end{center}

ενώ για τα ζευγάρια αντικειμένων, χρησιμοποιώντας τη μέθοδο Multistage (με indexing structure Triangular-Matrix) βρίσκουμε ότι είναι
\begin{center}
	% Result printed: [2, 3, 2, 1, 0, 3, 4, 2, 1, 4, 4, 2, 3, 3, 2]
	\begin{tabular}{| c | c || c | c || c | c |}
		\hline
		pair & support & pair & support & pair & support \\ \hhline{|=|=#=|=#=|=|}
		$\{1,2\}$ & $2$ & $\{2,3\}$ & $3$ & $\{3,5\}$ & $4$ \\ \hline
		$\{1,3\}$ & $3$ & $\{2,4\}$ & $4$ & $\{3,6\}$ & $2$ \\ \hline
		$\{1,4\}$ & $2$ & $\{2,5\}$ & $2$ & $\{4,5\}$ & $3$ \\ \hline
		$\{1,5\}$ & $1$ & $\{2,6\}$ & $1$ & $\{4,6\}$ & $3$ \\ \hline
		$\{1,6\}$ & $0$ & $\{3,4\}$ & $4$ & $\{5,6\}$ & $2$ \\ \hline
	\end{tabular}
\end{center}

\paragraph{(b)} Χρησιμοποιώντας τον κανόνα $\{i,j\} \rightarrow i \times j \bmod 11$ βρίσκουμε ότι τα ζευγάρια αντικειμένων αντιστοιχίζονται στα hash buckets ως εξής:
\begin{center}
	\begin{tabular}{| c | c || c | c || c | c |}
		\hline
		pair & bucket & pair & bucket & pair & bucket \\ \hhline{|=|=#=|=#=|=|}
		$\{1,2\}$ & $2$ & $\{2,3\}$ & $6$ & $\{3,5\}$ & $4$ \\ \hline
		$\{1,3\}$ & $3$ & $\{2,4\}$ & $8$ & $\{3,6\}$ & $7$ \\ \hline
		$\{1,4\}$ & $4$ & $\{2,5\}$ & $10$ & $\{4,5\}$ & $9$ \\ \hline
		$\{1,5\}$ & $5$ & $\{2,6\}$ & $1$ & $\{4,6\}$ & $2$ \\ \hline
		$\{1,6\}$ & $6$ & $\{3,4\}$ & $1$ & $\{5,6\}$ & $8$ \\ \hline
	\end{tabular}
\end{center}

% Hash support on first pass: [0, 5, 5, 3, 6, 1, 3, 2, 6, 3, 2]
\paragraph{(c)} Από τα buckets που φτιάξαμε από το hash table στο 1ο πέρασμα, εφόσον αυξάνουμε κατά 1 το counter του κάθε bucket όταν συναντάμε ένα σύνολο που κάνει hash σε αυτό, παίρνουμε
\begin{center}
	\begin{tabular}{| r | c || r | c || r | c || r | c |}
		\hline
		bucket & count & bucket & count & bucket & count & bucket & count \\
		\hhline{|=|=#=|=#=|=#=|=|}
		$0$ & 0 & $3$ & 3 & $6$ & 3 & $9$ & 3 \\ \hline
		$1$ & 5 & $4$ & 6 & $7$ & 2 & $10$ & 2 \\ \hline
		$2$ & 5 & $5$ & 1 & $8$ & 6 &  & \\ \hline
	\end{tabular}
\end{center}
οπότε τα συχνά buckets είναι τα $1,2,4,8$.

\paragraph{(d)} Τα ζευγάρια που θα μετρηθούν στο 2ο πέρασμα του αλγόριθμου PCY είναι αυτά στα οποία και τα δύο στοιχεία είναι συχνά, αλλά και το ζευγάρι αντιστοιχεί σε hash bucket που είναι συχνός.
Εφόσον όλα τα μονοσύνολα είναι συχνά, από τα hash buckets παίρνουμε ότι θα μετρηθούν τα:
\begin{itemize}
	\item $\{2,6\},\{3,4\}$ (hash bucket $1$)
	\item $\{1,2\},\{4,6\}$ (hash bucket $2$)
	\item $\{1,4\},\{3,5\}$ (hash bucket $4$)
	\item $\{2,4\},\{5,6\}$ (hash bucket $8$)
\end{itemize}

\subsection*{Άσκηση 6.3.2 (MMDS)}
% Hash support on second pass: [0, 3, 2, 2, 0, 2, 4, 4, 5]
Τρέχουμε τον Multistage αλγόριθμο με τα ίδια στοιχεία όπως στην Άσκηση 6.3.1 και το νέο hash κανόνα και παίρνουμε
\begin{center}
	\begin{tabular}{| r | c || r | c || r | c |}
		\hline
		bucket & count & bucket & count & bucket & count \\ \hhline{|=|=#=|=#=|=|}
		$0$ & 0 & $3$ & 2 & $6$ & 4 \\ \hline
		$1$ & 3 & $4$ & 0 & $7$ & 4 \\ \hline
		$2$ & 2 & $5$ & 2 & $8$ & 5 \\ \hline
	\end{tabular}
\end{center}
οπότε μόνο τα buckets $6,7,8$ γίνονται συχνά, και άρα τα υποψήφια ζευγάρια όντως μειώνονται στα
\[\{2,4\},\{2,6\},\{3,4\},\{3,5\}\]

\subsection*{Άσκηση 6.4.1}

Με οχτώ items $A,B,\dots,H$ και συχνά itemsets $\{A,B\},\{B,C\},\{A,C\},\{A,D\},\{E\},\{F\}$, το Negative Border αποτελείται από
\begin{itemize}
	\item τα μη συχνά 1-itemsets $\{G\},\{H\}$
	\item όλα τα μη συχνά 2-itemsets που είναι συνδυασμός από συχνά 1-itemsets, εδώ τα $A,B,\dots,F$
		\[
			\{A,E\},\{A,F\},\{B,D\},\{B,E\},\{B,F\},\{C,D\},\{C,E\},\{C,F\},\{D,E\},\{D,F\},\{E,F\}
		\]
	\item το $\{A,B,C\}$, το μοναδικό 3-itemset που έχει όλα τα υποσύνολά του συχνά
\end{itemize}

\end{document}

### 2022-05-10 ads/ask_s01.py

@@ -1,0 +1,124 @@
+# Exercise 1
+
+
+class Multistage:
+    # Class implementing the Multistage algorithm.
+
+    def __init__(self, baskets, support_threshold):
+        # Initiate the class
+        self.baskets = baskets
+        self.support_threshold = support_threshold
+
+        # Count the support for the singletons and the pairs.
+        self.singletons_support = [0 for i in range(6)]
+        self.pairs_support = [0 for j in range(15)]
+        # Also hash the pairs into buckets.
+        self.hash_buckets = [0 for k in range(11)]
+        self.hash_buckets_multistage = [0 for m in range(9)]
+
+    @property
+    def singletons_support(self):
+        return self._singletons_support
+
+    @singletons_support.setter
+    def singletons_support(self, value):
+        self._singletons_support = value
+
+    @property
+    def pairs_support(self):
+        return self._pairs_support
+
+    @pairs_support.setter
+    def pairs_support(self, value):
+        self._pairs_support = value
+
+    @property
+    def hash_buckets(self):
+        return self._hash_buckets
+
+    @hash_buckets.setter
+    def hash_buckets(self, value):
+        self._hash_buckets = value
+
+    @property
+    def hash_buckets_multistage(self):
+        return self._hash_buckets_multistage
+
+    @hash_buckets_multistage.setter
+    def hash_buckets_multistage(self, value):
+        self._hash_buckets_multistage = value
+
+    # Get the index using the Triangular-Matrix method.
+    @staticmethod
+    def triangular_matrix_index(i, j):
+        k = (i - 1) * (6 - i / 2) + j - i
+        return int(k)
+
+    # Calculate the hash for the first pass.
+    @staticmethod
+    def hash_first_pass(pair):
+        return (pair[0] * pair[1]) % 11
+
+    # Calculate the hash for the second pass.
+    @staticmethod
+    def hash_second_pass(pair):
+        return (pair[0] + pair[1]) % 9
+
+    # Given a list with counts, return a boolean list of whether the respective item is frequent.
+    def get_is_frequent(self, count_list):
+        is_frequent = []
+        for count in count_list:
+            is_frequent.append(True if count >= self.support_threshold else False)
+        return is_frequent
+
+    def run(self):
+        # First pass.
+        for basket in self.baskets:
+            for i in range(3):
+                item = basket[i]
[…]

### 2022-05-11 ads/ask_s01.tex
ADS: Exer01: Added exercise 2
Didn't elaborate on the b subquestion

@@
 
-\usepackage{amsmath}
+%\usepackage{amsmath}
 \usepackage{hhline}
+\usepackage{tikz}
+\usetikzlibrary{positioning}
 
@@
 \author{Θωμάς Παππάς}
-%\date{}
+\date{12 Μαΐου 2022}
 \maketitle
@@
 % Hash support on second pass: [0, 3, 2, 2, 0, 2, 4, 4, 5]
-Τρέχουμε τον Multistage αλγόριθμο με τα ίδια στοιχεία όπως στην Άσκηση 6.3.1 και το νέο hash κανόνα και παίρνουμε
+Τρέχουμε τον Multistage αλγόριθμο και κάνουμε hash τα στοιχεία που βρήκαμε συχνά στην Άσκηση 6.3.1 με το νέο hash κανόνα.
+Το hash table που παίρνουμε είναι
 \begin{center}
@@
 
+\section*{Άσκηση 2}
+
+\paragraph{(α)} Η ορθότητα της μεθόδου A-priori βασίζεται στην αντι-μονοτονικότητα της συνάρτησης support, δηλαδή $\forall X,Y: X \subseteq Y$ έχουμε $\textnormal{support}(X) \geq \textnormal{support}(Y)$.
+Από αυτό παίρνουμε ότι αν ένα itemset είναι συχνό, τότε και όλα τα υποσύνολά του είναι συχνά, και άρα στο βήμα παραγωγής υποψηφίων itemsets όπου βάζουμε μόνο αυτά που ικανοποιούν αυτή τη συνθήκη, ξέρουμε ότι δεν θα προσπεράσουμε κάποιο που είναι όντως συχνό.
+
+Με αυτόν τον αλγόριθμο πραγματοποιούνται τόσες διασχίσεις στη βάση δεδομένων όσο και το μήκος του μεγαλύτερου συχνού itemset, αφού απαιτείται μετά από κάθε παραγωγή $C_i$ συνόλου.
+
+\paragraph{(β)} Είναι πολυωνυμική ως προς την έξοδο, διότι όπως αναφέραμε και στο \textbf{(α)}, πραγματοποιούνται τόσες διασχίσεις στη βάση δεδομένων όσο και το μήκος του μεγαλύτερου συχνού itemset.
+
+\paragraph{(γ)} Ο FP-Growth αρχικά χρειάζεται 2 περάσματα στη βάση δεδομένων ώστε να κατασκευάσει το FP-trie structure.
+Από εκεί και πέρα θα χρειαστεί να διασχίσει το δέντρο σε κάθε βήμα ώστε να φτιάξει τα υποδέντρα, να κάνεις τις ανανεώσεις στις συχνότητες και να υπολογίσει το πλήθος των υπόλοιπων στοιχείων.
+Εφόσον η διάσχιση του δέντρου μπορεί να γίνει σε γραμμικό χρόνο, η πολυπλοκότητα εξαρτάται πιο πολύ από τον αριθμό των βημάτων που θα χρειαστούν, δηλαδή πάλι ανάλογα με το μήκος του μεγαλύτερου συχνού itemset.
+Οπότε και ο FP-Growth αλγόριθμος είναι πολυωνυμικός ως προς την έξοδο.
+\\[8pt]
+Για την πολυπλοκότητα του αλγορίθμου ίσως αξίζει να αναφέρουμε και τη σχέση που έχει ως προς το πλήθος των items $k$.
+Tο μέγεθος του δέντρου που θα προκύψει εξαρτάται από το πόσες διαφορετικές λεξικογραφικές εγγραφές αποτελείται η βάση, όπου στη χειρότερη θα μπορούσε να είναι $2^k$.
+Ο αλγόριθμος θα πρέπει να το διασχίσει τουλάχιστον $k$ φορές, μία για κάθε στοιχείο, οπότε στη χειρότερη έχουμε μια πολυπλοκότητα $\mathcal{O}(k2^k)$.
+Εφόσον βέβαια το $k$ είναι μικρός αριθμός σε σχέση με το πλήθος των εγγραφών, ενώ επίσης έχουμε και τη γενική υπόθεση ότι τα συχνά υποσύνολα θα είναι πολύ λιγότερα από το μέγεθος της βάσης, μπορούμε να περιμένουμε ότι ακόμα και σε αυτήν την περίπτωση τα υποδέντρα που θα προκύψουν θα μικρύνουν μετά από ένα μικρό αριθμό βημάτων.
+
+\paragraph{(δ)}
+\subparagraph{Α-priori}
+Ξεκινάμε με το 1ο πέρασμα της βάσης δεδομένων όπου μετράμε τα συχνά 1-itemsets $a,b,c,d$, τα οποία και βρίσκουμε ότι έχουν συχνότητα $7,6,7,9$ αντίστοιχα, οπότε
+\[ L_1 = \{ \{a\},\{b\},\{c\},\{d\} \} \]
+Οπότε όλα τα πιθανά 2-itemsets είναι candidate
+\[ C_2 = \{ \{a,b\},\{a,c\},\{a,d\},\{b,c\},\{b,d\},\{c,d\} \} \]
+τα οποία μετράμε στο 2ο πέρασμα της βάσης και βρίσκουμε ότι έχουν συχνότητα $2,4,5,3,5,4$ αντίστοιχα, οπότε με threshold $s=4$ παίρνουμε
+\[ L_2 = \{ \{a,c\},\{a,d\},\{b,d\},\{c,d\} \} \]
+Συνεχίζοντας για candidate 3-itemsets, αρχικά ψάχνουμε δύο συχνά 2-itemsets που διαφέρουν κατά ένα στοιχείο ώστε με την ένωσή τους να πάρουμε ένα 3-itemset, για το οποίο στη συνέχεια ελέγχουμε εάν όλα τα 2-itemset υποσύνολά του είναι επίσης συχνά.
+Βρίσκουμε τα $\{a,c,d\},\{a,b,d\}$ από τους συνδυασμούς, αλλά το δεύτερο απορρίπτεται διότι το $\{a,b\}$ δεν είναι συχνό.
+Οπότε
+\[ C_3 = \{ \{a,c,d\} \} \]
+το οποίο και μετράμε στη βάση (3ο πέρασμα) και βλέπουμε ότι δεν είναι συχνό.
+Παίρνουμε λοιπόν $L_3 = \emptyset$ και σταματάμε.
+\\[8pt]
+Οπότε τα συχνά υποσύνολα της βάσης δεδομένων είναι τα
+\[ \{ \{a,c\},\{a,d\},\{b,d\},\{c,d\} \} \]
+
+\subparagraph{FP-Growth}
+Ξεκινάμε όπως με τον A-priori και βρίσκουμε τα συχνά 1-itemsets $a,b,c,d$ με συχνότητα $7,6,7,9$ αντίστοιχα.
+Κάνοντας ένα 2ο πέρασμα στη βάση ταξινομούμε τα στοιχεία σε κάθε itemset κατά φθίνουσα συχνότητα, δηλαδή $d,a,c,b$, και φτιάχνουμε το FP-trie.
+\begin{center}
+	\begin{tikzpicture}[
+			node distance=40pt,
+			main/.style = {draw, circle, inner sep=.5pt}
+		]
+		\node[main, label=above:{root}] (r) {};
+		% Level 1.
+		\node[main, below of=r] (a) {$a:2$};
+		\node[main, left of=a] (d) {$d:9$};
+		\node[main, right of=a] (c) {$c:1$};
+		% Level 2.
+		\node[main, below of=d] (dc) {$c:2$};
+		\node[main, left of=dc] (da) {$a:5$};
+		\node[main, right of=dc] (db) {$b:2$};
+		\node[main, below right of=a] (ac) {$c:2$};
+		\node[main, below right of=c] (cb) {$b:1$};
+		% Level 3.
+		\node[main, below of=da] (dac) {$c:2$};
+		\node[main, left of=dac] (dab) {$b:1$};
+		\node[main, below of=dc] (dcb) {$b:1$};
+		% Level 4.
+		\node[main, below of=dac] (dacb) {$b:1$};
+
+		\draw[->] (r) to (a);
+		\draw[->] (r) to (d);
+		\draw[->] (r) to (c);
+		\draw[->] (d) to (dc);
+		\draw[->] (d) to (da);
+		\draw[->] (d) to (db);
+		\draw[->] (a) to (ac);
+		\draw[->] (c) to (cb);
+		\draw[->] (da) to (dac);
+		\draw[->] (da) to (dab);
+		\draw[->] (dc) to (dcb);
+		\draw[->] (dac) to (dacb);
+	\end{tikzpicture}
+\end{center}
+
+Τώρα θα δούμε τα υποδέντρα που καταλήγουν σε κάθε στοιχείο.
+Ξεκινάμε με το $b$ που έχει τη μικρότερη συχνότητα οπότε φτιάχνουμε το υποδέντρο μονοπατιών που καταλήγουν σε αυτό και ανανεώνουμε συχνότητες.
+\begin{center}
+	\begin{tikzpicture}[
+			node distance=40pt,
+			main/.style = {draw, circle, inner sep=.5pt}
+		]
+		\node[main, label=above:{root}] (r) {};
+		% Level 1.
+		\node[main, below left of=r] (d) {$d:9$};
+		\node[main, below right of=r] (c) {$c:1$};
+		% Level 2.
+		\node[main, below of=d] (dc) {$c:2$};
+		\node[main, left of=dc] (da) {$a:5$};
+		\node[main, right of=dc] (db) {$b:2$};
+		\node[main, below right of=c] (cb) {$b:1$};
+		% Level 3.
+		\node[main, below of=da] (dac) {$c:2$};
+		\node[main, left of=dac] (dab) {$b:1$};
+		\node[main, below of=dc] (dcb) {$b:1$};
+		% Level 4.
+		\node[main, below of=dac] (dacb) {$b:1$};
+
+		\draw[->] (r) to (d);
+		\draw[->] (r) to (c);
+		\draw[->] (d) to (dc);
+		\draw[->] (d) to (da);
+		\draw[->] (d) to (db);
+		\draw[->] (c) to (cb);
+		\draw[->] (da) to (dac);
+		\draw[->] (da) to (dab);
+		\draw[->] (dc) to (dcb);
+		\draw[->] (dac) to (dacb);
+	\end{tikzpicture}
+	\begin{tikzpicture}[
+			node distance=40pt,
+			main/.style = {draw, circle, inner sep=.5pt}
+		]
+		\node[main, label=above:{root}] (r) {};
+		% Level 1.
+		\node[main, below left of=r] (d) {$d:\mathbf{5}$};
+		\node[main, below right of=r] (c) {$c:1$};
+		% Level 2.
+		\node[main, below of=d] (dc) {$c:\mathbf{1}$};
+		\node[main, left of=dc] (da) {$a:\mathbf{2}$};
+		\node[main, right of=dc] (db) {$b:2$};
+		\node[main, below right of=c] (cb) {$b:1$};
+		% Level 3.
+		\node[main, below of=da] (dac) {$c:\mathbf{1}$};
+		\node[main, left of=dac] (dab) {$b:1$};
+		\node[main, below of=dc] (dcb) {$b:1$};
+		% Level 4.
+		\node[main, below of=dac] (dacb) {$b:1$};
+
+		\draw[->] (r) to (d);
+		\draw[->] (r) to (c);
+		\draw[->] (d) to (dc);
+		\draw[->] (d) to (da);
+		\draw[->] (d) to (db);
+		\draw[->] (c) to (cb);
+		\draw[->] (da) to (dac);
+		\draw[->] (da) to (dab);
+		\draw[->] (dc) to (dcb);
+		\draw[->] (dac) to (dacb);
+	\end{tikzpicture}
+\end{center}
+Μετράμε τις συχνότητες από τα υπόλοιπα στοιχεία ($a,c,d$) και βρίσκουμε $2,3,5$ αντίστοιχα οπότε εφόσον μόνο το $d$ βγαίνει πάνω από το threshold έχουμε ότι το $\{b,d\}$ συχνό.
+
+Θα μπορούσαμε να συνεχίσουμε να ψάξουμε για συχνά 3-itemsets αλλά εφόσον δεν βρήκαμε άλλο συχνό 2-itemset που να περιέχει το $b$ τότε σίγουρα δεν υπάρχουν 3-itemsets που να το περιέχουν.
+\\[8pt]
+Ομοίως τώρα με το στοιχείο $c$.
+\begin{center}
+	\begin{tikzpicture}[
+			node distance=40pt,
+			main/.style = {draw, circle, inner sep=.5pt}
+		]
+		\node[main, label=above:{root}] (r) {};
+		% Level 1.
+		\node[main, below of=r] (a) {$a:2$};
+		\node[main, left of=a] (d) {$d:9$};
+		\node[main, right of=a] (c) {$c:1$};
+		% Level 2.
+		\node[main, below of=d] (dc) {$c:2$};
+		\node[main, left of=dc] (da) {$a:5$};
+		\node[main, below of=a] (ac) {$c:2$};
+		% Level 3.
+		\node[main, below of=da] (dac) {$c:2$};
+
+		\draw[->] (r) to (a);
+		\draw[->] (r) to (d);
+		\draw[->] (r) to (c);
+		\draw[->] (d) to (dc);
+		\draw[->] (d) to (da);
+		\draw[->] (a) to (ac);
+		\draw[->] (da) to (dac);
+	\end{tikzpicture}
+	\begin{tikzpicture}[
+			node distance=40pt,
+			main/.style = {draw, circle, inner sep=.5pt}
+		]
+		\node[main, label=above:{root}] (r) {};
+		% Level 1.
+		\node[main, below of=r] (a) {$a:2$};
+		\node[main, left of=a] (d) {$d:\mathbf{4}$};
+		\node[main, right of=a] (c) {$c:1$};
+		% Level 2.
+		\node[main, below of=d] (dc) {$c:2$};
+		\node[main, left of=dc] (da) {$a:\mathbf{2}$};
+		\node[main, below of=a] (ac) {$c:2$};
+		% Level 3.
+		\node[main, below of=da] (dac) {$c:2$};
+
+		\draw[->] (r) to (a);
+		\draw[->] (r) to (d);
+		\draw[->] (r) to (c);
+		\draw[->] (d) to (dc);
+		\draw[->] (d) to (da);
+		\draw[->] (a) to (ac);
+		\draw[->] (da) to (dac);
+	\end{tikzpicture}
+\end{center}
+Βρίσκουμε συχνότητα για το $a$ ίση με $2+2=4$ και για το $d$ επίσης $4$.
+Οπότε έχουμε συχνά 2-itemsets τα $\{a,c\},\{c,d\}$.
+
+Συνεχίζουμε για 3-itemsets με μόνο υποψήφιο το $\{a,c,d\}$ οπότε χρησιμοποιώντας το $\{c,d\}$ παίρνουμε το υποδέντρο με τα μονοπάτια που το περιέχει, ανανεώνουμε συχνότητες (πάλι εδώ δεν χρειάζεται) και μετά μετράμε συχνότητα για το $a$.
+(Tο ίδιο αποτέλεσμα θα πάρουμε και εάν χρησιμοποιήσουμε το $\{a,c\}$ και μετά μετρήσουμε τη συχνότητα του $d$)
+\begin{center}
+	\begin{tikzpicture}[
+			node distance=40pt,
+			main/.style = {draw, circle, inner sep=.5pt}
+		]
+		\node[main, label=above:{root}] (r) {};
+		% Level 1.
+		\node[main, below of=r] (d) {$d:4$};
+		% Level 2.
+		\node[main, below right of=d] (dc) {$c:2$};
+		\node[main, below left of=d] (da) {$a:2$};
+		% Level 3.
+		\node[main, below left of=da] (dac) {$c:2$};
+
+		\draw[->] (r) to (d);
+		\draw[->] (d) to (dc);
+		\draw[->] (d) to (da);
+		\draw[->] (da) to (dac);
+	\end{tikzpicture}
+\end{center}
+Βλέπουμε ότι η συχνότητα του $a$ είναι $2$ οπότε το $\{a,c,d\}$ δεν είναι συχνό.
+\\[8pt]
+Συνεχίζουμε ομοίως με το στοιχείο $a$.
+\begin{center}
+	\begin{tikzpicture}[
+			node distance=40pt,
+			main/.style = {draw, circle, inner sep=.5pt}
+		]
+		\node[main, label=above:{root}] (r) {};
+		% Level 1.
+		\node[main, below left of=r] (d) {$d:9$};
+		\node[main, below right of=r] (a) {$a:2$};
+		% Level 2.
+		\node[main, below left of=d] (da) {$a:5$};
+
+		\draw[->] (r) to (d);
+		\draw[->] (r) to (a);
+		\draw[->] (d) to (da);
+	\end{tikzpicture}
+	\begin{tikzpicture}[
+			node distance=40pt,
+			main/.style = {draw, circle, inner sep=.5pt}
+		]
+		\node[main, label=above:{root}] (r) {};
+		% Level 1.
+		\node[main, below left of=r] (d) {$d:\mathbf{5}$};
+		\node[main, below right of=r] (a) {$a:2$};
+		% Level 2.
+		\node[main, below left of=d] (da) {$a:5$};
+
+		\draw[->] (r) to (d);
+		\draw[->] (r) to (a);
+		\draw[->] (d) to (da);
+	\end{tikzpicture}
+\end{center}
+Εφόσον η συχνότητα του $d$ είναι $5$ παίρνουμε ότι το $\{a,d\}$ συχνό.
+Εφόοσον το υποδέντρο έχει μόνο δύο στοιχεία δεν έχει νόημα να ψάξουμε για 3-itemsets, ενώ για τον ίδιο λόγο δεν έχει νόημα να κοιτάξουμε το στοιχείο $d$ (το υποδέντρο θα έχει μόνο έναν κόμβο πέρα από το root).
+\\[8pt]
+Οπότε τα συχνά υποσύνολα της βάσης δεδομένων είναι τα
+\[ \{ \{a,c\},\{a,d\},\{b,d\},\{c,d\} \} \]
+
+\paragraph{(ε)}
+\subparagraph{$s^\prime=1$} Με threshold $s^\prime$ από τις 3 πρώτες εγγραφές παίρνουμε ότι τα υποψήφια συχνά itemets είναι τα
+\[ \{a,c,d\},\{b,c,d\} \]
+προφανώς μαζί με όλα τα υποσύνολά τους.
+Το Negative Border είναι το σύνολο $\{ \{a,b\} \}$ εφόσον αυτό είναι το μοναδικό 2-itemset που δεν είναι συχνό (τα 1-itemsets είναι όλα συχνά), ενώ τα 3-itemsets που δεν είναι συχνά είναι τα $\{a,b,c\},\{a,b,d\}$ τα οποία και τα δύο έχουν υποσύνολο το $\{a,b\}$.
+Τέλος προφανώς και το 4-itemset $\{a,b,c,d\}$ επίσης δεν είναι στο Negative Border.
+
+Με έναν έλεγχο στη βάση βλέπουμε ότι ο αλγόριθμος θα βρει σωστά τα συχνά itemsets αφού όλα βρίσκονται στα υποψήφια ενώ το Negative Border θα βγει μη συχνό.
+
+\subparagraph{$s^{\prime\prime}=2$} Με threshold $s^{\prime\prime}$ από τις 3 πρώτες εγγραφές παίρνουμε ότι τα υποψήφια συχνά itemsets είναι τα
+\[ \{ \{c\},\{a,d\} \} \]
+και το Negative Border είναι το
+\[ \{ \{b\},\{a,c\},\{c,d\} \} \]
+Βλέπουμε ότι ο αλγόριθμος δεν θα δουλέψει διότι το $\{b\}$ από το Negative Border είναι συχνό itemset στη βάση.
+\\[8pt]
+Παρατηρούμε ότι όπως περιμέναμε το $s^{\prime\prime}$ δεν ήταν καλή επιλογή για threshold.
+Εφόσον πήραμε το $1/4$ των εγγραφών για δείγμα, το προτεινόμενο θα ήταν να πάρουμε ένα ακόμα μικρότερο κλάσμα του αρχικού threshold.
+Αυτό εδώ προφανώς δεν γίνεται οπότε το $s^\prime$, το ακριβώς $1/4$ του $s$, είναι μια καλή επιλογή που εσωκλείει όλα τα συχνά στα υποψήφια, ενώ το $s^{\prime\prime}$ αφήνει τα περισσότερα απ' έξω.
+
 \end{document}

### 2022-05-12 ads/ask_s01.tex
ADS: Exer01: Added exercise 5 with 7.3.2 pending, with python helper script

@@
 
-%\usepackage{amsmath}
+\usepackage{amsmath}
 \usepackage{hhline}
@@
 
+\section*{Άσκηση 5}
+
+\subsection*{7.2.2 (MMDS)}
+
+\paragraph{(a)} Θα χρησιμοποιήσουμε το κριτήριο της ελάχιστης απόστασης δύο οποιοδήποτε σημείων μεταξύ δύο clusters στο παράδειγμα 7.2 του MMDS.
+Για το συγκεκριμένο κριτήριο συμφέρει να υπολογίσουμε έναν πίνακα που να περιέχει όλες τις αποστάσεις μεταξύ των σημείων, και από εκεί να ψάξουμε την μικρότερη τιμή όπου τα σημεία δεν ανήκουν στον ίδιο cluster για να κάνουμε τα merges.
+Σε αντίθεση με το κριτήριο κοντινότερου centroid, ένα merge δεν αλλάζει τις αποστάσεις που θα πρέπει να συγκρίνουμε.
+Οπότε τα merges γίνονται ως εξής
+\begin{center}
+	\begin{tabular}{| c | c || c | c |}
+		\hline
+		points & distance & points & distance \\ \hhline{|=|=#=|=|}
+		$(10,5),(11,4)$ & $\sqrt{2}$ & $(6,8),(7,10)$ & $\sqrt{5}$ \\ \hline
+		$(11,4),(12,3)$ & $\sqrt{2}$ & $(10,5),(12,6)$ & $\sqrt{5}$ \\ \hline
+		$(4,8),(4,10)$ & $2$ & $(9,3),(10,5)$ & $\sqrt{5}$\\ \hline
+		$(4,8),(6,8)$ & $2$ & $(2,2),(3,4)$ & $\sqrt{5}$ \\ \hline
+		& & $(5,2),(3,4)$ & $\sqrt{5}$ \\ \hline
+	\end{tabular}
+\end{center}
+με τα οποία οι τελικοί clusters είναι οι ίδιοι με το παράδειγμα, δηλαδή τρεις clusters
+\[ \{ (4,10),(7,10),(4,8),(6,8) \}, \{ (10,5),(12,6),(11,4),(9,3),(12,3) \}, \{ (3,4),(2,2),(5,2) \} \]
+
+\paragraph{(b)}
+Θα χρησιμοποιήσουμε το κριτήριο της μέσης απόστασης δύο σημείων μεταξύ δύο clusters στο παράδειγμα 7.2 του MMDS.
+Θα χρησιμοποιήσουμε πάλι τον πίνακα με όλες τις αποστάσεις των σημείων για να υπολογίσουμε τη μέση απόσταση μεταξύ δύο clusters.
+Επίσης μπορούμε να παρατηρήσουμε ότι η μέση απόσταση είναι μεγαλύτερη ή ίση από την ελάχιστη απόσταση μεταξύ δυο σημείων, ένα από κάθε cluster (κριτήριο στο (a)), οπότε μπορούμε να αποφύγουμε κάποιους υπολογισμούς.
+Τα merges λοιπόν γίνονται ως εξής
+\begin{center}
+	\begin{tabular}{| c | c |}
+		\hline
+		clusters & av. distance \\ \hhline{|=|=|}
+		$\{(10,5)\},\{(11,4)\}$ & $\sqrt{2}$ \\ \hline
+		$\{(4,8)\},\{(4,10)\}$ & $2$ \\ \hline
+		$\{(10,5),(11,4)\},\{(12,3)\}$ & $(\sqrt{2}+\sqrt{8})/2$ \\ \hline
+		$\{(6,8)\},\{(7,10)\}$ & $\sqrt{5}$ \\ \hline
+		$\{(2,2)\},\{(3,4)\}$ & $\sqrt{5}$ \\ \hline
+		$\{(10,5),(11,4)\},(12,3)\},\{(9,3)\}$ & $(\sqrt{5}+\sqrt{5}+3)/3$ \\ \hline
+		$\{(2,2),(3,4)\},\{(5,2)\}$ & $(\sqrt{5}+3)/2$ \\ \hline
+		$\{(4,8),(4,10)\},\{(6,8),(7,10)\}$ & $(2+\sqrt{8}+3+\sqrt{13})/4$ \\ \hline
+		$\{(10,5),(11,4)\},(12,3),(9,3)\},\{(12,6)\}$ & $(\sqrt{5}+\sqrt{5}+3+\sqrt{18})/4$ \\ \hline
+	\end{tabular}
+\end{center}
+με τα οποία οι τελικοί clusters είναι πάλι οι ίδιοι με προηγουμένως
+\[ \{ (4,10),(7,10),(4,8),(6,8) \}, \{ (10,5),(12,6),(11,4),(9,3),(12,3) \}, \{ (3,4),(2,2),(5,2) \} \]
+
+\subsection*{7.2.3 (MMDS)}
+
+\paragraph{(a)} Θα χρησιμοποιήσουμε το κριτήριο της ελάχιστης ακτίνας στο παράδειγμα 7.2 του MMDS.
+Θεωρούμε ως ακτίνα ενός cluster τη μέγιστη απόσταση ενός σημείου του με το centroid.
+Λόγω απαιτητικών υπολογισμών η παρακάτω ακολουθία cluster merges υπολογίστηκε μέσω Python script.
+
+\begin{center}
+	\begin{tabular}{| c | c | c |}
+		\hline
+		clusters & centroid & radius \\ \hhline{|=|=|=|}
+		$\{(10,5)\},\{(11,4)\}$ & $(10.5,4.5)$ & $0.7$ \\ \hline
+		$\{(4, 10)\},\{(4, 8)\}$ & $(4.0, 9.0)$ & $1.0$ \\ \hline
+		$\{(7, 10)\},\{(6, 8)\}$ & $(6.5, 9.0)$ & $1.12$ \\ \hline
+		$\{(3, 4)\},\{(2, 2)\}$ & $(2.5, 3.0)$ & $1.12$ \\ \hline
+		$\{(12, 6)\},\{(10, 5), (11, 4)\}$ & $(11.0, 5.0)$ & $1.41$ \\ \hline
+		$\{(9, 3)\},\{(12, 3)\}$ & $(10.5, 3.0)$ & $1.5$ \\ \hline
+		$\{(5, 2)\},\{(3, 4), (2, 2)\}$ & $(3.33, 2.67)$ & $1.8$ \\ \hline
+		$\{(4, 10), (4, 8)\},\{(7, 10), (6, 8)\}$ & $(5.25, 9.0)$ & $2.02$ \\ \hline
+		$\{(12, 6), (10, 5), (11, 4)\},\{(12, 3), (9, 3)\}$ & $(10.8, 4.2)$ & $2.16$ \\ \hline
+	\end{tabular}
+\end{center}
+όπου καταλήγουμε πάλι στους γνωστούς τρεις clusters
+\[ \{ (4,10),(7,10),(4,8),(6,8) \}, \{ (10,5),(12,6),(11,4),(9,3),(12,3) \}, \{ (3,4),(2,2),(5,2) \} \]
+
+\paragraph{(b)} Θα χρησιμοποιήσουμε το κριτήριο της ελάχιστης διαμέτρου στο παράδειγμα 7.2 του MMDS.
+Θεωρούμε ως διάμετρο ενός cluster τη μέγιστη απόσταση μεταξύ δύο οποιονδήποτε σημείων του.
+Mέσω Python script παίρνουμε τα παρακάτω cluster merges.
+\begin{center}
+	\begin{tabular}{| c | c |}
+		\hline
+		clusters & diameter \\ \hhline{|=|=|}
+		$\{(10, 5)\},\{(11, 4)\}$ & $1.41$ \\ \hline
+		$\{(4, 10)\},\{(4, 8)\}$ & $2.0$ \\ \hline
+		$\{(7, 10)\},\{(6, 8)\}$ & $2.24$ \\ \hline
+		$\{(12, 6)\},\{(10, 5), (11, 4)\}$ & $2.24$ \\ \hline
+		$\{(3, 4)\},\{(2, 2)\}$ & $2.24$ \\ \hline
+		$\{(9, 3)\},\{(12, 3)\}$ & $3.0$ \\ \hline
+		$\{(5, 2)\},\{(3, 4), (2, 2)\}$ & $3.0$ \\ \hline
+		$\{(4, 10), (4, 8)\},\{(7, 10), (6, 8)\}$ & $3.61$ \\ \hline
+		$\{(12, 6), (10, 5), (11, 4)\},\{(12, 3), (9, 3)\}$ & $4.24$ \\ \hline
+	\end{tabular}
+\end{center}
+όπου καταλήγουμε πάλι στους γνωστούς τρεις clusters
+\[ \{ (4,10),(7,10),(4,8),(6,8) \}, \{ (10,5),(12,6),(11,4),(9,3),(12,3) \}, \{ (3,4),(2,2),(5,2) \} \]
+
+%\subsection*{7.3.2 (MMDS)}
+
+%Έστω $A,B,C$ οι τρεις clusters του παραδείγματος, δηλαδή
+%\begin{flalign*}
+%	A &= \{ (4,10),(7,10),(4,8),(6,8) \} \\
+%	B &= \{ (10,5),(12,6),(11,4),(9,3),(12,3) \} \\
+%	C &= \{ (3,4),(2,2),(5,2) \}
+%\end{flalign*}
+%Μετά όπως βλέπουμε από τον πίνακα της 7.2.2 (b) (τρεις τελευταίες γραμμές), οι διάμετροι των $A,B,C$ %είναι $3.61,4.24,3$ αντίστοιχα.
+%Τώρα για το minimum intercluster distance βρίσκουμε
+%\[ A,B:5 \qquad A,C:4.12 \qquad B,C:4.12 \]
+
+\subsection*{7.4.1 (MMDS)}
+
+Έστω $K$ το κοινό centroid των δύο clusters που έχουμε (κύκλο και δακτύλιο).
+Εφόσον τα representative points είναι στα όριά τους, τότε ένα τέτοιο point από τον κύκλο θα έχει απόσταση $c$ από το $K$ ενώ αν είναι από το δακτύλιο τότε θα έχει είτε $i$ είτε $o$ ανάλογα αν είναι στο inner ή outer boundary.
+Άρα το κοντινότερο που θα μπορούσαν να είναι δύο σημεία, ένα από κάθε cluster, είναι εάν βρίσκονται στην ίδια ευθεία με το $K$, στο ίδιο ημικύκλιο και το σημείο του δακτυλίου να είναι στο inner boundary, και άρα θα έχουν απόσταση $i-c$.
+
+Προχωρώντας στο βήμα της μετακίνησης των σημείων στο $20\%$ της απόστασή τους από το centroid, η παραπάνω απόσταση προσαρμόζεται αντίστοιχα ως εξής
+\[ \frac{20}{100}i-\frac{20}{100}c = \frac{1}{5}(i-c) \]
+Οπότε εάν ισχύει ότι $1/5(i-c)<d$, ή αλλιώς
+\[ i-c < 5d \]
+τότε είναι πιθανό να υπάρχουν σημεία που θα ικανοποιούν τις παραπάνω συνθήκες και θα κάνουν trigger την συνθήκη που κάνει merge τους δύο clusters.
+\\[8pt]
+Στη συνέχεια μπορούμε να κάνουμε τη συνθήκη πιο αυστηρή εξετάζοντας τη μεγαλύτερη πιθανή απόσταση δύο σημείων, ένα από κάθε cluster, το οποίο συμβαίνει όταν πάλι τα σημεία είναι στην ίδια ευθεία με το $K$ αλλά σε αντίθετα ημισφαίρια (οπότε θα προσθέσουμε τις ακτίνες τους) και το σημείο του δακτυλίου να βρίσκεται στο outer boundary (ακτίνα $o$).
+Τότε με την ίδια λογική όπως και παραπάνω παίρνουμε ότι οι δύο clusters θα γίνουν σίγουρα merge όταν
+\[ o+c < 5d \]
+
 \end{document}

### 2022-05-12 ads/ask_s01.py

@@ -1,4 +1,5 @@
 # Exercise 1
+import math
 
 
 class Multistage:
@@ -122,3 +123,105 @@ print(mg.hash_buckets)
 # Exercise 6.3.2
 print(mg.hash_buckets_multistage)
 
+
+# Exercise 5
+def d2(point_a, point_b):
+    return math.sqrt((point_a[0] - point_b[0]) ** 2 + (point_a[1] - point_b[1]) ** 2)
+
+
+data = [(4, 10), (7, 10), (4, 8), (6, 8), (12, 6), (10, 5), (3, 4), (11, 4), (9, 3), (12, 3), (2, 2), (5, 2)]
+
+# Exercise 7.2.2
+format_row = "{:>8}" * (len(data) + 1)
+print(format_row.format('', *list(map(lambda x: str(x), data))))
+for point_row in data:
+    distances = []
+    for point_col in data:
+        distances.append(round(d2(point_col, point_row), 2))
+    print(format_row.format(str(point_row), *distances))
+
+
+# Exercise 7.2.3
+class Cluster:
+    def __init__(self, points):
+        self.points = list(set(points))
+        self.centroid = self.get_centroid()
+
+    def get_centroid(self):
+        x = (sum([point[0] for point in self.points])) / len(self.points)
+        y = (sum([point[1] for point in self.points])) / len(self.points)
+        return x, y
+
+    def get_radius(self):
+        radii = [d2(self.centroid, point) for point in self.points]
+        return max(radii)
+
+    def get_diameter(self):
+        diameter = 0
+        for point_a in self.points:
+            for point_b in self.points:
+                if point_a == point_b:
+                    continue
+                d = d2(point_a, point_b)
+                diameter = d if d > diameter else diameter
+        return diameter
+
+    def __repr__(self):
+        return str(self.points)
+
+
+class HClustering:
+    def __init__(self, points):
+        self.points = points
+        self.clusters = [Cluster([point]) for point in points]
+        self.criterion = ''
+
+    def cluster_step(self):
+        radius_min = 1000
+        diameter_min = 1000
+        merge = {}
+        for cluster_a in self.clusters:
+            for cluster_b in self.clusters:
+                if cluster_a == cluster_b:
+                    continue
+                cluster_new = Cluster(cluster_a.points + cluster_b.points)
+
+                if self.criterion == 'radius':
+                    radius = cluster_new.get_radius()
+                    if radius < radius_min:
[…]

### 2022-05-12 ads/ask_s01.tex
ADS: Exer01: Added exercise 4, i.e. 5.2.2, 5.2.3, 5.3.2, 5.4.2 from MMDS
Helper python script updates also included

@@
 \usepackage{tikz}
+\usepackage{multirow}
+
 \usetikzlibrary{positioning}
@@
 
+\section*{Άσκηση 4}
+
+\subsection*{5.2.2 (MMDS)}
+
+\paragraph{(a)} Για το γράφο του σχήματος 5.4 (MMDS), η αναπαράστασή του ως sparse matrix είναι
+\begin{center}
+	\begin{tabular}{| c | c | l |}
+		\hline
+		Source & Degree & Destinations \\ \hhline{|=|=|=|}
+		$A$ & $3$ & $B,C,D$ \\
+		$B$ & $2$ & $A,D$ \\
+		$C$ & $1$ & $E$ \\
+		$D$ & $2$ & $B,C$ \\
+		\hline
+	\end{tabular}
+\end{center}
+Παραλείπουμε τη γραμμή για το $E$ αφού δεν έχει κανένα outgoing link.
+
+\paragraph{(b)} Για το γράφο του σχήματος 5.7 (MMDS), η αναπαράστασή του ως sparse matrix είναι
+\begin{center}
+	\begin{tabular}{| c | c | l |}
+		\hline
+		Source & Degree & Destinations \\ \hhline{|=|=|=|}
+		$a$ & $3$ & $a,b,c$ \\
+		$b$ & $2$ & $a,c$ \\
+		$c$ & $1$ & $b,c$ \\
+		\hline
+	\end{tabular}
+\end{center}
+
+\subsection*{5.2.3 (MMDS)}
+
+Ο γράφο του σχήματος 5.3 (MMDS) έχει τέσσερις κόμβους-σελίδες οπότε ο πίνακάς του είναι $4x4$, οπότε μια διαμέριση $2x2$ θα το χωρίσει σε τέσσερα blocks.
+\begin{center}
+	\begin{tabular}{| c | c | c |}
+		\hline
+		& $A \quad B$ & $C \quad D$ \\ \hhline{|=|=|=|}
+		$A$ & \multirow{2}{*}{$M_{11}$} & \multirow{2}{*}{$M_{12}$} \\
+		$B$ & & \\
+		\hline
+		$C$ & \multirow{2}{*}{$M_{21}$} & \multirow{2}{*}{$M_{22}$} \\
+		$D$ & & \\
+		\hline
+	\end{tabular}
+\end{center}
+Οπότε έχουμε για το $M_{11}$ (από $A,B$ σε $A,B$)
+\begin{center}
+	\begin{tabular}{| c | c | l |}
+		\hline
+		Source & Degree & Destinations \\ \hhline{|=|=|=|}
+		$A$ & $3$ & $B$ \\
+		$B$ & $2$ & $A$ \\
+		\hline
+	\end{tabular}
+\end{center}
+για $M_{12}$ (από $A,B$ σε $C,D$)
+\begin{center}
+	\begin{tabular}{| c | c | l |}
+		\hline
+		Source & Degree & Destinations \\ \hhline{|=|=|=|}
+		$A$ & $3$ & $C,D$ \\
+		$B$ & $2$ & $D$ \\
+		\hline
+	\end{tabular}
+\end{center}
+για $M_{21}$ (από $C,D$ σε $A,B$)
+\begin{center}
+	\begin{tabular}{| c | c | l |}
+		\hline
+		Source & Degree & Destinations \\ \hhline{|=|=|=|}
+		$D$ & $2$ & $B$ \\
+		\hline
+	\end{tabular}
+\end{center}
+και τέλος για $M_{22}$ (από $C,D$ σε $C,D$)
+\begin{center}
+	\begin{tabular}{| c | c | l |}
+		\hline
+		Source & Degree & Destinations \\ \hhline{|=|=|=|}
+		$D$ & $2$ & $C$ \\
+		\hline
+	\end{tabular}
+\end{center}
+
+\subsection*{5.3.1 (MMDS)}
+
+Για το γράφο του σχήματος 5.15 (MMDS) έχουμε από το παράδειγμα του βιβλίου ότι ο πίνακας μετάβασης είναι (έχουμε $\beta=0.8$)
+\[
+	\beta M =
+	\begin{bmatrix}
+		0 & 2/5 & 4/5 & 0 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 2/5 & 0 & 0
+	\end{bmatrix}
+\]
+
+\paragraph{(a)} Αν $S={A}$ τότε παίρνουμε $(1-\beta)/|S|=1/5$ και άρα
+\[
+	\textbf{v}^\prime = \beta M \textbf{v} + (1-\beta)\textbf{e}_S/|S| =
+	\begin{bmatrix}
+		0 & 2/5 & 4/5 & 0 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 2/5 & 0 & 0
+	\end{bmatrix}
+	\textbf{v} +
+	\begin{bmatrix}
+		1/5 \\ 0 \\ 0 \\ 0
+	\end{bmatrix}
+\]
+Ξεκινώντας λοιπόν από το $(1,0,0,0)$ παίρνουμε
+\[
+	\textbf{v}^\prime=
+	\begin{bmatrix}1 \\ 0 \\ 0 \\ 0\end{bmatrix},
+	\begin{bmatrix}0.2 \\ 0.27 \\ 0.27 \\ 0.27\end{bmatrix},
+	\begin{bmatrix}0.52 \\ 0.16 \\ 0.16 \\ 0.16\end{bmatrix},
+	\begin{bmatrix}0.39 \\ 0.20 \\ 0.20 \\ 0.20\end{bmatrix},
+	\begin{bmatrix}0.44 \\ 0.19 \\ 0.19 \\ 0.19\end{bmatrix},
+	\begin{bmatrix}0.42 \\ 0.19 \\ 0.19 \\ 0.19\end{bmatrix},
+	\begin{bmatrix}0.43 \\ 0.19 \\ 0.19 \\ 0.19]\end{bmatrix},
+	\dots
+\]
+Οπότε ο topic-sensitive PageRank πίνακας είναι ο
+\[ \textbf{v}^\prime = [0.43,0.19,0.19,0.19] \]
+
+\paragraph{(b)} Αν $S={A,C}$ τότε παίρνουμε $(1-\beta)/|S|=1/10$ και άρα
+\[
+	\textbf{v}^\prime =
+	\begin{bmatrix}
+		0 & 2/5 & 4/5 & 0 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 2/5 & 0 & 0
+	\end{bmatrix}
+	\textbf{v} +
+	\begin{bmatrix}
+	1/10 \\ 0 \\ 1/10 \\ 0
+	\end{bmatrix}
+\]
+Ξεκινώντας λοιπόν από το $(1,0,1,0)$ παίρνουμε
+\[
+	\textbf{v}^\prime=
+	\begin{bmatrix}1 \\ 0 \\ 1 \\ 0\end{bmatrix},
+	\begin{bmatrix}0.9 \\ 0.27 \\ 0.37 \\ 0.27\end{bmatrix},
+	\begin{bmatrix}0.5 \\ 0.35 \\ 0.45 \\ 0.35\end{bmatrix},
+	\begin{bmatrix}0.6 \\ 0.27 \\ 0.37 \\ 0.27\end{bmatrix},
+	\begin{bmatrix}0.5 \\ 0.27 \\ 0.37 \\ 0.27\end{bmatrix},
+	\begin{bmatrix}0.5 \\ 0.24 \\ 0.34 \\ 0.24\end{bmatrix},
+	\begin{bmatrix}0.47 \\ 0.23 \\ 0.33 \\ 0.23\end{bmatrix},
+	\begin{bmatrix}0.46 \\ 0.22 \\ 0.32 \\ 0.22\end{bmatrix},
+	\dots,
+	\begin{bmatrix}0.39 \\ 0.17 \\ 0.27 \\ 0.17]\end{bmatrix}
+\]
+(Στον παραπάνω υπολογισμό, για να συγκλίνει ο $\textbf{v}$ κάναμε $20$ επαναλήψεις.)
+\\[8pt]
+Οπότε ο topic-sensitive PageRank πίνακας είναι ο
+\[ \textbf{v}^\prime = [0.39,0.17,0.27,0.17] \]
+
+\subsection*{5.4.2 (MMDS)}
+
+\paragraph{(a)} Για να υπολογίσουμε το TrustRank θα ακολουθήσουμε την ίδια διαδικασία με το topic-sensitive PageRank.
+Ξεκινάμε με τον transition matrix του σχήματος 5.1 (MMDS) όπου αν πολλαπλασιάζουμε με το $\beta=0.8$ θα πάρουμε πάλι
+\[
+	\beta M =
+	\begin{bmatrix}
+		0 & 2/5 & 4/5 & 0 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 2/5 & 0 & 0 \\
+	\end{bmatrix}
+\]
+Μετά εφόσον μόνο το $B$ είναι trusted page, έχουμε ότι $(1-\beta)/|S|=1/5$ άρα
+\[
+	\textbf{v}^\prime =
+	\begin{bmatrix}
+		0 & 2/5 & 4/5 & 0 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 0 & 0 & 2/5 \\
+		4/15 & 2/5 & 0 & 0 \\
+	\end{bmatrix}
+	\textbf{v} +
+	\begin{bmatrix}
+		0 \\ 1/5 \\ 0 \\ 0
+	\end{bmatrix}
+\]
+Οπότε ξεκινώντας από το $[0,1,0,0]$ παίρνουμε
+\[
+	\textbf{v}^\prime =
+	\begin{bmatrix}0 \\ 1 \\ 0 \\ 0\end{bmatrix},
+	\begin{bmatrix}0.4 \\ 0.2 \\ 0 \\ 0.4\end{bmatrix},
+	\begin{bmatrix}0.08 \\ 0.47 \\ 0.27 \\ 0.19\end{bmatrix},
+	\begin{bmatrix}0.4 \\ 0.3 \\ 0.1 \\ 0.2\end{bmatrix},
+	\begin{bmatrix}0.2 \\ 0.39 \\ 0.19 \\ 0.23\end{bmatrix},
+	\begin{bmatrix}0.31 \\ 0.34 \\ 0.14 \\ 0.21 \\ \end{bmatrix},
+	\begin{bmatrix}0.25 \\ 0.37 \\ 0.17 \\ 0.22\end{bmatrix},
+	\begin{bmatrix}0.28 \\ 0.35 \\ 0.15 \\ 0.21\end{bmatrix},
+	\begin{bmatrix}0.27 \\ 0.36 \\ 0.16 \\ 0.22\end{bmatrix},
+	\begin{bmatrix}0.27 \\ 0.36 \\ 0.16 \\ 0.21\end{bmatrix},
+	\dots
+\]
+και εντέλει ο TrustRank της κάθε σελίδας είναι
+\[ \textbf{v}^\prime = [0.27,0.36,0.16,0.21]\]
+
+\paragraph{(b)} Για να βρούμε το spam mass της κάθε σελίδας θα πρέπει αρχικά να υπολογίσουμε το PageRank τους.
+Από τα παραδείγματα του βιβλίου βλέπουμε ότι το PageRank των σελιδών του σχήματος 5.1 (MMDS) είναι $[3/9,2/9/,2/9,2/9]$.
+Οπότε
+\begin{center}
+	\begin{tabular}{c c c c}
+		Node & PageRank & TrustRank & Spam Mass \\
+		\hline
+		$A$ & 3/9 & 0.27 & 0.19 \\
+		$B$ & 2/9 & 0.36 & -0.62 \\
+		$C$ & 2/9 & 0.16 & 0.28 \\
+		$D$ & 2/9 & 0.21 & 0.05
+	\end{tabular}
+\end{center}
+
 \section*{Άσκηση 5}

### 2022-05-12 ads/ask_s01.py

@@ -1,5 +1,6 @@
 # Exercise 1
 import math
+import numpy as np
 
 
 class Multistage:
@@ -124,7 +125,46 @@ print(mg.hash_buckets)
 print(mg.hash_buckets_multistage)
 
 
+# Exercise 4
+print()
+# Exercise 5.3.1
+print('Exercise 5.3.1')
+trans = np.array([
+    [0, 2/5, 4/5, 0],
+    [4/15, 0, 0, 2/5],
+    [4/15, 0, 0, 2/5],
+    [4/15, 2/5, 0, 0]
+])
+
+# Question (a)
+print('(a)')
+taxation = np.array([1/5, 0, 0, 0])
+v = np.array([1, 0, 0, 0])
+for i in range(1000):
+    v = (trans @ v) + taxation
+print(v)
+
+# Question (b)
+print('(b)')
+taxation = np.array([1/10, 0, 1/10, 0])
+v = np.array([1, 0, 1, 0])
+for i in range(1000):
+    v = (trans @ v) + taxation
+print(v)
+
+# Exersice 5.3.2
+print()
+print('Exersice 5.3.2 (a)')
+taxation = np.array([0, 1/5, 0, 0])
+v = np.array([0, 1, 0, 0])
+for i in range(1000):
+    v = (trans @ v) + taxation
+print(v)
+
 # Exercise 5
+print()
+
+
 def d2(point_a, point_b):
     return math.sqrt((point_a[0] - point_b[0]) ** 2 + (point_a[1] - point_b[1]) ** 2)
 
@@ -132,6 +172,7 @@ def d2(point_a, point_b):
 data = [(4, 10), (7, 10), (4, 8), (6, 8), (12, 6), (10, 5), (3, 4), (11, 4), (9, 3), (12, 3), (2, 2), (5, 2)]
 
 # Exercise 7.2.2
+print('Exercise 7.2.2')
 format_row = "{:>8}" * (len(data) + 1)
 print(format_row.format('', *list(map(lambda x: str(x), data))))
 for point_row in data:

### 2022-05-15 ads/ask_s01.tex
ADS: Exer01: Added exercise 3 with bash script to run all algorithms-datasets

@@
 
+\section*{Άσκηση 3}
+
+Θα χρησιμοποιήσουμε τις υλοποιήσεις patricia και lcm από το FIMI repository, πάνω στα datasets chess, retail και accidents.
+\begin{center}
+	\begin{tabular}{| l | c | c | c |}
+		\hline
+		Database & \#Items & Avg. Length & \#Entries \\ \hhline{|=|=|=|=|}
+		chess & $75$ & $37$ & $3,196$ \\ \hline
+		retail & $16,469$ & $10.3$ & $88,162$ \\ \hline
+		accidents & $468$ & $33.8$ & $340,183$ \\ \hline
+	\end{tabular}
+\end{center}
+Όπως και στο πείραμα θα τρέξουμε τους αλγορίθμους με support $10\%, 20\%, \dots,90\%$ του συνολικού αριθμού entries του κάθε dataset και θα μετρήσουμε το χρόνο εκτέλεσης.
+Σε κάθε εκτέλεση θα γράψουμε και τα αποτελέσματα στο δίσκο ώστε να πλησιάσουμε τις ρεαλιστικές χρήσεις αυτών των αλγορίθμων.
+
+Τα αποτελέσματα που πήραμε φαίνονται στον παρακάτω πίνακα.
+\begin{center}
+	\begin{tabular}{| r | c | c || c | c || c | c |}
+		\hline
+		& \multicolumn{2}{c}{chess} & \multicolumn{2}{|c|}{retail} & \multicolumn{2}{|c|}{accidents} \\ \hline
+		\multirow{2}{*}{support (\%)} & \multicolumn{6}{|c|}{Time (s)} \\
+		& patricia & lcm & patricia & lcm & patricia & lcm \\ \hhline{|=|=|=#=|=#=|=|}
+		$10$ & $23.593$ & $19.237$ & $0.050$ & $0.034$ & $8.304$ & $16.976$ \\ \hline
+		$20$ & $2.754$ & $3.484$ & $0.051$ & $0.029$ & $3.025$ & $7.900$ \\ \hline
+		$30$ & $0.519$ & $1.085$ & $0.048$ & $0.030$ & $1.544$ & $3.184$ \\ \hline
+		$40$ & $0.237$ & $0.327$ & $0.048$ & $0.029$ & $1.144$ & $2.321$ \\ \hline
+		$50$ & $0.099$ & $0.147$ & $0.047$ & $0.027$ & $0.769$ & $1.232$ \\ \hline
+		$60$ & $0.047$ & $0.050$ & $0.046$ & $0.023$ & $0.649$ & $0.920$ \\ \hline
+		$70$ & $0.018$ & $0.022$ & $0.046$ & $0.022$ & $0.512$ & $0.609$ \\ \hline
+		$80$ & $0.010$ & $0.007$ & $0.045$ & $0.025$ & $0.459$ & $0.362$ \\ \hline
+		$90$ & $0.005$ & $0.004$ & $0.046$ & $0.022$ & $0.392$ & $0.219$ \\ \hline
+	\end{tabular}
+\end{center}
+Παρατηρούμε ότι αν και στα chess και retail datasets ο patricia είναι πιο αργός από τον lcm, στο accidents dataset συμβαίνει το αντίθετο, πιθανώς λόγω μεγαλύτερου αριθμού εγγραφών σε σχέση με τα δύο πρώτα.
+
 \section*{Άσκηση 4}

### 2022-05-15 ads/ask_s01_run.sh

@@ -1,0 +1,17 @@
+#!/usr/bin/bash
+cd fimi;
+
+for dataset in retail
+do
+
+	for sp in 10 20 30 40 50 60 70 80 90
+	do
+		echo $dataset - $sp;
+		len=$(cat $dataset.dat | wc -l);
+		s=$(( ($sp * $len) / 100 ));
+		echo patricia;
+		time PATRICIAMINE/fim_all $dataset.dat $s $dataset_results;
+		echo lcm
+		time lcm/fim_all $dataset.dat $s $dataset_results;
+	done
+done

### 2022-05-15 ads/ask_s01.tex
ADS: Exer01: Final proofread and python script cleanup

@@
 
-\paragraph{(d)} Τα ζευγάρια που θα μετρηθούν στο 2ο πέρασμα του αλγόριθμου PCY είναι αυτά στα οποία και τα δύο στοιχεία είναι συχνά, αλλά και το ζευγάρι αντιστοιχεί σε hash bucket που είναι συχνός.
+\paragraph{(d)} Τα ζευγάρια που θα μετρηθούν στο 2ο πέρασμα του αλγόριθμου PCY είναι αυτά στα οποία και τα δύο στοιχεία είναι συχνά, αλλά και το ζευγάρι αντιστοιχεί σε hash bucket που είναι συχνό.
 Εφόσον όλα τα μονοσύνολα είναι συχνά, από τα hash buckets παίρνουμε ότι θα μετρηθούν τα:
@@
 
-Με αυτόν τον αλγόριθμο πραγματοποιούνται τόσες διασχίσεις στη βάση δεδομένων όσο και το μήκος του μεγαλύτερου συχνού itemset, αφού απαιτείται μετά από κάθε παραγωγή $C_i$ συνόλου.
+Με τον συγκεκριμένο αλγόριθμο πραγματοποιούνται τόσες διασχίσεις στη βάση δεδομένων όσο και το μήκος του μεγαλύτερου συχνού itemset, εφόσον απαιτείται καθε φορά μετά από παραγωγή μη κενού $C_i$ συνόλου.
 
@@
 Οπότε και ο FP-Growth αλγόριθμος είναι πολυωνυμικός ως προς την έξοδο.
-\\[8pt]
-Για την πολυπλοκότητα του αλγορίθμου ίσως αξίζει να αναφέρουμε και τη σχέση που έχει ως προς το πλήθος των items $k$.
-Tο μέγεθος του δέντρου που θα προκύψει εξαρτάται από το πόσες διαφορετικές λεξικογραφικές εγγραφές αποτελείται η βάση, όπου στη χειρότερη θα μπορούσε να είναι $2^k$.
-Ο αλγόριθμος θα πρέπει να το διασχίσει τουλάχιστον $k$ φορές, μία για κάθε στοιχείο, οπότε στη χειρότερη έχουμε μια πολυπλοκότητα $\mathcal{O}(k2^k)$.
-Εφόσον βέβαια το $k$ είναι μικρός αριθμός σε σχέση με το πλήθος των εγγραφών, ενώ επίσης έχουμε και τη γενική υπόθεση ότι τα συχνά υποσύνολα θα είναι πολύ λιγότερα από το μέγεθος της βάσης, μπορούμε να περιμένουμε ότι ακόμα και σε αυτήν την περίπτωση τα υποδέντρα που θα προκύψουν θα μικρύνουν μετά από ένα μικρό αριθμό βημάτων.
 
@@
 Εφόσον η συχνότητα του $d$ είναι $5$ παίρνουμε ότι το $\{a,d\}$ συχνό.
-Εφόοσον το υποδέντρο έχει μόνο δύο στοιχεία δεν έχει νόημα να ψάξουμε για 3-itemsets, ενώ για τον ίδιο λόγο δεν έχει νόημα να κοιτάξουμε το στοιχείο $d$ (το υποδέντρο θα έχει μόνο έναν κόμβο πέρα από το root).
+Εφόοσον το υποδέντρο έχει μόνο δύο στοιχεία δεν έχει νόημα να ψάξουμε για 3-itemsets, ενώ για τον ίδιο λόγο δεν έχει νόημα να κοιτάξουμε το στοιχείο $d$ (το υποδέντρο θα έχει μόνο έναν κόμβο πέρα από τον root).
 \\[8pt]
@@
 
-Με έναν έλεγχο στη βάση βλέπουμε ότι ο αλγόριθμος θα βρει σωστά τα συχνά itemsets αφού όλα βρίσκονται στα υποψήφια ενώ το Negative Border θα βγει μη συχνό.
+Με έναν έλεγχο στη βάση βλέπουμε ότι ο αλγόριθμος θα βρει το Negative Border μη συχνό και άρα θα βρει σωστά τα συχνά itemsets (όλα βρίσκονται στα υποψήφια).
 
@@
 
-Ο γράφο του σχήματος 5.3 (MMDS) έχει τέσσερις κόμβους-σελίδες οπότε ο πίνακάς του είναι $4x4$, οπότε μια διαμέριση $2x2$ θα το χωρίσει σε τέσσερα blocks.
+Ο γράφο του σχήματος 5.3 (MMDS) έχει τέσσερις κόμβους-σελίδες οπότε ο πίνακάς του είναι $4 \times 4$ και άρα μια διαμέριση $2 \times 2$ θα το χωρίσει σε τέσσερα blocks.
 \begin{center}
@@
 	\begin{bmatrix}0.42 \\ 0.19 \\ 0.19 \\ 0.19\end{bmatrix},
-	\begin{bmatrix}0.43 \\ 0.19 \\ 0.19 \\ 0.19]\end{bmatrix},
+	\begin{bmatrix}0.43 \\ 0.19 \\ 0.19 \\ 0.19\end{bmatrix},
 	\dots
@@
 
+Τα παρακάτω ακολουθίες cluster merges λόγω απαιτητικών υπολογισμών έγιναν μέσω Python script.
+
 \paragraph{(a)} Θα χρησιμοποιήσουμε το κριτήριο της ελάχιστης ακτίνας στο παράδειγμα 7.2 του MMDS.
 Θεωρούμε ως ακτίνα ενός cluster τη μέγιστη απόσταση ενός σημείου του με το centroid.
-Λόγω απαιτητικών υπολογισμών η παρακάτω ακολουθία cluster merges υπολογίστηκε μέσω Python script.
-
+Παίρνουμε λοιπόν την παρακάτω ακολουθία cluster merges.
 \begin{center}
@@
 Θεωρούμε ως διάμετρο ενός cluster τη μέγιστη απόσταση μεταξύ δύο οποιονδήποτε σημείων του.
-Mέσω Python script παίρνουμε τα παρακάτω cluster merges.
+Παίρνουμε λοιπόν την παρακάτω ακολουθία cluster merges.
 \begin{center}

### 2022-05-15 ads/ask_s01.py

@@ -18,38 +18,6 @@ class Multistage:
         self.hash_buckets = [0 for k in range(11)]
         self.hash_buckets_multistage = [0 for m in range(9)]
 
-    @property
-    def singletons_support(self):
-        return self._singletons_support
-
-    @singletons_support.setter
-    def singletons_support(self, value):
-        self._singletons_support = value
-
-    @property
-    def pairs_support(self):
-        return self._pairs_support
-
-    @pairs_support.setter
-    def pairs_support(self, value):
-        self._pairs_support = value
-
-    @property
-    def hash_buckets(self):
-        return self._hash_buckets
-
-    @hash_buckets.setter
-    def hash_buckets(self, value):
-        self._hash_buckets = value
-
-    @property
-    def hash_buckets_multistage(self):
-        return self._hash_buckets_multistage
-
-    @hash_buckets_multistage.setter
-    def hash_buckets_multistage(self, value):
-        self._hash_buckets_multistage = value
-
     # Get the index using the Triangular-Matrix method.
     @staticmethod
     def triangular_matrix_index(i, j):
@@ -104,6 +72,7 @@ class Multistage:
 
 
 # Exercise 6.3.1
+print('Exercise 6.3.1')
 # Dataset and requirements from Exercise 6.3.1.
 items = range(1, 7)
 data = [
@@ -115,13 +84,17 @@ mg = Multistage(data, 4)
 mg.run()
 
 # Question (a).
+print('(a)')
 print(mg.singletons_support)
 print(mg.pairs_support)
 
 # Question (c).
+print('(c)')
 print(mg.hash_buckets)
 
 # Exercise 6.3.2
+print()
+print('Exercise 6.3.2')
 print(mg.hash_buckets_multistage)
 
 

### 2022-07-02 ads/ask_s02.tex
ADS: Exer02: First draft with ex1 and ex 3b-7
Exercise 1 based on last year's solution

% -*- mode: LaTeX; coding: utf-8 -*-
% Typeset with: XeLaTeX

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
  % you may want to try: {Liberation Serif} or {Times New Roman}
\setmainfont{FreeSerif}
  % you may want to try: {Liberation Sans} or {Arial}
\setsansfont[Scale=MatchLowercase]{FreeSans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{FreeMono}

\usepackage{amsmath}
\usepackage{hhline}

\newcommand{\RightarrowArg}[1]{\stackrel{#1}{\Longrightarrow}}

% Main document
\begin{document}
\title{Αλγοριθμική Επιστήμη Δεδομένων - 2η σειρά ασκήσεων}
\author{Θωμάς Παππάς}
\date{4 Ιουλίου 2022}
\maketitle

\section*{Άσκηση 1}

\paragraph{(α)} Έστω τα στοιχεία $k_1,k_2 \in U$ με $k_1 \leq m$ και $k_2 = k_1+m \leq m^k$.
Προφανώς $k_1 \neq k_2$ και $k_1 \equiv k_2 \bmod m$.
Θα δείξουμε ότι $\forall a \in [m] \setminus 0, b \in [m]$ παίρνουμε $h_{a,b}(k_1) = h_{a,b}(k_2)$.
Όντως
\[k_1 \equiv k_2 \bmod m \Rightarrow ak_1+b \equiv ak_2+b \bmod m \Leftrightarrow h_{a,b}(k_1) = h_{a,b}(k_2)\]
και εφόσον αυτό ισχύει $\forall a, b$, η πιθανότητα να έχουμε $h_{a,b}(k_1) = h_{a,b}(k_2)$ είναι $1 \geq \frac1{m}$, και άρα αυτή η οικογένεια συναρτήσεων κατακερματισμού δεν είναι καθολική.

\paragraph{(β)} Έστω $k_1,k_2 \in U$ με $k_1 \neq k_2$. Παρατηρούμε τα εξής:

\begin{itemize}
	\item Το πλήθος των πιθανών $h_{a,b}$ συναρτήσεων είναι $|H|=p(p-1)$
	\item Εφόσον $p$ πρώτος, $\forall a,b \in [p], a \neq 0$ υπάρχει μοναδικό ζευγάρι $(y_1,y_2) \in [p] \times [p]$ όπου\\
		$y_1 \equiv ak_1+b \bmod p, y_2 \equiv ak_2+b \bmod p$ και $y_1 \neq y_2$, αφού
		\[y_1=y_2 \Rightarrow ak_1+b \equiv ak_2+b \bmod p \RightarrowArg{p \text{ πρώτος}} k_1 \equiv k_2 \bmod p \RightarrowArg{k_1,k_2<p} k_1=k_2 \text{ άτοπο}\]
		Δηλαδή τα $p(p-1)$ το πλήθος ζευγάρια $y_1,y_2$ αντιστοιχούνται 1-1 με τις $p(p-1)$ πιθανές επιλογές των $a,b$
	\item Έχουμε $h_{a,b}(k_1) = h_{a,b}(k_2) \Leftrightarrow y_1 \equiv y_2 \bmod m$
\end{itemize}
Μετράμε λοιπόν τα πιθανά ζευγάρια $y_1,y_2$ τέτοια ώστε $y_1 \equiv y_2 \bmod m$.
Έστω ότι $y_1 \equiv 0 \bmod m$ όπου υπάρχουν $\lfloor p/m \rfloor + 1$ πιθανές τιμές για το $y_1$. Για καθεμία έχουμε το πολύ $\lfloor p/m \rfloor$ το πλήθος $y_2$ τέτοια ώστε $y_2 \equiv 0 \bmod p$ (εξαιρούμε την περίπτωση $y_2=y_1$).
Επαναλαμβάνουμε το παραπάνω $\forall i = 1,2,\dots,m-1$ και παίρνουμε $m$ φορές το προηγούμενο.
Οπότε συνολικά έχουμε
\[
	|h_{a,b}|_{h_{a,b}(k_1)=h_{a,b}(k_2)} \leq m \left(\left\lfloor \frac{p}{m} \right\rfloor + 1\right) \left\lfloor \frac{p}{m} \right\rfloor \leq m \frac{p(p+m)}{m^2} \leq ??? %\frac{p(p-1)}{m} = \frac{|H|}{m}
\]
%Άρα η $H$ είναι καθολική οικογένεια συναρτήσεων κατακερματισμού.

%\paragraph{(γ)} Θέτοντας $U=[p]$ παρατηρούμε ότι η παραπάνω απόδειξη παραμένει απαράλλαχτη, εφόσον για μια τυχαία επιλογή  $k_1,k_2 \in U = [p]$ έχουμε πάλι ότι $\forall a,b \in [p], a \neq 0$ αντιστοιχούν σε ένα μοναδικό ζευγάρι $(y_1, y_2) \in [p] \times [p]$, οπότε με τον ίδιο συλλογισμό καταλήγουμε ότι η οικογένεια συναρτήσεων κατακερματισμού παραμένει καθολική.

%\section*{Άσκηση 2}

%\paragraph{(α)} Ο χρόνος εισαγωγής του $i$-οστού στοιχείου είναι ένα τυχαίο γεγονός που ακολουθεί την κατανομή Bernoulli($m-i/m$).
%Άρα ο αναμενόμενος αριθμός επαναλήψεων μέχρι την πρώτη επιτυχία είναι $m/m-i$ (εφόσον αυτό ακολουθεί Geom($m-i/m$)).
%\paragraph{(α)} Μετά από την εισαγωγή $n$ στοιχείων, η επιτυχής αναζήτηση .
%Άρα ο αναμενόμενος αριθμός επαναλήψεων μέχρι την πρώτη επιτυχία είναι $1/(1-a)$ (εφόσον αυτό ακολουθεί Geom($1-a$)).
%\\[8pt]
%Από την άλλη, με την ίδια λογική, ο χρόνος εισαγωγής του $i$-οστού στοιχείου είναι $m/m-i$, εφόσον εδώ η πιθανότητα επιτυχίας να βρεθεί κενή θέση είναι $m-i/m$.

\section*{Άσκηση 3}

\paragraph{(β)} Στην περίπτωση που ο γράφος είναι δέντρο τότε κάθε ακμή είναι γέφυρα και άρα τα συντομότερα μονοπάτια που περνάνε από την ακμή αυτή είναι αυτά που ξεκινάνε από έναν κόμβο της μιας πλευράς και καταλήγουν σε κόμβο της άλλης.
Οπότε αν η ακμή χωρίζει το γράφο στους υπογράφους $G_1,G_2$ τότε το edge betweeness της ακμής είναι $|G_1| \times |G_2|$.

Άρα ο αλγόριθμος μπορεί να απλοποιηθεί στο να κάνουμε ένα BFS στο δέντρο όπου σε κάθε κόμβο $v$ που κάνουμε visit παίρνουμε το υποδέντρο με ρίζα $v$, έστω $T$, και τότε το edge betweeness της ακμής που καταλήγει στον $v$ είναι $|T| \times |G \setminus T|$.

Αυτός ο αλγόριθμος έχει πολυπλοκότητα όσο και το BFS, δηλαδή $\mathcal{O}(|V|+|E|)$.

\section*{Άσκηση 4}

\subsection*{10.4.1 (MMDS)}

Στους παρακάτω πίνακες η σειρά των κόμβων είναι η αλφαβητική.

\paragraph{(a)} Πίνακας γειτνίασης:
\[
	\begin{bmatrix}
		0 & 1 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
		1 & 0 & 1 & 0 & 0 & 0 & 0 & 1 & 0 \\
		1 & 1 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & 1 & 0 & 1 & 1 & 0 & 0 & 0 \\
		0 & 0 & 0 & 1 & 0 & 1 & 1 & 0 & 0 \\
		0 & 0 & 0 & 1 & 1 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & 1 & 0 & 0 & 1 & 1 \\
		0 & 1 & 0 & 0 & 0 & 0 & 1 & 0 & 1 \\
		0 & 0 & 0 & 0 & 0 & 0 & 1 & 1 & 0
	\end{bmatrix}
\]

\paragraph{(b)} Πίνακας βαθμών:
\[
	\begin{bmatrix}
		2 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
		0 & 3 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & 3 & 0 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 3 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & 3 & 0 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & 0 & 2 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & 0 & 0 & 3 & 0 & 0 \\
		0 & 0 & 0 & 0 & 0 & 0 & 0 & 3 & 0 \\
		0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 2
	\end{bmatrix}
\]

\paragraph{(c)} Πίνακας Laplace:
\[
	\begin{bmatrix}
		2 & -1 & -1 & 0 & 0 & 0 & 0 & 0 & 0 \\
		-1 & 3 & -1 & 0 & 0 & 0 & 0 & -1 & 0 \\
		-1 & -1 & 3 & -1 & 0 & 0 & 0 & 0 & 0 \\
		0 & 0 & -1 & 3 & -1 & -1 & 0 & 0 & 0 \\
		0 & 0 & 0 & -1 & 3 & -1 & -1 & 0 & 0 \\
		0 & 0 & 0 & -1 & -1 & 2 & 0 & 0 & 0 \\
		0 & 0 & 0 & 0 & -1 & 0 & 3 & -1 & -1 \\
		0 & -1 & 0 & 0 & 0 & 0 & -1 & 3 & -1 \\
		0 & 0 & 0 & 0 & 0 & 0 & -1 & -1 & 2
	\end{bmatrix}
\]

\subsection*{10.4.2 (MMDS)}

Χρησιμοποιώντας python βρίσκουμε ότι η δεύτερη μικρότερη ιδιοτιμή είναι $0.7$ και ο αντίστοιχος ιδιοπίνακας ο
\[[-0.33,-0.22,-0.33,-0.52,0.09,0,-0.36,-0.39,-0.41]\]
το οποίο και προτείνει τη διαμέριση $\{A,B,C,D,G,H,I\},\{E,F\}$.

\section*{Άσκηση 5}

\paragraph{(α)} Η τιμή της normalised cut για το γράφο του σχήματος 10.16 (MMDS) και τη διαμέριση $\{1,2,3\},\{4,5,6\}$ είναι
\[
	\frac{Cut(\{1,2,3\},\{4,5,6\})}{Vol(\{1,2,3\})} + \frac{Cut(\{1,2,3\},\{4,5,6\})}{Vol(\{4,5,6\})} = \frac25 + \frac25 = \frac45
\]

\paragraph{(β)} Για να βρούμε τις τιμές modularity για το γράφο $G$ του σχήματος 10.16 (MMDS) θα χρησιμοποιήσουμε τους βαθμούς για τον κάθε κόμβο, δηλαδή
\begin{center}
	\begin{tabular}{| c || c | c | c | c | c | c |}
		\hline
		κόμβοι & $1$ & $2$ & $3$ & $4$ & $5$ & $6$ \\ \hline
		βαθμός & $3$ & $2$ & $3$ & $3$ & $2$ & $3$ \\ \hline
	\end{tabular}
\end{center}
Επίσης έχουμε $m=8$. Οπότε για διαμέριση $S=\{ \{1,2,3\},\{4,5,6\} \}$ έχουμε
\begin{flalign*}
	Q(G,S) &= \left[ (3+2+3) - \frac{1}{2 \cdot 5}(3 \cdot 2 + 3 \cdot 3 + 2 \cdot 3) \right] + \left[ (3+2+3) - \frac{1}{2 \cdot 5}(3 \cdot 2 + 3 \cdot 3 + 2 \cdot 3) \right]\\
		&= \left( 8-\frac{21}{10} \right) + \left( 8-\frac{21}{10} \right) = 16 - 4.2 = 11.6
\end{flalign*}
Μετά για $S=\{ \{1\},\{2,3\},\{4,5\},\{6\} \}$ έχουμε
\[
	Q(G,S) = \left[ 3 - 0 \right] + \left[ (2+3) - \frac{2 \cdot 3}{2 \cdot 5} \right] + \left[ (3+2) - \frac{3 \cdot 2}{2 \cdot 5} \right] + \left[ 3 - 0 \right] = 16 - 1.2 = 14.8
\]

\section*{Άσκηση 6}

\subsection*{8.2.1 (MMDS)}

Θεωρούμε όπως και στο παράδειγμα της εκφώνησης το $n$ να είναι πόσες μέρες έχω πάει για σκι προηγουμένως.
Επίσης θεωρούμε $k$ τον αριθμό της μέρας που θα τα παρατήσω.

Αρχικά, θα πρέπει να δούμε πώς δουλεύει ο offline αλγόριθμος.
Με το $k$ γνωστό, αρκεί να δει αν $k \leq 10$ για να κάνει rent (cost $\$10k$), ενώ αν $k > 10$ κάνει buy (cost $\$100$).

Τώρα ο αλγόριθμός μας έχει μόνο το $n$ σαν πληροφορία, οπότε η στρατηγική του θα έχει τη μορφή "ξεκίνα με renting, και για κάποιο $m>0$ αν $n>m$ τότε άλλαξε σε buy", όπου η χειρότερη περίπτωση θα είναι να τα παρατήσω την ίδια μέρα $(k=m)$.
Οπότε online cost $=10m+100$.

Βλέπουμε τώρα για το competitive ratio:
\begin{itemize}
	\item αν $m \leq 10$:
		\[
			\frac{\text{offline}}{\text{online}} = \frac{10m}{10m+100} = \frac{m}{m+10} = 1 - \frac{10}{m+10}
		\]
		το οποίο γίνεται maximum στο $1/2$ για $m=10$
	\item αν $m \geq 10$:
		\[
			\frac{\text{offline}}{\text{online}} = \frac{100}{10m+100}
		\]
		το οποίο γίνεται πάλι maximum στο $1/2$ για $m=10$
\end{itemize}
Άρα ο αλγόριθμος που κάνει rent μέχρι τις $10$ μέρες και μετά buy έχει το μεγαλύτερο competitive ratio $=1/2$.

\subsection*{8.4.1 (MMDS)}

\begin{center}
	\begin{tabular}{| c || c | c | c |}
		\hline
		& $A$ & $B$ & $C$ \\ \hhline{|=#=|=|=|}
		bids & $x$ & $x,y$ & $x,y,z$ \\ \hline
		budget & $2$ & $2$ & $2$ \\ \hline
	\end{tabular}
\end{center}

\paragraph{(a)} Ξέρουμε ότι ο greedy αλγόριθμος θα αναθέσει τυχαία ένα query σε έναν advertiser αρκεί να έχουν budget.
Για input: $xxyyzz$, αρχικά βλέπουμε τα δύο πρώτα $x$ queries θα πάνε σίγουρα σε κάποιον, εφόσον όλοι τα θέλουν και έχουν όλοι αρκετό budget.
Μετά βλέπουμε ότι τα δύο επόμενα $y$ queries τα έχουν κάνει bid οι $B,C$ με budget $2$ o καθένας, οπότε όποιος και να έχει πάρει τα δύο προηγούμενα $x$ και πάλι θα βρεθεί διαθέσιμος advertiser για να γίνουν assign τα δύο $y$.

Οπότε ο greedy αλγόριθμος θα κάνει assign σίγουρα τουλάχιστον $4$ queries.

\paragraph{(b)} Θα εξετάσουμε το query: $xxzzzz$.

Ο optimal αλγόριθμος θα έκανε assign τα πρώτα δύο $x$ στον $A$, τα επόμενα δύο $z$ στον $C$ και τα τελευταία δύο $z$ σε κανέναν, οπότε συνολικός αριθμός assignments $=4$.

Ο greedy αλγόριθμος θα μπορούσε στη χειρότερη να κάνει assign τα δύο πρώτα $x$ στον $C$ με τα υπόλοιπα τέσσερα $z$ να μην γίνουν καθόλου, οπότε συνολικός αριθμός assignments $=2=4/2$.

\section*{Άσκηση 7}

\subsection*{9.2.3 (MMDS)}

\paragraph{(a)} Αρχικά έχουμε ότι ο μέσος όρος των ratings του χρήστη είναι $\frac{4+2+5}{3} = 11/3$.
Οπότε τα normalised ratings είναι
\begin{center}
	\begin{tabular}{| c || c | c | c |}
		\hline
		& $A$ & $B$ & $C$ \\ \hline
		user & $1/3$ & $-5/3$ & $4/3$ \\ \hline
	\end{tabular}
\end{center}

\paragraph{(b)} Το user profile του χρήστη θα αποτελείται από τις στήλες των υπολογιστών $A,B,C$, για τις οποίες έχουμε
\begin{flalign*}
	\text{Processor Speed:}& \quad \frac{3.06+2.68+2.92}{3} = \frac{88.6}{3} \approx 2.89\\
	\text{Disk Size:}& \quad \frac{500+320+640}{3} = \frac{1460}{3} \approx 486.67 \\
	\text{Main-Memory Size:}& \quad \frac{6+4+6}{3} = \frac{16}{3} \approx 5.33
\end{flalign*}
Οπότε το user profile του χρήστη είναι η γραμμή του παρακάτω πίνακα.
\begin{center}
	\begin{tabular}{| c || c | c | c |}
		\hline
		& $A$ & $B$ & $C$ \\ \hhline{|=#=|=|=|}
		user & $88.6/3$ & $1460/3$ & $16/3$ \\ \hline
	\end{tabular}
\end{center}

\subsection*{9.3.2 (MMDS)}

Παίρνουμε τον πίνακα 9.8 (MMDS) και αντικαθιστούμε τα $3,4,5$ με $1$ και τα $1,2$ και τα κενά με 0
\begin{center}
	\begin{tabular}{| c || c | c | c | c | c | c | c | c |}
		\hline
		& $a$ & $b$ & $c$ & $d$ & $e$ & $f$ & $g$ & $h$ \\ \hhline{|=#=|=|=|=|=|=|=|=|}
		$A$ & $1$ & $1$ & $0$ & $1$ & $0$ & $0$ & $1$ & $0$ \\ \hline
		$B$ & $0$ & $1$ & $1$ & $1$ & $0$ & $0$ & $0$ & $0$ \\ \hline
		$C$ & $0$ & $0$ & $0$ & $1$ & $0$ & $1$ & $1$ & $1$ \\ \hline
	\end{tabular}
\end{center}
και υπολογίζουμε τη Jaccard distance ($1-$ Jaccard similarity) για όλα τα ζευγάρια
\begin{center}
	\begin{tabular}{c | c c c c c c c c}
		& $a$ & $b$ & $c$ & $d$ & $e$ & $f$ & $g$ & $h$ \\ \hline
		$a$ & & $1/2$ & $1$ & $2/3$ & $1$ & $1$ & $1/2$ & $1$ \\
		$b$ & & & $1/2$ & $1/3$ & $1$ & $1$ & $2/3$ & $1$ \\
		$c$ & & & & $2/3$ & $1$ & $1$ & $1$ & $1$ \\
		$d$ & & & & & $1$ & $2/3$ & $1/3$ & $2/3$ \\
		$e$ & & & & & & $1$ & $1$ & $1$ \\
		$f$ & & & & & & & $1/2$ & $0$ \\
		$g$ & & & & & & & & $1/2$ \\
	\end{tabular}
\end{center}
όπου αξίζει να σημειώσουμε ότι οι τιμές $0,1/3,1/2,2/3,1$ είναι οι μόνες πιθανές τιμές για Jaccard distance μεταξύ συνόλων με τρία στοιχεία.

Θεωρούμε κάθε στήλη ένα cluster.
Προφανώς το πρώτο merge που θα κάνουμε είναι μεταξύ των $f,h$ που έχουν τη μικρότερη απόσταση, ενώ ταυτόχρονα επειδή οι δύο αυτές στήλες είναι ίδιες οι αποστάσεις μεταξύ των cluster παραμένουν ίδιες.
Συνεχίζουμε κάνοντας merge τις $b,d,g$ που έχουν την αμέσως μικρότερη απόσταση $(1/3)$.
Μπορούμε να κάνουμε και τις δύο διότι εφόσον οι $b,d,g$ δεν έχουν απόσταση $0$ με κάποια στήλη, τότε όποιες δύο και να κάνουμε πρώτα merge, οι νέες αποστάσεις δεν θα είναι καμία $0$ και το $1/3$ θα παραμείνει το αμέσως μικρότερο.

Με τα παραπάνω merges βλέπουμε τον ανανεωμένο πίνακα αποστάσεων
\begin{center}
	\begin{tabular}{c | c c c c c}
		& $a$ & $bdg$ & $c$ & $e$ & $fh$ \\ \hline
		$a$ & & $1/2$ & $1$ & $1$ & $1$ \\
		$bdg$ & & & $1/2$ & $1$ & $1/2$ \\
		$c$ & & & & $1$ & $1$ \\
		$e$ & & & & & $1$ \\
	\end{tabular}
\end{center}
οπότε το επόμενο merge μπορεί να είναι είτε το $a$ είτε το $c$ με το $bdg$.
Επιλέγουμε το $a$ και έτσι το τελικό clustering σε 4 στοιχεία είναι το
\[\{(abdg), (c), (e), (fh)\}\]

\paragraph{(b)} Υπολογίζουμε τις νέες τιμές για τα cluster profiles.
Συγκεκριμένα για το $(abdg)$ έχουμε
\[
	A: \frac{4+5+5+3}{4} = \frac{17}{4} \qquad B: \frac{3+3+1}{3} = \frac73 \qquad C: \frac{2+3+5}{3}=\frac{10}{3}
\]
ενώ για το $(fh)$ αρκεί να βρούμε για το $C: (4+3)/2 = 7/2$.
Οπότε ο νέος πίνακας με τις τιμές ανά cluster είναι
\begin{center}
	\begin{tabular}{| c || c | c | c | c |}
		\hline
		& $(abdg)$ & $(c)$ & $(e)$ & $(fg)$ \\ \hhline{|=#=|=|=|=|}
		$A$ & $17/4$ & & $1$ & $2$ \\ \hline
		$B$ & $7/3$ & $4$ & $1$ & $2$\\ \hline
		$C$ & $10/3$ & $1$ & & $7/2$ \\ \hline
	\end{tabular}
\end{center}

\paragraph{(c)}
\begin{flalign*}
	cos(\hat{AB}) &= 1 - \frac{\frac{17}{4} \cdot \frac73 + 0 + 1 + 2 \cdot 2}{\sqrt{\left(\frac{17}{4}\right)^2 + 1^2 + 2^2} \cdot \sqrt{\left(\frac73\right)^2 + 4^2 + 1^2 + 2^2}} \approx 1-0.6 = 0.4\\
	cos(\hat{AC}) &= 1 - \frac{\frac{17}{4} \cdot \frac{10}{3} + 0 + 0 + 2 \cdot \frac72}{\sqrt{\left(\frac{17}{4}\right)^2 + 1^2 + 2^2} \cdot \sqrt{\left(\frac{10}{3}\right)^2 + 1^2 + \left(\frac72\right)^2}} \approx 1-0.9 = 0.1 \\
	cos(\hat{BC}) &= 1 - \frac{\frac73 \cdot \frac{10}{3} + 4 + 0 + 2 \cdot \frac72}{\sqrt{\left(\frac73\right)^2 + 4^2 + 1^2 + 2^2} \cdot \sqrt{\left(\frac{10}{3}\right)^2 + 1^2 + \left(\frac72\right)^2}} \approx 1-0.74 = 0.26
\end{flalign*}

\end{document}

### 2022-07-03 ads/ask_s02.tex
ADS: Exer02: Finished exercise 1

@@
 \newcommand{\RightarrowArg}[1]{\stackrel{#1}{\Longrightarrow}}
+\newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
 
@@
 		\[y_1=y_2 \Rightarrow ak_1+b \equiv ak_2+b \bmod p \RightarrowArg{p \text{ πρώτος}} k_1 \equiv k_2 \bmod p \RightarrowArg{k_1,k_2<p} k_1=k_2 \text{ άτοπο}\]
-		Δηλαδή τα $p(p-1)$ το πλήθος ζευγάρια $y_1,y_2$ αντιστοιχούνται 1-1 με τις $p(p-1)$ πιθανές επιλογές των $a,b$
+		Δηλαδή τα $p(p-1)$ το πλήθος ζευγάρια $(y_1,y_2)$ αντιστοιχούνται 1-1 με τις $p(p-1)$ πιθανές επιλογές των $a,b$
 	\item Έχουμε $h_{a,b}(k_1) = h_{a,b}(k_2) \Leftrightarrow y_1 \equiv y_2 \bmod m$
@@
 Έστω ότι $y_1 \equiv 0 \bmod m$ όπου υπάρχουν $\lfloor p/m \rfloor + 1$ πιθανές τιμές για το $y_1$.
-Για καθεμία έχουμε το πολύ $\lfloor p/m \rfloor$ το πλήθος $y_2$ τέτοια ώστε $y_2 \equiv 0 \bmod p$ (εξαιρούμε την περίπτωση $y_2=y_1$).
-Επαναλαμβάνουμε το παραπάνω $\forall i = 1,2,\dots,m-1$ και παίρνουμε $m$ φορές το προηγούμενο.
-Οπότε συνολικά έχουμε
-\[
-	|h_{a,b}|_{h_{a,b}(k_1)=h_{a,b}(k_2)} \leq m \left(\left\lfloor \frac{p}{m} \right\rfloor + 1\right) \left\lfloor \frac{p}{m} \right\rfloor \leq m \frac{p(p+m)}{m^2} \leq ???
-%\frac{p(p-1)}{m} = \frac{|H|}{m}
-\]
-%Άρα η $H$ είναι καθολική οικογένεια συναρτήσεων κατακερματισμού.
+Για καθεμία έχουμε $\lfloor p/m \rfloor$ το πλήθος $y_2$ τέτοια ώστε $y_2 \equiv 0 \bmod p$ (εξαιρούμε την περίπτωση $y_2=y_1$).
+Επαναλαμβάνουμε το παραπάνω για $y_1 \equiv i \bmod m, \forall i = 1,2,\dots,[(p-1) \bmod m]$ διότι μέχρι εκεί θα ισχύουν τα ίδια πλήθη.
+Για $i=(p \bmod m),\dots,m-1$ έχουμε $\lfloor p/m \rfloor$ πιθανές τιμές για το $y_1$ και $\lfloor p/m \rfloor - 1$ για το $y_2$.
 
-%\paragraph{(γ)} Θέτοντας $U=[p]$ παρατηρούμε ότι η παραπάνω απόδειξη παραμένει απαράλλαχτη, εφόσον για μια τυχαία επιλογή  $k_1,k_2 \in U = [p]$ έχουμε πάλι ότι $\forall a,b \in [p], a \neq 0$ αντιστοιχούν σε ένα μοναδικό ζευγάρι $(y_1, y_2) \in [p] \times [p]$, οπότε με τον ίδιο συλλογισμό καταλήγουμε ότι η οικογένεια συναρτήσεων κατακερματισμού παραμένει καθολική.
+Θέτουμε $p_m = p \bmod m$ και αναφέρουμε ότι
+\begin{equation}
+	m \left\lfloor \frac{p}{m} \right\rfloor = p - p_m \label{eq1}
+\end{equation}
+
+Συνολικά λοιπόν έχουμε 
+\begin{flalign*}
+	|h_{a,b}|_{h_{a,b}(k_1)=h_{a,b}(k_2)} &= p_m \left(\left\lfloor \frac{p}{m} \right\rfloor + 1\right) \left\lfloor \frac{p}{m} \right\rfloor + (m-p_m) \left\lfloor \frac{p}{m} \right\rfloor \left(\left\lfloor \frac{p}{m} \right\rfloor - 1\right) \\
+		&= \left\lfloor \frac{p}{m} \right\rfloor \left( p_m \left\lfloor \frac{p}{m} \right\rfloor + p_m + (m-p_m) \left\lfloor \frac{p}{m} \right\rfloor - m + p_m \right) \\
+		&= \left\lfloor \frac{p}{m} \right\rfloor \left( m \left\lfloor \frac{p}{m} \right\rfloor - m + 2p_m \right) \\
+		&\indeq{(\ref{eq1})} \left\lfloor \frac{p}{m} \right\rfloor (p - p_m - m + 2p_m) \\
+		&= \left\lfloor \frac{p}{m} \right\rfloor (p - (m - p_m)) \\
+		&\leq \left(\frac{p}{m}\right) (p - 1) = \frac{|H|}{m}
+\end{flalign*}
+Άρα η $H$ είναι καθολική οικογένεια συναρτήσεων κατακερματισμού.
+
+\paragraph{(γ)} Θέτοντας $U=[p]$ παρατηρούμε ότι η παραπάνω απόδειξη παραμένει απαράλλαχτη, εφόσον για μια τυχαία επιλογή  $k_1,k_2 \in U = [p]$ έχουμε πάλι ότι $\forall a,b \in [p], a \neq 0$ υπάρχει 1-1 αντιστοιχία σε ένα ζευγάρι $(y_1, y_2) \in [p] \times [p]$, οπότε με τον ίδιο συλλογισμό καταλήγουμε ότι η οικογένεια συναρτήσεων κατακερματισμού παραμένει καθολική.
 

### 2022-07-03 ads/ask_s02.tex
ADS: Exer02: Added exercise 3a and improved 4-10.4.2

@@
 \usepackage{amsmath}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 \usepackage{hhline}
@@
 
+\paragraph{(α)} Βλέπε τους αλγoρίθμους \ref{gn-bfsdfs} και \ref{gn-main}.
+
+\begin{algorithm}
+	\caption{Girvan-Newman($V, E$) - BFS/DFS functions}
+	\label{gn-bfsdfs}
+	\begin{algorithmic}
+		\Function{bfs\_step\_1}{$v, dag$}
+			\Comment{BFS loop to construct the DAG Tree.}
+			\ForAll{$u:(v,u) \in E$}
+				\If{$u \notin dag$}
+					\State $dag.insert(u, \text{parent} \gets v$)
+				\EndIf
+			\EndFor
+			\ForAll{$u \in dag.nodes[v].children$}
+				\State \Call{bfs\_step\_1}{$u, dag$}
+			\EndFor
+		\EndFunction
+		\Statex
+		\Function{bfs\_step\_2}{$v, dag$}
+			\Comment{BFS loop to calculate the node labels.}
+			\If{$v == dag.root$}
+				\State $dag.nodes[v].label \gets 1$
+			\Else
+				\State $label \gets 0$
+				\ForAll{$p \in dag.nodes[v].parents$}
+					$label \gets label + p.label$
+				\EndFor
+				\State $dag.nodes[v].label \gets label$
+			\EndIf
+			\ForAll{$u \in dag.nodes[v].children$}
+				\State \Call{bfs\_step\_2}{$u, dag$}
+			\EndFor
+		\EndFunction
+		\Statex
+		\Function{dfs\_step\_3}{$v, dag$}
+			\Comment{DFS loop to calculate the node/DAG edge credits.}
+			\ForAll{$c \in dag.nodes[v].children$}
+				\State \Call{dfs\_step\_3}{$c, dag$}
+			\EndFor
+			\State $credit \gets 1$
+			\If{$v$ is not leaf}
+				\ForAll{$c \in dag.nodes[v].children$}
+					\State $credit \gets credit + dag.edges[(v,c)].credit$
+				\EndFor
+			\EndIf
+			\State $dag.nodes[v].credit \gets credit$
+			\State $parent\_total\_credit \gets 0$
+			\ForAll{$p \in dag.nodes[v].parents$}
+				\State $parent\_total\_credit \gets parent\_total\_credit + p.credit$
+			\EndFor
+			\ForAll{$p \in dag.nodes[v].parents$}
+				\State $dag.edges[(p,v)].credit \gets p.credit / parent\_total\_credit$
+			\EndFor
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+\begin{algorithm}
+	\caption{Girvan-Newman($V, E$) - main}
+	\label{gn-main}
+	\begin{algorithmic}
+		\If {$|E| == 0$ OR $|V| \leq 1$}
+			\State \Return FALSE
+		\EndIf
+		\State $edge\_credit \gets array[]$
+		\ForAll{$e \in E$}
+			\State $edge\_credit[e] \gets 0$
+		\EndFor
+		\Statex
+		\ForAll{$v \in V$}
+			\State $dag \gets new \; DAG()$
+			\Comment{The DAG tree structure.}
+			\State $dag.root \gets v$
+			\State \Call{bfs\_step\_1}{$v, dag$}
+			\State \Call{bfs\_step\_2}{$v, dag$}
+			\State \Call{dfs\_step\_3}{$v, dag$}
+			\ForAll{$e \in dag.edges$}
+				\State $edge\_credit[e] \gets edge\_credit + e.credit$
+			\EndFor
+		\EndFor
+		\Statex
+		\ForAll{$e \in E$}
+			\Comment{Finally divide everything by 2.}
+			\State $edge\_credit[e] \gets edge\_credit[e] / 2$
+		\EndFor
+		\Statex
+		\Return $edge\_credit$
+	\end{algorithmic}
+\end{algorithm}
+
+Βλέποντας τα βήματα του αλγορίθμου έχουμε ένα pre και post-processing για τις ακμές πριν και μετά τα BFS/DFS.
+Οπότε η πολυπλοκότητά του είναι $\mathcal{O}(m + n[(m+n) + (m+n) + (m+n)] + m) = \mathcal{O}(n(m+n))$.
+
 \paragraph{(β)} Στην περίπτωση που ο γράφος είναι δέντρο τότε κάθε ακμή είναι γέφυρα και άρα τα συντομότερα μονοπάτια που περνάνε από την ακμή αυτή είναι αυτά που ξεκινάνε από έναν κόμβο της μιας πλευράς και καταλήγουν σε κόμβο της άλλης.
@@
 \[[-0.33,-0.22,-0.33,-0.52,0.09,0,-0.36,-0.39,-0.41]\]
-το οποίο και προτείνει τη διαμέριση $\{A,B,C,D,G,H,I\},\{E,F\}$.
+το οποίο και προτείνει τη διαμέριση $\{\{A,B,C,D,G,H,I\},\{E,F\}\}$ αν θεωρήσουμε ως κέντρο το $0$, ενώ αν πάρουμε το μέσο όρο τους $-0.27$ τότε παίρνουμε τη διαμέριση $\{\{A,C,D,G,H,I\},\{B,E,F\}\}$.
 

### 2022-07-04 ads/ask_s02.tex
ADS: Exer02: Added exercise 2 and made final fixes and improvements, submitted version

@@
 \newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
+\newcommand{\indleq}[1]{\stackrel{\text{#1}}{\leq}}
+\newcommand{\Expect}{{\rm I\kern-.3em E}}
 
@@
 Προφανώς $k_1 \neq k_2$ και $k_1 \equiv k_2 \bmod m$.
-Θα δείξουμε ότι $\forall a \in [m] \setminus 0, b \in [m]$ παίρνουμε $h_{a,b}(k_1) = h_{a,b}(k_2)$.
+Θα δείξουμε ότι $\forall a \in [m] \setminus \{0\}, b \in [m]$ παίρνουμε $h_{a,b}(k_1) = h_{a,b}(k_2)$.
 Όντως
@@
 	\item Το πλήθος των πιθανών $h_{a,b}$ συναρτήσεων είναι $|H|=p(p-1)$
-	\item Εφόσον $p$ πρώτος, $\forall a,b \in [p], a \neq 0$ υπάρχει μοναδικό ζευγάρι $(y_1,y_2) \in [p] \times [p]$ όπου\\
-		$y_1 \equiv ak_1+b \bmod p, y_2 \equiv ak_2+b \bmod p$ και $y_1 \neq y_2$, αφού
+	\item Εφόσον $p$ πρώτος, $\forall (a,b) \in ([p] \setminus \{0\}) \times [p]$ υπάρχει μοναδικό ζευγάρι $(y_1,y_2) \in [p] \times [p]$ όπου $y_1 \equiv ak_1+b \bmod p, y_2 \equiv ak_2+b \bmod p$ και $y_1 \neq y_2$, αφού
 		\[y_1=y_2 \Rightarrow ak_1+b \equiv ak_2+b \bmod p \RightarrowArg{p \text{ πρώτος}} k_1 \equiv k_2 \bmod p \RightarrowArg{k_1,k_2<p} k_1=k_2 \text{ άτοπο}\]
@@
 Μετράμε λοιπόν τα πιθανά ζευγάρια $y_1,y_2$ τέτοια ώστε $y_1 \equiv y_2 \bmod m$.
-Έστω ότι $y_1 \equiv 0 \bmod m$ όπου υπάρχουν $\lfloor p/m \rfloor + 1$ πιθανές τιμές για το $y_1$.
-Για καθεμία έχουμε $\lfloor p/m \rfloor$ το πλήθος $y_2$ τέτοια ώστε $y_2 \equiv 0 \bmod p$ (εξαιρούμε την περίπτωση $y_2=y_1$).
-Επαναλαμβάνουμε το παραπάνω για $y_1 \equiv i \bmod m, \forall i = 1,2,\dots,[(p-1) \bmod m]$ διότι μέχρι εκεί θα ισχύουν τα ίδια πλήθη.
-Για $i=(p \bmod m),\dots,m-1$ έχουμε $\lfloor p/m \rfloor$ πιθανές τιμές για το $y_1$ και $\lfloor p/m \rfloor - 1$ για το $y_2$.
+Έστω ότι $y_1 \equiv 0 \bmod m$, τότε υπάρχουν $\lfloor p/m \rfloor + 1$ πιθανές τιμές για το $y_1$ και για καθεμία από αυτές έχουμε $\lfloor p/m \rfloor$ το πλήθος $y_2$ τέτοια ώστε $y_2 \equiv 0 \bmod p$ (εξαιρούμε την περίπτωση $y_2=y_1$).
+Επαναλαμβάνουμε το παραπάνω για $y_1 \equiv i \bmod m, \forall i = 1,2,\dots,[(p-1) \bmod m]$ όπου παίρνουμε τις ίδιες τιμές για τα πλήθη των $y_1,y_2$, ενώ για $i=(p \bmod m),\dots,m-1$ έχουμε $\lfloor p/m \rfloor$ πιθανές τιμές για το $y_1$ και $\lfloor p/m \rfloor - 1$ τιμές για το $y_2$.
 
-Θέτουμε $p_m = p \bmod m$ και αναφέρουμε ότι
+Θέτουμε $p_m = p \bmod m$ και αναφέρουμε ότι ισχύει ότι
 \begin{equation}
@@
 \end{flalign*}
-Άρα η $H$ είναι καθολική οικογένεια συναρτήσεων κατακερματισμού.
+και άρα καταλήγουμε ότι η $H$ είναι μια καθολική οικογένεια συναρτήσεων κατακερματισμού.
 
@@
 
-%\section*{Άσκηση 2}
+\section*{Άσκηση 2}
 
-%\paragraph{(α)} Ο χρόνος εισαγωγής του $i$-οστού στοιχείου είναι ένα τυχαίο γεγονός που ακολουθεί την κατανομή Bernoulli($m-i/m$).
-%Άρα ο αναμενόμενος αριθμός επαναλήψεων μέχρι την πρώτη επιτυχία είναι $m/m-i$ (εφόσον αυτό ακολουθεί Geom($m-i/m$)).
-%\paragraph{(α)} Μετά από την εισαγωγή $n$ στοιχείων, η επιτυχής αναζήτηση .
-%Άρα ο αναμενόμενος αριθμός επαναλήψεων μέχρι την πρώτη επιτυχία είναι $1/(1-a)$ (εφόσον αυτό ακολουθεί Geom($1-a$)).
-%\\[8pt]
-%Από την άλλη, με την ίδια λογική, ο χρόνος εισαγωγής του $i$-οστού στοιχείου είναι $m/m-i$, εφόσον εδώ η πιθανότητα επιτυχίας να βρεθεί κενή θέση είναι $m-i/m$.
+\paragraph{(α)} Γνωρίζουμε ότι όταν ο αλγόριθμος προσθέτει ένα στοιχείο $k$ στο hash table τότε επισκέπτεται μια ακολουθία κελιών $h(k,0),h(k,1),\dots,h(k,(m-1))$ μέχρι να βρει κενό κελί.
+Από την άλλη, κατά τη διάρκεια επιτυχούς αναζήτησης του στοιχείου $k$ ο αλγόριθμος θα επισκεφθεί την ίδια ακολουθία κελιών μέχρι να βρει το στοιχείο, δηλαδή θα χρειαστεί το ίδιο πλήθος βημάτων με όσα χρειάστηκαν για να προστεθεί το $k$ στον πίνακα.
+Άρα ο μέσος χρόνος επιτυχούς αναζήτησης για όλα τα $n$ στοιχεία είναι ίσος με το μέσο χρόνο εισαγωγής του καθενός από αυτά.
+
+\paragraph{(β)} Έστω $X_i$ τυχαία μεταβλητή για τον αριθμό των δοκιμών που θα χρειαστούμε για την εισαγωγή του $i$-οστού στοιχείου ($i \in \{0,1,\dots,n-1\}$) στον πίνακα.
+Βλέπουμε ότι αν ο πίνακας έχει ήδη $i$ στοιχεία, τότε η εισαγωγή ενός καινούργιου έχει πιθανότητα επιτυχίας $\frac{m-i}{m}$, δηλαδή είναι ένα τυχαίο γεγονός που ακολουθεί κατανομή Bernoulli($\frac{m-i}{m}$).
+Οπότε εφόσον $X_i$ είναι το πλήθος αυτών των δοκιμών παίρνουμε $X_i \sim \text{Geom}(\frac{m-i}{m})$ και άρα
+\[\Expect[X_i]=\frac{1}{\frac{m-i}{m}}=\frac{m}{m-i}\]
+Εδώ να αναφέρουμε ότι ισχύει το παρακάτω που θα το χρειαστούμε
+\begin{equation}
+	\sum_{x=1}^{n} \frac1{x+1} \leq \int_{1}^{n} \frac1x = \ln(x) \label{eq2}
+\end{equation}
+Υπολογίζουμε τώρα το μέσο χρόνο εισαγωγής, 
+\begin{flalign*}
+	\Expect[\bar{X_i}] &= \frac1n \sum_{i=0}^{n-1} \Expect[X_i] = \frac1n \sum_{i=0}^{n-1} \frac{m}{m-i} = \frac1a \sum_{i=0}^{n-1} \frac1{m-i} \\
+		&= \frac1a \left( \frac1m + \frac1{m-1} + \cdots + \frac1{m-(n-2)} + \frac1{m-(n-1)} \right) \\
+		&= \frac1a \left( \frac1{(m-n)+1} + \frac1{(m-n)+2} + \cdots + \frac1{(m-n)+(n-1)} + \frac1{(m-n)+n} \right) \\
+		&= \frac1a \sum_{i=m-n}^{m-1} \frac1{i+1} \leq \frac1a \sum_{i=m-n}^m \frac1{i+1} \indleq{(\ref{eq2})} \frac1a \int_{m-n}^m \frac1x dx = \frac1a \left( \int_1^m \frac1x dx - \int_1^{m-n} \frac1x dx \right) \\
+		&= \frac1a (\ln(m) - \ln(m-n)) = \frac1a \ln \frac{m}{m-n} = \frac1a \ln \frac1{1-a}
+\end{flalign*}
 
@@
 				\ForAll{$p \in dag.nodes[v].parents$}
-					$label \gets label + p.label$
+					\State $label \gets label + p.label$
 				\EndFor
@@
 			\ForAll{$p \in dag.nodes[v].parents$}
-				\State $dag.edges[(p,v)].credit \gets p.credit / parent\_total\_credit$
+				\State $dag.edges[(p,v)].credit \gets v.credit * (p.credit / parent\_total\_credit)$
 			\EndFor
@@
 Βλέποντας τα βήματα του αλγορίθμου έχουμε ένα pre και post-processing για τις ακμές πριν και μετά τα BFS/DFS.
-Οπότε η πολυπλοκότητά του είναι $\mathcal{O}(m + n[(m+n) + (m+n) + (m+n)] + m) = \mathcal{O}(n(m+n))$.
+Οπότε η πολυπλοκότητά του είναι
+\[\mathcal{O}(m + n[(m+n) + (m+n) + (m+n)] + m) = \mathcal{O}(n(m+n))\]
+\[= \mathcal{O}(n^2+nm))\]
 
@@
 \[[-0.33,-0.22,-0.33,-0.52,0.09,0,-0.36,-0.39,-0.41]\]
-το οποίο και προτείνει τη διαμέριση $\{\{A,B,C,D,G,H,I\},\{E,F\}\}$ αν θεωρήσουμε ως κέντρο το $0$, ενώ αν πάρουμε το μέσο όρο τους $-0.27$ τότε παίρνουμε τη διαμέριση $\{\{A,C,D,G,H,I\},\{B,E,F\}\}$.
+το οποίο και προτείνει τη διαμέριση $\{\{A,B,C,D,G,H,I\},\{E,F\}\}$ αν θεωρήσουμε ως κέντρο το $0$.
+
+Εναλλακτικά, αν πάρουμε ως κέντρο το μέσο όρο τους $-0.27$ τότε παίρνουμε τη διαμέριση $\{\{A,C,D,G,H,I\},\{B,E,F\}\}$.
 
@@
 
-Τώρα ο αλγόριθμός μας έχει μόνο το $n$ σαν πληροφορία, οπότε η στρατηγική του θα έχει τη μορφή "ξεκίνα με renting, και για κάποιο $m>0$ αν $n>m$ τότε άλλαξε σε buy", όπου η χειρότερη περίπτωση θα είναι να τα παρατήσω την ίδια μέρα $(k=m)$.
+Τώρα ο αλγόριθμός μας έχει μόνο το $n$ σαν πληροφορία, οπότε η στρατηγική του θα έχει τη μορφή "ξεκίνα με renting, και για κάποιο $m>0$ αν $n>m$ τότε άλλαξε σε buy", με τη χειρότερη περίπτωση να είναι να τα παρατήσω την ίδια μέρα $(k=m)$.
 Οπότε online cost $=10m+100$.

### 2022-07-04 ads/ask_s02.py
ADS: Exer02: Included helper python script

@@ -1,0 +1,25 @@
+import numpy as np
+
+
+# Excercise 4 - 10.4.2 (MMDS)
+m = np.array([
+  [2, -1, -1, 0, 0, 0, 0, 0, 0],
+  [-1, 3, -1, 0, 0, 0, 0, -1, 0],
+  [-1, -1, 3, -1, 0, 0, 0, 0, 0],
+  [0, 0, -1, 3, -1, -1, 0, 0, 0],
+  [0, 0, 0, -1, 3, -1, -1, 0, 0],
+  [0, 0, 0, -1, -1, 2, 0, 0, 0],
+  [0, 0, 0, 0, -1, 0, 3, -1, -1],
+  [0, -1, 0, 0, 0, 0, -1, 3, -1],
+  [0, 0, 0, 0, 0, 0, -1, -1, 2]
+])
+print(m)
+
+#eig1 = np.linalg.eig(m)
+#print(np.round(eig1[0], 2))
+#print(np.round(eig1[1], 2))
+
+eig2 = np.linalg.eigh(m)
+#print(np.round(eig2[0], 2))
+#print(np.round(eig2[1], 2))
+print(np.round(eig2[1][1], 2))

### 2024-03-17 thesis/article.tex
Thesis: First draft, introduction and basic skeleton

\documentclass[a4paper,11pt]{article}
\usepackage{a4wide}

% Greek fonts
\RequirePackage{fontspec}
\defaultfontfeatures{Ligatures=TeX}
  % you may want to try: {Liberation Serif} or {Times New Roman}
\setmainfont{FreeSerif}
  % you may want to try: {Liberation Sans} or {Arial}
\setsansfont[Scale=MatchLowercase]{FreeSans}
  % you may want to try: {FreeMono} or {Courier New}
\setmonofont[Scale=MatchLowercase]{FreeMono}

% \usepackage{mathtools}
% \usepackage{tikz}
\usepackage{enumerate}

\newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
% Commands for wrapping properly common expressions.
\newcommand{\Exp}{\mathrm{Exp}}
\newcommand{\Expect}{{\rm I\kern-.3em E}}
\newcommand{\at}{\mathrm{\alpha_t}}
\newcommand{\NE}{\mathrm{N.E.}}

% Main document
\begin{document}
\title{Profit Optimisation in Heterogeneous 2-link Parallel Games}
\author{Thomas Pappas}
\date{}
\maketitle

\section*{Abstract}
We study (so far) a 3-level optimisation problem where, in a 2-link $s-t$ network, link owners compete for profit by assigning tolls to links, thus creating a toll congestion game.
In addition, each player responds to tolls in a heterogeneous way, described by a distribution function $\alpha(p)$.
We first introduce a new term $\at$ which, given a set of tolls, can help us describe how the flow is split between the 2 links, and then we will use it to prove some properties of the game.
We will show that even with affine latencies, there are cases where no Nash Equilibrium exists in the profit game between the toll owners.

Then what else? Maybe find cases where there always exists a $\NE$.

\section{Introduction}

In this thesis we study a three level optimisation problem.
On the basis there is a 2-node $(s, t)$, 2-link $s-t$ network, each link with a non-decreasing latency function that defines how the traffic increases as more players flow into that link.
On the first level a flow $[0, 1]$ wants to move from $s$ to $t$ and experience the minimum latency (traffic).
On the second level, the links might also have tolls which impose an additional cost to the flow players, plus in our case (heterogeneous users) each player has a different money-time trade-off and thus see the link costs differently.
Finally on the third level (are the levels really that way?), the tolls are owned by players who profit on the flow that uses that link and compete to maximise it.

We know from [insert ref] that regardless of the distribution function $a$ or the latency functions (as long as they are non-decreasing) a $\NE$ always exists.
In that $\NE$ the users are split with the money-sensitive ones on the link with the lower toll and the time-sensitive ones on the higher toll one, each one seeing their link as either lower or equal cost with the other (while they all see traffic equally).

We introduce a new term $\at=\frac{l_1(x)-l_2(1-x)}{t_2-t_1}$ which is the $a(p)$ value of a user $p$ which sees the link costs equally.

\section{Related Work}
TODO

\section{Preliminaries}

A 2-link $s-t$ parallel network is a graph with a source node $s$, a destination node $t$ and $2$ edges connecting $s$ to $t$.
Each link is associated with a latency function $l_1, l_2$
[TODO: Add figure]
A flow of infinitesimal users totaling up to a flow of $[0, 1]$ wishes to move from $s$ to $t$ through the link with the lowest cost.

\section{2-link parallel networks}

We start with the simple case of 2-link parallel networks.
[TODO: Add figure]
In this simple setup a user of the flow

\subsection{Time-money sensitivity split}

Consider a 2-link parallel network.
For the 2 edges of the game we introduce the term time-money sensitivity split, or sensitivity split for simplicity, $\alpha_s(t)$ as the value which if any player $p$ has $\alpha(p)=\alpha_s(t)$ then that player sees the 2 edge total latencies as equal.
More specifically, $\alpha_s(t)$ is the value of the distribution function $\alpha$ such that
\[l_1(x(t)) + \alpha_s(t) t_1 = l_2(1 - x(t)) + \alpha_s(t) t_2 \Rightarrow \alpha_s(t) = \frac{l_1(x(t)) - l_2(1 - x(t)))}{t_2 - t_1}\]
For a set of tolls $t=(t_1,t_2)$ and their respective latencies $l_1(x(t)), l_2(1-x(t))$ on the flows enforced by $t$, $a_s(t)$ is defined as

Some basic properties
\begin{enumerate}[(i)]
	\item $a_s(t) \in [\alpha(0), \alpha(1)] \subseteq [0, +\infty]$
	\item $\alpha_s(t)$
\end{enumerate}

\end{document}

### 2024-03-18 thesis/article.tex
Thesis: Adds sensitivity split definition and properties i-iv

@@
 \usepackage{enumerate}
+\usepackage{amssymb}
+\usepackage{amsthm}
 
+% Commands for wrapping properly common expressions.
 \newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
-% Commands for wrapping properly common expressions.
-\newcommand{\Exp}{\mathrm{Exp}}
-\newcommand{\Expect}{{\rm I\kern-.3em E}}
-\newcommand{\at}{\mathrm{\alpha_t}}
+\newcommand{\RightarrowArg}[1]{\stackrel{#1}{\Longrightarrow}}
+\newcommand{\LeftrightarrowArg}[1]{\stackrel{#1}{\Leftrightarrow}}
 \newcommand{\NE}{\mathrm{N.E.}}
+\newcommand{\as}{\mathrm{\alpha_s}}
+% \newcommand{\Exp}{\mathrm{Exp}}
+% \newcommand{\Expect}{{\rm I\kern-.3em E}}
+
+% Theorem structures.
+\newtheorem{definition}{Definition}[section]
+\newtheorem{lemma}{Lemma}[section]
 
@@
 In addition, each player responds to tolls in a heterogeneous way, described by a distribution function $\alpha(p)$.
-We first introduce a new term $\at$ which, given a set of tolls, can help us describe how the flow is split between the 2 links, and then we will use it to prove some properties of the game.
+We first introduce a new term $\as$ which, given a set of tolls, can help us describe how the flow is split between the 2 links, and then we will use it to prove some properties of the game.
 We will show that even with affine latencies, there are cases where no Nash Equilibrium exists in the profit game between the toll owners.
@@
 
-We introduce a new term $\at=\frac{l_1(x)-l_2(1-x)}{t_2-t_1}$ which is the $a(p)$ value of a user $p$ which sees the link costs equally.
+We introduce a new term $\as=\frac{l_1(x)-l_2(1-x)}{t_2-t_1}$ which is the $a(p)$ value of a user $p$ which sees the link costs equally.
 
@@
 
-Consider a 2-link parallel network.
-For the 2 edges of the game we introduce the term time-money sensitivity split, or sensitivity split for simplicity, $\alpha_s(t)$ as the value which if any player $p$ has $\alpha(p)=\alpha_s(t)$ then that player sees the 2 edge total latencies as equal.
-More specifically, $\alpha_s(t)$ is the value of the distribution function $\alpha$ such that
-\[l_1(x(t)) + \alpha_s(t) t_1 = l_2(1 - x(t)) + \alpha_s(t) t_2 \Rightarrow \alpha_s(t) = \frac{l_1(x(t)) - l_2(1 - x(t)))}{t_2 - t_1}\]
-For a set of tolls $t=(t_1,t_2)$ and their respective latencies $l_1(x(t)), l_2(1-x(t))$ on the flows enforced by $t$, $a_s(t)$ is defined as
+Consider a 2-link parallel network with latency functions $l_1(x), l_2(x)$ and tolls $t=(t_1, t_2)$ assigned to them.
+Without loss of generality we assume $t_1 > t_2$ which in turn means that for the resulting equilibrium flow $x = (x_1(t), x_2(t))$ it holds that $l_1(x_1(t)) < l_2(x_2(t))$.
+This equilibrium is guaranteed to exist according to [TODO: add ref]).
+For the 2 edges of the game we introduce the term time-money sensitivity split $\as(t)$ as the value for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edge total latencies as equal.
+More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
+\[l_1(x_1(t)) + \as(t) t_1 = l_2(x_2(t)) + \as(t) t_2\]
+Solving for $\as$ we get
+\[\as(t) = \frac{l_2(x_2(t)) - l_1(x_1(t))}{t_1 - t_2}\]
+\\
+Before we get into a more formal definition and description of $\as$, it'd help to first discuss the nature of the split that $\as$ captures.
+Regardless of whether there exists a player $p$ such that $\alpha(p) = \as(t)$, it still holds that
+\begin{itemize}
+	\item if $\alpha(p) < \as$ then $l_1(x_1(t)) + \alpha(p) t_1 < l_2(x_2(t)) + \alpha(p) t_2$, thus $p$ is on edge $1$
+	\item if $\alpha(p) > \as$ then $l_1(x_1(t)) + \alpha(p) t_1 > l_2(x_2(t)) + \alpha(p) t_2$, thus $p$ is on edge $2$
+	\item if $\alpha(p) = \as$ then $l_1(x_1(t)) + \alpha(p) t_1 = l_2(x_2(t)) + \alpha(p) t_2$, thus $p$ is either on edge $1$ or $2$
+\end{itemize}
+Remember that we have assumed that $t_1 > t_2 \Rightarrow l_1(x_1(t)) < l_2(x_2(t))$.
+Therefore the flow passing through the faster edge $1$ is contained with players where $\alpha(p) \le \as(t)$, while the flow in the cheaper edge $2$ is contained with players where $\alpha(p) \ge \as(t)$.
+Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "higher" part of the split.
+[TODO: Alternative splits: rushed-relaxed, rich-poor]
+Table \ref{table:split_summary} provides of a summary for each part of the split
 
-Some basic properties
+\begin{table}[h!]
+	\centering
+	\caption{Summary of properties for the sensitivity split.}
+	\begin{tabular}{| c || c | c |}
+		\hline
+		& $\alpha(p) \le \as(t)$ & $\alpha(p) \ge \as(t)$ \\ \hline
+		sensitivity & time $\ge$ money & time $\le$ money \\ \hline
+		latency & lower $(l_2)$ & higher $(l_1)$ \\ \hline
+		toll & higher $(t_1)$ & lower $(t_2)$ \\ \hline
+		edge & low-latency, high-toll $(1)$ & high-latency, low-toll $(2)$ \\ \hline
+		$t_1 - t_2$ & lower & higher \\ \hline
+		split & lower & higher \\ \hline
+	\end{tabular}
+	\label{table:split_summary}
+\end{table}
+
+Finally to acknowledge that we have arbitrarily handled any players with $\alpha(p) = \as(t)$.
+Those players, if any, even though they see both edges with equal total cost, in the optimal flow $x$ they have settled in either edge $1$ or $2$.
+We investigate more in depth the relation of $\as$ to the flow in [TODO: add ref].
+\\[12pt]
+We can now formally define $\as$ and prove some of its properties.
+\begin{definition}
+	Given a 2-link parallel heterogeneous game with latency functions $l_1, l_2$, we define the time-money sensitivity split function $\as: \mathbb{R}^2_+ \rightarrow (0, +\infty)$ where for given tolls $t = (t_1, t_2)$
+	\[\as(t) = \frac{l_2(x_2(t)) - l_1(x_1(t))}{t_1 - t_2}\]
+\end{definition}
+The function is well defined since the given tolls $t$ result in a single optimal flow $x(t) = (x_1(t), x_2(t))$ [TODO: add ref].
+
+\begin{lemma}
+	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$, the following hold:
 	\begin{enumerate}[(i)]
-	\item $a_s(t) \in [\alpha(0), \alpha(1)] \subseteq [0, +\infty]$
-	\item $\alpha_s(t)$
+		\item $\as(t) > 0$
+		\item if $x_1(t), x_2(t) > 0$ then $\as(t) \in [\alpha(0), \alpha(1)]$
+		\item if $0 < x_1(t) < x_2(t)$ then $\alpha(x_1(t)) \le \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon > 0$ arbitrarily small
+		\item if $t, t^\prime$ tolls such that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0$ then
+			\begin{itemize}
+				\item $\as(t) \ge \as(t^\prime)$ iff $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1$
+				\item $\as(t) \le \as(t^\prime)$ iff $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \ge 1$
+			\end{itemize}
+		\item $\as(t) \rightarrow 0$ iff $|t_1 - t_2| \rightarrow \infty$
+		\item $\lim_{t_1 \rightarrow t_2^-} \as(t) = \alpha(x_1), \lim_{t_1 \rightarrow t_2^+} \as(t) = \alpha(x_2)$, where ($x_1, x_2)$ the optimal flow under no tolls
 	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	$ $ % Just to make a line break after "Proof".
+	\begin{enumerate}[(i)]
+		\item Obviously $\as(t) \ne 0$ since $\as(t) = 0 \Rightarrow l_1(x_1(t)) = l_2(x_2(t))$ which is impossible in a heterogeneous setup.
+		Then we only need to notice that $l_1(x_1(t)) < l_2(x_2(t)) \iff t_1 > t_2$ and we get $\as(t) > 0$ from definition.
+		\item Since $x_1(t), x_2(t) > 0$ then $\exists p_1, p_2 \in [0, 1]$ each on a different edge, for which we assume w.l.o.g. that $\alpha(p_1) \le \alpha(p_2)$.
+		It holds that $\alpha(p_1) \le \as(t) \le \alpha(p_2)$ so with $\alpha$ being non-decreasing it follows
+		\[\alpha(0) \le \alpha(p_1) \le \as(t) \le \alpha(p_2) \le \alpha(1) \Rightarrow \as(t) \in [\alpha(0), \alpha(1)]\]
+		\item We know that $x_1(t) < x_2(t)$ means that edge 1 has the lower split.
+		Therefore we have
+		\[\alpha(p) \le \as(t), \forall p \in [0, x_1(t)] \Rightarrow \alpha(x_1(t)) \le \as(t)\]
+		Likewise for edge 2 we have
+		\[\as(t) \le \alpha(p), \forall p \in (x_1(t), 1] \Rightarrow \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon \in (0, 1 - x_1(t))\]
+		\item The condition
+		\begin{equation}
+			\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0
+			\label{eq:split_property_cond_tolls_0}
+		\end{equation}
+		ensures that the two tolls provide splits with same edges in their respective lower and higher sections.
+		We show this for $t_1 > t_2$ and likewise it also holds for $t_1 < t_2$.
+		\[t_1 > t_2 \Leftrightarrow t_1 - t_2 > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_1^\prime - t_2^\prime > 0 \Leftrightarrow t_1^\prime > t_2^\prime\]
+		%Also note that this property extends to the latencies, giving us
+		%\begin{equation}
+		%	\frac{l_1(x_1(t)) - l_2(x_2(t))}{l_1(x_1^\prime(t)) - l_2(x_2^\prime(t))} > 0
+		%	\label{eq:split_property_cond_latencies_0}
+		%\end{equation}
+		Then moving on to the first case, we first see that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1 \Leftrightarrow |t_1 - t_2| \le |t_1^\prime - t_2^\prime|$ (opposite direction is ensured by $(\ref{eq:split_property_cond_tolls_0})$), i.e.
+the toll difference is increasing.
+		Assume w.l.o.g. that $x_1 < x_2$.
+
+		If $x_1(t) = 0$ then
+		\[\as(t) = \frac{l_2(1)}{t_2 - t_1}, \as(t^\prime) = \frac{l_2(1)}{t_2^\prime - t_1^\prime}\] 
+		so obviously $t_2 - t_1 \le t_2^\prime - t_1^\prime \Rightarrow \as(t) \ge \as(t^\prime)$.
+
+		If $x_1(t) > 0$ then we know [TODO: do we?] that the latency difference might also increase, with flow from the lower latency edge, if any, moving towards the slower one, i.e.
+$x_1(t) \ge x_1(t^\prime)$.
+		If no flow moves then we can easily show that $\as(t) \ge \as(t^\prime)$ similarly to the case with $x_1(t) = 0$.
+		Otherwise $x_1(t) > x_1(t^\prime) \Rightarrow \exists \epsilon > 0: x_1(t) = x_1(t^\prime) + \epsilon$.
+		%\[|t_1 - t_2| \le |t_1^\prime - t_2^\prime| \Leftrightarrow |l_1(x_1(t)) - l_2(x_2(t))| \le |l_1(x_1(t^\prime)) - l_2(x_2(t^\prime))|\]
+		%\begin{equation}
+		%	|l_1(x_1(t)) - l_2(x_2(t))| \le |l_1(x_1(t^\prime)) - l_2(x_2(t^\prime))| \LeftrightarrowArg{(\ref{eq:split_property_cond_latencies_0})} \frac{l_1(x_1(t)) - l_2(x_2(t))}{|l_1(x_1(t^\prime)) - l_2(x_2(t^\prime))|} \le 1
+		%	\label{eq:split_property_cond_latencies_1}
+		%\end{equation}
+		Finally, by carefully applying property (ii) we get
+		\[\as(t^\prime) \le \alpha(x_1(t^\prime) + \epsilon) = \alpha(x_1(t)) \le \as(t)\]
+
+		All steps can be followed backwards as well, therefore the opposite also holds.
+
+		For the second case, we see that the toll difference decreases, and following respectively the same arguments we can show that $\as(t) \le \as(t^\prime)$.
+		\item If $\alpha(0) > 0$ then...
+	\end{enumerate}
+\end{proof}
+
+\subsection{Example with no $\NE$}
 

### 2024-03-18 thesis/article.tex
Thesis: Refactors split properties to different lemmas

@@
 
+We start with some basic properties.
 \begin{lemma}
+	\label{lemma:split_basic}
 	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$, the following hold:
@@
 		\item if $0 < x_1(t) < x_2(t)$ then $\alpha(x_1(t)) \le \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon > 0$ arbitrarily small
-		\item if $t, t^\prime$ tolls such that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0$ then
-			\begin{itemize}
-				\item $\as(t) \ge \as(t^\prime)$ iff $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1$
-				\item $\as(t) \le \as(t^\prime)$ iff $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \ge 1$
-			\end{itemize}
-		\item $\as(t) \rightarrow 0$ iff $|t_1 - t_2| \rightarrow \infty$
-		\item $\lim_{t_1 \rightarrow t_2^-} \as(t) = \alpha(x_1), \lim_{t_1 \rightarrow t_2^+} \as(t) = \alpha(x_2)$, where ($x_1, x_2)$ the optimal flow under no tolls
 	\end{enumerate}
@@
 		\[\as(t) \le \alpha(p), \forall p \in (x_1(t), 1] \Rightarrow \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon \in (0, 1 - x_1(t))\]
-		\item The condition
+	\end{enumerate}
+\end{proof}
+
+The next lemma will help us describe how $\as(t)$ is changing in relation to toll difference (and in extend to latency difference).
+\begin{lemma}
+	Given a 2-link parallel heterogeneous game with time-money sensitivity split function $\as$ and tolls $t, t^\prime$ such that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0$, the following hold:
+	\begin{enumerate}[(i)]
+		\item $\as(t) \ge \as(t^\prime)$ iff $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1$
+		\item $\as(t) \le \as(t^\prime)$ iff $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \ge 1$
+	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	Before we get into the propositions, notice that the condition
 	\begin{equation}
@@
 	%\end{equation}
-		Then moving on to the first case, we first see that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1 \Leftrightarrow |t_1 - t_2| \le |t_1^\prime - t_2^\prime|$ (opposite direction is ensured by $(\ref{eq:split_property_cond_tolls_0})$), i.e.
+	Now moving on to the prepositions, we focus on proving $(i)$ in the right-to-left direction; then the same steps can be followed backwards to prove left-to-right.
+	Finally proving $(ii)$ will be much easier as there are many steps symmetric to the ones for $(i)$.
+
+	\paragraph{$(i)$}
+	Begin by noticing that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1 \Leftrightarrow |t_1 - t_2| \le |t_1^\prime - t_2^\prime|$ (opposite direction is ensured by $(\ref{eq:split_property_cond_tolls_0})$), i.e.
 the toll difference is increasing.
@@
 $x_1(t) \ge x_1(t^\prime)$.
-		If no flow moves then we can easily show that $\as(t) \ge \as(t^\prime)$ similarly to the case with $x_1(t) = 0$.
-		Otherwise $x_1(t) > x_1(t^\prime) \Rightarrow \exists \epsilon > 0: x_1(t) = x_1(t^\prime) + \epsilon$.
 	%\[|t_1 - t_2| \le |t_1^\prime - t_2^\prime| \Leftrightarrow |l_1(x_1(t)) - l_2(x_2(t))| \le |l_1(x_1(t^\prime)) - l_2(x_2(t^\prime))|\]
@@
 	%\end{equation}
-		Finally, by carefully applying property (ii) we get
+	If no flow moves then we can easily show that $\as(t) \ge \as(t^\prime)$ similarly to the case with $x_1(t) = 0$.
+	Otherwise we have $x_1(t) > x_1(t^\prime) \Rightarrow \exists \epsilon > 0: x_1(t) = x_1(t^\prime) + \epsilon$ and by carefully applying property $\ref{lemma:split_basic}(ii)$ we get
 	\[\as(t^\prime) \le \alpha(x_1(t^\prime) + \epsilon) = \alpha(x_1(t)) \le \as(t)\]
 
-		All steps can be followed backwards as well, therefore the opposite also holds.
+	\paragraph{$(ii)$}
+	Symmetrically to $(i)$ in this case the toll difference is decreasing, and therefore flow from the higher latency edge will move towards the lower one, i.e.
+$x_1(t) \le x_1(t^\prime)$ (assuming again $x_1 < x_2$).
+	With a similar argument we then get $\as(t) \le \as(t^\prime)$.
+\end{proof}
 
-		For the second case, we see that the toll difference decreases, and following respectively the same arguments we can show that $\as(t) \le \as(t^\prime)$.
+The next lemma gives us some insight of the behavior of $\as(t)$ around its edge values.
+\begin{lemma}
+	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$, the following hold:
+	\begin{enumerate}[(i)]
+		\item $\as(t) \rightarrow 0$ iff $|t_1 - t_2| \rightarrow \infty$
+		\item $\lim_{t_1 \rightarrow t_2^-} \as(t) = \alpha(x_1), \lim_{t_1 \rightarrow t_2^+} \as(t) = \alpha(x_2)$, where ($x_1, x_2)$ the optimal flow under no tolls
+	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	\begin{enumerate}[(i)]
 		\item If $\alpha(0) > 0$ then...
+		\item 
 	\end{enumerate}

### 2024-03-18 thesis/article.tex
Thesis: Adds spit lemma that describes split bounds

@@
 	\begin{enumerate}[(i)]
-		\item $\as(t) \rightarrow 0$ iff $|t_1 - t_2| \rightarrow \infty$
-		\item $\lim_{t_1 \rightarrow t_2^-} \as(t) = \alpha(x_1), \lim_{t_1 \rightarrow t_2^+} \as(t) = \alpha(x_2)$, where ($x_1, x_2)$ the optimal flow under no tolls
+		\item if $\alpha(0) > 0$ then $\as(t) < \alpha(0) \Rightarrow x(t) = (0, 1)$ or $(1, 0)$
+		\item if $\alpha(0) = 0$ with $0$ an accumulation point, then $x_1(t), x_2(t) > 0, \forall t \in \mathbb{R}_+^2$
+		\item $\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = 0$
+		\item $\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_1), \lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_2)$, where ($x_1, x_2)$ the optimal flow under no tolls
 	\end{enumerate}
@@
 \begin{proof}
+	$ $
 	\begin{enumerate}[(i)]
-		\item If $\alpha(0) > 0$ then...
-		\item 
+		\item Direct consequence from the fact that all players $p$ with $\as(t) < \alpha(p)$ are in the low latency edge.
+		\item Since $\alpha(0) = 0$ and $0$ an accumulation point, then $\forall \delta > 0 \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
+		Therefore $\forall t \in \mathbb{R}_+^2$ if $\delta = \as(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as(t)$, which means that the lower latency edge will always have flow some $\epsilon > 0$, and therefore $x_1(t), x_2(t) > 0$.
+		\item We only need to notice that $|l_1(x_1(t)) - l_2(x_2(t))| \le \max\{l_1(1), l_2(1)\} = L$ and we find
+		\[\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = \lim_{|t_1 - t_2| \rightarrow +\infty}\frac{|l_1(x_1(t)) - l_2(x_2(t))|}{|t_1 - t_2|} \le \lim_{|t_1 - t_2| \rightarrow +\infty}\frac{L}{|t_1 - t_2|} = 0\]
+		and since $\as(t) > 0$ we get $\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = 0$.
+		\item As $|t_1 - t_2| \rightarrow 0$ then also $|l_1(x_1(t)) - l_2(x_2(t))| \rightarrow 0$ as the game approaches the homogeneous case.
+		Then flow on the low latency edge will define the limit of $\as(t)$.
+			\begin{itemize}
+				\item For $t_1 > t_2$ we get lower latency edge $1$ with flow $x_1(t) \rightarrow x_1$ and therefore
+				\[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_1)\]
+				\item For $t_1 < t_2$ we get lower latency edge $2$ with flow $x_2(t) \rightarrow x_2$ and therefore
+				\[\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_2)\]
+			\end{itemize}
 	\end{enumerate}

### 2024-03-20 thesis/games/ParallelGame.py
Thesis: Adds TwoLinkParallelGame class that computes best responses (homogeneous), with tests

@@ -1,0 +1,72 @@
+from sympy import symbols, solve, simplify
+
+
+class TwoLinkParallelGame:
+    """A class for the 2-link network parallel game."""
+
+    def __init__(self, affine_latencies):
+        """Initiates the game class.
+
+        Args:
+            affine_latencies (list): A list of the latency functions' factors.
+        """
+        self.x1 = symbols('x1')
+        self.x2 = 1 - self.x1
+
+        [[a1, b1], [a2, b2]] = affine_latencies
+        self.l1 = a1 * self.x1 + b1
+        self.l2 = a2 * self.x2 + b2
+
+        self.t1, self.t2 = symbols('t1 t2')
+        self.c1 = self.l1 + self.t1
+        self.c2 = self.l2 + self.t2
+
+        self.br1 = None
+        self.br2 = None
+
+    def calculate_equilibrium(self):
+        """Calculate the optimal flow x w.r.t. tolls (t1, t2) at which there is an equilibrium.
+            # Optimal flow occurs when the two links have the same cost.
+            # Use the expression c1 == c2, solve for x1 and store the resulting expression.
+        """
+        solution = solve(self.c1 - self.c2, self.x1)
+        if len(solution) == 1:
+            self.x1 = solution[0]
+            self.x2 = simplify(1 - self.x1)
+
+    def calculate_best_responses(self):
+        """Calculate the best responses for each player."""
+        # Step 1: Calculate the optimal flow x at which there is an equilibrium.
+        self.calculate_equilibrium()
+
+        # Step 2: Calculate the argmax for each profit function (differentiate, find root and solve for t).
+        p1 = self.x1 * self.t1
+        p2 = self.x2 * self.t2
+        br1_1 = solve(p1.diff(self.t1), self.t1)
+        br2_1 = solve(p2.diff(self.t2), self.t2)
+        if len(br1_1) != 1 or len(br2_1) != 1:
+            return
+        br1_1, br2_1 = br1_1[0], br2_1[0]
+
+        # Step 3: Calculate the limit of the above argmax,
+        # i.e. the argmax results in the player controlling all the flow.
+        br1_1_cond = solve(self.x1.subs(self.t1, br1_1) - 1, self.t2)
+        br2_1_cond = solve(self.x2.subs(self.t2, br2_1) - 1, self.t1)
[…]

### 2024-03-20 thesis/games/tests/TestParallelGame.py

@@ -1,0 +1,30 @@
+import unittest
+from sympy import symbols
+from games.ParallelGame import TwoLinkParallelGame
+
+
+class TestTwoLinkParallelGame(unittest.TestCase):
+    def test_calculate_equilibrium(self):
+        a = symbols('a')
+        game = TwoLinkParallelGame([[1, 0], [a, 0]])
+        x1 = (game.t2 - game.t1 + a) / (a + 1)
+        x2 = (game.t1 - game.t2 + 1) / (a + 1)
+        game.calculate_equilibrium()
+        self.assertEqual(x1, game.x1)
+        self.assertEqual(x2, game.x2)
+
+    def test_calculate_best_responses(self):
+        a = symbols('a')
+        game = TwoLinkParallelGame([[1, 0], [a, 0]])
+        br1 = [
+            {'cond': game.t2 < a + 2, 'func': (game.t2 + a) / 2},
+            {'cond': game.t2 >= a + 2, 'func': game.t2 - 1}
+        ]
+        br2 = [
+            {'cond': game.t1 < 2 * a + 1, 'func': (game.t1 + 1) / 2},
+            {'cond': game.t1 >= 2 * a + 1, 'func': game.t1 - a}
+        ]
+
+        game.calculate_best_responses()
+        self.assertEqual(game.br1, br1)
+        self.assertEqual(game.br2, br2)

### 2024-03-21 thesis/article.tex
Thesis: Adds section with bad examples (a(eps)=0, 0 a.p.)

@@
 
-% \usepackage{mathtools}
 % \usepackage{tikz}
@@
 \usepackage{amsthm}
+\usepackage{mathtools}
 
@@
 \newcommand{\as}{\mathrm{\alpha_s}}
+\newcommand{\R}{\mathbb{R}}
+\DeclareMathOperator*{\argmax}{arg\,max}
 % \newcommand{\Exp}{\mathrm{Exp}}
@@
 \newtheorem{lemma}{Lemma}[section]
+\newtheorem{example}{Example}[section]
 
@@
 \begin{definition}
-	Given a 2-link parallel heterogeneous game with latency functions $l_1, l_2$, we define the time-money sensitivity split function $\as: \mathbb{R}^2_+ \rightarrow (0, +\infty)$ where for given tolls $t = (t_1, t_2)$
+	Given a 2-link parallel heterogeneous game with latency functions $l_1, l_2$, we define the time-money sensitivity split function $\as: \R^2_+ \rightarrow (0, +\infty)$ where for given tolls $t = (t_1, t_2)$
 	\[\as(t) = \frac{l_2(x_2(t)) - l_1(x_1(t))}{t_1 - t_2}\]
@@
 \begin{lemma}
+	\label{lemma:split_bounds}
 	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$, the following hold:
@@
 		\item if $\alpha(0) > 0$ then $\as(t) < \alpha(0) \Rightarrow x(t) = (0, 1)$ or $(1, 0)$
-		\item if $\alpha(0) = 0$ with $0$ an accumulation point, then $x_1(t), x_2(t) > 0, \forall t \in \mathbb{R}_+^2$
+		\item if $\alpha(0) = 0$ with $0$ an accumulation point, then $x_1(t), x_2(t) > 0, \forall t \in \R_+^2$
 		\item $\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = 0$
@@
 		\item Since $\alpha(0) = 0$ and $0$ an accumulation point, then $\forall \delta > 0 \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
-		Therefore $\forall t \in \mathbb{R}_+^2$ if $\delta = \as(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as(t)$, which means that the lower latency edge will always have flow some $\epsilon > 0$, and therefore $x_1(t), x_2(t) > 0$.
+		Therefore $\forall t \in \R_+^2$ if $\delta = \as(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as(t)$, which means that the lower latency edge will always have flow some $\epsilon > 0$, and therefore $x_1(t), x_2(t) > 0$.
 		\item We only need to notice that $|l_1(x_1(t)) - l_2(x_2(t))| \le \max\{l_1(1), l_2(1)\} = L$ and we find
@@
 
-\subsection{Example with no $\NE$}
+\subsection{Profit maximisation and distribution function}
+
+In this section we will examine how different distribution functions $\alpha$ can affect the profit maximisation game between the toll owners.
+[TODO: add framework for examining games]
+We will restrict our analysis on distribution functions such that $\alpha(0) > 0$, the reason being that we want to avoid two instances.
+The first is to ensure that $\alpha(p) > 0$ when $p > 0$, while the second is that $0$ is not an accumulation point.
+[TODO: maybe mention add ref who also take the first restriction as it creates games with no optimal tolls]
+The following two examples demonstrate the issues that might occur if these restrictions are not met.
+
+\begin{example}
+	Consider a $2$-link parallel network pricing game with distribution function $\alpha$ for which it does not hold that $\alpha(p) > 0$ when $p > 0$.
+\end{example}
+
+The property not holding for $\alpha$ means that $\exists x_\epsilon > 0 : \alpha(x_\epsilon) = 0 \forall p < x_\epsilon$.
+That $x_\epsilon$ flow will completely neglect the tolls and play the congestion game only considering the flow latency, therefore they will always select the fastest edge regardless of the toll price.
+This in turn means that any toll owner can exploit it and set their toll to an arbitrary high value $T$ which will force all players with $\alpha(p) > 0$ to leave, thus making their own edge the fastest one.
+Even if the edge has a latency function with a high increasing rate, there will be at least a small flow $x_{\epsilon^\prime} \le x_\epsilon$ on that edge.
+Therefore the owner can achieve any arbitrary profit $P$ by setting their toll price as $T + P/\epsilon$.
+Since both player have that strategy available, we conclude that no equilibrium exists in the pricing game.
+
+\begin{example}
+	\label{example:a_0_ap}
+	Consider a $2$-link parallel network pricing game with $l_1(x) = x, l_2(x) = 2x$ and distribution function $\alpha(p) = p$.
+\end{example}
+
+Notice that the condition $\alpha(p) > 0$ when $p > 0$ holds for this example.
+However in this case $0$ is an accumulation point, and by Lemma $\ref{lemma:split_bounds}(ii)$ it follows $x_1(t), x_2(t) > 0, \forall t \in \R_+^2$.
+Then Lemma $\ref{lemma:split_basic}$ entails that, assuming $t_1 > t_2$, $\alpha(x_1(t)) \le \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon > 0$ arbitrarily small, and since in this example $\alpha$ is onto, then $\as(t) = \alpha(x_1(t))$.
+
+We will calculate $B_i(t_{-i})$ by calculating $x_i(t)$ and then finding $\argmax \Pi_i(t)$.
+Note that since we always have $x_1(t), x_2(t) > 0$ we don't need to take cases where the flow is on one edge.
+For tolls $t = (t_1, t_2)$ and respective optimal flow $x = (x_1(t), x_2(t))$ we take the following cases.
+
+\paragraph{If $t_1 > t_2$}
+then $x_1$ is the low-latency flow and thus $\as(t) = \alpha(x_1(t)) = x_1(t)$.
+We therefore get
+\begin{align}
+	l_1(x_1(t)) + \as(t) t_1 &= l_2(x_2(t)) + \as(t) t_2 &\Rightarrow \notag \\
+	x_1(t) + x_1(t) t_1 &= 2 (1 - x_1(t)) + x_1(t) t_2 &\Rightarrow \notag \\
+	x_1(t) &= \frac{2}{3 + t_1 - t_2} \label{eq:ex2_x1_1}
+\end{align}
+\[
+	B_1^>(t_2) = \argmax_{t_2 < t_1} x_1(t) t_1 \indeq{(\ref{eq:ex2_x1_1})} \argmax_{t_2 < t_1} \frac{2 t_1}{3 + t_1 - t_2} = \argmax_{t_2 < t_1} \frac{2}{1 + \frac{3 - t_2}{t_1}} =
+		\begin{cases}
+			+\infty, & t_2 < 3 \\
+			\textrm{undefined}, & t_2 = 3 \\
+			t_2, & t_2 > 3 \\
+		\end{cases}
+\]
+We can already see some of the problems that appear.
+If $t_2 = 3$ then $x_1(t_1, 3) = 2/t_1$ and thus $\Pi_1(t_1, 3) = 2 \; \forall t_1 > 3$ resulting in $B_1^>(3)$ being undefinable.
+Then for $t_2 < 3$ if we set $c = 3 - t_2 > 0$ we have $\Pi_1(t) = \frac{2}{1 + c/t_1}$ so as $t_1 \rightarrow +\infty$ we get that $\Pi_1(t)$ is increasing and $\Pi_1(t) \rightarrow 2$, making no $t_1 > t_2$ a best candidate.
+Finally, if $t_2 > 3$ then $\Pi_1(t) = \frac{2}{1 - c/t_1}$ making $\Pi_1$ decrease as $t_1$ increases, and in turn making $t_2$ the best response with profit $\Pi_1(t) = {2 t_2}/3$.
+
+Continuing for $B_2^>(t_1)$ where $x_2(t) = 1 - x_1(t) = \frac{1 + t_1 - t_2}{3 + t_1 - t_2}$, we calculate $\argmax_{t_2 < t_1} \Pi_2(t)$ by taking first order conditions and we get
+\[\argmax_{t_2 < t_1} \Pi_2(t) = t_1 + 3 - \sqrt{2 t_1 + 6}\]
+This value is within bounds when $t_1 + 3 - \sqrt{2 t_1 + 6} < t_1 \Rightarrow t_1 > 3/2$.
+For $t_1 \le 3/2$ we have $\Pi_2(t)$ non-decreasing in $[0, t_1]$ achieving maximum at $t_2 = t_1$.
+Therefore
+\[
+	B_2^>(t_1) =
+		\begin{cases}
+			t_1, & t_1 \le 3/2 \\
+			t_1 + 3 - \sqrt{2 t_1 + 6}, & t_1 > 3/2
+		\end{cases}
+\]
+with profit $\Pi_2(t) = t_1/3$ and $t_1 + 5 - 2 \sqrt{2 t_1 + 6}$ respectively.
+
+\paragraph{If $t_1 < t_2$}
+we follow a similar analysis and find the following
+\begin{equation*}
+	\begin{aligned}
+		B_1^<(t_2) =
+			\begin{cases}
+				t_2, & t_2 \le 6 \\
+				t_2 + 3 - \sqrt{t_2 + 3}, & t_1 > 6
+			\end{cases}
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		B_2^<(t_1) =
+			\begin{cases}
+				+\infty, & t_1 < 3 \\
+				\textrm{undefined}, & t_1 = 3 \\
+				t_1, & t_1 > 3 \\
+			\end{cases}
+	\end{aligned}
+\end{equation*}
+with profits $\Pi_1(t) = {2 t_2}/3, t_2 + 4 - 2 \sqrt{t_2 + 3}$ and $\Pi_2(t) = 1 - \epsilon, 1, t_1/3$.
+
+\paragraph{Combining} $B_1^>(t_2), B_1^<(t_2)$ and $B_2^>(t_1), B_2^<(t_1)$ by comparing at each interval the profits between the strategies $t_1 > t_2$ and $t_1 < t_2$ (i.e.
+comparing profits when playing a toll either higher or lower from the other toll owner), we get the final best response functions
+\begin{equation*}
+	\begin{aligned}
+		B_1(t_2) =
+			\begin{cases}
+				+\infty, & t_2 < 3 \\
+				\textrm{undefined}, & t_2 = 3 \\
+				t_2, & 3 < t_2 < 6 \\
+				t2 + 3 - \sqrt{t_2 + 3} & t_2 \ge 6
+			\end{cases}
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		B_2(t_1) =
+			\begin{cases}
+				+\infty, & t_1 < 2 \sqrt{2} \\
+				t_1 + 3 - \sqrt{2 t_1 + 6}, & t_1 \ge 2 \sqrt{2}
+			\end{cases}
+	\end{aligned}
+\end{equation*}
+Both toll owners have one thing in common, above a specific threshold $(t_2 > 3, t_1 > 2 \sqrt{2})$ they always play either the same or a lower toll than the other toll owner.
+Below that threshold, which will eventually occur from any starting point, they both get divergent best responses and thus a $\NE$ cannot be defined.
+
+\paragraph{The bad behaviors} are obviously having divergent or undefined best response functions, which we claim occur only when we allow $0$ to be an accumulation point in $\alpha$, since this allows players with arbitrarily low money-sensitivity to always stay on the expensive edge.
+Assume that in Example $\ref{example:a_0_ap}$ we use $\alpha(p) = p + 1$ as a distribution function.
+Then we get best response functions
 

### 2024-04-04 thesis/article.tex
Thesis: Adds more bad examples
Finishes the one with a(0)=0 with well-behaved case (a(0) > 0) and adds bad example with a discrete

@@
 				t_2, & 3 < t_2 < 6 \\
-				t2 + 3 - \sqrt{t_2 + 3} & t_2 \ge 6
+				t_2 + 3 - \sqrt{t_2 + 3} & t_2 \ge 6
 			\end{cases}
@@
 Assume that in Example $\ref{example:a_0_ap}$ we use $\alpha(p) = p + 1$ as a distribution function.
-Then we get best response functions
+Then we get the following best response functions
+\begin{align*}
+	B_1(t_2) &=
+	\begin{cases}
+		\sqrt{5 (3 - t_2)} - (3 - t_2), & t_2 < 6/5 \\
+		t_2, & 6/5 \le t_2 \le 3/2 \\
+		t_2 + 3 - \sqrt{2 t_2 + 6}, & 3/2 < t_2 < 5 \\
+		t_2 - 1 & t_2 \ge 5
+	\end{cases}\\
+	B_2(t_1) &=
+	\begin{cases}
+		2 \sqrt{3 - t_1} - (3 - t_1), & t_1 \le \frac29 \sqrt{22 - 4 \sqrt{10}} \\
+		t_1 + 3 - \frac{\sqrt{10}}2 \sqrt{t_1 + 3}, & \frac29 \sqrt{22 - 4 \sqrt{10}} < t_1 < 7 \\
+		t_1 - 2, & t_1 \ge 7
+	\end{cases}
+\end{align*}
+which can be shown [TODO: currently done experimentally in python] that has a $\NE$ at $t \approx (1.1464, 0.9268)$.
+
+\begin{example}
+	Consider a $2$-link parallel network pricing game with $l_1(x) = x, l_2(x) = 2x$ and distribution function
+	\[
+		\alpha(p) =
+		\begin{cases}
+			1, & p \le 1/2 \\
+			5, & p > 1/2
+		\end{cases}
+	\]
+\end{example}
+
+First we calculate the edge cases [TODO: add relevant section in preliminaries].
+If all flow is in edge $1$ then $t_2 - t_1 = \alpha(0) l_1(1) = 1$, while if all flow is in edge $2$ then $t_1 - t_2 = \alpha(0) l_2(1) = 2$ therefore
+\[t_2 - t_1 \le 1 \qquad t_1 - t_2 \le 2\]
+
+\paragraph{If $t_1 < t_2$} then $x_2(t)$ is the low-latency flow with $x_2(t) < 1/3$ as without tolls we have Wardrop equilibrium at $x = (2/3, 1/3)$.
+As such we get $\as(t) = 1$ and therefore
+\[
+	l_1(x_1(t)) + \as(t) t_1 = l_2(x_2(t)) + \as(t) t_2 \Rightarrow	x_1(t) + t_1 = 2 (1 - x_1(t)) + t_2 \Rightarrow
+\]
+\begin{equation*}
+	\begin{aligned}
+		x_1(t) = \frac{2 + (t_2 - t_1)}3
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		x_2(t) = \frac{1 - (t_2 - t_1)}3
+	\end{aligned}
+\end{equation*}
+Using first order conditions we find
+\begin{equation*}
+	\begin{aligned}
+		\argmax_{t_1 < t_2}\Pi_1(t_2) = \frac{t_2 + 2}2
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		\argmax_{t_1 < t_2}\Pi_2(t_1) = \frac{t_1 + 1}2
+	\end{aligned}
+\end{equation*}
+and by also applying the edge case restrictions we get
+\begin{equation*}
+	\begin{aligned}
+		B_1^<(t_2) =
+		\begin{cases}
+			t_2, & t_2 \le 2 \\
+			\frac{t_2 + 2}2, & 2 < t_2 < 4 \\
+			t_2 - 1, & t_2 \ge 4
+		\end{cases}
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		B_2^<(t_1) =
+		\begin{cases}
+			\frac{t_1 + 1}2, & t_1 < 1 \\
+			t_1, & t_1 \ge 1
+		\end{cases}
+	\end{aligned}
+\end{equation*}
+with profits
+\begin{equation*}
+	\begin{aligned}
+		\Pi_1^<(t_2) =
+		\begin{cases}
+			\frac23 t_2, & t_2 \le 2 \\
+			\frac{(t_2 + 2)^2}{12}, & 2 < t_2 < 4 \\
+			t_2 - 1, & t_2 \ge 4
+		\end{cases}
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		\Pi_2^<(t_1) =
+		\begin{cases}
+			\frac{(t_1 + 1)^2}{12}, & t_1 < 1 \\
+			\frac13 t_1, & t_1 \ge 1
+		\end{cases}
+	\end{aligned}
+\end{equation*}
+
+\paragraph{If $t_1 > t_2$} then $x_1(t)$ is the low-latency flow so we need to take cases depending on its value.
+We will show analytically the process for toll owner $1$.
+
+\subparagraph{If $x_1 < 1/2$} then $\as(t) = 1$ so we get $x_1(t), x_2(t)$ and best responses as before.
+Also
+\[x_1(t) < \frac12 \Rightarrow \frac{2 - (t_1 - t_2)}{3} < \frac12 \Rightarrow t_1 - t_2 > \frac12\]
+so for toll owner $1$ with $B_1^>(t_2) = \frac{t_2 + 2}2$ we have
+\[t_1 - t_2 > \frac12 \Rightarrow \frac{t_2 + 2}2 - t_2 > \frac12 \Rightarrow t_2 < 1\]
+\[t_1 > t_2 \Rightarrow \frac{t_2 + 2}2 > t_2 \Rightarrow t_2 < 2\]
+
+\subparagraph{If $x_1 > 1/2$} then $\as(t) = 5$ so we calculate $x_1(t)$ and its $\argmax$ using first order conditions.
+\[
+	l_1(x_1(t)) + \as(t) t_1 = l_2(x_2(t)) + \as(t) t_2 \Rightarrow	x_1(t) + 5 t_1 = 2 (1 - x_1(t)) + 5 t_2 \Rightarrow
+\]
+\begin{equation*}
+	\begin{aligned}
+		x_1(t) = \frac{2 + 5 (t_2 - t_1)}3
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		\argmax_{t_1 > t_2}\Pi_1(t_2) = \frac{5 t_2 + 2}{10}
+	\end{aligned}
+\end{equation*}
+Also
+\[x_1(t) > \frac12 \Rightarrow \frac{2 - 5 (t_1 - t_2)}{3} > \frac12 \Rightarrow t_1 - t_2 < \frac1{10}\]
+so for toll owner $1$ we have
+\[t_1 - t_2 < \frac1{10} \Rightarrow \frac{5 t_2 + 2}{10} - t_2 < \frac1{10} \Rightarrow t_2 > \frac15\]
+\[t_1 > t_2 \Rightarrow \frac{5 t_2 + 2}{10} > t_2 \Rightarrow t_2 < \frac25\]
+
+\subparagraph{If $x_1 = 1/2$} then $\as(t) \in [1, 5]$ and using the definition we get
+\[\as(t) = \frac{l_2(1/2) - l_1(1/2)}{t_1 - t_2} = \frac1{2 (t_1 - t_2)}\]
+and in order to get the range of $t_1 - t_2$ where this applies we check
+\[1 \le \as(t) \le 5 \Rightarrow 1 \le \frac1{2 (t_1 - t_2)} \le 5 \Rightarrow \frac12 \ge t_1 - t_2 \ge \frac1{10}\]
+
+The flow is always the same so the best response for toll owner $1$ is to maximize $t_1 - t_2$ so we get $t_1 - t_2 = 1/2 \Rightarrow t_1 = t_2 + 1/2$.
+
+\subparagraph{Gathering all the above} we see that the player has the option to play $t_1$ with the case that provides the maximum profit, so we calculate them.
+\[
+	\Pi_1^>(t_2) =
+	\begin{cases}
+		\frac{(5 t_2 + 2)^2}{60}, & t_1 - t_2 < \frac1{10} \\
+		\frac{2 t_2 + 1}4, & t_1 - t_2 \in \left[\frac1{10}, \frac12\right] \\
+		\frac{(t_2 + 2)^2}{12}, & t_1 - t_2 > \frac12
+	\end{cases}
+\]
+and by solving the inequalities (in each respective bound) we finally get
+\begin{equation*}
+	\begin{aligned}
+		B_1^>(t_2) =
+		\begin{cases}
+			\frac{t_2 + 2}{12}, & t_2 < 1 \\
+			t_2 + \frac12, & t_2 \ge 1
+		\end{cases}
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		\Pi_1^>(t_2) =
+		\begin{cases}
+			\frac{(t_2 + 2)^2}{12}, & t_2 < 1 \\
+			\frac{2 t_2 + 1}4, & t_2 \ge 1
+		\end{cases}
+	\end{aligned}
+\end{equation*}
+
+In a similar way we calculate $B_2^>(t_1)$ and $\Pi_2^>(t_1)$, with only some extra care on the bounds as since $t_2 < t_1$ then not all options are always available (e.g.
+if $t_1 < 1/10$ then only $t_1 - t_2 < 1/10$ can be picked).
+Finally we get
+
+\begin{equation*}
+	\begin{aligned}
+		B_2^>(t_1) =
+		\begin{cases}
+			t_1, & t_1 < \frac15 \\
+			\frac{5 t_1 + 1}{10}, & \frac15 \le t_1 \le \frac25 \\
+			t_1 - \frac1{10}, & \frac25 < t_1 < \frac{10 + 2 \sqrt{15}}5 \\
+			\frac{t_1 + 1}2, & \frac{10 + 2 \sqrt{15}}5 \le t_1 \le 5 \\
+			t_1 - 2, & t_2 > 5
+		\end{cases}
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		\Pi_2^>(t_1) =
+		\begin{cases}
+			\frac13 t_1, & t_1 < \frac15 \\
+			\frac{(5 t_1 + 1)^2}{12}, & \frac15 \le t_1 \le \frac25 \\
+			\frac{10 t_1 - 1}{20}, & \frac25 < t_1 < \frac{10 + 2 \sqrt{15}}5 \\
+			\frac{(t_1 + 1)^2}{12}, & \frac{10 + 2 \sqrt{15}}5 \le t_1 \le 5 \\
+			t_1 - 2, & t_2 > 5
+		\end{cases}
+	\end{aligned}
+\end{equation*}
+
+\subparagraph{Combining} $B_1^>(t_2), B_1^<(t_2)$ and $B_2^>(t_1), B_2^<(t_1)$ the same way as in Example $\ref{example:a_0_ap}$ we get the final best response functions.
+\begin{equation*}
+	\begin{aligned}
+		B_1(t_2) =
+		\begin{cases}
+			\frac{t_2 + 2}2, & t_2 \le 1 \\
+			t_2 + \frac12, & 1 < t_2 < \frac32 \\
+			t_2, & \frac32 \le t_2 \le 2 \\
+			\frac{t_2 + 2}2, & 2 < t_2 < 4 \\
+			t_2 - 1, & t_2 \ge 4
+		\end{cases}
+	\end{aligned}
+	\qquad
+	\begin{aligned}
+		B_2(t_2) =
+		\begin{cases}
+			\frac{t_1 + 1}2, & t_1 \le \frac15 \\
+			\frac{5 t_1 + 1}{10}, & \frac15 < t_1 < frac25 \\
+			t_1 - \frac1{10}, & \frac25 \le t_1 \le \frac{10 + 2 \sqrt{15}}5 \\
+			\frac{t_1 + 1}2, & \frac{10 + 2 \sqrt{15}}5 < t_1 < 5 \\
+			t_1 - 2, & t_1 \ge 5
+		\end{cases}
+	\end{aligned}
+\end{equation*}
+
+For the above functions we can show [TODO: currently done experimentally in python] that there is NO $\NE$ for the pricing game.
+
+\subsection{Equilibrium}
+
+In this section we will show that if the distribution function has the following properties
+\begin{itemize}
+	\item $\alpha(0) > 0$
+	\item $\alpha$ is onto
+\end{itemize}
+Then a $\NE$ for the pricing game exists ???
 

### 2024-04-04 thesis/article.tex
Thesis: Adds corollary about max a_s and why higher a values are irrelevant

@@
 \newtheorem{example}{Example}[section]
+\newtheorem{corollary}{Corollary}[section]
 
@@
 \end{proof}
+
+From the above lemma we can also observe the following
+
+\begin{corollary}
+	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$ and $x = (x_1, x_2)$ the optimal flow in the game without tolls, then $\as(t) \le \max\{\alpha(x_1), \alpha(x_2)\}$.
+\end{corollary}
+
+This corollary hints that all values of $\alpha$ above $\max\{x_1, x_2\}$ are irrelevant to the game.
+This will become more obvious later when calculating best responses as those values will never be used.
+[TODO: Maybe put this in its own Lemma and prove it?]
 

### 2024-08-25 thesis/article.tex
Thesis: Corrections in split function Lemmas
Corrections noted by Th. Lianeas in the 10/4/24 meeting
Thesis: Integrates ALMA LaTeX thesis template

@@
-\documentclass[a4paper,11pt]{article}
-\usepackage{a4wide}
+%Typeset using XeLaTeX
 
-% Greek fonts
-\RequirePackage{fontspec}
-\defaultfontfeatures{Ligatures=TeX}
-  % you may want to try: {Liberation Serif} or {Times New Roman}
-\setmainfont{FreeSerif}
-  % you may want to try: {Liberation Sans} or {Arial}
-\setsansfont[Scale=MatchLowercase]{FreeSans}
-  % you may want to try: {FreeMono} or {Courier New}
-\setmonofont[Scale=MatchLowercase]{FreeMono}
+\documentclass[10pt,a4paper]{book}
+\usepackage{mathtools,amssymb,amsthm}
+%\usepackage{phonetic}
+\usepackage{fancyhdr}
+\usepackage[pass]{geometry}
+\usepackage{fontspec}
+%\usepackage{xunicode}
+%\usepackage{xltxtra}
+%\usepackage{xgreek}
+\setmainfont[Mapping=TeX-text]{Times New Roman}
+\usepackage{hyperref}
+%\usepackage{color}
+\usepackage[Glenn]{fncychap}
+\ChNameVar{\bfseries\Large}
+%\usepackage{tabularx}
+%\usepackage[normalem]{ulem}
 
-% \usepackage{tikz}
+%\usepackage{tikz}
 \usepackage{enumerate}
-\usepackage{amssymb}
-\usepackage{amsthm}
-\usepackage{mathtools}
+
+\renewcommand{\maketitle}{
+	\begin{titlepage}
+		\newgeometry{left=4cm, top=2.3cm, bottom=2.3cm}
+		\hbox{\mbox{\hspace{-1.3cm}}
+			\vrule depth 0.98\textheight
+			\mbox{\hspace{1cm}}
+			\vtop{
+				\vspace{2cm}
+				\begin{flushleft}
+					\huge{\bf Profit Optimisation in Heterogeneous 2-link Parallel Games\\}
+					\vskip3cm
+					\Large  Thomas Pappas\\
+					AL1.18.0011\\
+					\vskip3cm
+					\begin{minipage}{7.5cm}
+						\begin{flushleft}
+							\normalsize {\it {\bf Examination committee:}\\
+								Dimitris Fotakis, School of Electrical and Computer Engineering, National Technical University of Athens.\\
+								Professor's name, Department or School, Institution.\\
+								Professor's name, Department or School, Institution.}
+						\end{flushleft}
+					\end{minipage}
+					\hskip0.5cm
+					\begin{minipage}{6cm}
+						\begin{flushleft}
+							\normalsize {\it {\bf Supervisor:}\\
+								Dimitris Fotakis, Professor, \\ School of Electrical and Computer Engineering,\\
+								National Technical University of Athens.\\
+							}
+						\end{flushleft}
+					\end{minipage}
+				\end{flushleft}
+				\vskip6cm
+				\hskip4.5cm
+				\begin{minipage}{5cm}
+					\begin{center}
+						\includegraphics[width=0.8\textwidth]{alma.png}
+					\end{center}
+		\end{minipage}}}
+	\end{titlepage}
+}
 
@@
 % Theorem structures.
-\newtheorem{definition}{Definition}[section]
-\newtheorem{lemma}{Lemma}[section]
-\newtheorem{example}{Example}[section]
-\newtheorem{corollary}{Corollary}[section]
+\theoremstyle{definition}
+\newtheorem{ex}{}[section]
+\newtheorem{definition}{Definition}[chapter]
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{lemma}[definition]{Lemma}
+\newtheorem{corollary}[definition]{Corollary}
+\theoremstyle{comment}
+\newtheorem{example}[definition]{Example}
+\newtheorem{claim}[definition]{Claim}
+
+\fancyhead[LO]{\slshape \leftmark}
+\fancyhead[RE]{\slshape \rightmark}
+\fancyhead[LE]{}
+\fancyhead[RO]{}
+\fancyfoot[LO,RE]{\tiny{\it}}
 
@@
 \begin{document}
-\title{Profit Optimisation in Heterogeneous 2-link Parallel Games}
-\author{Thomas Pappas}
-\date{}
+
 \maketitle
+\clearpage
 
-\section*{Abstract}
+\thispagestyle{empty}
+\null
+\clearpage
+
+\restoregeometry
+
+\thispagestyle{empty}
+\pagenumbering{gobble}
+\chapter*{Abstract}
 We study (so far) a 3-level optimisation problem where, in a 2-link $s-t$ network, link owners compete for profit by assigning tolls to links, thus creating a toll congestion game.
@@
 Then what else? Maybe find cases where there always exists a $\NE$.
+\clearpage
 
-\section{Introduction}
+\thispagestyle{empty}
+\null
+\clearpage
+
+\thispagestyle{empty}
+\pagenumbering{gobble}
+\chapter*{Σύνοψη}
+TODO: Να μεταφράσω το Abstract στα ελληνικά.
+\clearpage
+
+\thispagestyle{empty}
+\null
+\clearpage
+
+\clearpage
+\thispagestyle{empty}
+
+\pagestyle{fancy}
+
+\pagenumbering{roman}
+\tableofcontents
+\clearpage
+
+\thispagestyle{empty}
+\null
+\clearpage
+
+\pagenumbering{arabic}
+
+\chapter{Introduction}
 
@@
 
-\section{Related Work}
+\chapter{Related Work}
 TODO
 
-\section{Preliminaries}
+\chapter{Preliminaries}
 
@@
 
-\section{2-link parallel networks}
+\chapter{2-link parallel networks}
 
@@
 
-\subsection{Time-money sensitivity split}
+\section{Time-money sensitivity split}
 
@@
 [TODO: Alternative splits: rushed-relaxed, rich-poor]
-Table \ref{table:split_summary} provides of a summary for each part of the split
+Table \autoref{table:split_summary} provides of a summary for each part of the split
 
@@
 		\item if $x_1(t), x_2(t) > 0$ then $\as(t) \in [\alpha(0), \alpha(1)]$
-		\item if $0 < x_1(t) < x_2(t)$ then $\alpha(x_1(t)) \le \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon > 0$ arbitrarily small
+		\item if $0 < l_1(x_1(t)) < l_2(x_2(t))$ then $\alpha(x_1(t)) \le \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon > 0$ arbitrarily small
 	\end{enumerate}
@@
 		\item if $\alpha(0) > 0$ then $\as(t) < \alpha(0) \Rightarrow x(t) = (0, 1)$ or $(1, 0)$
-		\item if $\alpha(0) = 0$ with $0$ an accumulation point, then $x_1(t), x_2(t) > 0, \forall t \in \R_+^2$
+		\item if $x_1(0), x_2(0) > 0$ and $\alpha(0) = 0$ with $0$ an accumulation point, then $x_1(t), x_2(t) > 0, \forall t \in \R_+^2$
 		\item $\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = 0$
@@
 
-\subsection{Profit maximisation and distribution function}
+\section{Profit maximisation and distribution function}
 
@@
 
-\subsection{Equilibrium}
+\section{Equilibrium}
 
@@
 
+\cleardoublepage
+\phantomsection
+\addcontentsline{toc}{chapter}{Bibliography}
+
+\chapter*{Bibliography}
+%\begin{thebibliography}{99}
+%\end{thebibliography}
+TODO
+
 \end{document}

### 2024-08-25 thesis/article.tex
Thesis: Adds Bibliography with Harks and Cole references

@@
 \usepackage{enumerate}
+\usepackage{natbib}
 
@@
 
-We know from [insert ref] that regardless of the distribution function $a$ or the latency functions (as long as they are non-decreasing) a $\NE$ always exists.
+We know from Cole et al. \cite{10.1145/780542.780618} that regardless of the distribution function $a$ or the latency functions (as long as they are non-decreasing) a $\NE$ always exists.
 In that $\NE$ the users are split with the money-sensitive ones on the link with the lower toll and the time-sensitive ones on the higher toll one, each one seeing their link as either lower or equal cost with the other (while they all see traffic equally).
@@
 Without loss of generality we assume $t_1 > t_2$ which in turn means that for the resulting equilibrium flow $x = (x_1(t), x_2(t))$ it holds that $l_1(x_1(t)) < l_2(x_2(t))$.
-This equilibrium is guaranteed to exist according to [TODO: add ref]).
+This equilibrium is guaranteed to exist according to Harks et al. \cite{Harks_2019}.
 For the 2 edges of the game we introduce the term time-money sensitivity split $\as(t)$ as the value for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edge total latencies as equal.
@@
 \end{definition}
-The function is well defined since the given tolls $t$ result in a single optimal flow $x(t) = (x_1(t), x_2(t))$ [TODO: add ref].
+The function is well defined since the given tolls $t$ result in a single optimal flow $x(t) = (x_1(t), x_2(t))$ \cite{Harks_2019}.
 
@@
 The first is to ensure that $\alpha(p) > 0$ when $p > 0$, while the second is that $0$ is not an accumulation point.
-[TODO: maybe mention add ref who also take the first restriction as it creates games with no optimal tolls]
+[TODO: maybe mention \cite{10.1145/780542.780618} where they also take the first restriction as it creates games with no optimal tolls]
 The following two examples demonstrate the issues that might occur if these restrictions are not met.
@@
 
-\chapter*{Bibliography}
-%\begin{thebibliography}{99}
-%\end{thebibliography}
-TODO
+\bibliographystyle{plain}
+\bibliography{ref.bib}
 

### 2024-08-25 thesis/article.tex
Thesis: Updates Title and Abstract, also adds greek abstract translation

@@
 				\begin{flushleft}
-					\huge{\bf Profit Optimisation in Heterogeneous 2-link Parallel Games\\}
+					\huge{\bf Profit Games in Heterogeneous 2-link Parallel Networks\\}
 					\vskip3cm
@@
 \chapter*{Abstract}
-We study (so far) a 3-level optimisation problem where, in a 2-link $s-t$ network, link owners compete for profit by assigning tolls to links, thus creating a toll congestion game.
-In addition, each player responds to tolls in a heterogeneous way, described by a distribution function $\alpha(p)$.
-We first introduce a new term $\as$ which, given a set of tolls, can help us describe how the flow is split between the 2 links, and then we will use it to prove some properties of the game.
-We will show that even with affine latencies, there are cases where no Nash Equilibrium exists in the profit game between the toll owners.
-
-Then what else? Maybe find cases where there always exists a $\NE$.
+In this masters thesis we study a $2$-level optimisation problem where, on a $2$-link network from a source $s$ to a target $t$, a unit of flow wants to move from $s$ to $t$ using the link with the lowest cost, while the two link owners compete for profit by assigning tolls to links and thus creating a toll congestion game.
+We examine only affine latencies for the links.
+In addition, each flow player responds to tolls in a heterogeneous way, i.e.
+each flow player $p$ has a different money-time sensitivity value, which is described by a distribution function $\alpha(p)$.
+First we present some basic definitions and properties of profit homogeneous games.
+Using them as base, we examine cases of fixed and step distribution functions, where for the latter we present strict conditions for the existence or not of a Nash Equilibrium.
+We then introduce a new term, the split function $\as(t)$, defined as the time-money sensitivity value for which the $2$ link costs are equal for a given set of tolls $t$.
+With the help of $\as$ we will describe and prove some properties of the heterogeneous games for continuous distribution functions.
+In our main result, we generalise the conditions necessary for the existence of a Nash Equilibrium in the profit game between the toll owners, and finally we discuss some extensions to $n$-link parallel networks.
 \clearpage
@@
 \pagenumbering{gobble}
-\chapter*{Σύνοψη}
-TODO: Να μεταφράσω το Abstract στα ελληνικά.
+\chapter*{Συνοψη}
+Σε αυτή τη διπλωματική μεταπτυχιακού μελετάμε ένα πρόβλημα βελτιστοποίησης $2$ επιπέδων, όπου σε ένα δίκτυο με $2$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι δύο ιδιοκτήτες των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
+Εξετάζουμε μόνο αφινικές καθυστερήσεις για τις ακμές.
+Επιπλέον, ο κάθε παίκτης ροής αντιδρά στα διόδια με ετερογενή τρόπο, δηλ.
+ο κάθε παίκτης ροής $p$ έχει διαφορετική τιμή ευαισθησίας χρόνου-χρήματος, η οποία περιγράφεται από μια συνάρτηση κατανομής $\alpha(p)$.
+Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομογενών παιγνίων κέρδους.
+Mε αυτά ως βάση, εξετάζουμε περιπτώσεις σταθερών και βηματικών συναρτήσεων κατανομής, όπου για το τελευταίο παρουσιάζουμε αυστηρές συνθήκες για την ύπαρξη ή μη σημείου ισορροπίας Nash.
+Μετά εισαγάγουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού $\as(t)$, ορισμένη ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία τα κόστη των $2$ ακμών είναι ίσα για ένα δοσμένο σετ διοδίων $t$.
+Με τη βοήθεια της $\as$ θα περιγράψουμε και θα αποδείξουμε μερικές ιδιότητες των ετερογενών παιγνίων με συνεχή συνάρτηση κατανομής.
+Στο κύριο αποτέλεσμά μας, γενικοποιούμε τις συνθήκες που είναι απαραίτητες για την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των ιδιοκτητών των ακμών, και τελικώς συζητάμε κάποιες επεκτάσεις για δίκτυα με $n$ ακμές.
 \clearpage

### 2024-09-16 thesis/article.tex
Thesis: Adds Preliminaries, Network Games, Heterogeneous players
Started Heterogeneous players, WIP

@@
 
-\clearpage
-\thispagestyle{empty}
-
 \pagestyle{fancy}
@@
 
-\chapter{Related Work}
+\section{Related Work}
+
+Adding tolls to a Network Game has began as a standard practice to regulate the network flow, as it is well known that the equilibrium that occurs by the game is not guarranteed to be the most efficient.
+
 TODO
@@
 \chapter{Preliminaries}
+
+In this section we will describe the model utilised throughout this thesis.
+If we attempted to call that model by including all of it's properties, the result would be a Heterogeneous Non-atomic 2-link Parallel Network Toll Congestion Pricing Game, so while we will describe each of those properties, we will eventually focus on heterogeneity and the pricing competition, thus calling it a Heterogeneous Pricing Game.
+
+\section*{Non-atomic Parallel Network Games}
+
+We consider a directed graph $G = (\{s, t\}, N)$ where $N = \{1,\dots, n\}$ is a set of parallel links from a source node $s$ to a target node $t$.
+For the non-atomic case, there is one unit of traffic that wishes to travel from $s$ to $t$, described as the unit interval $[0, 1]$ endowed with Lebesque measure $\lambda$.
+Each point $p \in [0, 1]$ will be called a \textit{player} and will be considered to be non-cooperative and contribute to the traffic by an infinitesimal amount.
+As such the decisions of individual players have no effect on the game and it becomes natural to only consider non-zero measure collection of players.
+
+A \textit{flow} is a (stochastic) vector $x = (x_i)_{i \in N}$ where $x_i$ is the total flow on link $i$.
+The flow then creates congestion on the links, each described by a non-decreasing latency function $(\ell_i)_{i \in N}$ which we assume to be affine.
+We denote by $\mathcal{L}_d$ the class of polynomial latency functions with nonnegative coefficients and degree at most $d$, and as such $\mathcal{L}_1$ becomes the class of affine latency functions.
+Finally, the network can also be extended by allowing a set of tolls $t = (t_i)_{i \in N}$ to be assigned to each link, which in turn adds to the effective cost of a player using them.
+
+The above set-up creates a Non-atomic Parallel Network Game with tolls where each player will select the edge that minimises their \textit{individual} traffic latency.
+We consider two cases where players either react to tolls in a \textit{homogeneous} or a \textit{heterogeneous} manner.
+
+\subsection*{Homogeneous players}
+
+In the homogeneous case all players have an equal reaction to tolls, and therefore the effective cost of a player using link $i$ becomes $\ell_i(x_i) + t_i$.
+For a given set of tolls $t$, a flow $x$ is a \textit{Wardrop equilibrium for $t$} if $\forall i, j \in N$ with $x_i > 0$ it holds that
+\begin{equation}
+	\label{wardrop_inequality_cost}
+	\ell_i(x_i) + t_i \leq \ell_j(x_j) + t_j
+\end{equation}
+In that case, all links with $x_i > 0$ have equal effective costs, i.e. there exists some $K > 0$ such that $\ell_i(x_1) + t_i = K$ for all links $i$ with $x_i > 0$.
+From a well-known result from Beckman et al.
+\cite{beckmann1956studies} and Dafermos and Sparrow \cite{1363388843888284416}, such and an equilibrium for $t$ exists and is unique, therefore for a toll vector $t$ we can denote by $x(t)$ the flow occurring on  that unique equilibrium for the given toll $t$.
+We copy Lemma 2.1 from Harkes et al \cite{Harks_2019} as is for later use.
+\begin{lemma}
+	\label{lemma:wardrop_equilibrium}
+	A flow $x$ is a Wardrop equilibrium for $t$ if and only if for all feasible flows $x^\prime$,
+	\[\sum_{i \in N} (\ell_i(x_i) + t_i) \cdot (x_i - x_i^\prime) \leq 0\]
+\end{lemma}
+If $t = 0$ then the equilibrium is called the \textit{Wardrop equilibrium}.
+It's also worth noting that looking at \eqref{wardrop_inequality_cost}, we can see that what actually matters, with regard to the flow, is the relative difference among the tolls.
+I.e.
+if we consider any $c \in \R_+$ (or even $c \geq -\min_{i \in N} t_i$) then for $t^\prime = t + c$ the inequalities remain true for all $i, j \in N$ and thus the network game for the flow between tolls $t$ and $t^\prime$ is the same.
+
+Finally for affine latencies we can calculate $x(t)$.
+For $l_i(x_i) = a_i \cdot x_i + b_i, a_i > 0, b_i \geq 0$ and $t \in \R_+^N$ define $N(t) = \{i \in N | x_i(t) > 0\}$.
+Since $x(t)$ is an equilibrium for $t$ and $\sum_{i \in N(t)}x_i(t) = 1$ we solve the equations with regard to the common efficient cost $K$ and then we get for all $i \in N(t)$
+\begin{equation}
+	x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
+\end{equation}
+
+\subsection*{Heterogeneous players}
+
+In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different money/time valuation ratios.
+We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of each edge as $c_i^p(x, t) = \ell_i(x_i) + \alpha(p) t_i$ and then seek the shortest link among them.
+By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, \infty]$.
+We call $\alpha$ a \textit{distribution function}.
+Even though the definition does allow functions that are not upper bounded with $\alpha(1) = +\infty$, we will always assume that $\alpha$ is finite on $[0, 1)$.
+Also we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Section ??, allowing many players close to $0$ breaks the pricing game.
+
+\section*{Pricing Games}
+
+We introduce $n$ link owners which can assign a toll $t_i$ on link $i$ and profit from it.
+
+\section*{2-link Pricing Games (our model)}
 

### 2024-09-17 thesis/article.tex
Thesis: Updates Preliminaries, adds Pricing Games and Our model sections and improves previous ones

@@
 
-A \textit{flow} is a (stochastic) vector $x = (x_i)_{i \in N}$ where $x_i$ is the total flow on link $i$.
+A \textit{flow} is a Lebesque measurable function $f: [0, 1] \rightarrow N$ that describes which link is selected by each player.
+It is more intuitive, however, to consider the resulting flow on each link (\textit{flow on paths}), i.e. $x_i = \lambda(\{p \in [0, 1]: f(p) = i\})$.
+Hence we get flow as a (stochastic) vector $x = (x_i)_{i \in N}$ where $x_i$ is the total flow on link $i$ with $x_i \geq 0$ and $\sum_{i \in N}x_i = 1$.
 The flow then creates congestion on the links, each described by a non-decreasing latency function $(\ell_i)_{i \in N}$ which we assume to be affine.
@@
 \cite{beckmann1956studies} and Dafermos and Sparrow \cite{1363388843888284416}, such and an equilibrium for $t$ exists and is unique, therefore for a toll vector $t$ we can denote by $x(t)$ the flow occurring on  that unique equilibrium for the given toll $t$.
+We will freely use when needed the general game-theoretical notation of $x(t_i, t_{-i})$ where $t_{-i} = t \setminus \{t_i\}$.
 We copy Lemma 2.1 from Harkes et al \cite{Harks_2019} as is for later use.
@@
 In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different money/time valuation ratios.
-We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of each edge as $c_i^p(x, t) = \ell_i(x_i) + \alpha(p) t_i$ and then seek the shortest link among them.
+We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of each edge as $c_i^p(x(t)) = \ell_i(x_i) + \alpha(p) \cdot t_i$ and then seek the shortest link among them.
 By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, \infty]$.
@@
 Even though the definition does allow functions that are not upper bounded with $\alpha(1) = +\infty$, we will always assume that $\alpha$ is finite on $[0, 1)$.
-Also we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Section ??, allowing many players close to $0$ breaks the pricing game.
+Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Example \ref{example:a_0_0}, allowing many players close to $0$ breaks the pricing game.
+
+With the above we can again define a Nash equilibrium for the game if $\forall i \in N$ and $\forall p \in [0, 1]$ it holds that
+\[c_{f(p)}^p(x(t)) \leq c_i^p(x(t))\]
+Existence of an equilibrium is guaranteed by the more general results of Schmeidler \cite[Thm 2]{1973JSP.....7..295S}, while uniqueness is covered by Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220}; for a more detailed coverage of those look at the definitions and propositions of Cole et al.
+\cite[\S2]{10.1145/780542.780618}.
+Therefore can extend the definition for $x(t)$ similarly as in the homogeneous case.
 
@@
 
-We introduce $n$ link owners which can assign a toll $t_i$ on link $i$ and profit from it.
+While keeping the above Network Game model, we introduce $n$ agents who each own one link of the network and can thus assign its toll and profit from it.
+The profit is defined for each link owner $i$ as $\Pi_i = x_i \cdot t_i$ which, since we defined $x(t)$ above, we can extend the definition to $\Pi_i(t) = x_i(t) \cdot t_i$ describing the profit at the equilibrium for given toll $t$.
+The link owners compete with each other for profit, each selfishly selecting the toll $t_i$ that will maximise their profit given the remaining tolls $t_{-i}$.
+We describe this best response as $B_i(t_{-i}) = \argmax_{t_i \geq 0} \Pi_i(t_i, t_{-i})$.
+Consequently, a toll vector $t$ is a \textit{Nash Equilibrium} for the pricing game, if $\forall i \in N$ and $\forall t_i^\prime \in \R$ it holds that
+\[\Pi_i(t_i, t_{-i}) \geq \Pi_i(t_i^\prime, t_{-i})\]
 
-\section*{2-link Pricing Games (our model)}
+\subsection*{Homogeneous players}
 
-A 2-link $s-t$ parallel network is a graph with a source node $s$, a destination node $t$ and $2$ edges connecting $s$ to $t$.
-Each link is associated with a latency function $l_1, l_2$
+For homogeneous players and affine latencies we can calculate the best response functions for each link owner by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$. TODO
+
+\section*{2-link Heterogeneous Pricing Games (our model)}
+
+Focusing on the model that will be used in this thesis, simplify our network by only having two links but consider that the flow is acting in a heterogeneous way.
+The model can thus be defined as the tuple $(\ell, \alpha)$, where $\ell = (\ell_1, \ell_2)$ the latency functions and $\alpha$ the distribution function.
 [TODO: Add figure]
-A flow of infinitesimal users totaling up to a flow of $[0, 1]$ wishes to move from $s$ to $t$ through the link with the lowest cost.
 
@@
 \begin{example}
+	\label{example:a_0_0}
 	Consider a $2$-link parallel network pricing game with distribution function $\alpha$ for which it does not hold that $\alpha(p) > 0$ when $p > 0$.

### 2024-09-23 thesis/article.tex
Thesis: Refactors split function section into chapter, reaches main theorem
Many fixes and rewrites, small improvements in other sections

@@
 \newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
-\newcommand{\RightarrowArg}[1]{\stackrel{#1}{\Longrightarrow}}
+\newcommand{\RightarrowArg}[1]{\stackrel{#1}{\Rightarrow}}
 \newcommand{\LeftrightarrowArg}[1]{\stackrel{#1}{\Leftrightarrow}}
@@
 In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different money/time valuation ratios.
-We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of each edge as $c_i^p(x(t)) = \ell_i(x_i) + \alpha(p) \cdot t_i$ and then seek the shortest link among them.
+We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of each edge as $c_i^p(t) = \ell_i(x_i(t)) + \alpha(p) \cdot t_i$ and then seek the shortest link among them.
 By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, \infty]$.
@@
 
-With the above we can again define a Nash equilibrium for the game if $\forall i \in N$ and $\forall p \in [0, 1]$ it holds that
-\[c_{f(p)}^p(x(t)) \leq c_i^p(x(t))\]
+We can therefore define an instance of a Heterogeneous Pricing Game as the tuple $(N, \ell, \alpha)$ with $N = \{1, 2, \dots, n\}$, $\ell = (\ell_i)_{i \in N}$ and $\alpha$ the distribution function.
+Then with all the above we can again define a Nash equilibrium for the game if $\forall i \in N$ and $\forall p \in [0, 1]$ it holds that
+\[c_{f(p)}^p(t) \leq c_i^p(t)\]
 Existence of an equilibrium is guaranteed by the more general results of Schmeidler \cite[Thm 2]{1973JSP.....7..295S}, while uniqueness is covered by Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220}; for a more detailed coverage of those look at the definitions and propositions of Cole et al.
@@
 Therefore can extend the definition for $x(t)$ similarly as in the homogeneous case.
+
+Finally, we will prove here a general property of parallel networks which capture the relationship between latencies and tolls.
+It is trivial for homogeneous games that higher tolls create lower latencies on the respective edges, but for the heterogeneous case it is not straightforward so we'll prove it.
+
+\begin{lemma}
+	\label{lemma:latencies_tolls}
+	For a Heterogeneous Parallel Game $(N, \ell, \alpha)$ with tolls $t$ and Nash equilibrium for $t$ flow $x(t)$, it holds that for all $i, j \in N$ with $x_i(t), x_j(t) > 0$
+	\begin{enumerate}[(i)]
+		\item $\ell_i(x_i(t)) < \ell_j(x_j(t))$ iff $t_i > t_j$
+		\item $\ell_i(x_i(t)) = \ell_j(x_j(t))$ iff $t_i = t_j$
+		\item $\ell_i(x_i(t)) > \ell_j(x_j(t))$ iff $t_i < t_j$
+	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	We will prove $(i)$ and the rest follow similarly.
+	For the left-to-right direction we assume that $\ell_i(x_i(t)) < \ell_j(x_j(t))$.
+	If now $t_i \le t_j$ then for all players $p$ we get $\ell_i(x_i(t)) + \alpha(p) \cdot t_i < \ell_j(x_j(t)) + \alpha(p) \cdot t_j \Rightarrow c_i^p(t) < c_j^p(t)$.
+	Therefore there exist players $p_j$ on link $j$ for which $c_{f(p_j)}^{p_j}(t) = c_j^{p_j}(t) > c_i^{p_j}(t)$, which is a contradiction since $x(t)$ is a Nash equilibrium.
+	The opposite direction is also proved similarly.
+\end{proof}
 
@@
 
-Focusing on the model that will be used in this thesis, simplify our network by only having two links but consider that the flow is acting in a heterogeneous way.
-The model can thus be defined as the tuple $(\ell, \alpha)$, where $\ell = (\ell_1, \ell_2)$ the latency functions and $\alpha$ the distribution function.
+Focusing on the model that will be used in this thesis, we simplify our network by only having $2$ links, and then consider that the flow is acting in a heterogeneous way.
+The model can thus be defined as the tuple $([2], \ell, \alpha)$, where $[2] = \{1, 2\}$ the links, $\ell = (\ell_1, \ell_2)$ the latency functions and $\alpha$ the distribution function.
 [TODO: Add figure]
+When discussing properties of the model where the pricing game is not relevant, we will refer to a $([2], \ell, \alpha)$ instance as a toll game, and otherwise as a pricing game.
 
-\chapter{2-link parallel networks}
+\chapter{Money sensitivity split}
 
-We start with the simple case of 2-link parallel networks.
-[TODO: Add figure]
-In this simple setup a user of the flow
+\section{Introduction}
 
-\section{Time-money sensitivity split}
-
-Consider a 2-link parallel network with latency functions $l_1(x), l_2(x)$ and tolls $t=(t_1, t_2)$ assigned to them.
-Without loss of generality we assume $t_1 > t_2$ which in turn means that for the resulting equilibrium flow $x = (x_1(t), x_2(t))$ it holds that $l_1(x_1(t)) < l_2(x_2(t))$.
-This equilibrium is guaranteed to exist according to Harks et al. \cite{Harks_2019}.
-For the 2 edges of the game we introduce the term time-money sensitivity split $\as(t)$ as the value for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edge total latencies as equal.
+Consider a $([2], \ell, \alpha)$ toll game such that $x_1(0), x_2(0) > 0$ with tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
+Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} follows that $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
+For the $2$ edges of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edges' total latencies as equal.
 More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
-\[l_1(x_1(t)) + \as(t) t_1 = l_2(x_2(t)) + \as(t) t_2\]
+\[\ell_1(x_1(t)) + \as(t) \cdot t_1 = \ell_2(x_2(t)) + \as(t) \cdot t_2\]
 Solving for $\as$ we get
-\[\as(t) = \frac{l_2(x_2(t)) - l_1(x_1(t))}{t_1 - t_2}\]
+\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
 \\
@@
 \begin{itemize}
-	\item if $\alpha(p) < \as$ then $l_1(x_1(t)) + \alpha(p) t_1 < l_2(x_2(t)) + \alpha(p) t_2$, thus $p$ is on edge $1$
-	\item if $\alpha(p) > \as$ then $l_1(x_1(t)) + \alpha(p) t_1 > l_2(x_2(t)) + \alpha(p) t_2$, thus $p$ is on edge $2$
-	\item if $\alpha(p) = \as$ then $l_1(x_1(t)) + \alpha(p) t_1 = l_2(x_2(t)) + \alpha(p) t_2$, thus $p$ is either on edge $1$ or $2$
+	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on edge $1$
+	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on edge $2$
+	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on edge $1$ or $2$
 \end{itemize}
-Remember that we have assumed that $t_1 > t_2 \Rightarrow l_1(x_1(t)) < l_2(x_2(t))$.
+Remember that we have assumed that $t_1 > t_2 \Rightarrow \ell_1(x_1(t)) < \ell_2(x_2(t))$.
 Therefore the flow passing through the faster edge $1$ is contained with players where $\alpha(p) \le \as(t)$, while the flow in the cheaper edge $2$ is contained with players where $\alpha(p) \ge \as(t)$.
-Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "higher" part of the split.
-[TODO: Alternative splits: rushed-relaxed, rich-poor]
+Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
+If it helps with the intuition, alternative split labels could be rushed-relaxed or rich-poor.
 Table \autoref{table:split_summary} provides of a summary for each part of the split
@@
 		sensitivity & time $\ge$ money & time $\le$ money \\ \hline
-		latency & lower $(l_2)$ & higher $(l_1)$ \\ \hline
+		latency & lower $(\ell_2)$ & higher $(\ell_1)$ \\ \hline
 		toll & higher $(t_1)$ & lower $(t_2)$ \\ \hline
-		edge & low-latency, high-toll $(1)$ & high-latency, low-toll $(2)$ \\ \hline
+		link/edge & low-latency, high-toll $(1)$ & high-latency, low-toll $(2)$ \\ \hline
 		$t_1 - t_2$ & lower & higher \\ \hline
-		split & lower & higher \\ \hline
+		split & lower & upper \\ \hline
 	\end{tabular}
@@
 Those players, if any, even though they see both edges with equal total cost, in the optimal flow $x$ they have settled in either edge $1$ or $2$.
-We investigate more in depth the relation of $\as$ to the flow in [TODO: add ref].
+We investigate more in depth the relation of $\as$ with the flow in the following Lemmas.
 \\[12pt]
 We can now formally define $\as$ and prove some of its properties.
+
+\section{Definitions}
+
 \begin{definition}
-	Given a 2-link parallel heterogeneous game with latency functions $l_1, l_2$, we define the time-money sensitivity split function $\as: \R^2_+ \rightarrow (0, +\infty)$ where for given tolls $t = (t_1, t_2)$
-	\[\as(t) = \frac{l_2(x_2(t)) - l_1(x_1(t))}{t_1 - t_2}\]
+	\label{definition:split_function}
+	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$, tolls $t = (t_1, t_2), t_1 \ne t_2$ and $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$, we define the \textit{money sensitivity split function} $\as: \R_+^2 \setminus \{(a, a) | a \in \R_+\} \rightarrow (0, +\infty)$ as follows
+	\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
 \end{definition}
-The function is well defined since the given tolls $t$ result in a single optimal flow $x(t) = (x_1(t), x_2(t))$ \cite{Harks_2019}.
 
-We start with some basic properties.
+We will also give a more formal definition to the lower-upper split intuition we described above.
+\begin{definition}
+	\label{definition:split_lower_upper}
+	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$, tolls $t \ne 0$ and $x(t)$ the Nash equilibrium for $t$, and also assuming w.l.o.g.
+that $t_1 > t_2$, we define as \textit{lower split} the (possibly zero) flow $x_1(t)$ and as \textit{upper split} the remaining flow $x_2(t)$.
+\end{definition}
+
+\begin{corollary}
+	\label{corollary:split_to_alpha}
+	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, it holds that
+	\begin{itemize}
+		\item $\alpha(p) \le \as(t)$, for all players $p$ in the lower split
+		\item $\alpha(p) \ge \as(t)$, for all players $p$ in the upper split
+	\end{itemize}
+\end{corollary}
+
+\begin{proof}
+	Let again w.l.o.g.
+assume $t_1 > t_2 \LeftrightarrowArg{\ref{lemma:latencies_tolls}} \ell_1(x_1(t)) < \ell_2(x_2(t))$, making by definition \ref{definition:split_lower_upper} a player $p$ in the lower split be in link $1$.
+	Since $x$ is a Nash equilibrium we have
+	\begin{align*}
+		c_1^p(t) &\le c_2^p(t) \Rightarrow \ell_1(x_1(t)) + \alpha(p) \cdot t_1 \le \ell_2(x_2(t)) + \alpha(p) \cdot t_2 \\
+		&\RightarrowArg{t_1 > t_2} \alpha(p) \le \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2} \RightarrowArg{\ref{definition:split_function}} \alpha(p) \le \as(t)
+	\end{align*}
+	Similarly we can show that $\alpha(p) \ge \as(t)$, for all players $p$ in the upper split.
+\end{proof}
+
+At this point in our analysis, we will additionally need the notion of the lowest and highest $\alpha$ value in a flow of players.
+
+In general, since we're working with a Lebesque-measurable flow, it is natural to not bother with distinguishing between a flow $[0, x_1]$ or $[0, x_1)$, as the player $x_1$ can be arbitrarily placed at any link without affecting the game.
+In a heterogeneous setting, however, the existence or not of that player matters, as its $\alpha(x_1)$ value might be different from the rest of the players in the flow, depending on how $\alpha$ is defined.
+We bypass this issue by instead using set border bounds.
+
+\begin{definition}
+	\label{definition:alpha_flow_sets}
+	Let $([2], \ell, \alpha)$ a toll game with $x_1(0), x_2(0) > 0$, tolls $t \ne 0$ and $x(t)$ the Nash equilibrium for $t$.
+	We define as $A_i(t)$ the set of $\alpha(p)$ values for players $p$ on edge $i$ in the Nash equilibrium for $t$.
+	More formally, we define a set function $A_i: \R_+^2 \setminus \{(a, a) | a \in \R_+\} \rightarrow \mathcal{P}(\R_+)$ such that
+	\[A_i(t) = \{\alpha(p)|p \text{ in edge } i \textit{ for } x(t) \}\]
+	For tolls where $t_1 = t_2$ we cannot define lower and upper split, but we will extend the definition of $A_i$ for those tolls with a sign to specify which split we assume the link to have.
+	Therefore we define $A_i^-(0)$ and $A_i^+(0)$ respectively as
+	\[A_i^-(0) = \{\alpha(p)|p \in [0, x_i(0))\} \qquad A_i^+(0) = \{\alpha(p)|p \in (x_i(0), 1]\}\]
+	%\[A_i^-(0) = \lim_{t_1 - t_2 \rightarrow 0^-}A_i(t) \qquad A_i^+(0) = \lim_{t_1 - t_2 \rightarrow 0^+}A_i(t)\]
+\end{definition}
+
+We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any edge and their $\alpha$ value could change the sets' properties.
+It doesn't affect our analysis, however, since having a split on that player is only possible for $t = 0$ and $\as(0)$ is undefined, plus as we'll show in the next section neither it's limit exists, making the $\alpha$ value of player $x_i(0)$ (in each assumingly split case) irrelevant.
+
+We continue with describing some basic properties around the values of $\as$.
+
+\section{Properties and analysis}
+
 \begin{lemma}
 	\label{lemma:split_basic}
-	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$, the following hold:
+	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, the following hold:
 	\begin{enumerate}[(i)]
@@
 		\item if $x_1(t), x_2(t) > 0$ then $\as(t) \in [\alpha(0), \alpha(1)]$
-		\item if $0 < l_1(x_1(t)) < l_2(x_2(t))$ then $\alpha(x_1(t)) \le \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon > 0$ arbitrarily small
+		\item if $\as(t) < \alpha(0)$ or $\as(t) > \alpha(1)$ then $x(t) = (0, 1)$ or $(1, 0)$
+		\item if $x_1(t), x_2(t) > 0$ with $\ell_1(x_1(t)) < \ell_2(x_2(t))$ then\\
+		$\sup A_1(t) \le \as(t) \le \inf A_2(t)$
 	\end{enumerate}
@@
 	\begin{enumerate}[(i)]
-		\item Obviously $\as(t) \ne 0$ since $\as(t) = 0 \Rightarrow l_1(x_1(t)) = l_2(x_2(t))$ which is impossible in a heterogeneous setup.
-		Then we only need to notice that $l_1(x_1(t)) < l_2(x_2(t)) \iff t_1 > t_2$ and we get $\as(t) > 0$ from definition.
-		\item Since $x_1(t), x_2(t) > 0$ then $\exists p_1, p_2 \in [0, 1]$ each on a different edge, for which we assume w.l.o.g. that $\alpha(p_1) \le \alpha(p_2)$.
-		It holds that $\alpha(p_1) \le \as(t) \le \alpha(p_2)$ so with $\alpha$ being non-decreasing it follows
+		\item Trivial application of Lemma \ref{lemma:latencies_tolls}.
+		Since we have $t_1 \ne t_2$ it follows that $\ell_1(x_1(t)) \ne \ell_2(x_2(t))$ and therefore $\as(t) \ne 0$.
+		Then we only need to notice that $\ell_1(x_1(t)) < \ell_2(x_2(t)) \Leftrightarrow t_1 > t_2$ and we get $\as(t) > 0$ from Definition \ref{definition:split_function}.
+		\item Since $x_1(t), x_2(t) > 0$ then $\exists p_1, p_2 \in [0, 1]$ each on a different link, for which we assume w.l.o.g. that $\alpha(p_1) \le \alpha(p_2)$.
+		It holds from \ref{corollary:split_to_alpha} that $\alpha(p_1) \le \as(t) \le \alpha(p_2)$ so with $\alpha$ being non-decreasing it follows
 		\[\alpha(0) \le \alpha(p_1) \le \as(t) \le \alpha(p_2) \le \alpha(1) \Rightarrow \as(t) \in [\alpha(0), \alpha(1)]\]
-		\item We know that $x_1(t) < x_2(t)$ means that edge 1 has the lower split.
-		Therefore we have
-		\[\alpha(p) \le \as(t), \forall p \in [0, x_1(t)] \Rightarrow \alpha(x_1(t)) \le \as(t)\]
-		Likewise for edge 2 we have
-		\[\as(t) \le \alpha(p), \forall p \in (x_1(t), 1] \Rightarrow \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon \in (0, 1 - x_1(t))\]
+		\item Inverse logic statement of $(ii)$ ($(P \rightarrow Q) \rightarrow (\neg Q \rightarrow \neg P)$).
+		\item Natural consequence from Corollary \ref{corollary:split_to_alpha} and Definition \ref{definition:alpha_flow_sets}.
 	\end{enumerate}
@@
 
-The next lemma will help us describe how $\as(t)$ is changing in relation to toll difference (and in extend to latency difference).
+At this point we should notice that $\as$, similarly to $x$, depends only on the toll difference $t_1 - t_2$ and whether $t_1 < t_2$ or otherwise.
+In order to emphasise on this, let's point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
+\[
+	x(t_d) =
+	\begin{cases*}
+		x((t_d, 0)) & $t_d \ge 0$ \\
+		x((0, -t_d)) & $t_d < 0$ \\
+	\end{cases*}
+\]
+We will not utilise this definition as is in this work, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll difference does in $\R$.
+
+With that in mind, we will investigate the monotonicity of $\as(t)$ in relation to toll differences (and in extension to latency differences).
+For this we will need to compare different tolls that create lower-upper splits in the same edges, or in other words for tolls $t, t^\prime$ to hold that if $t_1 > t_2$ then also $t_1^\prime > t_2^\prime$ and vice-versa.
+We will capture this with the following condition
+\begin{equation}
+	\label{eq:split_property_cond_tolls_0}
+	\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0
+\end{equation}
+where indeed if $t_1 > t_2$ then
+\[t_1 > t_2 \Leftrightarrow t_1 - t_2 > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_1^\prime - t_2^\prime > 0 \Leftrightarrow t_1^\prime > t_2^\prime\]
+and likewise we also get $t_1 < t_2 \Leftrightarrow t_1^\prime < t_2^\prime$.
+Also note that this property also holds for the respective latencies.
+
 \begin{lemma}
-	Given a 2-link parallel heterogeneous game with time-money sensitivity split function $\as$ and tolls $t, t^\prime$ such that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0$, the following hold:
+	\label{lemma:split_monotonicity}
+	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t, t^\prime \ne 0$ such that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0$, the following hold:
 	\begin{enumerate}[(i)]
-		\item $\as(t) \ge \as(t^\prime)$ iff $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1$
-		\item $\as(t) \le \as(t^\prime)$ iff $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \ge 1$
+		\item if $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1$ then $\as(t) \ge \as(t^\prime)$
+		\item if $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \ge 1$ then $\as(t) \le \as(t^\prime)$
+		\item if $\as(t) > \as(t^\prime)$ then $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} < 1$
+		\item if $\as(t) < \as(t^\prime)$ then $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 1$
 	\end{enumerate}
@@
 \begin{proof}
-	Before we get into the propositions, notice that the condition
-	\begin{equation}
-		\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0
-		\label{eq:split_property_cond_tolls_0}
-	\end{equation}
-	ensures that the two tolls provide splits with same edges in their respective lower and higher sections.
-	We show this for $t_1 > t_2$ and likewise it also holds for $t_1 < t_2$.
-	\[t_1 > t_2 \Leftrightarrow t_1 - t_2 > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_1^\prime - t_2^\prime > 0 \Leftrightarrow t_1^\prime > t_2^\prime\]
-	%Also note that this property extends to the latencies, giving us
-	%\begin{equation}
-	%	\frac{l_1(x_1(t)) - l_2(x_2(t))}{l_1(x_1^\prime(t)) - l_2(x_2^\prime(t))} > 0
-	%	\label{eq:split_property_cond_latencies_0}
-	%\end{equation}
-	Now moving on to the prepositions, we focus on proving $(i)$ in the right-to-left direction; then the same steps can be followed backwards to prove left-to-right.
-	Finally proving $(ii)$ will be much easier as there are many steps symmetric to the ones for $(i)$.
+	$ $
+	\paragraph{$(i)$}
+	Begin by noticing that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1 \Rightarrow |t_1 - t_2| \le |t_1^\prime - t_2^\prime|$, i.e.
+from $t$ to $t^\prime$ the toll difference is not decreasing, which means that the players in the upper link (i.e.
+the players who already prefer the higher latency and lower toll link) will still view their link as the best option.
+	Therefore only flow from the lower latency edge, if any, might move towards the slower one.
+	Assume w.l.o.g. that $t_1 > t_2$, giving us $x_1(t) \ge x_1(t^\prime)$ and $x_2(t) \le x_2(t^\prime)$.
 
-	\paragraph{$(i)$}
-	Begin by noticing that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1 \Leftrightarrow |t_1 - t_2| \le |t_1^\prime - t_2^\prime|$ (opposite direction is ensured by $(\ref{eq:split_property_cond_tolls_0})$), i.e.
-the toll difference is increasing.
-	Assume w.l.o.g. that $x_1 < x_2$.
+	If $x_1(t) = x_1(t^\prime)$, then looking at $\as$ we get
+	\[\as(t^\prime) = \frac{\ell_2(x_2(t^\prime)) - \ell_1(x_1(t^\prime))}{t_2^\prime - t_1^\prime} = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_2^\prime - t_1^\prime} = \as(t) \frac{t_2 - t_1}{t_2^\prime - t_1^\prime}\]
+	so obviously $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1 \Leftrightarrow \as(t^\prime) \le \as(t)$.
 
-	If $x_1(t) = 0$ then
-	\[\as(t) = \frac{l_2(1)}{t_2 - t_1}, \as(t^\prime) = \frac{l_2(1)}{t_2^\prime - t_1^\prime}\] 
-	so obviously $t_2 - t_1 \le t_2^\prime - t_1^\prime \Rightarrow \as(t) \ge \as(t^\prime)$.
-
-	If $x_1(t) > 0$ then we know [TODO: do we?] that the latency difference might also increase, with flow from the lower latency edge, if any, moving towards the slower one, i.e.
-$x_1(t) \ge x_1(t^\prime)$.
-	%\[|t_1 - t_2| \le |t_1^\prime - t_2^\prime| \Leftrightarrow |l_1(x_1(t)) - l_2(x_2(t))| \le |l_1(x_1(t^\prime)) - l_2(x_2(t^\prime))|\]
-	%\begin{equation}
-	%	|l_1(x_1(t)) - l_2(x_2(t))| \le |l_1(x_1(t^\prime)) - l_2(x_2(t^\prime))| \LeftrightarrowArg{(\ref{eq:split_property_cond_latencies_0})} \frac{l_1(x_1(t)) - l_2(x_2(t))}{|l_1(x_1(t^\prime)) - l_2(x_2(t^\prime))|} \le 1
-	%	\label{eq:split_property_cond_latencies_1}
-	%\end{equation}
-	If no flow moves then we can easily show that $\as(t) \ge \as(t^\prime)$ similarly to the case with $x_1(t) = 0$.
-	Otherwise we have $x_1(t) > x_1(t^\prime) \Rightarrow \exists \epsilon > 0: x_1(t) = x_1(t^\prime) + \epsilon$ and by carefully applying property $\ref{lemma:split_basic}(ii)$ we get
-	\[\as(t^\prime) \le \alpha(x_1(t^\prime) + \epsilon) = \alpha(x_1(t)) \le \as(t)\]
+	If $x_1(t) > x_1(t^\prime)$ then there exists a player $p$ who is in link $1$ in the Nash equilibrium for $t$ and in link $2$ for the one for $t^\prime$, meaning that from Definition \ref{definition:alpha_flow_sets} we get
+	\[\inf A_2(t^\prime) \le \alpha(p) \le \sup A_1(t)\]
+	By now carefully applying  (twice) the property from Lemma $\ref{lemma:split_basic}(iv)$ we get
+	\[\as(t^\prime) \le \inf A_2(t^\prime) \le \sup A_1(t) \le \as(t)\]
 
 	\paragraph{$(ii)$}
-	Symmetrically to $(i)$ in this case the toll difference is decreasing, and therefore flow from the higher latency edge will move towards the lower one, i.e.
-$x_1(t) \le x_1(t^\prime)$ (assuming again $x_1 < x_2$).
+	Symmetrically to $(i)$ in this case the toll difference is non-increasing from $t$ to $t^\prime$, and therefore flow from the higher latency edge will move towards the lower one, i.e.
+$x_1(t) \le x_1(t^\prime)$ and $x_2(t) \ge x_2(t^\prime)$ (assuming again $t_1 > t_2$).
 	With a similar argument we then get $\as(t) \le \as(t^\prime)$.
+
+	\paragraph{$(iii)$}
+	Assume $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \ge 1$.
+	Then by $(ii)$ it would hold that $\as(t) \le \as(t^\prime)$ which is a contradiction.
+
+	\paragraph{$(iv)$}
+	Assume $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1$.
+	Then by $(i)$ it would hold that $\as(t) \ge \as(t^\prime)$ which is a contradiction.
 \end{proof}
 
-The next lemma gives us some insight of the behavior of $\as(t)$ around its edge values.
+Finally, focusing on the asymptotic behavior or $\as$, we can easily check that when $t_d \rightarrow 0$ the flow approaches $x(0)$.
+However, if $t_1 > t_2$ then $x_1$ (otherwise $x_2$) is the lower split, and from Lemma \ref{lemma:split_basic}$(iv)$ we can see that $\as$ is between the highest value of the lower split and the lowest value of the upper split.
+Therefore the direction of $t_1 > t_2$ matters to as to which $\alpha$ value $\as$ approaches as $t_1 - t_2 \rightarrow 0$, a distinction which we can capture by using $t_1 - t_2 \rightarrow 0^-$ and $t_1 - t_2 \rightarrow 0^+$ accordingly.
+
+The next lemma sums up the above discussion and gives us some insight about the asymptotic behavior of $\as(t)$.
 \begin{lemma}
-	\label{lemma:split_bounds}
-	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$, the following hold:
+	\label{lemma:split_asymptotic}
+	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, the following hold:
 	\begin{enumerate}[(i)]
-		\item if $\alpha(0) > 0$ then $\as(t) < \alpha(0) \Rightarrow x(t) = (0, 1)$ or $(1, 0)$
-		\item if $x_1(0), x_2(0) > 0$ and $\alpha(0) = 0$ with $0$ an accumulation point, then $x_1(t), x_2(t) > 0, \forall t \in \R_+^2$
-		\item $\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = 0$
-		\item $\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_1), \lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_2)$, where ($x_1, x_2)$ the optimal flow under no tolls
+		\item
+		\begin{flalign*}
+			\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) &= 0 &
+		\end{flalign*}
+		\item
+		\begin{flalign*}
+			\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) &= \sup A_1^-(0) \qquad \text{and} \qquad \lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \sup A_2^-(0) &
+		\end{flalign*}
 	\end{enumerate}
@@
 	\begin{enumerate}[(i)]
-		\item Direct consequence from the fact that all players $p$ with $\as(t) < \alpha(p)$ are in the low latency edge.
-		\item Since $\alpha(0) = 0$ and $0$ an accumulation point, then $\forall \delta > 0 \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
-		Therefore $\forall t \in \R_+^2$ if $\delta = \as(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as(t)$, which means that the lower latency edge will always have flow some $\epsilon > 0$, and therefore $x_1(t), x_2(t) > 0$.
-		\item We only need to notice that $|l_1(x_1(t)) - l_2(x_2(t))| \le \max\{l_1(1), l_2(1)\} = L$ and we find
-		\[\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = \lim_{|t_1 - t_2| \rightarrow +\infty}\frac{|l_1(x_1(t)) - l_2(x_2(t))|}{|t_1 - t_2|} \le \lim_{|t_1 - t_2| \rightarrow +\infty}\frac{L}{|t_1 - t_2|} = 0\]
+		\item We only need to notice that
+		\[|\ell_1(x_1(t)) - \ell_2(x_2(t))| \le \max\{\ell_1(1) - \ell_2(0), \ell_2(1) - \ell_1(0)\} = L\]
+		and we find
+		\[\lim_{|t_1 - t_2| \rightarrow +\infty}|\as(t)| = \lim_{|t_1 - t_2| \rightarrow +\infty}\frac{|\ell_1(x_1(t)) - \ell_2(x_2(t))|}{|t_1 - t_2|} \le \lim_{|t_1 - t_2| \rightarrow +\infty}\frac{L}{|t_1 - t_2|} = 0\]
 		and since $\as(t) > 0$ we get $\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = 0$.
-		\item As $|t_1 - t_2| \rightarrow 0$ then also $|l_1(x_1(t)) - l_2(x_2(t))| \rightarrow 0$ as the game approaches the homogeneous case.
-		Then flow on the low latency edge will define the limit of $\as(t)$.
-			\begin{itemize}
-				\item For $t_1 > t_2$ we get lower latency edge $1$ with flow $x_1(t) \rightarrow x_1$ and therefore
-				\[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_1)\]
-				\item For $t_1 < t_2$ we get lower latency edge $2$ with flow $x_2(t) \rightarrow x_2$ and therefore
-				\[\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_2)\]
-			\end{itemize}
+		\item We begin with the first equality.
+		Assume in $[0, x_1(0))$ an increasing sequence $(p_n)_{n \in \mathbb{N}}$ for which $p_n \rightarrow x_1(0)$.
+		From the fact that $x(t)$ is continuous (TODO: add ref?) and that if $x_1(t) < x_1(0)$ then link $1$ has the lower split by definition, we can see that for each $p_n$ we can find (not unique) tolls $t_n$ such that $x_1(t_n) = p_n$.
+		Indeed we can simply solve $\ell_1(p_n) + \alpha(p_n) \cdot t_{n, 1} = \ell_2(1 - p_n) + \alpha(p_n) \cdot t_{n, 2}$ which has as solution a unique toll difference for which $t_{n, 1} - t_{n, 2} > 0$.
+		Obviously $\as(t_n) = \alpha(p_n)$.
+
+		Now notice that, as $p_n$ increases, the toll difference is decreasing, which in turn means from Lemma \ref{lemma:split_monotonicity}$(ii)$, while adding that for $t_1 - t_2 \rightarrow 0^+$ condition \ref{eq:split_property_cond_tolls_0} also holds, that $\as$ is non-decreasing.
+		We can therefore find a non-decreasing sequence $(\as(t_n))_{n \in \mathbb{N}}$ where $t_{n, 1} - t_{n, 2} \rightarrow 0^-$ as $n \rightarrow +\infty$.
+		From all the above, and by observing that $p_n \in A_1^-(0), \forall n \in \mathbb{N}$, we get
+		\[\lim_{t_1 - t_2 \rightarrow 0^+}\as(t) = \lim_{t_{n, 1} - t_{n, 2} \rightarrow 0^+}\as(t_n) = \lim_{n \rightarrow +\infty}\alpha(p_n) = \sup A_1^-(0) \]
+
+		We can show the second equality with a similar argument, as all steps are symmetric for $t_1 - t_2 \rightarrow 0^-$.
 	\end{enumerate}
@@
 
-From the above lemma we can also observe the following
-
 \begin{corollary}
-	Given a 2-link parallel heterogeneous game with distribution function $\alpha$ and time-money sensitivity split function $\as$ and $x = (x_1, x_2)$ the optimal flow in the game without tolls, then $\as(t) \le \max\{\alpha(x_1), \alpha(x_2)\}$.
+	\label{corollary:split_asymptotic_continuous}
+	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, the following hold:
+	\begin{enumerate}[(i)]
+		\item if $\alpha$ continuous at $x_1(0)$, then
+		\[\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0))\]
+		\item if $\alpha$ continuous at $x_2(0)$, then
+		\[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_2(0))\]
+	\end{enumerate}
 \end{corollary}
 
-This corollary hints that all values of $\alpha$ above $\max\{x_1, x_2\}$ are irrelevant to the game.
-This will become more obvious later when calculating best responses as those values will never be used.
-[TODO: Maybe put this in its own Lemma and prove it?]
+All the above lemmas can now help us describe the behaviour of $\as$ for different tolls.
+On one side, as $t_d = t_1 - t_2 \rightarrow -\infty$ then $\as(t) \rightarrow 0$ (Lemma \ref{lemma:split_asymptotic}$(i)$), while afterwards as $t_d$ increases below $0$, meaning the difference (absolute) value is decreasing, then $\as(t)$ is non-decreasing (Lemma \ref{lemma:split_monotonicity}$(i)$), and finally as $t_d \rightarrow 0^-$, $\as(t)$ approaches $\sup A_2^-(0)$ (Lemma \ref{lemma:split_asymptotic}$(ii)$).
+On the other side from $t_d \rightarrow +\infty$ we get a symmetric behavior all the way ending up in $\sup A_1^-(0)$.
+The above show that $\as(t)$ is continuous for all $t \ne 0$ and any limit around $0$ has different left and right sides (apart from the very specific case where $x_1(0) = x_2(0)$).
+We proceed with an example to solidify this.
 
-\section{Profit maximisation and distribution function}
+\begin{example}
+	\label{example:simple_alpha}
+	Let $([2], \ell, \alpha)$ a toll game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha(p) = p + 1$.
+\end{example}
+TODO: Add figure of game graph.
+
+We have $x(0) = (2/3, 1/3)$.
+Then since $\alpha$ is continuous we get from \ref{corollary:split_asymptotic_continuous} that
+\[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_2(0)) = 4/3, \lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0)) = 5/3\]
+Finally, for a more complete picture, we also calculate the max toll difference where $x(t) = (0, 1)$ or $(1, 0)$.
+If $t_1 > t_2$ then $x(t) = (1, 0)$ is impossible since we need $\ell_1(x_1(t)) \le \ell_2(x_2(t))$.
+We have $x(t) = (0, 1)$ when even the player with the least money sensitivity views the two edges' costs as equal, i.e.
+\[
+	\ell_1(0) + \alpha(0) \cdot t_1 = \ell_2(1) + \alpha(0) \cdot t_2 \Rightarrow t_1 - t_2 = 2
+\]
+Respectively, if $t_1 < t_2$ we have $x(t) = (1, 0)$ when
+\[
+	\ell_1(1) + \alpha(0) \cdot t_1 = \ell_2(0) + \alpha(0) \cdot t_2 \Rightarrow t_2 - t_1 = 1
+\]
+
+All the above give us the graph for $\as$ in Figure \ref{figure:split_example}.
+
+TODO: Add figure of $\as$ for different $t_d$.
+
+\section{Upper bound}
+
+Having now a good overview of the overall values $\as$, we notice that there exist values of $\alpha$ that will never be a value of $\as$.
+Do then those values actually affect our game in any way?
+We answer this in the theorem below, which is the main result of this chapter, preceded by a lemma to describe those missing values.
+
+\begin{lemma}
+	\label{lemma:as_upper_bound}
+	Let $([2], \ell, \alpha)$ a toll game with $x_1(0), x_2(0) > 0$.
+	For all $t \in \R_+^2 \setminus \{(a, a) | a \in \R_+\}$, let .
+	It holds that
+	\[\as(t) \le \max\{\sup A_1^-(0), \sup A_2^-(0)\}\]
+	or equivalently if $\alpha$ continuous at $x_1(0)$ and $x_2(0)$
+	\[\as(t) \le \max\{\alpha(x_1(0)), \alpha(x_2(0))\}\]
+\end{lemma}
+
+\begin{proof}
+	 From Lemmas \ref{lemma:split_asymptotic} and \ref{lemma:split_monotonicity} we get that $\as$, for $t_1 - t_2$ in $(-\infty, 0)$ and $(0, +\infty)$, is non-decreasing and non-increasing respectively.
+	 Therefore $\as$ is upper bounded by its sided limits as $t_1 - t_2 \rightarrow 0$, which means that for all $t \in \R_+^2 \setminus \{(a, a) | a \in \R_+\}$ we get
+	 \[\as(t) \le \max\left\{\lim_{t_1 - t_2 \rightarrow 0^-}\as(t), \lim_{t_1 - t_2 \rightarrow 0^+}\as(t)\right\}\]
+	 which in turn after applying Lemma \ref{lemma:split_asymptotic}$(ii)$ becomes
+	 \[\as(t) \le \max\{\sup A_2^-(0), \sup A_1^-(0)\}\]
+\end{proof}
+
+\begin{theorem}
+	\label{theorem:alpha_upper_irrelevant}
+	Let $([2], \ell, \alpha^{(1)})$ and $([2], \ell, \alpha^{(2)})$ two toll games with same latency functions, where $x_1(0), x_2(0) > 0$ for their common flow $x(0)$ and distribution functions $\alpha_1$ and $\alpha_2$ such that $\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p \le \max\{x_1(0), x_2(0)\}$.
+	Then the two games are equivalent.
+\end{theorem}
+
+\begin{proof}
+	For tolls $t \in \R_+^2$ let $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t$ for each game respectively.
+	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \forall t \in \R_+^2$.
+	It's already stated that the equality holds for $t = 0$, i.e. for $t \in \{(a, a) | a \in \R_+\}$.
+	For the remaining $t$, assume w.l.o.g. that $t_1 > t_2$, which now makes it sufficient to show that the flow in the (common) lower split is equal, i.e $x_1^{(1)}(t) \ne x_1^{(2)}(t)$.
+
+	Assume that $x_1^{(1)}(t) \ne x_1^{(2)}(t)$ and again w.l.o.g. that $x_1^{(1)}(t) < x_1^{(2)}(t)$.
+	Then there exists a player $p$ such that $x_1^{(1)}(t) < p \le x_1^{(2)}(t)$ who is on link $2$ on the first game and on link $1$ for the second one.
+	Also note that since $p$ is in the lower split, it holds that $p < \max\{x_1(0), x_2(0)\}$ so by the hypothesis we get $\alpha^{(1)}(p) = \alpha^{(2)}(p)$.
+	With the above we get
+	\[x_1^{(1)}(t) < x_1^{(2)}(t) \Rightarrow x_1^{(1)}(t) + \alpha^{(1)}(p)t_1 < x_1^{(2)}(t) + \alpha^{(2)}(p)t_1 \Rightarrow c_1^{p, (1)}(t) < c_1^{p, (2)}(t)\]
+	and respectively
+	\[x_2^{(1)}(t) > x_2^{(2)}(t) \Rightarrow x_2^{(1)}(t) + \alpha^{(1)}(p)t_2 > x_2^{(2)}(t) + \alpha^{(2)}(p)t_2 \Rightarrow c_2^{p, (1)}(t) > c_2^{p, (2)}(t)\]
+	The above inequations mean that, between the first and the second game, for player $p$, the cost of link $1$ increased while the cost of link $2$ decreased, concluding that $p$ cannot be on link $2$ in the first but then change to link $1$ in the second, which is a contradiction.
+
+	Therefore $x_1^{(1)}(t) = x_1^{(2)}(t)$ for all $t \in \R_+^2 \setminus \{(a, a) | a \in \R_+\}$, and in turn also $x^{(1)}(t) = x^{(2)}(t)$ for all $t \in \R_+$.
+	To conclude, the two games are equivalent.
+\end{proof}
+We can see how this theorem applies to Example \ref{example:simple_alpha}, where since $x(0) = (2/3, 1/3)$ then $\max\{x_1(0), x_2(0)\} = 2/3$.
+Then even if we used a distribution function such as
+\[
+	\alpha(p) =
+	\begin{cases}
+		p + 1 & p \le 2/3 \\
+		p + 10 & p > 2/3
+	\end{cases}
+\]
+then $\as$ would still behave the same way as those $(2/3, 1]$ players will always be in the upper split regardless of their $\alpha$ value.
+
+It will become more apparent later when calculating best responses as even in the pricing games those higher values will never be used.
+We finish this section with a lemma about the behaviour of $\as$ when many players have money sensitivity close to 0.
+Note that it doesn't suffice to assume $\alpha(0) = 0$ as the behavior of that single player has no effect on the game, so we additionally assume that $0$ is an accumulation point in $\alpha$.
+\begin{lemma}
+	If for any $i = 1, 2 \; x_i(0) > 0$ and $\alpha(0) = 0$ with $0$ an accumulation point in $\alpha$, then $x_i(t) > 0, \forall t \in \R_+^2$
+\end{lemma}
+
+\begin{proof}
+	By the definition of an accumulation point, we get for $0$ in $\alpha$ that $\forall \delta > 0 \; \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
+	Therefore $\forall t \in \R_+^2$ if $\delta = \as(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as(t)$, which means that the lower latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t), x_2(t) > 0$.
+\end{proof}
+
+\chapter{Profit maximisation and distribution function}
 

### 2024-09-28 thesis/article.tex
Thesis: Starts Pricing games chapter with 0 sensitivity section, also moves Examples to Appendix

@@
 				\begin{flushleft}
-					\huge{\bf Profit Games in Heterogeneous 2-link Parallel Networks\\}
+					\huge{\bf Pricing Games in Heterogeneous 2-link Parallel Networks\\}
 					\vskip3cm
@@
 
+\cleardoublepage
+
 \chapter{Preliminaries}
@@
 Even though the definition does allow functions that are not upper bounded with $\alpha(1) = +\infty$, we will always assume that $\alpha$ is finite on $[0, 1)$.
-Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Example \ref{example:a_0_0}, allowing many players close to $0$ breaks the pricing game.
+Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Lemma \ref{lemma:a_0_0}, allowing many players close to $0$ breaks the pricing game.
 
@@
 	\label{theorem:alpha_upper_irrelevant}
-	Let $([2], \ell, \alpha^{(1)})$ and $([2], \ell, \alpha^{(2)})$ two toll games with same latency functions, where $x_1(0), x_2(0) > 0$ for their common flow $x(0)$ and distribution functions $\alpha_1$ and $\alpha_2$ such that $\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p \le \max\{x_1(0), x_2(0)\}$.
+	Let $([2], \ell, \alpha^{(1)})$ and $([2], \ell, \alpha^{(2)})$ two toll games with same latency functions, where $x_1(0), x_2(0) > 0$ for their common flow $x(0)$ and distribution functions $\alpha_1$ and $\alpha_2$ such that $\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < \max\{x_1(0), x_2(0)\}$.
 	Then the two games are equivalent.
@@
 
-\chapter{Profit maximisation and distribution function}
+\cleardoublepage
 
-In this section we will examine how different distribution functions $\alpha$ can affect the profit maximisation game between the toll owners.
+\chapter{Equilibria in Pricing Games}
+
+In this section we introduce the pricing game to our model and examine how different distribution functions $\alpha$ can affect the profit maximisation game between the toll owners, specifically when $\alpha$ is fixed, step or continuous.
+We begin, though, with some necessary restrictions.
+
+\section{Problems with $0$ money sensitivity}
+
+In general having players with $\alpha(p) = 0$, i.e. players completely indifferent to tolls, creates issues.
+Even Cole et al. \cite{10.1145/780542.780618} assume $\alpha(p) > 0$ when $p > 0$ for their model to support optimal tolls.
+In fact, this restriction proves necessary for our pricing game as well, since its absence allows distribution functions with arbitrarily small flow all at $0$, which in turn, as we'll see in the following Lemma, breaks the pricing game, too.
+
+\begin{lemma}
+	\label{lemma:a_0_0}
+	Let $([2], \ell, \alpha)$ a pricing game for which it holds that $\exists \epsilon > 0: \alpha(p) = 0 \; \forall p < \epsilon$.
+	Then the best response functions $B_i(t_{-i})$ are unbounded.
+\end{lemma}
+
+\begin{proof}
+	All players $p$ with $\alpha(p) = 0$ will completely neglect the toll values and play the congestion game only considering the flow latencies, thus always selecting the fastest edge, regardless of the toll prices.
+
+	We have from assumption that $x_i(0) > 0$.
+	Consider $x_i^\prime = \min\{x_i(0), \epsilon\} > 0$.
+	Obviously $\alpha(p) = 0 \; \forall p < x_i$.
+	Then we can see that for all $t_i > t_{-i}$ where edge $i$ has the lower latency edge, all those players will be on that edge and will remain so regardless of how high is the value of $t_i$.
+	For the respective profit that means $\Pi_i(t_i, t_{-i}) \ge x_i t_i \; \forall t_i > t_{-i}$.
+	Consequently, as $t_i \rightarrow +\infty$ then so does $x_i t_i$ and $\Pi_i(t_i, t_{-i})$, making in turn $B_i(t_{-i}) \rightarrow +\infty$.
+\end{proof}
+We therefore need the restriction of $\alpha(p) > 0$ when $p > 0$ in order for our pricing game to have an equilibrium.
+
+\section{Fixed distribution function}
+
+\section{Step distribution function}
+
+\section{Continuous distribution function}
+
+For the continuous distribution function case, the previous restriction of $\alpha(p) > 0$ when $p > 0$ is not sufficient, as it still allows for distribution functions with many player values close to $0$ < Is that actually the problem?.
+Specifically the case of $\alpha(p) = cp$, for some $c > 0$, shows some interesting behavior, as it creates instances where $\Pi_i$ becomes either unbounded or fixed; in the first case then $B_i$ becomes unbounded, while in the second it becomes an an infinite set.
+This is showcased analytically in Example \ref{example:ap_p} in the Appendix, where for $\alpha(p) = p$ we see that the resulting best responses can indeed be undefined or unbounded.
+
+When does this happen?
+Is the problem $0$ being an accumulation point?
+\begin{lemma}[Conjecture]
+	If a distribution function has $\alpha(p) \le p \; \forall p$, then $\Pi_i$ becomes either unbounded or fixed.
+\end{lemma}
+
+We will avoid all the above bad behaviors by assuming in all further cases that $\alpha(0) > 0$.
+
+\cleardoublepage
+
+\chapter{Future work}
+
+\cleardoublepage
+
+\phantomsection
+\addcontentsline{toc}{chapter}{Bibliography}
+\bibliographystyle{plain}
+\bibliography{ref.bib}
+\cleardoublepage
+
+\phantomsection
+\addcontentsline{toc}{chapter}{Appendix}
+\chapter*{Appendix}
+
 [TODO: add framework for examining games]
-We will restrict our analysis on distribution functions such that $\alpha(0) > 0$, the reason being that we want to avoid two instances.
-The first is to ensure that $\alpha(p) > 0$ when $p > 0$, while the second is that $0$ is not an accumulation point.
-[TODO: maybe mention \cite{10.1145/780542.780618} where they also take the first restriction as it creates games with no optimal tolls]
-The following two examples demonstrate the issues that might occur if these restrictions are not met.
 
 \begin{example}
-	\label{example:a_0_0}
-	Consider a $2$-link parallel network pricing game with distribution function $\alpha$ for which it does not hold that $\alpha(p) > 0$ when $p > 0$.
-\end{example}
-
-The property not holding for $\alpha$ means that $\exists x_\epsilon > 0 : \alpha(x_\epsilon) = 0 \forall p < x_\epsilon$.
-That $x_\epsilon$ flow will completely neglect the tolls and play the congestion game only considering the flow latency, therefore they will always select the fastest edge regardless of the toll price.
-This in turn means that any toll owner can exploit it and set their toll to an arbitrary high value $T$ which will force all players with $\alpha(p) > 0$ to leave, thus making their own edge the fastest one.
-Even if the edge has a latency function with a high increasing rate, there will be at least a small flow $x_{\epsilon^\prime} \le x_\epsilon$ on that edge.
-Therefore the owner can achieve any arbitrary profit $P$ by setting their toll price as $T + P/\epsilon$.
-Since both player have that strategy available, we conclude that no equilibrium exists in the pricing game.
-
-\begin{example}
-	\label{example:a_0_ap}
+	\label{example:ap_p}
 	Consider a $2$-link parallel network pricing game with $l_1(x) = x, l_2(x) = 2x$ and distribution function $\alpha(p) = p$.
@@
 \paragraph{The bad behaviors} are obviously having divergent or undefined best response functions, which we claim occur only when we allow $0$ to be an accumulation point in $\alpha$, since this allows players with arbitrarily low money-sensitivity to always stay on the expensive edge.
-Assume that in Example $\ref{example:a_0_ap}$ we use $\alpha(p) = p + 1$ as a distribution function.
+Assume that in Example $\ref{example:ap_p}$ we use $\alpha(p) = p + 1$ as a distribution function.
 Then we get the following best response functions
@@
 
-\subparagraph{Combining} $B_1^>(t_2), B_1^<(t_2)$ and $B_2^>(t_1), B_2^<(t_1)$ the same way as in Example $\ref{example:a_0_ap}$ we get the final best response functions.
+\subparagraph{Combining} $B_1^>(t_2), B_1^<(t_2)$ and $B_2^>(t_1), B_2^<(t_1)$ the same way as in Example $\ref{example:ap_p}$ we get the final best response functions.
 \begin{equation*}
@@
 
-\section{Equilibrium}
-
-In this section we will show that if the distribution function has the following properties
-\begin{itemize}
-	\item $\alpha(0) > 0$
-	\item $\alpha$ is onto
-\end{itemize}
-Then a $\NE$ for the pricing game exists ???
-
-\cleardoublepage
-\phantomsection
-\addcontentsline{toc}{chapter}{Bibliography}
-
-\bibliographystyle{plain}
-\bibliography{ref.bib}
-
 \end{document}

### 2024-09-28 thesis/article.tex
Thesis: Adds in Pricing Games basics for fixed dist func case

@@
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\Gm}{\mathcal{G}}
 \DeclareMathOperator*{\argmax}{arg\,max}
@@
 
+For the case where the distribution function of our model is fixed, i.e.
+$\alpha(p) = c$ for some $c > 0$, then the game becomes homogeneous again, simply with a different -common- sensitivity to tolls.
+However, what interests us in this study is the relation between games for different $c > 0$, as it will prove crucial when analysing step distribution functions later.
+We start with formalising our base.
+
+\begin{lemma}
+	\label{lemma:a_fixed_base}
+	Let $\Gm_1 = ([2], \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = ([2], \ell^{(1)} / c, 1)$ a homogeneous pricing game with latencies $\ell^{(1)} / c$ for the same $c$.
+	Then the two games are equivalent.
+\end{lemma}
+
+\begin{proof}
+	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^2 \cup \{0\}$, where $x^{(1)}(t), x^{(2)}(t)$ the respective Nash Equilibrium for $t$ for $\Gm_1, \Gm_2$.
+	Begin by noticing that while $\Gm_1$ is heterogeneous, all its players have the same money sensitivity, and thus at an equilibrium they will all see the two edges as the same.
+	Therefore for all $t \in \R_+ \cup \{0\}$, $x^{(1)}(t)$ is the unique solution of the equation
+	\[
+		\ell_1^{(1)}(x_1^{(1)}(t)) + ct_1 = \ell_2^{(1)}(x_2^{(1)}(t)) + ct_2
+	\]
+	It is easy to check now that $x^{(2)}(t)$ is also a solution to the above equation, since in $\Gm_2$ it is the equivalent unique solution for
+	\[
+		\ell_1^{(1)}(x_1^{(2)}(t)) / c = \ell_2^{(1)}(x_2^{(2)}(t)) / c \Leftrightarrow \ell_1^{(1)}(x_1^{(2)}(t)) = \ell_2^{(1)}(x_2^{(2)}(t)) 
+	\]
+	Therefore $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^2 \cup \{0\}$, making $\Gm_1, \Gm_2$ equivalent.
+\end{proof}
+Intuitively, the above means that increasing the money sensitivity of the players in equivalent to analogously decreasing the traffic that flows create on all edges.
+Unfortunately this correspondence  disappears for non-fixed distribution functions, since, as we saw in Chapter 2, we loose the $1-1$ relation between the latency functions and the distribution function due to heterogeneity.
+
+Still, looking now at the relation between fixed distribution functions, Lemma \ref{lemma:a_fixed_base} gives us the following corollary.
+\begin{corollary}
+		Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
+		Then the following are true
+		\begin{enumerate}[$(i)$]
+			\item $x^{(1)}(0) = x^{(2)}(0)$
+			\item $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)$
+			\item $\Pi_i^{(1)}(t_i, t_{-i}) = \frac{c_2}{c_1} \cdot \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right)$
+			\item $B_i^{(1)}(t_{-i}) = \frac{c_2}{c_1} \cdot B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right)$
+		\end{enumerate}
+\end{corollary}
+
+\begin{proof}
+	$ $
+	\begin{enumerate}[$(i)$]
+		\item Obvious since for $t = 0$ the flow in both $\Gm_1, \Gm_2$ play a homogeneous game with common latencies $\ell$, which makes the two games identical and therefore $x^{(1)}(0) = x^{(2)}(0)$.
+		\item With the same rational as in Lemma \ref{lemma:a_fixed_base}, looking at the respective cost equalities for the two games we see that starting from $\Gm_2$ for tolls $(c_1 / c_2)t$ we get
+		\begin{flalign*}
+			\ell_1&\left(x_1^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)\right) + c_2 \cdot \left(\frac{c_1}{c_2} \cdot t_1\right) = \ell_2\left(x_2^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)\right) + c_2 \cdot \left(\frac{c_1}{c_2} \cdot t_2\right) & \\
+			&\Rightarrow \ell_1\left(x_1^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)\right) + c_1 t_1 = \ell_2\left(x_2^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)\right) + c_1 t_2 &
+		\end{flalign*}
+		with the last equation being the one for edge equality in $\Gm_1$ with a unique solution at $x^{(1)}(t)$, leading us to $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)$
+		\item From $(ii)$ and the definition of $\Pi_i$ we get
+		\begin{flalign*}
+			\Pi_i^{(1)}(t_i, t_{-i}) &= x_i^{(1)}(t) \cdot t_i \stackrel{(ii)}{=} x_i^{(2)}\left(\frac{c_1}{c_2} \cdot t\right) \cdot t_i & \\
+			&= \frac{c_2}{c_1} \cdot \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) &
+		\end{flalign*}
+		\item From $(iii)$ and the definition of $B_i$ we get
+		\begin{flalign*}
+			B_i^{(1)}(t_{-i}) &= \argmax_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) \stackrel{(iii)}{=} \argmax_{t_i > 0}\frac{c_2}{c_1} \cdot \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) & \\
+			&= \frac{c_2}{c_1} \cdot B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right) &
+		\end{flalign*}
+	\end{enumerate}
+\end{proof}
+
+While the above properties seem straightforward, they are of little use to us as they are.
+What we actually need to examine is how those two games react differently for an edge $i$ given a fixed $t_{-i}$.
+
 \section{Step distribution function}

### 2024-10-01 thesis/article.tex
Thesis: Finishes fixed dist func main theory in Pricing Games, 2 proofs pending

@@
 \begin{equation}
+	\label{eq:x_i}
 	x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
@@
 When discussing properties of the model where the pricing game is not relevant, we will refer to a $([2], \ell, \alpha)$ instance as a toll game, and otherwise as a pricing game.
+We finish this section with a crucial property for homogeneous pricing games that we will need later.
+TODO: This property probably exists as a general theorem in convex programming or something, maybe with non-decreasing property instead of decreasing.
+Until then, we prove it analytically for affine latencies.
+
+\begin{lemma}
+	\label{lemma:tolls_diff}
+	Let $([2], \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$.
+	Then $D_i$ is decreasing for all links $i$.
+\end{lemma}
+
+\begin{proof}
+	From equation \ref{eq:x_i} for $2$ links we get
+	\[
+		x_i(t) = \frac{1 + \frac{b_{-i} + t_{-i} - b_i - t_i}{a_{-i}}}{\frac{a_i}{a_{-i}}} = \frac{a_{-i} + b_{-i} + t_{-i} - b_i - t_i}{a_i}
+	\]
+	from which by following the definitions and from first order conditions for quadratic functions we get
+	\[
+		B_i(t_{-i}) = \argmax_{t_i > 0}x_i(t) \cdot t_i = \frac{a_{-i} + b_{-i} + t_{-i} - b_i}{2}
+	\]
+	Finally
+	\[
+		D_i(t_{-i}) = -\frac{1}{2}t_{-i} + \frac{a_{-i} + b_{-i} - b_i}{2}
+	\]
+	which is obviously decreasing.
+\end{proof}
 
@@
 \begin{lemma}
-	\label{lemma:a_fixed_base}
+	\label{lemma:a_fixed_homogeneous}
 	Let $\Gm_1 = ([2], \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = ([2], \ell^{(1)} / c, 1)$ a homogeneous pricing game with latencies $\ell^{(1)} / c$ for the same $c$.
@@
 
-Still, looking now at the relation between fixed distribution functions, Lemma \ref{lemma:a_fixed_base} gives us the following corollary.
+Still, looking now at the relation between fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} gives us the following corollary.
 \begin{corollary}
-		Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
+	\label{corollary:a_fixed_c_relation}
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
 	Then the following are true
 	\begin{enumerate}[$(i)$]
-			\item $x^{(1)}(0) = x^{(2)}(0)$
+		%\item $x^{(1)}(0) = x^{(2)}(0)$
 		\item $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)$
-			\item $\Pi_i^{(1)}(t_i, t_{-i}) = \frac{c_2}{c_1} \cdot \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right)$
-			\item $B_i^{(1)}(t_{-i}) = \frac{c_2}{c_1} \cdot B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right)$
+		\item $\frac{c_1}{c_2} \cdot \Pi_i^{(1)}(t_i, t_{-i}) = \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right)$
+		\item $\frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i}) = B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right)$
 	\end{enumerate}
@@
 	\begin{enumerate}[$(i)$]
-		\item Obvious since for $t = 0$ the flow in both $\Gm_1, \Gm_2$ play a homogeneous game with common latencies $\ell$, which makes the two games identical and therefore $x^{(1)}(0) = x^{(2)}(0)$.
-		\item With the same rational as in Lemma \ref{lemma:a_fixed_base}, looking at the respective cost equalities for the two games we see that starting from $\Gm_2$ for tolls $(c_1 / c_2)t$ we get
+		%\item Obvious since for $t = 0$ the flow in both $\Gm_1, \Gm_2$ play a homogeneous game with common latencies $\ell$, which makes the two games identical and therefore $x^{(1)}(0) = x^{(2)}(0)$.
+		\item With the same rational as in Lemma \ref{lemma:a_fixed_homogeneous}, looking at the respective cost equalities for the two games we see that starting from $\Gm_2$ for tolls $(c_1 / c_2)t$ we get
 		\begin{flalign*}
@@
 		\begin{flalign*}
-			\Pi_i^{(1)}(t_i, t_{-i}) &= x_i^{(1)}(t) \cdot t_i \stackrel{(ii)}{=} x_i^{(2)}\left(\frac{c_1}{c_2} \cdot t\right) \cdot t_i & \\
-			&= \frac{c_2}{c_1} \cdot \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) &
+			\frac{c_1}{c_2} \cdot \Pi_i^{(1)}(t_i, t_{-i}) &= \frac{c_1}{c_2} \cdot x_i^{(1)}(t) \cdot t_i \stackrel{(ii)}{=} \cdot x_i^{(2)}\left(\frac{c_1}{c_2} \cdot t\right) \cdot \left(\frac{c_1}{c_2} \cdot t_i\right) & \\
+			&= \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) &
 		\end{flalign*}
@@
 		\begin{flalign*}
-			B_i^{(1)}(t_{-i}) &= \argmax_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) \stackrel{(iii)}{=} \argmax_{t_i > 0}\frac{c_2}{c_1} \cdot \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) & \\
-			&= \frac{c_2}{c_1} \cdot B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right) &
+			\frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i}) &= \frac{c_1}{c_2} \cdot \argmax_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) \stackrel{(iii)}{=} \argmax_{t_i > 0}\Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) & \\
+			&= B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right) &
 		\end{flalign*}
@@
 What we actually need to examine is how those two games react differently for an edge $i$ given a fixed $t_{-i}$.
+For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference, which is in turn non-increasing with regards to $t_{-i}$ (\ref{lemma:tolls_diff}).
+Therefore, as $t_{-i}$ increases, the best response gets decreasing difference with $t_{-i}$, thus taking more flow in $x_i$.
+Eventually there will be a smallest possible $t_{-i}$ where the best response is to take all flow, and henceforth any larger $t_{-i}$ will also result in a best response with the same toll difference and flow.
+We will use this property to describe the flow relation between the two games in the following lemma.
+
+\begin{lemma}
+	\label{lemma:a_fixed_t_iM_fixed}
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
+	Also let $t_{-i_M}^{(1)}, t_{-i_M}^{(2)}$ the smallest possible $t_{-i}$ where $x_i(B_i(t_{-i}), t_{-i}) = 1$, respectively for each game.
+	Then the following hold.
+	\begin{enumerate}[$(i)$]
+		\item $t_{-i_M}^{(2)} < t_{-i_M}^{(1)}$
+		\item $x_i^{(1)}(B_i^{(1)}(0), 0) = x_i^{(2)}(B_i^{(2)}(0), 0)$
+		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) = x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i}) = 1$ for all $t_{-i} \ge t_{-i_M}^{(1)}$
+		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) < x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})$, for all $t_{-i} \in (0, t_{-i_M}^{(1)})$
+		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}), x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})$ get max distance at $t_{-i_M}^{(2)}$ \\
+		\textit{(conjecture)}
+	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	$ $
+	\begin{enumerate}[$(i)$]
+		\item Assume $t_{-i_M}^{(2)} \ge t_{-i_M}^{(1)}$.
+		Then from Corollary \ref{corollary:a_fixed_c_relation} we get
+		\begin{flalign*}
+			1 = &x_i^{(1)}(B_i^{(1)}(t_{-i_M}^{(1)}), t_{-i_M}^{(1)}) = x_i^{(2)}\left( \frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i_M}^{(1)}), \frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right) & \\
+			&= x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right), \frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right) &
+		\end{flalign*}
+		which is a contradiction since $\frac{c_1}{c_2} t_{-i_M}^{(1)} < t_{-i_M}^{(1)} \le t_{-i_M}^{(2)}$ and $t_{-i_M}^{(2)}$ is the smallest value with that property.
+		Therefore the initial assumption is wrong and we get $t_{-i_M}^{(2)} < t_{-i_M}^{(1)}$.
+		\item With application of Corollary \ref{corollary:a_fixed_c_relation} we have
+		\[
+			x_i^{(1)}(B_i^{(1)}(0), 0) = x_i^{(2)}\left(\frac{c_1}{c_2} \cdot B_i^{(1)}(0), 0\right) = x_i^{(2)}(B_i^{(2)}(0), 0)
+		\]
+		\item Since from $(i)$ we have $t_{-i_M}^{(1)} = \max\{t_{-i_M}^{(1)}, t_{-i_M}^{(2)}\}$ then the property follows from the definitions of $t_{-i_M}^{(1)}, t_{-i_M}^{(2)}$.
+		\item For $t_{-i} \in (t_{-i_M}^{(2)}, t_{-i_M}^{(1)})$ obviously
+		\[
+			x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) < 1 = x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})
+		\]
+		Then for $t_{-i} \in (0, t_{-i_M}^{(2)})$ with the same way we used Corollary \ref{corollary:a_fixed_c_relation} as in $(i)$ we see that
+		\[
+			x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) = x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right), \frac{c_1}{c_2} \cdot t_{-i}\right)
+		\]
+		where the second part is the flow in $\Gm_2$ at the best response of link owner $i$ against $\frac{c_1}{c_2} t_{-i}$.
+		Therefore their best response against $t_{-i} > \frac{c_1}{c_2} t_{-i}$ will have a lower toll difference to $t_{-i}$ (\ref{lemma:tolls_diff}) and thus more flow, arriving at
+		\[
+			x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right), \frac{c_1}{c_2} \cdot t_{-i}\right) < x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})
+		\]
+	\end{enumerate}
+\end{proof}
+
+%\begin{lemma}
+%	\label{lemma:a_fixed_x12}
+%	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
+%	Then the following hold.
+%	\begin{enumerate}[$(i)$]
+%		\item $x^{(1)}(0) = x^{(2)}(0)$
+%		\item $x_i^{(1)}(t) - x_i^{(2)}(t)$ is non-decreasing in relation to $t_i - t_{-i}$
+%	\end{enumerate}
+%\end{lemma}
+%Notice that the above Lemma also provides us with $x_i^{(1)}(t) < x_i^{(2)}(t)$ iff $t_i < t_{-i}$ and vice versa, as well as that this difference is expanded as $t_i - t_{-i}$ does.
+%We avoided using the affinity of the latency functions on purpose to get a more general notion between the two games.
+%Using latency functions now, we can get a calculated version of the above.
+%\begin{corollary}
+%	\label{lemma:a_fixed_x12_calc}
+%	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same affine latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
+%	Then for some fixed number $K_i > 0$ it holds that
+%	\[x_i^{(1)}(t) - x_i^{(2)}(t) = K_i \cdot (t_i - t_{-i})\]
+%\end{corollary}
+%
+%\begin{proof}
+%	From equation \ref{eq:x_i} for $2$ links and under universal sensitivity $c_1, c_2$ respectively we get
+%	\begin{align*}
+%		x_i^{(1)}(t) - x_i^{(2)}(t) &= \frac{a_{-i} + b_{-i} + c_1t_{-i} - b_i - c_1t_i}{a_i} - \frac{a_{-i} + b_{-i} + c_2t_{-i} - b_i - c_2t_i}{a_i} \\
+%		&= \frac{(c_2 - c_1)(t_i - t_{-i})}{a_i}
+%	\end{align*}
+%	So the property holds for $K_i = \frac{c_2 - c_1}{a_i} > 0$.
+%\end{proof}
+
+We finally arrive at the main theorem of this section, which describes similar properties for the relative behaviour of the profit functions between the two games.
+Fist, let's remind ourselves that from Lemma \ref{lemma:tolls_diff} for each game $B_i(t_{-i}) - t_{-i}$ is decreasing as well as continuous.
+Therefore, given that best responses range from above and below $t_{-i}$ values, there exists some $t_{-i_0}$ for which $B_i(t_{-i_0}) = t_{-i_0}$.
+We state now our theorem.
+
+\begin{theorem}
+	\label{theorem:a_fixed_t_i0}
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
+	Also let $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ the respective tolls for which $B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)}$ and $B_i^{(1)}(t_{-i_0}^{(2)}) = t_{-i_0}^{(2)}$.
+	Then for all links $i$ it holds that
+	\begin{enumerate}[$(i)$]
+		\item $t_{-i_0}^{(1)} > t_{-i_0}^{(2)}$
+		\item There exists $t_{-i_0} \in \left(t_{-i_0}^{(2)}, t_{-i_0}^{(1)}\right)$ such that
+		\[\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}) = \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0})\]
+		\item $\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$ is non-increasing in relation to $t_{-i}$.
+		\item $t_{-i_0}$ is the geometric mean of $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$
+	\end{enumerate}
+\end{theorem}
+
+\begin{proof}
+	$ $
+	\begin{enumerate}[$(i)$]
+		\item From Corollary \ref{corollary:a_fixed_c_relation}$(iii)$ we get
+		\[
+			B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)} \Rightarrow B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i_0}^{(1)}\right) = \frac{c_1}{c_2} \cdot t_{-i_0}^{(1)}
+		\]
+		and from the fact that $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ are the unique solutions of their respective equations we get $t_{-i_0}^{(2)} = \frac{c_1}{c_2} \cdot t_{-i_0}^{(1)} < t_{-i_0}^{(1)}$.
+		\item Consider the function $\Pi_i(t_{-i}) = \max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$.
+		Then for $t_{-i} = t_{-i_0}^{(2)}$ we see that in $\Gm_2$ the best response for link owner $i$ is to play the same toll as in the other link, therefore they get max profit at $x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$.
+		In $\Gm_1$ now, since $t_{-i_0}^{(2)} < t_{-i_0}^{(1)}$ then the best response for link owner $i$ is for some $t_i > t_{-i_0}^{(2)}$, and since from \ref{corollary:a_fixed_c_relation}$(i)$ the profit $x_i^{(1)}(0) = x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$ is also one of their options, it means that the profit at $t_i$ is greater, i.e.
+		\[
+			\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}^{(2)}) > \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0}^{(2)}) \Rightarrow \Pi_i(t_{-i_0}^{(2)}) > 0
+		\]
+		Similarly we can show that $\Pi_i(t_{-i_0}^{(1)}) < 0$.
+		With all the above and given that we know from the analysis in Harkes et al.
+\cite{Harks_2019} that best response functions are continuous, from the Bolzano theorem (TODO: Is this the right theorem?
+Reference?) we get that there exists $t_{-i_0} \in \left(t_{-i_0}^{(2)}, t_{-i_0}^{(1)}\right)$ such that $\Pi_i(t_{-i_0}) = 0$, which gives us the desired proposition.
+		\item We will use the same $\Pi_i$ function as in $(ii)$, so we instead need to show that $\Pi_i(t_{-i})$ is non-decreasing in relation to $t_{-i}$.
+		For all $t_{-i} \ge t_{-i_M}^{(1)}$ from Lemma \ref{lemma:a_fixed_t_iM_fixed} we get $\Pi_i(t_{-i}) = 1 \cdot B_i^{(1)}(t_{-i}) - 1 \cdot B_i^{(2)}(t_{-i})$, where the best responses have fixed differences to $t_{-i}$ (and therefore to each other as well), making $\Pi_i(t_{-i})$ in turn fixed for all $t_{-i} \ge t_{-i_M}^{(1)}$.
+		TODO: Pending.
+		\item By using the $B_i(t_{-i})$ formula to find $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ and then solve $\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}) = \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0})$.
+		TODO: Either replace with a theoretical proof or write the calculations.
+	\end{enumerate}
+\end{proof}
+
+Finally, we can again calculate $t_{-i_0}$ using the closed formulas provided by the affine assumption.
+
+\begin{corollary}
+	\label{corollary:a_fixed_ti0_calc}
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
+	Then for $t_{-i_0}$ defined in Theorem \ref{theorem:a_fixed_t_i0} for the two games it holds that
+	\[t_{-i_0} = \frac{a_{-i} + b_{-i} - b_i}{\sqrt{c_1 c_2}}\]
+\end{corollary}
+
+\begin{proof}
+	We can easily calculate $t_{-i_0}^{(1)}$ and $t_{-i_0}^{(2)}$.
+	For $\Gm_1$ we have
+	\[B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)} \Rightarrow \frac{a_{-i} + b_{-i} - b_i + c_1 t_{-i_0}^{(1)}}{2 c_1} = t_{-i_0}^{(1)} \Rightarrow t_{-i_0}^{(1)} = \frac{a_{-i} + b_{-i} - b_i}{c_1}\]
+	Similarly for $\Gm_2$ we have $t_{-i_0}^{(2)} = \frac{a_{-i} + b_{-i} - b_i}{c_2}$, so finally from Theorem \ref{theorem:a_fixed_t_i0}$(iv)$ we get
+	\[t_{-i_0} = \sqrt{t_{-i_0}^{(1)} \cdot t_{-i_0}^{(2)}} = \frac{a_{-i} + b_{-i} - b_i}{\sqrt{c_1 c_2}}\]
+\end{proof}
+We have now gathered all necessary tools to start investigating step distribution functions.
 
@@
 \chapter{Future work}
+
+A natural extension of the above would be to examine them for $[N]$ parallel graphs.
+Some of the properties naturally extend but for others more care is required.
+Special notice and expansion is certainly necessary for the split function, as it is only defined for two edges.
+On a first thought, it seems trivial to also order the edges on an equilibrium by latency and then define the split function on each consecutive pair, therefore also having an ordered set of split function values.
+Still, more investigation is needed to uncover the relation between those values, and its consequences to the flow's or the pricing game's behaviours.
+
+Putting the pricing games aside, it would also be interesting to expand the split function for series-parallel graphs.
 

### 2024-10-04 thesis/article.tex
Thesis: Adds step dist func in Pricing Games
Draft #2

@@
 	Consider $x_i^\prime = \min\{x_i(0), \epsilon\} > 0$.
-	Obviously $\alpha(p) = 0 \; \forall p < x_i$.
+	Obviously $\alpha(p) = 0 \; \forall p < x_i^\prime$.
 	Then we can see that for all $t_i > t_{-i}$ where edge $i$ has the lower latency edge, all those players will be on that edge and will remain so regardless of how high is the value of $t_i$.
@@
 	\label{lemma:a_fixed_homogeneous}
-	Let $\Gm_1 = ([2], \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = ([2], \ell^{(1)} / c, 1)$ a homogeneous pricing game with latencies $\ell^{(1)} / c$ for the same $c$.
+	Let $\Gm_1 = ([2], \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = ([2], \frac{\ell^{(1)}}{c}, 1)$ a homogeneous pricing game with latencies $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
 	Then the two games are equivalent.
@@
 	\[
-		\ell_1^{(1)}(x_1^{(2)}(t)) / c = \ell_2^{(1)}(x_2^{(2)}(t)) / c \Leftrightarrow \ell_1^{(1)}(x_1^{(2)}(t)) = \ell_2^{(1)}(x_2^{(2)}(t)) 
+		\frac{\ell_1^{(1)}(x_1^{(2)}(t))}{c} + t_1 = \frac{\ell_2^{(1)}(x_2^{(2)}(t))}{c} + t_2 \Leftrightarrow \ell_1^{(2)}(x_1^{(2)}(t)) + t_1 = \ell_2^{(2)}(x_2^{(2)}(t)) + t_2
 	\]
@@
 		with the last equation being the one for edge equality in $\Gm_1$ with a unique solution at $x^{(1)}(t)$, leading us to $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)$
-		\item From $(ii)$ and the definition of $\Pi_i$ we get
+		\item From $(i)$ and the definition of $\Pi_i$ we get
 		\begin{flalign*}
-			\frac{c_1}{c_2} \cdot \Pi_i^{(1)}(t_i, t_{-i}) &= \frac{c_1}{c_2} \cdot x_i^{(1)}(t) \cdot t_i \stackrel{(ii)}{=} \cdot x_i^{(2)}\left(\frac{c_1}{c_2} \cdot t\right) \cdot \left(\frac{c_1}{c_2} \cdot t_i\right) & \\
+			\frac{c_1}{c_2} \cdot \Pi_i^{(1)}(t_i, t_{-i}) &= \frac{c_1}{c_2} \cdot x_i^{(1)}(t) \cdot t_i \stackrel{(i)}{=} x_i^{(2)}\left(\frac{c_1}{c_2} \cdot t\right) \cdot \left(\frac{c_1}{c_2} \cdot t_i\right) & \\
 			&= \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) &
 		\end{flalign*}
-		\item From $(iii)$ and the definition of $B_i$ we get
+		\item From $(ii)$ and the definition of $B_i$ we get
 		\begin{flalign*}
-			\frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i}) &= \frac{c_1}{c_2} \cdot \argmax_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) \stackrel{(iii)}{=} \argmax_{t_i > 0}\Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) & \\
+			\frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i}) &= \frac{c_1}{c_2} \cdot \argmax_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) \stackrel{(ii)}{=} \argmax_{t_i > 0}\Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) & \\
 			&= B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right) &
@@
 
-While the above properties seem straightforward, they are of little use to us as they are.
-What we actually need to examine is how those two games react differently for an edge $i$ given a fixed $t_{-i}$.
+What we need to examine  next is how those two games react differently for an edge $i$ given a fixed $t_{-i}$.
 For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference, which is in turn non-increasing with regards to $t_{-i}$ (\ref{lemma:tolls_diff}).
@@
 
+Moving now to actual heterogeneous games, we will examine how the pricing game behaves when the distribution function is a step function, i.e. it takes finitely many values.
+There will be a strong connection with the fixed distribution function games we studied earlier, and that connection extends beyond the step function, which is why we will prove it here for any distribution function.
+
+\begin{lemma}
+	\label{lemma:heterogenous_flow_equiv_fixed}
+	Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls and $x^{(1)}(t)$ the Nash equilibrium for $t$.
+	Now let $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
+	Then $x^{(1)}(t) = x^{(2)}(t)$.
+\end{lemma}
+
+\begin{proof}
+	From definition, $\as^{(1)}(t)$ is the value for which any player that has such $\alpha^{(1)}$ value will view the two edge costs as equal.
+	Then, since the latency functions are the same between $\Gm_1, \Gm_2$, we get $x^{(1)}(t) = x^{(2)}(t)$, and since all players have money sensitivity $\as^{(1)}(t)$, they will all view the two edges equally with no one wishing to change.
+	We conclude that $x^{(1)}(t)$ is a Nash equilibrium for $t$ in $\Gm_2$ as well.
+\end{proof}
+
+\begin{corollary}
+	\label{corollary:heterogenous_profit_equiv_fixed}
+	Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls, $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
+	Then for each link owner $i$ it holds that $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$.
+\end{corollary}
+
+\begin{proof}
+	Natural conclusion from Lemma \ref{lemma:heterogenous_flow_equiv_fixed} and the definition of $\Pi_i$.
+\end{proof}
+
+For a game with step distribution function in particular, the above mean that we can "slice" its flow and respective profit depending on the money sensitivity of each flow section, and apply the properties we investigated earlier on fixed distribution function games.
+Combining it with the discussion around the values of $\as$ for different tolls, especially Theorem \ref{theorem:alpha_upper_irrelevant}, we can see that the game is played among a subset of $\alpha$ values, mirrored around the lower and upper splits.
+We visualise this idea in the following example.
+
+\begin{example}
+	\label{example:a_step_simple}
+	Let $([2], \ell, \alpha)$ be a heterogeneous pricing game where
+	\begin{align*}
+		\begin{aligned}
+			\ell_1 &= x + 1 \\
+			\ell_2 &= 2x
+		\end{aligned}
+		\qquad
+		\alpha(p) =
+		\begin{cases}
+			1 & p \le 1 / 5 \\
+			3 & p > 0
+		\end{cases}&
+	\end{align*}
+	TODO: Add flow and profit plots for a fixed $t_{-i}$.
+	In each case include all flow/profit for the game with $\alpha(p) = 1, 3$ and make bold the sub-intervals that are relevant.
+\end{example}
+
+In order to be able to describe the different profits on the different intervals of the step function, we introduce a definition of profit for a link owner within a flow section.
+
+\begin{definition}
+	\label{definition:profit_interval}
+	Let $([2], \ell, \alpha)$ be a heterogeneous pricing game.
+	For a flow interval $[a, b] \subset [0, 1]$ and a link owner $i$, we define the \textit{profit in $[a, b]$} $\Pi_{i, [a, b]}$ as the toll that maximises the link owner's profit against the opposing toll $t_{-i}$, with the flow $x_i(t)$ being within $[a, b]$.
+	More formally
+	\[
+		\Pi_{i, [a, b]}(t_{-i}) = \max_{\stackrel{t_i > 0}{x_i(t_i, t_{-i}) \in [a, b]}}\Pi_i(t_i, t_{-i})
+	\]
+	%from which we also get
+	%\[B_i(t_{-i}) = \argmax_{t_i > 0} \cup_{\forall [a, b] \subset [0, 1]}\Pi_{i, [a, b]}(t_{-i})\]
+\end{definition}
+
+From this definition it naturally follows that the best response of a link owner $i$ given $t_{-i}$ depends on the max profit value over any set of intervals that completely cover $[0, 1]$.
+For step distribution functions, this set can be the domains of each of its finitely different values $\alpha_1 < \ldots < \alpha_m$.
+As such $\forall k \in [m]$ we denote as $A_k$ the closed set of all players $p$ in $[0, 1]$ for whom $\alpha(p) = \alpha_k$.
+Obviously $\cup_{k=1}^m A_k = [0, 1]$ and from the assumption that $\alpha$ is non-decreasing we also get $A_k$ convex $\forall k \in [m]$.
+When looking at the flow (and consequently profit) of a specific link $i$, however, the split behaviour of the distribution function makes it possible for different flows having the same money sensitivity split.
+We will therefore use the money sensitivity split function to refer to the respective flows that follow it, and formalise the profit and respective best response of link owner $i$ in the following definition.
+
+\begin{definition}
+	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function and $(A_k)_{k \in [m]}$ the partition of $[0, 1]$ that is defined by the domain of $\alpha$.
+	Then for link owner $i$ the definition of $\Pi_i$ is extended for an interval $A_k$ as
+	\[
+		\Pi_{i, k}(t_{-i}) = \max_{\stackrel{t_i > 0}{\as(t_i, t_{-i}) = \alpha_k}}\Pi_i(t_i, t_{-i})
+	\]
+\end{definition}
+
+When it comes to maximising profit for the pricing games, those values included in all $\Pi_{i, k}$ are all we need, because if $\as(t)$ takes any other in-between value, then we are on an instance where no player views the two edge costs as equal, with players viewing a purely smaller cost in either edge.
+For the link owners, this means there at least one who can increase their toll and still keep the flow the same, achieving pure profit.
+This can also happen in edge cases of $\as(t) = \alpha_k$, so we move our full description of this behavior in the following lemma.
+
+\begin{lemma}
+	\label{lemma:a_step_gaps}
+	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
+	If $t^\prime$ a set of tolls in the closure of $T_{-\alpha} = \{t | \as(t) \ne \alpha_k \; \forall k \in [m]\}$, then $t^\prime$ is not a Nash equilibrium for the pricing game.
+\end{lemma}
+
+\begin{proof}
+	It suffices to show that there exists link owner $i$ such that $B_i(t_{-i}^\prime) \ne t_i$.
+	First, notice that from \ref{lemma:split_basic} and \ref{theorem:alpha_upper_irrelevant} we get $\alpha_1 \le \as(t) \le \alpha_k$ for all $t$, and therefore $\as$ is always in-between some $\alpha_k, \alpha_{k+1}$.
+	Even if $\as(t) \ \alpha_k$ for some $k$, belonging in the closed border of $T_{-\alpha}$, it will be either the lowest or highest toll difference possible, ensuring there is always an edge where no players are viewing the two edges equally.
+
+	Let $i$ be that edge which we also assume is the lower split of the flow equilibrium, i.e. $t_i^\prime > t_{-i}^\prime$, and let $k \in [m - 1]$ such that $\alpha_k < \as(t^\prime) < \alpha_{k+1}$.
+	Then link owner $i$ can increase their toll to a $t_i^{\prime\prime} > t_i^\prime$, thus decreasing the value of $\as$, up to the point where $\alpha(t^{\prime\prime}, t_{-i}^\prime) = \alpha_k$.
+	Players in link $i$ will now view their edge as of either lower or equal cost value as the other, while the players in the other link will view theirs as of purely lower cost, making none wishing to change.
+	We therefore get that $x_i(t_i^{\prime\prime}, t_i^\prime) = x_i(t^\prime)$ making in turn $\Pi_i(t_i^{\prime\prime}, t_i^\prime) > \Pi_i(t^\prime)$ and finally $B_i(t_{-i}^\prime) \ne t_i$.
+
+	Similarly we can show that $B_{-i}(t_i^\prime) \ne t_{-i}$ if $i$ is the upper split of the flow equilibrium, decisively making $t^\prime$ a set of tolls where there never is a Nash equilibrium for the pricing game.
+\end{proof}
+
+We complete the picture now with correlation result for the Nash equilibrium of the pricing game.
+
+\begin{theorem}
+	\label{theorem:a_step_ne_equiv_fixed}
+	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
+	If $\Gm_1$ has a Nash equilibrium for the pricing game at toll $t^*$, then the game $\Gm_2 = ([2], \ell, \as(t^*))$, with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha(p) = \as(t^*)$, also has its unique Nash equilibrium for the pricing game at $t^*$.
+\end{theorem}
+
+\begin{proof}
+	First observe that from Lemma \ref{lemma:a_step_gaps} we get $t^*$ is not in the closure of $T_{-\alpha}$, otherwise it couldn't be a Nash equilibrium, therefore $\as(t^*) = \alpha_k$ for some $k \in [m]$.
+	Then, again due to $t^*$ being a Nash equilibrium, it holds that $\Pi_i(t^*) \ge \Pi_i(t_i, t_{-i}^*)$ for all $t_i > 0$.
+
+	Now it is important to note that from the analysis in Harks et al. \cite{Harks_2019} we know that for homogeneous games the profit functions $\Pi_i$ are concave, making them have unique maximum.
+	Therefore when restricting the domain to an interval, either that same maximum is within that interval or a lower maximum of the interval is achieved at its corners.
+	The restriction of $t^*$ not belonging in the closure of $T_{-\alpha}$ also forbids the latter case, making $\Pi_i(t^*)$ also the global maximum for $\Gm_2$.
+	That condition holds for all link owners $i \in [2]$, therefore $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
+\end{proof}
+
+The most important corollary from that lemma comes from the fact that, as stated in \ref{lemma:a_fixed_ne}, for any $c > 0$ the flow for which the Nash Equilibrium emerges is always the same.
+Consequently for any step function assigned to a pricing game with fixed latency functions, if a Nash Equilibrium exists then it needs to be on the same flow as the one emerging in the respective homogeneous pricing game.
+
+With such a strong notion of the pricing Nash equilibrium, we can now see a potential algorithm that can be used to query its existence or not as well as calculate it.
+We present it here.
+
+\begin{definition}[Algorithm]
+	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
+	Then we define the following algorithm that takes as input a game's parameters and returns the Nash Equilibrium of the pricing game, if any.
+	\begin{enumerate}
+		\item Consider $\Gm^\prime = ([2], \ell, 1)$ the homogeneous pricing game with latency functions same as in $\Gm$, and calculate its Nash equilibrium $t^*$.
+		\item Calculate $\as(t^*)$.
+		\begin{enumerate}
+			\item[2.1] If $t^*$ in the closure of $T_{-a}$, then there is no Nash equilibrium for the pricing game in $\Gm$.
+			\item[2.2] Otherwise, calculate $\Pi_{i, k}$ for all link owners $i$ and $\alpha_k$ values.
+			\begin{enumerate}
+				\item[2.2.1] If $\Pi_i(t^*) \ge \Pi_{i, k}$ for all $k \in [m]$ and for all $i \in [2]$ then $t^*$ is a Nash equilibrium in $\Gm$.
+				\item[2.2.2] Otherwise, there is no Nash equilibrium in $\Gm$.
+			\end{enumerate}
+		\end{enumerate}
+	\end{enumerate}
+\end{definition}
+
+Given the restrictions of the possible positions for Nash equilibrium tolls, it would be tempting to try and calculate exact conditions for it.
+Those conditions would depend on latencies and the distance of the step function's $k$ values.
+
+Unfortunately the results do not scale for $[N]$ parallel networks.
+
+We will conclude this chapter with some investigation on games with continuous distribution function.
+
 \section{Continuous distribution function}
 
-For the continuous distribution function case, the previous restriction of $\alpha(p) > 0$ when $p > 0$ is not sufficient, as it still allows for distribution functions with many player values close to $0$ < Is that actually the problem?.
+For the continuous distribution function case, the previous restriction of $\alpha(p) > 0$ when $p > 0$ is not sufficient, as it still allows for distribution functions with many player values close to $0$ $\rightarrow$ Is that actually the problem?.
 Specifically the case of $\alpha(p) = cp$, for some $c > 0$, shows some interesting behavior, as it creates instances where $\Pi_i$ becomes either unbounded or fixed; in the first case then $B_i$ becomes unbounded, while in the second it becomes an an infinite set.

### 2024-11-25 thesis/article.tex
Thesis: Updates with fixes from Th. Lianeas notes (until Preliminaries)
Updates in Title, Abstract (convert to n-links), Introduction, Related Work (wip) and Preliminaries (conversion to n-links, fixes, adds game equivalence)

@@
 				\begin{flushleft}
-					\huge{\bf Pricing Games in Heterogeneous 2-link Parallel Networks\\}
+					\huge{\bf Pricing Games in Heterogeneous Parallel Networks\\}
 					\vskip3cm
@@
 \chapter*{Abstract}
-In this masters thesis we study a $2$-level optimisation problem where, on a $2$-link network from a source $s$ to a target $t$, a unit of flow wants to move from $s$ to $t$ using the link with the lowest cost, while the two link owners compete for profit by assigning tolls to links and thus creating a toll congestion game.
+In this masters thesis we study a $2$-level optimisation problem where, on an $n$-link network from a source $s$ to a target $t$, a unit of flow wants to move from $s$ to $t$ using the link with the lowest cost, while the link owners compete for profit by assigning tolls to links and thus creating a toll congestion game.
 We examine only affine latencies for the links.
@@
 First we present some basic definitions and properties of profit homogeneous games.
-Using them as base, we examine cases of fixed and step distribution functions, where for the latter we present strict conditions for the existence or not of a Nash Equilibrium.
+Using them as base, we examine cases of fixed and step distribution functions, where for the latter we first restrict our model to $2$-link instances and then we present strict conditions for the existence or not of a Nash Equilibrium.
 We then introduce a new term, the split function $\as(t)$, defined as the time-money sensitivity value for which the $2$ link costs are equal for a given set of tolls $t$.
 With the help of $\as$ we will describe and prove some properties of the heterogeneous games for continuous distribution functions.
-In our main result, we generalise the conditions necessary for the existence of a Nash Equilibrium in the profit game between the toll owners, and finally we discuss some extensions to $n$-link parallel networks.
+In our main result, we generalise the conditions necessary for the existence of a Nash Equilibrium in the profit game between two toll owners, and finally we discuss some extensions to $n$-link parallel networks.
 \clearpage
@@
 \chapter*{Συνοψη}
-Σε αυτή τη διπλωματική μεταπτυχιακού μελετάμε ένα πρόβλημα βελτιστοποίησης $2$ επιπέδων, όπου σε ένα δίκτυο με $2$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι δύο ιδιοκτήτες των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
+Σε αυτή τη διπλωματική μεταπτυχιακού μελετάμε ένα πρόβλημα βελτιστοποίησης $2$ επιπέδων, όπου σε ένα δίκτυο με $n$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι δύο ιδιοκτήτες των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
 Εξετάζουμε μόνο αφινικές καθυστερήσεις για τις ακμές.
@@
 Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομογενών παιγνίων κέρδους.
-Mε αυτά ως βάση, εξετάζουμε περιπτώσεις σταθερών και βηματικών συναρτήσεων κατανομής, όπου για το τελευταίο παρουσιάζουμε αυστηρές συνθήκες για την ύπαρξη ή μη σημείου ισορροπίας Nash.
+Mε αυτά ως βάση, εξετάζουμε περιπτώσεις σταθερών και βηματικών συναρτήσεων κατανομής, όπου για το τελευταίο πρώτα περιοριζόμαστε σε στιγμιότυπα $2$ ακμών και παρουσιάζουμε αυστηρές συνθήκες για την ύπαρξη ή μη σημείου ισορροπίας Nash.
 Μετά εισαγάγουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού $\as(t)$, ορισμένη ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία τα κόστη των $2$ ακμών είναι ίσα για ένα δοσμένο σετ διοδίων $t$.
 Με τη βοήθεια της $\as$ θα περιγράψουμε και θα αποδείξουμε μερικές ιδιότητες των ετερογενών παιγνίων με συνεχή συνάρτηση κατανομής.
-Στο κύριο αποτέλεσμά μας, γενικοποιούμε τις συνθήκες που είναι απαραίτητες για την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των ιδιοκτητών των ακμών, και τελικώς συζητάμε κάποιες επεκτάσεις για δίκτυα με $n$ ακμές.
+Στο κύριο αποτέλεσμά μας, γενικοποιούμε τις συνθήκες που είναι απαραίτητες για την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ δύο ιδιοκτητών ακμών, και τελικώς συζητάμε κάποιες επεκτάσεις για δίκτυα με $n$ ακμές.
 \clearpage
@@
 \chapter{Introduction}
-
-In this thesis we study a three level optimisation problem.
-On the basis there is a 2-node $(s, t)$, 2-link $s-t$ network, each link with a non-decreasing latency function that defines how the traffic increases as more players flow into that link.
-On the first level a flow $[0, 1]$ wants to move from $s$ to $t$ and experience the minimum latency (traffic).
-On the second level, the links might also have tolls which impose an additional cost to the flow players, plus in our case (heterogeneous users) each player has a different money-time trade-off and thus see the link costs differently.
-Finally on the third level (are the levels really that way?), the tolls are owned by players who profit on the flow that uses that link and compete to maximise it.
-
-We know from Cole et al. \cite{10.1145/780542.780618} that regardless of the distribution function $a$ or the latency functions (as long as they are non-decreasing) a $\NE$ always exists.
-In that $\NE$ the users are split with the money-sensitive ones on the link with the lower toll and the time-sensitive ones on the higher toll one, each one seeing their link as either lower or equal cost with the other (while they all see traffic equally).
-
-We introduce a new term $\as=\frac{l_1(x)-l_2(1-x)}{t_2-t_1}$ which is the $a(p)$ value of a user $p$ which sees the link costs equally.
+\label{chapter:intro}
+
+In this thesis we study a two level optimisation problem.
+On the basis there is a network with 2 nodes $(s, t)$ and $n$ links, each link directed from $s$ to $t$ and weighted by a non-decreasing latency function that defines how the traffic increases as more players flow into that link.
+On the first level, a flow $[0, 1]$ wants to move from $s$ to $t$ using one of the $n$ links and experience minimum latency (traffic).
+On the second level, each link is owned by a different owner who can add a toll to their link and gain profit proportional to the flow that uses it.
+The tolls impose an additional cost to the flow players, affecting the first level game, and the link owners compete with each other to maximise their profit.
+In our case we will additionally assume that the flow users behave in a heterogeneous way when it comes to tolls, meaning that each player has a different money-time trade-off and thus see the link costs differently.
+
+The structure of this thesis is as such.
+We finish this chapter by briefly presenting previous work in this field, all while examining some of the different models and properties that have been researched in the literature so far.
+This will also serve as a bridge to Chapter \ref{chapter:preliminaries} were we will set our basis for the rest of the study.
+This includes formal definitions of the models and properties we introduced from previous work as well as some additional -but still basic- properties of the models, with heavy focus on the money-time user sensitivity, captured by a distribution function $\alpha$.
+
+Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money-time sensitivity split}, which captures the notion of a (potentially non-existent) player whose money-time sensitivity makes them view the two links as equal.
+We will then analyse that notion and provide properties and bounds for its values.
+Finally, in the chapter's main result, we prove a general property of homogeneous network games as, due to the previously found bounds, there might be a portion of users whose sensitivity value can be arbitrarily large without affecting the game.
+
+Having arrived at our main results in this work, in Chapter \ref{chapter:pricing_equilibria} we investigate the pricing competition game between the link owners of a network with heterogeneous users.
+We begin by examining a class of games where the distribution function is fixed across all users, which, as we'll formally describe, makes the game \textit{pseudo-heterogeneous}.
+Particular interest in the above class is the relation between games with identical setup but with different fixed distribution functions.
+We describe and prove some properties for them, and using those we then tackle step distribution functions (where the user sensitivity can take values out of a finite set).
+At this point we restrict our model to instances with $2$ links, and provide strict restrictions for equilibrium existence for the pricing competition game.
+
+We conclude this thesis with a short discussion around the main outtakes of this study, while also presenting potential directions for future work.
 
 \section{Related Work}
-
-Adding tolls to a Network Game has began as a standard practice to regulate the network flow, as it is well known that the equilibrium that occurs by the game is not guarranteed to be the most efficient.
-
-TODO
+\label{section:related_work}
+
+Selfish routing has a vast history of literature as it's been proven useful in solving a variety of real-world problems in economics \cite{pigou1920economics}, transportation \cite{beckmann1956studies} and more (see \cite{roughgarden2002sr} and \cite{roughgarden2005slpoa} for more references).
+It has been well-established, at least as early as 1920 from the work of Pigou \cite{pigou1920economics}, that selfish behavior in congested networks can create (arbitrary) inefficiencies with regard to the total latency experienced by all users.
+A long-standing practice to solve these inefficiencies has been to regulate the network by adding tolls to the links, thus altering the cost of the link usage.
+A classical result on this is the use of marginal tolls (Beckman et al.
+\cite{beckmann1956studies}), where each link user is charged a toll corresponding to their externality, i.e.
+the added congestion effect caused by their participation in the network.
+This technique can eradicate the inefficiencies and create optimal flow in the network, however it assumes a strong homogeneity among the users.
+Marginal cost pricing has been investigated in networks with homogeneous users (e.g.
+Dafermos \cite{dafermos1973toll}), with the resulting payment required by users on same links being different, an unwanted and non-practical approach, which also requires knowledge of the users' sensitivity beforehand.
+
+One of the major contributions in this field has been the introduction of the concept of a Nash Equilibrium for networks, defined as Wardrop equilibrium \cite{wardrop_theoretical_1952}.
+
+Congestion games were formally introduced by Rosenthal \cite{Rosenthal1973ACO} who also proved that in those games a pure Nash Equilibrium always exists.
+Later, Monterer-Shapely \cite{MONDERER1996124} defined the class of potential games (games where the incentive for all players to change their strategy can be expressed with a global function) and proved that congestion games are equivalent to exact potential games (potential games where a change in strategy from any player alter the potential function the exact way it alters the player's cost).
+Milchtaich \cite{MILCHTAICH1996111} then investigated the different pay-offs 
+Given the above, with the existence of a Nash equilibrium always existing, later research focused on investigating the quality of an equilibrium by using the notion of \textit{Price of Anarchy}, introduced by Koutsoupias-Papadimitriou \cite{KOUTSOUPIAS200965}.
+The Price of Anarchy describes the ratio between a Nash Equilibrium and the most cost-efficient solution, therefore lower values denote a qualitative equilibrium while a lower value denotes a bad one.
+Finally, in terms of complexity, Fabrikant et al. \cite{10.1145/1007352.1007445} have shown that calculating a pure Nash Equilibrium for congestion games is PLS-complete in the general case.
+
+Heterogeneity has been studied by Schmeilder \cite{1973JSP.....7..295S} and Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220} has contributed through with work on the more general crowding games, a class of games where the cost assigned to each player is affected only by the number of players selecting the same action (or strategy).
+Large crowding games are basically less restrictive $n$-link parallel congestion games.
+
+Discussing more the algorithmic aspect of toll computation, there has been significant research in finding optimal tolls for homogeneous network users.
+Marginal cost prices can be computed using convex programming \cite{beckmann1956studies},
+
+Acemoglu and Ozdaglar were the first to introduce pricing competition between link owners to the above model \cite{10.1287/moor.1060.0231}.
+They showed that increasing the competition among operators from a monopoly to an oligopoly may reduce the efficiency of the network, achieving tight bounds on the Price of Anarchy.
+In a follow-up work \cite{10.1109/JSAC.2007.070812}, they generalised the above by assuming more general topologies where links can also be linked serially (series-parallel networks).
 
@@
 \chapter{Preliminaries}
+\label{chapter:preliminaries}
 
 In this section we will describe the model utilised throughout this thesis.
-If we attempted to call that model by including all of it's properties, the result would be a Heterogeneous Non-atomic 2-link Parallel Network Toll Congestion Pricing Game, so while we will describe each of those properties, we will eventually focus on heterogeneity and the pricing competition, thus calling it a Heterogeneous Pricing Game.
+If we attempted to call that model by including all of its properties, the result would be a Heterogeneous Non-atomic 2-link Parallel Network Toll Congestion Pricing Game, so while we will describe each of those properties, we will eventually focus on heterogeneity and the pricing competition, thus calling it a Heterogeneous Pricing Game.
 
@@
 Finally, the network can also be extended by allowing a set of tolls $t = (t_i)_{i \in N}$ to be assigned to each link, which in turn adds to the effective cost of a player using them.
+At this point we should also mention that we will freely use, when needed, the standard game-theoretical notation of $t_{-i} = t \setminus \{t_i\}$.
 
@@
 For a given set of tolls $t$, a flow $x$ is a \textit{Wardrop equilibrium for $t$} if $\forall i, j \in N$ with $x_i > 0$ it holds that
-\begin{equation}
-	\label{wardrop_inequality_cost}
+\begin{equation*}
 	\ell_i(x_i) + t_i \leq \ell_j(x_j) + t_j
-\end{equation}
+\end{equation*}
 In that case, all links with $x_i > 0$ have equal effective costs, i.e. there exists some $K > 0$ such that $\ell_i(x_1) + t_i = K$ for all links $i$ with $x_i > 0$.
 From a well-known result from Beckman et al.
-\cite{beckmann1956studies} and Dafermos and Sparrow \cite{1363388843888284416}, such and an equilibrium for $t$ exists and is unique, therefore for a toll vector $t$ we can denote by $x(t)$ the flow occurring on  that unique equilibrium for the given toll $t$.
-We will freely use when needed the general game-theoretical notation of $x(t_i, t_{-i})$ where $t_{-i} = t \setminus \{t_i\}$.
-We copy Lemma 2.1 from Harkes et al \cite{Harks_2019} as is for later use.
+\cite{beckmann1956studies} and Dafermos and Sparrow \cite{1363388843888284416}, such and an equilibrium for $t$ exists, is unique with regard to costs and can be described by the following inequality.
 \begin{lemma}
@@
 \end{lemma}
+
+We can therefore denote by $x(t)$ the flow occurring on that unique equilibrium for a given toll $t$.
 If $t = 0$ then the equilibrium is called the \textit{Wardrop equilibrium}.
-It's also worth noting that looking at \eqref{wardrop_inequality_cost}, we can see that what actually matters, with regard to the flow, is the relative difference among the tolls.
-I.e.
-if we consider any $c \in \R_+$ (or even $c \geq -\min_{i \in N} t_i$) then for $t^\prime = t + c$ the inequalities remain true for all $i, j \in N$ and thus the network game for the flow between tolls $t$ and $t^\prime$ is the same.
+It's also worth noting that looking at Lemma \ref{lemma:wardrop_equilibrium}, we can see that what actually matters, with regard to the flow, is the relative difference among the tolls, and not their actual values.
+To demonstrate this, if we consider an arbitrary $c \in \R_+$ and tolls $t^\prime = t + c$ then for the same flow $x$ and any other flow $x^\prime$ the sum becomes
+\begin{flalign*}
+	\sum_{i \in N} (\ell_i(x_i) + t_i + c) (x_i - x_i^\prime) &= \sum_{i \in N} (\ell_i(x_i) + t_i) (x_i - x_i^\prime) + c \left(\sum_{i \in N} x_i - \sum_{i \in N} x_i^\prime\right) \\
+	&= \sum_{i \in N} (\ell_i(x_i) + t_i) (x_i - x_i^\prime) \leq 0
+\end{flalign*}
+which makes $x$ the Wardrop equilibrium for $t^\prime$ as well.
+The last equality holds because $x_i, x_i^\prime$ are flows of the network and therefore $\sum_{i \in N} x_i = \sum_{i \in N} x_i^\prime = 1$.
+Also, this reasoning is still valid for $c < 0$ as long as $t_i + c \ge 0$ for all $i \in N$, or in other words, as long as $c \ge -\min_{i \in N}{t_i}$.
 
 Finally for affine latencies we can calculate $x(t)$.
-For $l_i(x_i) = a_i \cdot x_i + b_i, a_i > 0, b_i \geq 0$ and $t \in \R_+^N$ define $N(t) = \{i \in N | x_i(t) > 0\}$.
-Since $x(t)$ is an equilibrium for $t$ and $\sum_{i \in N(t)}x_i(t) = 1$ we solve the equations with regard to the common efficient cost $K$ and then we get for all $i \in N(t)$
+For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^N$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
+Since $x(t)$ is an equilibrium for $t$ then for all $i \in N(t)$ we get $\ell_i(x_i) + t_i = K$ for some common efficient cost $K$.
+By also using the fact that $\sum_{j \in N(t)} x_i = 1$ we solve the equations with regard to $K$ and eventually we get for all $i \in N(t)$
 \begin{equation}
-	\label{eq:x_i}
+	\label{eq:homogeneous_x_i}
 	x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
@@
 
+It is important to note here that formula \ref{eq:homogeneous_x_i} is valid only for $t$ such that the result is in $[0, 1]$.
+If we allow any arbitrary $t \in \R_+^N$ then we can find extreme instances of the game, which wouldn't occur in the optimal play of the link owners anyway.
+For example, if for tolls $t$ link owner $i$ has $t_i$ large enough such that $x_i(t) = 0$, then for any $t_i^\prime > t_i$ it also holds that $x_i(t_i^\prime, t_{-i}) = 0$, while formula \ref{eq:homogeneous_x_i} would decrease.
+Since we assume that link owners play optimally, we will also assume that tolls $t$ are within the bounds where formula \ref{eq:homogeneous_x_i} is valid.
+
 \subsection*{Heterogeneous players}
 
-In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different money/time valuation ratios.
+In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different money-time sensitivity values.
 We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of each edge as $c_i^p(t) = \ell_i(x_i(t)) + \alpha(p) \cdot t_i$ and then seek the shortest link among them.
@@
 Even though the definition does allow functions that are not upper bounded with $\alpha(1) = +\infty$, we will always assume that $\alpha$ is finite on $[0, 1)$.
-Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Lemma \ref{lemma:a_0_0}, allowing many players close to $0$ breaks the pricing game.
-
-We can therefore define an instance of a Heterogeneous Pricing Game as the tuple $(N, \ell, \alpha)$ with $N = \{1, 2, \dots, n\}$, $\ell = (\ell_i)_{i \in N}$ and $\alpha$ the distribution function.
+%Finally, we will assume that $\alpha(0) > 0$, since, as we'll see in more detail in Lemma \ref{lemma:a_0_0}, allowing many players close to $0$ breaks the pricing game.
+
+We can therefore define an instance of a Heterogeneous Pricing Game as the tuple $(N, \ell, \alpha)$ with $N = \{1, 2, \dots, n\}$, $\ell = (\ell_i)_{i \in N}$ and $\alpha$ a non-decreasing distribution function.
 Then with all the above we can again define a Nash equilibrium for the game if $\forall i \in N$ and $\forall p \in [0, 1]$ it holds that
 \[c_{f(p)}^p(t) \leq c_i^p(t)\]
-Existence of an equilibrium is guaranteed by the more general results of Schmeidler \cite[Thm 2]{1973JSP.....7..295S}, while uniqueness is covered by Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220}; for a more detailed coverage of those look at the definitions and propositions of Cole et al.
+Existence of an equilibrium is guaranteed by the more general results of Schmeidler \cite[Thm 2]{1973JSP.....7..295S}, while uniqueness is covered by Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220} (see Related Work \ref{section:related_work}); for a more detailed coverage of those look at the definitions and propositions of Cole et al.
 \cite[\S2]{10.1145/780542.780618}.
-Therefore can extend the definition for $x(t)$ similarly as in the homogeneous case.
+We can therefore also extend the definition of $x(t)$, being the Nash Equilibrium for $t$, similarly as in the homogeneous case.
 
@@
 	\label{lemma:latencies_tolls}
-	For a Heterogeneous Parallel Game $(N, \ell, \alpha)$ with tolls $t$ and Nash equilibrium for $t$ flow $x(t)$, it holds that for all $i, j \in N$ with $x_i(t), x_j(t) > 0$
+	For a Heterogeneous Parallel Game $(N, \ell, \alpha)$ with tolls $t$ and flow $x(t)$ the Nash equilibrium for $t$, it holds for all $i, j \in N$ with $x_i(t), x_j(t) > 0$ that
 	\begin{enumerate}[(i)]
@@
 	If now $t_i \le t_j$ then for all players $p$ we get $\ell_i(x_i(t)) + \alpha(p) \cdot t_i < \ell_j(x_j(t)) + \alpha(p) \cdot t_j \Rightarrow c_i^p(t) < c_j^p(t)$.
-	Therefore there exist players $p_j$ on link $j$ for which $c_{f(p_j)}^{p_j}(t) = c_j^{p_j}(t) > c_i^{p_j}(t)$, which is a contradiction since $x(t)$ is a Nash equilibrium.
+	Since $x_j(t) > 0$ there exist players $p_j$ on link $j$ for which $c_{f(p_j)}^{p_j}(t) = c_j^{p_j}(t) > c_i^{p_j}(t)$, which is a contradiction since $x(t)$ is a Nash equilibrium.
 	The opposite direction is also proved similarly.
@@
 
-\section*{Pricing Games}
-
-While keeping the above Network Game model, we introduce $n$ agents who each own one link of the network and can thus assign its toll and profit from it.
-The profit is defined for each link owner $i$ as $\Pi_i = x_i \cdot t_i$ which, since we defined $x(t)$ above, we can extend the definition to $\Pi_i(t) = x_i(t) \cdot t_i$ describing the profit at the equilibrium for given toll $t$.
+\section*{Pricing Games (our model)}
+
+Arriving at the main model that will be used in this thesis, we keep the above Network Game model and introduce $n = |N|$ agents who each own one link of the network and can thus assign toll to it and gain profit.
+For each link owner $i$, their profit $\Pi_i$ is defined as $\Pi_i = x_i \cdot t_i$, and since we have defined $x(t)$ we can extend $\Pi_i$ to $\Pi_i(t) = x_i(t) \cdot t_i$, which describes the profit of link owner $i$ at the Nash equilibrium for a given toll $t$.
 The link owners compete with each other for profit, each selfishly selecting the toll $t_i$ that will maximise their profit given the remaining tolls $t_{-i}$.
@@
 \[\Pi_i(t_i, t_{-i}) \geq \Pi_i(t_i^\prime, t_{-i})\]
+We will denote this toll equilibrium as $t^*$ when relevant.
+
+\begin{example}
+	[TODO: Add figure]
+\end{example}
 
@@
 
-For homogeneous players and affine latencies we can calculate the best response functions for each link owner by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$. TODO
-
-\section*{2-link Heterogeneous Pricing Games (our model)}
-
-Focusing on the model that will be used in this thesis, we simplify our network by only having $2$ links, and then consider that the flow is acting in a heterogeneous way.
-The model can thus be defined as the tuple $([2], \ell, \alpha)$, where $[2] = \{1, 2\}$ the links, $\ell = (\ell_1, \ell_2)$ the latency functions and $\alpha$ the distribution function.
-[TODO: Add figure]
-When discussing properties of the model where the pricing game is not relevant, we will refer to a $([2], \ell, \alpha)$ instance as a toll game, and otherwise as a pricing game.
+For homogeneous players and affine latencies we can calculate the best response functions $B_i(t_{-i})$.
+For each link owner $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
+\begin{equation}
+	\label{eq:homogeneous_br_i}
+	B_i(t_{-i}) = \frac{1 + \sum_{j \in N(t) : j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \in N(t) : j \ne i}\frac{2}{a_j}}
+\end{equation}
+
+Similarly to \ref{eq:homogeneous_x_i}, this formula is valid only for tolls in a bounded subset of $\R_+^N$.
+
+%In the extreme cases where the toll differences are arbitrarily large, the best response of some players will be to lower their toll and take all available flow.
+
+%From Harkes et al. \cite[Lemma 3.3]{Harks_2019} we can also get an equation for the Nash Equilibrium of the pricing game.
+%\begin{equation}
+%	\label{eq:homogeneous_ne_br_i}
+%	t_i^* = \left(a_i + \frac{1}{\sum_{j \ne i} \frac{1}{a_j}}\right) \cdot x_i(t^*)
+%\end{equation}
+
 We finish this section with a crucial property for homogeneous pricing games that we will need later.
-TODO: This property probably exists as a general theorem in convex programming or something, maybe with non-decreasing property instead of decreasing.
-Until then, we prove it analytically for affine latencies.
-
 \begin{lemma}
 	\label{lemma:tolls_diff}
-	Let $([2], \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$.
-	Then $D_i$ is decreasing for all links $i$.
+	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
+	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
 \end{lemma}
@@
 \begin{proof}
-	From equation \ref{eq:x_i} for $2$ links we get
-	\[
-		x_i(t) = \frac{1 + \frac{b_{-i} + t_{-i} - b_i - t_i}{a_{-i}}}{\frac{a_i}{a_{-i}}} = \frac{a_{-i} + b_{-i} + t_{-i} - b_i - t_i}{a_i}
-	\]
-	from which by following the definitions and from first order conditions for quadratic functions we get
-	\[
-		B_i(t_{-i}) = \argmax_{t_i > 0}x_i(t) \cdot t_i = \frac{a_{-i} + b_{-i} + t_{-i} - b_i}{2}
-	\]
-	Finally
-	\[
-		D_i(t_{-i}) = -\frac{1}{2}t_{-i} + \frac{a_{-i} + b_{-i} - b_i}{2}
-	\]
-	which is obviously decreasing.
-\end{proof}
+	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
+	From formula \ref{eq:homogeneous_br_i} after some calculations we get
+	\[
+		B_i(t_{-i}) - t_j = \left(\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1\right)t_j + \frac{1 + \frac{b_j - b_i}{a_j} + \sum_{k \ne i, j}\frac{b_k + t_k - b_i}{a_k}}{\sum_{k \ne i} \frac{2}{a_k}}
+	\]
+	which decreasing with regards to $t_j$ if and only if its coefficient is negative.
+	Indeed, since $a_i > 0$ for all $i$, we get
+	\[
+		\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1 = \frac{1}{2 \left(1 + \sum_{k \ne i, j} \frac{a_j}{a_k}\right)} - 1 \leq \frac{1}{2} - 1 < 0
+	\]
+\end{proof}
+
+\section*{Game equivalence}
+
+Another notion we will need in our analysis is when two games are equivalent.
+This concept will be helpful because in some cases, even though the parameters of a game might change, the players' utilities and respective strategies do not, making the two instances in practice identical.
+For example, similarly to our analysis of toll differences using Lemma \ref{lemma:wardrop_equilibrium}, if we consider the two homogeneous games $(N, \ell, 1)$ and $(N, \ell + c, 1)$ for some $c > 0$, then the flow's behavior will be the same in both of them, resulting in equivalent instances.
+We give here a formal definition.
+
+\begin{definition}[Game equivalence]
+	\label{definition:game_equivalence}
+	Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
+	$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
+\end{definition}
+
+It trivially follows from this definition that the two pricing competition games played on two equivalent network congestion games are identical.
 
 \chapter{Money sensitivity split}
+\label{chapter:split}
 
@@
 \chapter{Equilibria in Pricing Games}
+\label{chapter:pricing_equilibria}
 
@@
 %\begin{proof}
-%	From equation \ref{eq:x_i} for $2$ links and under universal sensitivity $c_1, c_2$ respectively we get
+%	From equation \ref{eq:homogeneous_x_i} for $2$ links and under universal sensitivity $c_1, c_2$ respectively we get
 %	\begin{align*}

### 2024-11-27 thesis/article.tex
Thesis: Generalises split function chapter for n-links, also Preliminaries improvements

@@
 \end{equation*}
-In that case, all links with $x_i > 0$ have equal effective costs, i.e. there exists some $K > 0$ such that $\ell_i(x_1) + t_i = K$ for all links $i$ with $x_i > 0$.
+In that case, all links with $x_i > 0$ have equal effective costs, i.e. there exists some $K > 0$ such that for all those links $i$ it holds that $\ell_i(x_1) + t_i = K$.
 From a well-known result from Beckman et al.
@@
 We can therefore denote by $x(t)$ the flow occurring on that unique equilibrium for a given toll $t$.
-If $t = 0$ then the equilibrium is called the \textit{Wardrop equilibrium}.
+If $t = 0^N$ then the equilibrium is called the \textit{Wardrop equilibrium}.
 It's also worth noting that looking at Lemma \ref{lemma:wardrop_equilibrium}, we can see that what actually matters, with regard to the flow, is the relative difference among the tolls, and not their actual values.
@@
 
+With this observation we can see that the case of $t = 0^N$ is equivalent to any toll instance such that $t_1 = t_2 = \dots = t_n$.
+We will therefore simplify our notation and write $t = 0$ when talking about the game without tolls, though we will in fact mean the entire class $\{t = (c)_{i \in N}, c \in \R_+\}$.
+
 Finally for affine latencies we can calculate $x(t)$.
 For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^N$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
-Since $x(t)$ is an equilibrium for $t$ then for all $i \in N(t)$ we get $\ell_i(x_i) + t_i = K$ for some common efficient cost $K$.
-By also using the fact that $\sum_{j \in N(t)} x_i = 1$ we solve the equations with regard to $K$ and eventually we get for all $i \in N(t)$
+Since $x(t)$ is an equilibrium for $t$ then for all $i \in N(t)$ we get $\ell_i(x_i) + t_i = K$ for some common effective cost $K$.
+By also using the fact that $\sum_{j \in N(t)} x_i = 1$ we solve the equations with regard to $K$ and eventually get for all $i \in N(t)$
 \begin{equation}
@@
 \end{equation}
-
-It is important to note here that formula \ref{eq:homogeneous_x_i} is valid only for $t$ such that the result is in $[0, 1]$.
-If we allow any arbitrary $t \in \R_+^N$ then we can find extreme instances of the game, which wouldn't occur in the optimal play of the link owners anyway.
-For example, if for tolls $t$ link owner $i$ has $t_i$ large enough such that $x_i(t) = 0$, then for any $t_i^\prime > t_i$ it also holds that $x_i(t_i^\prime, t_{-i}) = 0$, while formula \ref{eq:homogeneous_x_i} would decrease.
-Since we assume that link owners play optimally, we will also assume that tolls $t$ are within the bounds where formula \ref{eq:homogeneous_x_i} is valid.
 
@@
 
-\begin{example}
-	[TODO: Add figure]
-\end{example}
-
 \subsection*{Homogeneous players}
 
-For homogeneous players and affine latencies we can calculate the best response functions $B_i(t_{-i})$.
+For homogeneous players, from the work of Harkes et al.
+\cite[Example 4.2]{Harks_2019}, we know that uniqueness of $t^*$ is guaranteed only when $x_i(0) > 0$ for all $i \in N$, a property called the \textit{full Wardrop support assumption}.
+This is seemingly not as much restrictive in practice, as there would be little motivation to add tolls to a route with no traffic.
+From the same work we also get that if the full Wardrop support assumption holds, then $t^*$ is unique \cite[Lemma 3.3]{Harks_2019} and $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ \cite[Lemma 3.2]{Harks_2019}.
+
+Also, for affine latencies, we can calculate the best response functions $B_i(t_{-i})$.
 For each link owner $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
@@
 	\label{eq:homogeneous_br_i}
-	B_i(t_{-i}) = \frac{1 + \sum_{j \in N(t) : j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \in N(t) : j \ne i}\frac{2}{a_j}}
+	B_i(t_{-i}) = \frac{1 + \sum_{j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \ne i}\frac{2}{a_j}}
 \end{equation}
-
-Similarly to \ref{eq:homogeneous_x_i}, this formula is valid only for tolls in a bounded subset of $\R_+^N$.
 
@@
 
-We finish this section with a crucial property for homogeneous pricing games that we will need later.
+To describe more properties of homogeneous pricing games we will need the following crucial Lemma.
 \begin{lemma}
@@
 	\]
-	which decreasing with regards to $t_j$ if and only if its coefficient is negative.
+	which is decreasing with regards to $t_j$ if and only if its coefficient is negative.
 	Indeed, since $a_i > 0$ for all $i$, we get
@@
 \end{proof}
+
+\subsection*{Heterogeneous players}
+
+\begin{example}
+	[TODO: Add figure]
+\end{example}
 
@@
 
-Consider a $([2], \ell, \alpha)$ toll game such that $x_1(0), x_2(0) > 0$ with tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
-Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} follows that $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
+Consider a $([2], \ell, \alpha)$ heterogeneous parallel game with links $[2] = \{1, 2\}$ such that $x_1(0), x_2(0) > 0$ with tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
+Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} leads to $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
 For the $2$ edges of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edges' total latencies as equal.
@@
 	\label{definition:split_function}
-	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$, tolls $t = (t_1, t_2), t_1 \ne t_2$ and $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$, we define the \textit{money sensitivity split function} $\as: \R_+^2 \setminus \{(a, a) | a \in \R_+\} \rightarrow (0, +\infty)$ as follows
-	\[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
+	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
+	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
 \end{definition}
 
+For $t_i = t_j$ any split value will work, so the function is not well-defined for this case.
 We will also give a more formal definition to the lower-upper split intuition we described above.
@@
 	\label{definition:split_lower_upper}
-	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$, tolls $t \ne 0$ and $x(t)$ the Nash equilibrium for $t$, and also assuming w.l.o.g.
-that $t_1 > t_2$, we define as \textit{lower split} the (possibly zero) flow $x_1(t)$ and as \textit{upper split} the remaining flow $x_2(t)$.
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
+	Assuming w.l.o.g. that $t_i > t_j$, we define as \textit{lower split} the (possibly empty) flow $x_i(t)$ and as \textit{upper split} the (possibly empty) flow $x_j(t)$. 
 \end{definition}
@@
 	\label{corollary:split_to_alpha}
-	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, it holds that
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$.
+	It holds that
 	\begin{itemize}
-		\item $\alpha(p) \le \as(t)$, for all players $p$ in the lower split
-		\item $\alpha(p) \ge \as(t)$, for all players $p$ in the upper split
+		\item $\alpha(p) \le \as^{(i, j)}(t)$, for all players $p$ in the lower split
+		\item $\alpha(p) \ge \as^{(i, j)}(t)$, for all players $p$ in the upper split
 	\end{itemize}
@@
 \begin{proof}
-	Let again w.l.o.g.
-assume $t_1 > t_2 \LeftrightarrowArg{\ref{lemma:latencies_tolls}} \ell_1(x_1(t)) < \ell_2(x_2(t))$, making by definition \ref{definition:split_lower_upper} a player $p$ in the lower split be in link $1$.
+	Let again w.l.o.g. assume $t_i > t_j$, making by definition \ref{definition:split_lower_upper} a player $p$ in the lower split be in link $i$.
 	Since $x$ is a Nash equilibrium we have
 	\begin{align*}
-		c_1^p(t) &\le c_2^p(t) \Rightarrow \ell_1(x_1(t)) + \alpha(p) \cdot t_1 \le \ell_2(x_2(t)) + \alpha(p) \cdot t_2 \\
-		&\RightarrowArg{t_1 > t_2} \alpha(p) \le \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2} \RightarrowArg{\ref{definition:split_function}} \alpha(p) \le \as(t)
+		c_i^p(t) &\le c_j^p(t) \Rightarrow \ell_i(x_i(t)) + \alpha(p) \cdot t_i \le \ell_j(x_j(t)) + \alpha(p) \cdot t_j \\
+		&\RightarrowArg{t_i > t_j} \alpha(p) \le \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j} \RightarrowArg{\ref{definition:split_function}} \alpha(p) \le \as^{(i, j)}(t)
 	\end{align*}
-	Similarly we can show that $\alpha(p) \ge \as(t)$, for all players $p$ in the upper split.
-\end{proof}
-
-At this point in our analysis, we will additionally need the notion of the lowest and highest $\alpha$ value in a flow of players.
-
+	Similarly we can show that $\alpha(p) \ge \as^{(i, j)}(t)$, for all players $p$ in the upper split.
+\end{proof}
+
+At this point in our analysis, we will need to describe the notion of the lowest and highest $\alpha$ value in a flow of players.
 In general, since we're working with a Lebesque-measurable flow, it is natural to not bother with distinguishing between a flow $[0, x_1]$ or $[0, x_1)$, as the player $x_1$ can be arbitrarily placed at any link without affecting the game.
-In a heterogeneous setting, however, the existence or not of that player matters, as its $\alpha(x_1)$ value might be different from the rest of the players in the flow, depending on how $\alpha$ is defined.
-We bypass this issue by instead using set border bounds.
+In a heterogeneous setting, however, the player's $\alpha(x_1)$ might deterministically put him in a specific link depending on how $\alpha$ is defined, so we need to be careful with our notation.
+We will define the $\alpha$ values of a link's flow in a set and then use border bounds which covers both open and closed intervals.
+
+One difficulty we need to consider with this approach are cases where $t_i = t_j$ for some links $i, j \in N$.
+For such tolls $t$, even though $x(t)$ is uniquely defined, we get for all players $p$ that $c_i^p(t) = c_j^p(t)$, and thus the players in links $i$ and $j$ can be put arbitrarily in any of the two, regardless of the $\alpha$ value.
+Even if we attempted to put them orderly, it actually matters which edge we will put first, as the link might have different flow volume resulting in different $\alpha$ values within.
+For this reason we will assume our sets contain all possible $\alpha$ values of any player that might use a link.
+We therefore loose the information about the actual flow splits among those links and keep only the ones among links with different toll values (and in consequence different latencies, Lemma \ref{lemma:latencies_tolls}).
+Still, even with this information loss, we can still observe that
+\begin{enumerate}
+	\item The notion of $\as$ as the $\alpha$ value that views two links as equal is still valid, since such a player will also view as equal any other link with the same toll value as any of the initial two.
+	\item If we limit our scope to only include the links with equal tolls, we actually get a homogeneous sub-game for the total flow in those links.
+\end{enumerate}
+With the above we arrive at the following definition.
 
@@
 	\label{definition:alpha_flow_sets}
-	Let $([2], \ell, \alpha)$ a toll game with $x_1(0), x_2(0) > 0$, tolls $t \ne 0$ and $x(t)$ the Nash equilibrium for $t$.
-	We define as $A_i(t)$ the set of $\alpha(p)$ values for players $p$ on edge $i$ in the Nash equilibrium for $t$.
-	More formally, we define a set function $A_i: \R_+^2 \setminus \{(a, a) | a \in \R_+\} \rightarrow \mathcal{P}(\R_+)$ such that
-	\[A_i(t) = \{\alpha(p)|p \text{ in edge } i \textit{ for } x(t) \}\]
-	For tolls where $t_1 = t_2$ we cannot define lower and upper split, but we will extend the definition of $A_i$ for those tolls with a sign to specify which split we assume the link to have.
-	Therefore we define $A_i^-(0)$ and $A_i^+(0)$ respectively as
-	\[A_i^-(0) = \{\alpha(p)|p \in [0, x_i(0))\} \qquad A_i^+(0) = \{\alpha(p)|p \in (x_i(0), 1]\}\]
-	%\[A_i^-(0) = \lim_{t_1 - t_2 \rightarrow 0^-}A_i(t) \qquad A_i^+(0) = \lim_{t_1 - t_2 \rightarrow 0^+}A_i(t)\]
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ and $x(t)$ the Nash equilibrium for $t$.
+	We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
+	More formally, we define a set function $A_i: \R_+^N \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
+	\[A_i(t) = \{\alpha(p)|p \text{ in edge } j \text{ for } x(t) \text{ where } t_j = t_i\}\]
 \end{definition}
 
-We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any edge and their $\alpha$ value could change the sets' properties.
-It doesn't affect our analysis, however, since having a split on that player is only possible for $t = 0$ and $\as(0)$ is undefined, plus as we'll show in the next section neither it's limit exists, making the $\alpha$ value of player $x_i(0)$ (in each assumingly split case) irrelevant.
-
+Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for all $i \in N$.
 We continue with describing some basic properties around the values of $\as$.
+
+%We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any edge and their $\alpha$ value could change the sets' properties.
+%It doesn't affect our analysis, however, since having a split on that player is only possible for $t = 0$ and $\as(0)$ is undefined, plus as we'll show in the next section neither it's limit exists, making the $\alpha$ value of player $x_i(0)$ (in each assumingly split case) irrelevant.
 
@@
 	\label{lemma:split_basic}
-	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, the following hold:
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
+	Then the following hold:
 	\begin{enumerate}[(i)]
-		\item $\as(t) > 0$
-		\item if $x_1(t), x_2(t) > 0$ then $\as(t) \in [\alpha(0), \alpha(1)]$
-		\item if $\as(t) < \alpha(0)$ or $\as(t) > \alpha(1)$ then $x(t) = (0, 1)$ or $(1, 0)$
-		\item if $x_1(t), x_2(t) > 0$ with $\ell_1(x_1(t)) < \ell_2(x_2(t))$ then\\
-		$\sup A_1(t) \le \as(t) \le \inf A_2(t)$
+		\item $\as^{(i, j)}(t) > 0$
+		\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
+		%\item if $\as^{(i, j)}(t) < \alpha(0)$ (or $\as^{(i, j)}(t) > \alpha(1)$) then $x(t) = (0, 1)$ (or $(1, 0)$)
+		\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
+		$\sup A_i(t) \le \as^{(i, j)}(t) \le \inf A_j(t)$
 	\end{enumerate}
@@
 		\item Trivial application of Lemma \ref{lemma:latencies_tolls}.
-		Since we have $t_1 \ne t_2$ it follows that $\ell_1(x_1(t)) \ne \ell_2(x_2(t))$ and therefore $\as(t) \ne 0$.
-		Then we only need to notice that $\ell_1(x_1(t)) < \ell_2(x_2(t)) \Leftrightarrow t_1 > t_2$ and we get $\as(t) > 0$ from Definition \ref{definition:split_function}.
-		\item Since $x_1(t), x_2(t) > 0$ then $\exists p_1, p_2 \in [0, 1]$ each on a different link, for which we assume w.l.o.g. that $\alpha(p_1) \le \alpha(p_2)$.
-		It holds from \ref{corollary:split_to_alpha} that $\alpha(p_1) \le \as(t) \le \alpha(p_2)$ so with $\alpha$ being non-decreasing it follows
-		\[\alpha(0) \le \alpha(p_1) \le \as(t) \le \alpha(p_2) \le \alpha(1) \Rightarrow \as(t) \in [\alpha(0), \alpha(1)]\]
-		\item Inverse logic statement of $(ii)$ ($(P \rightarrow Q) \rightarrow (\neg Q \rightarrow \neg P)$).
+		Since we have $t_i \ne t_j$ it follows that $\ell_i(x_i(t)) \ne \ell_j(x_j(t))$ and therefore $\as^{(i, j)}(t) \ne 0$.
+		Then we only need to notice that $\ell_i(x_i(t)) < \ell_j(x_j(t)) \Leftrightarrow t_i > t_j$ and we get $\as^{(i, j)}(t) > 0$ from Definition \ref{definition:split_function}.
+		\item Since $x_i(t), x_j(t) > 0$ then $\exists p_i, p_j \in [0, 1]$ each on a different link, for which we assume w.l.o.g. that $\alpha(p_i) \le \alpha(p_j)$.
+		Then from Corollary \ref{corollary:split_to_alpha} It holds that $\alpha(p_i) \le \as^{(i, j)}(t) \le \alpha(p_j)$.
+		With $\alpha$ being non-decreasing it follows
+		\[\alpha(0) \le \alpha(p_i) \le \as^{(i, j)}(t) \le \alpha(p_j) \le \alpha(1) \Rightarrow \as(t) \in [\alpha(0), \alpha(1)]\]
+		%\item Inverse logic statement of $(ii)$ ($(P \rightarrow Q) \rightarrow (\neg Q \rightarrow \neg P)$).
 		\item Natural consequence from Corollary \ref{corollary:split_to_alpha} and Definition \ref{definition:alpha_flow_sets}.
@@
 
-At this point we should notice that $\as$, similarly to $x$, depends only on the toll difference $t_1 - t_2$ and whether $t_1 < t_2$ or otherwise.
-In order to emphasise on this, let's point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
+At this point we should notice that $\as$, similarly to $x$, depends only on the toll differences and on the toll ordering of the links.
+In order to emphasise on this, let's restrict ourselves to $2$ links and point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
 \[
@@
 \]
-We will not utilise this definition as is in this work, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll difference does in $\R$.
-
-With that in mind, we will investigate the monotonicity of $\as(t)$ in relation to toll differences (and in extension to latency differences).
-For this we will need to compare different tolls that create lower-upper splits in the same edges, or in other words for tolls $t, t^\prime$ to hold that if $t_1 > t_2$ then also $t_1^\prime > t_2^\prime$ and vice-versa.
+We will not utilise this definition as is in this work as it gets more complex for games with $n$ links, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll differences do in $\R^{N - 1}$.
+
+With that in mind, we will investigate the monotonicity of $\as$ in relation to toll differences (and in extension to latency differences) and only when the ordering does not change.
+For this we will need to compare different tolls that create lower-upper splits in the same edges, or in other words for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$ and vice-versa.
 We will capture this with the following condition
@@
 	\label{eq:split_property_cond_tolls_0}
-	\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0
+	\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0
 \end{equation}
-where indeed if $t_1 > t_2$ then
-\[t_1 > t_2 \Leftrightarrow t_1 - t_2 > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_1^\prime - t_2^\prime > 0 \Leftrightarrow t_1^\prime > t_2^\prime\]
-and likewise we also get $t_1 < t_2 \Leftrightarrow t_1^\prime < t_2^\prime$.
-Also note that this property also holds for the respective latencies.
+where indeed if $t_i > t_j$ then
+\[t_i > t_j \Leftrightarrow t_i - t_j > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_i^\prime - t_j^\prime > 0 \Leftrightarrow t_i^\prime > t_j^\prime\]
+and likewise we also get $t_i < t_j \Leftrightarrow t_i^\prime < t_j^\prime$.
+Also note that this property also holds for the respective latencies, meaning that if $t$ and $t^\prime$ define the same link toll ordering, then $\frac{\ell_i(x_i(t_i)) - \ell_j(x_j(t_j))}{\ell_i(x_i(t_i^\prime)) - \ell_j(x_j(t_j^\prime))} > 0$.
 
@@
 	\label{lemma:split_monotonicity}
-	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t, t^\prime \ne 0$ such that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 0$, the following hold:
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t, t^\prime$ such that for some links $i, j \in N$ it holds that $t_i \ne t_j, t_i^\prime \ne t_j^\prime$ and $t_k = t_k^\prime$ for all other $k \in N \setminus \{i, j\}$.
+	If it also holds that $x_i(t), x_j(t), x_i(t^\prime), x_j(t^\prime) > 0$ and $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0$, then the following are true:
 	\begin{enumerate}[(i)]
-		\item if $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1$ then $\as(t) \ge \as(t^\prime)$
-		\item if $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \ge 1$ then $\as(t) \le \as(t^\prime)$
-		\item if $\as(t) > \as(t^\prime)$ then $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} < 1$
-		\item if $\as(t) < \as(t^\prime)$ then $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} > 1$
+		\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1$ then $\as^{(i, j)}(t) \ge \as^{(i, j)}(t^\prime)$
+		\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \ge 1$ then $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$
+		\item if $\as^{(i, j)}(t) > \as^{(i, j)}(t^\prime)$ then $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} < 1$
+		\item if $\as^{(i, j)}(t) < \as^{(i, j)}(t^\prime)$ then $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 1$
 	\end{enumerate}
@@
 	\paragraph{$(i)$}
-	Begin by noticing that $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1 \Rightarrow |t_1 - t_2| \le |t_1^\prime - t_2^\prime|$, i.e.
+	Begin by noticing that $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1 \Rightarrow |t_i - t_j| \le |t_i^\prime - t_j^\prime|$, i.e.
 from $t$ to $t^\prime$ the toll difference is not decreasing, which means that the players in the upper link (i.e.
-the players who already prefer the higher latency and lower toll link) will still view their link as the best option.
+the players who already prefer the higher latency and lower toll link, non-empty from assumption) will still view their link as the best option.
 	Therefore only flow from the lower latency edge, if any, might move towards the slower one.
-	Assume w.l.o.g. that $t_1 > t_2$, giving us $x_1(t) \ge x_1(t^\prime)$ and $x_2(t) \le x_2(t^\prime)$.
-
-	If $x_1(t) = x_1(t^\prime)$, then looking at $\as$ we get
-	\[\as(t^\prime) = \frac{\ell_2(x_2(t^\prime)) - \ell_1(x_1(t^\prime))}{t_2^\prime - t_1^\prime} = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_2^\prime - t_1^\prime} = \as(t) \frac{t_2 - t_1}{t_2^\prime - t_1^\prime}\]
-	so obviously $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1 \Leftrightarrow \as(t^\prime) \le \as(t)$.
-
-	If $x_1(t) > x_1(t^\prime)$ then there exists a player $p$ who is in link $1$ in the Nash equilibrium for $t$ and in link $2$ for the one for $t^\prime$, meaning that from Definition \ref{definition:alpha_flow_sets} we get
-	\[\inf A_2(t^\prime) \le \alpha(p) \le \sup A_1(t)\]
-	By now carefully applying  (twice) the property from Lemma $\ref{lemma:split_basic}(iv)$ we get
-	\[\as(t^\prime) \le \inf A_2(t^\prime) \le \sup A_1(t) \le \as(t)\]
+	Assume w.l.o.g. that $t_i > t_j$, giving us $x_i(t) \ge x_i(t^\prime)$ and $x_j(t) \le x_j(t^\prime)$.
+
+	If $x_i(t) = x_i(t^\prime)$, then looking at $\as^{(i, j)}$ we get
+	\[\as^{(i, j)}(t^\prime) = \frac{\ell_j(x_j(t^\prime)) - \ell_i(x_i(t^\prime))}{t_j^\prime - t_i^\prime} = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_j^\prime - t_i^\prime} = \as^{(i, j)}(t) \frac{t_j - t_i}{t_j^\prime - t_i^\prime}\]
+	so obviously $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1 \Leftrightarrow \as^{(i, j)}(t^\prime) \le \as^{(i, j)}(t)$.
+
+	If $x_i(t) > x_i(t^\prime)$ then there exists a player $p$ who is in link $i$ in the Nash equilibrium for $t$ and in link $j$ for the one for $t^\prime$, meaning that from Definition \ref{definition:alpha_flow_sets} we get
+	\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
+	By now carefully applying  (twice) the property from Lemma $\ref{lemma:split_basic}(iii)$ we get
+	\[\as^{(i, j)}(t^\prime) \le \inf A_j(t^\prime) \le \sup A_i(t) \le \as^{(i, j)}(t)\]
 
@@
 	Symmetrically to $(i)$ in this case the toll difference is non-increasing from $t$ to $t^\prime$, and therefore flow from the higher latency edge will move towards the lower one, i.e.
-$x_1(t) \le x_1(t^\prime)$ and $x_2(t) \ge x_2(t^\prime)$ (assuming again $t_1 > t_2$).
-	With a similar argument we then get $\as(t) \le \as(t^\prime)$.
+$x_i(t) \le x_i(t^\prime)$ and $x_j(t) \ge x_j(t^\prime)$ (assuming again $t_i > t_j$).
+	With a similar argument we then get $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$.
 
 	\paragraph{$(iii)$}
-	Assume $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \ge 1$.
-	Then by $(ii)$ it would hold that $\as(t) \le \as(t^\prime)$ which is a contradiction.
+	Assume $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \ge 1$.
+	Then by $(ii)$ it would hold that $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$ which is a contradiction.
 
 	\paragraph{$(iv)$}
-	Assume $\frac{t_1 - t_2}{t_1^\prime - t_2^\prime} \le 1$.
-	Then by $(i)$ it would hold that $\as(t) \ge \as(t^\prime)$ which is a contradiction.
-\end{proof}
-
-Finally, focusing on the asymptotic behavior or $\as$, we can easily check that when $t_d \rightarrow 0$ the flow approaches $x(0)$.
-However, if $t_1 > t_2$ then $x_1$ (otherwise $x_2$) is the lower split, and from Lemma \ref{lemma:split_basic}$(iv)$ we can see that $\as$ is between the highest value of the lower split and the lowest value of the upper split.
-Therefore the direction of $t_1 > t_2$ matters to as to which $\alpha$ value $\as$ approaches as $t_1 - t_2 \rightarrow 0$, a distinction which we can capture by using $t_1 - t_2 \rightarrow 0^-$ and $t_1 - t_2 \rightarrow 0^+$ accordingly.
+	Assume $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1$.
+	Then by $(i)$ it would hold that $\as^{(i, j)}(t) \ge \as^{(i, j)}(t^\prime)$ which is a contradiction.
+\end{proof}
+
+Finally, focusing on the asymptotic behavior or $\as$, we can easily check that when $t \rightarrow 0$ the flow approaches $x(0)$.
+However, if $t_i > t_j$ then $x_i$ (otherwise $x_j$) is the lower split, and from Lemma \ref{lemma:split_basic}$(iii)$ we can see that $\as$ is between the highest value of the lower split and the lowest value of the upper split.
+Therefore the direction of $t_i > t_j$ matters to as to which $\alpha$ value $\as^{(i, j)}$ approaches as $t_i - t_j \rightarrow 0$, a distinction which we can capture by using $t_i - t_j \rightarrow 0^-$ and $t_i - t_j \rightarrow 0^+$ accordingly.
+However, since $t_i - t_j \rightarrow 0^+$ is equivalent to $t_j - t_i \rightarrow 0^-$, we will focus on the latter.
 
@@
 	\label{lemma:split_asymptotic}
-	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, the following hold:
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
+	Then the following hold:
 	\begin{enumerate}[(i)]
@@
 		\begin{flalign*}
-			\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) &= 0 &
+			\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) &= 0 &
 		\end{flalign*}
@@
 		\begin{flalign*}
-			\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) &= \sup A_1^-(0) \qquad \text{and} \qquad \lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \sup A_2^-(0) &
+			\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \limsup_{t_i - t_j \rightarrow 0^+} A_i(t) &
 		\end{flalign*}
@@
 		\item We only need to notice that
-		\[|\ell_1(x_1(t)) - \ell_2(x_2(t))| \le \max\{\ell_1(1) - \ell_2(0), \ell_2(1) - \ell_1(0)\} = L\]
+		\[|\ell_i(x_i(t)) - \ell_j(x_j(t))| \le \max\{\ell_i(1) - \ell_j(0), \ell_j(1) - \ell_i(0)\} = L\]
 		and we find
-		\[\lim_{|t_1 - t_2| \rightarrow +\infty}|\as(t)| = \lim_{|t_1 - t_2| \rightarrow +\infty}\frac{|\ell_1(x_1(t)) - \ell_2(x_2(t))|}{|t_1 - t_2|} \le \lim_{|t_1 - t_2| \rightarrow +\infty}\frac{L}{|t_1 - t_2|} = 0\]
-		and since $\as(t) > 0$ we get $\lim_{|t_1 - t_2| \rightarrow +\infty}\as(t) = 0$.
-		\item We begin with the first equality.
-		Assume in $[0, x_1(0))$ an increasing sequence $(p_n)_{n \in \mathbb{N}}$ for which $p_n \rightarrow x_1(0)$.
-		From the fact that $x(t)$ is continuous (TODO: add ref?) and that if $x_1(t) < x_1(0)$ then link $1$ has the lower split by definition, we can see that for each $p_n$ we can find (not unique) tolls $t_n$ such that $x_1(t_n) = p_n$.
-		Indeed we can simply solve $\ell_1(p_n) + \alpha(p_n) \cdot t_{n, 1} = \ell_2(1 - p_n) + \alpha(p_n) \cdot t_{n, 2}$ which has as solution a unique toll difference for which $t_{n, 1} - t_{n, 2} > 0$.
-		Obviously $\as(t_n) = \alpha(p_n)$.
-
-		Now notice that, as $p_n$ increases, the toll difference is decreasing, which in turn means from Lemma \ref{lemma:split_monotonicity}$(ii)$, while adding that for $t_1 - t_2 \rightarrow 0^+$ condition \ref{eq:split_property_cond_tolls_0} also holds, that $\as$ is non-decreasing.
-		We can therefore find a non-decreasing sequence $(\as(t_n))_{n \in \mathbb{N}}$ where $t_{n, 1} - t_{n, 2} \rightarrow 0^-$ as $n \rightarrow +\infty$.
-		From all the above, and by observing that $p_n \in A_1^-(0), \forall n \in \mathbb{N}$, we get
-		\[\lim_{t_1 - t_2 \rightarrow 0^+}\as(t) = \lim_{t_{n, 1} - t_{n, 2} \rightarrow 0^+}\as(t_n) = \lim_{n \rightarrow +\infty}\alpha(p_n) = \sup A_1^-(0) \]
-
-		We can show the second equality with a similar argument, as all steps are symmetric for $t_1 - t_2 \rightarrow 0^-$.
+		\begin{flalign*}
+			\lim_{|t_i - t_j| \rightarrow +\infty}|\as^{(i, j)}(t)| &= \lim_{|t_i - t_j| \rightarrow +\infty}\frac{|\ell_i(x_i(t)) - \ell_j(x_j(t))|}{|t_i - t_j|}\\
+			&\le \lim_{|t_i - t_j| \rightarrow +\infty}\frac{L}{|t_i - t_j|} = 0
+		\end{flalign*}
+		and since from Lemma \ref{lemma:split_basic}$(i)$ we have $\as^{(i, j)}(t) > 0$ we get
+		\[\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) = 0\]
+		\item Denote by $P(x_i)$ the set of all players in link $i$, i.e. $P(x_i) = \{p \in [0, 1] | f(p) = i\}$ (using the definition of flow $f$ from Preliminaries).
+		Let $(p_n)_{n \in \mathbb{N}}$ be an increasing sequence of players from $P(x_i(t))$, which is non-empty since $x_i(t) > 0$, such that $p_n \rightarrow \sup P(x_i(t))$.
+		It is simple to see that if $t_i$ increases to $t_i^\prime > t_i$, then $x_i(t_i^\prime, t_{-i}) \le x_i(t)$.
+		%and the fact that $x(t)$ is continuous (TODO: ref?)
+		%\footnote{Harkes et al.
+\cite[Lemma 3.1]{Harks_2019} prove a more general property where also $x_j(t_i^\prime, t_{-i}) \le x_j(t)$ for all $j \ne i$.
+Though it seems that also holds for heterogeneous users, since we don't need the latter property and proving it seems tricky, we omit it from this study.}
+		Therefore we can find a decreasing sequence of $(t_n)_{n \in \mathbb{N}}$ with $t_n \rightarrow t_i$, such that $\max P(x_i(t_n, t_{-i})) = p_n$.
+		Such a $t_n$ might not be unique, though since $t_n > t_i > t_j$, link $i$ always remains the lower split.
+		If $t_n$ is unique, then from the monotonicity of $\as$ (Lemma \ref{lemma:split_monotonicity}) we get $\as^{(i, j)}(t_n, t_{-i}) = \alpha(p_n)$. 
+		Otherwise, it means there is a range of $t_n$ such that $\as^{(i, j)}(t_n, t_{-i}) \ge \alpha(p_n)$, so we select the highest one for which we get equality.
+		Considering all the above, we finally get
+		\begin{flalign*}
+			\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \lim_{t_i - t_j \rightarrow 0^+} \left(\lim_{n \rightarrow +\infty} \as^{(i, j)}(t_n, t_{-i})\right) \\
+			&= \lim_{t_i - t_j \rightarrow 0^+} \left(\lim_{n \rightarrow +\infty} \alpha(p_n)\right) \\
+			&= \lim_{t_i - t_j \rightarrow 0^+} \alpha(\sup P(x_i(t))) \\
+			&= \limsup_{t_i - t_j \rightarrow 0^+} A_i(t)
+		\end{flalign*}
 	\end{enumerate}
 \end{proof}
+
+All the above lemmas can now help us describe the behaviour of $\as$ for different tolls.
+Still, there is a lot of complexity in the properties, mostly due to having many links in our network.
+In order to help with the intuition, we will restrict our final analysis and examples to $2$-link networks, where we get the additional property of interchanging $\limsup_{t_1 - t_2 \rightarrow 0^+} A_1(t)$ with $\alpha(x_1(0))$ (see next corollary).
+Also, the concepts presented here are still valid for $n$-link networks, by simply focusing on the two relevant links and the flow between them.
+We start with the following corollary.
 
@@
 	\label{corollary:split_asymptotic_continuous}
-	Given a $([2], \ell, \alpha)$ toll game with $x_1(0), x_2(0) > 0$ and tolls $t \ne 0$, the following hold:
-	\begin{enumerate}[(i)]
-		\item if $\alpha$ continuous at $x_1(0)$, then
-		\[\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0))\]
-		\item if $\alpha$ continuous at $x_2(0)$, then
-		\[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_2(0))\]
-	\end{enumerate}
+	Let $([2], \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_1 \ne t_2$ and $x_1(t), x_2(t) > 0$.
+	If $\alpha$ is continuous at $x_i(0)$, then
+	\[
+		\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0)) \qquad \text{ and } \qquad \lim_{t_2 - t_1 \rightarrow 0^+} \as(t) = \alpha(x_2(0))
+	\]
 \end{corollary}
 
-All the above lemmas can now help us describe the behaviour of $\as$ for different tolls.
-On one side, as $t_d = t_1 - t_2 \rightarrow -\infty$ then $\as(t) \rightarrow 0$ (Lemma \ref{lemma:split_asymptotic}$(i)$), while afterwards as $t_d$ increases below $0$, meaning the difference (absolute) value is decreasing, then $\as(t)$ is non-decreasing (Lemma \ref{lemma:split_monotonicity}$(i)$), and finally as $t_d \rightarrow 0^-$, $\as(t)$ approaches $\sup A_2^-(0)$ (Lemma \ref{lemma:split_asymptotic}$(ii)$).
+\begin{proof}
+	Using the $P$ set function from the proof of Lemma \ref{lemma:split_asymptotic}$(ii)$, since our network has $2$ links, meaning the flow will either be in link $1$ or $2$, we get that $P(x_1(t)) = [0, x_1(t)]$ or $[1 - x_1(t), 1]$, depending on whether link $1$ is the lower or upper split respectively.
+	Therefore, for $t_1 > t_2$, link $1$ is the lower split and we get $P(x_1(t)) = [0, x_1(t)]$, which also means from Definition \ref{definition:alpha_flow_sets} that $\sup A_1(t) = \alpha(x_1(t))$.
+	Since $\alpha$ is continuous at $x_i(0)$ and $x(t)$ continuous at $t = 0$, we get
+	\[
+		\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \limsup_{t_1 - t_2 \rightarrow 0^+} A_1(t) = \lim_{t_1 - t_2 \rightarrow 0^+} \alpha(x_1(t)) = \alpha(x_1(0))
+	\]
+	The second equation follows from a similar argument on link $2$ for $t_1 < t_2$.
+\end{proof}
+
+\subsection{Function characterisation}
+
+Beginning with the function's characterisation, on one side, as $t_d = t_1 - t_2 \rightarrow -\infty$ then $\as(t) \rightarrow 0$ (Lemma \ref{lemma:split_asymptotic}$(i)$), while afterwards as $t_d$ increases below $0$, meaning the difference (absolute) value is decreasing, then $\as(t)$ is non-decreasing (Lemma \ref{lemma:split_monotonicity}$(i)$), and finally as $t_d \rightarrow 0^-$, $\as(t)$ approaches $\sup A_2^-(0)$ (Lemma \ref{lemma:split_asymptotic}$(ii)$).
 On the other side from $t_d \rightarrow +\infty$ we get a symmetric behavior all the way ending up in $\sup A_1^-(0)$.

### 2024-11-28 thesis/article.tex
Thesis: Generalises upper bound theorem for n-links

@@
 
+TODO: Tolls define ordering $t_1 \ge t_2 \ge \dots t_n$ and $\ell_1(x_1(t)) \le \ell_2(x_2(t)) \le \dots \le \ell_n(x_n(t))$.
+
+\begin{lemma}
+	\label{lemma:xn_xn0_lower_bound}
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
+	For tolls $t \in \R_+^N$ consider the links in decreasing toll ordering.
+	It holds that $x_n(t) \ge x_n(0)$.
+\end{lemma}
+
+\begin{proof}
+	From assumption we have $t_n = \min_{i \in N} t_i$, which makes tolls $t^\prime = t - t_n$ be in $\R_+^N$ with $t_n^\prime = 0$.
+	Since the flow equilibrium $x(t)$ is dependent only on the toll differences, we get $x(t) = x(t^\prime)$.
+	Also, comparing $t^\prime$ with $t = 0$, no additional tolls have been added to link $n$, making $x_n(t^\prime) \ge x_n(0)$.
+	The proposition follows naturally from the previous two statements.
+\end{proof}
+
 \begin{example}
@@
 	\label{lemma:as_upper_bound}
-	Let $([2], \ell, \alpha)$ a toll game with $x_1(0), x_2(0) > 0$.
-	For all $t \in \R_+^2 \setminus \{(a, a) | a \in \R_+\}$, let .
-	It holds that
-	\[\as(t) \le \max\{\sup A_1^-(0), \sup A_2^-(0)\}\]
-	or equivalently if $\alpha$ continuous at $x_1(0)$ and $x_2(0)$
-	\[\as(t) \le \max\{\alpha(x_1(0)), \alpha(x_2(0))\}\]
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
+	For all $i, j \in N, i \ne j$ it holds that
+	\[\as^{(i, j)}(t) \le \max\left\{\limsup_{t_i - t_j \rightarrow 0^+} A_i(t), \limsup_{t_j - t_i \rightarrow 0^+} A_j(t)\right\}\]
+	%or equivalently if $\alpha$ continuous at $x_1(0)$ and $x_2(0)$
+	%\[\as(t) \le \max\{\alpha(x_1(0)), \alpha(x_2(0))\}\]
 \end{lemma}
@@
 \begin{proof}
-	 From Lemmas \ref{lemma:split_asymptotic} and \ref{lemma:split_monotonicity} we get that $\as$, for $t_1 - t_2$ in $(-\infty, 0)$ and $(0, +\infty)$, is non-decreasing and non-increasing respectively.
-	 Therefore $\as$ is upper bounded by its sided limits as $t_1 - t_2 \rightarrow 0$, which means that for all $t \in \R_+^2 \setminus \{(a, a) | a \in \R_+\}$ we get
-	 \[\as(t) \le \max\left\{\lim_{t_1 - t_2 \rightarrow 0^-}\as(t), \lim_{t_1 - t_2 \rightarrow 0^+}\as(t)\right\}\]
-	 which in turn after applying Lemma \ref{lemma:split_asymptotic}$(ii)$ becomes
-	 \[\as(t) \le \max\{\sup A_2^-(0), \sup A_1^-(0)\}\]
+	 From Lemmas \ref{lemma:split_asymptotic} and \ref{lemma:split_monotonicity} (also look the discussion at the function characterisation above) we get that $\as$, for $t_i - t_j$ in $(-\infty, 0)$ and $(0, +\infty)$, is non-decreasing and non-increasing respectively.
+	 Therefore $\as$ is upper bounded by its sided limits as $t_i - t_j \rightarrow 0$, which means that for all $t$ in the domain of $\as$ we get
+	 \[\as^{(i j)}(t) \le \max\left\{\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t), \lim_{t_i - t_j \rightarrow 0^-} \as^{(i, j)}(t)\right\}\]
+	 which in turn, since $t_i - t_j \rightarrow 0^-$ is equivalent to $t_j - t_i \rightarrow 0^+$ and after applying Lemma \ref{lemma:split_asymptotic}$(ii)$, becomes
+	 \[\as^{(i j)}(t) \le \max\left\{\limsup_{t_i - t_j \rightarrow 0^+} A_i(t), \limsup_{t_j - t_i \rightarrow 0^+} A_j(t)\right\}\]
 \end{proof}
@@
 	\label{theorem:alpha_upper_irrelevant}
-	Let $([2], \ell, \alpha^{(1)})$ and $([2], \ell, \alpha^{(2)})$ two toll games with same latency functions, where $x_1(0), x_2(0) > 0$ for their common flow $x(0)$ and distribution functions $\alpha_1$ and $\alpha_2$ such that $\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < \max\{x_1(0), x_2(0)\}$.
-	Then the two games are equivalent.
+	Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games with the common number of links $n = |N|$  and latency functions $\ell$.
+	For $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t \in \R_+^N$ in $\Gm_1, \Gm_2$ respectively, denote as $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the common flow on link of $\Gm_1$ and $\Gm_2$ for $t = 0$.
+	If the distribution functions $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that $\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < 1 - \min_{i \in N}\{x_i(0)\}$, then $\Gm_1$ and $\Gm_2$ are equivalent.
 \end{theorem}
@@
 \begin{proof}
-	For tolls $t \in \R_+^2$ let $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t$ for each game respectively.
-	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \forall t \in \R_+^2$.
-	It's already stated that the equality holds for $t = 0$, i.e. for $t \in \{(a, a) | a \in \R_+\}$.
-	For the remaining $t$, assume w.l.o.g. that $t_1 > t_2$, which now makes it sufficient to show that the flow in the (common) lower split is equal, i.e $x_1^{(1)}(t) \ne x_1^{(2)}(t)$.
-
-	Assume that $x_1^{(1)}(t) \ne x_1^{(2)}(t)$ and again w.l.o.g. that $x_1^{(1)}(t) < x_1^{(2)}(t)$.
-	Then there exists a player $p$ such that $x_1^{(1)}(t) < p \le x_1^{(2)}(t)$ who is on link $2$ on the first game and on link $1$ for the second one.
-	Also note that since $p$ is in the lower split, it holds that $p < \max\{x_1(0), x_2(0)\}$ so by the hypothesis we get $\alpha^{(1)}(p) = \alpha^{(2)}(p)$.
+	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \forall t \in \R_+^N$.
+	It's already stated that the equality holds for $t = 0$.
+	%assume w.l.o.g. that $t_1 > t_2$, which now makes it sufficient to show that the flow in the (common) lower split is equal, i.e $x_1^{(1)}(t) \ne x_1^{(2)}(t)$.
+	For $t \ne 0$, assume for simplicity that all $t_i \ne t_j$ for all $i, j \in N$.
+	Note that since we apply the same tolls $t$ to both game, the ordering they impose on the links is the same.
+	We denote as $i = i^{(1)} = i^{(2)}$ the common corresponding link $i$ between the two games.
+
+	Assume that the theorem does not hold, i.e. $x^{(1)}(t) \ne x^{(2)}(t)$.
+	Then there exists some link $i \in N$ such that $x_i^{(1)}(t) > x_i^{(2)}(t)$, and therefore there exists a player $p$ who is on link $i$ in $\Gm_1$ but not in $\Gm_2$.
+	We can assume that for the link $j$ this player went to in $\Gm_2$ it holds $x_j^{(1)}(t) \le x_j^{(2)}(t)$; if not, then select $j$ and start the same reasoning from the beginning.
+
+	If we consider now the split between $i$ and $j$, player $p$ exist in the lower split for one game and on the upper one for the other, let w.l.o.g. those game be $\Gm_1$ and $\Gm_2$ respectively.
+	So if we take $\Gm_1$ where $p$ in the lower split, then it holds that $p$ is not in $x_n^{(1)}$, since the link with the highest toll is always the upper split with regard to all others.
+	Therefore $p < 1 - x_n^{(1)}$ and from Lemma \ref{lemma:xn_xn0_lower_bound} we then get $p < 1 - x_n(0) < 1 - \min_{i \in N}\{x_i(0)\}$, which from the hypothesis leads us to $\alpha^{(1)}(p) = \alpha^{(2)}(p)$.
+
 	With the above we get
-	\[x_1^{(1)}(t) < x_1^{(2)}(t) \Rightarrow x_1^{(1)}(t) + \alpha^{(1)}(p)t_1 < x_1^{(2)}(t) + \alpha^{(2)}(p)t_1 \Rightarrow c_1^{p, (1)}(t) < c_1^{p, (2)}(t)\]
+	\[x_i^{(1)}(t) > x_i^{(2)}(t) \Rightarrow x_i^{(1)}(t) + \alpha^{(1)}(p)t_i > x_i^{(2)}(t) + \alpha^{(2)}(p)t_i \Rightarrow c_i^{p, (1)}(t) > c_i^{p, (2)}(t)\]
 	and respectively
-	\[x_2^{(1)}(t) > x_2^{(2)}(t) \Rightarrow x_2^{(1)}(t) + \alpha^{(1)}(p)t_2 > x_2^{(2)}(t) + \alpha^{(2)}(p)t_2 \Rightarrow c_2^{p, (1)}(t) > c_2^{p, (2)}(t)\]
-	The above inequations mean that, between the first and the second game, for player $p$, the cost of link $1$ increased while the cost of link $2$ decreased, concluding that $p$ cannot be on link $2$ in the first but then change to link $1$ in the second, which is a contradiction.
-
-	Therefore $x_1^{(1)}(t) = x_1^{(2)}(t)$ for all $t \in \R_+^2 \setminus \{(a, a) | a \in \R_+\}$, and in turn also $x^{(1)}(t) = x^{(2)}(t)$ for all $t \in \R_+$.
-	To conclude, the two games are equivalent.
+	\[x_j^{(1)}(t) \le x_j^{(2)}(t) \Rightarrow x_j^{(1)}(t) + \alpha^{(1)}(p)t_j \le x_j^{(2)}(t) + \alpha^{(2)}(p)t_j \Rightarrow c_j^{p, (1)}(t) \le c_j^{p, (2)}(t)\]
+	The above inequations mean that, between $\Gm_1$ and $\Gm_2$, for player $p$, the cost of link $i$ decreased while the cost of link $j$ didn't, concluding that $p$ cannot be on link $i$ in $\Gm_1$ but then change to link $j$ in $\Gm_2$, which is a contradiction.
+
+	Therefore $x^{(1)}(t) = x^{(2)}(t)$ for all $t \in \R_+$ and from Definition \ref{definition:game_equivalence} the two games are equivalent.
 \end{proof}
@@
 We finish this section with a lemma about the behaviour of $\as$ when many players have money sensitivity close to 0.
-Note that it doesn't suffice to assume $\alpha(0) = 0$ as the behavior of that single player has no effect on the game, so we additionally assume that $0$ is an accumulation point in $\alpha$.
+Note that it doesn't suffice to assume $\alpha(0) = 0$ as the behavior of a single player has no effect on the game, so we additionally assume that $0$ is an accumulation point in $\alpha$.
 \begin{lemma}
-	If for any $i = 1, 2 \; x_i(0) > 0$ and $\alpha(0) = 0$ with $0$ an accumulation point in $\alpha$, then $x_i(t) > 0, \forall t \in \R_+^2$
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game with distribution function $\alpha$ such that $\alpha(0) = 0$ and $0$ is an accumulation point.
+	If for any $i \in N$ it holds that $x_i(0) > 0$, then $x_i(t) > 0, \forall t \in \R_+^N$
 \end{lemma}
@@
 	By the definition of an accumulation point, we get for $0$ in $\alpha$ that $\forall \delta > 0 \; \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
-	Therefore $\forall t \in \R_+^2$ if $\delta = \as(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as(t)$, which means that the lower latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t), x_2(t) > 0$.
-\end{proof}
+	Therefore $\forall t \in \R_+^N$ if $\delta = \min_{j \in N \setminus \{i\}}\as^{(i, j)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(i, j)}(t)$ for all $j \in N \setminus \{i\}$, which means that the lower latency link will always have flow some $\epsilon > 0$, and therefore $x_i(t) > 0$.
+\end{proof}
+Intuitively, the property describes the fact that having almost no toll fear makes a player not motivated to leave the edge, which in turn makes the network having little control over those players using toll regulations.
 

### 2024-11-28 thesis/article.tex
Thesis: Updates Related Work, adds toll boundsnote and missing example plots
Draft #3

@@
 
-%\usepackage{tikz}
 \usepackage{enumerate}
+\usepackage{tikz}
+\usepackage{multicol}
 \usepackage{natbib}
@@
 
-One of the major contributions in this field has been the introduction of the concept of a Nash Equilibrium for networks, defined as Wardrop equilibrium \cite{wardrop_theoretical_1952}.
-
 Congestion games were formally introduced by Rosenthal \cite{Rosenthal1973ACO} who also proved that in those games a pure Nash Equilibrium always exists.
 Later, Monterer-Shapely \cite{MONDERER1996124} defined the class of potential games (games where the incentive for all players to change their strategy can be expressed with a global function) and proved that congestion games are equivalent to exact potential games (potential games where a change in strategy from any player alter the potential function the exact way it alters the player's cost).
-Milchtaich \cite{MILCHTAICH1996111} then investigated the different pay-offs 
+One of the major contributions in this field has been the introduction of the Wardrop equilibrium \cite{wardrop_theoretical_1952}, a notion of Nash equilibrium for potential games, where the Wardrop principles provide a framework to describe and analyse those equilibria.
+Milchtaich \cite{MILCHTAICH1996111} then investigated different pay-off functions for congestion games, where he showed that even though some best-reply strategies may end up in a cyclic path, there is always a path that leads to Nash equilibrium with pure strategies.
+
 Given the above, with the existence of a Nash equilibrium always existing, later research focused on investigating the quality of an equilibrium by using the notion of \textit{Price of Anarchy}, introduced by Koutsoupias-Papadimitriou \cite{KOUTSOUPIAS200965}.
@@
 
+Regarding the model properties, there is a multitude of variations in the classical selfish routing model.
+Beginning with the network topology, one can distinguish between parallel networks (our case) or series-parallel ones.
+In addition the flow traversing through the network can either be atomic (finite number of players, each contributing to congestion equally or weighted) or non-atomic (infinite number of players, each contributing to congestion by an non-influencing infinitesimal amount).
+Also the model might admit elastic demand (e.g.
+\cite{10.1287/moor.1060.0231}, \cite{Hearn1998}), a property where the users have a bound on the cost they're willing to pay, making instances having potential players not participating in the flow.
+
+Most work considers homogeneous network users.
 Heterogeneity has been studied by Schmeilder \cite{1973JSP.....7..295S} and Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220} has contributed through with work on the more general crowding games, a class of games where the cost assigned to each player is affected only by the number of players selecting the same action (or strategy).
 Large crowding games are basically less restrictive $n$-link parallel congestion games.
+Also, Cole et al.
+\cite{10.1145/780542.780618} in their work showed that even general heterogeneous networks can be priced so that an optimal routing emerges while computing those efficient tolls can be done in polynomial time for convex latency functions and distribution functions with only finitely many values.
+The latter paper has been one of the main pillars of this thesis.
 
 Discussing more the algorithmic aspect of toll computation, there has been significant research in finding optimal tolls for homogeneous network users.
-Marginal cost prices can be computed using convex programming \cite{beckmann1956studies},
+Marginal cost prices can be computed using convex programming \cite{beckmann1956studies}, while the transportation community has made significant progress in optimising efficient computation and characterisating minimum-latency tolls (\cite{10.1007/978-3-642-59179-2_4}, \cite{Hearn1998}, \cite{Hearn2002}).
 
@@
 In a follow-up work \cite{10.1109/JSAC.2007.070812}, they generalised the above by assuming more general topologies where links can also be linked serially (series-parallel networks).
+Correa et al. \cite{correa2018pricing} showed pricing games may not exist, may not be unique and can be arbitrarily inefficient, but regulating the network with toll caps can solve all three issues.
+Harkes et al. \cite{Harks_2019} then showed that the same is true for uniform toll caps, which is stronger in practice as toll discrimination is often not allowed.
+The latter two papers have also been main pillars of the current work.
 
@@
 
+This property shows us that for a give $t \in \R_+^N$, if we order the links according to decreasing tolls, then the latencies are ordered in increasing order (and vice-versa).
+It's easy to show that the players in each link are also ordered according to their $\alpha$ value increasing.
+Therefore tolls define an ordering $t_1 \ge t_2 \ge \dots t_n$ where also $\ell_1(x_1(t)) \le \ell_2(x_2(t)) \le \dots \le \ell_n(x_n(t))$ and if we select player representatives from each link $p_1, p_2, \dots, p_n$ we also get $\alpha(p_1) \le \alpha(p_2) \le \dots \le \alpha(p_n)$.
+We continue with the follow lemma which describes a property for the last link in an ordering.
+
+\begin{lemma}
+	\label{lemma:xn_xn0_lower_bound}
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
+	For tolls $t \in \R_+^N$ consider the links in decreasing toll ordering.
+	It holds that $x_n(t) \ge x_n(0)$.
+\end{lemma}
+
+\begin{proof}
+	From assumption we have $t_n = \min_{i \in N} t_i$, which makes tolls $t^\prime = t - t_n$ be in $\R_+^N$ with $t_n^\prime = 0$.
+	Since the flow equilibrium $x(t)$ is dependent only on the toll differences, we get $x(t) = x(t^\prime)$.
+	Also, comparing $t^\prime$ with $t = 0$, no additional tolls have been added to link $n$, making $x_n(t^\prime) \ge x_n(0)$.
+	The proposition follows naturally from the previous two statements.
+\end{proof}
+
+Finally we need to discuss again toll differences.
+While the definition for $t \in \R_+^N$ allows any arbitrary value, there are some edge cases which have little meaning for any game setup.
+Assume that for a toll $t$ where for some link $i \in N$ we have $t_i$ so low that $x_i(t) = 1$ and $x_j(t) = 0$ for all other links $j \ne i$.
+Decreasing $t_i$ further changes nothing, plus in any setup (optimality, maximal profit, etc.) those cases never come into play.
+Same reasoning can be done for increasing $t_i$ to the degree where $x_i(t) = 0$.
+We can therefore see that the valid max toll difference is that which covers the latency imposed on that link by all flow.
+Since we are in a heterogeneous setup, we also need to account for sensitivity, and since we need all players to move in (or out) of a link, it's enough that the least sensitive player is covered.
+In other words, assuming $\alpha(0) > 0$ we get
+\[t_i - t_j \le \alpha(0) \cdot (\ell_i(1) - \ell_j(0)) \qquad t_j - t_i \le \alpha(0) \cdot (\ell_j(1) - \ell_i(0))\]
+for $t_i > t_j$ and $t_j > t_i$ respectively.
+We give an example to solidify all the above.
+
+\begin{example}
+	\label{example:simple_alpha}
+	Let $([2], \ell, \alpha)$ a toll game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha(p) = p + 1$.
+\end{example}
+
+\begin{center}
+	\begin{multicols}{2}
+		% Left Column: Network Graph
+		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
+			% Nodes
+			\node[circle, draw, fill=blue!20, minimum size=1cm] (s) at (0,0) {$s$};
+			\node[circle, draw, fill=blue!20, minimum size=1cm] (t) at (4,0) {$t$};
+
+			% Edges
+			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+			\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
+
+			% Description
+			\node[align=center] at (2, -2) {Network of Example \ref{example:simple_alpha}};
+		\end{tikzpicture}
+
+		% Right Column: Distribution function Graph
+		\begin{tikzpicture}[x=3cm, y=1.5cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
+			\draw[->] (0,0) -- (0,2.2) node[above] {$a(p)$};
+
+			% Tick marks
+			\draw (0,0) -- (0,-0.05) node[below] {$0$};
+			\draw (1,0) -- (1,-0.05) node[below] {$1$};
+			\draw (0,1) -- (-0.05,1) node[left] {$1$};
+			\draw (0,2) -- (-0.05,2) node[left] {$2$};
+
+			% Function graph
+			\draw[thick] (0,1) -- (1,2);
+
+			% Description
+			\node[align=center] at (0.7, -0.7) {Distribution function of\\Example \ref{example:simple_alpha}};
+		\end{tikzpicture}
+	\end{multicols}
+\end{center}
+
+We have $x(0) = (2/3, 1/3)$.
+We also calculate the max toll difference where $x(t) = (0, 1)$ or $(1, 0)$.
+If $t_1 > t_2$ then $x(t) = (1, 0)$ is impossible since we need $\ell_1(x_1(t)) \le \ell_2(x_2(t))$.
+We have $x(t) = (0, 1)$ when even the player with the least money sensitivity views the two edges' costs as equal, i.e.
+\[
+\ell_1(0) + \alpha(0) \cdot t_1 = \ell_2(1) + \alpha(0) \cdot t_2 \Rightarrow t_1 - t_2 = 2
+\]
+Respectively, if $t_1 < t_2$ we have $x(t) = (1, 0)$ when
+\[
+\ell_1(1) + \alpha(0) \cdot t_1 = \ell_2(0) + \alpha(0) \cdot t_2 \Rightarrow t_2 - t_1 = 1
+\]
+
 \section*{Pricing Games (our model)}
@@
 \end{proof}
-
-\subsection*{Heterogeneous players}
-
-TODO: Tolls define ordering $t_1 \ge t_2 \ge \dots t_n$ and $\ell_1(x_1(t)) \le \ell_2(x_2(t)) \le \dots \le \ell_n(x_n(t))$.
-
-\begin{lemma}
-	\label{lemma:xn_xn0_lower_bound}
-	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
-	For tolls $t \in \R_+^N$ consider the links in decreasing toll ordering.
-	It holds that $x_n(t) \ge x_n(0)$.
-\end{lemma}
-
-\begin{proof}
-	From assumption we have $t_n = \min_{i \in N} t_i$, which makes tolls $t^\prime = t - t_n$ be in $\R_+^N$ with $t_n^\prime = 0$.
-	Since the flow equilibrium $x(t)$ is dependent only on the toll differences, we get $x(t) = x(t^\prime)$.
-	Also, comparing $t^\prime$ with $t = 0$, no additional tolls have been added to link $n$, making $x_n(t^\prime) \ge x_n(0)$.
-	The proposition follows naturally from the previous two statements.
-\end{proof}
-
-\begin{example}
-	[TODO: Add figure]
-\end{example}
 
@@
 The above show that $\as(t)$ is continuous for all $t \ne 0$ and any limit around $0$ has different left and right sides (apart from the very specific case where $x_1(0) = x_2(0)$).
-We proceed with an example to solidify this.
-
-\begin{example}
-	\label{example:simple_alpha}
-	Let $([2], \ell, \alpha)$ a toll game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha(p) = p + 1$.
-\end{example}
-TODO: Add figure of game graph.
-
-We have $x(0) = (2/3, 1/3)$.
-Then since $\alpha$ is continuous we get from \ref{corollary:split_asymptotic_continuous} that
+
+We apply this on Example \ref{example:simple_alpha} to solidify this.
+Since $\alpha$ is continuous we get from \ref{corollary:split_asymptotic_continuous} that
 \[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_2(0)) = 4/3, \lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0)) = 5/3\]
-Finally, for a more complete picture, we also calculate the max toll difference where $x(t) = (0, 1)$ or $(1, 0)$.
-If $t_1 > t_2$ then $x(t) = (1, 0)$ is impossible since we need $\ell_1(x_1(t)) \le \ell_2(x_2(t))$.
-We have $x(t) = (0, 1)$ when even the player with the least money sensitivity views the two edges' costs as equal, i.e.
-\[
-	\ell_1(0) + \alpha(0) \cdot t_1 = \ell_2(1) + \alpha(0) \cdot t_2 \Rightarrow t_1 - t_2 = 2
-\]
-Respectively, if $t_1 < t_2$ we have $x(t) = (1, 0)$ when
-\[
-	\ell_1(1) + \alpha(0) \cdot t_1 = \ell_2(0) + \alpha(0) \cdot t_2 \Rightarrow t_2 - t_1 = 1
-\]
-
-All the above give us the graph for $\as$ in Figure \ref{figure:split_example}.
-
-TODO: Add figure of $\as$ for different $t_d$.
+
+All the above give us the graph for $\as$ in Figure \ref{figure:apha_simple:split_example}.
+\begin{center}
+\begin{tikzpicture}[x=5cm, y=2cm, every node/.style={font=\small}]
+	\label{figure:apha_simple:split_example}
+
+	% Axes
+	\draw[->] (0,0) -- (1.2,0) node[right] {$t_1$};
+	\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};
+
+	% Tick marks
+	\draw (0,0) -- (0,-0.05) node[below] {$0$};
+	\draw (0.5,0) -- (0.5,-0.05) node[below] {$t_2$};
+	\draw (0,4/3) -- (-0.05,4/3) node[left] {$4/3$};
+	\draw (0,5/3) -- (-0.05,5/3) node[left] {$5/3$};
+
+	% Function graph
+	\draw[thick] (0,0.1) -- (0.5,4/3);
+	\draw[thick] (0.5,5/3) -- (1,0.1);
+
+	% Dots
+	\fill[white] (0.5,4/3) ellipse (0.02 and 0.04);
+	\draw[black] (0.5,4/3) ellipse (0.02 and 0.04);
+	\fill[white] (0.5,5/3) ellipse (0.02 and 0.04);
+	\draw[black] (0.5,5/3) ellipse (0.02 and 0.04);
+
+	% Description
+	\node[align=center] at (0.7, -0.7) {\textbf{Figure \ref*{figure:apha_simple:split_example}:} Split function of Example \ref{example:simple_alpha}};
+\end{tikzpicture}
+\end{center}
 
@@
 \end{proof}
+
 We can see how this theorem applies to Example \ref{example:simple_alpha}, where since $x(0) = (2/3, 1/3)$ then $\max\{x_1(0), x_2(0)\} = 2/3$.
@@
 
-Unfortunately the results do not scale for $[N]$ parallel networks.
-
-We will conclude this chapter with some investigation on games with continuous distribution function.
-
-\section{Continuous distribution function}
-
-For the continuous distribution function case, the previous restriction of $\alpha(p) > 0$ when $p > 0$ is not sufficient, as it still allows for distribution functions with many player values close to $0$ $\rightarrow$ Is that actually the problem?.
-Specifically the case of $\alpha(p) = cp$, for some $c > 0$, shows some interesting behavior, as it creates instances where $\Pi_i$ becomes either unbounded or fixed; in the first case then $B_i$ becomes unbounded, while in the second it becomes an an infinite set.
-This is showcased analytically in Example \ref{example:ap_p} in the Appendix, where for $\alpha(p) = p$ we see that the resulting best responses can indeed be undefined or unbounded.
-
-When does this happen?
-Is the problem $0$ being an accumulation point?
-\begin{lemma}[Conjecture]
-	If a distribution function has $\alpha(p) \le p \; \forall p$, then $\Pi_i$ becomes either unbounded or fixed.
-\end{lemma}
-
-We will avoid all the above bad behaviors by assuming in all further cases that $\alpha(0) > 0$.
+Unfortunately the results do not scale for $n$-link parallel networks.
+
+%Specifically the case of $\alpha(p) = cp$, for some $c > 0$, shows some interesting behavior, as it creates instances where $\Pi_i$ becomes either unbounded or fixed; in the first case then $B_i$ becomes unbounded, while in the second it becomes an an infinite set.
+%This is showcased analytically in Example \ref{example:ap_p} in the Appendix, where for $\alpha(p) = p$ we see that the resulting best responses can indeed be undefined or unbounded.
+%When does this happen?
+%Is the problem $0$ being an accumulation point?
+%\begin{lemma}[Conjecture]
+%	If a distribution function has $\alpha(p) \le p \; \forall p$, then $\Pi_i$ becomes either unbounded or fixed.
+%\end{lemma}
 

### 2024-12-09 thesis/slides.tex
Thesis: Pres: First entry with template, agenda and citations

\documentclass{beamer}
\usepackage[style=authoryear,backend=bibtex]{biblatex}
\addbibresource{ref.bib}

\mode<presentation>
{
	\usetheme[progressbar=foot,numbering=fraction,background=light,block=fill]{metropolis}
	\usecolortheme{default}
	\usefonttheme{default}
	\setbeamertemplate{navigation symbols}{}
	\setbeamertemplate{caption}[numbered]
	\setbeamertemplate{frame footer}{Thomas Pappas | ALMA }
}

\title[]{Pricing Games in Heterogeneous Parallel Networks}
\author[Thomas Pappas]{Thomas Pappas}
\institute[ALMA]{
	\begin{columns}
		\column{0.4\textwidth}
		\begin{figure}
			\centering
			\includegraphics[scale=0.1]{alma.png}
		\end{figure}
		\column{0.5\textwidth}
		ALMA \\
		\tiny{INTER-INSTITUTIONAL GRADUATE PROGRAM \\
			"ALGORITHMS, LOGIC AND DISCRETE MATHEMATICS"}
	\end{columns}
}
\date{\today}

\begin{document}
\AtBeginSection[]{
  \begin{frame}[noframenumbering,plain]
	  \vfill
	  \centering
	  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
	    \usebeamerfont{title}\insertsectionhead\par
	  \end{beamercolorbox}
	  \vfill
  \end{frame}
}

\begin{frame}[noframenumbering,plain]
  \titlepage
\end{frame}

\begin{frame}[noframenumbering,plain]
    \frametitle{Agenda}
    \tableofcontents[hideallsubsections]
\end{frame}

\section{History}

\begin{frame}{History}
	\begin{itemize}
		\item Selfish routing \footcite{pigou1920economics}
		\item Congestion games \footcite{Rosenthal1973ACO}
		\item Wardrop equilibrium \footcite{wardrop_theoretical_1952}
		\item Pricing competition \footcite{10.1287/moor.1060.0231}
		\begin{itemize}
			\item Homogeneous case with toll caps \footcite{Harks_2019}
		\end{itemize}
	\end{itemize}
\end{frame}

\section{Homogeneous Pricing Games}

\section{Sensitivity split}

\section{Pseudo-heterogeneous Pricing Games}

\section{Step distribution function}

\section{Future work}

\begin{frame}[noframenumbering,plain]{}
	\centering
    \huge Thank you!\\
    \normalsize Thomas Pappas\\
    thpappas@di.uoa.gr
\end{frame}

\end{document}

### 2024-12-15 thesis/slides.tex
Thesis: Pres: Adds Preliminaries first draft
Also adds base skeleton for Sensitivity split

@@
 \documentclass{beamer}
+\usepackage{tikz}
+\usepackage{multicol}
 \usepackage[style=authoryear,backend=bibtex]{biblatex}
@@
 }
+
+% Commands for wrapping properly common expressions.
+\newcommand{\indeq}[1]{\stackrel{\text{#1}}{=}}
+\newcommand{\RightarrowArg}[1]{\stackrel{#1}{\Rightarrow}}
+\newcommand{\LeftrightarrowArg}[1]{\stackrel{#1}{\Leftrightarrow}}
+\newcommand{\NE}{\mathrm{N.E.}}
+\newcommand{\as}{\mathrm{\alpha_s}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\Gm}{\mathcal{G}}
+\DeclareMathOperator*{\argmax}{arg\,max}
 
@@
 
-\section{History}
+\section{Introduction}
 
@@
 
-\section{Homogeneous Pricing Games}
+\begin{frame}{Our model}
+	\begin{center}
+		Heterogeneous Non-atomic $n$-link Parallel Network\\
+		Toll Congestion Pricing Game
+	\end{center}
+\end{frame}
+\begin{frame}{Our model}
+	\begin{center}
+		\textbf{Heterogeneous} Non-atomic $n$-link Parallel Network\\
+		Toll Congestion \textbf{Pricing} Game
+	\end{center}
+\end{frame}
+
+\begin{frame}{Our model}
+	\;
+	\begin{block}{$2$-level optimisation problem}
+		\begin{enumerate}
+			\item Shelfish routing game, flow on minimum cost paths
+			\item Profit maximisation game for link owners
+		\end{enumerate}
+	\end{block}
+\end{frame}
+
+\begin{frame}{Preliminaries}
+	\;
+	\begin{block}{Non-atomic $n$-link Parallel Network Game}
+		A \textbf{Parallel Network} is a directed graph $G = (\{s, t\}, N)$, where $N = \{1, \dots, n\}$ a set of $n$ parallel $s-t$ links.
+
+		For a \textbf{non-atomic} game, a unit of traffic $[0, 1]$, endowed with Lebesque measure $\lambda$, wishes to travel from $s$ to $t$.
+
+		Traffic creates congestion on links and each \textit{player} $p \in [0, 1]$:
+		\begin{itemize}
+			\item is selfish and wants to experience minimum congestion
+			\item has infinitesimal effect on congestion
+		\end{itemize}
+	\end{block}
+
+	\begin{center}
+		\begin{tikzpicture}[scale=0.8, every node/.style={font=\small}]
+			% Nodes
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0, 0) {$s$};
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4, 0) {$t$};
+
+			% Edges
+			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$1$} (t);
+			\draw[->, thick] (s) to[bend left=10] node[midway, above] {$2$} (t);
+			\node[align=center] at (2, 0) {$\vdots$};
+			\draw[->, thick] (s) to[bend right=35] node[midway, above] {$n$} (t);
+		\end{tikzpicture}
+	\end{center}
+\end{frame}
+
+\begin{frame}{Preliminaries}
+	\;
+	\begin{block}{Non-atomic $n$-link Parallel Network Game}
+		Flow $f: [0, 1] \rightarrow N$ is a Lebesque measurable function assigning players to links.
+
+		\textit{Flow on paths} $x_i = \lambda(\{p \in [0, 1]: f(p) = i\})$
+		\begin{itemize}
+			\item $x = (x_i)_{i \in N}$ a (stochastic) vector with $x_i \ge 0$ and $\sum_{i \in N} x_i = 1$
+		\end{itemize}
+		Congestion on links is represented by affine latency functions $(\ell_i)_{i \in N}$ where $\ell_i \in \mathcal{L}_1$, making congestion on link $i$ equal to $\ell_i(x_i)$.
+	\end{block}
+
+	\begin{center}
+		\begin{tikzpicture}[scale=1.2, every node/.style={font=\small}]
+			% Nodes
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0, 0) {$s$};
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4, 0) {$t$};
+
+			% Edges
+			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$\ell_1(x_1)$} (t);
+			\draw[->, thick] (s) to[bend left=10] node[midway, above] {$\ell_2(x_2)$} (t);
+			\node[align=center] at (2, 0) {$\vdots$};
+			\draw[->, thick] (s) to[bend right=35] node[midway, above] {$\ell_n(x_n)$} (t);
+		\end{tikzpicture}
+	\end{center}
+\end{frame}
+
+\begin{frame}{Homogeneous players}
+	Links can be tolled by assigning tolls $t \in \R_+^N$.
+
+	Player $p$ experiences on link $i$ total cost $c_i(p) = \ell_i(x_i) + t_i$.
+	\begin{definition}
+		For a given set of tolls $t$, a flow $x$ is a \textit{Wardrop equilibrium for $t$} if $\forall i, j \in N$ with $x_i > 0$ it holds that
+		\begin{equation*}
+			\ell_i(x_i) + t_i \leq \ell_j(x_j) + t_j
+		\end{equation*}
+	\end{definition}
+	Links with $x_i > 0$ have $\ell_i(x_i) + t_i = K$ for some $K > 0$.
+
+	Wardrop equilibrium always exits and is unique\footcite{??}, denote it by $x(t)$.
+\end{frame}
+
+\begin{frame}{Homogeneous players}
+	\begin{lemma}[variational inequality\footcite{dafermos1973toll}]
+		A flow $x$ is a Wardrop equilibrium for $t$ if and only if for all feasible flows $x^\prime$,
+		\[\sum_{i \in N} (\ell_i(x_i) + t_i) \cdot (x_i - x_i^\prime) \leq 0\]
+	\end{lemma}
+	Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$) or (affine) latencies.
+\end{frame}
+
+\begin{frame}{Heterogeneous players}
+	Players value time-money differently, so add weight $\alpha$ to money.
+	\begin{block}{Distribution function $\alpha: [0, 1] \rightarrow [0, +\infty]$}
+		\begin{itemize}
+			\item players are ordered w.r.t. sensitivity
+			\item $\alpha$ is non-decreasing
+		\end{itemize}
+	\end{block}
+	Player $p$ experiences on link $i$ total cost $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
+	\begin{definition}
+		For a given set of tolls $t$, a flow $x$ is a \textit{Nash equilibrium for $t$} if for all players $p \in [0, 1]$ and $\forall i \in N$ it holds that
+		\begin{equation*}
+			c_{f(p)}(p) \leq c_j(p)
+		\end{equation*}
+	\end{definition}
+\end{frame}
+
+\begin{frame}
+	Nash equilibrium for $t$ always exists\footcite{1973JSP.....7..295S} and is unique\footcite{MILCHTAICH1996111}, again denote it by $x(t)$.
+\end{frame}
+
+\begin{frame}{Pricing competition (2\textsuperscript{nd} level)}
+	Links are owned by agents who compete for profit.
+	\begin{block}{Profit}
+		For given set of tolls $t \in \R_+^N$, link owner $i$ gains profit
+		\[\Pi_i(t) = x_i(t) \cdot t_i\]
+	\end{block}
+
+	\begin{block}{Best response}
+		For fixed tolls assignments from other link owners $t_{-i} = t \setminus \{t_i\}$, link owner $i$ will try and maximise their profit
+		\[B_i(t_{-i}) = \argmax_{t_i \ge 0} \Pi(t_i, t_{-i})\]
+	\end{block}
+\end{frame}
+
+\begin{frame}{Pricing competition (2\textsuperscript{nd} level)}
+	\begin{block}{Nash Equilibrium}
+		A given set of tolls $t$ is a \textit{Nash Equilibrium for the pricing game} if $\forall i \in N$ and $\forall t_i^\prime \in \R_+$
+		\[\Pi_i(t_i, t_{-i}) \geq \Pi_i(t_i^\prime, t_{-i})\]
+	\end{block}
+	\begin{block}{Nash Equilibrium}
+		A given set of tolls $t$ is a \textit{Nash Equilibrium for the pricing game} if
+		$\forall i \in N$ we have $|B_i(t_{-i})| = 1$ and
+		\[t = (B_i(t_{-i}))_{i \in N}\]
+	\end{block}
+\end{frame}
+
+\begin{frame}{Game equivalence}
+	\begin{definition}[Game equivalence]
+		Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
+		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
+	\end{definition}
+\end{frame}
+
+\section{Heterogeneous players}
+
+\begin{frame}{Heterogeneous players}
+	\begin{lemma}
+		For $\Gm = (N, \ell, \alpha)$ with tolls $t$ and flow $x(t)$ the Nash equilibrium for $t$, it holds for all $i, j \in N$ with $x_i(t), x_j(t) > 0$ that
+		\begin{enumerate}[(i)]
+			\item $\ell_i(x_i(t)) < \ell_j(x_j(t))$ iff $t_i > t_j$
+			\item $\ell_i(x_i(t)) = \ell_j(x_j(t))$ iff $t_i = t_j$
+			\item $\ell_i(x_i(t)) > \ell_j(x_j(t))$ iff $t_i < t_j$
+		\end{enumerate}
+	\end{lemma}
+	\begin{proof}
+		Assume $\ell_i(x_i(t)) < \ell_j(x_j(t))$ and $t_i < t_j$ for some $i, j \in N$.
+		Then for \textbf{all} players $c_i(p) < c_j(p)$ so $x_j(t) > 0$ is a contradiction.
+	\end{proof}
+\end{frame}
+
+\begin{frame}{Heterogeneous players}
+	Latencies are viewed the same for all players.
+
+	Toll order is the same for all players.
+
+	Tolls define an ordering of the $N$ links where
+	\begin{itemize}
+		\item $t_1 \ge t_2 \ge \dots \ge t_n$
+		\item $\ell_1(x_1(t)) \le \ell_2(x_2(t)) \le \dots \le \ell_n(x_n(t))$
+		\item for player representatives from each link $p_1, p_2, \dots, p_n$ we also get $\alpha(p_1) \le \alpha(p_2) \le \dots \le \alpha(p_n)$
+	\end{itemize}
+	Ordering is unique only when the toll (and therefore also latency) inequalities are strict.
+\end{frame}
 
 \section{Sensitivity split}
+
+\begin{frame}{Sensitivity split}
+	\begin{definition}
+		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
+		We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
+		\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
+	\end{definition}
+\end{frame}
+
+\begin{frame}{Sensitivity split}
+	\begin{block}{Properties}
+		περιεχόμενο...
+	\end{block}
+\end{frame}
+
+\begin{frame}{Sensitivity split}
+	\begin{block}{Monotonicity}
+		περιεχόμενο...
+	\end{block}
+\end{frame}
+
+\begin{frame}{Sensitivity split}
+	Characterisation.
+\end{frame}
 

### 2024-12-25 thesis/article.tex
Thesis: Final fixes in Chapters 1 and 2, fixes from Th. Lianeas notes
Extended Abstract, Chapter 1 note fixes, Chapter 2 final checks and fixes, overall typos and rewordings

@@
 \chapter*{Abstract}
-In this masters thesis we study a $2$-level optimisation problem where, on an $n$-link network from a source $s$ to a target $t$, a unit of flow wants to move from $s$ to $t$ using the link with the lowest cost, while the link owners compete for profit by assigning tolls to links and thus creating a toll congestion game.
+In this masters thesis we study a $2$-level game where, on an $n$-link network from a source $s$ to a target $t$, a unit of flow wants to move from $s$ to $t$ using the link with the lowest cost, while the link operators compete for profit by assigning tolls to links and thus creating a toll congestion game.
 We examine only affine latencies for the links.
-In addition, each flow player responds to tolls in a heterogeneous way, i.e.
-each flow player $p$ has a different money-time sensitivity value, which is described by a distribution function $\alpha(p)$.
-First we present some basic definitions and properties of profit homogeneous games.
-Using them as base, we examine cases of fixed and step distribution functions, where for the latter we first restrict our model to $2$-link instances and then we present strict conditions for the existence or not of a Nash Equilibrium.
-We then introduce a new term, the split function $\as(t)$, defined as the time-money sensitivity value for which the $2$ link costs are equal for a given set of tolls $t$.
-With the help of $\as$ we will describe and prove some properties of the heterogeneous games for continuous distribution functions.
-In our main result, we generalise the conditions necessary for the existence of a Nash Equilibrium in the profit game between two toll owners, and finally we discuss some extensions to $n$-link parallel networks.
+In addition, each flow user responds to tolls in a heterogeneous way, i.e.
+each player $p$ in the flow has a different money-time sensitivity value, which is described by a distribution function $\alpha(p)$.
+We first present some definitions and properties of pricing homogeneous games, heavily based on previous work, and using them as base, we extend them to describe pricing games with heterogeneous users.
+We introduce a new term, the sensitivity split function $\as(t)$, defined for any $2$ links of the network as the time-money sensitivity value for which, given a set of tolls $t$, the link costs are equal.
+With the help of $\as$ we describe some properties around the selfish behaviour of heterogeneous users for different tolls, as well as prove the existence of bounds for the sensitivity values that are relevant to the game.
+Then, arriving at the main body of this study, we investigate the existence of a Nash Equilibrium in the profit game between the link operators for different cases of heterogeneous users.
+We show there is no Nash Equilibrium when there are many users with $0$ sensitivity, i.e. players not affected by tolls, so we further assume $\alpha(p) > 0$.
+We then investigate cases of fixed distribution functions, which, even though create homogeneous behaviour for the users (making them pseudo-heterogeneous games), help us describe how flow, tolls and equilibria behave as that fixed value changes.
+Using all the above, we study step distribution functions, where by limiting our scope to $2$ links, we present strict conditions necessary for the existence or not of a Nash Equilibrium in the profit game between the link operators.
+We present and analyse an algorithm to calculate that equilibrium, if it exists, and finish with some discussion about potential future work.
 \clearpage
@@
 \chapter*{Συνοψη}
-Σε αυτή τη διπλωματική μεταπτυχιακού μελετάμε ένα πρόβλημα βελτιστοποίησης $2$ επιπέδων, όπου σε ένα δίκτυο με $n$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι δύο ιδιοκτήτες των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
+Σε αυτή τη διπλωματική μεταπτυχιακού μελετάμε ένα παίγνιο $2$ επιπέδων όπου, σε ένα δίκτυο με $n$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι διαχειριστές των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
 Εξετάζουμε μόνο αφινικές καθυστερήσεις για τις ακμές.
-Επιπλέον, ο κάθε παίκτης ροής αντιδρά στα διόδια με ετερογενή τρόπο, δηλ.
-ο κάθε παίκτης ροής $p$ έχει διαφορετική τιμή ευαισθησίας χρόνου-χρήματος, η οποία περιγράφεται από μια συνάρτηση κατανομής $\alpha(p)$.
-Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομογενών παιγνίων κέρδους.
-Mε αυτά ως βάση, εξετάζουμε περιπτώσεις σταθερών και βηματικών συναρτήσεων κατανομής, όπου για το τελευταίο πρώτα περιοριζόμαστε σε στιγμιότυπα $2$ ακμών και παρουσιάζουμε αυστηρές συνθήκες για την ύπαρξη ή μη σημείου ισορροπίας Nash.
-Μετά εισαγάγουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού $\as(t)$, ορισμένη ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία τα κόστη των $2$ ακμών είναι ίσα για ένα δοσμένο σετ διοδίων $t$.
-Με τη βοήθεια της $\as$ θα περιγράψουμε και θα αποδείξουμε μερικές ιδιότητες των ετερογενών παιγνίων με συνεχή συνάρτηση κατανομής.
-Στο κύριο αποτέλεσμά μας, γενικοποιούμε τις συνθήκες που είναι απαραίτητες για την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ δύο ιδιοκτητών ακμών, και τελικώς συζητάμε κάποιες επεκτάσεις για δίκτυα με $n$ ακμές.
+Επιπλέον, ο κάθε χρήστης δικτύου αντιδρά στα διόδια με ετερογενή τρόπο, δηλ.
+ο κάθε παίκτης $p$ στη ροή του δικτύου έχει διαφορετική τιμή ευαισθησίας χρόνου-χρήματος, η οποία περιγράφεται από μια συνάρτηση κατανομής $\alpha(p)$.
+Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομογενών παιγνίων κέρδους, κυρίως βασισμένα σε προηγούμενες δουλειές, και με αυτά ως βάση, τα επεκτείνουμε για να περιγράψουμε παίγνια κέρδους με ετερογενείς χρήστες.
+Εισαγάγουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού ευαισθησίας $\as(t)$, ορισμένη για οποιεσδήποτε $2$ ακμές του δικτύου ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία, δωσμένων σετ διοδίων $t$, τα κόστη των $2$ ακμών είναι ίσα.
+Με τη βοήθεια της $\as$ θα περιγράψουμε μερικές ιδιότητες γύρω από την εγωιστική συμπεριφορά των ετερογενών χρηστών για διαφορετικά διόδια, καθώς και θα αποδείξουμε την ύπαρξη άνω φράγματος για τις τιμές ευαισθησίας που αφορούν το παίγνιο.
+Στη συνέχεια, φτάνοντας στο κύριο σώμα αυτής της έρευνας, εξετάζουμε την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών για διαφορετικές περιπτώσεις ετερογενών χρηστών.
+Δείχνουμε ότι δεν υπάρχει ισορροπία Nash όταν υπάρχουν πολλοί χρήστες με $0$ ευαισθησία, δηλ. παίκτες που δεν επηρρεάζονται από τα διόδια, οπότε στο εξής υποθέτουμε ότι $\alpha(p) > 0$.
+Κατόπιν εξετάζουμε περιπτώσεις όπου η συνάρτηση κατανομής είναι σταθερή, η οποίες, αν και δημιουργούν ομογενή συμπεριφορά στους χρήστες (κάνοντάς τα ψευδο-ετερογενή παίγνια), μας βοηθάνε να περιγράψουμε πώς συμπεριφέρονται η ροή, τα διόδια και τα σημεία ισορροπίας όταν αυτή η σταθερή τιμή μεταβάλλεται.
+Χρησιμοποιώντας όλα τα παραπάνω, μελετάμε βηματικές συναρτήσεις κατανομής, όπου περιορίζοντας το μοντέλο μας σε στιγμιότυπα $2$ ακμών, παρουσιάζουμε αυστηρές συνθήκες αναγκαίες για την ύπαρξη ή μη σημείου ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών.
+Παρουσιάζουμε και αναλύουμε έναν αλγόριθμο για τον υπολογισμό του σημείου ισορροπίας, αν υπάρχει, και κλείνουμε με μια συζήτηση για πιθανή μελοντική δουλειά.
+
 \clearpage
@@
 
-In this thesis we study a two level optimisation problem.
+In this thesis we study a two level game.
 On the basis there is a network with 2 nodes $(s, t)$ and $n$ links, each link directed from $s$ to $t$ and weighted by a non-decreasing latency function that defines how the traffic increases as more players flow into that link.
-On the first level, a flow $[0, 1]$ wants to move from $s$ to $t$ using one of the $n$ links and experience minimum latency (traffic).
-On the second level, each link is owned by a different owner who can add a toll to their link and gain profit proportional to the flow that uses it.
-The tolls impose an additional cost to the flow players, affecting the first level game, and the link owners compete with each other to maximise their profit.
+On the lower level, a flow $[0, 1]$ wants to move from $s$ to $t$ using one of the $n$ links and experience minimum latency (traffic).
+On the upper level, each link is managed by a different operator who can assign a toll to their link and gain profit proportional to that toll and the flow that ends up using the link.
+The tolls impose an additional cost to the flow players, affecting the lower level game, and the link operators compete with each other to maximise their profit.
 In our case we will additionally assume that the flow users behave in a heterogeneous way when it comes to tolls, meaning that each player has a different money-time trade-off and thus see the link costs differently.
@@
 We will then analyse that notion and provide properties and bounds for its values.
-Finally, in the chapter's main result, we prove a general property of homogeneous network games as, due to the previously found bounds, there might be a portion of users whose sensitivity value can be arbitrarily large without affecting the game.
-
-Having arrived at our main results in this work, in Chapter \ref{chapter:pricing_equilibria} we investigate the pricing competition game between the link owners of a network with heterogeneous users.
+Finally, in the chapter's main result, we prove a general property of heterogeneous network games as, due to the previously found bounds, there might be a portion of users whose sensitivity value can be arbitrarily large without affecting the game.
+
+Having arrived at our main results in this work, in Chapter \ref{chapter:pricing_equilibria} we investigate the pricing competition game between the link operators of a network with heterogeneous users.
 We begin by examining a class of games where the distribution function is fixed across all users, which, as we'll formally describe, makes the game \textit{pseudo-heterogeneous}.
@@
 This technique can eradicate the inefficiencies and create optimal flow in the network, however it assumes a strong homogeneity among the users.
-Marginal cost pricing has been investigated in networks with homogeneous users (e.g.
+Marginal cost pricing has been investigated in networks with heterogeneous users (e.g.
 Dafermos \cite{dafermos1973toll}), with the resulting payment required by users on same links being different, an unwanted and non-practical approach, which also requires knowledge of the users' sensitivity beforehand.
@@
 Also the model might admit elastic demand (e.g.
-\cite{10.1287/moor.1060.0231}, \cite{Hearn1998}), a property where the users have a bound on the cost they're willing to pay, making instances having potential players not participating in the flow.
+\cite{10.1287/moor.1060.0231}, \cite{Hearn1998}), a property where users have a bound on the cost they're willing to pay, making a player potentially not participate in the flow if all link costs are above that bound.
 
 Most work considers homogeneous network users.
-Heterogeneity has been studied by Schmeilder \cite{1973JSP.....7..295S} and Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220} has contributed through with work on the more general crowding games, a class of games where the cost assigned to each player is affected only by the number of players selecting the same action (or strategy).
+Heterogeneity has been studied by Schmeilder \cite{1973JSP.....7..295S} while Milchtaich \cite[Prop $3.3$]{doi:10.1287/moor.25.3.349.12220} has contributed through with work on the more general crowding games, a class of games where the cost assigned to each player is affected only by the number of players selecting the same action (or strategy).
 Large crowding games are basically less restrictive $n$-link parallel congestion games.
@@
 
-Acemoglu and Ozdaglar were the first to introduce pricing competition between link owners to the above model \cite{10.1287/moor.1060.0231}.
+Acemoglu and Ozdaglar were the first to introduce pricing competition between link operators to the above model \cite{10.1287/moor.1060.0231}.
 They showed that increasing the competition among operators from a monopoly to an oligopoly may reduce the efficiency of the network, achieving tight bounds on the Price of Anarchy.
@@
 In this section we will describe the model utilised throughout this thesis.
-If we attempted to call that model by including all of its properties, the result would be a Heterogeneous Non-atomic 2-link Parallel Network Toll Congestion Pricing Game, so while we will describe each of those properties, we will eventually focus on heterogeneity and the pricing competition, thus calling it a Heterogeneous Pricing Game.
+If we attempted to call that model by including all of its properties, the result would be a Heterogeneous Non-atomic $n$-link Parallel Network Toll Congestion Pricing Game, so while we will describe each of those properties, we will eventually focus on heterogeneity and the pricing competition, thus calling it a Heterogeneous Pricing Game.
 
@@
 The flow then creates congestion on the links, each described by a non-decreasing latency function $(\ell_i)_{i \in N}$ which we assume to be affine.
-We denote by $\mathcal{L}_d$ the class of polynomial latency functions with nonnegative coefficients and degree at most $d$, and as such $\mathcal{L}_1$ becomes the class of affine latency functions.
+We denote by $\mathcal{L}_d$ the class of polynomial latency functions with nonnegative coefficients and degree at most $d$, and as such $\mathcal{L}_1$ becomes the class of non-decreasing latency functions.
 Finally, the network can also be extended by allowing a set of tolls $t = (t_i)_{i \in N}$ to be assigned to each link, which in turn adds to the effective cost of a player using them.
@@
 
-We can therefore denote by $x(t)$ the flow occurring on that unique equilibrium for a given toll $t$.
+The notion of uniqueness under costs is important in order to acknowledge that a given flow on paths can be achieved by many player-link assignments, since the users can be put arbitrarily on the links, as long as each link is receiving the same total traffic.
+
+We can therefore denote by $x(t)$ the flow occurring on that unique up to costs equilibrium for a given set of toll $t$.
 If $t = 0^N$ then the equilibrium is called the \textit{Wardrop equilibrium}.
@@
 
-Finally for affine latencies we can calculate $x(t)$.
+Finally for affine latencies we can calculate $x(t)$ by following the same reasoning as \cite[Prop $3.1$]{Harks_2019}.
 For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^N$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
@@
 In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different money-time sensitivity values.
-We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of each edge as $c_i^p(t) = \ell_i(x_i(t)) + \alpha(p) \cdot t_i$ and then seek the shortest link among them.
-By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, \infty]$.
+We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of an edge with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
+For a flow $x$ and tolls $t$, each player considers their costs experienced across all links and then selects to use the one (or one of potentially many) with the lowest cost. 
+By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, +\infty]$.
 We call $\alpha$ a \textit{distribution function}.
@@
 
-We can therefore define an instance of a Heterogeneous Pricing Game as the tuple $(N, \ell, \alpha)$ with $N = \{1, 2, \dots, n\}$, $\ell = (\ell_i)_{i \in N}$ and $\alpha$ a non-decreasing distribution function.
-Then with all the above we can again define a Nash equilibrium for the game if $\forall i \in N$ and $\forall p \in [0, 1]$ it holds that
-\[c_{f(p)}^p(t) \leq c_i^p(t)\]
-Existence of an equilibrium is guaranteed by the more general results of Schmeidler \cite[Thm 2]{1973JSP.....7..295S}, while uniqueness is covered by Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220} (see Related Work \ref{section:related_work}); for a more detailed coverage of those look at the definitions and propositions of Cole et al.
+We can therefore define an instance of a Heterogeneous Pricing Game as the tuple $(N, \ell, \alpha)$, with $N = \{1, 2, \dots, n\}$ the links of the network, $\ell = (\ell_i)_{i \in N}$ the affine latency functions for each link and $\alpha$ the non-decreasing distribution function.
+With all the above we can again define a Nash equilibrium for the game if $\forall i \in N$ and $\forall p \in [0, 1]$ it holds that
+\[c_{f(p)}(p) \leq c_i(p)\]
+Existence of an equilibrium is guaranteed by the more general results of Schmeidler \cite[Thm 2]{1973JSP.....7..295S}, while uniqueness with regard to costs is covered by Milchtaich \cite[Prop 3.3]{doi:10.1287/moor.25.3.349.12220} (see Related Work \ref{section:related_work}); for a more detailed coverage of those look at the definitions and propositions of Cole et al.
 \cite[\S2]{10.1145/780542.780618}.
@@
 
-Finally, we will prove here a general property of parallel networks which capture the relationship between latencies and tolls.
-It is trivial for homogeneous games that higher tolls create lower latencies on the respective edges, but for the heterogeneous case it is not straightforward so we'll prove it.
+We will now prove a general property of parallel networks which captures the relationship between latencies and tolls.
+It is trivial for homogeneous games that higher tolls create lower latencies on their respective links, but for the heterogeneous case it is not straightforward so we'll prove it.
 
@@
 	\label{lemma:latencies_tolls}
-	For a Heterogeneous Parallel Game $(N, \ell, \alpha)$ with tolls $t$ and flow $x(t)$ the Nash equilibrium for $t$, it holds for all $i, j \in N$ with $x_i(t), x_j(t) > 0$ that
+	Let $(N, \ell, \alpha)$ a Heterogeneous Parallel Game with tolls $t$ and flow $x(t)$ the Nash equilibrium for $t$.
+	It holds for all $i, j \in N$ with $x_i(t), x_j(t) > 0$ that
 	\begin{enumerate}[(i)]
@@
 	For the left-to-right direction we assume that $\ell_i(x_i(t)) < \ell_j(x_j(t))$.
-	If now $t_i \le t_j$ then for all players $p$ we get $\ell_i(x_i(t)) + \alpha(p) \cdot t_i < \ell_j(x_j(t)) + \alpha(p) \cdot t_j \Rightarrow c_i^p(t) < c_j^p(t)$.
-	Since $x_j(t) > 0$ there exist players $p_j$ on link $j$ for which $c_{f(p_j)}^{p_j}(t) = c_j^{p_j}(t) > c_i^{p_j}(t)$, which is a contradiction since $x(t)$ is a Nash equilibrium.
+	If we also assume that $t_i \le t_j$, then for all players $p$ we get $\ell_i(x_i(t)) + \alpha(p) \cdot t_i < \ell_j(x_j(t)) + \alpha(p) \cdot t_j \Rightarrow c_i(p) < c_j(p)$.
+	Since $x_j(t) > 0$ there exist players $p_j$ on link $j$ for which $c_{f(p_j)}(p_j) = c_j(p_j) > c_i(p_j)$, which is a contradiction since $x(t)$ is a Nash equilibrium.
 	The opposite direction is also proved similarly.
@@
 
-This property shows us that for a give $t \in \R_+^N$, if we order the links according to decreasing tolls, then the latencies are ordered in increasing order (and vice-versa).
-It's easy to show that the players in each link are also ordered according to their $\alpha$ value increasing.
-Therefore tolls define an ordering $t_1 \ge t_2 \ge \dots t_n$ where also $\ell_1(x_1(t)) \le \ell_2(x_2(t)) \le \dots \le \ell_n(x_n(t))$ and if we select player representatives from each link $p_1, p_2, \dots, p_n$ we also get $\alpha(p_1) \le \alpha(p_2) \le \dots \le \alpha(p_n)$.
-We continue with the follow lemma which describes a property for the last link in an ordering.
+This property shows us that for a given $t \in \R_+^N$, if we order the links according to decreasing toll values, then the same link order will have latencies ordered in increasing values (and vice-versa).
+It is then easy to show that the players using each such link are also ordered with regard to their $\alpha$ values in increasing order.
+Therefore a given set of tolls can define an ordering of links where $t_1 \ge t_2 \ge \dots \ge t_n$ and $\ell_1(x_1(t)) \le \ell_2(x_2(t)) \le \dots \le \ell_n(x_n(t))$, while if we were to pick player representatives from each link with positive flow $p_1, p_2, \dots, p_k$, we also get $\alpha(p_1) \le \alpha(p_2) \le \dots \le \alpha(p_k)$.
+Note that the ordering is unique only when the inequalities are strict, as had we had $t_i = t_j$ for any $i, j \in N$ then $i$ and $j$ can be ordered arbitrarily.
+If $t = 0$ then all links can be ordered arbitrarily, which is why when comparing $t$ with $0$ we will assume the ordering is the same for simplicity.
+We continue with the following lemma which describes a property for the last link in such an ordering.
 
@@
 \begin{proof}
-	From assumption we have $t_n = \min_{i \in N} t_i$, which makes tolls $t^\prime = t - t_n$ be in $\R_+^N$ with $t_n^\prime = 0$.
+	Consider $t^\prime = t - t_n$.
+	From assumption we have $t_n = \min_{i \in N} t_i$, which makes $t^\prime \in \R_+^N$ with $t_n^\prime = 0$.
 	Since the flow equilibrium $x(t)$ is dependent only on the toll differences, we get $x(t) = x(t^\prime)$.
-	Also, comparing $t^\prime$ with $t = 0$, no additional tolls have been added to link $n$, making $x_n(t^\prime) \ge x_n(0)$.
+	Also, by now comparing $t^\prime$ with $t = 0$, no additional tolls have been added to link $n$, making $x_n(t^\prime) \ge x_n(0)$.
 	The proposition follows naturally from the previous two statements.
@@
 
-Finally we need to discuss again toll differences.
-While the definition for $t \in \R_+^N$ allows any arbitrary value, there are some edge cases which have little meaning for any game setup.
-Assume that for a toll $t$ where for some link $i \in N$ we have $t_i$ so low that $x_i(t) = 1$ and $x_j(t) = 0$ for all other links $j \ne i$.
-Decreasing $t_i$ further changes nothing, plus in any setup (optimality, maximal profit, etc.) those cases never come into play.
-Same reasoning can be done for increasing $t_i$ to the degree where $x_i(t) = 0$.
-We can therefore see that the valid max toll difference is that which covers the latency imposed on that link by all flow.
-Since we are in a heterogeneous setup, we also need to account for sensitivity, and since we need all players to move in (or out) of a link, it's enough that the least sensitive player is covered.
-In other words, assuming $\alpha(0) > 0$ we get
-\[t_i - t_j \le \alpha(0) \cdot (\ell_i(1) - \ell_j(0)) \qquad t_j - t_i \le \alpha(0) \cdot (\ell_j(1) - \ell_i(0))\]
-for $t_i > t_j$ and $t_j > t_i$ respectively.
-We give an example to solidify all the above.
+Finally we need to discuss about toll differences again.
+While the definition for $t \in \R_+^N$ allows any arbitrary value, the meaningful ones actually reside in a more limited space.
+Assume for example that a toll $t$ is such that $x_i(t) = 1$ for some link $i \in N$ with $t_i > 0$ and $x_j(t) = 0$ for all other links $j \ne i$.
+It's obvious that further decreasing $t_i$ changes nothing for the flow, which is why in any optimisation setup (minimum total cost, maximal profit, etc.) those cases never come into play.
+Same reasoning can be done for increasing $t_i$ in tolls $t$ where $x_i(t) = 0$.
+Therefore there exists an upper bound for the valid toll difference between any two links $i, j \in N$, which can be calculated as the toll difference which even the least sensitive player $0$ (to account for heterogeneity) will view the link with the lowest toll (and all flow) as the one with the lowest cost.
+In other words, assuming $t_i > t_j$ with all flow in $j$ and $\alpha(0) > 0$ we get
+\[\ell_j(1) + \alpha(0) \cdot t_i \le \ell_i(0) + \alpha(0) \cdot t_j \Rightarrow t_i - t_j \le \frac{\ell_j(1) - \ell_i(0)}{\alpha(0)}\]
+In the following chapters we will generalise and investigate more formally this idea, along with the overall relation between the toll and latency differences with regard to sensitivity values.
+
+We conclude this section by providing an example to solidify all the above.
 
@@
 
-We have $x(0) = (2/3, 1/3)$.
-We also calculate the max toll difference where $x(t) = (0, 1)$ or $(1, 0)$.
-If $t_1 > t_2$ then $x(t) = (1, 0)$ is impossible since we need $\ell_1(x_1(t)) \le \ell_2(x_2(t))$.
-We have $x(t) = (0, 1)$ when even the player with the least money sensitivity views the two edges' costs as equal, i.e.
-\[
-\ell_1(0) + \alpha(0) \cdot t_1 = \ell_2(1) + \alpha(0) \cdot t_2 \Rightarrow t_1 - t_2 = 2
-\]
-Respectively, if $t_1 < t_2$ we have $x(t) = (1, 0)$ when
-\[
-\ell_1(1) + \alpha(0) \cdot t_1 = \ell_2(0) + \alpha(0) \cdot t_2 \Rightarrow t_2 - t_1 = 1
-\]
-
-\section*{Pricing Games (our model)}
-
-Arriving at the main model that will be used in this thesis, we keep the above Network Game model and introduce $n = |N|$ agents who each own one link of the network and can thus assign toll to it and gain profit.
-For each link owner $i$, their profit $\Pi_i$ is defined as $\Pi_i = x_i \cdot t_i$, and since we have defined $x(t)$ we can extend $\Pi_i$ to $\Pi_i(t) = x_i(t) \cdot t_i$, which describes the profit of link owner $i$ at the Nash equilibrium for a given toll $t$.
-The link owners compete with each other for profit, each selfishly selecting the toll $t_i$ that will maximise their profit given the remaining tolls $t_{-i}$.
+We can easily calculate that $x(0) = (2/3, 1/3)$ with equal cost $4/3$ in both links.
+If tolls $t = (3, 2)$ are assigned to the links, then $x(3, 2) = (1/4, 3/4)$.
+Indeed, since $t_1 > t_2$ then the flow users with the lowest sensitivity will use link $1$, while the more sensitive ones will use link $2$.
+With players ordered in increasing sensitivity order, the less sensitive link $1$ users will have players $p_1 \in [0, 1/4]$ with $\alpha(p_1) \le \alpha(1/4) = 5/4$ and respectively link $2$ users $p_2 \in (1/4, 1]$ (player $x_i$ can be put arbitrarily in link $1$ or $2$) we have $\alpha(p_2) \ge \alpha(1/4) = 5/4$.
+Finally, all flow users will view the link latencies similarly as
+\[
+\ell\left(\tfrac14, \tfrac34\right) = \left(\ell_1\left(\tfrac14\right), \ell_2\left(\tfrac34\right)\right) = \left(\tfrac24, \tfrac74\right)
+\]
+With all the above we can verify now that for all players in link $1$ it holds that
+\[
+c_1(p) \le c_2(p) \Leftrightarrow \tfrac24 + 3\alpha(p_1) \le \tfrac74 + 2\alpha(p) \Leftrightarrow \alpha(p) \le \tfrac54
+\]
+while the opposite direction also holds similarly for players in link $2$.
+We postpone the discussion of how that flow can be calculated until Chapter \ref{chapter:split}, as we'll require a better notion of the player who views the two links as equal (in this case player $1/4$).
+
+We can also calculate the maximum valid toll difference for each case where all flow is in one link, as the minimum toll difference for which $x(t) = (0, 1)$ or $(1, 0)$.
+If $x(t) = (0, 1)$ then even the player with the least money sensitivity value $\alpha(0) = 1$ views link $2$ as the lowest one, i.e.
+\[
+\ell_2(1) + \alpha(0) \cdot t_2 \le \ell_1(0) + \alpha(0) \cdot t_1 \Rightarrow t_1 - t_2 \ge 2
+\]
+Respectively, if $x(t) = (1, 0)$ then
+\[
+\ell_1(1) + \alpha(0) \cdot t_1 \le \ell_2(0) + \alpha(0) \cdot t_2 \Rightarrow t_2 - t_1 \ge 1
+\]
+We can easily check that, for toll differences tight on the above inequalities, indeed all flow goes into a single link, e.g.
+$x(4, 2) = (0, 1)$ and $x(2, 3) = (1, 0)$, and thus any larger toll difference is meaningless to consider.
+
+\section*{Pricing Games}
+
+Arriving at the main model that will be used in this thesis, we keep the above Network Game model and introduce an agent for each link, hereby called link operator, who can assign a toll to it and gain profit from it.
+For each link operator $i$, their profit $\Pi_i$ is defined as $\Pi_i = x_i \cdot t_i$, and since we have defined $x(t)$ we can extend $\Pi_i$ to $\Pi_i(t) = x_i(t) \cdot t_i$, which describes the profit of link operator $i$ at the Nash equilibrium for a given toll $t$.
+The link operators compete with each other for profit, each selfishly selecting the toll $t_i$ that will maximise their profit, given fixed remaining tolls $t_{-i}$.
 We describe this best response as $B_i(t_{-i}) = \argmax_{t_i \geq 0} \Pi_i(t_i, t_{-i})$.
@@
 \[\Pi_i(t_i, t_{-i}) \geq \Pi_i(t_i^\prime, t_{-i})\]
+or, equivalently, if for all $i \in N$ we have $|B_i(t_{-i})| = 1$ and
+\[t = (B_i(t_{-i}))_{i \in N}\]
 We will denote this toll equilibrium as $t^*$ when relevant.
@@
 
-For homogeneous players, from the work of Harkes et al.
-\cite[Example 4.2]{Harks_2019}, we know that uniqueness of $t^*$ is guaranteed only when $x_i(0) > 0$ for all $i \in N$, a property called the \textit{full Wardrop support assumption}.
+From the work of Harkes et al.
+\cite[Example 4.2]{Harks_2019}, we know that, for homogeneous players, uniqueness of $t^*$ is guaranteed only when $x_i(0) > 0$ for all $i \in N$, a property called the \textit{full Wardrop support assumption}.
 This is seemingly not as much restrictive in practice, as there would be little motivation to add tolls to a route with no traffic.
-From the same work we also get that if the full Wardrop support assumption holds, then $t^*$ is unique \cite[Lemma 3.3]{Harks_2019} and $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ \cite[Lemma 3.2]{Harks_2019}.
-
-Also, for affine latencies, we can calculate the best response functions $B_i(t_{-i})$.
-For each link owner $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
+From the same work we also get that if the full Wardrop support assumption holds, then $t^*$ is unique \cite[Lemma 3.3]{Harks_2019} while also $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ \cite[Lemma 3.2]{Harks_2019}.
+%We will thus assume for all further instances that the full Wardrop support assumption is true.
+Finally, again from Harkes et al. \cite[Lemma 3.3]{Harks_2019} we can also get a formula for the Nash Equilibrium of the pricing game for affine latencies $\ell_i(x) = a_i x + b_i$.
 \begin{equation}
-	\label{eq:homogeneous_br_i}
-	B_i(t_{-i}) = \frac{1 + \sum_{j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \ne i}\frac{2}{a_j}}
+	\label{eq:homogeneous_ne_br_i}
+	t_i^* = \left(a_i + \frac{1}{\sum_{j \ne i} \frac{1}{a_j}}\right) \cdot x_i(t^*)
 \end{equation}
-
-%In the extreme cases where the toll differences are arbitrarily large, the best response of some players will be to lower their toll and take all available flow.
-
-%From Harkes et al. \cite[Lemma 3.3]{Harks_2019} we can also get an equation for the Nash Equilibrium of the pricing game.
-%\begin{equation}
-%	\label{eq:homogeneous_ne_br_i}
-%	t_i^* = \left(a_i + \frac{1}{\sum_{j \ne i} \frac{1}{a_j}}\right) \cdot x_i(t^*)
-%\end{equation}
-
-To describe more properties of homogeneous pricing games we will need the following crucial Lemma.
-\begin{lemma}
-	\label{lemma:tolls_diff}
-	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
-	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
-\end{lemma}
-
-\begin{proof}
-	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
-	From formula \ref{eq:homogeneous_br_i} after some calculations we get
-	\[
-		B_i(t_{-i}) - t_j = \left(\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1\right)t_j + \frac{1 + \frac{b_j - b_i}{a_j} + \sum_{k \ne i, j}\frac{b_k + t_k - b_i}{a_k}}{\sum_{k \ne i} \frac{2}{a_k}}
-	\]
-	which is decreasing with regards to $t_j$ if and only if its coefficient is negative.
-	Indeed, since $a_i > 0$ for all $i$, we get
-	\[
-		\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1 = \frac{1}{2 \left(1 + \sum_{k \ne i, j} \frac{a_j}{a_k}\right)} - 1 \leq \frac{1}{2} - 1 < 0
-	\]
-\end{proof}
 
@@
 	\begin{align*}
-		c_i^p(t) &\le c_j^p(t) \Rightarrow \ell_i(x_i(t)) + \alpha(p) \cdot t_i \le \ell_j(x_j(t)) + \alpha(p) \cdot t_j \\
+		c_i(p) &\le c_j(p) \Rightarrow \ell_i(x_i(t)) + \alpha(p) \cdot t_i \le \ell_j(x_j(t)) + \alpha(p) \cdot t_j \\
 		&\RightarrowArg{t_i > t_j} \alpha(p) \le \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j} \RightarrowArg{\ref{definition:split_function}} \alpha(p) \le \as^{(i, j)}(t)
@@
 One difficulty we need to consider with this approach are cases where $t_i = t_j$ for some links $i, j \in N$.
-For such tolls $t$, even though $x(t)$ is uniquely defined, we get for all players $p$ that $c_i^p(t) = c_j^p(t)$, and thus the players in links $i$ and $j$ can be put arbitrarily in any of the two, regardless of the $\alpha$ value.
+For such tolls $t$, even though $x(t)$ is uniquely defined, we get for all players $p$ that $c_i(p) = c_j(p)$, and thus the players in links $i$ and $j$ can be put arbitrarily in any of the two, regardless of the $\alpha$ value.
 Even if we attempted to put them orderly, it actually matters which edge we will put first, as the link might have different flow volume resulting in different $\alpha$ values within.
@@
 	\label{corollary:a_fixed_c_relation}
-	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
+	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
 	Then the following are true
@@
 What we need to examine  next is how those two games react differently for an edge $i$ given a fixed $t_{-i}$.
-For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference, which is in turn non-increasing with regards to $t_{-i}$ (\ref{lemma:tolls_diff}).
+For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference.
+
+TODO: Fix the next Lemma.
+For affine latencies, we can calculate the best response functions $B_i(t_{-i})$.
+For each link operator $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
+\begin{equation}
+	\label{eq:homogeneous_br_i}
+	B_i(t_{-i}) = \frac{1 + \sum_{j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \ne i}\frac{2}{a_j}}
+\end{equation}
+
+%In the extreme cases where the toll differences are arbitrarily large, the best response of some players will be to lower their toll and take all available flow.
+
+To describe more properties of homogeneous pricing games we will need the following crucial Lemma.
+\begin{lemma}
+	\label{lemma:tolls_diff}
+	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
+	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
+\end{lemma}
+
+\begin{proof}
+	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
+	From formula \ref{eq:homogeneous_br_i} after some calculations we get
+	\[
+	B_i(t_{-i}) - t_j = \left(\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1\right)t_j + \frac{1 + \frac{b_j - b_i}{a_j} + \sum_{k \ne i, j}\frac{b_k + t_k - b_i}{a_k}}{\sum_{k \ne i} \frac{2}{a_k}}
+	\]
+	which is decreasing with regards to $t_j$ if and only if its coefficient is negative.
+	Indeed, since $a_i > 0$ for all $i$, we get
+	\[
+	\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1 = \frac{1}{2 \left(1 + \sum_{k \ne i, j} \frac{a_j}{a_k}\right)} - 1 \leq \frac{1}{2} - 1 < 0
+	\]
+\end{proof}
+
+ which is in turn non-increasing with regards to $t_{-i}$ (\ref{lemma:tolls_diff}).
 Therefore, as $t_{-i}$ increases, the best response gets decreasing difference with $t_{-i}$, thus taking more flow in $x_i$.
@@
 		\]
-		where the second part is the flow in $\Gm_2$ at the best response of link owner $i$ against $\frac{c_1}{c_2} t_{-i}$.
+		where the second part is the flow in $\Gm_2$ at the best response of link operator $i$ against $\frac{c_1}{c_2} t_{-i}$.
 		Therefore their best response against $t_{-i} > \frac{c_1}{c_2} t_{-i}$ will have a lower toll difference to $t_{-i}$ (\ref{lemma:tolls_diff}) and thus more flow, arriving at
@@
 		\item Consider the function $\Pi_i(t_{-i}) = \max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$.
-		Then for $t_{-i} = t_{-i_0}^{(2)}$ we see that in $\Gm_2$ the best response for link owner $i$ is to play the same toll as in the other link, therefore they get max profit at $x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$.
-		In $\Gm_1$ now, since $t_{-i_0}^{(2)} < t_{-i_0}^{(1)}$ then the best response for link owner $i$ is for some $t_i > t_{-i_0}^{(2)}$, and since from \ref{corollary:a_fixed_c_relation}$(i)$ the profit $x_i^{(1)}(0) = x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$ is also one of their options, it means that the profit at $t_i$ is greater, i.e.
+		Then for $t_{-i} = t_{-i_0}^{(2)}$ we see that in $\Gm_2$ the best response for link operator $i$ is to play the same toll as in the other link, therefore they get max profit at $x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$.
+		In $\Gm_1$ now, since $t_{-i_0}^{(2)} < t_{-i_0}^{(1)}$ then the best response for link operator $i$ is for some $t_i > t_{-i_0}^{(2)}$, and since from \ref{corollary:a_fixed_c_relation}$(i)$ the profit $x_i^{(1)}(0) = x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$ is also one of their options, it means that the profit at $t_i$ is greater, i.e.
 		\[
@@
 	Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls, $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
-	Then for each link owner $i$ it holds that $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$.
+	Then for each link operator $i$ it holds that $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$.
 \end{corollary}
@@
 
-In order to be able to describe the different profits on the different intervals of the step function, we introduce a definition of profit for a link owner within a flow section.
+In order to be able to describe the different profits on the different intervals of the step function, we introduce a definition of profit for a link operator within a flow section.
 
@@
 	Let $([2], \ell, \alpha)$ be a heterogeneous pricing game.
-	For a flow interval $[a, b] \subset [0, 1]$ and a link owner $i$, we define the \textit{profit in $[a, b]$} $\Pi_{i, [a, b]}$ as the toll that maximises the link owner's profit against the opposing toll $t_{-i}$, with the flow $x_i(t)$ being within $[a, b]$.
+	For a flow interval $[a, b] \subset [0, 1]$ and a link operator $i$, we define the \textit{profit in $[a, b]$} $\Pi_{i, [a, b]}$ as the toll that maximises the link operator's profit against the opposing toll $t_{-i}$, with the flow $x_i(t)$ being within $[a, b]$.
 	More formally
@@
 
-From this definition it naturally follows that the best response of a link owner $i$ given $t_{-i}$ depends on the max profit value over any set of intervals that completely cover $[0, 1]$.
+From this definition it naturally follows that the best response of a link operator $i$ given $t_{-i}$ depends on the max profit value over any set of intervals that completely cover $[0, 1]$.
 For step distribution functions, this set can be the domains of each of its finitely different values $\alpha_1 < \ldots < \alpha_m$.
@@
 When looking at the flow (and consequently profit) of a specific link $i$, however, the split behaviour of the distribution function makes it possible for different flows having the same money sensitivity split.
-We will therefore use the money sensitivity split function to refer to the respective flows that follow it, and formalise the profit and respective best response of link owner $i$ in the following definition.
+We will therefore use the money sensitivity split function to refer to the respective flows that follow it, and formalise the profit and respective best response of link operator $i$ in the following definition.
 
@@
 	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function and $(A_k)_{k \in [m]}$ the partition of $[0, 1]$ that is defined by the domain of $\alpha$.
-	Then for link owner $i$ the definition of $\Pi_i$ is extended for an interval $A_k$ as
+	Then for link operator $i$ the definition of $\Pi_i$ is extended for an interval $A_k$ as
 	\[
@@
 When it comes to maximising profit for the pricing games, those values included in all $\Pi_{i, k}$ are all we need, because if $\as(t)$ takes any other in-between value, then we are on an instance where no player views the two edge costs as equal, with players viewing a purely smaller cost in either edge.
-For the link owners, this means there at least one who can increase their toll and still keep the flow the same, achieving pure profit.
+For the link operators, this means there at least one who can increase their toll and still keep the flow the same, achieving pure profit.
 This can also happen in edge cases of $\as(t) = \alpha_k$, so we move our full description of this behavior in the following lemma.
@@
 \begin{proof}
-	It suffices to show that there exists link owner $i$ such that $B_i(t_{-i}^\prime) \ne t_i$.
+	It suffices to show that there exists link operator $i$ such that $B_i(t_{-i}^\prime) \ne t_i$.
 	First, notice that from \ref{lemma:split_basic} and \ref{theorem:alpha_upper_irrelevant} we get $\alpha_1 \le \as(t) \le \alpha_k$ for all $t$, and therefore $\as$ is always in-between some $\alpha_k, \alpha_{k+1}$.
@@
 	Let $i$ be that edge which we also assume is the lower split of the flow equilibrium, i.e. $t_i^\prime > t_{-i}^\prime$, and let $k \in [m - 1]$ such that $\alpha_k < \as(t^\prime) < \alpha_{k+1}$.
-	Then link owner $i$ can increase their toll to a $t_i^{\prime\prime} > t_i^\prime$, thus decreasing the value of $\as$, up to the point where $\alpha(t^{\prime\prime}, t_{-i}^\prime) = \alpha_k$.
+	Then link operator $i$ can increase their toll to a $t_i^{\prime\prime} > t_i^\prime$, thus decreasing the value of $\as$, up to the point where $\alpha(t^{\prime\prime}, t_{-i}^\prime) = \alpha_k$.
 	Players in link $i$ will now view their edge as of either lower or equal cost value as the other, while the players in the other link will view theirs as of purely lower cost, making none wishing to change.
@@
 	The restriction of $t^*$ not belonging in the closure of $T_{-\alpha}$ also forbids the latter case, making $\Pi_i(t^*)$ also the global maximum for $\Gm_2$.
-	That condition holds for all link owners $i \in [2]$, therefore $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
+	That condition holds for all link operators $i \in [2]$, therefore $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
 \end{proof}
@@
 			\item[2.1] If $t^*$ in the closure of $T_{-a}$, then there is no Nash equilibrium for the pricing game in $\Gm$.
-			\item[2.2] Otherwise, calculate $\Pi_{i, k}$ for all link owners $i$ and $\alpha_k$ values.
+			\item[2.2] Otherwise, calculate $\Pi_{i, k}$ for all link operators $i$ and $\alpha_k$ values.
 			\begin{enumerate}

### 2024-12-27 thesis/article.tex
Thesis: Final fixes in Chapter 3, fixes from Th. Lianeas notes, rewordings

@@
 In addition, each flow user responds to tolls in a heterogeneous way, i.e.
-each player $p$ in the flow has a different money-time sensitivity value, which is described by a distribution function $\alpha(p)$.
+each player $p$ in the flow has a different time-money sensitivity value, which is described by a distribution function $\alpha(p)$.
 We first present some definitions and properties of pricing homogeneous games, heavily based on previous work, and using them as base, we extend them to describe pricing games with heterogeneous users.
@@
 The tolls impose an additional cost to the flow players, affecting the lower level game, and the link operators compete with each other to maximise their profit.
-In our case we will additionally assume that the flow users behave in a heterogeneous way when it comes to tolls, meaning that each player has a different money-time trade-off and thus see the link costs differently.
+In our case we will additionally assume that the flow users behave in a heterogeneous way when it comes to tolls, meaning that each player has a different time-money trade-off and thus see the link costs differently.
 
@@
 This will also serve as a bridge to Chapter \ref{chapter:preliminaries} were we will set our basis for the rest of the study.
-This includes formal definitions of the models and properties we introduced from previous work as well as some additional -but still basic- properties of the models, with heavy focus on the money-time user sensitivity, captured by a distribution function $\alpha$.
-
-Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money-time sensitivity split}, which captures the notion of a (potentially non-existent) player whose money-time sensitivity makes them view the two links as equal.
+This includes formal definitions of the models and properties we introduced from previous work, as well as some additional -but still basic- properties of the models, with heavy focus on the user's time-money trade-off, captured by a money-sensitivity distribution function $\alpha$.
+
+Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money-sensitivity split}, which captures the notion of a (potentially non-existent) player whose money-sensitivity makes them view the two links as equal.
 We will then analyse that notion and provide properties and bounds for its values.
@@
 
-The above set-up creates a Non-atomic Parallel Network Game with tolls where each player will select the edge that minimises their \textit{individual} traffic latency.
+The above set-up creates a Non-atomic Parallel Network Game with tolls where each player will select the link that minimises their \textit{individual} traffic latency.
 We consider two cases where players either react to tolls in a \textit{homogeneous} or a \textit{heterogeneous} manner.
@@
 
-In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different money-time sensitivity values.
-We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by the player, making them see the cost of an edge with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
+In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different time-money trade-off values.
+We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by a player, making them see the cost of a link with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
 For a flow $x$ and tolls $t$, each player considers their costs experienced across all links and then selects to use the one (or one of potentially many) with the lowest cost. 
@@
 
-			% Edges
+			% Links
 			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
@@
 
-Consider a $([2], \ell, \alpha)$ heterogeneous parallel game with links $[2] = \{1, 2\}$ such that $x_1(0), x_2(0) > 0$ with tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
+One of the main difficulties with heterogeneity is that, for a given set of tolls, flow users with different money-sensitivity values, view toll values also differently, and therefore, in practice, play different games.
+In the analysis of Example \ref{example:simple_alpha} we can find a first glimpse on how to tackle this issue, as we can see that the flow users on each link are organised around the player that views the two link costs as equal.
+This notion will be the center of this chapter, and using it we will try and describe some properties about all users.
+
+We start with a simple example in a network with $2$ links.
+Consider $([2], \ell, \alpha)$, a heterogeneous parallel game with two links $[2] = \{1, 2\}$ such that $x_1(0), x_2(0) > 0$, tolls $t = (t_1, t_2)$ assigned to them and  $x(t) = (x_1(t), x_2(t))$ the Nash equilibrium for $t$.
 Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} leads to $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
-For the $2$ edges of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player sees the $2$ edges' total latencies as equal.
+For the $2$ links of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player views the $2$ links' total costs as equal.
 More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
 \[\ell_1(x_1(t)) + \as(t) \cdot t_1 = \ell_2(x_2(t)) + \as(t) \cdot t_2\]
-Solving for $\as$ we get
+from which, after solving for $\as(t)$, we get
 \[\as(t) = \frac{\ell_2(x_2(t)) - \ell_1(x_1(t))}{t_1 - t_2}\]
@@
 \begin{itemize}
-	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on edge $1$
-	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on edge $2$
-	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on edge $1$ or $2$
+	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on link $1$
+	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on link $2$
+	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on link $1$ or $2$
 \end{itemize}
-Remember that we have assumed that $t_1 > t_2 \Rightarrow \ell_1(x_1(t)) < \ell_2(x_2(t))$.
-Therefore the flow passing through the faster edge $1$ is contained with players where $\alpha(p) \le \as(t)$, while the flow in the cheaper edge $2$ is contained with players where $\alpha(p) \ge \as(t)$.
+Remember that we have assumed that $t_1 > t_2 \stackrel{\ref{lemma:latencies_tolls}}{\Leftrightarrow} \ell_1(x_1(t)) < \ell_2(x_2(t))$.
+Therefore the flow in the lower-latency link $1$ has players with $\alpha(p) \le \as(t)$, while the flow in the higher-latency link $2$ has players with $\alpha(p) \ge \as(t)$.
 Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
-If it helps with the intuition, alternative split labels could be rushed-relaxed or rich-poor.
-Table \autoref{table:split_summary} provides of a summary for each part of the split
+Alternative split labels could be rushed-relaxed or rich-poor.
+\autoref{table:split_summary} provides of a summary of the properties for each part of the split
 
@@
 		\hline
-		& $\alpha(p) \le \as(t)$ & $\alpha(p) \ge \as(t)$ \\ \hline
+		& \textbf{lower split} & \textbf{upper split} \\ \hline
+		$\alpha$ & $\alpha(p) \le \as(t)$ & $\alpha(p) \ge \as(t)$ \\ \hline
+		link & low-latency, high-toll & high-latency, low-toll \\ \hline
 		sensitivity & time $\ge$ money & time $\le$ money \\ \hline
-		latency & lower $(\ell_2)$ & higher $(\ell_1)$ \\ \hline
-		toll & higher $(t_1)$ & lower $(t_2)$ \\ \hline
-		link/edge & low-latency, high-toll $(1)$ & high-latency, low-toll $(2)$ \\ \hline
-		$t_1 - t_2$ & lower & higher \\ \hline
-		split & lower & upper \\ \hline
+		%latency & lower $(\ell_1)$ & higher $(\ell_2)$ \\ \hline
+		%toll & higher $(t_1)$ & lower $(t_2)$ \\ \hline
+		%$t_1 - t_2$ & lower & higher \\ \hline
 	\end{tabular}
@@
 Finally to acknowledge that we have arbitrarily handled any players with $\alpha(p) = \as(t)$.
-Those players, if any, even though they see both edges with equal total cost, in the optimal flow $x$ they have settled in either edge $1$ or $2$.
-We investigate more in depth the relation of $\as$ with the flow in the following Lemmas.
-\\[12pt]
+Those players, if any, even though they see both links with equal total cost, in the optimal flow $x$ they have settled in either link $1$ or $2$.
+We investigate more in depth the relation of $\as$ with the flow in the next propositions.
+
 We can now formally define $\as$ and prove some of its properties.
@@
 \end{definition}
-
-For $t_i = t_j$ any split value will work, so the function is not well-defined for this case.
+We can easily see that if any flow user $p$ has $\alpha(p) = \as^{(i, j)}(t)$ then $c_i(p) = c_j(p)$.
+The fact that the function is not well-defined for $t_i = t_j$ matches with the notion we're trying to capture, as in that case we get $c_i(p) = c_j(p)$ for all flow users of the network, regardless of their money-sensitivity value.
 We will also give a more formal definition to the lower-upper split intuition we described above.
@@
 
-At this point in our analysis, we will need to describe the notion of the lowest and highest $\alpha$ value in a flow of players.
-In general, since we're working with a Lebesque-measurable flow, it is natural to not bother with distinguishing between a flow $[0, x_1]$ or $[0, x_1)$, as the player $x_1$ can be arbitrarily placed at any link without affecting the game.
-In a heterogeneous setting, however, the player's $\alpha(x_1)$ might deterministically put him in a specific link depending on how $\alpha$ is defined, so we need to be careful with our notation.
-We will define the $\alpha$ values of a link's flow in a set and then use border bounds which covers both open and closed intervals.
-
-One difficulty we need to consider with this approach are cases where $t_i = t_j$ for some links $i, j \in N$.
-For such tolls $t$, even though $x(t)$ is uniquely defined, we get for all players $p$ that $c_i(p) = c_j(p)$, and thus the players in links $i$ and $j$ can be put arbitrarily in any of the two, regardless of the $\alpha$ value.
-Even if we attempted to put them orderly, it actually matters which edge we will put first, as the link might have different flow volume resulting in different $\alpha$ values within.
-For this reason we will assume our sets contain all possible $\alpha$ values of any player that might use a link.
-We therefore loose the information about the actual flow splits among those links and keep only the ones among links with different toll values (and in consequence different latencies, Lemma \ref{lemma:latencies_tolls}).
-Still, even with this information loss, we can still observe that
-\begin{enumerate}
-	\item The notion of $\as$ as the $\alpha$ value that views two links as equal is still valid, since such a player will also view as equal any other link with the same toll value as any of the initial two.
-	\item If we limit our scope to only include the links with equal tolls, we actually get a homogeneous sub-game for the total flow in those links.
-\end{enumerate}
-With the above we arrive at the following definition.
+At this point in our analysis, we will need to describe the notion of the lowest and highest $\alpha$ value in a link's flow, which then in turn requires us to look at which interval from the $[0, 1]$ flow is assigned to which link.
+We have assumed that the flow is ordered by increasing $\alpha$ values, so from the fact that for any given set of tolls, any toll ordering defines a respective link ordering where the users are assigned again with increasing $\alpha$ values, it follows that a toll ordering can define a partition of $[0, 1]$ where the elements are the intervals of each link.
+Example \ref{example:simple_alpha}, for instance, has flow on paths $x(3, 2) = (1/4, 3/4)$ which corresponds to partition $\left[0, \tfrac14\right] \cup \left(\tfrac14, 1\right]$ or $\left[0, \tfrac14\right) \cup \left[\tfrac14, 1\right]$, since player $1/4$ views the two link costs as equal.
+
+Using flow on paths to describe the assignment of flow to links, we inherently ignore the edge players of the respective flow intervals as negligible in a Lebesque-measurable flow.
+When looking at $\alpha$ values, however, a player's $\alpha$ value might deterministically put them in a specific link, depending on how $\alpha$ is defined.
+If in Example \ref{example:simple_alpha} we consider a different distribution function where $\alpha(p) = 1$ for $p < 1/4$ and $\alpha(p) = 2$ otherwise, we'd still get $x(3, 2) = (1/4, 3/4)$ (checked similarly as in the example's analysis) but with player $1/4$ strictly selecting link $2$ (since $\alpha(1/4) = 2$) and no player viewing the two link costs equally.
+We will cover both cases of open and closed intervals by using border bounds on the set of all $\alpha$ values of a link's flow.
+
+One other difficulty we need to consider are cases where $t_i = t_j$ for some links $i, j \in N$.
+Remember that $x(t)$ is only uniquely defined with regards to costs, which in extension makes players in such links with equal cost (viewed as such by all players of the game) able to be put arbitrarily in any of the two, regardless of their $\alpha$ value.
+Even if we attempted to assume a link assignment ordered by $\alpha$, the link order also matters, as the (equal latency) links might have different flow volume, resulting in different $\alpha$ values in the flow that uses each.
+We tackle this by assuming that our sets contain all possible $\alpha$ values of any player that might use that link.
+We therefore ignore the information about the actual flow splits among those links and keep only the ones among links with different toll values (and in consequence different latencies, Lemma \ref{lemma:latencies_tolls}).
+%Still, even with this information loss, we observe that
+%\begin{enumerate}
+%	\item The notion of $\as$ as the $\alpha$ value that views two links as equal is still valid, since such a player will also view as equal any other link with the same toll value as any of the initial two.
+%	\item If we limit our scope to only include the links with equal tolls, we actually get a homogeneous sub-game for the total flow in those links.
+%\end{enumerate}
+
+With all the above we arrive at the following definition.
 
@@
 	More formally, we define a set function $A_i: \R_+^N \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
-	\[A_i(t) = \{\alpha(p)|p \text{ in edge } j \text{ for } x(t) \text{ where } t_j = t_i\}\]
+	\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
 \end{definition}
 
-Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for all $i \in N$.
+Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for any $i \in N$.
 We continue with describing some basic properties around the values of $\as$.
 
-%We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any edge and their $\alpha$ value could change the sets' properties.
+%We ignore all $\alpha(x_i(0))$ values in order to avoid any confusion, since they are arbitrarily placed in any link and their $\alpha$ value could change the sets' properties.
 %It doesn't affect our analysis, however, since having a split on that player is only possible for $t = 0$ and $\as(0)$ is undefined, plus as we'll show in the next section neither it's limit exists, making the $\alpha$ value of player $x_i(0)$ (in each assumingly split case) irrelevant.
@@
 	\begin{cases*}
-		x((t_d, 0)) & $t_d \ge 0$ \\
-		x((0, -t_d)) & $t_d < 0$ \\
+		x(t_d, 0) & $t_d \ge 0$ \\
+		x(0, -t_d) & $t_d < 0$ \\
 	\end{cases*}
@@
 With that in mind, we will investigate the monotonicity of $\as$ in relation to toll differences (and in extension to latency differences) and only when the ordering does not change.
-For this we will need to compare different tolls that create lower-upper splits in the same edges, or in other words for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$ and vice-versa.
+For this we will need to compare different tolls that create lower-upper splits in the same links, or in other words for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$ and vice-versa.
 We will capture this with the following condition
@@
 and likewise we also get $t_i < t_j \Leftrightarrow t_i^\prime < t_j^\prime$.
-Also note that this property also holds for the respective latencies, meaning that if $t$ and $t^\prime$ define the same link toll ordering, then $\frac{\ell_i(x_i(t_i)) - \ell_j(x_j(t_j))}{\ell_i(x_i(t_i^\prime)) - \ell_j(x_j(t_j^\prime))} > 0$.
+Also note that this property also holds for the respective latencies, meaning that if $t$ and $t^\prime$ define the same toll ordering on links, then $\frac{\ell_i(x_i(t_i)) - \ell_j(x_j(t_j))}{\ell_i(x_i(t_i^\prime)) - \ell_j(x_j(t_j^\prime))} > 0$.
 
@@
 the players who already prefer the higher latency and lower toll link, non-empty from assumption) will still view their link as the best option.
-	Therefore only flow from the lower latency edge, if any, might move towards the slower one.
+	Therefore only flow from the lower latency link, if any, might move towards the slower one.
 	Assume w.l.o.g. that $t_i > t_j$, giving us $x_i(t) \ge x_i(t^\prime)$ and $x_j(t) \le x_j(t^\prime)$.
@@
 
-	If $x_i(t) > x_i(t^\prime)$ then there exists a player $p$ who is in link $i$ in the Nash equilibrium for $t$ and in link $j$ for the one for $t^\prime$, meaning that from Definition \ref{definition:alpha_flow_sets} we get
+	If $x_i(t) > x_i(t^\prime)$ then there exists a player $p$ who is in link $i$ in the Nash equilibrium for $t$ and in link $j$ for the one for $t^\prime$, meaning that by applying (twice) Definition \ref{definition:alpha_flow_sets} we get
 	\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
@@
 	\paragraph{$(ii)$}
-	Symmetrically to $(i)$ in this case the toll difference is non-increasing from $t$ to $t^\prime$, and therefore flow from the higher latency edge will move towards the lower one, i.e.
+	Arguing symmetrically to $(i)$, we see that in this case the toll difference is non-increasing from $t$ to $t^\prime$, and therefore flow from the higher latency link will move towards the lower one, i.e.
 $x_i(t) \le x_i(t^\prime)$ and $x_j(t) \ge x_j(t^\prime)$ (assuming again $t_i > t_j$).
@@
 
-Finally, focusing on the asymptotic behavior or $\as$, we can easily check that when $t \rightarrow 0$ the flow approaches $x(0)$.
-However, if $t_i > t_j$ then $x_i$ (otherwise $x_j$) is the lower split, and from Lemma \ref{lemma:split_basic}$(iii)$ we can see that $\as$ is between the highest value of the lower split and the lowest value of the upper split.
-Therefore the direction of $t_i > t_j$ matters to as to which $\alpha$ value $\as^{(i, j)}$ approaches as $t_i - t_j \rightarrow 0$, a distinction which we can capture by using $t_i - t_j \rightarrow 0^-$ and $t_i - t_j \rightarrow 0^+$ accordingly.
-However, since $t_i - t_j \rightarrow 0^+$ is equivalent to $t_j - t_i \rightarrow 0^-$, we will focus on the latter.
+Finally, focusing on the asymptotic behavior or $\as^{(i, j)}$, we can easily check that when $t \rightarrow 0$ the flow approaches $x(0)$.
+However, if $t_i > t_j$ then $x_i$ (otherwise $x_j$) is the lower split, and from Lemma \ref{lemma:split_basic}$(iii)$ we can see that $\as^{(i, j)}$ is between the highest value of the lower split and the lowest value of the upper split.
+Therefore the direction of $t_i > t_j$ matters to as to which $\alpha$ value $\as^{(i, j)}$ approaches as $t_i - t_j \rightarrow 0$, a distinction which we can capture by using side limits $t_i - t_j \rightarrow 0^-$ and $t_i - t_j \rightarrow 0^+$ accordingly.
+However, since $t_i - t_j \rightarrow 0^+$ is equivalent to $t_j - t_i \rightarrow 0^-$, it suffices to focus on one of them.
 
@@
 		\[\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) = 0\]
-		\item Denote by $P(x_i)$ the set of all players in link $i$, i.e. $P(x_i) = \{p \in [0, 1] | f(p) = i\}$ (using the definition of flow $f$ from Preliminaries).
-		Let $(p_n)_{n \in \mathbb{N}}$ be an increasing sequence of players from $P(x_i(t))$, which is non-empty since $x_i(t) > 0$, such that $p_n \rightarrow \sup P(x_i(t))$.
-		It is simple to see that if $t_i$ increases to $t_i^\prime > t_i$, then $x_i(t_i^\prime, t_{-i}) \le x_i(t)$.
+		\item We are interested in $\as^{(i, j)}(t)$ when $t_i > t_j$, i.e. when link $i$ has the lower split.
+		Denote by $P_i(t)$ the set of all players in link $i$ in the Nash Equlibrium for $t$, i.e. $P_i(t) = \{p \in [0, 1] | f(p) = i\}$.
+		$P_i(t)$ is non-empty since $x_i(t) > 0$.
+
+		Let $(t_{i_m})_{m \in \mathbb{N}}$ a decreasing sequence of tolls in link $i$, such that $t_{i_m} \rightarrow t_i$.
+		We know that as a toll decreases, the link can only gain flow, which in turn makes $(x_i(t_{i_m}, t_{-i}))_{m \in \mathbb{N}}$ non-decreasing with $x_i(t_{i_m}, t_{-i}) \rightarrow x_i(t)$.
+		Therefore we can define from each $t_{i_m}$ an edge player $(p_m)_{m \in \mathbb{N}}$ such that $p_m = \sup P_i(t_{i_m}, t_{-i})$, thus making the non-decreasing sequence $(p_m)_{m \in \mathbb{N}}$ with $p_m \rightarrow \sup P_i(t)$.
+
+		Corollary \ref{corollary:split_to_alpha} gives us $\alpha(p_m) \le \as^{(i, j)}(t_{i_m}, t_{-i})$ for all $m \in \mathbb{N}$.
+		If the inequality holds as equality (in which case $c_i(p_m) = c_j(p_m)$), we take $t_{i_m}^\prime = t_{i_m}$.
+		Otherwise, it holds for all players in link $i$ that $c_i(p) < c_j(p)$, which means there is room to increase $t_{i_m}$ with no link users leaving the link (also no player from other links will enter a more expensive one), making the total flow remain the same.
+		Since we're interested in $t_i$ values very close to $t_j$, we can safely assume that $i, j$ are consequent links in the toll ordering on links defined by $t$, and since $t_{i_m} \rightarrow t_i$ we can also assume that no $t_{i_m}$ element breaks that ordering.
+		We can therefore see from Lemma \ref{lemma:split_monotonicity} that if we take $t_{i_m}^\prime > t_{i_m}$ then $\as^{(i, j)}(t_{i_m}^\prime, t_{-i}) \le \as^{(i, j)}(t_{i_m}, t_{-i})$, so we do so until we again reach the point where the most sensitive player of the link will view the $i, j$ link costs equally, i.e.
+$\alpha(p_m) = \as^{(i, j)}(t_{i_m}^\prime, t_{-i})$.
+		That increase doesn't break the monotonicity of the sequence, since the increase will happen at most until the value of the previous sequence element is reached, for which we've already checked that the inequality from Corollary \ref{corollary:split_to_alpha} is tight.
+		Therefore, the updated toll sequence $(t_{i_m}^\prime)_{m \in \mathbb{N}}$ becomes non-decreasing with $t_{i_m}^\prime \rightarrow t_i^\prime$ and it holds for all elements that
+		\[\alpha(p_m) = \as^{(i, j)}(t_{i_m}^\prime, t_{-i})\]
+
+		Finally we need to notice that from Lemma \ref{lemma:latencies_tolls} we have $t_i = t_j$ if and only if $\ell_i(x_i(t)) = \ell_j(x_j(t))$, so as $t_i - t_j$ approaches $0$, $\ell_i(x_i(t)) - \ell_j(x_j(t))$ also asymptotically approaches $0$.
+		From the fact that, as $t_i$ approaches $t_j$, the flow also needs to change to approach $\ell_i(x_i(t)) = \ell_j(x_j(t))$, it seems safe to assume that for $t_i$ arbitrarily close to $t_j$ there will be players viewing the two links as equal, making the corollary inequality tight, and in turn $t_i^\prime = t_i$.
+
 		%and the fact that $x(t)$ is continuous (TODO: ref?)
@@
 Though it seems that also holds for heterogeneous users, since we don't need the latter property and proving it seems tricky, we omit it from this study.}
-		Therefore we can find a decreasing sequence of $(t_n)_{n \in \mathbb{N}}$ with $t_n \rightarrow t_i$, such that $\max P(x_i(t_n, t_{-i})) = p_n$.
-		Such a $t_n$ might not be unique, though since $t_n > t_i > t_j$, link $i$ always remains the lower split.
-		If $t_n$ is unique, then from the monotonicity of $\as$ (Lemma \ref{lemma:split_monotonicity}) we get $\as^{(i, j)}(t_n, t_{-i}) = \alpha(p_n)$. 
-		Otherwise, it means there is a range of $t_n$ such that $\as^{(i, j)}(t_n, t_{-i}) \ge \alpha(p_n)$, so we select the highest one for which we get equality.
-		Considering all the above, we finally get
+		%Let $(p_n)_{n \in \mathbb{N}}$ be an increasing sequence of players from $P_i(t)$, which , such that $p_n \rightarrow \sup P_i(t)$.
+		%Therefore we can find a decreasing sequence of $(t_{i_n})_{i_n \in \mathbb{N}}$ with $t_{i_n} \rightarrow t_i$, such that $\max P_i(t_{i_n}, t_{-i}) = p_n$.
+		%Such a $t_n$ might not be unique, though since $t_n > t_i > t_j$, link $i$ always remains the lower split.
+		%If $t_n$ is unique, then from the monotonicity of $\as$ (Lemma \ref{lemma:split_monotonicity}) we get $\as^{(i, j)}(t_n, t_{-i}) = \alpha(p_n)$. 
+		%Otherwise, it means there is a range of $t_n$ such that $\as^{(i, j)}(t_n, t_{-i}) \ge \alpha(p_n)$, so we select the highest one for which we get equality.
+
+		Considering all the above, while also noting that from Definition \ref{definition:alpha_flow_sets} we have $\alpha(P_i(t)) = A_i(t)$, we finally get
 		\begin{flalign*}
-			\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \lim_{t_i - t_j \rightarrow 0^+} \left(\lim_{n \rightarrow +\infty} \as^{(i, j)}(t_n, t_{-i})\right) \\
-			&= \lim_{t_i - t_j \rightarrow 0^+} \left(\lim_{n \rightarrow +\infty} \alpha(p_n)\right) \\
-			&= \lim_{t_i - t_j \rightarrow 0^+} \alpha(\sup P(x_i(t))) \\
+			\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t_i^\prime, t_{-i})\\
+			&= \lim_{t_i - t_j \rightarrow 0^+} \left(\lim_{m \rightarrow +\infty} \as^{(i, j)}(t_{i_m}^\prime, t_{-i})\right) \\
+			&= \lim_{t_i - t_j \rightarrow 0^+} \left(\lim_{m \rightarrow +\infty} \alpha(p_m)\right) \\
+			&= \lim_{t_i - t_j \rightarrow 0^+} \alpha(\sup P_i(t)) \\
 			&= \limsup_{t_i - t_j \rightarrow 0^+} A_i(t)
@@
 
-All the above lemmas can now help us describe the behaviour of $\as$ for different tolls.
-Still, there is a lot of complexity in the properties, mostly due to having many links in our network.
-In order to help with the intuition, we will restrict our final analysis and examples to $2$-link networks, where we get the additional property of interchanging $\limsup_{t_1 - t_2 \rightarrow 0^+} A_1(t)$ with $\alpha(x_1(0))$ (see next corollary).
-Also, the concepts presented here are still valid for $n$-link networks, by simply focusing on the two relevant links and the flow between them.
+All the above lemmas can now help us describe the behaviour of $\as$ for different tolls, and more specifically how it behaves with regards to $t_i$ for a fixed $t_{-i}$.
+The main challenge in this analysis is that a changing $t_i$ can affect the sensitivity split of multiple link pairs, while even the link ordering is not always fixed, as we can put link $i$ at any place by selecting an appropriate $t_i$.
+In order to help with the intuition, we will simplify our final analysis to $2$-link networks, where we essentially have two possible toll orderings, thus giving us a simplified look on what happens when that ordering changes.
+Note that the concepts presented here are still valid for $n$-link networks, if we simply focus on consecutive links.
 We start with the following corollary.
@@
 	\label{corollary:split_asymptotic_continuous}
-	Let $([2], \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_1 \ne t_2$ and $x_1(t), x_2(t) > 0$.
-	If $\alpha$ is continuous at $x_i(0)$, then
-	\[
-		\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0)) \qquad \text{ and } \qquad \lim_{t_2 - t_1 \rightarrow 0^+} \as(t) = \alpha(x_2(0))
+	Let $([2], \ell, \alpha)$ a heterogeneous parallel game and tolls $t = (t_1, t_2)$ such that $t_1 > t_2$ and $x_1(t) > 0$.
+	If $\alpha$ is continuous at $x_1(0)$, then
+	\[
+		\lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0))
 	\]
@@
 \begin{proof}
-	Using the $P$ set function from the proof of Lemma \ref{lemma:split_asymptotic}$(ii)$, since our network has $2$ links, meaning the flow will either be in link $1$ or $2$, we get that $P(x_1(t)) = [0, x_1(t)]$ or $[1 - x_1(t), 1]$, depending on whether link $1$ is the lower or upper split respectively.
-	Therefore, for $t_1 > t_2$, link $1$ is the lower split and we get $P(x_1(t)) = [0, x_1(t)]$, which also means from Definition \ref{definition:alpha_flow_sets} that $\sup A_1(t) = \alpha(x_1(t))$.
-	Since $\alpha$ is continuous at $x_i(0)$ and $x(t)$ continuous at $t = 0$, we get
+	Since $t_1 > t_2$ then link $1$ is the lower split and, using the $P_i$ set function from the proof of Lemma \ref{lemma:split_asymptotic}$(ii)$, we get that $P_1(x_1(t)) = [0, x_1(t)]$ or $[0, x_1(t))$.
+	In either case, from Definition \ref{definition:alpha_flow_sets} we get $\sup A_1(t) = \alpha(\sup P_1(t)) =  \alpha(x_1(t))$.
+	We see that
 	\[
@@
 	\]
-	The second equation follows from a similar argument on link $2$ for $t_1 < t_2$.
+	The first equality follows from Lemma \ref{lemma:split_asymptotic}$(ii)$, the second from the relation discussed above and the last one from the fact that $\alpha$ is continuous at $x_1(0)$ and $x(t)$ continuous at $t = 0$.
 \end{proof}
@@
 
-Beginning with the function's characterisation, on one side, as $t_d = t_1 - t_2 \rightarrow -\infty$ then $\as(t) \rightarrow 0$ (Lemma \ref{lemma:split_asymptotic}$(i)$), while afterwards as $t_d$ increases below $0$, meaning the difference (absolute) value is decreasing, then $\as(t)$ is non-decreasing (Lemma \ref{lemma:split_monotonicity}$(i)$), and finally as $t_d \rightarrow 0^-$, $\as(t)$ approaches $\sup A_2^-(0)$ (Lemma \ref{lemma:split_asymptotic}$(ii)$).
-On the other side from $t_d \rightarrow +\infty$ we get a symmetric behavior all the way ending up in $\sup A_1^-(0)$.
-The above show that $\as(t)$ is continuous for all $t \ne 0$ and any limit around $0$ has different left and right sides (apart from the very specific case where $x_1(0) = x_2(0)$).
-
+Arriving at the function's characterisation, we will fix $t_2$ (arbitrarily large, if needed) and investigate $\as(t)$ as $t_1$ goes from $0$ to $+\infty$, or equivalently, as $t_d = t_1 - t_2$ takes values in $(-\infty, 0) \cup (0, +\infty)$.
+Starting from the left side, we know from Lemma \ref{lemma:split_asymptotic}$(i)$ that $\lim_{t_d \rightarrow -\infty} \as(t) = 0$, with link $2$ being the lower split since $t_d < 0$.
+By keeping $t_d < 0$ we also maintain the toll order, so as $t_d$ increases (which means the absolute toll difference decreases) from Lemma \ref{lemma:split_monotonicity}$(i)$ we get that $\as$ is non-decreasing.
+Eventually, Lemma \ref{lemma:split_asymptotic}$(ii)$ gives us that $\lim_{t_d \rightarrow 0^-} \as(t) = \limsup_{t_d \rightarrow 0^-} A_2(t)$.
+Proceeding to cases where $t_d > 0$, we symmetrically get $\lim_{t_d \rightarrow 0^+} \as(t) = \limsup_{t_d \rightarrow 0^+} A_1(t)$, $\as$ non-increasing as $t_d$ increases and $\lim_{t_d \rightarrow +\infty} = 0$.
+
+The above show that $\as(t)$ is continuous for all $t \ne 0$, approaches $0$ at large toll differences and increases as that difference approaches $0$, thus making the side limits around $0$ have different values (apart from the very specific case where $x_1(0) = x_2(0)$).
 We apply this on Example \ref{example:simple_alpha} to solidify this.
-Since $\alpha$ is continuous we get from \ref{corollary:split_asymptotic_continuous} that
+Since $\alpha$ is continuous we get from Corollary \ref{corollary:split_asymptotic_continuous} that
 \[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_2(0)) = 4/3, \lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0)) = 5/3\]
@@
 
-Having now a good overview of the overall values $\as$, we notice that there exist values of $\alpha$ that will never be a value of $\as$.
+Having now a good overview of the overall values of $\as$, we notice that there exist values of $\alpha$ that will never be a value of $\as$.
 Do then those values actually affect our game in any way?
@@
 \begin{proof}
-	 From Lemmas \ref{lemma:split_asymptotic} and \ref{lemma:split_monotonicity} (also look the discussion at the function characterisation above) we get that $\as$, for $t_i - t_j$ in $(-\infty, 0)$ and $(0, +\infty)$, is non-decreasing and non-increasing respectively.
+	 From Lemmas \ref{lemma:split_asymptotic} and \ref{lemma:split_monotonicity} (also look the discussion at the function characterisation above) we get that, for $t_i - t_j$ in $(-\infty, 0)$ and $(0, +\infty)$, $\as$ is non-decreasing and non-increasing respectively.
 	 Therefore $\as$ is upper bounded by its sided limits as $t_i - t_j \rightarrow 0$, which means that for all $t$ in the domain of $\as$ we get
 	 \[\as^{(i j)}(t) \le \max\left\{\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t), \lim_{t_i - t_j \rightarrow 0^-} \as^{(i, j)}(t)\right\}\]
-	 which in turn, since $t_i - t_j \rightarrow 0^-$ is equivalent to $t_j - t_i \rightarrow 0^+$ and after applying Lemma \ref{lemma:split_asymptotic}$(ii)$, becomes
-	 \[\as^{(i j)}(t) \le \max\left\{\limsup_{t_i - t_j \rightarrow 0^+} A_i(t), \limsup_{t_j - t_i \rightarrow 0^+} A_j(t)\right\}\]
+	 which in turn, after applying Lemma \ref{lemma:split_asymptotic}$(ii)$ while noticing that $t_i - t_j \rightarrow 0^-$ is equivalent to $t_j - t_i \rightarrow 0^+$, becomes
+	 \[\as^{(i, j)}(t) \le \max\left\{\limsup_{t_i - t_j \rightarrow 0^+} A_i(t), \limsup_{t_j - t_i \rightarrow 0^+} A_j(t)\right\}\]
 \end{proof}
@@
 	\label{theorem:alpha_upper_irrelevant}
-	Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games with the common number of links $n = |N|$  and latency functions $\ell$.
-	For $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t \in \R_+^N$ in $\Gm_1, \Gm_2$ respectively, denote as $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the common flow on link of $\Gm_1$ and $\Gm_2$ for $t = 0$.
-	If the distribution functions $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that $\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < 1 - \min_{i \in N}\{x_i(0)\}$, then $\Gm_1$ and $\Gm_2$ are equivalent.
+	Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games with the same number of links $n = |N|$  and latency functions $\ell$.
+	For $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t \in \R_+^N$ in $\Gm_1, \Gm_2$ respectively, denote as $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the equal flow on paths between $\Gm_1$ and $\Gm_2$ for $t = 0$.
+	If the distribution functions $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that
+	\[\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < 1 - \min_{i \in N}\{x_i(0)\}\]
+	then $\Gm_1$ and $\Gm_2$ are equivalent.
 \end{theorem}
@@
 	For $t \ne 0$, assume for simplicity that all $t_i \ne t_j$ for all $i, j \in N$.
-	Note that since we apply the same tolls $t$ to both game, the ordering they impose on the links is the same.
+	Note that since we apply the same tolls $t$ to both games, the ordering they impose on the links is also the same.
 	We denote as $i = i^{(1)} = i^{(2)}$ the common corresponding link $i$ between the two games.
@@
 	Assume that the theorem does not hold, i.e. $x^{(1)}(t) \ne x^{(2)}(t)$.
-	Then there exists some link $i \in N$ such that $x_i^{(1)}(t) > x_i^{(2)}(t)$, and therefore there exists a player $p$ who is on link $i$ in $\Gm_1$ but not in $\Gm_2$.
-	We can assume that for the link $j$ this player went to in $\Gm_2$ it holds $x_j^{(1)}(t) \le x_j^{(2)}(t)$; if not, then select $j$ and start the same reasoning from the beginning.
-
-	If we consider now the split between $i$ and $j$, player $p$ exist in the lower split for one game and on the upper one for the other, let w.l.o.g. those game be $\Gm_1$ and $\Gm_2$ respectively.
+	Then there exists some link $i \in N$ such that $x_i^{(1)}(t) > x_i^{(2)}(t) > 0$, meaning that there exists a player $p$ who is on link $i$ in $\Gm_1$ but not in $\Gm_2$.
+	Let $j$ be that link.
+	If $x_j^{(1)}(t) > x_j^{(2)}(t)$ then select $j$ and start the same reasoning from the beginning, until eventually we arrive to $i, j$ such that $x_j^{(1)}(t) \le x_j^{(2)}(t)$.
+
+	If we consider now the split between $i$ and $j$ and since the toll ordering on links is the same between the two games, player $p$ exists in the lower split for one game and on the upper one for the other, let w.l.o.g.
+those games be $\Gm_1$ and $\Gm_2$ respectively.
 	So if we take $\Gm_1$ where $p$ in the lower split, then it holds that $p$ is not in $x_n^{(1)}$, since the link with the highest toll is always the upper split with regard to all others.
@@
 	With the above we get
-	\[x_i^{(1)}(t) > x_i^{(2)}(t) \Rightarrow x_i^{(1)}(t) + \alpha^{(1)}(p)t_i > x_i^{(2)}(t) + \alpha^{(2)}(p)t_i \Rightarrow c_i^{p, (1)}(t) > c_i^{p, (2)}(t)\]
+	\[x_i^{(1)}(t) > x_i^{(2)}(t) \Rightarrow x_i^{(1)}(t) + \alpha^{(1)}(p)t_i > x_i^{(2)}(t) + \alpha^{(2)}(p)t_i \Rightarrow c_i^{(1)}(p) > c_i^{(2)}(p)\]
 	and respectively
-	\[x_j^{(1)}(t) \le x_j^{(2)}(t) \Rightarrow x_j^{(1)}(t) + \alpha^{(1)}(p)t_j \le x_j^{(2)}(t) + \alpha^{(2)}(p)t_j \Rightarrow c_j^{p, (1)}(t) \le c_j^{p, (2)}(t)\]
-	The above inequations mean that, between $\Gm_1$ and $\Gm_2$, for player $p$, the cost of link $i$ decreased while the cost of link $j$ didn't, concluding that $p$ cannot be on link $i$ in $\Gm_1$ but then change to link $j$ in $\Gm_2$, which is a contradiction.
+	\[x_j^{(1)}(t) \le x_j^{(2)}(t) \Rightarrow x_j^{(1)}(t) + \alpha^{(1)}(p)t_j \le x_j^{(2)}(t) + \alpha^{(2)}(p)t_j \Rightarrow c_j^{(1)}(p) \le c_j^{(2)}(p)\]
+	The above inequalities mean that, between $\Gm_1$ and $\Gm_2$ for player $p$, the cost of link $i$ decreased while the cost of link $j$ didn't, concluding that $p$ cannot be on link $i$ in $\Gm_1$ but then change to link $j$ in $\Gm_2$, which is a contradiction.
 
@@
 
-We can see how this theorem applies to Example \ref{example:simple_alpha}, where since $x(0) = (2/3, 1/3)$ then $\max\{x_1(0), x_2(0)\} = 2/3$.
-Then even if we used a distribution function such as
+We can see how this theorem applies to Example \ref{example:simple_alpha}, where $\max\{x_1(0), x_2(0)\} = \max\{2/3, 1/3\} = 2/3$.
+Theorem \ref{theorem:alpha_upper_irrelevant} states that even if we used a distribution function such as
 \[
@@
 
-It will become more apparent later when calculating best responses as even in the pricing games those higher values will never be used.
+This irrelevancy will become more apparent later when calculating best responses, as even in the pricing games those higher values are never used.
 We finish this section with a lemma about the behaviour of $\as$ when many players have money sensitivity close to 0.
-Note that it doesn't suffice to assume $\alpha(0) = 0$ as the behavior of a single player has no effect on the game, so we additionally assume that $0$ is an accumulation point in $\alpha$.
+Note that since the behavior of a single player has no effect on the game, it doesn't suffice to assume $\alpha(0) = 0$ just for player $0$, so in order to capture the notion of having many players with $\alpha$ values close to $0$ we additionally assume that $0$ is an accumulation point in $\alpha$.
 \begin{lemma}
 	Let $(N, \ell, \alpha)$ a heterogeneous parallel game with distribution function $\alpha$ such that $\alpha(0) = 0$ and $0$ is an accumulation point.
-	If for any $i \in N$ it holds that $x_i(0) > 0$, then $x_i(t) > 0, \forall t \in \R_+^N$
+	Then $x_1(t) > 0, \forall t \in \R_+^N$
 \end{lemma}
@@
 	By the definition of an accumulation point, we get for $0$ in $\alpha$ that $\forall \delta > 0 \; \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
-	Therefore $\forall t \in \R_+^N$ if $\delta = \min_{j \in N \setminus \{i\}}\as^{(i, j)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(i, j)}(t)$ for all $j \in N \setminus \{i\}$, which means that the lower latency link will always have flow some $\epsilon > 0$, and therefore $x_i(t) > 0$.
-\end{proof}
-Intuitively, the property describes the fact that having almost no toll fear makes a player not motivated to leave the edge, which in turn makes the network having little control over those players using toll regulations.
+	Therefore $\forall t \in \R_+^N$ if $\delta = \min_{j \in N \setminus \{i\}}\as^{(i, j)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(i, j)}(t)$ for all $j \in N \setminus \{i\}$, which means that the lower-latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t) > 0$.
+\end{proof}
+The main interest in the above lemma is the fact that it affects the lowest-latency, and therefore highest-toll, link, meaning that regardless of how high the highest toll is, some players will always remain in that link.
+Intuitively, it describes the fact that having almost no toll fear makes a player not motivated to leave the link, which in turn means having little control over those players using toll regulations.
 
@@
 \begin{proof}
-	All players $p$ with $\alpha(p) = 0$ will completely neglect the toll values and play the congestion game only considering the flow latencies, thus always selecting the fastest edge, regardless of the toll prices.
+	All players $p$ with $\alpha(p) = 0$ will completely neglect the toll values and play the congestion game only considering the flow latencies, thus always selecting the fastest link, regardless of the toll prices.
 
@@
 	Obviously $\alpha(p) = 0 \; \forall p < x_i^\prime$.
-	Then we can see that for all $t_i > t_{-i}$ where edge $i$ has the lower latency edge, all those players will be on that edge and will remain so regardless of how high is the value of $t_i$.
+	Then we can see that for all $t_i > t_{-i}$ where link $i$ has the lower latency link, all those players will be on that link and will remain so regardless of how high is the value of $t_i$.
 	For the respective profit that means $\Pi_i(t_i, t_{-i}) \ge x_i t_i \; \forall t_i > t_{-i}$.
@@
 	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^2 \cup \{0\}$, where $x^{(1)}(t), x^{(2)}(t)$ the respective Nash Equilibrium for $t$ for $\Gm_1, \Gm_2$.
-	Begin by noticing that while $\Gm_1$ is heterogeneous, all its players have the same money sensitivity, and thus at an equilibrium they will all see the two edges as the same.
+	Begin by noticing that while $\Gm_1$ is heterogeneous, all its players have the same money sensitivity, and thus at an equilibrium they will all see the two links as the same.
 	Therefore for all $t \in \R_+ \cup \{0\}$, $x^{(1)}(t)$ is the unique solution of the equation
@@
 \end{proof}
-Intuitively, the above means that increasing the money sensitivity of the players in equivalent to analogously decreasing the traffic that flows create on all edges.
+Intuitively, the above means that increasing the money sensitivity of the players in equivalent to analogously decreasing the traffic that flows create on all links.
 Unfortunately this correspondence  disappears for non-fixed distribution functions, since, as we saw in Chapter 2, we loose the $1-1$ relation between the latency functions and the distribution function due to heterogeneity.
@@
 		\end{flalign*}
-		with the last equation being the one for edge equality in $\Gm_1$ with a unique solution at $x^{(1)}(t)$, leading us to $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)$
+		with the last equation being the one for link equality in $\Gm_1$ with a unique solution at $x^{(1)}(t)$, leading us to $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)$
 		\item From $(i)$ and the definition of $\Pi_i$ we get
@@
 
-What we need to examine  next is how those two games react differently for an edge $i$ given a fixed $t_{-i}$.
+What we need to examine  next is how those two games react differently for an link $i$ given a fixed $t_{-i}$.
 For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference.
@@
 \begin{proof}
-	From definition, $\as^{(1)}(t)$ is the value for which any player that has such $\alpha^{(1)}$ value will view the two edge costs as equal.
-	Then, since the latency functions are the same between $\Gm_1, \Gm_2$, we get $x^{(1)}(t) = x^{(2)}(t)$, and since all players have money sensitivity $\as^{(1)}(t)$, they will all view the two edges equally with no one wishing to change.
+	From definition, $\as^{(1)}(t)$ is the value for which any player that has such $\alpha^{(1)}$ value will view the two link costs as equal.
+	Then, since the latency functions are the same between $\Gm_1, \Gm_2$, we get $x^{(1)}(t) = x^{(2)}(t)$, and since all players have money sensitivity $\as^{(1)}(t)$, they will all view the two links equally with no one wishing to change.
 	We conclude that $x^{(1)}(t)$ is a Nash equilibrium for $t$ in $\Gm_2$ as well.
@@
 
-When it comes to maximising profit for the pricing games, those values included in all $\Pi_{i, k}$ are all we need, because if $\as(t)$ takes any other in-between value, then we are on an instance where no player views the two edge costs as equal, with players viewing a purely smaller cost in either edge.
+When it comes to maximising profit for the pricing games, those values included in all $\Pi_{i, k}$ are all we need, because if $\as(t)$ takes any other in-between value, then we are on an instance where no player views the two link costs as equal, with players viewing a purely smaller cost in either link.
 For the link operators, this means there at least one who can increase their toll and still keep the flow the same, achieving pure profit.
-This can also happen in edge cases of $\as(t) = \alpha_k$, so we move our full description of this behavior in the following lemma.
+This can also happen in link cases of $\as(t) = \alpha_k$, so we move our full description of this behavior in the following lemma.
 
@@
 	First, notice that from \ref{lemma:split_basic} and \ref{theorem:alpha_upper_irrelevant} we get $\alpha_1 \le \as(t) \le \alpha_k$ for all $t$, and therefore $\as$ is always in-between some $\alpha_k, \alpha_{k+1}$.
-	Even if $\as(t) \ \alpha_k$ for some $k$, belonging in the closed border of $T_{-\alpha}$, it will be either the lowest or highest toll difference possible, ensuring there is always an edge where no players are viewing the two edges equally.
-
-	Let $i$ be that edge which we also assume is the lower split of the flow equilibrium, i.e. $t_i^\prime > t_{-i}^\prime$, and let $k \in [m - 1]$ such that $\alpha_k < \as(t^\prime) < \alpha_{k+1}$.
+	Even if $\as(t) \ \alpha_k$ for some $k$, belonging in the closed border of $T_{-\alpha}$, it will be either the lowest or highest toll difference possible, ensuring there is always a link where no players are viewing the two links equally.
+
+	Let $i$ be that link which we also assume is the lower split of the flow equilibrium, i.e. $t_i^\prime > t_{-i}^\prime$, and let $k \in [m - 1]$ such that $\alpha_k < \as(t^\prime) < \alpha_{k+1}$.
 	Then link operator $i$ can increase their toll to a $t_i^{\prime\prime} > t_i^\prime$, thus decreasing the value of $\as$, up to the point where $\alpha(t^{\prime\prime}, t_{-i}^\prime) = \alpha_k$.
-	Players in link $i$ will now view their edge as of either lower or equal cost value as the other, while the players in the other link will view theirs as of purely lower cost, making none wishing to change.
+	Players in link $i$ will now view their link as of either lower or equal cost value as the other, while the players in the other link will view theirs as of purely lower cost, making none wishing to change.
 	We therefore get that $x_i(t_i^{\prime\prime}, t_i^\prime) = x_i(t^\prime)$ making in turn $\Pi_i(t_i^{\prime\prime}, t_i^\prime) > \Pi_i(t^\prime)$ and finally $B_i(t_{-i}^\prime) \ne t_i$.
@@
 Some of the properties naturally extend but for others more care is required.
-Special notice and expansion is certainly necessary for the split function, as it is only defined for two edges.
-On a first thought, it seems trivial to also order the edges on an equilibrium by latency and then define the split function on each consecutive pair, therefore also having an ordered set of split function values.
+Special notice and expansion is certainly necessary for the split function, as it is only defined for two links.
+On a first thought, it seems trivial to also order the links on an equilibrium by latency and then define the split function on each consecutive pair, therefore also having an ordered set of split function values.
 Still, more investigation is needed to uncover the relation between those values, and its consequences to the flow's or the pricing game's behaviours.
@@
 We will calculate $B_i(t_{-i})$ by calculating $x_i(t)$ and then finding $\argmax \Pi_i(t)$.
-Note that since we always have $x_1(t), x_2(t) > 0$ we don't need to take cases where the flow is on one edge.
+Note that since we always have $x_1(t), x_2(t) > 0$ we don't need to take cases where the flow is on one link.
 For tolls $t = (t_1, t_2)$ and respective optimal flow $x = (x_1(t), x_2(t))$ we take the following cases.
@@
 
-\paragraph{The bad behaviors} are obviously having divergent or undefined best response functions, which we claim occur only when we allow $0$ to be an accumulation point in $\alpha$, since this allows players with arbitrarily low money-sensitivity to always stay on the expensive edge.
+\paragraph{The bad behaviors} are obviously having divergent or undefined best response functions, which we claim occur only when we allow $0$ to be an accumulation point in $\alpha$, since this allows players with arbitrarily low money-sensitivity to always stay on the expensive link.
 Assume that in Example $\ref{example:ap_p}$ we use $\alpha(p) = p + 1$ as a distribution function.
@@
 First we calculate the edge cases [TODO: add relevant section in preliminaries].
-If all flow is in edge $1$ then $t_2 - t_1 = \alpha(0) l_1(1) = 1$, while if all flow is in edge $2$ then $t_1 - t_2 = \alpha(0) l_2(1) = 2$ therefore
+If all flow is in link $1$ then $t_2 - t_1 = \alpha(0) l_1(1) = 1$, while if all flow is in link $2$ then $t_1 - t_2 = \alpha(0) l_2(1) = 2$ therefore
 \[t_2 - t_1 \le 1 \qquad t_1 - t_2 \le 2\]

### 2024-12-27 thesis/article.tex
Thesis: Generalises propositions to n links and final fixes in first part of Chapter 4

@@
 Finally for affine latencies we can calculate $x(t)$ by following the same reasoning as \cite[Prop $3.1$]{Harks_2019}.
-For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^N$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
+For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^{|N|}$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
 Since $x(t)$ is an equilibrium for $t$ then for all $i \in N(t)$ we get $\ell_i(x_i) + t_i = K$ for some common effective cost $K$.
@@
 
-This property shows us that for a given $t \in \R_+^N$, if we order the links according to decreasing toll values, then the same link order will have latencies ordered in increasing values (and vice-versa).
+This property shows us that for a given $t \in \R_+^{|N|}$, if we order the links according to decreasing toll values, then the same link order will have latencies ordered in increasing values (and vice-versa).
 It is then easy to show that the players using each such link are also ordered with regard to their $\alpha$ values in increasing order.
@@
 	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
-	For tolls $t \in \R_+^N$ consider the links in decreasing toll ordering.
+	For tolls $t \in \R_+^{|N|}$ consider the links in decreasing toll ordering.
 	It holds that $x_n(t) \ge x_n(0)$.
@@
 	Consider $t^\prime = t - t_n$.
-	From assumption we have $t_n = \min_{i \in N} t_i$, which makes $t^\prime \in \R_+^N$ with $t_n^\prime = 0$.
+	From assumption we have $t_n = \min_{i \in N} t_i$, which makes $t^\prime \in \R_+^{|N|}$ with $t_n^\prime = 0$.
 	Since the flow equilibrium $x(t)$ is dependent only on the toll differences, we get $x(t) = x(t^\prime)$.
@@
 Finally we need to discuss about toll differences again.
-While the definition for $t \in \R_+^N$ allows any arbitrary value, the meaningful ones actually reside in a more limited space.
+While the definition for $t \in \R_+^{|N|}$ allows any arbitrary value, the meaningful ones actually reside in a more limited space.
 Assume for example that a toll $t$ is such that $x_i(t) = 1$ for some link $i \in N$ with $t_i > 0$ and $x_j(t) = 0$ for all other links $j \ne i$.
@@
 	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
-	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
+	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^{|N|}|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
 	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
@@
 	We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
-	More formally, we define a set function $A_i: \R_+^N \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
+	More formally, we define a set function $A_i: \R_+^{|N|} \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
 	\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
@@
 \]
-We will not utilise this definition as is in this work as it gets more complex for games with $n$ links, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll differences do in $\R^{N - 1}$.
+We will not utilise this definition as is in this work as it gets more complex for games with $n$ links, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll differences do in $\R^{|N| - 1}$.
 
@@
 	Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games with the same number of links $n = |N|$  and latency functions $\ell$.
-	For $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t \in \R_+^N$ in $\Gm_1, \Gm_2$ respectively, denote as $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the equal flow on paths between $\Gm_1$ and $\Gm_2$ for $t = 0$.
+	For $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t \in \R_+^{|N|}$ in $\Gm_1, \Gm_2$ respectively, denote as $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the equal flow on paths between $\Gm_1$ and $\Gm_2$ for $t = 0$.
 	If the distribution functions $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that
@@
 \begin{proof}
-	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \forall t \in \R_+^N$.
+	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \forall t \in \R_+^{|N|}$.
 	It's already stated that the equality holds for $t = 0$.
@@
 	Let $(N, \ell, \alpha)$ a heterogeneous parallel game with distribution function $\alpha$ such that $\alpha(0) = 0$ and $0$ is an accumulation point.
-	Then $x_1(t) > 0, \forall t \in \R_+^N$
+	Then $x_1(t) > 0, \forall t \in \R_+^{|N|}$
 \end{lemma}
@@
 	By the definition of an accumulation point, we get for $0$ in $\alpha$ that $\forall \delta > 0 \; \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
-	Therefore $\forall t \in \R_+^N$ if $\delta = \min_{j \in N \setminus \{i\}}\as^{(i, j)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(i, j)}(t)$ for all $j \in N \setminus \{i\}$, which means that the lower-latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t) > 0$.
+	Therefore $\forall t \in \R_+^{|N|}$ if $\delta = \min_{j \in N \setminus \{i\}}\as^{(i, j)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(i, j)}(t)$ for all $j \in N \setminus \{i\}$, which means that the lower-latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t) > 0$.
 \end{proof}
@@
 
-In this section we introduce the pricing game to our model and examine how different distribution functions $\alpha$ can affect the profit maximisation game between the toll owners, specifically when $\alpha$ is fixed, step or continuous.
+In this section we introduce the pricing competition game to our model and examine how different distribution functions $\alpha$ can affect the profit maximisation game between the toll owners, specifically when $\alpha$ is fixed or step.
 We begin, though, with some necessary restrictions.
@@
 Even Cole et al. \cite{10.1145/780542.780618} assume $\alpha(p) > 0$ when $p > 0$ for their model to support optimal tolls.
-In fact, this restriction proves necessary for our pricing game as well, since its absence allows distribution functions with arbitrarily small flow all at $0$, which in turn, as we'll see in the following Lemma, breaks the pricing game, too.
+In fact, this restriction proves necessary for our pricing game as well, since its absence allows distribution functions with arbitrarily small flow all at $0$, which in turn, as we'll see in the following Lemma, break the pricing game, too.
 
@@
 	\label{lemma:a_0_0}
-	Let $([2], \ell, \alpha)$ a pricing game for which it holds that $\exists \epsilon > 0: \alpha(p) = 0 \; \forall p < \epsilon$.
-	Then the best response functions $B_i(t_{-i})$ are unbounded.
+	Let $(N, \ell, \alpha)$ a heterogeneous pricing game for which it holds that $\exists \epsilon > 0: \alpha(p) = 0 \; \forall p < \epsilon$.
+	Let $i \in N$ be a link for which $\ell_i(0) = \min_{j \in N} \ell_i(0)$.
+	Then $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{|N| - 1}$.
 \end{lemma}
@@
 \begin{proof}
-	All players $p$ with $\alpha(p) = 0$ will completely neglect the toll values and play the congestion game only considering the flow latencies, thus always selecting the fastest link, regardless of the toll prices.
-
-	We have from assumption that $x_i(0) > 0$.
-	Consider $x_i^\prime = \min\{x_i(0), \epsilon\} > 0$.
-	Obviously $\alpha(p) = 0 \; \forall p < x_i^\prime$.
-	Then we can see that for all $t_i > t_{-i}$ where link $i$ has the lower latency link, all those players will be on that link and will remain so regardless of how high is the value of $t_i$.
-	For the respective profit that means $\Pi_i(t_i, t_{-i}) \ge x_i t_i \; \forall t_i > t_{-i}$.
-	Consequently, as $t_i \rightarrow +\infty$ then so does $x_i t_i$ and $\Pi_i(t_i, t_{-i})$, making in turn $B_i(t_{-i}) \rightarrow +\infty$.
+	All players $p$ with $\alpha(p) = 0$ will completely neglect the toll values and play the congestion game only considering the link latencies, thus always selecting the fastest link regardless of the toll prices.
+	The condition of $\ell_i(0) = \min_{j \in N} \ell_i(0)$, then, ensures that link $i$ will always have flow, i.e.
+$x_i(t) > 0, \forall t \in \R_+^{|N|}$, since if $x_i(t) = 0$ for some set of tolls $t$, then $i$ becomes a lowest-latency link meaning that at least some of the players with $\alpha(p) = 0$ view this as the lowest cost, a contradiction.
+
+	Link operator $i$ can therefore select a $t_i > \max t_{-i}$ which will make link $i$ the lowest-latency link and be populated exclusively by players with $\alpha(p) = 0$.
+	Indeed, consider $x_i^\prime(t) = \min\{x_i(t), \epsilon\} > 0$; obviously $\alpha(p) = 0 \; \forall p < x_i^\prime(t)$.
+	Consequently, $t_i$ can be increased arbitrarily with no link user ever leaving the link, resulting to a fixed flow and pure profit for link operator $i$.
+	More formally, for any $t_i^\prime > \max t_{-i}$ and any $t_i > t_i^\prime$ we have $x_i^\prime(t_i, t_{-i}) = x_i^\prime(t_i^\prime, t_{-i})$ and therefore $\Pi_i(t_i, t_{-i}) = x_i(t_i, t_{-i}) t_i \ge x_i^\prime(t_i, t_{-i}) t_i = x_i^\prime(t_i^\prime, t_{-i})t_i$.
+	We fix $t_i^\prime$ and we see that
+	\[
+		\lim_{t_i \rightarrow +\infty} \Pi_i(t_i, t_{-i}) \ge \lim_{t_i \rightarrow +\infty} x_i^\prime(t_i^\prime, t_{-i})t_i = +\infty
+	\]
+	%Consequently, as $t_i \rightarrow +\infty$ then so does $x_i t_i$ and $\Pi_i(t_i, t_{-i})$,
+	making in turn $B_i(t_{-i}) = +\infty$.
 \end{proof}
@@
 	\label{lemma:a_fixed_homogeneous}
-	Let $\Gm_1 = ([2], \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = ([2], \frac{\ell^{(1)}}{c}, 1)$ a homogeneous pricing game with latencies $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
+	Let $\Gm_1 = (N, \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = (N, \frac{\ell^{(1)}}{c}, 1)$ a homogeneous pricing game with latencies $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
 	Then the two games are equivalent.
@@
 \begin{proof}
-	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^2 \cup \{0\}$, where $x^{(1)}(t), x^{(2)}(t)$ the respective Nash Equilibrium for $t$ for $\Gm_1, \Gm_2$.
-	Begin by noticing that while $\Gm_1$ is heterogeneous, all its players have the same money sensitivity, and thus at an equilibrium they will all see the two links as the same.
-	Therefore for all $t \in \R_+ \cup \{0\}$, $x^{(1)}(t)$ is the unique solution of the equation
-	\[
-		\ell_1^{(1)}(x_1^{(1)}(t)) + ct_1 = \ell_2^{(1)}(x_2^{(1)}(t)) + ct_2
-	\]
-	It is easy to check now that $x^{(2)}(t)$ is also a solution to the above equation, since in $\Gm_2$ it is the equivalent unique solution for
-	\[
-		\frac{\ell_1^{(1)}(x_1^{(2)}(t))}{c} + t_1 = \frac{\ell_2^{(1)}(x_2^{(2)}(t))}{c} + t_2 \Leftrightarrow \ell_1^{(2)}(x_1^{(2)}(t)) + t_1 = \ell_2^{(2)}(x_2^{(2)}(t)) + t_2
-	\]
-	Therefore $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^2 \cup \{0\}$, making $\Gm_1, \Gm_2$ equivalent.
-\end{proof}
-Intuitively, the above means that increasing the money sensitivity of the players in equivalent to analogously decreasing the traffic that flows create on all links.
-Unfortunately this correspondence  disappears for non-fixed distribution functions, since, as we saw in Chapter 2, we loose the $1-1$ relation between the latency functions and the distribution function due to heterogeneity.
-
-Still, looking now at the relation between fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} gives us the following corollary.
+	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^{|N|}$, where $x^{(1)}(t), x^{(2)}(t)$ the respective Nash Equilibrium for $t$ in $\Gm_1, \Gm_2$.
+	Since $\Gm_2$ is homogeneous, we can use Lemma \ref{lemma:wardrop_equilibrium} to get that for any other flow $x^{(2)}$ it holds that
+	\[
+		\sum_{i \in N} \left(\tfrac1c \cdot \ell_i^{(1)}(x_i^{(2)}(t)) + t_i\right) \cdot \left(x_i^{(2)}(t) - x_i^{(2)}\right) \leq 0
+	\]
+	which is equivalent to
+	\[
+		\sum_{i \in N} \left(\ell_i^{(1)}(x_i^{(2)}(t)) + c t_i\right) \cdot \left(x_i^{(2)}(t) - x_i^{(2)}\right) \leq 0
+	\]
+	Notice that $\ell_i^{(1)}(x_i) + c t_i$ is the link cost of link $i$ for players in $\Gm_1$, given flow $x_i$ and toll $t_i$.
+	Regardless of the heterogeneity of our users, since the above inequality holds, then for flow $x^{(2)}(t)$ in $\Gm_1$ it will also hold for any other flow $x_i^{(1)} = x^{(2)}$.
+	It follows that any flow movement from $x^{(2)}(t)$ will again put players in links with larger link costs, making $x^{(2)}(t)$ a Nash Equilibrium for $t$ in $\Gm_1$ as well.
+	Uniqueness of the equilibrium with regards to costs finally gives us $x^{(1)}(t) = x^{(2)}(t)$.
+	Since the above hold for all $t \in \R_+^{|N|}$, we conclude from Definition \ref{definition:game_equivalence} that $\Gm_1, \Gm_2$ are equivalent.
+\end{proof}
+Intuitively, the above means that increasing the money sensitivity of the players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
+Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money-sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
+We discuss more about the relation between time and money sensitivity in Chapter \ref{chapter:future_work}.
+
+Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} gives us the following corollary.
 \begin{corollary}
@@
 		%\item $x^{(1)}(0) = x^{(2)}(0)$
-		\item $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)$
-		\item $\frac{c_1}{c_2} \cdot \Pi_i^{(1)}(t_i, t_{-i}) = \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right)$
-		\item $\frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i}) = B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right)$
+		\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
+		\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
+		\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
 	\end{enumerate}
@@
 \begin{proof}
-	$ $
 	\begin{enumerate}[$(i)$]
 		%\item Obvious since for $t = 0$ the flow in both $\Gm_1, \Gm_2$ play a homogeneous game with common latencies $\ell$, which makes the two games identical and therefore $x^{(1)}(0) = x^{(2)}(0)$.
-		\item With the same rational as in Lemma \ref{lemma:a_fixed_homogeneous}, looking at the respective cost equalities for the two games we see that starting from $\Gm_2$ for tolls $(c_1 / c_2)t$ we get
-		\begin{flalign*}
-			\ell_1&\left(x_1^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)\right) + c_2 \cdot \left(\frac{c_1}{c_2} \cdot t_1\right) = \ell_2\left(x_2^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)\right) + c_2 \cdot \left(\frac{c_1}{c_2} \cdot t_2\right) & \\
-			&\Rightarrow \ell_1\left(x_1^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)\right) + c_1 t_1 = \ell_2\left(x_2^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)\right) + c_1 t_2 &
-		\end{flalign*}
-		with the last equation being the one for link equality in $\Gm_1$ with a unique solution at $x^{(1)}(t)$, leading us to $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} \cdot t\right)$
+		\item Consider the homogeneous games $\Gm_3 = (N, \frac{\ell}{c_1}, 1)$ and $\Gm_4 = (N, \frac{\ell}{c_2}, 1)$, for which it follows from Lemma \ref{lemma:a_fixed_homogeneous} that they are equivalent to $\Gm_1, \Gm_2$ respectively, meaning that for all $t \in \R_+^{|N|}$ we have $x^{(1)}(t) = x^{(3)}(t)$ and $x^{(2)}(t) = x^{(4)}(t)$.
+		If we now assign tolls $c_2 t$ to $\Gm_3$, then from Lemma \ref{lemma:wardrop_equilibrium} we get that for any other flow $x^{(3)}$ it holds that
+		\[
+			\sum_{i \in N} \left(\tfrac{1}{c_1} \cdot \ell_i(x_i^{(3)}(c_2 t)) + c_2 t_i\right) \cdot \left(x_i^{(3)}(c_2 t) - x_i^{(3)}\right) \leq 0
+		\]
+		which is equivalent to
+		\[
+			\sum_{i \in N} \left(\tfrac{1}{c_2} \cdot \ell_i(x_i^{(3)}(c_2 t)) + c_1 t_i\right) \cdot \left(x_i^{(3)}(c_2 t) - x_i^{(3)}\right) \leq 0
+		\]
+		which again, since $x^{(3)}$ is an arbitrary flow, from Lemma \ref{lemma:wardrop_equilibrium} it follows that $x^{(3)}(c_2 t)$ is a Nash Equilibrium for $c_1 t$ in $\Gm_4$, i.e.
+$x^{(3)}(c_2 t) = x^{(4)}(c_1 t)$.
+		Gathering all the above, we have
+		\[x^{(1)}(c_2 t) = x^{(3)}(c_2 t) = x^{(4)}(c_1 t) = x^{(2)}(c_1 t)\]
 		\item From $(i)$ and the definition of $\Pi_i$ we get
 		\begin{flalign*}
-			\frac{c_1}{c_2} \cdot \Pi_i^{(1)}(t_i, t_{-i}) &= \frac{c_1}{c_2} \cdot x_i^{(1)}(t) \cdot t_i \stackrel{(i)}{=} x_i^{(2)}\left(\frac{c_1}{c_2} \cdot t\right) \cdot \left(\frac{c_1}{c_2} \cdot t_i\right) & \\
-			&= \Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) &
+			c_1 \cdot \Pi_i^{(1)}(c_2 t_i, c_2 t_{-i}) &= c_1 \cdot x_i^{(1)}(c_2 t) \cdot c_2 t_i & \\
+			&\stackrel{(i)}{=} c_1 \cdot x_i^{(2)}(c_1 t) \cdot c_2 t_i & \\
+			&= c_2 \cdot x_i^{(2)}(c_1 t) \cdot c_1 t_i & \\
+			&= c_2 \cdot \Pi_i^{(2)}(c_1 t_i, c_1 t_{-i}) &
 		\end{flalign*}
@@
 		\begin{flalign*}
-			\frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i}) &= \frac{c_1}{c_2} \cdot \argmax_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) \stackrel{(ii)}{=} \argmax_{t_i > 0}\Pi_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_i, \frac{c_1}{c_2} \cdot t_{-i}\right) & \\
-			&= B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right) &
+			c_1 \cdot B_i^{(1)}(c_2 t_{-i}) &= c_1 \cdot \argmax_{t_i > 0}\Pi_i^{(1)}(c_2 t_i, c_2 t_{-i}) & \\
+			&\stackrel{(ii)}{=} c_2 \cdot \argmax_{t_i > 0}\Pi_i^{(2)}(c_1 t_i, c_1 t_{-i}) & \\
+			&= c_2 \cdot B_i^{(2)}(c_1 t_{-i}) &
 		\end{flalign*}
@@
 \chapter{Future work}
+\label{chapter:future_work}
 
@@
 Putting the pricing games aside, it would also be interesting to expand the split function for series-parallel graphs.
+
+\section*{Time-money sensitivity relation}
+
+The standard technique to capture heterogeneity in the users of a network has been to apply a weight $\alpha$ to the toll cost viewed be each user, making their total cost $\ell(x) + \alpha t$.
+This approach is equivalent to applying the inverse weight to the latency, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
+Though less intuitive we already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed} where we showed that a fixed distribution function is equivalent to restricting the latency functions inversely proportionally, however the idea could potentially be extended outside of fixed values.
+This would of course does not guarantee that the latency functions will remain affine, or even polynomial.
+One could attempt and investigate distribution functions that are inverse polynomials, making the respective latencies remain polynomial.
+In any case we believe that a future work on the relation of the time-sensitivity with money-sensitivity approaches, could uncover further insights in the behavior of heterogeneity.
 

### 2024-12-28 thesis/article.tex
Thesis: Major fixes in step dist function in Chapter 4
Fixes figure labels

@@
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\N}{\mathbb{N}}
 \newcommand{\Gm}{\mathcal{G}}
@@
 			% Nodes
-			\node[circle, draw, fill=blue!20, minimum size=1cm] (s) at (0,0) {$s$};
-			\node[circle, draw, fill=blue!20, minimum size=1cm] (t) at (4,0) {$t$};
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
 
@@
 	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
+	In the case of $N = [2]$ where there exists only one link pair, we will simply write $\as(t)$.
 \end{definition}
@@
 
-		Let $(t_{i_m})_{m \in \mathbb{N}}$ a decreasing sequence of tolls in link $i$, such that $t_{i_m} \rightarrow t_i$.
-		We know that as a toll decreases, the link can only gain flow, which in turn makes $(x_i(t_{i_m}, t_{-i}))_{m \in \mathbb{N}}$ non-decreasing with $x_i(t_{i_m}, t_{-i}) \rightarrow x_i(t)$.
-		Therefore we can define from each $t_{i_m}$ an edge player $(p_m)_{m \in \mathbb{N}}$ such that $p_m = \sup P_i(t_{i_m}, t_{-i})$, thus making the non-decreasing sequence $(p_m)_{m \in \mathbb{N}}$ with $p_m \rightarrow \sup P_i(t)$.
-
-		Corollary \ref{corollary:split_to_alpha} gives us $\alpha(p_m) \le \as^{(i, j)}(t_{i_m}, t_{-i})$ for all $m \in \mathbb{N}$.
+		Let $(t_{i_m})_{m \in \N}$ a decreasing sequence of tolls in link $i$, such that $t_{i_m} \rightarrow t_i$.
+		We know that as a toll decreases, the link can only gain flow, which in turn makes $(x_i(t_{i_m}, t_{-i}))_{m \in \N}$ non-decreasing with $x_i(t_{i_m}, t_{-i}) \rightarrow x_i(t)$.
+		Therefore we can define from each $t_{i_m}$ an edge player $(p_m)_{m \in \N}$ such that $p_m = \sup P_i(t_{i_m}, t_{-i})$, thus making the non-decreasing sequence $(p_m)_{m \in \N}$ with $p_m \rightarrow \sup P_i(t)$.
+
+		Corollary \ref{corollary:split_to_alpha} gives us $\alpha(p_m) \le \as^{(i, j)}(t_{i_m}, t_{-i})$ for all $m \in \N$.
 		If the inequality holds as equality (in which case $c_i(p_m) = c_j(p_m)$), we take $t_{i_m}^\prime = t_{i_m}$.
@@
 		That increase doesn't break the monotonicity of the sequence, since the increase will happen at most until the value of the previous sequence element is reached, for which we've already checked that the inequality from Corollary \ref{corollary:split_to_alpha} is tight.
-		Therefore, the updated toll sequence $(t_{i_m}^\prime)_{m \in \mathbb{N}}$ becomes non-decreasing with $t_{i_m}^\prime \rightarrow t_i^\prime$ and it holds for all elements that
+		Therefore, the updated toll sequence $(t_{i_m}^\prime)_{m \in \N}$ becomes non-decreasing with $t_{i_m}^\prime \rightarrow t_i^\prime$ and it holds for all elements that
 		\[\alpha(p_m) = \as^{(i, j)}(t_{i_m}^\prime, t_{-i})\]
@@
 Though it seems that also holds for heterogeneous users, since we don't need the latter property and proving it seems tricky, we omit it from this study.}
-		%Let $(p_n)_{n \in \mathbb{N}}$ be an increasing sequence of players from $P_i(t)$, which , such that $p_n \rightarrow \sup P_i(t)$.
-		%Therefore we can find a decreasing sequence of $(t_{i_n})_{i_n \in \mathbb{N}}$ with $t_{i_n} \rightarrow t_i$, such that $\max P_i(t_{i_n}, t_{-i}) = p_n$.
+		%Let $(p_n)_{n \in \N}$ be an increasing sequence of players from $P_i(t)$, which , such that $p_n \rightarrow \sup P_i(t)$.
+		%Therefore we can find a decreasing sequence of $(t_{i_n})_{i_n \in \N}$ with $t_{i_n} \rightarrow t_i$, such that $\max P_i(t_{i_n}, t_{-i}) = p_n$.
 		%Such a $t_n$ might not be unique, though since $t_n > t_i > t_j$, link $i$ always remains the lower split.
@@
 
-All the above give us the graph for $\as$ in Figure \ref{figure:apha_simple:split_example}.
-\begin{center}
+All the above give us the graph for $\as$ in Figure \ref{figure:alpha_simple:split_example}.
+\begin{figure}
+	\centering
 	\begin{tikzpicture}[x=5cm, y=2cm, every node/.style={font=\small}]
-	\label{figure:apha_simple:split_example}
-
 		% Axes
@@
 		% Dots
-	\fill[white] (0.5,4/3) ellipse (0.02 and 0.04);
-	\draw[black] (0.5,4/3) ellipse (0.02 and 0.04);
-	\fill[white] (0.5,5/3) ellipse (0.02 and 0.04);
-	\draw[black] (0.5,5/3) ellipse (0.02 and 0.04);
-
-	% Description
-	\node[align=center] at (0.7, -0.7) {\textbf{Figure \ref*{figure:apha_simple:split_example}:} Split function of Example \ref{example:simple_alpha}};
+		\fill[white] (0.5,4/3) ellipse (0.02 and 0.05);
+		\draw[black] (0.5,4/3) ellipse (0.02 and 0.05);
+		\fill[white] (0.5,5/3) ellipse (0.02 and 0.05);
+		\draw[black] (0.5,5/3) ellipse (0.02 and 0.05);
 	\end{tikzpicture}
-\end{center}
+	\caption{Split function of Example \ref{example:simple_alpha}}
+	\label{figure:alpha_simple:split_example}
+\end{figure}
 
@@
 \end{proof}
-Intuitively, the above means that increasing the money sensitivity of the players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
+Since a heterogeneous game with a fixed distribution function is, in practice, homogeneous with regard to the flow behaviour, we will also use, when relevant, the term \textit{pseudo-heterogeneous game} to describe such flows more easily.
+
+Intuitively, the above means that increasing the money sensitivity of all players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
 Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money-sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
@@
 
-Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} gives us the following corollary.
-\begin{corollary}
-	\label{corollary:a_fixed_c_relation}
+Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} leads us to the following one.
+\begin{lemma}
+	\label{lemma:a_fixed_c_relation}
 	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
@@
 	\end{enumerate}
-\end{corollary}
+\end{lemma}
 
@@
 
-\section{Step distribution function}
-
-Moving now to actual heterogeneous games, we will examine how the pricing game behaves when the distribution function is a step function, i.e. it takes finitely many values.
-There will be a strong connection with the fixed distribution function games we studied earlier, and that connection extends beyond the step function, which is why we will prove it here for any distribution function.
+\section{Step distribution function for $2$-link networks}
+
+Moving now to other (actual) heterogeneous games, we will once again restrict our model to networks with $2$ links in order to simplify our analysis.
+Even with this restriction, however, we will still uncover some vulnerabilities in reaching a Nash Equilibrium in the pricing competition game between the link operators.
+
+If the flow's distribution function is a step function, i.e. it takes finitely many values, then the flow sensitivity is fixed in finite intervals.
+This creates a strong connection with the pseudo-homogeneous games we studied earlier, and that connection is the main focus of this section.
+The following lemma holds for any distribution function, so we prove them as such, and by discussing afterwards their implications for step functions we'll move to our main result.
 
@@
 	Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls and $x^{(1)}(t)$ the Nash equilibrium for $t$.
-	Now let $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
-	Then $x^{(1)}(t) = x^{(2)}(t)$.
+	Now let $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a pseudo-heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
+	Then the following hold
+	\begin{enumerate}[$(i)$]
+		\item $x^{(1)}(t) = x^{(2)}(t)$
+		\item $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$ for each respective link operator $i$
+	\end{enumerate}
 \end{lemma}
@@
 \begin{proof}
-	From definition, $\as^{(1)}(t)$ is the value for which any player that has such $\alpha^{(1)}$ value will view the two link costs as equal.
-	Then, since the latency functions are the same between $\Gm_1, \Gm_2$, we get $x^{(1)}(t) = x^{(2)}(t)$, and since all players have money sensitivity $\as^{(1)}(t)$, they will all view the two links equally with no one wishing to change.
-	We conclude that $x^{(1)}(t)$ is a Nash equilibrium for $t$ in $\Gm_2$ as well.
+	\begin{enumerate}[$(i)$]
+		\item From Definition \ref{definition:split_function} we have that $\as^{(1)}(t)$ is the value for which any player that has such $\alpha^{(1)}$ value will view the two link costs equally.
+		So if we assume flow $x^{(1)}(t)$ in $\Gm_2$, where all players have money-sensitivity $\as^{(1)}(t)$, then all players will view the two link costs equally (latency functions and tolls are the same), which in turn means that everyone is happy with their choice.
+		We conclude that $x^{(1)}(t)$ is a Nash Equilibrium for $t$ in $\Gm_2$ as well, and from the uniqueness of the equilibrium with regard to costs, we finally get $x^{(1)}(t) = x^{(2)}(t)$.
+		\item Natural conclusion from $(i)$ and the definition of $\Pi_i$.
+	\end{enumerate}
 \end{proof}
 
-\begin{corollary}
-	\label{corollary:heterogenous_profit_equiv_fixed}
-	Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls, $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
-	Then for each link operator $i$ it holds that $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$.
-\end{corollary}
-
-\begin{proof}
-	Natural conclusion from Lemma \ref{lemma:heterogenous_flow_equiv_fixed} and the definition of $\Pi_i$.
-\end{proof}
-
-For a game with step distribution function in particular, the above mean that we can "slice" its flow and respective profit depending on the money sensitivity of each flow section, and apply the properties we investigated earlier on fixed distribution function games.
-Combining it with the discussion around the values of $\as$ for different tolls, especially Theorem \ref{theorem:alpha_upper_irrelevant}, we can see that the game is played among a subset of $\alpha$ values, mirrored around the lower and upper splits.
-We visualise this idea in the following example.
+We return our focus to step distribution functions, which we define as a function $\alpha$ which takes on a finite number of values $\alpha_1 < \alpha_2 < \dots < \alpha_m, \; m \in \N$.
+From Lemma \ref{lemma:split_basic}$(ii)$ we have $\as \in [\alpha_1, \alpha_m]$ and from the overall analysis of $\as$ in Chapter \ref{chapter:split} we get that $\as$ will move continuously among a subset of $(\alpha_k)_{k \in [m]}$, mirrored around the lower splits on each link.
+Lemma \ref{lemma:heterogenous_flow_equiv_fixed} shows us that in each case the game is corresponding to a pseudo-heterogeneous one with $\alpha(p) = \as(t)$, marking a clear connection with those games where $\alpha(p) \in (\alpha_k)_{k \in [m]}$.
+Intuitively, it seems to make sense to "slice" the flow into intervals in which we have equivalency with one of those games.
+We visualise this intuition in the following example.
 
@@
 	\label{example:a_step_simple}
-	Let $([2], \ell, \alpha)$ be a heterogeneous pricing game where
+	Let $([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
 	\begin{align*}
-		\begin{aligned}
-			\ell_1 &= x + 1 \\
-			\ell_2 &= 2x
-		\end{aligned}
-		\qquad
 		\alpha(p) =
 		\begin{cases}
-			1 & p \le 1 / 5 \\
-			3 & p > 0
+			1 & p \le \tfrac15 \\
+			3 & p \in \left(\tfrac15, \tfrac12\right) \\
+			4 & p \ge \tfrac12
 		\end{cases}&
 	\end{align*}
-	TODO: Add flow and profit plots for a fixed $t_{-i}$.
-	In each case include all flow/profit for the game with $\alpha(p) = 1, 3$ and make bold the sub-intervals that are relevant.
 \end{example}
 
-In order to be able to describe the different profits on the different intervals of the step function, we introduce a definition of profit for a link operator within a flow section.
+\begin{center}
+	\begin{multicols}{2}
+		% Left Column: Network Graph
+		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
+			% Nodes
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
+
+			% Links
+			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+			\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
+
+			% Description
+			\node[align=center] at (2, -2) {Network of Example \ref{example:a_step_simple}};
+		\end{tikzpicture}
+
+		% Right Column: Distribution function Graph
+		\begin{tikzpicture}[x=3cm, y=0.7cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
+			\draw[->] (0,0) -- (0,4.2) node[above] {$\as(p)$};
+
+			% Tick marks
+			\draw (0,0) -- (0,-0.05) node[below] {$0$};
+			\draw (0.2,0) -- (0.2,-0.05) node[below] {$\frac15$};
+			\draw (0.5,0) -- (0.5,-0.05) node[below] {$\frac12$};
+			\draw (1,0) -- (1,-0.05) node[below] {$1$};
+			\draw (0,1) -- (-0.05,1) node[left] {$1$};
+			\draw (0,3) -- (-0.05,3) node[left] {$3$};
+			\draw (0,4) -- (-0.05,4) node[left] {$4$};
+
+			% Function graph
+			\draw[thick] (0,1) -- (0.2,1);
+			\draw[thick] (0.2,3) -- (0.5,3);
+			\draw[thick] (0.5,4) -- (1,4);
+
+			% Closed / Open dots
+			\fill[white] (0.2,1) ellipse (0.014 and 0.06);
+			\draw[black] (0.2,1) ellipse (0.014 and 0.06);
+			\fill[black] (0.2,3) ellipse (0.014 and 0.06);
+			\draw[black] (0.2,3) ellipse (0.014 and 0.06);
+			\fill[black] (0.5,3) ellipse (0.014 and 0.06);
+			\draw[black] (0.5,3) ellipse (0.014 and 0.06);
+			\fill[white] (0.5,4) ellipse (0.014 and 0.06);
+			\draw[black] (0.5,4) ellipse (0.014 and 0.06);
+
+			% Description
+			\node[align=center] at (0.7, -1.7) {Distribution function of\\Example \ref{example:a_step_simple}};
+		\end{tikzpicture}
+	\end{multicols}
+\end{center}
+We can easily find that $x(0) = (2/3, 1/3)$, so from Corollary \ref{corollary:split_asymptotic_continuous} we get that the edge values of $\as$ are $\alpha(x_1(0)) = \alpha(2/3) = 4$ and $\alpha(x_2(0)) = \alpha(1/3) = 3$.
+Focusing on link $1$, we fix an arbitrarily large $t_2$ and examine $t_1 - t_2$ for different values of $t_1$.
+With a reasoning similar to that of Example \ref{example:simple_alpha} (since again $\alpha(0) = 1$) we get that the toll difference bounds are $t_1 - t_2 \le 2$ and $t_2 - t_1 \le 1$, which means that we can restrict our focus to $t_1 - t_2 \in [-1, 2]$.
+We also know at which flows the behaviour of the network will change, which are exactly the flows where each all player of each sensitivity type are using a single link, i.e.
+the flows $(4/5, 1/5), (1/2, 1/2), (1/5, 4/5)$, e.g.
+flow $(4/5, 1/5)$ has all players with $\alpha(p) = 1$ in link $2$ and all $\alpha(p) = 3, 4$ players in link $1$, which in turn means that such a flow can only have $\as$ value between $1$ and $3$.
+
+We focus on the edge cases.
+For each flow and each relevant $\alpha$ value we can calculate the toll difference that will cause it, e.g.
+if we want to find the toll difference for which we get flow $x(t) = (4/5, 1/5)$ with $\as(t) = 3$, then we solve $\ell_1(4/5) + 3t_1 = \ell_2(1/5) + 3t_2 \Rightarrow t_2 - t_1 = 2/15$.
+After calculating all cases we arrive at Figures \ref{figure:alpha_step:split} and \ref{figure:alpha_step:flow} which visualise respectively $\as(t)$ and $x_1(t)$ for all possible values of $t_1$.
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[x=3.4cm, y=1cm, every node/.style={font=\small}]
+		% Axes
+		\draw[->] (0,0) -- (-1.1,0);
+		\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+		\draw[->] (0,0) -- (0,4.4) node[above] {$\as(t)$};
+
+		% Tick marks
+		\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+		\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
+		\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
+		\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+		\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
+		\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
+		\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
+		\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
+		\draw (2,0) -- (2,-0.05) node[below] {$2$};
+		\draw (0,1) -- (-0.05,1) node[left] {$1$};
+		\draw (0,3) -- (0.05,3) node[right] {$3$};
+		\draw (0,4) -- (-0.05,4) node[left] {$4$};
+
+		% Function graph
+		% Left side
+		\draw[thick] (-1,1) -- (-2/5,1);
+		\draw[thick] (-2/5,1) -- (-2/15,3);
+		\draw[thick] (-2/15,3) -- (0,3);
+		% Right side
+		\draw[thick] (0,4) -- (1/8,4);
+		\draw[thick] (1/8,4) -- (1/6,3);
+		\draw[thick] (1/6,3) -- (7/15,3);
+		\draw[thick] (7/15,3) -- (7/5,1);
+		\draw[thick] (7/5,1) -- (2,1);
+
+		% Dots
+		\fill[white] (0,3) ellipse (0.02 and 0.066);
+		\draw[black] (0,3) ellipse (0.02 and 0.066);
+		\fill[white] (0,4) ellipse (0.02 and 0.066);
+		\draw[black] (0,4) ellipse (0.02 and 0.066);
+	\end{tikzpicture}
+	\caption{Split function of Example \ref{example:a_step_simple}}
+	\label{figure:alpha_step:split}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
+		% Axes
+		\draw[->] (0,0) -- (-1.1,0);
+		\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+		\draw[->] (0,0) -- (0,1.1) node[above] {$x_1(t)$};
+
+		% Tick marks
+		\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+		\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
+		\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
+		\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+		\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
+		\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
+		\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
+		\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
+		\draw (2,0) -- (2,-0.05) node[below] {$2$};
+		\draw (0,1) -- (-0.05,1) node[left] {$1$};
+		\draw (0,4/5) -- (0.05,4/5) node[right] {$\frac45$};
+		\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
+		\draw (0,1/2) -- (-0.05,1/2) node[left] {$\frac12$};
+		\draw (0,1/5) -- (-0.05,1/5) node[left] {$\frac15$};
+
+		% Function graph
+		% Left side
+		\draw[thick] (-1,1) -- (-2/5,4/5);
+		\draw[thick] (-2/5,4/5) -- (-2/15,4/5);
+		\draw[thick] (-2/15,4/5) -- (0,2/3);
+		% Right side
+		\draw[thick] (0,2/3) -- (1/8,1/2);
+		\draw[thick] (1/8,1/2) -- (1/6,1/2);
+		\draw[thick] (1/6,1/2) -- (7/15,1/5);
+		\draw[thick] (7/15,1/5) -- (7/5,1/5);
+		\draw[thick] (7/5,1/5) -- (2,0);
+	\end{tikzpicture}
+	\caption{Flow function for link $1$ of Example \ref{example:a_step_simple}}
+	\label{figure:alpha_step:flow}
+\end{figure}
+
+What one may first notice from those figures, is that when $x_1$ is fixed then $\as$ isn't and vice-versa.
+This happens due to the fact that we have a step distribution function, therefore if the flow is moving, then it does so among players with the same sensitivity type, which is one of the finitely many values $\alpha$ can take.
+Inversely, if all players of each sensitivity type are using a single link, then $\as$ can take any value between the lowest and highest $\alpha$ value in the upper and lower split respectively.
+
+Considering now the pricing competition game and looking at the profit function $\Pi_1(t)$, we can already notice from Figure \ref{figure:alpha_step:flow} that in the toll difference intervals where the flow remains the same, $\Pi_1(t)$ will be strictly increasing as $t_1$ also does.
+In extension, in terms of profit maximisation, it follows that max profit will never be within those intervals.
+We capture this idea in the following lemma.
+
+\begin{lemma}
+	\label{lemma:alpha_step_gaps}
+	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}, \; m \in N$.
+	Also let $t \ne 0$ a set of tolls for which it holds for all $k \in [m]$ that all players $p$ with $\alpha(p) = \alpha_k$ are using the same link.
+	Then $t$ is not a Nash equilibrium for the pricing game.
+\end{lemma}
+
+\begin{proof}
+	It suffices to show that there exists a link operator $i$ for which it holds that $B_i(t_{-i}) \ne t_i$.
+	From the condition about $t$ we get that there exists some $\alpha_k, \alpha_{k + 1}, \; k \in [m - 1]$ where $\alpha_k$ is the highest $\alpha$ value in the lower split and $\alpha_{k + 1}$ the lowest $\alpha$ value in the upper split.
+	It obviously follows that $\alpha_k \le \as(t) \le \alpha_{k + 1}$, but since also $\alpha_k \ne \alpha_{k + 1}$, we see that the inequalities cannot hold with equality both at the same time.
+
+	If $\as(t) > \alpha_k$, then let $i$ be the link operator of the link with the higher toll, i.e. the link with the lower split.
+	From Lemma \ref{lemma:split_asymptotic} we see that for any $t_i^\prime > t_i$, which increases the toll difference $t_i - t_{-i}$, may decrease $\as(t)$.
+	Still, if link operator $i$ increases their toll $t_i^\prime > t_i$ by an arbitrarily small amount, they can ensure that $\as(t) \ge \as(t_i^\prime, t_{-i}) > \alpha_k$ and not break the property of $\alpha_k < \as(t_i^\prime, t_{-i}) \le \alpha_{k + 1}$, thus achieving no flow movement between $t_i$ and $t_i^\prime$.
+	This gives us $x(t) = x(t_i^\prime, t_{-i})$, from which it is easy to show that $\Pi_i(t) < \Pi_i(t_i^\prime, t_{-i})$ and in turn $B_i(t_{-i}) \ne t_i$.
+
+	If $\as(t) < \alpha_{k + 1}$, then a symmetrical argument can be made by selecting as $i$ the link operator of the link with the higher toll.
+	Note that an increase in $t_i$ now causes the toll difference $t_{-i} - t_i$ to decrease which may increase $\as(t)$, so we again need to consider that the $t_i^\prime$ increase is arbitrarily small to ensure $\as(t_i^\prime, t_{-i}) < \alpha_{k + 1}$.
+	The rest of the argument continues as before.
+\end{proof}
+
+The above lemma shows us that the Nash Equilibrium for the pricing game (if existent at all) does not reside in tolls for which $\as$ is in-between the values of $\alpha$.
+We complement this idea with the following Theorem, one of the main results of this chapter, where we will show that if that Nash Equilibrium exists, then it has to happen for some specific flow.
+
+\begin{theorem}
+	\label{theorem:a_step_ne_equiv_fixed}
+	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
+	If $\Gm_1$ has a Nash equilibrium for the pricing game at toll $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ a pseudo-heterogeneous game with latency functions the same as the ones in $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as(t^*)$.
+	Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
+\end{theorem}
+
+\begin{proof}
+	First observe that from Lemma \ref{lemma:alpha_step_gaps} we get that $t^*$ cannot have all players of each sensitivity type using a single link, otherwise it wouldn't be a Nash equilibrium for the pricing game.
+	Therefore $\as(t^*) = \alpha_k$ for some $k \in [m]$ and there exists a non-zero flow of players with money-sensitivity $\alpha_k$ in both links.
+	That means that we can find arbitrarily small toll variations which will move some, but not all, of those players, thus keeping $\as$ at $\alpha_k$.
+	In other words, for an arbitrary link $i$, $\exists \epsilon > 0$ such that if $|t_i - t_i^*| < \epsilon$ then $\as(t_i, t_{-i}^*) = \alpha_k$.
+	Let $T_\epsilon$ denote the set of those $t_i$.
+
+	Notice that $\Gm_2$, from the way we defined it, has $\alpha^{(2)}(p) = \alpha_k$.
+	We can therefore apply Lemma \ref{lemma:heterogenous_flow_equiv_fixed}$(ii)$ on the elements of $T_\epsilon$ and get $\Pi_i^{(1)}(t_i, t_{-i}^*) = \Pi_i^{(2)}(t_i, t_{-i}^*)$ for all $t_i \in T_\epsilon$.
+	Since $t^*$ is a Nash equilibrium for the pricing game in $\Gm_1$, it holds that $\Pi_i^{(1)}(t^*) \ge \Pi_i^{(1)}(t_i, t_{-i}^*)$ for all $t_i > 0$, so if we restrict our domain to $T_\epsilon$ we get $\Pi_i^{(2)}(t^*) \ge \Pi_i^{(2)}(t_i, t_{-i}^*)$ for all $t_i \in T_\epsilon$.
+	That makes $\Pi_i^{(2)}(t^*)$ a local maximum in $\Gm_2$.
+	From the analysis in Harks et al. \cite{Harks_2019} we know that for homogeneous games the profit functions $\Pi_i$ are concave, making their values take a unique global maximum.
+	It follows that $\Pi_i^{(2)}(t^*)$ is the global maximum profit against $t_{-i}^*$ in $\Gm_2$, thus arriving at $B_i^{(2)}(t_{-i}^*) = t_i^*$.
+
+	The link selection was arbitrary, making $B_i^{(2)}(t_{-i}^*) = t_i^*$ hold for all links $i \in [2]$, finally concluding that $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
+\end{proof}
+
+It therefore seems to make sense to discuss profit only within those intervals where the flow changes, or equivalently view profit with regard to flow intervals, since we ignore instances where the flow remains the same and thus there exists a $1-1$ relation between profit and flow.
+We now introduce the notion of profit within a flow interval.
 
@@
 This can also happen in link cases of $\as(t) = \alpha_k$, so we move our full description of this behavior in the following lemma.
-
-\begin{lemma}
-	\label{lemma:a_step_gaps}
-	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
-	If $t^\prime$ a set of tolls in the closure of $T_{-\alpha} = \{t | \as(t) \ne \alpha_k \; \forall k \in [m]\}$, then $t^\prime$ is not a Nash equilibrium for the pricing game.
-\end{lemma}
-
-\begin{proof}
-	It suffices to show that there exists link operator $i$ such that $B_i(t_{-i}^\prime) \ne t_i$.
-	First, notice that from \ref{lemma:split_basic} and \ref{theorem:alpha_upper_irrelevant} we get $\alpha_1 \le \as(t) \le \alpha_k$ for all $t$, and therefore $\as$ is always in-between some $\alpha_k, \alpha_{k+1}$.
-	Even if $\as(t) \ \alpha_k$ for some $k$, belonging in the closed border of $T_{-\alpha}$, it will be either the lowest or highest toll difference possible, ensuring there is always a link where no players are viewing the two links equally.
-
-	Let $i$ be that link which we also assume is the lower split of the flow equilibrium, i.e. $t_i^\prime > t_{-i}^\prime$, and let $k \in [m - 1]$ such that $\alpha_k < \as(t^\prime) < \alpha_{k+1}$.
-	Then link operator $i$ can increase their toll to a $t_i^{\prime\prime} > t_i^\prime$, thus decreasing the value of $\as$, up to the point where $\alpha(t^{\prime\prime}, t_{-i}^\prime) = \alpha_k$.
-	Players in link $i$ will now view their link as of either lower or equal cost value as the other, while the players in the other link will view theirs as of purely lower cost, making none wishing to change.
-	We therefore get that $x_i(t_i^{\prime\prime}, t_i^\prime) = x_i(t^\prime)$ making in turn $\Pi_i(t_i^{\prime\prime}, t_i^\prime) > \Pi_i(t^\prime)$ and finally $B_i(t_{-i}^\prime) \ne t_i$.
-
-	Similarly we can show that $B_{-i}(t_i^\prime) \ne t_{-i}$ if $i$ is the upper split of the flow equilibrium, decisively making $t^\prime$ a set of tolls where there never is a Nash equilibrium for the pricing game.
-\end{proof}
-
-We complete the picture now with correlation result for the Nash equilibrium of the pricing game.
-
-\begin{theorem}
-	\label{theorem:a_step_ne_equiv_fixed}
-	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
-	If $\Gm_1$ has a Nash equilibrium for the pricing game at toll $t^*$, then the game $\Gm_2 = ([2], \ell, \as(t^*))$, with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha(p) = \as(t^*)$, also has its unique Nash equilibrium for the pricing game at $t^*$.
-\end{theorem}
-
-\begin{proof}
-	First observe that from Lemma \ref{lemma:a_step_gaps} we get $t^*$ is not in the closure of $T_{-\alpha}$, otherwise it couldn't be a Nash equilibrium, therefore $\as(t^*) = \alpha_k$ for some $k \in [m]$.
-	Then, again due to $t^*$ being a Nash equilibrium, it holds that $\Pi_i(t^*) \ge \Pi_i(t_i, t_{-i}^*)$ for all $t_i > 0$.
-
-	Now it is important to note that from the analysis in Harks et al. \cite{Harks_2019} we know that for homogeneous games the profit functions $\Pi_i$ are concave, making them have unique maximum.
-	Therefore when restricting the domain to an interval, either that same maximum is within that interval or a lower maximum of the interval is achieved at its corners.
-	The restriction of $t^*$ not belonging in the closure of $T_{-\alpha}$ also forbids the latter case, making $\Pi_i(t^*)$ also the global maximum for $\Gm_2$.
-	That condition holds for all link operators $i \in [2]$, therefore $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
-\end{proof}
 
@@
 In any case we believe that a future work on the relation of the time-sensitivity with money-sensitivity approaches, could uncover further insights in the behavior of heterogeneity.
+
+\section*{Pseudo-heterogeneous games}
+
+In Chapter \ref{chapter:pricing_equilibria} we investigated the class of heterogeneous games with a fixed distribution function, which maintains its homogeneous behaviour and presents interesting properties when comparing different fixed sensitivities.
+Since these games have a clear connection to heterogeneous games with step functions, it shows special interest to study the relation of flow and profit with regard to the same $t$, as this approach can then lead to a characterisation of those in step functions.
+
+\subsection*{Profit maximisation}
+
+During the investigation of this study, there has been some minor results in the relation of flow and profit between two similar pseudo-heterogeneous games.
+We present a list of conjectures that we believe are true.
 

### 2024-12-30 thesis/article.tex
Thesis: Related Work, Chapter 3 and Examples fixes after meeting with Th. Liannea

@@
 This will also serve as a bridge to Chapter \ref{chapter:preliminaries} were we will set our basis for the rest of the study.
-This includes formal definitions of the models and properties we introduced from previous work, as well as some additional -but still basic- properties of the models, with heavy focus on the user's time-money trade-off, captured by a money-sensitivity distribution function $\alpha$.
-
-Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money-sensitivity split}, which captures the notion of a (potentially non-existent) player whose money-sensitivity makes them view the two links as equal.
+This includes formal definitions of the models and properties we introduced from previous work, as well as some additional -but still basic- properties of the models, with heavy focus on the user's time-money trade-off, captured by a money sensitivity distribution function $\alpha$.
+
+Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money sensitivity split}, which captures the notion of a (potentially non-existent) player whose money sensitivity makes them view the two links as equal.
 We will then analyse that notion and provide properties and bounds for its values.
@@
 
-Selfish routing has a vast history of literature as it's been proven useful in solving a variety of real-world problems in economics \cite{pigou1920economics}, transportation \cite{beckmann1956studies} and more (see \cite{roughgarden2002sr} and \cite{roughgarden2005slpoa} for more references).
+Selfish routing is the study of trafficked networks where selfish users seek to optimise their own traffic cost.
+The main interest is on instances where all users are content with the traffic they experience and no one wishes to change their strategy, a notion known as a Nash Equilibrium, or equivalently from the work of Wardrop \cite{wardrop_theoretical_1952}, a Wardrop Equilibrium.
+Models from this field have been proven extremely useful in solving a variety of real-world problems in economics \cite{pigou1920economics}, transportation \cite{beckmann1956studies}, \cite{wardrop_theoretical_1952} and more, resulting in a vast history in the literature (see \cite{roughgarden2002sr} and \cite{roughgarden2005slpoa} for more references).
 It has been well-established, at least as early as 1920 from the work of Pigou \cite{pigou1920economics}, that selfish behavior in congested networks can create (arbitrary) inefficiencies with regard to the total latency experienced by all users.
@@
 Later, Monterer-Shapely \cite{MONDERER1996124} defined the class of potential games (games where the incentive for all players to change their strategy can be expressed with a global function) and proved that congestion games are equivalent to exact potential games (potential games where a change in strategy from any player alter the potential function the exact way it alters the player's cost).
-One of the major contributions in this field has been the introduction of the Wardrop equilibrium \cite{wardrop_theoretical_1952}, a notion of Nash equilibrium for potential games, where the Wardrop principles provide a framework to describe and analyse those equilibria.
+%One of the major contributions in this field has been the introduction of the Wardrop equilibrium \cite{wardrop_theoretical_1952}, a notion of Nash equilibrium for potential games, where the Wardrop principles provide a framework to describe and analyse those equilibria.
 Milchtaich \cite{MILCHTAICH1996111} then investigated different pay-off functions for congestion games, where he showed that even though some best-reply strategies may end up in a cyclic path, there is always a path that leads to Nash equilibrium with pure strategies.
@@
 In the heterogeneous case, each player $p$ reacts differently to tolls, presumably due to different time-money trade-off values.
-We describe this by adding a money-sensitivity weight $\alpha(p)$ on the toll costs experienced by a player, making them see the cost of a link with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
+We describe this by adding a money sensitivity weight $\alpha(p)$ on the toll costs experienced by a player, making them see the cost of a link with flow $x_i$ and toll $t_i$ as $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
 For a flow $x$ and tolls $t$, each player considers their costs experienced across all links and then selects to use the one (or one of potentially many) with the lowest cost. 
-By also assuming that the players are sorted by money-sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, +\infty]$.
+By also assuming that the players are sorted by money sensitivity, we can describe their heterogeneity by defining a non-decreasing function $\alpha: [0, 1] \rightarrow [0, +\infty]$.
 We call $\alpha$ a \textit{distribution function}.
@@
 
+\section*{Summary}
+
+In this chapter we will formalise and investigate the behaviour of the way a heterogeneous flow splits among the network links.
+In order to tackle the variance in money sensitivity among the flow users, we will focus on two (arbitrary) links and seek a money sensitivity value for which, for a given set of tolls, the two link costs are equal.
+After some discussion around the intuition of this idea, we will formally define a \textit{money sensitivity split} function (\ref{definition:split_function}) to capture this notion, as well as describe its essential idea of splitting the sensitivity values of the link's users to lower and higher values (Corollary \ref{corollary:split_to_alpha}).
+A discussion will then be necessary about the set of sensitivity values in the flow users of a link which will lead us to defining them in \ref{definition:alpha_flow_sets}.
+We then proceed with Lemmas to describe the split function's bounds (\ref{lemma:split_basic}), monotonicity (\ref{lemma:split_monotonicity}) and asymptotic behavior (\ref{lemma:split_asymptotic}), with which we'll arrive at the function's characterisation, cementing it visually for Example \ref{example:simple_alpha} in Figure \ref{figure:alpha_simple:split_example}.
+Finally, some observations about the split function's global upper bounds (Lemma \ref{lemma:split_upper_bound}) will have as logical consequence this chapter's main result, Theorem \ref{theorem:alpha_upper_irrelevant}, which states that there may exist a portion of players whose sensitivity value can be arbitrarily high without affecting the network game.
+
 \section{Introduction}
 
-One of the main difficulties with heterogeneity is that, for a given set of tolls, flow users with different money-sensitivity values, view toll values also differently, and therefore, in practice, play different games.
+One of the main difficulties with heterogeneity is that, for a given set of tolls, flow users with different money sensitivity values, view toll values also differently, and therefore, in practice, play different games.
 In the analysis of Example \ref{example:simple_alpha} we can find a first glimpse on how to tackle this issue, as we can see that the flow users on each link are organised around the player that views the two link costs as equal.
@@
 Without loss of generality we assume $t_1 > t_2$ which from Lemma \ref{lemma:latencies_tolls} leads to $\ell_1(x_1(t)) < \ell_2(x_2(t))$.
-For the $2$ links of the game we introduce the term money sensitivity split $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player views the $2$ links' total costs as equal.
+For the $2$ links of the game we introduce the term \textit{money sensitivity split} $\as(t)$ as the value of $\alpha$ for which if any player $p$ has $\alpha(p)=\as(t)$ then that player views the $2$ links' total costs as equal.
 More specifically, $\as(t)$ is the value of the distribution function $\alpha$ for which it holds
@@
 \begin{itemize}
-	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 < \ell_2(x_2(t)) + \alpha(p \cdot) t_2$, thus $p$ is on link $1$
-	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 > \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is on link $2$
-	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) \cdot t_1 = \ell_2(x_2(t)) + \alpha(p) \cdot t_2$, thus $p$ is either on link $1$ or $2$
+	\item if $\alpha(p) < \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) t_1 < \ell_2(x_2(t)) + \alpha(p) t_2$, so $p$ is on link $1$
+	\item if $\alpha(p) > \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) t_1 > \ell_2(x_2(t)) + \alpha(p) t_2$, so $p$ is on link $2$
+	\item if $\alpha(p) = \as(t)$ then $\ell_1(x_1(t)) + \alpha(p) t_1 = \ell_2(x_2(t)) + \alpha(p) t_2$, so $p$ is either on link $1$ or $2$
 \end{itemize}
@@
 We can easily see that if any flow user $p$ has $\alpha(p) = \as^{(i, j)}(t)$ then $c_i(p) = c_j(p)$.
-The fact that the function is not well-defined for $t_i = t_j$ matches with the notion we're trying to capture, as in that case we get $c_i(p) = c_j(p)$ for all flow users of the network, regardless of their money-sensitivity value.
+The fact that the function is not well-defined for $t_i = t_j$ matches with the notion we're trying to capture, as in that case we get $c_i(p) = c_j(p)$ for all flow users of the network, regardless of their money sensitivity value.
 We will also give a more formal definition to the lower-upper split intuition we described above.
@@
 
-At this point we should notice that $\as$, similarly to $x$, depends only on the toll differences and on the toll ordering of the links.
-In order to emphasise on this, let's restrict ourselves to $2$ links and point out that we could alternatively have defined both $x$ and $\as$ as single variable functions with a domain of values $t_d = t_1 - t_2 \in \R$ and function values as such
-\[
-	x(t_d) =
-	\begin{cases*}
-		x(t_d, 0) & $t_d \ge 0$ \\
-		x(0, -t_d) & $t_d < 0$ \\
-	\end{cases*}
-\]
-We will not utilise this definition as is in this work as it gets more complex for games with $n$ links, however displaying it helps with the intuition that the flow, and consequently $\as$, actually changes as the toll differences do in $\R^{|N| - 1}$.
-
-With that in mind, we will investigate the monotonicity of $\as$ in relation to toll differences (and in extension to latency differences) and only when the ordering does not change.
-For this we will need to compare different tolls that create lower-upper splits in the same links, or in other words for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$ and vice-versa.
+At this point we should notice that $\as$, similarly to $x$, depends only on the toll differences and on the toll ordering on links.
+With that in mind, we will investigate the monotonicity of $\as$ in relation to those toll differences (and in extension to latency differences) and only when the link ordering does not change.
+For the latter condition to be true, we will need to compare different tolls that create lower-upper splits in the same links, or, in other words, for tolls $t, t^\prime$ to hold that if $t_i > t_j$ then also $t_i^\prime > t_j^\prime$.
 We will capture this with the following condition
@@
 The above show that $\as(t)$ is continuous for all $t \ne 0$, approaches $0$ at large toll differences and increases as that difference approaches $0$, thus making the side limits around $0$ have different values (apart from the very specific case where $x_1(0) = x_2(0)$).
+At this point we should also mention that at the toll difference bounds we discussed in Chapter \ref{chapter:preliminaries}, $\as$ takes the value of the least sensitive player, i.e. $\alpha(0)$.
+
 We apply this on Example \ref{example:simple_alpha} to solidify this.
@@
 \[\lim_{t_1 - t_2 \rightarrow 0^-} \as(t) = \alpha(x_2(0)) = 4/3, \lim_{t_1 - t_2 \rightarrow 0^+} \as(t) = \alpha(x_1(0)) = 5/3\]
-
-All the above give us the graph for $\as$ in Figure \ref{figure:alpha_simple:split_example}.
+Toll difference bounds are $t_1 - t_2 \le 2$ and $t_2 - t_1 \le 1$.
+The distribution function for this example is simple enough for us to also calculate a closed type for $\as(t)$ (included analytically in the \hyperref[chapter:appendix]{Appendix}), from which calculations we get
+\[
+	\as(t) =
+	\begin{cases}
+		\frac{1}{t_2 - t_1} & t_1 - t_2 \le -1 \\
+		\frac{4}{3 + (t_2 - t_1)} & t_1 - t_2 \in (-1, 0) \\
+		\frac{5}{3 + (t_1 - t_2)} & t_1 - t_2 \in (0, 2) \\
+		\frac{2}{t_2 - t_1} & t_1 - t_2 \ge 2
+	\end{cases}
+\]
+whose plot is in Figure \ref{figure:alpha_simple:split_example} and which confirms the analysis we did above.
+
 \begin{figure}
 	\centering
-	\begin{tikzpicture}[x=5cm, y=2cm, every node/.style={font=\small}]
+	\begin{tikzpicture}[x=2cm, y=2cm, every node/.style={font=\small}]
 		% Axes
-		\draw[->] (0,0) -- (1.2,0) node[right] {$t_1$};
+		\draw[->] (0,0) -- (-1.1,0);
+		\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
 		\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};
@@
 		% Tick marks
-		\draw (0,0) -- (0,-0.05) node[below] {$0$};
-		\draw (0.5,0) -- (0.5,-0.05) node[below] {$t_2$};
-		\draw (0,4/3) -- (-0.05,4/3) node[left] {$4/3$};
+		\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+		\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+		\draw (2,0) -- (2,-0.05) node[below] {$2$};
+		\draw (0,2) -- (-0.05, 2) node[left] {$2$};
+		\draw (0,4/3) -- (0.05,4/3) node[right] {$4/3$};
 		\draw (0,5/3) -- (-0.05,5/3) node[left] {$5/3$};
+		\draw (0,1) -- (-0.05,1) node[left] {$1$};
 
 		% Function graph
-		\draw[thick] (0,0.1) -- (0.5,4/3);
-		\draw[thick] (0.5,5/3) -- (1,0.1);
+		%\draw[thick] (-1,1) -- (0,4/3);
+		%\draw[thick] (0,5/3) -- (2,1);
+		\draw[thick,samples at={-1,0}] plot (\x,{4/(3 - \x)});
+		\draw[thick,samples at={0,2}] plot (\x,{5/(3 + \x)});
 
 		% Dots
-		\fill[white] (0.5,4/3) ellipse (0.02 and 0.05);
-		\draw[black] (0.5,4/3) ellipse (0.02 and 0.05);
-		\fill[white] (0.5,5/3) ellipse (0.02 and 0.05);
-		\draw[black] (0.5,5/3) ellipse (0.02 and 0.05);
+		\fill[white] (0,4/3) ellipse (0.03 and 0.03);
+		\draw[black] (0,4/3) ellipse (0.03 and 0.03);
+		\fill[white] (0,5/3) ellipse (0.03 and 0.03);
+		\draw[black] (0,5/3) ellipse (0.03 and 0.03);
 	\end{tikzpicture}
@@
 Having now a good overview of the overall values of $\as$, we notice that there exist values of $\alpha$ that will never be a value of $\as$.
-Do then those values actually affect our game in any way?
+Do those values actually affect our game in any way?
 We answer this in the theorem below, which is the main result of this chapter, preceded by a lemma to describe those missing values.
@@
 \begin{lemma}
-	\label{lemma:as_upper_bound}
+	\label{lemma:split_upper_bound}
 	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
@@
 		p + 1 & p \le 2/3 \\
-		p + 10 & p > 2/3
+		\mathrm{e}^p & p > 2/3
 	\end{cases}
@@
 This irrelevancy will become more apparent later when calculating best responses, as even in the pricing games those higher values are never used.
-We finish this section with a lemma about the behaviour of $\as$ when many players have money sensitivity close to 0.
+
+\cleardoublepage
+
+\chapter{Equilibria in Pricing Games}
+\label{chapter:pricing_equilibria}
+
+In this section we introduce the pricing competition game to our model and examine how different distribution functions $\alpha$ can affect the profit maximisation game between the toll owners, specifically when $\alpha$ is fixed or step.
+We begin, though, with some necessary restrictions.
+
+\section{Problems with $0$ money sensitivity}
+
+We start this section with a lemma about the behaviour of $\as$ when many players have money sensitivity close to 0.
 Note that since the behavior of a single player has no effect on the game, it doesn't suffice to assume $\alpha(0) = 0$ just for player $0$, so in order to capture the notion of having many players with $\alpha$ values close to $0$ we additionally assume that $0$ is an accumulation point in $\alpha$.
@@
 Intuitively, it describes the fact that having almost no toll fear makes a player not motivated to leave the link, which in turn means having little control over those players using toll regulations.
-
-\cleardoublepage
-
-\chapter{Equilibria in Pricing Games}
-\label{chapter:pricing_equilibria}
-
-In this section we introduce the pricing competition game to our model and examine how different distribution functions $\alpha$ can affect the profit maximisation game between the toll owners, specifically when $\alpha$ is fixed or step.
-We begin, though, with some necessary restrictions.
-
-\section{Problems with $0$ money sensitivity}
 
@@
 Intuitively, the above means that increasing the money sensitivity of all players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
-Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money-sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
+Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
 We discuss more about the relation between time and money sensitivity in Chapter \ref{chapter:future_work}.
 
-Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} leads us to the following one.
+Looking now at the relation between different fixed distribution functions, Lemma \ref{lemma:a_fixed_homogeneous} leads us to the following proposition.
 \begin{lemma}
@@
 \end{proof}
+
+%Intuitively, the
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
+		% Axes
+		\draw[->] (0,0) -- (-1.1,0);
+		\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+		\draw[->] (0,0) -- (0,1.1) node[above] {$x_1(t)$};
+
+		% Tick marks
+		\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+		\draw (-1/3,0) -- (-1/3,-0.05) node[below] {$-\frac13$};
+		\draw (-1/4,0) -- (-1/4,-0.05) node[below] {$-\frac14$};
+		\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+		\draw (2/4,0) -- (2/4,-0.05) node[below] {$\frac12$};
+		\draw (2/3,0) -- (2/3,-0.05) node[below] {$\frac23$};
+		\draw (2,0) -- (2,-0.05) node[below] {$2$};
+		\draw (0,1) -- (0.05,1) node[right] {$1$};
+		\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
+
+		% Flow function graphs
+		\draw[thick, blue!33] (-1,1) -- (2,0) node[above, black] {$\alpha = 1$};
+		\draw[thick, blue!66] (-1/3,1) -- (2/3,0) node[above right, black] {$\alpha = 3$};
+		\draw[thick, blue!100] (-1/4,1) -- (2/4,0) node[black] at (0.2,0.17) {$\alpha = 4$};
+	\end{tikzpicture}
+	\caption{Flow function for link $1$ of Example \ref{example:simple_alpha} for $\alpha(p) = 1, 3, 4$.}
+	\label{figure:alpha_fixed:flow}
+\end{figure}
 
@@
 		\item From Definition \ref{definition:split_function} we have that $\as^{(1)}(t)$ is the value for which any player that has such $\alpha^{(1)}$ value will view the two link costs equally.
-		So if we assume flow $x^{(1)}(t)$ in $\Gm_2$, where all players have money-sensitivity $\as^{(1)}(t)$, then all players will view the two link costs equally (latency functions and tolls are the same), which in turn means that everyone is happy with their choice.
+		So if we assume flow $x^{(1)}(t)$ in $\Gm_2$, where all players have money sensitivity $\as^{(1)}(t)$, then all players will view the two link costs equally (latency functions and tolls are the same), which in turn means that everyone is happy with their choice.
 		We conclude that $x^{(1)}(t)$ is a Nash Equilibrium for $t$ in $\Gm_2$ as well, and from the uniqueness of the equilibrium with regard to costs, we finally get $x^{(1)}(t) = x^{(2)}(t)$.
@@
 		% Function graph
+		% Base flow functions
+		\draw[gray,dashed, very thin] (-1,1) -- (2,0);
+		\draw[gray,dashed, very thin] (-1/3,1) -- (2/3,0);
+		\draw[gray,dashed, very thin] (-1/4,1) -- (2/4,0);
+
 		% Left side
@@
 	First observe that from Lemma \ref{lemma:alpha_step_gaps} we get that $t^*$ cannot have all players of each sensitivity type using a single link, otherwise it wouldn't be a Nash equilibrium for the pricing game.
-	Therefore $\as(t^*) = \alpha_k$ for some $k \in [m]$ and there exists a non-zero flow of players with money-sensitivity $\alpha_k$ in both links.
+	Therefore $\as(t^*) = \alpha_k$ for some $k \in [m]$ and there exists a non-zero flow of players with money sensitivity $\alpha_k$ in both links.
 	That means that we can find arbitrarily small toll variations which will move some, but not all, of those players, thus keeping $\as$ at $\alpha_k$.
@@
 One could attempt and investigate distribution functions that are inverse polynomials, making the respective latencies remain polynomial.
-In any case we believe that a future work on the relation of the time-sensitivity with money-sensitivity approaches, could uncover further insights in the behavior of heterogeneity.
+In any case we believe that a future work on the relation of the time-sensitivity with money sensitivity approaches, could uncover further insights in the behavior of heterogeneity.
 
@@
 \chapter*{Appendix}
+\label{chapter:appendix}
+
+\section*{Example calculations}
+
+\subsection*{Example \ref{example:simple_alpha}}
+
+We calculate the flow $x$ by focusing on $x_1$ and solving
+\[
+	\ell_1(x_1) + \alpha(p)t_1 = \ell_2(1 - x_1) + \alpha(p) t_2 \Rightarrow 3 x_1 - 2 = \alpha(p) (t_2 - t_1)
+\]
+
+\paragraph{If $t_1 > t_2$} then $p = x_1$ so $\alpha(p) = x_1 + 1$.
+We replace and calculate
+\[
+	3 x_1 - 2 = (x_1 + 1) (t_2 - t_1) \Rightarrow x_1 (3 - (t_2 - t_1)) = 2 + (t_2 - t_1) \Rightarrow x_1 = \frac{2 - (t_1 - t_2)}{3 + (t_1 - t_2)}
+\]
+Now for $\as(t)$ we focus again on $x_1$ and get
+\[
+	\as(t) = \frac{\ell_2(1 - x_1) - \ell_1(x_1)}{t_1 - t_2} = \frac{2 - 3 x_1}{t_1 - t_2}
+\]
+and by replacing $x_1$ with the type from before we get
+\[
+	\as(t) = \frac{1}{t_1 - t_2} \left[2 - 3 \cdot \frac{2 - (t_1 - t_2)}{3 + (t_1 - t_2)}\right] = \frac{1}{t_1 - t_2} \cdot \frac{5(t_1 - t_2)}{3 + (t_1 - t_2)} = \frac{5}{3 + (t_1 - t_2)}
+\]
+
+\paragraph{If $t_1 < t_2$} then $p = x_2 = 1 - x_1$ so $\alpha(p) = 2 - x_1$.
+Similarly as before we get
+\[
+	x_1 = \frac{2 + 2(t_2 - t_1)}{3 + (t_2 - t_1)} \qquad \as(t) = \frac{4}{3 + (t_2 - t_1)}
+\]
+Finally we check for the toll difference bounds.
+For $t_1 - t_2 \ge 2$, the latency difference is fixed at $\ell_2(1) - \ell_1(0) = 2$, while for $t_2 - t_1 \ge 1$ it's fixed at $\ell_1(1) - \ell_2(0) = 1$.
+So as $|t_1 - t_2| \rightarrow 0$ in each case $\as$ becomes respectively
+\[
+	\as(t) = \frac{2}{t_1 - t_2} \qquad \as(t) = \frac{1}{t_2 - t_1}
+\]
+
+\section*{Additional examples}
 
@@
 
-\paragraph{The bad behaviors} are obviously having divergent or undefined best response functions, which we claim occur only when we allow $0$ to be an accumulation point in $\alpha$, since this allows players with arbitrarily low money-sensitivity to always stay on the expensive link.
+\paragraph{The bad behaviors} are obviously having divergent or undefined best response functions, which we claim occur only when we allow $0$ to be an accumulation point in $\alpha$, since this allows players with arbitrarily low money sensitivity to always stay on the expensive link.
 Assume that in Example $\ref{example:ap_p}$ we use $\alpha(p) = p + 1$ as a distribution function.

### 2024-12-31 thesis/article.tex
Thesis: Chapter 4 improvements
Adds summary, fixes 0 sensitivity section, first draft of the final algorithm with calculations

@@
 \usepackage{natbib}
+\usepackage{algorithm}
+\usepackage{algpseudocode}
 
@@
 \begin{equation}
-	\label{eq:homogeneous_ne_br_i}
+	\label{eq:homogeneous_pricing_ne_i}
 	t_i^* = \left(a_i + \frac{1}{\sum_{j \ne i} \frac{1}{a_j}}\right) \cdot x_i(t^*)
@@
 
-In this section we introduce the pricing competition game to our model and examine how different distribution functions $\alpha$ can affect the profit maximisation game between the toll owners, specifically when $\alpha$ is fixed or step.
-We begin, though, with some necessary restrictions.
+\section*{Summary}
+
+In this chapter we will introduce the pricing competition game to our model and examine how different distribution functions can affect the profit maximisation game between the toll operators.
+We will begin by noticing that players with no toll fear, i.e. $\alpha(p)$ close to $0$, can be exploited by some link operators who then get unbounded profits (Lemma \ref{lemma:a_0_0}).
+This obviously breaks the pricing competition game and, in turn, leads us to include the restriction of $\alpha(p) > 0$ when $p > 0$.
+We will then proceed to analyse games with fixed distribution functions, where in Lemma \ref{lemma:a_fixed_homogeneous} we will show that such games are, as intuition suggests, equivalent to homogeneous games.
+Special interest will then be on comparing such games, specifically those with the same setup but different fixed $\alpha$ functions, as Lemma \ref{lemma:a_fixed_c_relation} will reveal that uniformly varying the player sensitivity maps the toll values around the same flow.
+The tools and notions built above will prove extremely useful when we next analyse games with step distribution functions, where we'll restrict our analysis to instances with $2$ links to simplify our work.
+For those we will show an equivalence with a homogeneous game for a given toll \ref{lemma:heterogenous_flow_equiv_fixed} and combining it with Lemma \ref{lemma:alpha_step_gaps} where we'll show that a Nash Equilibrium cannot exist with all players of each sensitivity type using a single link, we get this chapter's main result, Theorem \ref{theorem:a_step_ne_equiv_fixed}, which states that if a Nash Equilibrium exists in a heterogeneous game with a step distribution function, then the respective homogeneous also has an equilibrium for the same set of tolls.
+Using this notion, we will describe an algorithm (\ref{definition:algorithm:ne_pricing}) which can decide existence and return the Nash Equilibrium for the pricing competition game in a heterogeneous $2$-link network.
 
@@
 
-We start this section with a lemma about the behaviour of $\as$ when many players have money sensitivity close to 0.
-Note that since the behavior of a single player has no effect on the game, it doesn't suffice to assume $\alpha(0) = 0$ just for player $0$, so in order to capture the notion of having many players with $\alpha$ values close to $0$ we additionally assume that $0$ is an accumulation point in $\alpha$.
-\begin{lemma}
-	Let $(N, \ell, \alpha)$ a heterogeneous parallel game with distribution function $\alpha$ such that $\alpha(0) = 0$ and $0$ is an accumulation point.
-	Then $x_1(t) > 0, \forall t \in \R_+^{|N|}$
-\end{lemma}
-
-\begin{proof}
-	By the definition of an accumulation point, we get for $0$ in $\alpha$ that $\forall \delta > 0 \; \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
-	Therefore $\forall t \in \R_+^{|N|}$ if $\delta = \min_{j \in N \setminus \{i\}}\as^{(i, j)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(i, j)}(t)$ for all $j \in N \setminus \{i\}$, which means that the lower-latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t) > 0$.
-\end{proof}
-The main interest in the above lemma is the fact that it affects the lowest-latency, and therefore highest-toll, link, meaning that regardless of how high the highest toll is, some players will always remain in that link.
-Intuitively, it describes the fact that having almost no toll fear makes a player not motivated to leave the link, which in turn means having little control over those players using toll regulations.
-
-In general having players with $\alpha(p) = 0$, i.e. players completely indifferent to tolls, creates issues.
+It is well known in the literature that having players with $\alpha(p) = 0$, i.e. players completely indifferent to tolls, creates issues.
 Even Cole et al. \cite{10.1145/780542.780618} assume $\alpha(p) > 0$ when $p > 0$ for their model to support optimal tolls.
-In fact, this restriction proves necessary for our pricing game as well, since its absence allows distribution functions with arbitrarily small flow all at $0$, which in turn, as we'll see in the following Lemma, break the pricing game, too.
+In fact, this restriction proves necessary for our pricing game as well, since its absence allows distribution functions with arbitrarily small flow all at $0$, which, as we'll see in the following Lemma, breaks the pricing game.
 
@@
 
-	Link operator $i$ can therefore select a $t_i > \max t_{-i}$ which will make link $i$ the lowest-latency link and be populated exclusively by players with $\alpha(p) = 0$.
+	Link operator $i$ can therefore select a $t_i > \max t_{-i}$ which will make link $i$ the lowest-latency link, populated exclusively by players with $\alpha(p) = 0$.
 	Indeed, consider $x_i^\prime(t) = \min\{x_i(t), \epsilon\} > 0$; obviously $\alpha(p) = 0 \; \forall p < x_i^\prime(t)$.
@@
 	\]
-	%Consequently, as $t_i \rightarrow +\infty$ then so does $x_i t_i$ and $\Pi_i(t_i, t_{-i})$,
 	making in turn $B_i(t_{-i}) = +\infty$.
@@
 We therefore need the restriction of $\alpha(p) > 0$ when $p > 0$ in order for our pricing game to have an equilibrium.
+The main interest in the above lemma is the fact that it affects the lowest-latency, and therefore highest-toll, link, meaning that regardless of how high the highest toll is, some players will always remain in that link.
+Intuitively, it describes the fact that having no toll fear makes a player not motivated to leave the link, which in turn means having little control over those players using toll regulations.
+
+In our current study of fixed and step distribution functions, this restriction will suffice.
+In general, however, similar issues can also arise when many players have $\alpha(p)$ close to $0$ (almost no toll fear), something that our restriction allows.
+We include Lemma \ref{lemma:a_0_accumulation_point} and Example \ref{example:ap_p} in the Appendix to showcase some properties of a setup where $0$ is an accumulation point in $\alpha$, but without going into any further analysis.
 
@@
 
-%Intuitively, the
+We consider Example \ref{example:simple_alpha} with fixed distribution functions $\alpha(p) = 1, 3$ and $4$ and visualise the flow function of link $1$ for each of those cases in Figure \ref{figure:alpha_fixed:flow}.
+The graph confirms what Lemma \ref{lemma:a_fixed_c_relation}$(i)$ suggests, that varying the fixed value in the distribution function basically "maps" the toll differences to a compressed or expanded range, with the respective flow for those corresponding toll differences remaining the same.
 
@@
 It therefore seems to make sense to discuss profit only within those intervals where the flow changes, or equivalently view profit with regard to flow intervals, since we ignore instances where the flow remains the same and thus there exists a $1-1$ relation between profit and flow.
-We now introduce the notion of profit within a flow interval.
-
-\begin{definition}
-	\label{definition:profit_interval}
-	Let $([2], \ell, \alpha)$ be a heterogeneous pricing game.
-	For a flow interval $[a, b] \subset [0, 1]$ and a link operator $i$, we define the \textit{profit in $[a, b]$} $\Pi_{i, [a, b]}$ as the toll that maximises the link operator's profit against the opposing toll $t_{-i}$, with the flow $x_i(t)$ being within $[a, b]$.
-	More formally
-	\[
-		\Pi_{i, [a, b]}(t_{-i}) = \max_{\stackrel{t_i > 0}{x_i(t_i, t_{-i}) \in [a, b]}}\Pi_i(t_i, t_{-i})
-	\]
-	%from which we also get
-	%\[B_i(t_{-i}) = \argmax_{t_i > 0} \cup_{\forall [a, b] \subset [0, 1]}\Pi_{i, [a, b]}(t_{-i})\]
-\end{definition}
-
-From this definition it naturally follows that the best response of a link operator $i$ given $t_{-i}$ depends on the max profit value over any set of intervals that completely cover $[0, 1]$.
+It naturally follows that the best response of a link operator $i$ given $t_{-i}$ depends on the max profit value over any set of intervals that completely cover $[0, 1]$.
 For step distribution functions, this set can be the domains of each of its finitely different values $\alpha_1 < \ldots < \alpha_m$.
@@
 \begin{definition}[Algorithm]
-	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
-	Then we define the following algorithm that takes as input a game's parameters and returns the Nash Equilibrium of the pricing game, if any.
+	\label{definition:algorithm:ne_pricing}
+	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous game with latency functions $\ell = (\ell_1(x), \ell_2(x))_{i \in [2]} = (a_ix + b_i)_{i \in [2]}$ and $\alpha$ a step distribution function with values $(\alpha_k)_{k \in [m]}$.
+	Then we define the following algorithm that takes a heterogeneous game's parameters as input and decides the existence of a Nash Equilibrium of the pricing game or not.
+
+	\begin{algorithm}
+		\caption{Decide and return the pricing Nash Equilibrium for a heterogeneous network with step distribution function}
+		\label{algorithm:ne_pricing}
+		\begin{algorithmic}[1]
+			%\Return $t^*$ the Nash Equilibrium for the pricing game, $0$ if not existent
+			\State $t_1 \gets \frac13 \cdot (2 a_2 + b_2 + a_1 - b_1)$; $t_2 \gets \frac13 \cdot (2 a_1 + b_1 + a_2 - b_2)$
+			\State $x_1 \gets t_1 / (a_1 + a_2)$; $x_2 \gets t_2 / (a_1 + a_2)$
+			\State $\as \gets \frac{\ell_2(x_2) - \ell_1(x_1)}{t_1 - t_2}$
+			\If{$\as \notin (\alpha_k)_{k \in [m]}$}
+				\State \Return $0$
+			\EndIf
+			\State $z \gets$ index of $\as$ in $(\alpha_k)_{k \in [m]}$
+			\State $t_1 \gets \alpha_z t_1$; $t_2 \gets \alpha_z t_2$
+			\State $\Pi_1 = x_1 t_1$; $\Pi_2 = x_2 t_2$
+			\ForAll{$k \in [m]$}
+				\State $t_{1, k} = B_{i, k}(t_2)$
+				\State $p_1, p_2 \gets$ the border players for which $\alpha(p) = \alpha_k$
+				\For{$p_1, p_2$}
+					\State $t_{1, k^-} = \frac{3p_1 - 2}{\alpha_k}$
+					\State $t_{1, k^+} = \frac{3p_2 - 2}{\alpha_k}$
+					\If{$t_{1, k} \in [t_{1, k^-}, t_{1, k^+}]$}
+						\State $\Pi_{1, k} \gets t_{1, k}$
+						\State $\Pi_{2, k} \gets t_{2, k}$
+					\Else
+						\State $\Pi_{1, k} \gets \max\{t_{1, k^-}, t_{1, k^+}\}$
+						\State $\Pi_{2, k} \gets \max\{t_{2, k^-}, t_{2, k^+}\}$
+					\EndIf
+				\EndFor
+				\If{$\Pi_{1, k} > \Pi_1$ \textbf{or} $\Pi_{2, k} > \Pi_2$}
+					\State \Return $0$
+				\EndIf
+				\If{($\Pi_{1, k} = \Pi_1$ \textbf{or} $\Pi_{2, k} = \Pi_2$) \textbf{and} $k \ne z$}
+					\State \Return $0$
+				\EndIf
+			\EndFor
+			\State \Return $(t_1, t_2)$
+		\end{algorithmic}
+	\end{algorithm}
+\end{definition}
+
+\begin{theorem}
+	Algorithm \ref{algorithm:ne_pricing} is correct.
+\end{theorem}
+
+\begin{proof}
+	Consider $\Gm^\prime = ([2], \ell, 1)$ the homogeneous pricing game with latency functions same as in $\Gm$.
+	We can use formulas \ref{eq:homogeneous_x_i} and \ref{eq:homogeneous_pricing_ne_i} for $2$ links to calculate the respective formulas for $t^*$ and $x(t^*)$ in $\Gm^\prime$.
+	Indeed, for $i, j$ our two links, we can find
+	\[
+		t_i^* = \frac{2 a_j + b_j + a_i - b_i}{3} \qquad x_i(t^*) = \frac{2 a_j + b_j + a_i - b_i}{3(a_j + a_i)} = \frac{t_i^*}{a_j + a_i}
+	\]
+	which leads our calculations in lines $1-5$.
+	After calculating $\as(t^*)$ from Definition \ref{definition:split_function}, we check whether that value is one of $(\alpha_k)_{k \in [m]}$, and if not, Lemma \ref{lemma:alpha_step_gaps} ensures that a Nash equilibrium for the pricing game does not exist.
+	Otherwise we denote as $z \in [m]$ the index for which $\as(t^*) = \alpha_z$.
+	From Corollary ?? we know that if a Nash Equilibrium exists, then it will be at $t^{*\prime} = \alpha_z \cdot t^*$.
 	\begin{enumerate}
-		\item Consider $\Gm^\prime = ([2], \ell, 1)$ the homogeneous pricing game with latency functions same as in $\Gm$, and calculate its Nash equilibrium $t^*$.
-		\item Calculate $\as(t^*)$.
-		\begin{enumerate}
-			\item[2.1] If $t^*$ in the closure of $T_{-a}$, then there is no Nash equilibrium for the pricing game in $\Gm$.
-			\item[2.2] Otherwise, calculate $\Pi_{i, k}$ for all link operators $i$ and $\alpha_k$ values.
+		\item Calculate $\Pi_{i, k}$ for all link operators $i$ and $\alpha_k$ values.
 		\begin{enumerate}
@@
 	\end{enumerate}
-	\end{enumerate}
-\end{definition}
+\end{proof}
 
@@
 \addcontentsline{toc}{chapter}{Appendix}
-\chapter*{Appendix}
+\chapter{Appendix}
 \label{chapter:appendix}
+
+\section*{Propositions}
+
+\begin{lemma}
+	\label{lemma:a_0_accumulation_point}
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game with distribution function $\alpha$ such that $\alpha(0) = 0$ and $0$ is an accumulation point.
+	For all $t \in \R_+^{|N|}$, if $x_1(t)$ the lowest-latency link in the link ordering of $t$, then $x_1(t) > 0$.
+\end{lemma}
+
+\begin{proof}
+	By the definition of an accumulation point, we get for $0$ in $\alpha$ that $\forall \delta > 0 \; \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
+	Therefore $\forall t \in \R_+^{|N|}$ if $\delta = \min_{i \in N \setminus \{1\}}\as^{(1, i)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(1, i)}(t)$ for all $i \in N \setminus \{1\}$, which means that the lowest-latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t) > 0$.
+\end{proof}
 
@@
 
-[TODO: add framework for examining games]
-
 \begin{example}
 	\label{example:ap_p}
-	Consider a $2$-link parallel network pricing game with $l_1(x) = x, l_2(x) = 2x$ and distribution function $\alpha(p) = p$.
+	Consider a $2$-link parallel network pricing game with $\ell_1(x) = x, \ell_2(x) = 2x$ and distribution function $\alpha(p) = p$.
 \end{example}
@@
 Notice that the condition $\alpha(p) > 0$ when $p > 0$ holds for this example.
-However in this case $0$ is an accumulation point, and by Lemma $\ref{lemma:split_bounds}(ii)$ it follows $x_1(t), x_2(t) > 0, \forall t \in \R_+^2$.
+However in this case $0$ is an accumulation point, and by Lemma $\ref{lemma:a_0_accumulation_point}$ it follows $x_1(t), x_2(t) > 0, \forall t \in \R_+^2$.
 Then Lemma $\ref{lemma:split_basic}$ entails that, assuming $t_1 > t_2$, $\alpha(x_1(t)) \le \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon > 0$ arbitrarily small, and since in this example $\alpha$ is onto, then $\as(t) = \alpha(x_1(t))$.

### 2025-01-03 thesis/article.tex
Thesis: Adds Chapter 4 final Algorithm with Lemma for NE relation in fixed dist func

@@
 For those we will show an equivalence with a homogeneous game for a given toll \ref{lemma:heterogenous_flow_equiv_fixed} and combining it with Lemma \ref{lemma:alpha_step_gaps} where we'll show that a Nash Equilibrium cannot exist with all players of each sensitivity type using a single link, we get this chapter's main result, Theorem \ref{theorem:a_step_ne_equiv_fixed}, which states that if a Nash Equilibrium exists in a heterogeneous game with a step distribution function, then the respective homogeneous also has an equilibrium for the same set of tolls.
-Using this notion, we will describe an algorithm (\ref{definition:algorithm:ne_pricing}) which can decide existence and return the Nash Equilibrium for the pricing competition game in a heterogeneous $2$-link network.
+Using this notion, we will describe an algorithm (\ref{algorithm:ne_pricing}) which can decide existence and return the Nash Equilibrium for the pricing competition game in a heterogeneous $2$-link network.
 
@@
 	\label{lemma:a_fixed_c_relation}
-	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1 > 0$ and $c_2 > 0$ respectively.
+	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha^{(1)}(p) = c_1 > 0$ and $\alpha^{(2)}(p) = c_2 > 0$ respectively.
 	Then the following are true
@@
 \end{figure}
+
+We proceed with a consequence of the above behaviour for the Nash Equilibrium for the pricing game.
+
+\begin{lemma}
+	\label{lemma:a_fixed_pricing_ne_relation}
+	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha^{(1)}(p) = c_1 > 0$ and $\alpha^{(2)}(p) = c_2 > 0$ respectively.
+	Also let $t^{*(1)}$ and $t^{*(2)}$ be the Nash Equilibria for the pricing games in $\Gm_1$ and $\Gm_2$ respectively.
+	Then the following are true
+	\begin{enumerate}[$(i)$]
+		\item $\frac{t^{*(1)}}{t^{*(2)}} = \frac{c_2}{c_1}$
+		\item $x^{(1)}(t^{*(1)}) = x^{(2)}(t^{*(2)})$
+	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	\begin{enumerate}[$(i)$]
+		\item From the definition of a Nash Equilibrium for the pricing game, we have for all $i \in N$ in $\Gm_1$ that
+		\[
+			t_i^{*(1)} = B_i^{(1)}(t_{-i}^{*(1)})
+		\]
+		where we observe from Lemma \ref{lemma:a_fixed_c_relation} that
+		\[
+			B_i^{(1)}(t_{-i}^{*(1)}) = \frac{c_1}{c_1} \cdot B_i^{(1)}\left(\frac{c_2}{c_2} t_{-i}^{*(1)}\right) \stackrel{\ref{lemma:a_fixed_c_relation}}{=} \frac{c_2}{c_1} \cdot B_i^{(2)}\left(\frac{c_1}{c_2}t_{-i}^{*(1)}\right)
+		\]
+		From those two equations we eventually get
+		\[
+			\frac{c_1}{c_2} t_i^{*(1)} = B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i}^{*(1)}\right)
+		\]
+		for all $i \in N$, which means that $\tfrac{c_1}{c_2} t_i^{*(1)}$ is a Nash Equilibrium for the pricing game in $\Gm_2$.
+		From the uniqueness of the equilibrium, we arrive at $\tfrac{c_1}{c_2} t^{*(1)} = t^{*(2)}$.
+		\item From $(i)$ and Lemma \ref{lemma:a_fixed_c_relation}$(i)$  we get
+		\[
+			x^{(1)}(t^{*(1)}) \stackrel{(i)}{=} x^{(1)}\left(\tfrac{c_2}{c_1}t^{*(2)}\right) \stackrel{\ref{lemma:a_fixed_c_relation}}{=} x^{(2)}(t^{*(2)})
+		\]
+	\end{enumerate}
+\end{proof}
 
@@
 
-\begin{definition}[Algorithm]
-	\label{definition:algorithm:ne_pricing}
-	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous game with latency functions $\ell = (\ell_1(x), \ell_2(x))_{i \in [2]} = (a_ix + b_i)_{i \in [2]}$ and $\alpha$ a step distribution function with values $(\alpha_k)_{k \in [m]}$.
-	Then we define the following algorithm that takes a heterogeneous game's parameters as input and decides the existence of a Nash Equilibrium of the pricing game or not.
-
 \begin{algorithm}
-		\caption{Decide and return the pricing Nash Equilibrium for a heterogeneous network with step distribution function}
-		\label{algorithm:ne_pricing}
+	\caption{Helper functions for Algorithm \ref{algorithm:step_ne_pricing}}
+	\label{algorithm:step_helper_functions}
 	\begin{algorithmic}[1]
-			%\Return $t^*$ the Nash Equilibrium for the pricing game, $0$ if not existent
-			\State $t_1 \gets \frac13 \cdot (2 a_2 + b_2 + a_1 - b_1)$; $t_2 \gets \frac13 \cdot (2 a_1 + b_1 + a_2 - b_2)$
-			\State $x_1 \gets t_1 / (a_1 + a_2)$; $x_2 \gets t_2 / (a_1 + a_2)$
-			\State $\as \gets \frac{\ell_2(x_2) - \ell_1(x_1)}{t_1 - t_2}$
-			\If{$\as \notin (\alpha_k)_{k \in [m]}$}
-				\State \Return $0$
+		\Function{\texttt{TollDiff}}{$\alpha_k, x_1$} \label{function:toll_diff}
+		\State \Return $\frac{1}{\alpha_k}[(a_1 + a_2) x_1 - a_2 + b_1 - b_2]$
+		\EndFunction
+
+		\Statex
+		\Function{\texttt{Profit1}}{$\alpha_k, t_1, t_2$} \label{function:profit_1}
+		\State \Return $\frac{t_1}{a_1 + a_2} [a_2 + b_2 - b_1 + \alpha_k (t_2 - t_1)]$
+		\EndFunction
+
+		\Statex
+		\Function{\texttt{Profit2}}{$\alpha_k, t_1, t_2$} \label{function:profit_2}
+		\State \Return $\frac{t_2}{a_1 + a_2} [a_1 + b_1 - b_2 + \alpha_k (t_1 - t_2)]$
+		\EndFunction
+
+		\Statex
+		\Function{\texttt{BestResponse1}}{$\alpha_k, t_2$} \label{function:best_response_1}
+		\If{$t_2 \le \frac{1}{\alpha_k}(2 a_1 + a_2 + b_1 - b_2)$}
+		\State \Return $\frac{t_2}{2} + \frac{1}{2 \alpha_k}(a_2 + b_2 - b_1)$
+		\Else
+		\State \Return $t_2 - \frac{1}{\alpha_k}(a_1 + b_1 - b_2)$
 		\EndIf
-			\State $z \gets$ index of $\as$ in $(\alpha_k)_{k \in [m]}$
-			\State $t_1 \gets \alpha_z t_1$; $t_2 \gets \alpha_z t_2$
-			\State $\Pi_1 = x_1 t_1$; $\Pi_2 = x_2 t_2$
-			\ForAll{$k \in [m]$}
-				\State $t_{1, k} = B_{i, k}(t_2)$
-				\State $p_1, p_2 \gets$ the border players for which $\alpha(p) = \alpha_k$
-				\For{$p_1, p_2$}
-					\State $t_{1, k^-} = \frac{3p_1 - 2}{\alpha_k}$
-					\State $t_{1, k^+} = \frac{3p_2 - 2}{\alpha_k}$
-					\If{$t_{1, k} \in [t_{1, k^-}, t_{1, k^+}]$}
-						\State $\Pi_{1, k} \gets t_{1, k}$
-						\State $\Pi_{2, k} \gets t_{2, k}$
+		\EndFunction
+
+		\Statex
+		\Function{\texttt{BestResponse2}}{$\alpha_k, t_1$} \label{function:best_response_2}
+		\If{$t_1 \le \frac{1}{\alpha_k}(2 a_2 + a_1 + b_2 - b_1)$}
+		\State \Return $\frac{t_1}{2} + \frac{1}{2 \alpha_k}(a_1 + b_1 - b_2)$
 		\Else
-						\State $\Pi_{1, k} \gets \max\{t_{1, k^-}, t_{1, k^+}\}$
-						\State $\Pi_{2, k} \gets \max\{t_{2, k^-}, t_{2, k^+}\}$
+		\State \Return $t_1 - \frac{1}{\alpha_k}(a_2 + b_2 - b_1)$
 		\EndIf
-				\EndFor
+		\EndFunction
+	\end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+	\caption{Decide existence and return the Nash Equilibrium for the pricing game of a heterogeneous network with $2$ links and step distribution function}
+	\label{algorithm:step_ne_pricing}
+	\begin{algorithmic}[1]
+		\Require $(a_i, b_i)_{i \in N}$, step function $\alpha$
+		\Ensure $(t_1, t_2)$
+		\State $t_1 \gets \frac13 \cdot (2 a_2 + b_2 + a_1 - b_1)$;\; $t_2 \gets \frac13 \cdot (2 a_1 + b_1 + a_2 - b_2)$
+		\State $x_1 \gets t_1 / (a_1 + a_2)$;\; $x_2 \gets t_2 / (a_1 + a_2)$
+		\If{$t_1 > t_2$}
+		\State $\as \gets \alpha(x_1)$
+		\Else
+		\State $\as \gets \alpha(x_2)$
+		\EndIf
+		\State $t_1 \gets \frac{t_1}{\alpha_s}$;\; $t_2 \gets \frac{t_2}{\alpha_s}$
+		\State $\Pi_1 = x_1 t_1$;\; $\Pi_2 = x_2 t_2$
+		\For{$k$ \textbf{in} $[1, 2, \dots, m]$}
+		\If{$\alpha_k = \as$}
+		\State \texttt{continue}
+		\EndIf
+		\State $t_{1, k} \gets \Call{\texttt{BestResponse1}}{\alpha_k, t_2}$;\; $t_{2, k} \gets \Call{\texttt{BestResponse2}}{\alpha_k, t_1}$
+		\State $p_k^-, p_k^+ \gets$ border players where $\alpha(p) = \alpha_k$
+		\State $t_{d^-}^- \gets \Call{\texttt{TollDiff}}{\alpha_k, p_k^-};\qquad t_{d^-}^+ \gets \Call{\texttt{TollDiff}}{\alpha_k, p_k^+}$
+		\State $t_{d^+}^- \gets \Call{\texttt{TollDiff}}{\alpha_k, 1 - p_k^+};\; t_{d^+}^+ \gets \Call{\texttt{TollDiff}}{\alpha_k, 1 - p_k^-}$
+		\State $t_{1, k^-}^- \gets t_2 - t_{d^-}^-$;\; $t_{1, k^-}^+ \gets t_2 - t_{d^-}^+$;\; $t_{1, k^+}^- \gets t_2 - t_{d^+}^-$;\; $t_{1, k^+}^+ \gets t_2 - t_{d^+}^+$
+		\State $t_{2, k^-}^- \gets t_1 + t_{d^-}^-$;\; $t_{2, k^-}^+ \gets t_1 + t_{d^-}^+$;\; $t_{2, k^+}^- \gets t_1 + t_{d^+}^-$;\; $t_{2, k^+}^+ \gets t_1 + t_{d^+}^+$
+		\If{$t_{1, k^-}^- \le t_{1, k} \le t_{1, k^-}^+$ \textbf{or} $t_{1, k^+}^- \le t_{1, k} \le t_{1, k^+}^+$}
+		\State $\Pi_{1, k} \gets \Call{\texttt{Profit1}}{\alpha_k, t_{1, k}, t_2}$
+		\Else
+		%\For{$(i, j)$ \textbf{in} $[(1, 2), (2, 1)]$}
+		\State $\Pi_{1, k} \gets \max\{\Call{\texttt{Profit1}}{\alpha_k, t_{1, k^-}^-, t_2},$ $\Call{\texttt{Profit1}}{\alpha_k, t_{1, k^-}^+, t_2},$
+		\Statex \hspace{8.5em} $\Call{\texttt{Profit1}}{\alpha_k, t_{1, k^+}^-, t_2},$ $\Call{\texttt{Profit1}}{\alpha_k, t_{1, k_+}^+, t_2}\}$
+		\EndIf
+		\If{$t_{2, k^-}^- \le t_{2, k} \le t_{2, k^-}^+$ \textbf{or} $t_{2, k^+}^- \le t_{2, k} \le t_{2, k^+}^+$}
+		\State $\Pi_{2, k} \gets \Call{\texttt{Profit2}}{\alpha_k, t_1, t_{2, k}}$
+		\Else
+		\State $\Pi_{2, k} \gets \max\{\Call{\texttt{Profit2}}{\alpha_k, t_1, t_{2, k^-}^-},$  $\Call{\texttt{Profit2}}{\alpha_k, t_1, t_{2, k^-}^+},$
+		\Statex \hspace{8.5em} $\Call{\texttt{Profit2}}{\alpha_k, t_1, t_{2, k^+}^-},$ $\Call{\texttt{Profit2}}{\alpha_k, t_1, t_{2, k_+}^+}\}$
+		\EndIf
 		\If{$\Pi_{1, k} > \Pi_1$ \textbf{or} $\Pi_{2, k} > \Pi_2$}
-					\State \Return $0$
-				\EndIf
-				\If{($\Pi_{1, k} = \Pi_1$ \textbf{or} $\Pi_{2, k} = \Pi_2$) \textbf{and} $k \ne z$}
 		\State \Return $0$
@@
 \end{algorithm}
-\end{definition}
 
 \begin{theorem}
-	Algorithm \ref{algorithm:ne_pricing} is correct.
+	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous game with latency functions $\ell = (\ell_1(x), \ell_2(x))_{i \in [2]} = (a_ix + b_i)_{i \in [2]}$ and $\alpha$ a step distribution function with values $(\alpha_k)_{k \in [m]}$.
+	Then Algorithm \ref{algorithm:step_ne_pricing} with input $(\ell, \alpha)$ calculates the Nash Equilibrium for the pricing game in $\Gm$ in $\mathcal{O}(m)$ time.
 \end{theorem}
@@
 \begin{proof}
-	Consider $\Gm^\prime = ([2], \ell, 1)$ the homogeneous pricing game with latency functions same as in $\Gm$.
-	We can use formulas \ref{eq:homogeneous_x_i} and \ref{eq:homogeneous_pricing_ne_i} for $2$ links to calculate the respective formulas for $t^*$ and $x(t^*)$ in $\Gm^\prime$.
-	Indeed, for $i, j$ our two links, we can find
+	Consider $\Gm^\prime = ([2], \ell, 1)$ the homogeneous pricing game with latency functions same as in $\Gm$ and let $t^*, t^{\prime*}$ the Nash Equilibria for the pricing games in $\Gm, \Gm^\prime$ respectively.
+	By using formulas \ref{eq:homogeneous_x_i} and \ref{eq:homogeneous_pricing_ne_i}, adjusted for $2$ links, we can solve for $t^{*}$ and get, for $i, j$ an arbitrary ordering of our two links, that
 	\[
@@
 	\]
-	which leads our calculations in lines $1-5$.
-	After calculating $\as(t^*)$ from Definition \ref{definition:split_function}, we check whether that value is one of $(\alpha_k)_{k \in [m]}$, and if not, Lemma \ref{lemma:alpha_step_gaps} ensures that a Nash equilibrium for the pricing game does not exist.
-	Otherwise we denote as $z \in [m]$ the index for which $\as(t^*) = \alpha_z$.
-	From Corollary ?? we know that if a Nash Equilibrium exists, then it will be at $t^{*\prime} = \alpha_z \cdot t^*$.
-	\begin{enumerate}
-		\item Calculate $\Pi_{i, k}$ for all link operators $i$ and $\alpha_k$ values.
-		\begin{enumerate}
-			\item[2.2.1] If $\Pi_i(t^*) \ge \Pi_{i, k}$ for all $k \in [m]$ and for all $i \in [2]$ then $t^*$ is a Nash equilibrium in $\Gm$.
-			\item[2.2.2] Otherwise, there is no Nash equilibrium in $\Gm$.
-		\end{enumerate}
-	\end{enumerate}
+	These formulas hold for homogeneous games, so we use them to calculate $t^{\prime*}$ and $x^\prime(t^{\prime*})$ in $\Gm^\prime$.
+	If we assume that $t^*$ exists, then Theorem \ref{theorem:a_step_ne_equiv_fixed} tells us that $t^*$ is also the Nash Equilibrium for the pseudo-heterogeneous pricing game $\Gm^{\prime\prime} = ([2], \ell, \as(t^*))$, while Lemma \ref{lemma:alpha_step_gaps} gives us that $\as(t^*)$ needs to take some value in $(\alpha_k)_{k \in [m]}$, with flow users for which $\alpha(p) = \as(t^*)$ assigned in both links.
+	Finally, by applying Lemma \ref{lemma:a_fixed_pricing_ne_relation}$(ii)$ in $\Gm^\prime$ and $\Gm^{\prime\prime}$, we can see that, regardless of the value of $\as(t^*)$, it always holds that $x(t^*) = x^\prime(t^{*\prime})$.
+	We can therefore check whether $t_1^{*\prime} > t_2^{*\prime}$ or $t_1^{*\prime} < t_2^{*\prime}$ and take $x_1$ or $x_2$ to be the lower split in each case (which will remain so in $\Gm$ for any sensitivity $\alpha_k > 0$), giving us $\as(t^*) = \alpha(x_1^\prime(t^{*\prime}))$ or $\alpha(x_2^\prime(t^{*\prime}))$ respectively.
+	Having calculated $\as(t^*)$, we now get from Lemma \ref{lemma:a_fixed_pricing_ne_relation}$(i)$ for $\Gm^\prime$ and $\Gm^{\prime\prime}$ that $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$, the calculation of which gives us our candidate Nash Equilibrium $t^*$.
+
+	We're only left with ensuring that $t^*$ is indeed a Nash Equilibrium for the pricing game in $\Gm$, i.e.
+for both link operators $i \in [2]$ to hold $\Pi_i(t_i^*, t_{-i}^*) \ge \Pi_i(t_i, t_{-i}^*)$ for all $t_i \in \R_+$.
+	Since $t^*$ is the equilibrium in $\Gm^{\prime\prime}$, we know that $t_i^*$ is the max profit toll response against $t_{-i}^*$ compared to $t_i$ where $\as(t_i, t_{-i}^*) = \as(t^*)$, and since $\as(t^*)$ takes a value $\alpha_z$ for some $z \in [m]$, we only need to check for splits in the remaining $(\alpha_k)_{k \in [m] \setminus \{z\}}$ values.
+	Therefore, for all $k \in [m] \setminus \{z\}$, we need to search for max profit within tolls $t_k$ such that $\as(t_k) = \alpha_k$ .
+	As showcased in Example \ref{example:a_step_simple}, we can find those toll difference ranges by solving the cost equality equation $\ell_1(x_1) + \alpha_k t_1 = \ell_2(x_2) + \alpha_k t_2$ for a target $\alpha_k$ value and flow such that all players with $\alpha(p) = \alpha_k$ are using a single link.
+	Indeed, if we consider from the definition of $\alpha$ the border players $p_k^-, p_k^+$ for which $\alpha(p) = \alpha_k$ when $p_k^- < p < p_k^+$, then the possible link splits are those where $x_1$ (arbitrarily chosen) has flow such that $x_1 = p_k^-, p_k^+, 1 - p_k^+, 1 - p_k^-$.
+	Solving the cost equality equation for $t_2 - t_1$ (and by substituting $x_2$ for $1 - x_1$) we get the formula of \texttt{TollDiff} function in \algref{algorithm:step_helper_functions}{function:toll_diff}, and by then using it in the above four cases for $x_1$, we get from each of the two pairs a min and a max toll difference, each belonging to a different split, for which a set of tolls $t$ is in that range if and only if $\as(t) = \alpha_k$.
+
+	Before we continue, we need to discuss the profit and best response functions.
+	By again solving the cost equality equation for $x_i$ we get
+	\[
+		x_i(t) = \frac{a_{-i} + b_{-i} - b_i + \alpha_k (t_{-i} - t_i)}{a_1 + a_2}
+	\]
+	so by using that and taking $\Pi_{i, k}(t) = x_i(t) t_i$ we get the \texttt{Profit1} (\algref{algorithm:step_helper_functions}{function:profit_1}) and \texttt{Profit2} (\algref{algorithm:step_helper_functions}{function:profit_2}) functions.
+	Finally, by taking first order conditions on them with regard to $t_i$, we also get the respective \texttt{BestResponse1} (\algref{algorithm:step_helper_functions}{function:best_response_1}) and \texttt{BestResponse2} (\algref{algorithm:step_helper_functions}{function:best_response_2}) functions.
+	For the latter, we need put extra care to handle large $t_{-i}$, as the current formulas can return $t_i$ such that $x_i(t_i, t_{-i}) > 1$.
+	We therefore need to take into account the toll difference bounds discussed in Chapter \ref{chapter:preliminaries}, i.e. solve for $t_{-i}$ the equation
+	\[
+		t_{-i} - \Call{\texttt{BestResponseI}}{t_{-i}} = \frac{\ell_i(1) - \ell_{-i}(0)}{\alpha_k} = \frac{a_i + b_i - b_{-i}}{\alpha_k}
+	\]
+	thus finding opposing toll $t_{-i} = \frac{2 a_i + a_{-i} + b_i - b_{-i}}{\alpha_k}$ for which the best response is to take the entire flow.
+	Any higher $t_{-i}$ will therefore also have as best response to take the entire flow, leading to a best response toll of $t_i = t_{-i} - \frac{a_i + b_i - b_{-i}}{\alpha_k}$.
+	The last condition and formula completes the \texttt{BestResponse1} (\algref{algorithm:step_helper_functions}{function:best_response_1}) and \texttt{BestResponse2} (\algref{algorithm:step_helper_functions}{function:best_response_2}) function definitions.
+
+	So for all $k \in [m] \setminus \{z\}$ and all link operators $i \in [2]$, we assume a pseudo-heterogeneous game $\Gm_k = ([2], \ell, \alpha_k)$ and calculate the best response toll $t_{i, k}$ against $t_{-i}^*$ using the respective \texttt{BestResponse1} or \texttt{BestResponse2} function.
+	Also, we solve $t_2 - t_1 = \texttt{TollDiff}$ for the respective $t_i$ against $t_{-i}^*$ and calculate the two $t_i$ ranges for which $\as(t_i, t_{-i}^*) = \alpha_k$.
+	If $t_{i, k}$ is within any of the two ranges, then max profit is obviously achieved at $t_{i, k}$, which is the $\max_{t_i} \Pi_i(t_i, t_{-i}^*)$ in $\Gm_k$.
+	Otherwise, since $\Pi_i(t)$ is concave from the analysis of Harkes et al.
+\cite{Harks_2019}, not taking a max value at a range follows that profit is either non-decreasing or non-increasing in that range, resulting in its local maximum achieved at one of its edge values.
+	So, in that case, we calculate all edge profit values from the two ranges and keep the overall max value.
+
+	Having now calculated the max profit among all tolls for which $\as(t) = \alpha_k$, we check whether that value is higher that the profit from the candidate toll, and if so, then $t^*$ is not a Nash Equilibrium for the pricing game in $\Gm$.
+	If the last condition fails for all $k \in [m] \setminus \{z\}$, then $t^*$ is a Nash Equilibrium for the pricing game in $\Gm$, so we return it.
+
+	We should also mention that we've on purpose ignored invalid toll difference cases.
+	Theorem \ref{theorem:alpha_upper_irrelevant} shows us there might be sensitivity values that are irrelevant to the game.
+	The algorithm will ignore those cases, however, as the \texttt{TollDiff} function will return $t_i < 0$, resulting in $\Pi_i < 0$, which will be skipped when looking for max profit values.
+
+	Finally, regarding the complexity of Algorithm \ref{algorithm:step_ne_pricing}, we can easily see that it mostly consists of base operations with a \texttt{for} loop taking at most $m - 1$ iterations, resulting in a time complexity of $\mathcal{O}(m)$.
 \end{proof}
 
-Given the restrictions of the possible positions for Nash equilibrium tolls, it would be tempting to try and calculate exact conditions for it.
-Those conditions would depend on latencies and the distance of the step function's $k$ values.
-
-Unfortunately the results do not scale for $n$-link parallel networks.
+Concluding our analysis for step distribution functions in $2$-link networks, one note we'd like to take from this chapter is the clear issues that gaps in the money-sensitivity values create in the Nash Equilibrium for the pricing game, making their removal (by e.g.
+assuming continuous functions) lead to better properties for the pricing game.
+We will continue the discussion on further extensions of this work in the next chapter.
+
+\cleardoublepage
+
+\chapter{Future work}
+\label{chapter:future_work}
+
+A natural extension of the above would be to examine them for $[N]$ parallel graphs.
+Some of the properties naturally extend but for others more care is required.
+Special notice and expansion is certainly necessary for the split function, as it is only defined for two links.
+On a first thought, it seems trivial to also order the links on an equilibrium by latency and then define the split function on each consecutive pair, therefore also having an ordered set of split function values.
+Still, more investigation is needed to uncover the relation between those values, and its consequences to the flow's or the pricing game's behaviours.
+
+Putting the pricing games aside, it would also be interesting to expand the split function for series-parallel graphs.
+
+\section*{Time-money sensitivity relation}
+
+The standard technique to capture heterogeneity in the users of a network has been to apply a weight $\alpha$ to the toll cost viewed be each user, making their total cost $\ell(x) + \alpha t$.
+This approach is equivalent to applying the inverse weight to the latency, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
+Though less intuitive we already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed} where we showed that a fixed distribution function is equivalent to restricting the latency functions inversely proportionally, however the idea could potentially be extended outside of fixed values.
+This would of course does not guarantee that the latency functions will remain affine, or even polynomial.
+One could attempt and investigate distribution functions that are inverse polynomials, making the respective latencies remain polynomial.
+In any case we believe that a future work on the relation of the time-sensitivity with money sensitivity approaches, could uncover further insights in the behavior of heterogeneity.
+
+\section*{Pseudo-heterogeneous games}
+
+In Chapter \ref{chapter:pricing_equilibria} we investigated the class of heterogeneous games with a fixed distribution function, which maintains its homogeneous behaviour and presents interesting properties when comparing different fixed sensitivities.
+Since these games have a clear connection to heterogeneous games with step functions, it shows special interest to study the relation of flow and profit with regard to the same $t$, as this approach can then lead to a characterisation of those in step functions.
+
+\subsection*{Profit maximisation}
+
+During the investigation of this study, there has been some minor results in the relation of flow and profit between two similar pseudo-heterogeneous games.
+We present a list of conjectures that we believe are true.
+
+\section*{Continuous functions}
 
@@
 
-\cleardoublepage
-
-\chapter{Future work}
-\label{chapter:future_work}
-
-A natural extension of the above would be to examine them for $[N]$ parallel graphs.
-Some of the properties naturally extend but for others more care is required.
-Special notice and expansion is certainly necessary for the split function, as it is only defined for two links.
-On a first thought, it seems trivial to also order the links on an equilibrium by latency and then define the split function on each consecutive pair, therefore also having an ordered set of split function values.
-Still, more investigation is needed to uncover the relation between those values, and its consequences to the flow's or the pricing game's behaviours.
-
-Putting the pricing games aside, it would also be interesting to expand the split function for series-parallel graphs.
-
-\section*{Time-money sensitivity relation}
-
-The standard technique to capture heterogeneity in the users of a network has been to apply a weight $\alpha$ to the toll cost viewed be each user, making their total cost $\ell(x) + \alpha t$.
-This approach is equivalent to applying the inverse weight to the latency, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
-Though less intuitive we already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed} where we showed that a fixed distribution function is equivalent to restricting the latency functions inversely proportionally, however the idea could potentially be extended outside of fixed values.
-This would of course does not guarantee that the latency functions will remain affine, or even polynomial.
-One could attempt and investigate distribution functions that are inverse polynomials, making the respective latencies remain polynomial.
-In any case we believe that a future work on the relation of the time-sensitivity with money sensitivity approaches, could uncover further insights in the behavior of heterogeneity.
-
-\section*{Pseudo-heterogeneous games}
-
-In Chapter \ref{chapter:pricing_equilibria} we investigated the class of heterogeneous games with a fixed distribution function, which maintains its homogeneous behaviour and presents interesting properties when comparing different fixed sensitivities.
-Since these games have a clear connection to heterogeneous games with step functions, it shows special interest to study the relation of flow and profit with regard to the same $t$, as this approach can then lead to a characterisation of those in step functions.
-
-\subsection*{Profit maximisation}
-
-During the investigation of this study, there has been some minor results in the relation of flow and profit between two similar pseudo-heterogeneous games.
-We present a list of conjectures that we believe are true.
+\section*{Other}
+
+Given the restrictions of the possible positions for Nash equilibrium tolls, it would be tempting to try and calculate exact conditions for it.
+Those conditions would depend on latencies and the distance of the step function's $k$ values.
+
+Unfortunately the results do not scale for $n$-link parallel networks.
 

### 2025-01-04 thesis/article.tex
Thesis: Finished Future Work and Appendix (with all unused propositions included)

@@
 \pagenumbering{gobble}
+
 \chapter*{Συνοψη}
@@
 They showed that increasing the competition among operators from a monopoly to an oligopoly may reduce the efficiency of the network, achieving tight bounds on the Price of Anarchy.
-In a follow-up work \cite{10.1109/JSAC.2007.070812}, they generalised the above by assuming more general topologies where links can also be linked serially (series-parallel networks).
+In a follow-up work \cite{10.1109/JSAC.2007.070812}, they generalised the above by assuming more general topologies where links can also be linked serially (serial-parallel networks).
 Correa et al. \cite{correa2018pricing} showed pricing games may not exist, may not be unique and can be arbitrarily inefficient, but regulating the network with toll caps can solve all three issues.
@@
 We will then proceed to analyse games with fixed distribution functions, where in Lemma \ref{lemma:a_fixed_homogeneous} we will show that such games are, as intuition suggests, equivalent to homogeneous games.
-Special interest will then be on comparing such games, specifically those with the same setup but different fixed $\alpha$ functions, as Lemma \ref{lemma:a_fixed_c_relation} will reveal that uniformly varying the player sensitivity maps the toll values around the same flow.
+Special interest will then be on comparing such games, specifically those with the same setup but different fixed $\alpha$ functions, as Lemma \ref{lemma:a_fixed_c_relation} will reveal that, uniformly varying the player sensitivity, maps the toll values around the same flow.
 The tools and notions built above will prove extremely useful when we next analyse games with step distribution functions, where we'll restrict our analysis to instances with $2$ links to simplify our work.
 For those we will show an equivalence with a homogeneous game for a given toll \ref{lemma:heterogenous_flow_equiv_fixed} and combining it with Lemma \ref{lemma:alpha_step_gaps} where we'll show that a Nash Equilibrium cannot exist with all players of each sensitivity type using a single link, we get this chapter's main result, Theorem \ref{theorem:a_step_ne_equiv_fixed}, which states that if a Nash Equilibrium exists in a heterogeneous game with a step distribution function, then the respective homogeneous also has an equilibrium for the same set of tolls.
-Using this notion, we will describe an algorithm (\ref{algorithm:ne_pricing}) which can decide existence and return the Nash Equilibrium for the pricing competition game in a heterogeneous $2$-link network.
+Using this notion, we will describe an algorithm (\ref{algorithm:step_ne_pricing}) which can decide existence and return the Nash Equilibrium for the pricing competition game in a heterogeneous $2$-link network.
 
@@
 
-What we need to examine  next is how those two games react differently for an link $i$ given a fixed $t_{-i}$.
-For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference.
-
-TODO: Fix the next Lemma.
-For affine latencies, we can calculate the best response functions $B_i(t_{-i})$.
-For each link operator $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
-\begin{equation}
-	\label{eq:homogeneous_br_i}
-	B_i(t_{-i}) = \frac{1 + \sum_{j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \ne i}\frac{2}{a_j}}
-\end{equation}
-
-%In the extreme cases where the toll differences are arbitrarily large, the best response of some players will be to lower their toll and take all available flow.
-
-To describe more properties of homogeneous pricing games we will need the following crucial Lemma.
-\begin{lemma}
-	\label{lemma:tolls_diff}
-	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
-	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
-\end{lemma}
-
-\begin{proof}
-	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
-	From formula \ref{eq:homogeneous_br_i} after some calculations we get
-	\[
-	B_i(t_{-i}) - t_j = \left(\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1\right)t_j + \frac{1 + \frac{b_j - b_i}{a_j} + \sum_{k \ne i, j}\frac{b_k + t_k - b_i}{a_k}}{\sum_{k \ne i} \frac{2}{a_k}}
-	\]
-	which is decreasing with regards to $t_j$ if and only if its coefficient is negative.
-	Indeed, since $a_i > 0$ for all $i$, we get
-	\[
-	\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1 = \frac{1}{2 \left(1 + \sum_{k \ne i, j} \frac{a_j}{a_k}\right)} - 1 \leq \frac{1}{2} - 1 < 0
-	\]
-\end{proof}
-
- which is in turn non-increasing with regards to $t_{-i}$ (\ref{lemma:tolls_diff}).
-Therefore, as $t_{-i}$ increases, the best response gets decreasing difference with $t_{-i}$, thus taking more flow in $x_i$.
-Eventually there will be a smallest possible $t_{-i}$ where the best response is to take all flow, and henceforth any larger $t_{-i}$ will also result in a best response with the same toll difference and flow.
-We will use this property to describe the flow relation between the two games in the following lemma.
-
-\begin{lemma}
-	\label{lemma:a_fixed_t_iM_fixed}
-	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
-	Also let $t_{-i_M}^{(1)}, t_{-i_M}^{(2)}$ the smallest possible $t_{-i}$ where $x_i(B_i(t_{-i}), t_{-i}) = 1$, respectively for each game.
-	Then the following hold.
-	\begin{enumerate}[$(i)$]
-		\item $t_{-i_M}^{(2)} < t_{-i_M}^{(1)}$
-		\item $x_i^{(1)}(B_i^{(1)}(0), 0) = x_i^{(2)}(B_i^{(2)}(0), 0)$
-		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) = x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i}) = 1$ for all $t_{-i} \ge t_{-i_M}^{(1)}$
-		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) < x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})$, for all $t_{-i} \in (0, t_{-i_M}^{(1)})$
-		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}), x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})$ get max distance at $t_{-i_M}^{(2)}$ \\
-		\textit{(conjecture)}
-	\end{enumerate}
-\end{lemma}
-
-\begin{proof}
-	$ $
-	\begin{enumerate}[$(i)$]
-		\item Assume $t_{-i_M}^{(2)} \ge t_{-i_M}^{(1)}$.
-		Then from Corollary \ref{corollary:a_fixed_c_relation} we get
-		\begin{flalign*}
-			1 = &x_i^{(1)}(B_i^{(1)}(t_{-i_M}^{(1)}), t_{-i_M}^{(1)}) = x_i^{(2)}\left( \frac{c_1}{c_2} \cdot B_i^{(1)}(t_{-i_M}^{(1)}), \frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right) & \\
-			&= x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right), \frac{c_1}{c_2} \cdot t_{-i_M}^{(1)}\right) &
-		\end{flalign*}
-		which is a contradiction since $\frac{c_1}{c_2} t_{-i_M}^{(1)} < t_{-i_M}^{(1)} \le t_{-i_M}^{(2)}$ and $t_{-i_M}^{(2)}$ is the smallest value with that property.
-		Therefore the initial assumption is wrong and we get $t_{-i_M}^{(2)} < t_{-i_M}^{(1)}$.
-		\item With application of Corollary \ref{corollary:a_fixed_c_relation} we have
-		\[
-			x_i^{(1)}(B_i^{(1)}(0), 0) = x_i^{(2)}\left(\frac{c_1}{c_2} \cdot B_i^{(1)}(0), 0\right) = x_i^{(2)}(B_i^{(2)}(0), 0)
-		\]
-		\item Since from $(i)$ we have $t_{-i_M}^{(1)} = \max\{t_{-i_M}^{(1)}, t_{-i_M}^{(2)}\}$ then the property follows from the definitions of $t_{-i_M}^{(1)}, t_{-i_M}^{(2)}$.
-		\item For $t_{-i} \in (t_{-i_M}^{(2)}, t_{-i_M}^{(1)})$ obviously
-		\[
-			x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) < 1 = x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})
-		\]
-		Then for $t_{-i} \in (0, t_{-i_M}^{(2)})$ with the same way we used Corollary \ref{corollary:a_fixed_c_relation} as in $(i)$ we see that
-		\[
-			x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) = x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right), \frac{c_1}{c_2} \cdot t_{-i}\right)
-		\]
-		where the second part is the flow in $\Gm_2$ at the best response of link operator $i$ against $\frac{c_1}{c_2} t_{-i}$.
-		Therefore their best response against $t_{-i} > \frac{c_1}{c_2} t_{-i}$ will have a lower toll difference to $t_{-i}$ (\ref{lemma:tolls_diff}) and thus more flow, arriving at
-		\[
-			x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i}\right), \frac{c_1}{c_2} \cdot t_{-i}\right) < x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})
-		\]
-	\end{enumerate}
-\end{proof}
-
-%\begin{lemma}
-%	\label{lemma:a_fixed_x12}
-%	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
-%	Then the following hold.
-%	\begin{enumerate}[$(i)$]
-%		\item $x^{(1)}(0) = x^{(2)}(0)$
-%		\item $x_i^{(1)}(t) - x_i^{(2)}(t)$ is non-decreasing in relation to $t_i - t_{-i}$
-%	\end{enumerate}
-%\end{lemma}
-%Notice that the above Lemma also provides us with $x_i^{(1)}(t) < x_i^{(2)}(t)$ iff $t_i < t_{-i}$ and vice versa, as well as that this difference is expanded as $t_i - t_{-i}$ does.
-%We avoided using the affinity of the latency functions on purpose to get a more general notion between the two games.
-%Using latency functions now, we can get a calculated version of the above.
-%\begin{corollary}
-%	\label{lemma:a_fixed_x12_calc}
-%	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same affine latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
-%	Then for some fixed number $K_i > 0$ it holds that
-%	\[x_i^{(1)}(t) - x_i^{(2)}(t) = K_i \cdot (t_i - t_{-i})\]
-%\end{corollary}
-%
-%\begin{proof}
-%	From equation \ref{eq:homogeneous_x_i} for $2$ links and under universal sensitivity $c_1, c_2$ respectively we get
-%	\begin{align*}
-%		x_i^{(1)}(t) - x_i^{(2)}(t) &= \frac{a_{-i} + b_{-i} + c_1t_{-i} - b_i - c_1t_i}{a_i} - \frac{a_{-i} + b_{-i} + c_2t_{-i} - b_i - c_2t_i}{a_i} \\
-%		&= \frac{(c_2 - c_1)(t_i - t_{-i})}{a_i}
-%	\end{align*}
-%	So the property holds for $K_i = \frac{c_2 - c_1}{a_i} > 0$.
-%\end{proof}
-
-We finally arrive at the main theorem of this section, which describes similar properties for the relative behaviour of the profit functions between the two games.
-Fist, let's remind ourselves that from Lemma \ref{lemma:tolls_diff} for each game $B_i(t_{-i}) - t_{-i}$ is decreasing as well as continuous.
-Therefore, given that best responses range from above and below $t_{-i}$ values, there exists some $t_{-i_0}$ for which $B_i(t_{-i_0}) = t_{-i_0}$.
-We state now our theorem.
-
-\begin{theorem}
-	\label{theorem:a_fixed_t_i0}
-	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
-	Also let $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ the respective tolls for which $B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)}$ and $B_i^{(1)}(t_{-i_0}^{(2)}) = t_{-i_0}^{(2)}$.
-	Then for all links $i$ it holds that
-	\begin{enumerate}[$(i)$]
-		\item $t_{-i_0}^{(1)} > t_{-i_0}^{(2)}$
-		\item There exists $t_{-i_0} \in \left(t_{-i_0}^{(2)}, t_{-i_0}^{(1)}\right)$ such that
-		\[\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}) = \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0})\]
-		\item $\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$ is non-increasing in relation to $t_{-i}$.
-		\item $t_{-i_0}$ is the geometric mean of $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$
-	\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-	$ $
-	\begin{enumerate}[$(i)$]
-		\item From Corollary \ref{corollary:a_fixed_c_relation}$(iii)$ we get
-		\[
-			B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)} \Rightarrow B_i^{(2)}\left(\frac{c_1}{c_2} \cdot t_{-i_0}^{(1)}\right) = \frac{c_1}{c_2} \cdot t_{-i_0}^{(1)}
-		\]
-		and from the fact that $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ are the unique solutions of their respective equations we get $t_{-i_0}^{(2)} = \frac{c_1}{c_2} \cdot t_{-i_0}^{(1)} < t_{-i_0}^{(1)}$.
-		\item Consider the function $\Pi_i(t_{-i}) = \max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$.
-		Then for $t_{-i} = t_{-i_0}^{(2)}$ we see that in $\Gm_2$ the best response for link operator $i$ is to play the same toll as in the other link, therefore they get max profit at $x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$.
-		In $\Gm_1$ now, since $t_{-i_0}^{(2)} < t_{-i_0}^{(1)}$ then the best response for link operator $i$ is for some $t_i > t_{-i_0}^{(2)}$, and since from \ref{corollary:a_fixed_c_relation}$(i)$ the profit $x_i^{(1)}(0) = x_i^{(2)}(0) \cdot t_{-i_0}^{(2)}$ is also one of their options, it means that the profit at $t_i$ is greater, i.e.
-		\[
-			\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}^{(2)}) > \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0}^{(2)}) \Rightarrow \Pi_i(t_{-i_0}^{(2)}) > 0
-		\]
-		Similarly we can show that $\Pi_i(t_{-i_0}^{(1)}) < 0$.
-		With all the above and given that we know from the analysis in Harkes et al.
-\cite{Harks_2019} that best response functions are continuous, from the Bolzano theorem (TODO: Is this the right theorem?
-Reference?) we get that there exists $t_{-i_0} \in \left(t_{-i_0}^{(2)}, t_{-i_0}^{(1)}\right)$ such that $\Pi_i(t_{-i_0}) = 0$, which gives us the desired proposition.
-		\item We will use the same $\Pi_i$ function as in $(ii)$, so we instead need to show that $\Pi_i(t_{-i})$ is non-decreasing in relation to $t_{-i}$.
-		For all $t_{-i} \ge t_{-i_M}^{(1)}$ from Lemma \ref{lemma:a_fixed_t_iM_fixed} we get $\Pi_i(t_{-i}) = 1 \cdot B_i^{(1)}(t_{-i}) - 1 \cdot B_i^{(2)}(t_{-i})$, where the best responses have fixed differences to $t_{-i}$ (and therefore to each other as well), making $\Pi_i(t_{-i})$ in turn fixed for all $t_{-i} \ge t_{-i_M}^{(1)}$.
-		TODO: Pending.
-		\item By using the $B_i(t_{-i})$ formula to find $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ and then solve $\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}) = \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0})$.
-		TODO: Either replace with a theoretical proof or write the calculations.
-	\end{enumerate}
-\end{proof}
-
-Finally, we can again calculate $t_{-i_0}$ using the closed formulas provided by the affine assumption.
-
-\begin{corollary}
-	\label{corollary:a_fixed_ti0_calc}
-	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_1)$ two heterogeneous pricing games with the same latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $c_2 > c_1 > 0$ respectively.
-	Then for $t_{-i_0}$ defined in Theorem \ref{theorem:a_fixed_t_i0} for the two games it holds that
-	\[t_{-i_0} = \frac{a_{-i} + b_{-i} - b_i}{\sqrt{c_1 c_2}}\]
-\end{corollary}
-
-\begin{proof}
-	We can easily calculate $t_{-i_0}^{(1)}$ and $t_{-i_0}^{(2)}$.
-	For $\Gm_1$ we have
-	\[B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)} \Rightarrow \frac{a_{-i} + b_{-i} - b_i + c_1 t_{-i_0}^{(1)}}{2 c_1} = t_{-i_0}^{(1)} \Rightarrow t_{-i_0}^{(1)} = \frac{a_{-i} + b_{-i} - b_i}{c_1}\]
-	Similarly for $\Gm_2$ we have $t_{-i_0}^{(2)} = \frac{a_{-i} + b_{-i} - b_i}{c_2}$, so finally from Theorem \ref{theorem:a_fixed_t_i0}$(iv)$ we get
-	\[t_{-i_0} = \sqrt{t_{-i_0}^{(1)} \cdot t_{-i_0}^{(2)}} = \frac{a_{-i} + b_{-i} - b_i}{\sqrt{c_1 c_2}}\]
-\end{proof}
+%What we need to examine  next is how those two games react differently for an link $i$ given a fixed $t_{-i}$.
+%For this it is important to focus again on the fact that the flow is exclusively dependent on the toll difference.
 We have now gathered all necessary tools to start investigating step distribution functions.
@@
 
-It therefore seems to make sense to discuss profit only within those intervals where the flow changes, or equivalently view profit with regard to flow intervals, since we ignore instances where the flow remains the same and thus there exists a $1-1$ relation between profit and flow.
-It naturally follows that the best response of a link operator $i$ given $t_{-i}$ depends on the max profit value over any set of intervals that completely cover $[0, 1]$.
-For step distribution functions, this set can be the domains of each of its finitely different values $\alpha_1 < \ldots < \alpha_m$.
-As such $\forall k \in [m]$ we denote as $A_k$ the closed set of all players $p$ in $[0, 1]$ for whom $\alpha(p) = \alpha_k$.
-Obviously $\cup_{k=1}^m A_k = [0, 1]$ and from the assumption that $\alpha$ is non-decreasing we also get $A_k$ convex $\forall k \in [m]$.
-When looking at the flow (and consequently profit) of a specific link $i$, however, the split behaviour of the distribution function makes it possible for different flows having the same money sensitivity split.
-We will therefore use the money sensitivity split function to refer to the respective flows that follow it, and formalise the profit and respective best response of link operator $i$ in the following definition.
-
-\begin{definition}
-	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function and $(A_k)_{k \in [m]}$ the partition of $[0, 1]$ that is defined by the domain of $\alpha$.
-	Then for link operator $i$ the definition of $\Pi_i$ is extended for an interval $A_k$ as
-	\[
-		\Pi_{i, k}(t_{-i}) = \max_{\stackrel{t_i > 0}{\as(t_i, t_{-i}) = \alpha_k}}\Pi_i(t_i, t_{-i})
-	\]
-\end{definition}
-
-When it comes to maximising profit for the pricing games, those values included in all $\Pi_{i, k}$ are all we need, because if $\as(t)$ takes any other in-between value, then we are on an instance where no player views the two link costs as equal, with players viewing a purely smaller cost in either link.
-For the link operators, this means there at least one who can increase their toll and still keep the flow the same, achieving pure profit.
-This can also happen in link cases of $\as(t) = \alpha_k$, so we move our full description of this behavior in the following lemma.
-
-The most important corollary from that lemma comes from the fact that, as stated in \ref{lemma:a_fixed_ne}, for any $c > 0$ the flow for which the Nash Equilibrium emerges is always the same.
-Consequently for any step function assigned to a pricing game with fixed latency functions, if a Nash Equilibrium exists then it needs to be on the same flow as the one emerging in the respective homogeneous pricing game.
-
 With such a strong notion of the pricing Nash equilibrium, we can now see a potential algorithm that can be used to query its existence or not as well as calculate it.
-We present it here.
+We present it in Algorithm \ref{algorithm:step_ne_pricing}.
 
@@
 
-A natural extension of the above would be to examine them for $[N]$ parallel graphs.
-Some of the properties naturally extend but for others more care is required.
-Special notice and expansion is certainly necessary for the split function, as it is only defined for two links.
-On a first thought, it seems trivial to also order the links on an equilibrium by latency and then define the split function on each consecutive pair, therefore also having an ordered set of split function values.
-Still, more investigation is needed to uncover the relation between those values, and its consequences to the flow's or the pricing game's behaviours.
-
-Putting the pricing games aside, it would also be interesting to expand the split function for series-parallel graphs.
+In this chapter we will close on some of the discussions from previous chapters by exploring potential extensions of them that could be studied in future projects.
 
@@
 
-The standard technique to capture heterogeneity in the users of a network has been to apply a weight $\alpha$ to the toll cost viewed be each user, making their total cost $\ell(x) + \alpha t$.
-This approach is equivalent to applying the inverse weight to the latency, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
-Though less intuitive we already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed} where we showed that a fixed distribution function is equivalent to restricting the latency functions inversely proportionally, however the idea could potentially be extended outside of fixed values.
-This would of course does not guarantee that the latency functions will remain affine, or even polynomial.
-One could attempt and investigate distribution functions that are inverse polynomials, making the respective latencies remain polynomial.
-In any case we believe that a future work on the relation of the time-sensitivity with money sensitivity approaches, could uncover further insights in the behavior of heterogeneity.
+For general heterogeneous models, the standard technique to capture the heterogeneity of the users in a network (at least in the accounted work) has been to apply a weight $\alpha$ to the toll cost viewed by each user, thus making their total cost $\ell(x) + \alpha t$.
+This approach is equivalent to applying the inverse weight to the latency cost, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
+We already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed}, where we showed that a heterogeneous game with a fixed distribution function is equivalent to a homogeneous game with latency functions restricted inversely proportionally.
+Unfortunately, as mentioned before, this correspondence is lost when considering non-fixed distribution functions, as then different tolls can create similar flows used by players with different sensitivity values, thus loosing the $1-1$ relation between latency and $\alpha$ values.
+
+Still, we believe that studying games with time sensitivity costs instead of money sensitivity ones, i.e.
+heterogeneous games with user cost $\tfrac1\alpha \ell(x) + t$, has the potential to reveal more insights about the game's mechanics and heterogeneous behaviour, which can then be mapped back to game models with the standard user cost of $\ell(x) + \alpha t$.
 
@@
 
-In Chapter \ref{chapter:pricing_equilibria} we investigated the class of heterogeneous games with a fixed distribution function, which maintains its homogeneous behaviour and presents interesting properties when comparing different fixed sensitivities.
-Since these games have a clear connection to heterogeneous games with step functions, it shows special interest to study the relation of flow and profit with regard to the same $t$, as this approach can then lead to a characterisation of those in step functions.
-
-\subsection*{Profit maximisation}
-
-During the investigation of this study, there has been some minor results in the relation of flow and profit between two similar pseudo-heterogeneous games.
-We present a list of conjectures that we believe are true.
-
-\section*{Continuous functions}
-
-%Specifically the case of $\alpha(p) = cp$, for some $c > 0$, shows some interesting behavior, as it creates instances where $\Pi_i$ becomes either unbounded or fixed; in the first case then $B_i$ becomes unbounded, while in the second it becomes an an infinite set.
-%This is showcased analytically in Example \ref{example:ap_p} in the Appendix, where for $\alpha(p) = p$ we see that the resulting best responses can indeed be undefined or unbounded.
-%When does this happen?
-%Is the problem $0$ being an accumulation point?
-%\begin{lemma}[Conjecture]
-%	If a distribution function has $\alpha(p) \le p \; \forall p$, then $\Pi_i$ becomes either unbounded or fixed.
-%\end{lemma}
-
-\section*{Other}
-
-Given the restrictions of the possible positions for Nash equilibrium tolls, it would be tempting to try and calculate exact conditions for it.
-Those conditions would depend on latencies and the distance of the step function's $k$ values.
-
-Unfortunately the results do not scale for $n$-link parallel networks.
+In Chapter \ref{chapter:pricing_equilibria} we investigated the class of heterogeneous games with a fixed distribution function, called in this work \textit{pseudo-heterogeneous games}, as we discovered that they still maintain a homogeneous behaviour, with tolls scaled inverse proportionally to their fixed sensitivity value (Figure \ref{figure:alpha_fixed:flow}).
+Continuing on the study of similar games with different fixed distribution functions, we believe there is special interest in doing so with regard to the same opposing toll $t_{-i}$.
+Such an analysis can shed more light into the relations between flow, tolls, profit etc.
+among similar games where the fixed sensitivity value varies, which, apart from its clear connection to games with step distribution functions (Lemma \ref{lemma:heterogenous_flow_equiv_fixed}), it could also potentially lead to a more complete characterisation of the heterogeneity's effect on the game overall.
+
+Having conducted this analysis partially, we include in the Appendix the (incomplete) propositions \ref{lemma:a_fixed_t_iM}, \ref{lemma:a_fixed_x12}, \ref{corollary:a_fixed_x12_calc} and \ref{lemma:a_fixed_t_i0}, which try to describe that relation between flow and profit, among similar games with varying fixed sensitivity, for the same opposing $t_{-i}$.
+We hope this work can be used as a basis for any further investigation on the property relations between similar pseudo-heterogeneous games.
+
+\section*{Step distribution functions}
+
+\subsection*{$2$-link networks}
+
+Algorithm \ref{algorithm:step_ne_pricing} calculates tolls which are a candidate Nash Equilibrium for the pricing game and then checks for all step function values that no profit earned in a different sensitivity split is higher than that.
+Given those restrictions, it seems very possible to calculate exact conditions for a candidate set of tolls to be a Nash Equilibrium.
+Those conditions would heavily depend on the definition of $\alpha$, making the player splits as well as the distance of the step function's $\alpha_k$ values appear to be the defining factors.
+Therefore another possible extension of this work would be to compute and study these exact conditions.
+
+\subsection*{$n$-link networks}
+
+A natural question pending from Chapter \ref{chapter:pricing_equilibria} is whether any of the properties described for step distribution functions for $2$-link networks can be extended for $n$-link parallel ones.
+The main issue with that potential extension is that, even for $3$-link parallel networks, the notion of a single user viewing all link costs equally is lost, as different sensitivity splits between any two pairs of links will make is so that no sensitivity value can view them all equal.
+
+A different approach is therefore required to study step distribution functions for $n$-link parallel heterogeneous networks, with possible directions being investigating the different sensitivity splits among the links, running simulations, or even focusing on the algorithmic aspect of the game, where complexity results regarding the calculation or simply decision of a Nash Equilibrium can also give us further insights into the game's properties.
+Finally, another (maybe odd) way to characterise the pricing game for some $n$-link networks, would be proving it never exists for $n \ge 3$ under some conditions, a possibility which the authors have suspected.
+The main motivation for such a suspicion, is that even for $n = 3$, with the condition of having different sensitivity splits between the two consecutive pairs of links (with regard to a toll ordering on links), the respective sub-games of those pairs will likely display a behaviour similar to $2$-link networks, thus each converging to their own toll equilibrium and never reaching one overall.
+
+It is clear that studying any of the above directions would require much additional analysis around heterogeneous pricing games, so we hope that the tools and notions developed in this thesis can be used as base in any such potential future work.
+
+\section*{Continuous distribution functions}
+
+Another possible continuation of this work would be to investigate Nash Equilibria in heterogeneous pricing games for which heterogeneity is described by continuous distribution functions.
+Though other function types can also be of interest, as we mentioned in our analysis of step distribution functions in Chapter \ref{chapter:pricing_equilibria}, gaps in the player sensitivity values may break a potential Nash Equilibrium for the pricing game, a case completely eradicated by assuming continuity.
+
+For such functions, however, our former restriction of $\alpha(p) > 0$ when $p > 0$ does not suffice, as similar issues can arise when considering many players with almost no toll-fear.
+In Lemma \ref{lemma:a_0_accumulation_point} we attempt to show that when $0$ is an accumulation point in $\alpha$, then the lowest latency toll will always have flow, conditions similar to those of Lemma \ref{lemma:a_0_0}, suggesting the possible emergence of a similar behaviour.
+Example \ref{example:ap_p} in the Appendix analyses a game with distribution function $\alpha(p) = p$, and showcases that the resulting best responses can indeed be undefined or unbounded, marking this function (or similar ones, e.g.
+$\alpha(p) = cp$, for some $c > 0$) to be of interest for further study.
+
+\section*{Split function for series-parallel links}
+
+Finally, in Chapter \ref{chapter:split}, we put the pricing games aside and introduced the concept of a money sensitivity split, which can help us describe how the user sensitivity is divided among the different links.
+While this notion works well for parallel networks, it could potentially also work on series-parallel ones, networks allowing for more general graph configurations.
+While in such complex networks the link sequence can vary greatly (potentially mixing different sensitivity split values in merging links), we believe there is great interest as well as value in examining how those split values behave as a heterogeneous flow moves through different link configurations, making any future research around this topic prone to acquiring further insights regarding heterogeneous games overall.
 
@@
 
+The following prepositions are not vetted and the author does not claim that any of the statements are concretely true.
+They are included here, however, first to present some parallel results that were produced during the development of this research, and then to provide additional info in some of the discussions throughout.
+
 \begin{lemma}
@@
 
-\section*{Example calculations}
+%To describe more properties of homogeneous pricing games we will need the following crucial Lemma.
+\begin{lemma}
+	\label{lemma:tolls_diff}
+	Let $(N, \ell, 1)$ be a homogeneous pricing game, and let $D_i$ a function for each link $i$ where $D_i(t_{-i}) = B_i(t_{-i}) - t_{-i}$, a vector of $t_i - t_j$ values for all $t_j \in t_{-i}$.
+	Then $D_i$ is decreasing with regard to any $t_j \in t_{-i}$.
+\end{lemma}
+
+\begin{proof}
+	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
+	For affine latency functions, we can calculate the best response functions $B_i(t_{-i})$ for each link operator $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
+	\begin{equation}
+		\label{eq:homogeneous_br_i}
+		B_i(t_{-i}) = \frac{1 + \sum_{j \ne i}\frac{b_j + t_j - b_i}{a_j}}{\sum_{j \ne i}\frac{2}{a_j}}
+	\end{equation}
+	From formula \ref{eq:homogeneous_br_i} after some calculations we get
+	\[
+		B_i(t_{-i}) - t_j = \left(\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1\right)t_j + \frac{1 + \frac{b_j - b_i}{a_j} + \sum_{k \ne i, j}\frac{b_k + t_k - b_i}{a_k}}{\sum_{k \ne i} \frac{2}{a_k}}
+	\]
+	which is decreasing with regards to $t_j$ if and only if its coefficient is negative.
+	Indeed, since $a_i > 0$ for all $i$, we get
+	\[
+		\frac{1}{\sum_{k \ne i} \frac{2a_j}{a_k}} - 1 = \frac{1}{2 \left(1 + \sum_{k \ne i, j} \frac{a_j}{a_k}\right)} - 1 \leq \frac{1}{2} - 1 < 0
+	\]
+\end{proof}
+
+which is in turn non-increasing with regards to $t_{-i}$ (\ref{lemma:tolls_diff}).
+Therefore, as $t_{-i}$ increases, the best response gets decreasing difference with $t_{-i}$, thus taking more flow in $x_i$.
+Eventually there will be a smallest possible $t_{-i}$ where the best response is to take all flow, and henceforth any larger $t_{-i}$ will also result in a best response with the same toll difference and flow.
+We will use this property to describe the flow relation between the two games in the following lemma.
+
+\subsection*{Pseudo-heterogeneous games}
+
+\begin{lemma}
+	\label{lemma:a_fixed_t_iM}
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_2)$ two pseudo-heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha^{(1)}(p) = c_1$ and $\alpha^{(2)}(p) = c_2 > c_1 > 0$ respectively.
+	Also let $t_{-i_M}^{(1)}, t_{-i_M}^{(2)}$ the smallest possible $t_{-i}$ where $x_i(B_i(t_{-i}), t_{-i}) = 1$, respectively for each game.
+	Then the following hold.
+	\begin{enumerate}[$(i)$]
+		\item $t_{-i_M}^{(2)} < t_{-i_M}^{(1)}$
+		\item $x_i^{(1)}(B_i^{(1)}(0), 0) = x_i^{(2)}(B_i^{(2)}(0), 0)$
+		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) = x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i}) = 1$ for all $t_{-i} \ge t_{-i_M}^{(1)}$
+		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) < x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})$, for all $t_{-i} \in (0, t_{-i_M}^{(1)})$
+		\item $x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}), x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})$ get max distance at $t_{-i_M}^{(2)}$ \\
+		\textit{(conjecture)}
+	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	$ $
+	\begin{enumerate}[$(i)$]
+		\item Assume $t_{-i_M}^{(2)} \ge t_{-i_M}^{(1)}$.
+		Then from Lemma \ref{lemma:a_fixed_c_relation} we get
+		\begin{flalign*}
+			1 = &x_i^{(1)}(B_i^{(1)}(t_{-i_M}^{(1)}), t_{-i_M}^{(1)}) = x_i^{(2)}\left( \frac{c_1}{c_2} B_i^{(1)}(t_{-i_M}^{(1)}), \frac{c_1}{c_2} t_{-i_M}^{(1)}\right) & \\
+			&= x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i_M}^{(1)}\right), \frac{c_1}{c_2} t_{-i_M}^{(1)}\right) &
+		\end{flalign*}
+		which is a contradiction since $\frac{c_1}{c_2} t_{-i_M}^{(1)} < t_{-i_M}^{(1)} \le t_{-i_M}^{(2)}$ and $t_{-i_M}^{(2)}$ is the smallest value with that property.
+		Therefore the initial assumption is wrong and we get $t_{-i_M}^{(2)} < t_{-i_M}^{(1)}$.
+		\item With the application of Lemma \ref{lemma:a_fixed_c_relation} we have
+		\[
+			x_i^{(1)}(B_i^{(1)}(0), 0) = x_i^{(2)}\left(\frac{c_1}{c_2} B_i^{(1)}(0), 0\right) = x_i^{(2)}(B_i^{(2)}(0), 0)
+		\]
+		\item Since from $(i)$ we have $t_{-i_M}^{(1)} = \max\{t_{-i_M}^{(1)}, t_{-i_M}^{(2)}\}$ then the property follows from the definitions of $t_{-i_M}^{(1)}, t_{-i_M}^{(2)}$.
+		\item For $t_{-i} \in (t_{-i_M}^{(2)}, t_{-i_M}^{(1)})$ obviously
+		\[
+			x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) < 1 = x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})
+		\]
+		Then for $t_{-i} \in (0, t_{-i_M}^{(2)})$, using Lemma \ref{lemma:a_fixed_c_relation} the same way as in $(i)$, we see that
+		\[
+		x_i^{(1)}(B_i^{(1)}(t_{-i}), t_{-i}) = x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i}\right), \frac{c_1}{c_2} t_{-i}\right)
+		\]
+		where the second part is the flow in $\Gm_2$ at the best response of link operator $i$ against $\frac{c_1}{c_2} t_{-i}$.
+		Lemma \ref{lemma:tolls_diff}, then, tells us that their best response against $t_{-i} > \frac{c_1}{c_2} t_{-i}$ will have a lower toll difference to $t_{-i}$, and thus more flow, arriving at
+		\[
+			x_i^{(2)}\left(B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i}\right), \frac{c_1}{c_2} t_{-i}\right) < x_i^{(2)}(B_i^{(2)}(t_{-i}), t_{-i})
+		\]
+	\end{enumerate}
+\end{proof}
+
+\begin{lemma}[Conjecture]
+	\label{lemma:a_fixed_x12}
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_2)$ two pseudo-heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha^{(1)}(p) = c_1$ and $\alpha^{(2)}(p) = c_2 > c_1 > 0$ respectively.
+	Then $x_i^{(1)}(t) - x_i^{(2)}(t)$ is non-decreasing in relation to $t_i - t_{-i}$.
+\end{lemma}
+Notice that the above Lemma also provides us with $x_i^{(1)}(t) < x_i^{(2)}(t)$ iff $t_i < t_{-i}$ and vice versa, as well as that this difference is expanded as $t_i - t_{-i}$ does.
+We avoided using the affinity of the latency functions on purpose to get a more general notion between the two games.
+Using latency functions now, we can get a calculated version of the above.
+\begin{corollary}
+	\label{corollary:a_fixed_x12_calc}
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_2)$ two pseudo-heterogeneous pricing games with common latency functions $\ell$ and distribution functions $\alpha^{(1)}(p) = c_1$ and $\alpha^{(2)}(p) = c_2 > c_1 > 0$ respectively.
+	Then for some fixed number $K_i > 0$ it holds that
+	\[x_i^{(1)}(t) - x_i^{(2)}(t) = K_i (t_i - t_{-i})\]
+\end{corollary}
+
+\begin{proof}
+	Using formula \ref{eq:homogeneous_x_i} for $2$ links we get $x_i(t)$ for a homogeneous game.
+	Lemma \ref{lemma:a_fixed_c_relation}$(i)$ gives us $x_i(c_2 t) = x^{(1)}(t)$ and $x_i(c_2 t) = x^{(2)}(t)$, resulting in
+	\begin{align*}
+		x_i^{(1)}(t) - x_i^{(2)}(t) &= \frac{a_{-i} + b_{-i} + c_1t_{-i} - b_i - c_1t_i}{a_i} - \frac{a_{-i} + b_{-i} + c_2t_{-i} - b_i - c_2t_i}{a_i} \\
+		&= \frac{(c_2 - c_1)(t_i - t_{-i})}{a_i}
+	\end{align*}
+	So the property holds for $K_i = \frac{c_2 - c_1}{a_i} > 0$.
+\end{proof}
+
+We finally arrive at the main proposition of this section, which describes similar properties for the relative behaviour of the profit functions between the two games.
+First, let's remind ourselves that, from Lemma \ref{lemma:tolls_diff}, each $B_i(t_{-i}) - t_{-i}$ is decreasing as well as continuous with regard to $t_{-i}$.
+Therefore, given that best responses range from above and below $t_{-i}$ values, there exists some $t_{-i_0}$ for which $B_i(t_{-i_0}) = t_{-i_0}$.
+We state now our lemma.
+
+\begin{lemma}
+	\label{lemma:a_fixed_t_i0}
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_2)$ two pseudo-heterogeneous pricing games with same latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $\alpha^{(2)}(p) = c_2 > c_1 > 0$ respectively.
+	Also let $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ the respective tolls for which $B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)}$ and $B_i^{(1)}(t_{-i_0}^{(2)}) = t_{-i_0}^{(2)}$.
+	Then for all links $i$ it holds that
+	\begin{enumerate}[$(i)$]
+		\item $t_{-i_0}^{(1)} > t_{-i_0}^{(2)}$
+		\item There exists $t_{-i_0} \in \left(t_{-i_0}^{(2)}, t_{-i_0}^{(1)}\right)$ such that
+		\[\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}) = \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0})\]
+		\item $\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$ is non-increasing in relation to $t_{-i}$.
+		\item $t_{-i_0}$ is the geometric mean of $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$
+	\end{enumerate}
+\end{lemma}
+
+\begin{proof}
+	$ $
+	\begin{enumerate}[$(i)$]
+		\item From Lemma \ref{lemma:a_fixed_c_relation}$(iii)$ we get
+		\[
+			B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)} \Rightarrow B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i_0}^{(1)}\right) = \frac{c_1}{c_2} t_{-i_0}^{(1)}
+		\]
+		and from the fact that $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ are the unique solutions of their respective definition equations, we get $t_{-i_0}^{(2)} = \frac{c_1}{c_2} t_{-i_0}^{(1)} < t_{-i_0}^{(1)}$.
+		\item Consider the function $\Pi_i(t_{-i}) = \max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$.
+		Then for $t_{-i} = t_{-i_0}^{(2)}$, in $\Gm_2$ by definition, the best response for link operator $i$ is to play the same toll as in the other link, therefore they get max profit at $x_i^{(2)}(0) t_{-i_0}^{(2)}$.
+		In $\Gm_1$ now, since $t_{-i_0}^{(2)} < t_{-i_0}^{(1)}$, Lemma \ref{lemma:tolls_diff} gives us
+		\[
+			B_i^{(1)}(t_{-i_0}^{(2)}) - t_{-i_0}^{(2)} \ge B_i^{(1)}(t_{-i_0}^{(1)}) - t_{-i_0}^{(1)} \Rightarrow B_i^{(1)}(t_{-i_0}^{(2)}) > t_{-i_0}^{(2)}
+		\]
+		and since $\Pi_i(t_{-i_0}^{(2)}, t_{-i_0}^{(2)}) = x_i^{(1)}(0) t_{-i_0}^{(2)} \indeq{\textrm{\ref{lemma:a_fixed_c_relation}}(i)} x_i^{(2)}(0) t_{-i_0}^{(2)}$ is also one of their options, it means that the profit at $t_i$ is greater, i.e.
+		\[
+			\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}^{(2)}) > \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0}^{(2)}) \Rightarrow \Pi_i(t_{-i_0}^{(2)}) > 0
+		\]
+		Similarly we can show that $\Pi_i(t_{-i_0}^{(1)}) < 0$.
+		With those two inequalities and given that we know from the analysis in Harkes et al.
+\cite{Harks_2019} that best response functions are continuous, we get (from ??) that there exists $t_{-i_0} \in \left(t_{-i_0}^{(2)}, t_{-i_0}^{(1)}\right)$ such that $\Pi_i(t_{-i_0}) = 0$, which gives us the desired proposition.
+		\item We will use the same $\Pi_i$ function as in $(ii)$ and show that $\Pi_i(t_{-i})$ is non-decreasing in relation to $t_{-i}$.
+		For all $t_{-i} \ge t_{-i_M}^{(1)}$, from Lemma \ref{lemma:a_fixed_t_iM}, we get $\Pi_i(t_{-i}) = 1 \cdot B_i^{(1)}(t_{-i}) - 1 \cdot B_i^{(2)}(t_{-i})$, where the best responses have fixed differences to $t_{-i}$ (and therefore to each other as well), making $\Pi_i(t_{-i})$ in turn fixed for all $t_{-i} \ge t_{-i_M}^{(1)}$.
+		We now follow the same reasoning as in $(ii)$.
+		%TODO: Pending.
+		\item We first use the $B_i(t_{-i})$ formula to find $t_{-i_0}^{(1)}$ and $t_{-i_0}^{(2)}$.
+		For $\Gm_1$ we have from the definition of $t_{-i_0}^{(1)}$ that
+		\[
+			B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)} \Rightarrow \frac{a_{-i} + b_{-i} - b_i + c_1 t_{-i_0}^{(1)}}{2 c_1} = t_{-i_0}^{(1)} \Rightarrow t_{-i_0}^{(1)} = \frac{a_{-i} + b_{-i} - b_i}{c_1}
+		\]
+		and similarly for $\Gm_2$ we have $t_{-i_0}^{(2)} = \frac{a_{-i} + b_{-i} - b_i}{c_2}$.
+		Then, solving for $t_{-i_0}$ in
+		\[\max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i_0}) = \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i_0})\]
+		we get
+		\begin{flalign*}
+			&\Pi_i^{(1)}(B_i^{(1)}(t_{-i_0}), t_{-i_0}) = \Pi_i^{(2)}(B_i^{(2)}(t_{-i_0}), t_{-i_0}) \\
+			\Rightarrow &\cdots \\
+			\Rightarrow &t_{-i_0} = \frac{a_{-i} + b_{-i} - b_i}{\sqrt{c_1 c_2}}
+		\end{flalign*}
+		which is obviously the geometric mean of $t_{-i_0}^{(1)}$ and $t_{-i_0}^{(2)}$.
+	\end{enumerate}
+\end{proof}
+
+\subsection*{Step distribution function}
+
+Extending on the discussion about viewing profit only within toll intervals where the flow will change for arbitrary toll variance, we can equivalently view profit with regard to flow intervals, since we ignore instances where the flow remains the same and thus there exists a $1-1$ relation between profit and flow.
+It naturally follows that the best response of a link operator $i$ given $t_{-i}$ depends on the max profit value over any set of intervals that completely cover $[0, 1]$.
+For step distribution functions, this set can be the domains of each of its finitely different values $\alpha_1 < \ldots < \alpha_m$.
+As such, $\forall k \in [m]$ we denote as $A_k$ the closed set of all players $p$ in $[0, 1]$ for whom $\alpha(p) = \alpha_k$.
+Obviously $\cup_{k=1}^m A_k = [0, 1]$ and from the assumption that $\alpha$ is non-decreasing we also get $A_k$ convex $\forall k \in [m]$.
+When looking at the flow (and consequently profit) of a specific link $i$, however, the split behaviour of the distribution function makes it possible for different flows having the same money sensitivity split.
+We will therefore use the money sensitivity split function to refer to the respective flows that follow it, and formalise the profit and respective best response of link operator $i$ in the following definition.
+
+\begin{definition}
+	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function and $(A_k)_{k \in [m]}$ the partition of $[0, 1]$ that is defined by the domain of $\alpha$.
+	Then for link operator $i$ the definition of $\Pi_i$ is extended for an interval $A_k$ as
+	\[
+	\Pi_{i, k}(t_{-i}) = \max_{\stackrel{t_i > 0}{\as(t_i, t_{-i}) = \alpha_k}}\Pi_i(t_i, t_{-i})
+	\]
+\end{definition}
+
+\section*{Examples}
 
@@
 
-\section*{Additional examples}
+\subsection*{Additional examples}
 
@@
 	\label{example:ap_p}
-	Consider a $2$-link parallel network pricing game with $\ell_1(x) = x, \ell_2(x) = 2x$ and distribution function $\alpha(p) = p$.
+	Consider a $2$-link heterogeneous pricing game with latency functions $\ell_1(x) = x, \ell_2(x) = 2x$ and distribution function $\alpha(p) = p$.
 \end{example}
 
-Notice that the condition $\alpha(p) > 0$ when $p > 0$ holds for this example.
-However in this case $0$ is an accumulation point, and by Lemma $\ref{lemma:a_0_accumulation_point}$ it follows $x_1(t), x_2(t) > 0, \forall t \in \R_+^2$.
-Then Lemma $\ref{lemma:split_basic}$ entails that, assuming $t_1 > t_2$, $\alpha(x_1(t)) \le \as(t) \le \alpha(x_1(t) + \epsilon), \forall \epsilon > 0$ arbitrarily small, and since in this example $\alpha$ is onto, then $\as(t) = \alpha(x_1(t))$.
-
-We will calculate $B_i(t_{-i})$ by calculating $x_i(t)$ and then finding $\argmax \Pi_i(t)$.
-Note that since we always have $x_1(t), x_2(t) > 0$ we don't need to take cases where the flow is on one link.
-For tolls $t = (t_1, t_2)$ and respective optimal flow $x = (x_1(t), x_2(t))$ we take the following cases.
+Notice that the condition $\alpha(p) > 0$ when $p > 0$ holds for this example, however in this case $0$ is an accumulation point for $\alpha$.
+Lemma \ref{lemma:split_basic}$(iii)$, combined with the fact that $\alpha$ is continuous, gives us that $\as(t) = \alpha(x_i(t))$ for $x_i$ is the lower split flow.
+
+We will thus calculate $B_i(t_{-i})$ by first calculating $x_i(t)$ and then use $\Pi_i(t) = x_i(t) t_i$ to search for $\argmax_{t_2 < t_1} \Pi_i(t)$.
+%Note that since we always have $x_1(t), x_2(t) > 0$ we don't need to take cases where the flow is on one link.
+For tolls $t = (t_1, t_2)$ and respective optimal flow $x(t) = (x_1(t), x_2(t))$ we take the following cases.
 
@@
 \begin{align}
-	l_1(x_1(t)) + \as(t) t_1 &= l_2(x_2(t)) + \as(t) t_2 &\Rightarrow \notag \\
-	x_1(t) + x_1(t) t_1 &= 2 (1 - x_1(t)) + x_1(t) t_2 &\Rightarrow \notag \\
-	x_1(t) &= \frac{2}{3 + t_1 - t_2} \label{eq:ex2_x1_1}
+	\ell_1(x_1(t)) + \as(t) t_1 &= \ell_2(x_2(t)) + \as(t) t_2 &\Rightarrow & \notag \\
+	x_1(t) + x_1(t) t_1 &= 2 (1 - x_1(t)) + x_1(t) t_2 &\Rightarrow & \notag \\
+	x_1(t) &= \frac{2}{3 + t_1 - t_2} \label{eq:ex2_x1_1} &
 \end{align}
-\[
-	B_1^>(t_2) = \argmax_{t_2 < t_1} x_1(t) t_1 \indeq{(\ref{eq:ex2_x1_1})} \argmax_{t_2 < t_1} \frac{2 t_1}{3 + t_1 - t_2} = \argmax_{t_2 < t_1} \frac{2}{1 + \frac{3 - t_2}{t_1}} =
+which means for the best response function when $t_1 > t_2$, denoted by $B_i^>(t_2)$, that
+\begin{flalign*}
+	B_1^>(t_2) &= \argmax_{t_2 < t_1} x_1(t) t_1 \indeq{(\ref{eq:ex2_x1_1})} \argmax_{t_2 < t_1} \frac{2 t_1}{3 + t_1 - t_2} & \\
+	&= \argmax_{t_2 < t_1} \frac{2}{1 + \frac{3 - t_2}{t_1}} =
 		\begin{cases}
@@
 			t_2, & t_2 > 3 \\
-		\end{cases}
-\]
+		\end{cases} &
+\end{flalign*}
 We can already see some of the problems that appear.
@@
 
-Continuing for $B_2^>(t_1)$ where $x_2(t) = 1 - x_1(t) = \frac{1 + t_1 - t_2}{3 + t_1 - t_2}$, we calculate $\argmax_{t_2 < t_1} \Pi_2(t)$ by taking first order conditions and we get
+Continuing for $B_2^>(t_1)$ where $x_2(t) = 1 - x_1(t) = \frac{1 + t_1 - t_2}{3 + t_1 - t_2}$, we now calculate $\argmax_{t_2 < t_1} \Pi_2(t)$ by taking first order conditions on $\Pi_2(t)$ (with regard to $t_2$), from which we get
 \[\argmax_{t_2 < t_1} \Pi_2(t) = t_1 + 3 - \sqrt{2 t_1 + 6}\]
@@
 
-\paragraph{Combining} $B_1^>(t_2), B_1^<(t_2)$ and $B_2^>(t_1), B_2^<(t_1)$ by comparing at each interval the profits between the strategies $t_1 > t_2$ and $t_1 < t_2$ (i.e.
-comparing profits when playing a toll either higher or lower from the other toll owner), we get the final best response functions
-\begin{equation*}
-	\begin{aligned}
-		B_1(t_2) =
+\paragraph{Combine} now $B_1^>(t_2), B_1^<(t_2)$ and $B_2^>(t_1), B_2^<(t_1)$ by comparing at each interval the profits between the strategies $t_1 > t_2$ and $t_1 < t_2$ (i.e.
+comparing profits for a link operator when their best response toll value is either higher or lower from the opposing one).
+By doing so we get the final best response functions
+\begin{align*}
+	B_1(t_2) &=
 	\begin{cases}
@@
 		t_2 + 3 - \sqrt{t_2 + 3} & t_2 \ge 6
-			\end{cases}
-	\end{aligned}
-	\qquad
-	\begin{aligned}
-		B_2(t_1) =
+	\end{cases} \\[10pt]
+	B_2(t_1) &=
 	\begin{cases}
@@
 	\end{cases}
-	\end{aligned}
-\end{equation*}
-Both toll owners have one thing in common, above a specific threshold $(t_2 > 3, t_1 > 2 \sqrt{2})$ they always play either the same or a lower toll than the other toll owner.
-Below that threshold, which will eventually occur from any starting point, they both get divergent best responses and thus a $\NE$ cannot be defined.
-
-\paragraph{The bad behaviors} are obviously having divergent or undefined best response functions, which we claim occur only when we allow $0$ to be an accumulation point in $\alpha$, since this allows players with arbitrarily low money sensitivity to always stay on the expensive link.
-Assume that in Example $\ref{example:ap_p}$ we use $\alpha(p) = p + 1$ as a distribution function.
+\end{align*}
+Both link operators have one thing in common, which is the fact that, above a specific threshold of the opposing toll ($t_2 > 3, t_1 > 2 \sqrt{2}$), they always play either the same or a lower toll than the other link operator.
+Below that threshold, which will eventually occur from any starting point, they both get divergent best responses and thus a Nash Equilibrium cannot exist.
+
+\paragraph{The bad behaviors} of having divergent or undefined best response functions, we claim only occur when we allow $0$ to be an accumulation point in $\alpha$, as in those cases some players with arbitrarily low money sensitivity value will always stay on the expensive link.
+Assume that in Example \ref{example:ap_p} we instead use $\alpha(p) = p + 1$ as a distribution function.
 Then we get the following best response functions
@@
 		t_2 - 1 & t_2 \ge 5
-	\end{cases}\\
+	\end{cases} \\[10pt]
 	B_2(t_1) &=
@@
 \end{align*}
-which can be shown [TODO: currently done experimentally in python] that has a $\NE$ at $t \approx (1.1464, 0.9268)$.
+which can be shown that have a Nash Equilibrium at
+\[t = \left(\frac{\sqrt{205} - 4}{9}, \frac{\sqrt{205} + 23}{9} - \frac{\sqrt{10}}{6} \sqrt{\sqrt{205} + 23}\right) \approx (1.1464, 0.9268)\]
+This result has been verified to hold in simulations of best response sequences in Python.
 
 \begin{example}
-	Consider a $2$-link parallel network pricing game with $l_1(x) = x, l_2(x) = 2x$ and distribution function
+	Let $\Gm = ([2], \ell, \alpha)$ a $2$-link heterogeneous pricing game with latency functions $\ell_1(x) = x, \ell_2(x) = 2x$ and distribution function
 	\[
@@
 
-First we calculate the edge cases [TODO: add relevant section in preliminaries].
-If all flow is in link $1$ then $t_2 - t_1 = \alpha(0) l_1(1) = 1$, while if all flow is in link $2$ then $t_1 - t_2 = \alpha(0) l_2(1) = 2$ therefore
+First we calculate the toll difference bounds we discussed in Chapter \ref{chapter:preliminaries}.
+If all flow is in link $1$ then $t_2 - t_1 = \frac{\ell_1(1) - \ell_2(0)}{\alpha(0)} = 1$, while if all flow is in link $2$ then $t_1 - t_2 = \frac{\ell_2(1) - \ell_1(0)}{\alpha(0)} = 2$ therefore
 \[t_2 - t_1 \le 1 \qquad t_1 - t_2 \le 2\]
@@
 \[
-	l_1(x_1(t)) + \as(t) t_1 = l_2(x_2(t)) + \as(t) t_2 \Rightarrow	x_1(t) + t_1 = 2 (1 - x_1(t)) + t_2 \Rightarrow
+	\ell_1(x_1(t)) + \as(t) t_1 = \ell_2(x_2(t)) + \as(t) t_2 \Rightarrow	x_1(t) + t_1 = 2 (1 - x_1(t)) + t_2 \Rightarrow
 \]
@@
 \end{equation*}
-and by also applying the edge case restrictions we get
+and by also applying the toll difference bound restrictions we get
 \begin{equation*}
@@
 \end{equation*}
-with profits
+with respective profits
 \begin{equation*}
@@
 
-\paragraph{If $t_1 > t_2$} then $x_1(t)$ is the low-latency flow so we need to take cases depending on its value.
-We will show analytically the process for toll owner $1$.
+\paragraph{If $t_1 > t_2$} then $x_1(t)$ is the low-latency flow, so we need to take cases depending on its value.
+We will show analytically the process for link operator $1$ and then directly present the results for link operator $2$, as the steps are similar.
 
@@
 \[x_1(t) < \frac12 \Rightarrow \frac{2 - (t_1 - t_2)}{3} < \frac12 \Rightarrow t_1 - t_2 > \frac12\]
-so for toll owner $1$ with $B_1^>(t_2) = \frac{t_2 + 2}2$ we have
+so for link operator $1$ with $B_1^>(t_2) = \frac{t_2 + 2}2$ we have
 \[t_1 - t_2 > \frac12 \Rightarrow \frac{t_2 + 2}2 - t_2 > \frac12 \Rightarrow t_2 < 1\]
@@
 \[
-	l_1(x_1(t)) + \as(t) t_1 = l_2(x_2(t)) + \as(t) t_2 \Rightarrow	x_1(t) + 5 t_1 = 2 (1 - x_1(t)) + 5 t_2 \Rightarrow
+	\ell_1(x_1(t)) + \as(t) t_1 = \ell_2(x_2(t)) + \as(t) t_2 \Rightarrow	x_1(t) + 5 t_1 = 2 (1 - x_1(t)) + 5 t_2 \Rightarrow
 \]
@@
 \[x_1(t) > \frac12 \Rightarrow \frac{2 - 5 (t_1 - t_2)}{3} > \frac12 \Rightarrow t_1 - t_2 < \frac1{10}\]
-so for toll owner $1$ we have
+so for link operator $1$ we have
 \[t_1 - t_2 < \frac1{10} \Rightarrow \frac{5 t_2 + 2}{10} - t_2 < \frac1{10} \Rightarrow t_2 > \frac15\]
@@
 \subparagraph{If $x_1 = 1/2$} then $\as(t) \in [1, 5]$ and using the definition we get
-\[\as(t) = \frac{l_2(1/2) - l_1(1/2)}{t_1 - t_2} = \frac1{2 (t_1 - t_2)}\]
+\[\as(t) = \frac{\ell_2(1/2) - \ell_1(1/2)}{t_1 - t_2} = \frac1{2 (t_1 - t_2)}\]
 and in order to get the range of $t_1 - t_2$ where this applies we check
@@
 
-The flow is always the same so the best response for toll owner $1$ is to maximize $t_1 - t_2$ so we get $t_1 - t_2 = 1/2 \Rightarrow t_1 = t_2 + 1/2$.
-
-\subparagraph{Gathering all the above} we see that the player has the option to play $t_1$ with the case that provides the maximum profit, so we calculate them.
+The flow is always the same, so the best response for link operator $1$ is to maximize $t_1 - t_2$, so we get $t_1 - t_2 = 1/2 \Rightarrow t_1 = t_2 + 1/2$.
+
+\subparagraph{Gathering all the above} we see that link operator $1$, when searching for the best response toll, will compare all profits that tolls in each case provide, so we calculate them.
 \[
@@
 
-In a similar way we calculate $B_2^>(t_1)$ and $\Pi_2^>(t_1)$, with only some extra care on the bounds as since $t_2 < t_1$ then not all options are always available (e.g.
-if $t_1 < 1/10$ then only $t_1 - t_2 < 1/10$ can be picked).
+In a similar way we calculate $B_2^>(t_1)$ and $\Pi_2^>(t_1)$, with only some extra care on the bounds, as for $t_2 < t_1$ not all options are always available (e.g.
+if $t_1 < 1/10$ then only $t_2$ such that $t_1 - t_2 < 1/10$ can be picked).
 Finally we get
 
-\begin{equation*}
-	\begin{aligned}
-		B_2^>(t_1) =
+\begin{align*}
+	B_2^>(t_1) &=
 	\begin{cases}
@@
 		t_1 - 2, & t_2 > 5
-		\end{cases}
-	\end{aligned}
-	\qquad
-	\begin{aligned}
-		\Pi_2^>(t_1) =
+	\end{cases} \\[10pt]
+	\Pi_2^>(t_1) &=
 	\begin{cases}
@@
 	\end{cases}
-	\end{aligned}
-\end{equation*}
-
-\subparagraph{Combining} $B_1^>(t_2), B_1^<(t_2)$ and $B_2^>(t_1), B_2^<(t_1)$ the same way as in Example $\ref{example:ap_p}$ we get the final best response functions.
+\end{align*}
+
+\subparagraph{Combining} $B_1^>(t_2), B_1^<(t_2)$ and $B_2^>(t_1), B_2^<(t_1)$ the same way as in Example \ref{example:ap_p}, we get the final best response functions.
 \begin{equation*}
@@
 
-For the above functions we can show [TODO: currently done experimentally in python] that there is NO $\NE$ for the pricing game.
+With the above functions, we can show by simulating best response sequences in Python, that there is no Nash Equilibrium for the pricing game in $\Gm$.
 

### 2025-01-08 thesis/article.tex
Thesis: Adds Examples showing NE step criterion, related discussion and Algorithm summary

@@
 We describe this best response as $B_i(t_{-i}) = \argmax_{t_i \geq 0} \Pi_i(t_i, t_{-i})$.
-Consequently, a toll vector $t$ is a \textit{Nash Equilibrium} for the pricing game, if $\forall i \in N$ and $\forall t_i^\prime \in \R$ it holds that
+Consequently, a toll vector $t$ is a \textit{Nash Equilibrium} for the pricing game, if $\forall i \in N$ and $\forall t_i^\prime \in \R_+$ it holds that
 \[\Pi_i(t_i, t_{-i}) \geq \Pi_i(t_i^\prime, t_{-i})\]
-or, equivalently, if for all $i \in N$ we have $|B_i(t_{-i})| = 1$ and
+or, equivalently, if
 \[t = (B_i(t_{-i}))_{i \in N}\]
@@
 		%\draw[thick] (0,5/3) -- (2,1);
-		\draw[thick,samples at={-1,0}] plot (\x,{4/(3 - \x)});
-		\draw[thick,samples at={0,2}] plot (\x,{5/(3 + \x)});
+		\draw[thick,domain=-1:0] plot (\x,{4/(3-\x)});
+		\draw[thick,domain=0:2] plot (\x,{5/(3+\x)});
 
@@
 		\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
-		\draw (-1/3,0) -- (-1/3,-0.05) node[below] {$-\frac13$};
-		\draw (-1/4,0) -- (-1/4,-0.05) node[below] {$-\frac14$};
+		\draw (-1/3,0) -- (-1/3,-0.05) node[left=9,below] {$-\frac13$};
+		\draw (-1/4,0) -- (-1/4,-0.05) node[right=3,below] {$-\frac14$};
 		\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
@@
 
-With such a strong notion of the pricing Nash equilibrium, we can now see a potential algorithm that can be used to query its existence or not as well as calculate it.
-We present it in Algorithm \ref{algorithm:step_ne_pricing}.
+The above provides a strong notion for the pricing Nash equilibrium, as it directly connects it to an equivalent one from a pseudo-heterogeneous game, leaving only the existence condition unexamined.
+From definition, a set of tolls $t^*$ is a pricing Nash equilibrium if and only if $\forall i \in N$ and $\forall t_i^\prime \in \R_+$ it holds that
+\[\Pi_i(t_i, t_{-i}) \geq \Pi_i(t_i^\prime, t_{-i})\]
+leading us to focus on profit for different sensitivity splits.
+Unsurprisingly, there is a heavy dependence on the definition of the distribution function, which we illustrate in the following examples.
+
+\begin{example}
+	\label{example:a_step_profit_ne}
+	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
+	\begin{align*}
+		\alpha(p) =
+		\begin{cases}
+			3 & p \le \tfrac14 \\
+			4 & p > \tfrac14
+		\end{cases}&
+	\end{align*}
+	Then $\Gm$ has a Nash Equilibrium for the pricing game at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+\end{example}
+
+\begin{proof}
+	First we verify that $t^* = \left(\tfrac59, \tfrac49\right)$ is indeed a valid candidate pricing Nash equilibrium.
+	Theorem \ref{theorem:a_step_ne_equiv_fixed} requires $t^*$ to also be a Nash Equilibrium at the pricing game of $\Gm^c = ([2], \ell, c)$, a pseudo-heterogeneous game where $c = 2$ or $3$.
+	Since Lemma \ref{lemma:a_fixed_pricing_ne_relation} suggests that the flow at that equilibrium will be the same regardless of the value of $c$, we calculate the one from the homogeneous game $G^{\prime} = ([2], \ell, 1)$.
+	We can calculate the latter equilibrium $t^{*\prime}$ by solving the system of equations with \ref{eq:homogeneous_x_i} and \ref{eq:homogeneous_pricing_ne_i}, from which we get $t^{*\prime} = \left(\tfrac53, \tfrac43\right)$ with $x^\prime(t^{*\prime}) = \left(\tfrac59, \tfrac49\right)$.
+	Such a flow split puts the flow of link $1$ in the upper split and link $2$ in the lower split, making $\as(t^*) = \alpha(x_1(t^{*\prime})) = \alpha(5/9) = 4$.
+	Lemma \ref{lemma:a_fixed_pricing_ne_relation} then gives us
+	\[
+		t^* = \frac13 t^{*\prime} = \left(\frac{5}{12}, \frac{4}{12}\right) \qquad x(t^*) = x^\prime(t^{*\prime}) = \left(\frac59, \frac49\right)
+	\]
+	We're only left to check whether $t^*$ satisfies the definition of a Nash Equilibrium, i.e. whether each link operator has a max profit toll in response to the opposing one.
+	We will therefore need to calculate the profit functions for each link, for which, thanks to \ref{lemma:heterogenous_flow_equiv_fixed}$(ii)$, we can use the respective pseudo-heterogeneous profit functions for each $c = 2, 3$.
+	We can then take the profit definition, formula \ref{eq:homogeneous_x_i} for $2$ links as well as Lemma \ref{lemma:a_fixed_c_relation}$(ii)$ and get for $\Gm^c$
+	\[
+		\Pi_1^c(t_1, t_2^*) = t_1 \cdot \frac{2 + c (4/3 - t_1)}{3}
+		\qquad
+		\Pi_2^c(t_1^*, t_2) = t_2 \cdot \frac{1 + c (5/3 - t_2)}{3}
+	\]
+	Next, we need to calculate the toll difference intervals for which $\as(t) = 2, 3$.
+	Similarly to Example \ref{example:a_step_simple}, for each link operator we fix the opposing toll $t_{-i}^*$ and consider all flow cases where all players of each sensitivity type are using a single link, i.e.
+$x = \left(\tfrac14, \tfrac34\right)$ and $\left(\tfrac34, \tfrac14\right)$, for all possible $\alpha$ values, i.e.
+$2$ and $3$.
+	We ignore the cases $x = (1, 0), (0, 1)$ as they minimise profit for both link operators.
+	For toll differences where $\as(t) = c$, then profit is equal to $\Pi_i^c(t)$ (Lemma \ref{lemma:heterogenous_flow_equiv_fixed}).
+	Otherwise, the flow remains static, making $x_i t_i$ a strictly increasing linear function with regards to $t_i$.
+
+	We visualise the results of our analysis in Figure \ref{figure:alpha_step:profit_ne}, where we can see that $B_i(t_{-i}^*) = t_i^*$ for both link operators, making $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$ a Nash Equilibrium for the pricing game in $\Gm$.
+\end{proof}
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[x=10cm, y=17cm, every node/.style={font=\small}]
+		% Axes
+		\draw[->] (0,0) -- (-0.4,0);
+		\draw[->] (0,0) -- (0.7,0) node[right] {$t_1 - t_2$};
+		\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};
+
+		% Tick marks
+		\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
+		\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
+		\draw (-1/12,0) -- (-1/12,-0.01) node[left=9,below] {$-\frac{1}{12}$};
+		\draw (-1/16,0) -- (-1/16,-0.01) node[right=2,below] {$-\frac{1}{16}$};
+		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=15] {$t_2^* = \frac{4}{12}$};
+		\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
+		\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
+		\draw (5/12,0) -- (5/12,-0.01) node[below] {$\frac{5}{12}$};
+		\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
+		\draw (2/3,0) -- (2/3,-0.01) node[below] {$\frac23$};
+		%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
+		%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};
+
+		% Pseudo-heterogeneous profits
+		\draw[gray,dashed,very thin,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[above=20,right=-5,black] {$c = 3$};
+		\draw[gray,dashed,very thin,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=15,right,black] {$c = 4$};
+
+		% Profit function
+		\draw[thick,domain=-1/3:-1/12] plot (\x,{((2-3*\x)/3)*(4/12+\x)});
+		\draw[thick] (-1/12,3/16) -- (-1/16, 39/192);
+		\fill[black] (-1/12,3/16) ellipse (0.0051 and 0.003) node[below right] {$\frac{3}{16}$};
+		\fill[black] (-1/16,39/192) ellipse (0.0051 and 0.003) node[above left] {$\frac{39}{192}$};
+		\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
+		\draw[thick] (5/16,31/192) -- (5/12,3/16);
+		\fill[black] (5/16,31/192) ellipse (0.0051 and 0.003) node[below left] {$\frac{31}{192}$};
+		\fill[black] (5/12,3/16) ellipse (0.0051 and 0.003) node[above right] {$\frac{3}{16}$};
+		\draw[thick,domain=5/12:2/3] plot (\x,{((2-3*\x)/3)*(4/12+\x)});
+
+		% Max point
+		\fill[red] (1/12, 25/108) ellipse (0.0068 and 0.004) node[below,black] {$\frac{25}{108}$};
+	\end{tikzpicture}
+	\begin{tikzpicture}[x=10cm, y=20cm, every node/.style={font=\small}]
+		% Axes
+		\draw[->] (0,0) -- (-0.55,0);
+		\draw[->] (0,0) -- (0.4,0) node[right] {$t_2 - t_1$};
+		\draw[->] (0,0) -- (0,0.2) node[above] {$\Pi_2(t)$};
+
+		% Tick marks
+		%\draw (-2/3,0) -- (-2/3,-0.01) node[below] {$-\frac23$};
+		\draw (-2/4,0) -- (-2/4,-0.01) node[below] {$-\frac24$};
+		\draw (-5/12,0) -- (-5/12,-0.01) node[below] {$-\frac{5}{12}$};
+		\draw (-5/16,0) -- (-5/16,-0.01) node[below] {$-\frac{5}{16}$};
+		\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
+		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=15] {$t_1^* = \frac{5}{12}$};
+		\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
+		\draw (1/12,0) -- (1/12,-0.01) node[right=3,below] {$\frac{1}{12}$};
+		\draw (1/4,0) -- (1/4,-0.01) node[below] {$\frac14$};
+		\draw (1/3,0) -- (1/3,-0.01) node[below] {$\frac13$};
+		%\draw (0,5/36) -- (-0.02,5/36) node[below=7,left] {$\frac{5}{36}$};
+
+		% Pseudo-heterogeneous profits
+		\draw[gray,dashed,very thin,domain=-5/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)}) node[above=20,right=-5,black] {$c = 3$};
+		\draw[gray,dashed,very thin,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,left=17,black] {$c = 4$};
+
+		% Profit function
+		\draw[thick] (-5/12,0) -- (-5/16,5/64);
+		\fill[black] (-5/12,0) ellipse (0.005 and 0.0025) node[above left] {$0$};
+		\fill[black] (-5/16,5/64) ellipse (0.005 and 0.0025) node[above left] {$\frac{5}{64}$};
+		\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
+		\draw[thick] (1/16,23/192) -- (1/12,1/8);
+		\fill[black] (1/16,23/192) ellipse (0.005 and 0.0025) node[below left] {$\frac{23}{192}$};
+		\fill[black] (1/12,1/8) ellipse (0.005 and 0.0025) node[above right] {$\frac18$};
+		\draw[thick,domain=1/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)});
+
+		% Max point
+		\fill[red] (-1/12, 4/27) ellipse (0.008 and 0.004) node[above,black] {$\frac{4}{27}$};
+	\end{tikzpicture}
+	\caption{Profit functions for link operators $1$ and $2$ of Example \ref{example:a_step_profit_ne}.\\Max profit for both at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.}
+	\label{figure:alpha_step:profit_ne}
+\end{figure}
+
+\begin{example}
+	\label{example:a_step_profit_no_ne}
+	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
+	\begin{align*}
+		\alpha(p) =
+		\begin{cases}
+			2 & p \le \tfrac14 \\
+			4 & p > \tfrac14
+		\end{cases}&
+	\end{align*}
+	Then $\Gm$ has no Nash Equilibrium for the pricing game.
+\end{example}
+
+\begin{proof}
+	Similarly to Example \ref{example:a_step_profit_ne}, we have from Theorem \ref{theorem:a_step_ne_equiv_fixed} that $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$ is the only candidate pricing Nash Equilibrium.
+	We calculate again the profit functions giving us Figure \ref{figure:alpha_step:profit_no_ne}, where we can see that
+	\[
+		B_1\left(\frac{4}{12}\right) = \frac58 \ne \frac{5}{12} \qquad B_2\left(\frac{5}{12}\right) = \frac{4}{12}
+	\]
+	Since $t^*$ is the only possible candidate (Theorem \ref{theorem:a_step_ne_equiv_fixed}), then $\Gm$ has no Nash equilibrium for its pricing game.
+\end{proof}
+
+\begin{figure}
+	\centering
+	\begin{tikzpicture}[x=6cm, y=17cm, every node/.style={font=\small}]
+		% Axes
+		\draw[->] (0,0) -- (-0.4,0);
+		\draw[->] (0,0) -- (1.1,0) node[right] {$t_1 - t_2$};
+		\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};
+
+		% Tick marks
+		\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
+		\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
+		\draw (-1/8,0) -- (-1/8,-0.01) node[left=5,below] {$-\frac18$};
+		\draw (-1/16,0) -- (-1/16,-0.01) node[below] {$-\frac{1}{16}$};
+		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=15] {$t_2^* = \frac{4}{12}$};
+		\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
+		\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
+		\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
+		\draw (5/8,0) -- (5/8,-0.01) node[below] {$\frac58$};
+		\draw (1,0) -- (1,-0.01) node[below] {$1$};
+		%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
+		%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};
+
+		% Pseudo-heterogeneous profits
+		\draw[gray,dashed,very thin,domain=-1/3:2/2] plot (\x,{((2-2*\x)/3)*(1/3+\x)}) node[above=20,right=-5,black] {$c = 2$};
+		\draw[gray,dashed,very thin,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=15,right,black] {$c = 4$};
+
+		% Profit function
+		\draw[thick,domain=-1/3:-1/8] plot (\x,{((2-2*\x)/3)*(4/12+\x)});
+		\draw[thick] (-1/8, 5/32) -- (-1/16, 39/192);
+		\fill[black] (-1/8, 5/32) ellipse (0.0085 and 0.003) node[below right] {$\frac{5}{32}$};
+		\fill[black] (-1/16,39/192) ellipse (0.0085 and 0.003) node[above left] {$\frac{39}{192}$};
+		\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
+		\draw[thick] (5/16,31/192) -- (5/8,23/96);
+		\fill[black] (5/16,31/192) ellipse (0.0085 and 0.003) node[below left] {$\frac{31}{192}$};
+		\fill[black] (5/8,23/96) ellipse (0.0085 and 0.003) node[above right] {$\frac{23}{96}$};
+		\draw[thick,domain=5/8:1] plot (\x,{((2-2*\x)/3)*(4/12+\x)});
+
+		% Max point
+		\fill[red] (1/12, 25/108) ellipse (0.0085 and 0.003) node[below,black] {$\frac{25}{108}$};
+	\end{tikzpicture}
+	\begin{tikzpicture}[x=10cm, y=20cm, every node/.style={font=\small}]
+		% Axes
+		\draw[->] (0,0) -- (-0.55,0);
+		\draw[->] (0,0) -- (0.6,0) node[right] {$t_2 - t_1$};
+		\draw[->] (0,0) -- (0,0.2) node[above] {$\Pi_2(t)$};
+
+		% Tick marks
+		%\draw (-2/3,0) -- (-2/3,-0.01) node[below] {$-\frac23$};
+		\draw (-2/4,0) -- (-2/4,-0.01) node[below] {$-\frac24$};
+		\draw (-5/12,0) -- (-5/12,-0.01) node[below] {$-\frac{5}{12}$};
+		\draw (-5/16,0) -- (-5/16,-0.01) node[below] {$-\frac{5}{16}$};
+		\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
+		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=15] {$t_1^* = \frac{5}{12}$};
+		\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
+		\draw (1/12,0) -- (1/12,-0.01) node[right=3,below] {$\frac{1}{12}$};
+		\draw (1/4,0) -- (1/4,-0.01) node[below] {$\frac14$};
+		\draw (1/3,0) -- (1/3,-0.01) node[below] {$\frac13$};
+		%\draw (0,5/36) -- (-0.02,5/36) node[below=7,left] {$\frac{5}{36}$};
+
+		% Pseudo-heterogeneous profits
+		\draw[gray,dashed,very thin,domain=-5/12:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)}) node[above=20,right=-5,black] {$c = 2$};
+		\draw[gray,dashed,very thin,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,left=17,black] {$c = 4$};
+
+		% Profit function
+		\draw[thick] (-5/12,0) -- (-5/16,5/64);
+		\fill[black] (-5/16,5/64) ellipse (0.005 and 0.0025) node[above left] {$\frac{5}{64}$};
+		\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
+		\draw[thick] (1/16,23/192) -- (1/8,13/96);
+		\fill[black] (1/16,23/192) ellipse (0.005 and 0.0025) node[below left] {$\frac{23}{192}$};
+		\fill[black] (1/8,13/96) ellipse (0.005 and 0.0025) node[above right] {$\frac{13}{96}$};
+		\draw[thick,domain=1/8:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)});
+
+		% Max point
+		\fill[red] (-1/12, 4/27) ellipse (0.008 and 0.004) node[above,black] {$\frac{4}{27}$};
+	\end{tikzpicture}
+	\caption{Profit functions for link operators $1$ and $2$ of Example \ref{example:a_step_profit_no_ne}.}
+	\label{figure:alpha_step:profit_no_ne}
+\end{figure}
+
+It seems apparent, from the previous two examples, that the success of a candidate pricing Nash equilibrium to extend for a step function is heavily dependent on the function's definition, i.e.
+the sensitivity values as well as the amount of flow corresponding to them.
+It would be tempting, at this point, to try and calculate exact conditions for the existence of such a Nash Equilibrium, given arbitrary game parameters.
+For example, assume the pricing game in Example \ref{example:a_step_profit_ne} has the distribution function
+\[
+	\alpha(p) =
+	\begin{cases}
+		c & p \le p_0 \\
+		4 & p > p_0
+	\end{cases}
+\]
+for $c < 4$ and $p_0 < 5/9$, with the last condition ensuring the sensitivity split for the equilibrium remains at $\as(t^*) = 4$.
+Looking at Example \ref{example:a_step_profit_no_ne}, we can see that for $c = 2$ the Nash Equilibrium breaks due to link operator $1$ getting higher profit at flow $p_0$.
+We can therefore assume that, for their equilibrium profit $\Pi_1(t^*) = \tfrac{25}{108}$ to remain maximum, it needs to be greater than the profit at flow $p_0$ for sensitivity $c$.
+We can then calculate $t_1$ such that $x(t_1, t_2^*) = p_0$, by solving the cost equality for $x = (p_0, 1 - p_0)$ and sensitivity $c$, and eventually get that link operator $1$ will not diverge from the equilibrium if
+\[
+	\frac{25}{108} \ge \frac{-3p_0^2 + p_0 (2 + c/3)}{c}
+\]
+Such a constrain can definitely provide insights into the numerical restrains between $c$ and $p_0$, however, as it also requires additional conditions to ensure the equilibrium won't still break due to higher profit at a different point, it suggests that a further analysis requires a more careful approach.
+As, admittedly based on our own capacity, will not proceed with such an analysis.
+We can still observe the following
+\begin{itemize}
+	\item larger differences in $\alpha_k$ values are more likely to break a pricing Nash Equilibrium
+	\item larger flow intervals around $\as(t^*)$ are more likely to have a pricing Nash Equilibrium (the game becomes more homogeneous)
+\end{itemize}
+
+Focusing now on the algorithmic aspect of existence, we see that things are much simpler.
+Looking at the profits of each pseudo-heterogeneous game overall, a sub-interval will either be monotonous or contain the global maximum, therefore the interval maximum will either be the profit on one of its edges or on the global best response in the pseudo-heterogeneous game.
+Using that property, along with everything from above, we can define now an algorithm that can be used to query the existence or not of a pricing Nash Equilibrium, as well as calculate it if so.
+We start with a short summary of the algorithm below, followed by a theorem to prove its validity.
+
+\paragraph{Summary of Algorithm \ref{algorithm:step_ne_pricing}}
+For a given heterogeneous pricing game $\Gm = ([2], \ell, \alpha)$
+\begin{enumerate}
+	\item Consider $\Gm^\prime = ([2], \ell, 1)$ and calculate its pricing Nash equilibrium $t^{*\prime}$ and respective flow $x^\prime(t^{*\prime})$.
+	\item Calculate $\as(t^*)$ as the $\alpha$ value of the lower split flow in $x^\prime(t^{*\prime})$ (valid since $x(t^*) = x^\prime(t^{*\prime})$ from Theorem \ref{theorem:a_step_ne_equiv_fixed}, Lemma \ref{lemma:a_fixed_pricing_ne_relation})
+	\item Calculate candidate pricing Nash Equilibrium at $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$ and respective profits $\Pi_1(t^*), \Pi_2(t^*)$.
+	\item For each $\alpha_k$, value of $\alpha$ different than $\as(t^*)$ and for each link operator $i \in [2]$
+	\begin{enumerate}[$4.1$]
+		\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i})$ as well as the tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
+		\begin{enumerate}[$4.1.1$]
+			\item If $B_{i, k}(t_{-i})$ is within the above ranges, then $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}), t_{-i})$.
+			\item Otherwise, $\Pi_{i, k}$ is the max of the profits for tolls in the edges of the above ranges.
+		\end{enumerate}
+		\item If $\Pi_i < \Pi_{i, k}$, then $\Gm$ has no pricing Nash Equilibrium.
+	\end{enumerate}
+	\item If none of the above checks fail, return $t^*$ as the Nash Equilibrium for the pricing game in $\Gm$.
+\end{enumerate}
 
@@
 	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous game with latency functions $\ell = (\ell_1(x), \ell_2(x))_{i \in [2]} = (a_ix + b_i)_{i \in [2]}$ and $\alpha$ a step distribution function with values $(\alpha_k)_{k \in [m]}$.
-	Then Algorithm \ref{algorithm:step_ne_pricing} with input $(\ell, \alpha)$ calculates the Nash Equilibrium for the pricing game in $\Gm$ in $\mathcal{O}(m)$ time.
+	Then Algorithm \ref{algorithm:step_ne_pricing} with input $(\ell, \alpha)$ decides existence and calculates the Nash Equilibrium for the pricing game in $\Gm$ in $\mathcal{O}(m)$ time.
 \end{theorem}

### 2025-01-08 thesis/article.tex
Thesis: Final fixes in Abstract, Introduction and Chapter 4
Release v1.0

@@
 Then, arriving at the main body of this study, we investigate the existence of a Nash Equilibrium in the profit game between the link operators for different cases of heterogeneous users.
-We show there is no Nash Equilibrium when there are many users with $0$ sensitivity, i.e. players not affected by tolls, so we further assume $\alpha(p) > 0$.
-We then investigate cases of fixed distribution functions, which, even though create homogeneous behaviour for the users (making them pseudo-heterogeneous games), help us describe how flow, tolls and equilibria behave as that fixed value changes.
-Using all the above, we study step distribution functions, where by limiting our scope to $2$ links, we present strict conditions necessary for the existence or not of a Nash Equilibrium in the profit game between the link operators.
-We present and analyse an algorithm to calculate that equilibrium, if it exists, and finish with some discussion about potential future work.
+We show there is no Nash Equilibrium when there are many users with $0$ sensitivity, i.e. players not affected by tolls, forcing us to assume onward $\alpha(p) > 0$.
+We then investigate cases of fixed distribution functions, which create homogeneous behaviours for the users (making them pseudo-heterogeneous games), through which we then describe how flow, tolls and equilibria behave as that fixed value changes.
+Using all the above, we study step distribution functions, where, by limiting our scope to $2$ links, we prove a strong requirement for the value of a potential Nash Equilibrium in the profit game between the link operators, connecting it to the equilibrium of an equivalent pseudo-heterogeneous game.
+We finally present and analyse an algorithm that calculates that equilibrium, if it exists, in time linear with regard to the step function's cardinality, and we finish with some discussion about potential future work.
 \clearpage
@@
 Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομογενών παιγνίων κέρδους, κυρίως βασισμένα σε προηγούμενες δουλειές, και με αυτά ως βάση, τα επεκτείνουμε για να περιγράψουμε παίγνια κέρδους με ετερογενείς χρήστες.
-Εισαγάγουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού ευαισθησίας $\as(t)$, ορισμένη για οποιεσδήποτε $2$ ακμές του δικτύου ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία, δωσμένων σετ διοδίων $t$, τα κόστη των $2$ ακμών είναι ίσα.
+Εισαγά-γουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού ευαισθησίας $\as(t)$, ορισμένη για ο-ποιεσδήποτε $2$ ακμές του δικτύου ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία, δωσμένων σετ διοδίων $t$, τα κόστη των $2$ ακμών είναι ίσα.
 Με τη βοήθεια της $\as$ θα περιγράψουμε μερικές ιδιότητες γύρω από την εγωιστική συμπεριφορά των ετερογενών χρηστών για διαφορετικά διόδια, καθώς και θα αποδείξουμε την ύπαρξη άνω φράγματος για τις τιμές ευαισθησίας που αφορούν το παίγνιο.
-Στη συνέχεια, φτάνοντας στο κύριο σώμα αυτής της έρευνας, εξετάζουμε την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών για διαφορετικές περιπτώσεις ετερογενών χρηστών.
-Δείχνουμε ότι δεν υπάρχει ισορροπία Nash όταν υπάρχουν πολλοί χρήστες με $0$ ευαισθησία, δηλ. παίκτες που δεν επηρρεάζονται από τα διόδια, οπότε στο εξής υποθέτουμε ότι $\alpha(p) > 0$.
-Κατόπιν εξετάζουμε περιπτώσεις όπου η συνάρτηση κατανομής είναι σταθερή, η οποίες, αν και δημιουργούν ομογενή συμπεριφορά στους χρήστες (κάνοντάς τα ψευδο-ετερογενή παίγνια), μας βοηθάνε να περιγράψουμε πώς συμπεριφέρονται η ροή, τα διόδια και τα σημεία ισορροπίας όταν αυτή η σταθερή τιμή μεταβάλλεται.
-Χρησιμοποιώντας όλα τα παραπάνω, μελετάμε βηματικές συναρτήσεις κατανομής, όπου περιορίζοντας το μοντέλο μας σε στιγμιότυπα $2$ ακμών, παρουσιάζουμε αυστηρές συνθήκες αναγκαίες για την ύπαρξη ή μη σημείου ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών.
-Παρουσιάζουμε και αναλύουμε έναν αλγόριθμο για τον υπολογισμό του σημείου ισορροπίας, αν υπάρχει, και κλείνουμε με μια συζήτηση για πιθανή μελοντική δουλειά.
+Στη συνέχεια, φτάνοντας στο κύριο σώμα αυτής της έρευνας, εξετάζουμε την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών για διαφορετικές περι-πτώσεις ετερογενών χρηστών.
+Δείχνουμε ότι δεν υπάρχει ισορροπία Nash όταν υπάρχουν πολλοί χρήστες με $0$ ευαισθησία, δηλ.
+παίκτες που δεν επηρρεάζονται από τα διόδια, το οποίο μας αναγκάζει στο εξής να υποθέσουμε ότι $\alpha(p) > 0$.
+Κατόπιν, εξετάζουμε περιπτώσεις όπου η συνάρτηση κατανομής είναι σταθερή, η οποίες δημιουργούν ομογενή συμπεριφορά στους χρήστες (κάνοντάς τα ψευδο-ετερογενή παίγνια), μέσω των οποίων μετά θα περιγράψουμε πώς συμπεριφέρονται η ροή, τα διόδια και τα σημεία ισορροπίας όταν αυτή η σταθερή τιμή μεταβάλλεται.
+Χρησιμοποιώντας όλα τα παραπάνω, μελετάμε βηματικές συναρτήσεις κατανομής, όπου, περιορίζοντας το μοντέλο μας σε στιγμιότυπα $2$ ακμών, αποδεικνύουμε μια αυστηρή συνθήκη για την τιμή ενός πιθανού σημείου ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών, συνδέοντάς το με το σημείο ισορροπίας σε ένα ισοδύναμο ψευδο-ετερογενή παίγνιο.
+Εντέλει, παρουσιάζουμε και αναλύουμε έναν αλγόριθμο για τον υπολογισμό αυτού του σημείου ισορροπίας, αν υπάρχει, σε χρόνο γραμμικό σε σχέση με τον πληθάριθμο της βηματικής συνάρτησης, και κλείνουμε με μια συζήτηση για πιθανές μελλοντικές εργασίες.
 
@@
 The tolls impose an additional cost to the flow players, affecting the lower level game, and the link operators compete with each other to maximise their profit.
-In our case we will additionally assume that the flow users behave in a heterogeneous way when it comes to tolls, meaning that each player has a different time-money trade-off and thus see the link costs differently.
+In our case, we will additionally assume that the flow users behave in a heterogeneous way when it comes to tolls, meaning that each player has a different time-money trade-off and thus see the link costs differently.
 
@@
 
-Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money sensitivity split}, which captures the notion of a (potentially non-existent) player whose money sensitivity makes them view the two links as equal.
+Entering the main body of our work, in Chapter \ref{chapter:split} we introduce a new term regarding any two links of the network, called \textit{money sensitivity split}, which captures the notion of a (potentially non-existent) player whose money sensitivity makes them view the two link costs as equal.
 We will then analyse that notion and provide properties and bounds for its values.
@@
 We describe and prove some properties for them, and using those we then tackle step distribution functions (where the user sensitivity can take values out of a finite set).
-At this point we restrict our model to instances with $2$ links, and provide strict restrictions for equilibrium existence for the pricing competition game.
-
-We conclude this thesis with a short discussion around the main outtakes of this study, while also presenting potential directions for future work.
+At this point we restrict our model to instances with $2$ links, and prove a strong condition about the value of a potential Nash Equilibrium for the pricing game, connecting it to the respective equilibrium of an equivalent pseudo-heterogeneous game.
+We will discuss with examples the consequences of such a condition, and finally, we will present, analyse and prove the validity of an algorithm which can decide on the existence as well as calculate a Nash Equilibrium for the pricing game in $\mathcal{O}(m)$ time (with $m$ being the size of the step distribution function's finite set of values).
+
+We conclude this thesis with a short discussion around potential directions for future work.
 
@@
 One other difficulty we need to consider are cases where $t_i = t_j$ for some links $i, j \in N$.
-Remember that $x(t)$ is only uniquely defined with regards to costs, which in extension makes players in such links with equal cost (viewed as such by all players of the game) able to be put arbitrarily in any of the two, regardless of their $\alpha$ value.
+Remember that $x(t)$ is only uniquely defined with regard to costs, which in extension makes players in such links with equal cost (viewed as such by all players of the game) able to be put arbitrarily in any of the two, regardless of their $\alpha$ value.
 Even if we attempted to assume a link assignment ordered by $\alpha$, the link order also matters, as the (equal latency) links might have different flow volume, resulting in different $\alpha$ values in the flow that uses each.
@@
 
-All the above lemmas can now help us describe the behaviour of $\as$ for different tolls, and more specifically how it behaves with regards to $t_i$ for a fixed $t_{-i}$.
+All the above lemmas can now help us describe the behaviour of $\as$ for different tolls, and more specifically how it behaves with regard to $t_i$ for a fixed $t_{-i}$.
 The main challenge in this analysis is that a changing $t_i$ can affect the sensitivity split of multiple link pairs, while even the link ordering is not always fixed, as we can put link $i$ at any place by selecting an appropriate $t_i$.
@@
 
-In this chapter we will introduce the pricing competition game to our model and examine how different distribution functions can affect the profit maximisation game between the toll operators.
+In this chapter we will introduce the pricing competition game to our model and examine how different distribution functions can affect the profit maximisation game between the link operators.
 We will begin by noticing that players with no toll fear, i.e. $\alpha(p)$ close to $0$, can be exploited by some link operators who then get unbounded profits (Lemma \ref{lemma:a_0_0}).
@@
 The tools and notions built above will prove extremely useful when we next analyse games with step distribution functions, where we'll restrict our analysis to instances with $2$ links to simplify our work.
-For those we will show an equivalence with a homogeneous game for a given toll \ref{lemma:heterogenous_flow_equiv_fixed} and combining it with Lemma \ref{lemma:alpha_step_gaps} where we'll show that a Nash Equilibrium cannot exist with all players of each sensitivity type using a single link, we get this chapter's main result, Theorem \ref{theorem:a_step_ne_equiv_fixed}, which states that if a Nash Equilibrium exists in a heterogeneous game with a step distribution function, then the respective homogeneous also has an equilibrium for the same set of tolls.
-Using this notion, we will describe an algorithm (\ref{algorithm:step_ne_pricing}) which can decide existence and return the Nash Equilibrium for the pricing competition game in a heterogeneous $2$-link network.
+We will show that $2$-link games, for a fixed set of tolls, are equivalent to a specific pseudo-heterogeneous game  (Lemma \ref{lemma:heterogenous_flow_equiv_fixed}) and combining this property with Lemma \ref{lemma:alpha_step_gaps}, where we'll show that a Nash Equilibrium cannot exist with all players of each sensitivity type using a single link, we get this chapter's main result, Theorem \ref{theorem:a_step_ne_equiv_fixed}, which states that if a Nash Equilibrium exists in a heterogeneous game with a step distribution function, then a respective pseudo-heterogeneous game also has an equilibrium for the same set of tolls.
+Using this notion, we will describe an algorithm (\ref{algorithm:step_ne_pricing}) which can decide existence and return the Nash Equilibrium for a $2$-link pricing competition game in $\mathcal{O}(m)$ time.
 
@@
 	It follows that any flow movement from $x^{(2)}(t)$ will again put players in links with larger link costs, making $x^{(2)}(t)$ a Nash Equilibrium for $t$ in $\Gm_1$ as well.
-	Uniqueness of the equilibrium with regards to costs finally gives us $x^{(1)}(t) = x^{(2)}(t)$.
+	Uniqueness of the equilibrium with regard to costs finally gives us $x^{(1)}(t) = x^{(2)}(t)$.
 	Since the above hold for all $t \in \R_+^{|N|}$, we conclude from Definition \ref{definition:game_equivalence} that $\Gm_1, \Gm_2$ are equivalent.
@@
 \begin{proof}
-	First we verify that $t^* = \left(\tfrac59, \tfrac49\right)$ is indeed a valid candidate pricing Nash equilibrium.
-	Theorem \ref{theorem:a_step_ne_equiv_fixed} requires $t^*$ to also be a Nash Equilibrium at the pricing game of $\Gm^c = ([2], \ell, c)$, a pseudo-heterogeneous game where $c = 2$ or $3$.
+	First we verify that $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$ is indeed a valid candidate pricing Nash equilibrium.
+	Theorem \ref{theorem:a_step_ne_equiv_fixed} requires $t^*$ to also be a Nash Equilibrium at the pricing game of $\Gm_c = ([2], \ell, c)$, a pseudo-heterogeneous game where $c = 2$ or $3$.
 	Since Lemma \ref{lemma:a_fixed_pricing_ne_relation} suggests that the flow at that equilibrium will be the same regardless of the value of $c$, we calculate the one from the homogeneous game $G^{\prime} = ([2], \ell, 1)$.
 	We can calculate the latter equilibrium $t^{*\prime}$ by solving the system of equations with \ref{eq:homogeneous_x_i} and \ref{eq:homogeneous_pricing_ne_i}, from which we get $t^{*\prime} = \left(\tfrac53, \tfrac43\right)$ with $x^\prime(t^{*\prime}) = \left(\tfrac59, \tfrac49\right)$.
-	Such a flow split puts the flow of link $1$ in the upper split and link $2$ in the lower split, making $\as(t^*) = \alpha(x_1(t^{*\prime})) = \alpha(5/9) = 4$.
+	Such a flow split puts the flow of link $1$ in the lower split and link $2$ in the upper split, making $\as(t^*) = \alpha(x_1(t^{*\prime})) = \alpha(5/9) = 4$.
 	Lemma \ref{lemma:a_fixed_pricing_ne_relation} then gives us
@@
 	We will therefore need to calculate the profit functions for each link, for which, thanks to \ref{lemma:heterogenous_flow_equiv_fixed}$(ii)$, we can use the respective pseudo-heterogeneous profit functions for each $c = 2, 3$.
-	We can then take the profit definition, formula \ref{eq:homogeneous_x_i} for $2$ links as well as Lemma \ref{lemma:a_fixed_c_relation}$(ii)$ and get for $\Gm^c$
-	\[
-		\Pi_1^c(t_1, t_2^*) = t_1 \cdot \frac{2 + c (4/3 - t_1)}{3}
+	We can then take the profit definition, formula \ref{eq:homogeneous_x_i} for $2$ links as well as Lemma \ref{lemma:a_fixed_c_relation}$(ii)$ and get for $\Gm_c$
+	\[
+		\Pi_{1, c}(t_1, t_2^*) = t_1 \cdot \frac{2 + c (4/3 - t_1)}{3}
 		\qquad
-		\Pi_2^c(t_1^*, t_2) = t_2 \cdot \frac{1 + c (5/3 - t_2)}{3}
+		\Pi_{2, c}(t_1^*, t_2) = t_2 \cdot \frac{1 + c (5/3 - t_2)}{3}
 	\]
@@
 	We ignore the cases $x = (1, 0), (0, 1)$ as they minimise profit for both link operators.
-	For toll differences where $\as(t) = c$, then profit is equal to $\Pi_i^c(t)$ (Lemma \ref{lemma:heterogenous_flow_equiv_fixed}).
-	Otherwise, the flow remains static, making $x_i t_i$ a strictly increasing linear function with regards to $t_i$.
+	For toll differences where $\as(t) = c$, profit is equal to $\Pi_{i, c}(t)$ (Lemma \ref{lemma:heterogenous_flow_equiv_fixed}).
+	Otherwise, the flow remains static, making $x_i t_i$ a linear function with regard to $t_i$, with slope $x_i > 0$.
 
@@
 	\centering
-	\begin{tikzpicture}[x=10cm, y=17cm, every node/.style={font=\small}]
+	\begin{tikzpicture}[x=8cm, y=10cm, every node/.style={font=\small}]
 		% Axes
@@
 		\draw (-1/16,0) -- (-1/16,-0.01) node[right=2,below] {$-\frac{1}{16}$};
-		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=15] {$t_2^* = \frac{4}{12}$};
+		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
 		\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
@@
 		% Pseudo-heterogeneous profits
-		\draw[gray,dashed,very thin,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[above=20,right=-5,black] {$c = 3$};
-		\draw[gray,dashed,very thin,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=15,right,black] {$c = 4$};
+		\draw[gray,dashed,thick,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[above=17,right=-7,black] {$c = 3$};
+		\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=10,right=-3,black] {$c = 4$};
 
@@
 		\draw[thick] (-1/12,3/16) -- (-1/16, 39/192);
-		\fill[black] (-1/12,3/16) ellipse (0.0051 and 0.003) node[below right] {$\frac{3}{16}$};
-		\fill[black] (-1/16,39/192) ellipse (0.0051 and 0.003) node[above left] {$\frac{39}{192}$};
+		\fill[black] (-1/12,3/16) ellipse (0.00625 and 0.005) node[below right] {$\frac{3}{16}$};
+		\fill[black] (-1/16,39/192) ellipse (0.00625 and 0.005) node[above left] {$\frac{39}{192}$};
 		\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
 		\draw[thick] (5/16,31/192) -- (5/12,3/16);
-		\fill[black] (5/16,31/192) ellipse (0.0051 and 0.003) node[below left] {$\frac{31}{192}$};
-		\fill[black] (5/12,3/16) ellipse (0.0051 and 0.003) node[above right] {$\frac{3}{16}$};
+		\fill[black] (5/16,31/192) ellipse (0.00625 and 0.005) node[below left] {$\frac{31}{192}$};
+		\fill[black] (5/12,3/16) ellipse (0.00625 and 0.005) node[above right] {$\frac{3}{16}$};
 		\draw[thick,domain=5/12:2/3] plot (\x,{((2-3*\x)/3)*(4/12+\x)});
@@
 		% Max point
-		\fill[red] (1/12, 25/108) ellipse (0.0068 and 0.004) node[below,black] {$\frac{25}{108}$};
+		\fill[red] (1/12, 25/108) ellipse (0.00625 and 0.005) node[below,black] {$\frac{25}{108}$};
 	\end{tikzpicture}
-	\begin{tikzpicture}[x=10cm, y=20cm, every node/.style={font=\small}]
+	\\[15pt]
+	\begin{tikzpicture}[x=10cm, y=15cm, every node/.style={font=\small}]
 		% Axes
@@
 		\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
-		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=15] {$t_1^* = \frac{5}{12}$};
+		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_1^* = \frac{5}{12}$};
 		\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
@@
 		% Pseudo-heterogeneous profits
-		\draw[gray,dashed,very thin,domain=-5/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)}) node[above=20,right=-5,black] {$c = 3$};
-		\draw[gray,dashed,very thin,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,left=17,black] {$c = 4$};
+		\draw[gray,dashed,thick,domain=-5/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)}) node[above=15,right=-7,black] {$c = 3$};
+		\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,left=17,black] {$c = 4$};
 
@@
 		\draw[thick] (-5/12,0) -- (-5/16,5/64);
-		\fill[black] (-5/12,0) ellipse (0.005 and 0.0025) node[above left] {$0$};
-		\fill[black] (-5/16,5/64) ellipse (0.005 and 0.0025) node[above left] {$\frac{5}{64}$};
+		\fill[black] (-5/12,0) ellipse (0.0045 and 0.003) node[above left] {$0$};
+		\fill[black] (-5/16,5/64) ellipse (0.0045 and 0.003) node[above left] {$\frac{5}{64}$};
 		\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
 		\draw[thick] (1/16,23/192) -- (1/12,1/8);
-		\fill[black] (1/16,23/192) ellipse (0.005 and 0.0025) node[below left] {$\frac{23}{192}$};
-		\fill[black] (1/12,1/8) ellipse (0.005 and 0.0025) node[above right] {$\frac18$};
+		\fill[black] (1/16,23/192) ellipse (0.0045 and 0.003) node[below left] {$\frac{23}{192}$};
+		\fill[black] (1/12,1/8) ellipse (0.0045 and 0.003) node[above right] {$\frac18$};
 		\draw[thick,domain=1/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)});
@@
 		% Max point
-		\fill[red] (-1/12, 4/27) ellipse (0.008 and 0.004) node[above,black] {$\frac{4}{27}$};
+		\fill[red] (-1/12, 4/27) ellipse (0.0045 and 0.003) node[above,black] {$\frac{4}{27}$};
 	\end{tikzpicture}
-	\caption{Profit functions for link operators $1$ and $2$ of Example \ref{example:a_step_profit_ne}.\\Max profit for both at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.}
+	\caption{Profit functions for link operators $1$ and $2$ of Example \ref{example:a_step_profit_ne} when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+Red dot indicates the max profit at $t^*$.
+Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
 	\label{figure:alpha_step:profit_ne}
@@
 	Similarly to Example \ref{example:a_step_profit_ne}, we have from Theorem \ref{theorem:a_step_ne_equiv_fixed} that $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$ is the only candidate pricing Nash Equilibrium.
-	We calculate again the profit functions giving us Figure \ref{figure:alpha_step:profit_no_ne}, where we can see that
+	We calculate again the profit functions, which we present in Figure \ref{figure:alpha_step:profit_no_ne}, and where we can see that
 	\[
@@
 	\]
-	Since $t^*$ is the only possible candidate (Theorem \ref{theorem:a_step_ne_equiv_fixed}), then $\Gm$ has no Nash equilibrium for its pricing game.
+	which makes $t^*$ ineligible for an equilibrium.
+	Since $t^*$ is the only possible candidate (Theorem \ref{theorem:a_step_ne_equiv_fixed}), it follows that $\Gm$ has no Nash equilibrium for its pricing game.
 \end{proof}
@@
 	\centering
-	\begin{tikzpicture}[x=6cm, y=17cm, every node/.style={font=\small}]
+	\begin{tikzpicture}[x=6cm, y=10cm, every node/.style={font=\small}]
 		% Axes
@@
 		\draw (-1/16,0) -- (-1/16,-0.01) node[below] {$-\frac{1}{16}$};
-		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=15] {$t_2^* = \frac{4}{12}$};
+		\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
 		\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
@@
 		% Pseudo-heterogeneous profits
-		\draw[gray,dashed,very thin,domain=-1/3:2/2] plot (\x,{((2-2*\x)/3)*(1/3+\x)}) node[above=20,right=-5,black] {$c = 2$};
-		\draw[gray,dashed,very thin,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=15,right,black] {$c = 4$};
+		\draw[gray,dashed,thick,domain=-1/3:2/2] plot (\x,{((2-2*\x)/3)*(1/3+\x)}) node[above=20,right=-5,black] {$c = 2$};
+		\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=15,right,black] {$c = 4$};
 
@@
 		\draw[thick] (-1/8, 5/32) -- (-1/16, 39/192);
-		\fill[black] (-1/8, 5/32) ellipse (0.0085 and 0.003) node[below right] {$\frac{5}{32}$};
-		\fill[black] (-1/16,39/192) ellipse (0.0085 and 0.003) node[above left] {$\frac{39}{192}$};
+		\fill[black] (-1/8, 5/32) ellipse (0.008333 and 0.005) node[below right] {$\frac{5}{32}$};
+		\fill[black] (-1/16,39/192) ellipse (0.008333 and 0.005) node[above left] {$\frac{39}{192}$};
 		\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
 		\draw[thick] (5/16,31/192) -- (5/8,23/96);
-		\fill[black] (5/16,31/192) ellipse (0.0085 and 0.003) node[below left] {$\frac{31}{192}$};
-		\fill[black] (5/8,23/96) ellipse (0.0085 and 0.003) node[above right] {$\frac{23}{96}$};
+		\fill[black] (5/16,31/192) ellipse (0.008333 and 0.005) node[below left] {$\frac{31}{192}$};
+		\fill[black] (5/8,23/96) ellipse (0.008333 and 0.005) node[above right] {$\frac{23}{96}$};
 		\draw[thick,domain=5/8:1] plot (\x,{((2-2*\x)/3)*(4/12+\x)});
@@
 		% Max point
-		\fill[red] (1/12, 25/108) ellipse (0.0085 and 0.003) node[below,black] {$\frac{25}{108}$};
+		\fill[red] (1/12, 25/108) ellipse (0.008333 and 0.005) node[below,black] {$\frac{25}{108}$};
 	\end{tikzpicture}
-	\begin{tikzpicture}[x=10cm, y=20cm, every node/.style={font=\small}]
+	\\[15pt]
+	\begin{tikzpicture}[x=8cm, y=15cm, every node/.style={font=\small}]
 		% Axes
@@
 		% Pseudo-heterogeneous profits
-		\draw[gray,dashed,very thin,domain=-5/12:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)}) node[above=20,right=-5,black] {$c = 2$};
-		\draw[gray,dashed,very thin,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,left=17,black] {$c = 4$};
+		\draw[gray,dashed,thick,domain=-5/12:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)}) node[above=20,right=-5,black] {$c = 2$};
+		\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,right,black] {$c = 4$};
 
@@
 		\draw[thick] (1/16,23/192) -- (1/8,13/96);
-		\fill[black] (1/16,23/192) ellipse (0.005 and 0.0025) node[below left] {$\frac{23}{192}$};
+		\fill[black] (1/16,23/192) ellipse (0.005 and 0.0025) node[left=6,below] {$\frac{23}{192}$};
 		\fill[black] (1/8,13/96) ellipse (0.005 and 0.0025) node[above right] {$\frac{13}{96}$};
@@
 	\end{tikzpicture}
-	\caption{Profit functions for link operators $1$ and $2$ of Example \ref{example:a_step_profit_no_ne}.}
+	\caption{Profit functions for link operators $1$ and $2$ of Example \ref{example:a_step_profit_no_ne} when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+Red dot indicates the max profit at $t^*$.
+Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
 	\label{figure:alpha_step:profit_no_ne}
@@
 
-It seems apparent, from the previous two examples, that the success of a candidate pricing Nash equilibrium to extend for a step function is heavily dependent on the function's definition, i.e.
+It seems apparent, from the previous two examples, that the criteria, for a candidate pricing Nash equilibrium to maintain its maximality among tolls at different $\alpha_k$ values, are heavily dependent on the function's definition, i.e.
 the sensitivity values as well as the amount of flow corresponding to them.
-It would be tempting, at this point, to try and calculate exact conditions for the existence of such a Nash Equilibrium, given arbitrary game parameters.
-For example, assume the pricing game in Example \ref{example:a_step_profit_ne} has the distribution function
+It would be tempting, at this point, to try and calculate exact conditions around the definition of $\alpha$ that would ensure existence of a Nash Equilibrium, given arbitrary game parameters.
+For example, assume we want to investigate Example \ref{example:a_step_profit_ne} by altering its distribution function to
 \[
@@
 \]
-for $c < 4$ and $p_0 < 5/9$, with the last condition ensuring the sensitivity split for the equilibrium remains at $\as(t^*) = 4$.
+for $c < 4$ and $p_0 < 5/9$, with the last condition ensuring the sensitivity split for the pricing equilibrium remains at $\as(t^*) = 4$.
 Looking at Example \ref{example:a_step_profit_no_ne}, we can see that for $c = 2$ the Nash Equilibrium breaks due to link operator $1$ getting higher profit at flow $p_0$.
 We can therefore assume that, for their equilibrium profit $\Pi_1(t^*) = \tfrac{25}{108}$ to remain maximum, it needs to be greater than the profit at flow $p_0$ for sensitivity $c$.
-We can then calculate $t_1$ such that $x(t_1, t_2^*) = p_0$, by solving the cost equality for $x = (p_0, 1 - p_0)$ and sensitivity $c$, and eventually get that link operator $1$ will not diverge from the equilibrium if
+By calculating $t_1$ such that $x(t_1, t_2^*) = p_0$, we can eventually get that link operator $1$ will not diverge from the equilibrium if
 \[
@@
 \]
-Such a constrain can definitely provide insights into the numerical restrains between $c$ and $p_0$, however, as it also requires additional conditions to ensure the equilibrium won't still break due to higher profit at a different point, it suggests that a further analysis requires a more careful approach.
-As, admittedly based on our own capacity, will not proceed with such an analysis.
-We can still observe the following
+Such a constrain can definitely e.g. provide insights into the numerical restrains between $c$ and $p_0$.
+In order to support the characterisation of the equilibrium existence, however, it requires to be considered alongside additional conditions to account for all other possibly higher profits (other sensitivity values, multiple global maximums, etc.).
+It therefore seems overall complex to tackle this task directly, and a smarter approach would be to first further develop our tools on pseudo-heterogeneous games, which is why we will leave such an analysis for future work.
+We discuss this again in Chapter \ref{chapter:future_work}.
+As a final note before leaving this topic, regarding the influence of the step distribution function on the equilibrium, we can still observe the following:
 \begin{itemize}
-	\item larger differences in $\alpha_k$ values are more likely to break a pricing Nash Equilibrium
-	\item larger flow intervals around $\as(t^*)$ are more likely to have a pricing Nash Equilibrium (the game becomes more homogeneous)
+	\item Larger differences between $\alpha_k$ values are more likely to result in no Nash Equilibrium for the pricing game.
+	\item Larger flow intervals around $\as(t^*)$ are more likely to result in having a Nash Equilibrium for the pricing game (the game becomes more homogeneous).
 \end{itemize}
@@
 	\item Calculate $\as(t^*)$ as the $\alpha$ value of the lower split flow in $x^\prime(t^{*\prime})$ (valid since $x(t^*) = x^\prime(t^{*\prime})$ from Theorem \ref{theorem:a_step_ne_equiv_fixed}, Lemma \ref{lemma:a_fixed_pricing_ne_relation})
-	\item Calculate candidate pricing Nash Equilibrium at $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$ and respective profits $\Pi_1(t^*), \Pi_2(t^*)$.
-	\item For each $\alpha_k$, value of $\alpha$ different than $\as(t^*)$ and for each link operator $i \in [2]$
+	\item Calculate the candidate pricing Nash Equilibrium $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$ as well as the respective profits $\Pi_1(t^*), \Pi_2(t^*)$.
+	\item For each $\alpha_k$, value of $\alpha$ different than $\as(t^*)$, and for each link operator $i \in [2]$
 	\begin{enumerate}[$4.1$]
-		\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i})$ as well as the tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
-		\begin{enumerate}[$4.1.1$]
-			\item If $B_{i, k}(t_{-i})$ is within the above ranges, then $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}), t_{-i})$.
-			\item Otherwise, $\Pi_{i, k}$ is the max of the profits for tolls in the edges of the above ranges.
+		\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i}^*)$ as well as the tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
+		\item Search for $\Pi_{i, k}$, the max profit for $i$ within those $t_i$ ranges:
+		\begin{enumerate}[$4.2.1$]
+			\item If $B_{i, k}(t_{-i}^*)$ is within the $t_i$ ranges, then $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}^*), t_{-i}^*)$.
+			\item Otherwise, $\Pi_{i, k}$ is the highest profit value among the ($4$) tolls in the edges of the two $t_1$ ranges.
 		\end{enumerate}
@@
 	\end{enumerate}
-	\item If none of the above checks fail, return $t^*$ as the Nash Equilibrium for the pricing game in $\Gm$.
+	\item If all of the above checks fail, then $t^*$ is the Nash Equilibrium for the pricing game in $\Gm$, so return it.
 \end{enumerate}
@@
 
-Algorithm \ref{algorithm:step_ne_pricing} calculates tolls which are a candidate Nash Equilibrium for the pricing game and then checks for all step function values that no profit earned in a different sensitivity split is higher than that.
-Given those restrictions, it seems very possible to calculate exact conditions for a candidate set of tolls to be a Nash Equilibrium.
-Those conditions would heavily depend on the definition of $\alpha$, making the player splits as well as the distance of the step function's $\alpha_k$ values appear to be the defining factors.
-Therefore another possible extension of this work would be to compute and study these exact conditions.
+In Chapter \ref{chapter:pricing_equilibria} we investigated the pricing Nash Equilibrium for step functions, and while Theorem \ref{theorem:a_step_ne_equiv_fixed} directly provides us with a candidate set of such tolls, the exact criteria deciding existence (mostly regarding the distribution function) can be elusive (see Examples \ref{example:a_step_profit_ne}, \ref{example:a_step_profit_no_ne} and the discussion thereafter).
+Even with the algorithmic approach being much simpler (shown in Algorithm \ref{algorithm:step_ne_pricing}), we believe there could still be value in investigating them.
+Apart from obviously discovering more patterns around maximising profit in arbitrary step functions, such criteria could also be utilised in order to identify classes of step distribution functions where existence is always (or never) ensured.
+Also note, that, as also mentioned in the relevant discussion in Chapter \ref{chapter:pricing_equilibria}, a potential progress in our understanding of pseudo-heterogeneous games can also support further analysis on the pricing Nash equilibrium criteria, and vice-versa.
 
@@
 $\alpha(p) = cp$, for some $c > 0$) to be of interest for further study.
+
+\section*{Function series approximation}
+
+The study of step distribution functions in this work opens up the opportunity to approach arbitrary functions analytically.
+By approximating a distribution function as a series of step functions where $m \rightarrow +\infty$, one could find the tools developed above useful for their analysis.
+For example, Algorithm \ref{algorithm:step_ne_pricing} could potentially approximate an equilibrium (or prove non-existence) by using as base a step function close enough to the original one.
+This should be viewed with skepticism, however, since equilibria in step functions all enforce the same flow, something not true for generic distribution functions, while large variation in the step function's values will make the algorithm, running in $\mathcal{O}(m)$ time, arbitrarily inefficient.
+Still, for properties that are maintained when approaching a function through step approximations, we believe that the use of the intuitions and tools built here do have the potential to support their analysis.
 
@@
 
-\phantomsection
-\addcontentsline{toc}{chapter}{Appendix}
 \chapter{Appendix}
@@
 	\]
-	which is decreasing with regards to $t_j$ if and only if its coefficient is negative.
+	which is decreasing with regard to $t_j$ if and only if its coefficient is negative.
 	Indeed, since $a_i > 0$ for all $i$, we get
@@
 
-which is in turn non-increasing with regards to $t_{-i}$ (\ref{lemma:tolls_diff}).
+which is in turn non-increasing with regard to $t_{-i}$ (\ref{lemma:tolls_diff}).
 Therefore, as $t_{-i}$ increases, the best response gets decreasing difference with $t_{-i}$, thus taking more flow in $x_i$.

### 2025-01-16 thesis/article.tex
Thesis: Final fixes from Th. Lianeas (greek Abstract, Future work) plus tikz fixes
Release v1.1

@@
 							\normalsize {\it {\bf Examination committee:}\\
-								Dimitris Fotakis, School of Electrical and Computer Engineering, National Technical University of Athens.\\
-								Professor's name, Department or School, Institution.\\
-								Professor's name, Department or School, Institution.}
+								Thanassis Lianeas,\\ School of Electrical and Computer Engineering, National Technical University of Athens.\\
+								Dimitris Fotakis,\\ School of Electrical and Computer Engineering, National Technical University of Athens.\\
+								Aris Pagourtzis,\\ School of Electrical and Computer Engineering, National Technical University of Athens.}
 						\end{flushleft}
@@
 							\normalsize {\it {\bf Supervisor:}\\
-								Dimitris Fotakis, Professor, \\ School of Electrical and Computer Engineering,\\
+								Thanassis Lianeas, Lecturer,\\School of Electrical and Computer Engineering,\\
 								National Technical University of Athens.\\
@@
 				\end{flushleft}
-				\vskip6cm
+				\vskip4cm
 				\hskip4.5cm
@@
 We show there is no Nash Equilibrium when there are many users with $0$ sensitivity, i.e. players not affected by tolls, forcing us to assume onward $\alpha(p) > 0$.
-We then investigate cases of fixed distribution functions, which create homogeneous behaviours for the users (making them pseudo-heterogeneous games), through which we then describe how flow, tolls and equilibria behave as that fixed value changes.
+We then investigate cases of fixed distribution functions, where the user behaviour remains homogeneous (making them pseudo-heterogeneous games), through which we then describe how flow, tolls and equilibria behave as that fixed value changes.
 Using all the above, we study step distribution functions, where, by limiting our scope to $2$ links, we prove a strong requirement for the value of a potential Nash Equilibrium in the profit game between the link operators, connecting it to the equilibrium of an equivalent pseudo-heterogeneous game.
@@
 Εξετάζουμε μόνο αφινικές καθυστερήσεις για τις ακμές.
-Επιπλέον, ο κάθε χρήστης δικτύου αντιδρά στα διόδια με ετερογενή τρόπο, δηλ.
+Επιπλέον, ο κάθε χρήστης δικτύου αντιδρά στα διόδια με ετερογενές τρόπο, δηλ.
 ο κάθε παίκτης $p$ στη ροή του δικτύου έχει διαφορετική τιμή ευαισθησίας χρόνου-χρήματος, η οποία περιγράφεται από μια συνάρτηση κατανομής $\alpha(p)$.
-Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομογενών παιγνίων κέρδους, κυρίως βασισμένα σε προηγούμενες δουλειές, και με αυτά ως βάση, τα επεκτείνουμε για να περιγράψουμε παίγνια κέρδους με ετερογενείς χρήστες.
-Εισαγά-γουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού ευαισθησίας $\as(t)$, ορισμένη για ο-ποιεσδήποτε $2$ ακμές του δικτύου ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία, δωσμένων σετ διοδίων $t$, τα κόστη των $2$ ακμών είναι ίσα.
+Πρώτα παρουσιάζουμε κάποιους βασικούς ορισμούς και ιδιότητες των ομοιογενών παιγνίων κέρδους, τα οποία είναι κυρίως βασισμένα σε προηγούμενες δουλειές, και με αυτά ως βάση, τα επεκτείνουμε για να περιγράψουμε παίγνια κέρδους με ετερογενείς χρήστες.
+Εισαγάγουμε έναν νέο όρο, τη συνάρτηση διαχωρισμού ευαισθησίας $\as(t)$, ορισμένη για οποιεσδήποτε $2$ ακμές του δικτύου ως η τιμή ευαισθησίας χρόνου-χρήματος για την οποία, δωσμένων σετ διοδίων $t$, τα κόστη των $2$ ακμών είναι ίσα.
 Με τη βοήθεια της $\as$ θα περιγράψουμε μερικές ιδιότητες γύρω από την εγωιστική συμπεριφορά των ετερογενών χρηστών για διαφορετικά διόδια, καθώς και θα αποδείξουμε την ύπαρξη άνω φράγματος για τις τιμές ευαισθησίας που αφορούν το παίγνιο.
 Στη συνέχεια, φτάνοντας στο κύριο σώμα αυτής της έρευνας, εξετάζουμε την ύπαρξη ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών για διαφορετικές περι-πτώσεις ετερογενών χρηστών.
-Δείχνουμε ότι δεν υπάρχει ισορροπία Nash όταν υπάρχουν πολλοί χρήστες με $0$ ευαισθησία, δηλ.
-παίκτες που δεν επηρρεάζονται από τα διόδια, το οποίο μας αναγκάζει στο εξής να υποθέσουμε ότι $\alpha(p) > 0$.
-Κατόπιν, εξετάζουμε περιπτώσεις όπου η συνάρτηση κατανομής είναι σταθερή, η οποίες δημιουργούν ομογενή συμπεριφορά στους χρήστες (κάνοντάς τα ψευδο-ετερογενή παίγνια), μέσω των οποίων μετά θα περιγράψουμε πώς συμπεριφέρονται η ροή, τα διόδια και τα σημεία ισορροπίας όταν αυτή η σταθερή τιμή μεταβάλλεται.
-Χρησιμοποιώντας όλα τα παραπάνω, μελετάμε βηματικές συναρτήσεις κατανομής, όπου, περιορίζοντας το μοντέλο μας σε στιγμιότυπα $2$ ακμών, αποδεικνύουμε μια αυστηρή συνθήκη για την τιμή ενός πιθανού σημείου ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών, συνδέοντάς το με το σημείο ισορροπίας σε ένα ισοδύναμο ψευδο-ετερογενή παίγνιο.
+Δείχνουμε ότι δεν υπάρχει ισορροπία Nash όταν υπάρ-χουν πολλοί χρήστες με $0$ ευαισθησία, δηλ.
+παίκτες που δεν επηρρεάζονται από τα διόδια, κάτι το οποίο μας αναγκάζει στο εξής να υποθέσουμε ότι $\alpha(p) > 0$.
+Στη συνέχεια, εξετάζουμε περιπτώσεις όπου η συνάρτηση κατανομής είναι σταθερή και άρα η συμπεριφορά των χρηστών παραμένει ομογενής (κάνοντάς τα ψευδο-ετερογενή παίγνια), μέσω των οποίων μετά θα περιγράψουμε πώς συμπεριφέρονται η ροή, τα διόδια και τα σημεία ισορροπίας όταν αυτή η σταθερή τιμή μεταβάλλεται.
+Χρησιμο-ποιώντας όλα τα παραπάνω, μελετάμε βηματικές συναρτήσεις κατανομής, όπου, περιο-ρίζοντας το μοντέλο μας σε στιγμιότυπα $2$ ακμών, αποδεικνύουμε μια ισχυρή απαίτηση για την τιμή ενός πιθανού σημείου ισορροπίας Nash στο παίγνιο κέρδους μεταξύ των διαχειριστών των ακμών, συνδέοντάς το με το σημείο ισορροπίας σε ένα ισοδύναμο ψευδο-ετερογενές παίγνιο.
 Εντέλει, παρουσιάζουμε και αναλύουμε έναν αλγόριθμο για τον υπολογισμό αυτού του σημείου ισορροπίας, αν υπάρχει, σε χρόνο γραμμικό σε σχέση με τον πληθάριθμο της βηματικής συνάρτησης, και κλείνουμε με μια συζήτηση για πιθανές μελλοντικές εργασίες.
@@
 		\draw (1/4,0) -- (1/4,-0.01) node[below] {$\frac14$};
-		\draw (1/3,0) -- (1/3,-0.01) node[below] {$\frac13$};
+		\draw (1/2,0) -- (1/2,-0.01) node[below] {$\frac12$};
 		%\draw (0,5/36) -- (-0.02,5/36) node[below=7,left] {$\frac{5}{36}$};
@@
 		\draw[thick] (-5/12,0) -- (-5/16,5/64);
-		\fill[black] (-5/16,5/64) ellipse (0.005 and 0.0025) node[above left] {$\frac{5}{64}$};
+		\fill[black] (-5/16,5/64) ellipse (0.008 and 0.004) node[above left] {$\frac{5}{64}$};
 		\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
 		\draw[thick] (1/16,23/192) -- (1/8,13/96);
-		\fill[black] (1/16,23/192) ellipse (0.005 and 0.0025) node[left=6,below] {$\frac{23}{192}$};
-		\fill[black] (1/8,13/96) ellipse (0.005 and 0.0025) node[above right] {$\frac{13}{96}$};
+		\fill[black] (1/16,23/192) ellipse (0.008 and 0.004) node[left=6,below] {$\frac{23}{192}$};
+		\fill[black] (1/8,13/96) ellipse (0.008 and 0.004) node[above right] {$\frac{13}{96}$};
 		\draw[thick,domain=1/8:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)});
@@
 
-\section*{Time-money sensitivity relation}
-
-For general heterogeneous models, the standard technique to capture the heterogeneity of the users in a network (at least in the accounted work) has been to apply a weight $\alpha$ to the toll cost viewed by each user, thus making their total cost $\ell(x) + \alpha t$.
-This approach is equivalent to applying the inverse weight to the latency cost, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
-We already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed}, where we showed that a heterogeneous game with a fixed distribution function is equivalent to a homogeneous game with latency functions restricted inversely proportionally.
-Unfortunately, as mentioned before, this correspondence is lost when considering non-fixed distribution functions, as then different tolls can create similar flows used by players with different sensitivity values, thus loosing the $1-1$ relation between latency and $\alpha$ values.
-
-Still, we believe that studying games with time sensitivity costs instead of money sensitivity ones, i.e.
+%\section*{Time-money sensitivity relation}
+
+%For general heterogeneous models, the standard technique to capture the heterogeneity of the users in a network (at least in the accounted work) has been to apply a weight $\alpha$ to the toll cost viewed by each user, thus making their total cost $\ell(x) + \alpha t$.
+%This approach is equivalent to applying the inverse weight to the latency cost, i.e. make the cost $\tfrac1\alpha \ell(x) + t$.
+%We already saw an application of this idea in Lemma \ref{lemma:heterogenous_flow_equiv_fixed}, where we showed that a heterogeneous game with a fixed distribution function is equivalent to a homogeneous game with latency functions restricted inversely proportionally.
+%Unfortunately, as mentioned before, this correspondence is lost when considering non-fixed distribution functions, as then different tolls can create similar flows used by players with different sensitivity values, thus loosing the $1-1$ relation between latency and $\alpha$ values.
+%Still, we believe that studying games with time sensitivity costs instead of money sensitivity ones, i.e.
 heterogeneous games with user cost $\tfrac1\alpha \ell(x) + t$, has the potential to reveal more insights about the game's mechanics and heterogeneous behaviour, which can then be mapped back to game models with the standard user cost of $\ell(x) + \alpha t$.

### 2025-01-20 thesis/article.tex
Thesis: Updates Th. Liannea title to Postdoctoral Researcher
Release v1.2

@@
 							\normalsize {\it {\bf Supervisor:}\\
-								Thanassis Lianeas, Lecturer,\\School of Electrical and Computer Engineering,\\
+								Thanassis Lianeas, Postdoctoral Researcher, School of Electrical and Computer Engineering,\\
 								National Technical University of Athens.\\

### 2025-02-01 thesis/slides.tex
Thesis: Pres: Adds draft slides for all sections
Preliminaries example, Sensitivity split, Pseudo-heterogeneous games, Step distribution functions, Future Work

@@
 	\;
-	\begin{block}{$2$-level optimisation problem}
+	\begin{block}{$2$-level game}
 		\begin{enumerate}
 			\item Shelfish routing game, flow on minimum cost paths
-			\item Profit maximisation game for link owners
+			\item Profit maximisation game for link operators
 		\end{enumerate}
@@
 		\begin{equation*}
-			c_{f(p)}(p) \leq c_j(p)
+			c_{f(p)}(p) \leq c_i(p)
 		\end{equation*}
@@
 
-\begin{frame}
+\begin{frame}{Heterogeneous players}
+	\begin{example}
+		Let $([2], \ell, \alpha)$ with $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and $\alpha(p) = p + 1$.
+	\end{example}
+	\begin{center}
+		\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
+			% Nodes
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+			\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
+
+			% Links
+			\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+			\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
+
+			% Description
+			%\node[align=center] at (2, -2) {Network of Example};
+		\end{tikzpicture}
+	\end{center}
+	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
+\end{frame}
+
+\begin{frame}{Heterogeneous players}
 	Nash equilibrium for $t$ always exists\footcite{1973JSP.....7..295S} and is unique\footcite{MILCHTAICH1996111}, again denote it by $x(t)$.
@@
 	\begin{block}{Profit}
-		For given set of tolls $t \in \R_+^N$, link owner $i$ gains profit
+		For given set of tolls $t \in \R_+^N$, link operator $i$ gains profit
 		\[\Pi_i(t) = x_i(t) \cdot t_i\]
@@
 	\begin{block}{Best response}
-		For fixed tolls assignments from other link owners $t_{-i} = t \setminus \{t_i\}$, link owner $i$ will try and maximise their profit
+		For fixed tolls assignments from remaining link operators $t_{-i} = t \setminus \{t_i\}$, link operator $i$ will try and maximise their profit
 		\[B_i(t_{-i}) = \argmax_{t_i \ge 0} \Pi(t_i, t_{-i})\]
@@
 	\end{definition}
+	The two pricing competition games played on two equivalent network congestion games are identical.
 \end{frame}
@@
 \begin{frame}{Sensitivity split}
+	In a heterogeneous game, in practice, each flow user plays a different game.
+
+	In example ?? the users are organised around the one for which $c_1(p) = c_2(p)$.
+
+	We need the notion of the money-sensitivity value for which two link costs are equal.
+\end{frame}
+
+\begin{frame}{Sensitivity split}
 	\begin{definition}
@@
 	\end{definition}
+	If $t_i = t_j \Leftrightarrow \ell_i(x_i) = \ell_j(x_j)$ then $c_i(p) = c_j(p)$ for \textbf{all} flow users.
 \end{frame}
@@
 \begin{frame}{Sensitivity split}
-	\begin{block}{Properties}
-		περιεχόμενο...
-	\end{block}
+	If $t_i \ne t_j$ then assume w.l.o.g. $t_i > t_j \Leftrightarrow \ell_i(x_i) < \ell_j(x_j)$.\\
+	Low money-sensitive players will use link $i$.\\
+	High money-sensitive players will use link $j$.
+
+	\begin{table}[h!]
+		\centering
+		\caption{Summary of properties for the sensitivity split.}
+		\begin{tabular}{| c || c | c |}
+			\hline
+			& \textbf{lower split} & \textbf{upper split} \\ \hline
+			$\alpha$ & $\alpha(p) \le \as^{(i, j)}(t)$ & $\alpha(p) \ge \as^{(i, j)}(t)$ \\ \hline
+			link & low-latency, high-toll & high-latency, low-toll \\ \hline
+			sensitivity & time $\ge$ money & time $\le$ money \\ \hline
+		\end{tabular}
+		\label{table:split_summary}
+	\end{table}
 \end{frame}
@@
 \begin{frame}{Sensitivity split}
-	\begin{block}{Monotonicity}
-		περιεχόμενο...
-	\end{block}
+	\begin{definition}
+		\label{definition:alpha_flow_sets}
+		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ and $x(t)$ the Nash equilibrium for $t$.
+		We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
+		We define a set function $A_i: \R_+^{|N|} \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
+		\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
+	\end{definition}
+
+	Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for any $i \in N$.
 \end{frame}
@@
 \begin{frame}{Sensitivity split}
-	Characterisation.
+	\begin{lemma}
+		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
+		Then the following hold:
+		\begin{enumerate}[(i)]
+			\item $\as^{(i, j)}(t) > 0$
+			\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
+			%\item if $\as^{(i, j)}(t) < \alpha(0)$ (or $\as^{(i, j)}(t) > \alpha(1)$) then $x(t) = (0, 1)$ (or $(1, 0)$)
+			\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
+			$\sup A_i(t) \le \as^{(i, j)}(t) \le \inf A_j(t)$
+		\end{enumerate}
+	\end{lemma}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Monotonicity}
+	\begin{lemma}
+		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t, t^\prime$ such that for some links $i, j \in N$ it holds that $t_i \ne t_j, t_i^\prime \ne t_j^\prime$ and $t_k = t_k^\prime$ $\forall k \in N \setminus \{i, j\}$.
+		If $x_i(t), x_j(t), x_i(t^\prime), x_j(t^\prime) > 0$ and $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0$, then:
+		\begin{enumerate}[(i)]
+			\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \le 1$ then $\as^{(i, j)}(t) \ge \as^{(i, j)}(t^\prime)$
+			\item if $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} \ge 1$ then $\as^{(i, j)}(t) \le \as^{(i, j)}(t^\prime)$
+		\end{enumerate}
+	\end{lemma}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Monotonicity}
+	\begin{proof}
+		We prove $(i)$ and $(ii)$ follows symmetrically.\\
+		If $x(t) = x(t^\prime)$ then the property follows from the definition of $\as$.
+		If $x(t) \ne x(t^\prime)$ then assume w.l.o.g. that $x_i(t) > x_i(t^\prime)$, so a player $p$ moved from $i$ to $j$ between $t$ and $t^\prime$.
+		\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
+		Applying the previous lemma gives us
+		\[\as^{(i, j)}(t^\prime) \le \inf A_j(t^\prime) \le \sup A_i(t) \le \as^{(i, j)}(t)\]
+	\end{proof}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Limits}
+	\begin{lemma}
+		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
+		Then:
+		\begin{enumerate}[(i)]
+			\item
+			\begin{flalign*}
+				\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) &= 0 &
+			\end{flalign*}
+			\item
+			\begin{flalign*}
+				\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \limsup_{t_i - t_j \rightarrow 0^+} A_i(t) &
+			\end{flalign*}
+		\end{enumerate}
+	\end{lemma}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Limits}
+	\begin{proof}
+		$ $
+		\begin{enumerate}[(i)]
+			\item For $L = \max\{\ell_i(1) - \ell_j(0), \ell_j(1) - \ell_i(0)\}$ we find
+			\begin{flalign*}
+				\lim_{|t_i - t_j| \rightarrow +\infty}|\as^{(i, j)}(t)| &= \lim_{|t_i - t_j| \rightarrow +\infty}\frac{|\ell_i(x_i(t)) - \ell_j(x_j(t))|}{|t_i - t_j|}\\
+				&\le \lim_{|t_i - t_j| \rightarrow +\infty}\frac{L}{|t_i - t_j|} = 0
+			\end{flalign*}
+		\end{enumerate}
+	\end{proof}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Limits}
+	\begin{proof}
+		$ $
+		\begin{enumerate}[(ii)]
+			\item ...
+		\end{enumerate}
+	\end{proof}
+\end{frame}
+
+\begin{frame}{Sensitivity split}
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[x=2cm, y=2cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-1.1,0);
+			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+			\draw[->] (0,0) -- (0,2.2) node[above] {$\as(t)$};
+
+			% Tick marks
+			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+			\draw (2,0) -- (2,-0.05) node[below] {$2$};
+			\draw (0,2) -- (-0.05, 2) node[left] {$2$};
+			\draw (0,4/3) -- (0.05,4/3) node[right] {$4/3$};
+			\draw (0,5/3) -- (-0.05,5/3) node[left] {$5/3$};
+			\draw (0,1) -- (-0.05,1) node[left] {$1$};
+
+			% Function graph
+			%\draw[thick] (-1,1) -- (0,4/3);
+			%\draw[thick] (0,5/3) -- (2,1);
+			\draw[thick,domain=-1:0] plot (\x,{4/(3-\x)});
+			\draw[thick,domain=0:2] plot (\x,{5/(3+\x)});
+
+			% Dots
+			\fill[white] (0,4/3) ellipse (0.03 and 0.03);
+			\draw[black] (0,4/3) ellipse (0.03 and 0.03);
+			\fill[white] (0,5/3) ellipse (0.03 and 0.03);
+			\draw[black] (0,5/3) ellipse (0.03 and 0.03);
+		\end{tikzpicture}
+		\caption{Split function of Example}
+		\label{figure:alpha_simple:split_example}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Upper bound}
+	We observe that $\as$ might never take some upper values of $\alpha$.\\
+	Are then those values relevant?
+
+	\begin{theorem}
+		Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games and $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the (equal) flow on paths for $t = 0$.
+		If $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that
+		\[\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < 1 - \min_{i \in N}\{x_i(0)\}\]
+		then $\Gm_1$ and $\Gm_2$ are equivalent.
+	\end{theorem}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Upper bound}
+	\begin{proof}
+		...
+	\end{proof}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Upper bound}
+	For the Example we have
+	\[\max\{x_1(0), x_2(0)\} = \max\{2/3, 1/3\} = 2/3\]
+	so if we used a distribution function such as
+	\[
+		\alpha(p) =
+		\begin{cases}
+			p + 1 & p \le 2/3 \\
+			\mathrm{e}^p & p > 2/3
+		\end{cases}
+	\]
+	then $\as(t)$ would remain the same for all $t \in \R_+^n$
 \end{frame}
@@
 
-\section{Step distribution function}
+\begin{frame}{Heterogeneous Pricing Games}
+	Zero money sensitivity creates issues.
+	\begin{lemma}
+		Let $(N, \ell, \alpha)$ where $\exists \epsilon > 0: \alpha(p) = 0 \; \forall p < \epsilon$.
+		Let $i \in N$ be a link for which $\ell_i(0) = \min_{j \in N} \ell_i(0)$.
+		Then $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{|N| - 1}$.
+	\end{lemma}
+	\begin{proof}
+		$\ell_i(0) = \min_{j \in N} \ell_i(0)$, ensures link $i$ will always have flow
+
+		$i$ can select $t_i > \max t_{-i}$ to make link $i$ the lowest-latency link, populated exclusively by players with $\alpha(p) = 0$
+
+		We fix $t_i^\prime$ and we see that
+		\[
+			\lim_{t_i \rightarrow +\infty} \Pi_i(t_i, t_{-i}) \ge \lim_{t_i \rightarrow +\infty} x_i^\prime(t_i^\prime, t_{-i})t_i = +\infty
+		\]
+		making in turn $B_i(t_{-i}) = +\infty$.
+	\end{proof}
+\end{frame}
+
+\begin{frame}{Pseudo-heterogeneous Pricing Games}
+	Consider cases where $\alpha(p) = c$ for some $c \in \R_+$.
+	\[
+		\sum_{i \in N} (\ell(x_i(t)) + c t_i) \cdot (x_i(t) - x_i) \leq 0
+	\]
+
+	\begin{lemma}
+		Let $\Gm_1 = (N, \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = (N, \ell^{(2)}, 1)$ a homogeneous pricing game with latencies $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
+		Then the two games are equivalent.
+	\end{lemma}
+	We will call such games \textit{pseudo-heterogeneous}.
+
+	Latency-sensitivity relation is lost for general $\alpha$
+\end{frame}
+
+\begin{frame}{Pseudo-heterogeneous Pricing Games}
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-1.1,0);
+			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+			\draw[->] (0,0) -- (0,1.1) node[above] {$x_1(t)$};
+
+			% Tick marks
+			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+			\draw (-1/3,0) -- (-1/3,-0.05) node[left=9,below] {$-\frac13$};
+			\draw (-1/4,0) -- (-1/4,-0.05) node[right=3,below] {$-\frac14$};
+			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+			\draw (2/4,0) -- (2/4,-0.05) node[below] {$\frac12$};
+			\draw (2/3,0) -- (2/3,-0.05) node[below] {$\frac23$};
+			\draw (2,0) -- (2,-0.05) node[below] {$2$};
+			\draw (0,1) -- (0.05,1) node[right] {$1$};
+			\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
+
+			% Flow function graphs
+			\draw[thick, blue!33] (-1,1) -- (2,0) node[above, black] {$\alpha = 1$};
+			\draw[thick, blue!66] (-1/3,1) -- (2/3,0) node[above right, black] {$\alpha = 3$};
+			\draw[thick, blue!100] (-1/4,1) -- (2/4,0) node[black] at (0.2,0.17) {$\alpha = 4$};
+		\end{tikzpicture}
+		\caption{Flow function for link $1$ of Example for $\alpha(p) = 1, 3, 4$.}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Pseudo-heterogeneous Pricing Games}
+	\begin{lemma}
+		Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with $\alpha^{(1)}(p) = c_1 > 0$, $\alpha^{(2)}(p) = c_2 > 0$, then
+		\begin{enumerate}[$(i)$]
+			%\item $x^{(1)}(0) = x^{(2)}(0)$
+			\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
+			\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
+			\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
+		\end{enumerate}
+	\end{lemma}
+\end{frame}
+
+\begin{frame}{Pseudo-heterogeneous Pricing Games}
+	\begin{lemma}
+		Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with $\alpha^{(1)}(p) = c_1 > 0$, $\alpha^{(2)}(p) = c_2 > 0$.\\
+		Let $t^{*(1)}, t^{*(2)}$ the Nash Equilibria for the pricing games in $\Gm_1$ and $\Gm_2$.
+		Then
+		\begin{enumerate}[$(i)$]
+			\item $\frac{t^{*(1)}}{t^{*(2)}} = \frac{c_2}{c_1}$
+			\item $x^{(1)}(t^{*(1)}) = x^{(2)}(t^{*(2)})$
+		\end{enumerate}
+	\end{lemma}
+	Nash Equilibrium always at the same flow.
+\end{frame}
+
+\section{Step distribution functions}
+
+\begin{frame}{Step distribution functions}
+	We will limit our model to instances with $2$ links.
+
+	In $2$-link games, $\as(t)^{(1, 2)} = \as(t)$.
+
+	There always exists an $\alpha$ value for which the two link costs are equal.
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{lemma}
+		Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls and $x^{(1)}(t)$ the Nash equilibrium for $t$.
+		Now let $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a pseudo-heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
+		Then
+		\begin{enumerate}[$(i)$]
+			\item $x^{(1)}(t) = x^{(2)}(t)$
+			\item $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$ for each respective link operator $i$
+		\end{enumerate}
+	\end{lemma}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{example}
+		Let $([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
+		\begin{align*}
+			\alpha(p) =
+			\begin{cases}
+				1 & p \le \tfrac15 \\
+				3 & p \in \left(\tfrac15, \tfrac12\right) \\
+				4 & p \ge \tfrac12
+			\end{cases}&
+		\end{align*}
+	\end{example}
+
+	\begin{center}
+		\begin{multicols}{2}
+			% Left Column: Network Graph
+			\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
+				% Nodes
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
+
+				% Links
+				\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+				\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
+
+				% Description
+				\node[align=center] at (2, -2) {Network of Example};
+			\end{tikzpicture}
+
+			% Right Column: Distribution function Graph
+			\begin{tikzpicture}[x=3cm, y=0.7cm, every node/.style={font=\small}]
+				% Axes
+				\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
+				\draw[->] (0,0) -- (0,4.2) node[above] {$\as(p)$};
+
+				% Tick marks
+				\draw (0,0) -- (0,-0.05) node[below] {$0$};
+				\draw (0.2,0) -- (0.2,-0.05) node[below] {$\frac15$};
+				\draw (0.5,0) -- (0.5,-0.05) node[below] {$\frac12$};
+				\draw (1,0) -- (1,-0.05) node[below] {$1$};
+				\draw (0,1) -- (-0.05,1) node[left] {$1$};
+				\draw (0,3) -- (-0.05,3) node[left] {$3$};
+				\draw (0,4) -- (-0.05,4) node[left] {$4$};
+
+				% Function graph
+				\draw[thick] (0,1) -- (0.2,1);
+				\draw[thick] (0.2,3) -- (0.5,3);
+				\draw[thick] (0.5,4) -- (1,4);
+
+				% Closed / Open dots
+				\fill[white] (0.2,1) ellipse (0.014 and 0.06);
+				\draw[black] (0.2,1) ellipse (0.014 and 0.06);
+				\fill[black] (0.2,3) ellipse (0.014 and 0.06);
+				\draw[black] (0.2,3) ellipse (0.014 and 0.06);
+				\fill[black] (0.5,3) ellipse (0.014 and 0.06);
+				\draw[black] (0.5,3) ellipse (0.014 and 0.06);
+				\fill[white] (0.5,4) ellipse (0.014 and 0.06);
+				\draw[black] (0.5,4) ellipse (0.014 and 0.06);
+
+				% Description
+				\node[align=center] at (0.7, -1.7) {Distribution function of Example};
+			\end{tikzpicture}
+		\end{multicols}
+	\end{center}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[x=3.4cm, y=1cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-1.1,0);
+			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+			\draw[->] (0,0) -- (0,4.4) node[above] {$\as(t)$};
+
+			% Tick marks
+			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
+			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
+			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
+			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
+			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
+			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
+			\draw (2,0) -- (2,-0.05) node[below] {$2$};
+			\draw (0,1) -- (-0.05,1) node[left] {$1$};
+			\draw (0,3) -- (0.05,3) node[right] {$3$};
+			\draw (0,4) -- (-0.05,4) node[left] {$4$};
+
+			% Function graph
+			% Left side
+			\draw[thick] (-1,1) -- (-2/5,1);
+			\draw[thick] (-2/5,1) -- (-2/15,3);
+			\draw[thick] (-2/15,3) -- (0,3);
+			% Right side
+			\draw[thick] (0,4) -- (1/8,4);
+			\draw[thick] (1/8,4) -- (1/6,3);
+			\draw[thick] (1/6,3) -- (7/15,3);
+			\draw[thick] (7/15,3) -- (7/5,1);
+			\draw[thick] (7/5,1) -- (2,1);
+
+			% Dots
+			\fill[white] (0,3) ellipse (0.02 and 0.066);
+			\draw[black] (0,3) ellipse (0.02 and 0.066);
+			\fill[white] (0,4) ellipse (0.02 and 0.066);
+			\draw[black] (0,4) ellipse (0.02 and 0.066);
+		\end{tikzpicture}
+		\caption{Split function of Example}
+		\label{figure:alpha_step:split}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-1.1,0);
+			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+			\draw[->] (0,0) -- (0,1.1) node[above] {$x_1(t)$};
+
+			% Tick marks
+			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
+			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
+			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
+			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
+			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
+			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
+			\draw (2,0) -- (2,-0.05) node[below] {$2$};
+			\draw (0,1) -- (-0.05,1) node[left] {$1$};
+			\draw (0,4/5) -- (0.05,4/5) node[right] {$\frac45$};
+			\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
+			\draw (0,1/2) -- (-0.05,1/2) node[left] {$\frac12$};
+			\draw (0,1/5) -- (-0.05,1/5) node[left] {$\frac15$};
+
+			% Function graph
+			% Base flow functions
+			\draw[gray,dashed, very thin] (-1,1) -- (2,0);
+			\draw[gray,dashed, very thin] (-1/3,1) -- (2/3,0);
+			\draw[gray,dashed, very thin] (-1/4,1) -- (2/4,0);
+
+			% Left side
+			\draw[thick] (-1,1) -- (-2/5,4/5);
+			\draw[thick] (-2/5,4/5) -- (-2/15,4/5);
+			\draw[thick] (-2/15,4/5) -- (0,2/3);
+			% Right side
+			\draw[thick] (0,2/3) -- (1/8,1/2);
+			\draw[thick] (1/8,1/2) -- (1/6,1/2);
+			\draw[thick] (1/6,1/2) -- (7/15,1/5);
+			\draw[thick] (7/15,1/5) -- (7/5,1/5);
+			\draw[thick] (7/5,1/5) -- (2,0);
+		\end{tikzpicture}
+		\caption{Flow function for link $1$ of Example}
+		\label{figure:alpha_step:flow}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	Notice that when $x_1$ is fixed then $\as$ isn't and vice-versa.\\
+	If the flow is moving, then it does so among players with the same sensitivity type, which is one of the finitely many values $\alpha$ can take.
+	If all players of each sensitivity type are using a single link, then $\as$ can take any value between the lowest and highest $\alpha$ value in the upper and lower split respectively.
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{theorem}
+		Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
+		If $\Gm_1$ has a Nash equilibrium for the pricing game at toll $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ a pseudo-heterogeneous game with latency functions the same as the ones in $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as(t^*)$.
+		Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
+	\end{theorem}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{example}
+		Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
+		\begin{align*}
+			\alpha(p) =
+			\begin{cases}
+				3 & p \le \tfrac14 \\
+				4 & p > \tfrac14
+			\end{cases}&
+		\end{align*}
+		Then $\Gm$ has a Nash Equilibrium for the pricing game at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+	\end{example}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[x=8cm, y=10cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-0.4,0);
+			\draw[->] (0,0) -- (0.7,0) node[right] {$t_1 - t_2$};
+			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};
+
+			% Tick marks
+			\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
+			\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
+			\draw (-1/12,0) -- (-1/12,-0.01) node[left=9,below] {$-\frac{1}{12}$};
+			\draw (-1/16,0) -- (-1/16,-0.01) node[right=2,below] {$-\frac{1}{16}$};
+			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
+			\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
+			\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
+			\draw (5/12,0) -- (5/12,-0.01) node[below] {$\frac{5}{12}$};
+			\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
+			\draw (2/3,0) -- (2/3,-0.01) node[below] {$\frac23$};
+			%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
+			%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};
+
+			% Pseudo-heterogeneous profits
+			\draw[gray,dashed,thick,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[above=17,right=-7,black] {$c = 3$};
+			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=10,right=-3,black] {$c = 4$};
+
+			% Profit function
+			\draw[thick,domain=-1/3:-1/12] plot (\x,{((2-3*\x)/3)*(4/12+\x)});
+			\draw[thick] (-1/12,3/16) -- (-1/16, 39/192);
+			\fill[black] (-1/12,3/16) ellipse (0.00625 and 0.005) node[below right] {$\frac{3}{16}$};
+			\fill[black] (-1/16,39/192) ellipse (0.00625 and 0.005) node[above left] {$\frac{39}{192}$};
+			\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
+			\draw[thick] (5/16,31/192) -- (5/12,3/16);
+			\fill[black] (5/16,31/192) ellipse (0.00625 and 0.005) node[below left] {$\frac{31}{192}$};
+			\fill[black] (5/12,3/16) ellipse (0.00625 and 0.005) node[above right] {$\frac{3}{16}$};
+			\draw[thick,domain=5/12:2/3] plot (\x,{((2-3*\x)/3)*(4/12+\x)});
+
+			% Max point
+			\fill[red] (1/12, 25/108) ellipse (0.00625 and 0.005) node[below,black] {$\frac{25}{108}$};
+		\end{tikzpicture}
+		\\[15pt]
+		\begin{tikzpicture}[x=10cm, y=15cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-0.55,0);
+			\draw[->] (0,0) -- (0.4,0) node[right] {$t_2 - t_1$};
+			\draw[->] (0,0) -- (0,0.2) node[above] {$\Pi_2(t)$};
+
+			% Tick marks
+			%\draw (-2/3,0) -- (-2/3,-0.01) node[below] {$-\frac23$};
+			\draw (-2/4,0) -- (-2/4,-0.01) node[below] {$-\frac24$};
+			\draw (-5/12,0) -- (-5/12,-0.01) node[below] {$-\frac{5}{12}$};
+			\draw (-5/16,0) -- (-5/16,-0.01) node[below] {$-\frac{5}{16}$};
+			\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
+			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_1^* = \frac{5}{12}$};
+			\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
+			\draw (1/12,0) -- (1/12,-0.01) node[right=3,below] {$\frac{1}{12}$};
+			\draw (1/4,0) -- (1/4,-0.01) node[below] {$\frac14$};
+			\draw (1/3,0) -- (1/3,-0.01) node[below] {$\frac13$};
+			%\draw (0,5/36) -- (-0.02,5/36) node[below=7,left] {$\frac{5}{36}$};
+
+			% Pseudo-heterogeneous profits
+			\draw[gray,dashed,thick,domain=-5/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)}) node[above=15,right=-7,black] {$c = 3$};
+			\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,left=17,black] {$c = 4$};
+
+			% Profit function
+			\draw[thick] (-5/12,0) -- (-5/16,5/64);
+			\fill[black] (-5/12,0) ellipse (0.0045 and 0.003) node[above left] {$0$};
+			\fill[black] (-5/16,5/64) ellipse (0.0045 and 0.003) node[above left] {$\frac{5}{64}$};
+			\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
+			\draw[thick] (1/16,23/192) -- (1/12,1/8);
+			\fill[black] (1/16,23/192) ellipse (0.0045 and 0.003) node[below left] {$\frac{23}{192}$};
+			\fill[black] (1/12,1/8) ellipse (0.0045 and 0.003) node[above right] {$\frac18$};
+			\draw[thick,domain=1/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)});
+
+			% Max point
+			\fill[red] (-1/12, 4/27) ellipse (0.0045 and 0.003) node[above,black] {$\frac{4}{27}$};
+		\end{tikzpicture}
+		\caption{Profit functions for link operators $1$ and $2$ of Example when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+Red dot indicates the max profit at $t^*$.
+Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
+		\label{figure:alpha_step:profit_ne}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{example}
+		Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
+		\begin{align*}
+			\alpha(p) =
+			\begin{cases}
+				2 & p \le \tfrac14 \\
+				4 & p > \tfrac14
+			\end{cases}&
+		\end{align*}
+		Then $\Gm$ has no Nash Equilibrium for the pricing game.
+	\end{example}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[x=6cm, y=10cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-0.4,0);
+			\draw[->] (0,0) -- (1.1,0) node[right] {$t_1 - t_2$};
+			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};
+
+			% Tick marks
+			\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
+			\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
+			\draw (-1/8,0) -- (-1/8,-0.01) node[left=5,below] {$-\frac18$};
+			\draw (-1/16,0) -- (-1/16,-0.01) node[below] {$-\frac{1}{16}$};
+			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
+			\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
+			\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
+			\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
+			\draw (5/8,0) -- (5/8,-0.01) node[below] {$\frac58$};
+			\draw (1,0) -- (1,-0.01) node[below] {$1$};
+			%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
+			%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};
+
+			% Pseudo-heterogeneous profits
+			\draw[gray,dashed,thick,domain=-1/3:2/2] plot (\x,{((2-2*\x)/3)*(1/3+\x)}) node[above=20,right=-5,black] {$c = 2$};
+			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=15,right,black] {$c = 4$};
+
+			% Profit function
+			\draw[thick,domain=-1/3:-1/8] plot (\x,{((2-2*\x)/3)*(4/12+\x)});
+			\draw[thick] (-1/8, 5/32) -- (-1/16, 39/192);
+			\fill[black] (-1/8, 5/32) ellipse (0.008333 and 0.005) node[below right] {$\frac{5}{32}$};
+			\fill[black] (-1/16,39/192) ellipse (0.008333 and 0.005) node[above left] {$\frac{39}{192}$};
+			\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
+			\draw[thick] (5/16,31/192) -- (5/8,23/96);
+			\fill[black] (5/16,31/192) ellipse (0.008333 and 0.005) node[below left] {$\frac{31}{192}$};
+			\fill[black] (5/8,23/96) ellipse (0.008333 and 0.005) node[above right] {$\frac{23}{96}$};
+			\draw[thick,domain=5/8:1] plot (\x,{((2-2*\x)/3)*(4/12+\x)});
+
+			% Max point
+			\fill[red] (1/12, 25/108) ellipse (0.008333 and 0.005) node[below,black] {$\frac{25}{108}$};
+		\end{tikzpicture}
+		\\[15pt]
+		\begin{tikzpicture}[x=8cm, y=15cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-0.55,0);
+			\draw[->] (0,0) -- (0.6,0) node[right] {$t_2 - t_1$};
+			\draw[->] (0,0) -- (0,0.2) node[above] {$\Pi_2(t)$};
+
+			% Tick marks
+			%\draw (-2/3,0) -- (-2/3,-0.01) node[below] {$-\frac23$};
+			\draw (-2/4,0) -- (-2/4,-0.01) node[below] {$-\frac24$};
+			\draw (-5/12,0) -- (-5/12,-0.01) node[below] {$-\frac{5}{12}$};
+			\draw (-5/16,0) -- (-5/16,-0.01) node[below] {$-\frac{5}{16}$};
+			\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
+			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_1^* = \frac{5}{12}$};
+			\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
+			\draw (1/12,0) -- (1/12,-0.01) node[right=3,below] {$\frac{1}{12}$};
+			\draw (1/4,0) -- (1/4,-0.01) node[below] {$\frac14$};
+			\draw (1/2,0) -- (1/2,-0.01) node[below] {$\frac12$};
+			%\draw (0,5/36) -- (-0.02,5/36) node[below=7,left] {$\frac{5}{36}$};
+
+			% Pseudo-heterogeneous profits
+			\draw[gray,dashed,thick,domain=-5/12:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)}) node[above=20,right=-5,black] {$c = 2$};
+			\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,right,black] {$c = 4$};
+
+			% Profit function
+			\draw[thick] (-5/12,0) -- (-5/16,5/64);
+			\fill[black] (-5/16,5/64) ellipse (0.008 and 0.004) node[above left] {$\frac{5}{64}$};
+			\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
+			\draw[thick] (1/16,23/192) -- (1/8,13/96);
+			\fill[black] (1/16,23/192) ellipse (0.008 and 0.004) node[left=6,below] {$\frac{23}{192}$};
+			\fill[black] (1/8,13/96) ellipse (0.008 and 0.004) node[above right] {$\frac{13}{96}$};
+			\draw[thick,domain=1/8:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)});
+
+			% Max point
+			\fill[red] (-1/12, 4/27) ellipse (0.008 and 0.004) node[above,black] {$\frac{4}{27}$};
+		\end{tikzpicture}
+		\caption{Profit functions for link operators $1$ and $2$ of Example when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+Red dot indicates the max profit at $t^*$.
+Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
+		\label{figure:alpha_step:profit_no_ne}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{lemma}
+		Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}, \; m \in N$.
+		Also let $t \ne 0$ a set of tolls for which it holds for all $k \in [m]$ that all players $p$ with $\alpha(p) = \alpha_k$ are using the same link.
+		Then $t$ is not a Nash equilibrium for the pricing game.
+	\end{lemma}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	\begin{theorem}
+		Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
+		If $\Gm_1$ has a Nash equilibrium for the pricing game at toll $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ a pseudo-heterogeneous game with latency functions the same as the ones in $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as(t^*)$.
+		Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
+	\end{theorem}
+\end{frame}
+
+\begin{frame}{Step distribution function}
+	Summary of Algorithm
+	For a given heterogeneous pricing game $\Gm = ([2], \ell, \alpha)$
+	\begin{enumerate}
+		\item Consider $\Gm^\prime = ([2], \ell, 1)$ and calculate its pricing Nash equilibrium $t^{*\prime}$ and respective flow $x^\prime(t^{*\prime})$.
+		\item Calculate $\as(t^*)$ as the $\alpha$ value of the lower split flow in $x^\prime(t^{*\prime})$ (valid since $x(t^*) = x^\prime(t^{*\prime})$ from Theorem \ref{theorem:a_step_ne_equiv_fixed}, Lemma \ref{lemma:a_fixed_pricing_ne_relation})
+		\item Calculate the candidate pricing Nash Equilibrium $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$ as well as the respective profits $\Pi_1(t^*), \Pi_2(t^*)$.
+		\item For each $\alpha_k$, value of $\alpha$ different than $\as(t^*)$, and for each link operator $i \in [2]$
+		\begin{enumerate}[$4.1$]
+			\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i}^*)$ as well as the tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
+			\item Search for $\Pi_{i, k}$, the max profit for $i$ within those $t_i$ ranges:
+			\begin{enumerate}[$4.2.1$]
+				\item If $B_{i, k}(t_{-i}^*)$ is within the $t_i$ ranges, then $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}^*), t_{-i}^*)$.
+				\item Otherwise, $\Pi_{i, k}$ is the highest profit value among the ($4$) tolls in the edges of the two $t_1$ ranges.
+			\end{enumerate}
+			\item If $\Pi_i < \Pi_{i, k}$, then $\Gm$ has no pricing Nash Equilibrium.
+		\end{enumerate}
+		\item If all of the above checks fail, then $t^*$ is the Nash Equilibrium for the pricing game in $\Gm$, so return it.
+	\end{enumerate}
+\end{frame}
 
 \section{Future work}
+
+\begin{frame}{Future work}
+	\begin{itemize}
+		\item Pseudo-heterogeneous games
+		\item Step distribution functions
+		\begin{itemize}
+			\item $2$-link networks
+			\item $n$-link networks
+		\end{itemize}
+		\item Continuous distribution functions
+		\item Function series approximation
+		\item Split function for series-parallel links
+	\end{itemize}
+\end{frame}
 

### 2025-02-07 thesis/slides.tex
Thesis: Pres: Improvements over all sections
History graph, Preliminaries and Pricing Games cleanup and restructuring, Sensitivity Split partial cleanup and some extra Future Work

@@
 {
-	\usetheme[progressbar=foot,numbering=fraction,background=light,block=fill]{metropolis}
+	\usetheme[subsectionpage=simple,progressbar=foot,numbering=fraction,background=light,block=fill]{metropolis}
 	\usecolortheme{default}
 	\usefonttheme{default}
+	\setbeamercolor{example text}{fg=mDarkTeal}
 	\setbeamertemplate{navigation symbols}{}
@@
 }
-\date{\today}
+%\date{\today}
+\date{February 10, 2025}
 
@@
 
-\section{Introduction}
-
-\begin{frame}{History}
-	\begin{itemize}
-		\item Selfish routing \footcite{pigou1920economics}
-		\item Congestion games \footcite{Rosenthal1973ACO}
-		\item Wardrop equilibrium \footcite{wardrop_theoretical_1952}
-		\item Pricing competition \footcite{10.1287/moor.1060.0231}
-		\begin{itemize}
-			\item Homogeneous case with toll caps \footcite{Harks_2019}
-		\end{itemize}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}{Our model}
+\section{Brief History}
+
+\begin{frame}{\insertsection}
+	Selfish routing can model and solve a variety of real-world problems in economics, transportation and more.
+	\\[20pt]
+	\begin{tikzpicture}[scale=0.9, every node/.style={font=\small,align=center}]
+		\draw (0,-0.15) node[below] {Pigou} -- (0,0.15) node[above] {$1920$};
+		\draw (0,0) -- (6,0);
+		\draw (6,-0.15) node[below] {Beckman\\et al.} -- (6,0.15) node[above] {$1956$};
+		\draw (6,0) -- (9,0);
+		\draw (9,-0.15) node[below] {Rosenthal} -- (9,0.15) node[above] {$1973$};
+		\draw (9,0) -- (10,0);
+
+		\draw (0,-2.65) node[below] {Cole\\et al.} -- (0,-2.35) node[above] {$2003$};
+		\draw (0,-2.5) -- (2,-2.5);
+		\draw (2,-2.65) node[below] {Acemoglu\\\& Ozdaglar} -- (2,-2.35) node[above] {$2007$};
+		\draw (2,-2.5) -- (7.5,-2.5);
+		\draw (7.5,-2.65) node[below] {Correa\\et al.} -- (7.5,-2.35) node[above] {$2018$};
+		\draw (7.5,-2.5) -- (9,-2.5);
+		\draw (9,-2.65) node[below] {Harks\\et al.} -- (9,-2.35) node[above] {$2019$};
+		\draw (9,-2.5) -- (10,-2.5);
+	\end{tikzpicture}
+\end{frame}
+
+\section{Preliminaries}
+
+\subsection{Our model}
+
+\begin{frame}{Preliminaries | Our model}
 	\begin{center}
@@
 \end{frame}
-\begin{frame}{Our model}
+\begin{frame}{Preliminaries | Our model}
 	\begin{center}
@@
 
-\begin{frame}{Our model}
+\begin{frame}{Preliminaries | Our model}
 	\;
@@
 
-\begin{frame}{Preliminaries}
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
 	\;
@@
 
-\begin{frame}{Homogeneous players}
-	Links can be tolled by assigning tolls $t \in \R_+^N$.
-
-	Player $p$ experiences on link $i$ total cost $c_i(p) = \ell_i(x_i) + t_i$.
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level) | Example}
+\begin{center}
+	\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
+		% Nodes
+		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+		\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
+
+		% Links
+		\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+		\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
+		\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
+	\end{tikzpicture}
+\end{center}
+Flow $x = \left(\frac23, \frac13, 0\right)$ has all players on minimum latency links.
+\end{frame}
+
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
+	Tolls $t \in \R_+^{|N|}$ can be assigned to links, affecting player cost.
+
+	In \textbf{homogeneous} networks, player $p$ on link $i$ experiences total cost $c_i(p) = \ell_i(x_i) + t_i$.
+
+	In \textbf{heterogeneous} networks, players value time-money differently, so we add a weight $\alpha$ to the toll (money) cost.
+
+	Player $p$ on link $i$ experiences total cost $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
+	\begin{block}{Distribution function $\alpha: [0, 1] \rightarrow [0, +\infty]$}
+		\begin{itemize}
+			\item players are ordered w.r.t. sensitivity
+			\item $\alpha$ is non-decreasing
+		\end{itemize}
+	\end{block}
+\end{frame}
+
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
+	In homogeneous networks, all players view link costs the same.
 	\begin{definition}
@@
 
-	Wardrop equilibrium always exits and is unique\footcite{??}, denote it by $x(t)$.
-\end{frame}
-
-\begin{frame}{Homogeneous players}
-	\begin{lemma}[variational inequality\footcite{dafermos1973toll}]
+	Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$).
+\end{frame}
+
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
+	\begin{lemma}[variational inequality\footcites{beckmann1956studies}{dafermos1973toll}]
 		A flow $x$ is a Wardrop equilibrium for $t$ if and only if for all feasible flows $x^\prime$,
@@
 	\end{lemma}
-	Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$) or (affine) latencies.
-\end{frame}
-
-\begin{frame}{Heterogeneous players}
-	Players value time-money differently, so add weight $\alpha$ to money.
-	\begin{block}{Distribution function $\alpha: [0, 1] \rightarrow [0, +\infty]$}
-		\begin{itemize}
-			\item players are ordered w.r.t. sensitivity
-			\item $\alpha$ is non-decreasing
-		\end{itemize}
-	\end{block}
-	Player $p$ experiences on link $i$ total cost $c_i(p) = \ell_i(x_i) + \alpha(p) \cdot t_i$.
+\end{frame}
+
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
 	\begin{definition}
-		For a given set of tolls $t$, a flow $x$ is a \textit{Nash equilibrium for $t$} if for all players $p \in [0, 1]$ and $\forall i \in N$ it holds that
+		For a given set of tolls $t$, a flow $x$ is a \textit{Nash equilibrium for $t$} if $\forall p \in [0, 1]$ and $\forall i \in N$ it holds that
 		\begin{equation*}
@@
 	\end{definition}
-\end{frame}
-
-\begin{frame}{Heterogeneous players}
-	\begin{example}
-		Let $([2], \ell, \alpha)$ with $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and $\alpha(p) = p + 1$.
-	\end{example}
+	N.E. always exists and is unique w.r.t. costs for homogeneous\footcite{beckmann1956studies} and heterogeneous\footcites{1973JSP.....7..295S}{MILCHTAICH1996111} networks.
+	We denote it by $x(t)$.
+\end{frame}
+
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level) | Example}
 \begin{center}
@@
 		\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
-			\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
-
-			% Description
-			%\node[align=center] at (2, -2) {Network of Example};
+		\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
+		\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
 	\end{tikzpicture}
 \end{center}
-	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
-\end{frame}
-
-\begin{frame}{Heterogeneous players}
-	Nash equilibrium for $t$ always exists\footcite{1973JSP.....7..295S} and is unique\footcite{MILCHTAICH1996111}, again denote it by $x(t)$.
-\end{frame}
-
-\begin{frame}{Pricing competition (2\textsuperscript{nd} level)}
+For homogeneous players and tolls $t = \left(4, 2, 1\right)$ we get
+\[x(t) = \left(0, \frac12, \frac12\right)\]
+since $\forall p \in [0, 1]$ it holds $c_2(p) = c_3(p) = 7/2$ and $c_1(p) = 4$.
+\end{frame}
+
+\begin{frame}{Preliminaries | Pricing competition (2\textsuperscript{nd} level)}
 	Links are owned by agents who compete for profit.
 	\begin{block}{Profit}
-		For given set of tolls $t \in \R_+^N$, link operator $i$ gains profit
+		For given set of tolls $t \in \R_+^{|N|}$, link operator $i$ gains profit
 		\[\Pi_i(t) = x_i(t) \cdot t_i\]
 	\end{block}
-
 	\begin{block}{Best response}
@@
 
-\begin{frame}{Pricing competition (2\textsuperscript{nd} level)}
-	\begin{block}{Nash Equilibrium}
-		A given set of tolls $t$ is a \textit{Nash Equilibrium for the pricing game} if $\forall i \in N$ and $\forall t_i^\prime \in \R_+$
-		\[\Pi_i(t_i, t_{-i}) \geq \Pi_i(t_i^\prime, t_{-i})\]
+\begin{frame}{Preliminaries | Pricing competition (2\textsuperscript{nd} level)}
+	\begin{block}{Nash Equilibrium ($t^*$)}
+		A set of tolls $t^*$ is a \textit{Nash Equilibrium for the pricing game} if $\forall i \in N$ and $\forall t_i^\prime \in \R_+$
+		\[\Pi_i(t_i^*, t_{-i}^*) \geq \Pi_i(t_i^\prime, t_{-i}^*)\]
 	\end{block}
-	\begin{block}{Nash Equilibrium}
-		A given set of tolls $t$ is a \textit{Nash Equilibrium for the pricing game} if
-		$\forall i \in N$ we have $|B_i(t_{-i})| = 1$ and
-		\[t = (B_i(t_{-i}))_{i \in N}\]
+	\begin{block}{Nash Equilibrium ($t^*$)}
+		A set of tolls $t^*$ is a \textit{Nash Equilibrium for the pricing game} if
+		$\forall i \in N$ we have
+		\[t^* = (B_i(t_{-i}^*))_{i \in N}\]
 	\end{block}
@@
 
-\begin{frame}{Game equivalence}
+\begin{frame}{Preliminaries | Our model}
+	We will describe a pricing game as the tuple $\Gm = (N, \ell, \alpha)$ where
+	\begin{itemize}
+		\item $N = \{1, 2, \cdots, n\}$ the links
+		\item $\ell = (\ell_i)_{i \in N}$ the latency functions
+		\item $\alpha$ the distribution function
+	\end{itemize}
+	A homogeneous game can be described as $(N, \ell, 1)$.
+\end{frame}
+
+\subsection{Game equivalence}
+
+\begin{frame}{Preliminaries | Game equivalence}
 	\begin{definition}[Game equivalence]
 		Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
-		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
+		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+^{|N|}$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
 	\end{definition}
+	Equivalency means same tolls cause same flow.
+
 	The two pricing competition games played on two equivalent network congestion games are identical.
@@
 
-\section{Heterogeneous players}
-
-\begin{frame}{Heterogeneous players}
+\subsection{Homogeneous networks}
+
+\begin{frame}{Preliminaries | Homogeneous networks}
+	\begin{block}{Flow formula\footcite{Harks_2019}}
+		Define $N(t) = \{i \in N | x_i(t) > 0\}$.
+		For affine latency functions $\ell_i(x) = a_i x + b_i$, $a_i > 0, b_i \ge 0$ and by solving $\ell_i(x_i) + t_i = K$ with $\sum_{i \in N} x_i = 1$, calculate $K$ and get for all $i \in N$
+		\begin{equation*}
+			x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
+		\end{equation*}
+	\end{block}
+\end{frame}
+
+\begin{frame}{Preliminaries | Homogeneous networks}
+	\begin{block}{Full Wardrop support assumption}
+		$x_i(0) > 0$ for all $i \in N$
+	\end{block}
+	\begin{block}{Pricing N.E. properties\footcite{Harks_2019}}
+		$\Pi_i(t)$ is either linear or quadratic, therefore $|B_i(t_{-i})| = 1$.
+		If the \textit{full Wardrop support assumption} is satisfied then $t^*$ is unique, $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ and
+		\begin{equation*}
+			t_i^* = \left(a_i + \frac{1}{\sum_{j \ne i} \frac{1}{a_j}}\right) \cdot x_i(t^*)
+		\end{equation*}
+	\end{block}
+\end{frame}
+
+%\begin{frame}{Preliminaries | Homogeneous players | Example}
+%	\begin{example}
+%	\end{example}
+%	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
+%\end{frame}
+
+\subsection{Heterogeneous networks}
+
+\begin{frame}{Preliminaries | Heterogeneous players}
 	\begin{lemma}
@@
 
-\begin{frame}{Heterogeneous players}
+\begin{frame}{Preliminaries | Heterogeneous players}
 	Latencies are viewed the same for all players.
@@
 
+%\begin{frame}{Preliminaries | Heterogeneous players}
+%	\begin{example}
+%		Let $([2], \ell, \alpha)$ with $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and $\alpha(p) = p + 1$.
+%	\end{example}
+%	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
+%\end{frame}
+
 \section{Sensitivity split}
@@
 
-	In example ?? the users are organised around the one for which $c_1(p) = c_2(p)$.
+	In example the users are organised around the one for which $c_1(p) = c_2(p)$.
 
@@
 		\label{definition:alpha_flow_sets}
-		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ and $x(t)$ the Nash equilibrium for $t$.
-		We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
-		We define a set function $A_i: \R_+^{|N|} \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
+		Let $(N, \ell, \alpha)$.
+		We define as $A_i(t), A_i: \R_+^n \rightarrow \mathcal{P}(\R_+)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in $x(t)$.
 		\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
 	\end{definition}
-
-	Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for any $i \in N$.
 \end{frame}
@@
 	\begin{lemma}
-		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
-		Then the following hold:
+		Let $(N, \ell, \alpha)$ and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
+		Then:
 		\begin{enumerate}[(i)]
@@
 
-\begin{frame}{Sensitivity split | Limits}
-	\begin{proof}
-		$ $
-		\begin{enumerate}[(i)]
-			\item For $L = \max\{\ell_i(1) - \ell_j(0), \ell_j(1) - \ell_i(0)\}$ we find
-			\begin{flalign*}
-				\lim_{|t_i - t_j| \rightarrow +\infty}|\as^{(i, j)}(t)| &= \lim_{|t_i - t_j| \rightarrow +\infty}\frac{|\ell_i(x_i(t)) - \ell_j(x_j(t))|}{|t_i - t_j|}\\
-				&\le \lim_{|t_i - t_j| \rightarrow +\infty}\frac{L}{|t_i - t_j|} = 0
-			\end{flalign*}
-		\end{enumerate}
-	\end{proof}
-\end{frame}
-
-\begin{frame}{Sensitivity split | Limits}
-	\begin{proof}
-		$ $
-		\begin{enumerate}[(ii)]
-			\item ...
-		\end{enumerate}
-	\end{proof}
-\end{frame}
-
 \begin{frame}{Sensitivity split}
@@
 	\end{theorem}
-\end{frame}
-
-\begin{frame}{Sensitivity split | Upper bound}
-	\begin{proof}
-		...
-	\end{proof}
 \end{frame}
@@
 
-\begin{frame}{Heterogeneous Pricing Games}
-	Zero money sensitivity creates issues.
+\begin{frame}{Pseudo-heterogeneous Pricing Games}
+	Consider distribution functions $\alpha(p) = c$ for some $c > 0$.
+
+	Players again all view link costs the same.
+	\[c_i(p) = \ell_i(x_i) + c t_i\]
+	Behaviour should be homogeneous with tolls "mapped" to $t \rightarrow t/c$.
+
+	Also note that 
+	\[c_i(p) = c \left(\frac1c \ell_i(x_i) + t_i\right)\]
+	where $\frac1c \ell_i(x_i) = \frac{a_i}{c} x_i + \frac{b_i}{c}$ affine.
+\end{frame}
+
+\begin{frame}{Pseudo-heterogeneous Pricing Games}
 	\begin{lemma}
-		Let $(N, \ell, \alpha)$ where $\exists \epsilon > 0: \alpha(p) = 0 \; \forall p < \epsilon$.
-		Let $i \in N$ be a link for which $\ell_i(0) = \min_{j \in N} \ell_i(0)$.
-		Then $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{|N| - 1}$.
+		Let $\Gm_1 = (N, \ell^{(1)}, \alpha)$ where $\forall p \in [0, 1] \; \alpha(p) = c$ for some $c \in \R_+$ and $\Gm_2 = (N, \ell^{(2)}, 1)$ where $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
+		Then the two games are equivalent.
 	\end{lemma}
 	\begin{proof}
-		$\ell_i(0) = \min_{j \in N} \ell_i(0)$, ensures link $i$ will always have flow
-
-		$i$ can select $t_i > \max t_{-i}$ to make link $i$ the lowest-latency link, populated exclusively by players with $\alpha(p) = 0$
-
-		We fix $t_i^\prime$ and we see that
+		For any $t \in \R_+^n$ and any flow $x_i$
 		\[
-			\lim_{t_i \rightarrow +\infty} \Pi_i(t_i, t_{-i}) \ge \lim_{t_i \rightarrow +\infty} x_i^\prime(t_i^\prime, t_{-i})t_i = +\infty
+			\sum_{i \in N} \left(\ell_i^{(1)}(x_i^{(2)}(t)) + c t_i\right) \left(x_i^{(2)}(t) - x_i\right) \leq 0
 		\]
-		making in turn $B_i(t_{-i}) = +\infty$.
+		$x^{(2)}(t)$ is the unique N.E. for $t$ in $\Gm_1$ so $x^{(1)}(t) = x^{(2)}(t)$.
 	\end{proof}
+	Costs are proportional.
 \end{frame}
@@
 \begin{frame}{Pseudo-heterogeneous Pricing Games}
-	Consider cases where $\alpha(p) = c$ for some $c \in \R_+$.
+	We will call such games \textit{pseudo-heterogeneous}.
+
+	Uniform increase in money-sensitivity is equivalent to uniform decrease in latencies (lost for general $\alpha$ functions).
+
+	\begin{lemma}
+		Let $\Gm_1 = \left(N, \frac{\ell}{c_1}, 1\right), \Gm_2 = \left(N, \frac{\ell}{c_2}, 1\right)$.
+		Then $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$.
+	\end{lemma}
+	\begin{proof}
 		\[
-		\sum_{i \in N} (\ell(x_i(t)) + c t_i) \cdot (x_i(t) - x_i) \leq 0
+			\begin{aligned}[t]
+				&\sum_{i \in N} \left(\frac{1}{c_1}\ell_i(x_i^{(1)}(c_2 t)) + c_2 t_i\right) \left(x_i^{(1)}(c_2 t) - x_i\right) \le 0\\
+				\Leftrightarrow &\sum_{i \in N} \left(\frac{1}{c_2}\ell_i(x_i^{(1)}(c_2 t)) + c_1 t_i\right) \left(x_i^{(1)}(c_2 t) - x_i\right) \le 0
+			\end{aligned}
 		\]
-
+	\end{proof}
+\end{frame}
+
+\begin{frame}{Pseudo-heterogeneous Pricing Games}
 \begin{lemma}
-		Let $\Gm_1 = (N, \ell^{(1)}, c)$ a heterogeneous pricing game with distribution function $\alpha(p) = c$ for some $c > 0$ and $\Gm_2 = (N, \ell^{(2)}, 1)$ a homogeneous pricing game with latencies $\ell^{(2)} = \frac{\ell^{(1)}}{c}$ for the same $c$.
-		Then the two games are equivalent.
-	\end{lemma}
-	We will call such games \textit{pseudo-heterogeneous}.
-
-	Latency-sensitivity relation is lost for general $\alpha$
+	Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$, $c_1, c_2 > 0$.
+	Then
+	\begin{enumerate}[$(i)$]
+		\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
+		\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
+		\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
+	\end{enumerate}
+\end{lemma}
+\begin{proof}
+	\begin{enumerate}[$(i)$]
+		\item Consider $\Gm_3 = (N, \ell/c_1, 1), \Gm_4 = (N, \ell/c_2, 1)$.\\
+		Then $x^{(1)}(c_2 t) = x^{(3)}(c_2 t) = x^{(4)}(c_1 t) = x^{(2)}(c_1 t)$.
+		\item and $(iii)$ follow from definitions.
+		\vspace{-20pt}
+	\end{enumerate}
+\end{proof}
+\end{frame}
+
+\begin{frame}{Pseudo-heterogeneous Pricing Games}
+	\begin{lemma}
+		Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$, $c_1, c_2 > 0$.
+		Then
+		\begin{enumerate}[$(i)$]
+			\item $x^{(1)}(t) = x^{(2)}\left(\frac{c_1}{c_2} t\right)$
+			\item $\Pi_i^{(1)}(t) = \frac{c_2}{c_1} \Pi_i^{(2)}\left(\frac{c_1}{c_2} t\right)$
+			\item $B_i^{(1)}(t_{-i}) = \frac{c_2}{c_1} B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i}\right)$
+		\end{enumerate}
+	\end{lemma}
 \end{frame}
@@
 		\centering
-		\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
+		\begin{tikzpicture}[x=3cm, y=3cm, every node/.style={font=\small}]
 			% Axes
@@
 			\draw (0,1) -- (0.05,1) node[right] {$1$};
-			\draw (0,2/3) -- (-0.05,2/3) node[left] {$\frac23$};
+			\draw (0,2/3) -- (-0.05,2/3) node[below=4,left] {$\frac23$};
 
 			% Flow function graphs
-			\draw[thick, blue!33] (-1,1) -- (2,0) node[above, black] {$\alpha = 1$};
-			\draw[thick, blue!66] (-1/3,1) -- (2/3,0) node[above right, black] {$\alpha = 3$};
+			\draw[thick, blue!33] (-1,1) -- (2,0) node[above=20,left=5,black] {$\alpha = 1$};
+			\draw[thick, blue!66] (-1/3,1) -- (2/3,0) node[above right,black] {$\alpha = 3$};
 			\draw[thick, blue!100] (-1/4,1) -- (2/4,0) node[black] at (0.2,0.17) {$\alpha = 4$};
+
+			% Example graph in corner
+			\begin{scope}[shift={(1.5,1)},scale=0.2]
+				% Nodes
+				\node[circle, draw, fill=blue!20, minimum size=0.4cm] (s) at (0,0) {$s$};
+				\node[circle, draw, fill=blue!20, minimum size=0.4cm] (t) at (4,0) {$t$};
+
+				% Links
+				\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+				\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
+			\end{scope}
 		\end{tikzpicture}
@@
 	\begin{lemma}
-		Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with $\alpha^{(1)}(p) = c_1 > 0$, $\alpha^{(2)}(p) = c_2 > 0$, then
-		\begin{enumerate}[$(i)$]
-			%\item $x^{(1)}(0) = x^{(2)}(0)$
-			\item $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$
-			\item $\frac{\Pi_i^{(1)}(c_2 t)}{\Pi_i^{(2)}(c_1 t)} = \frac{c_2}{c_1}$
-			\item $\frac{B_i^{(1)}(c_2t_{-i})}{B_i^{(2)}(c_1 t_{-i})} = \frac{c_2}{c_1}$
-		\end{enumerate}
-	\end{lemma}
-\end{frame}
-
-\begin{frame}{Pseudo-heterogeneous Pricing Games}
-	\begin{lemma}
-		Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$ two heterogeneous pricing games with $\alpha^{(1)}(p) = c_1 > 0$, $\alpha^{(2)}(p) = c_2 > 0$.\\
-		Let $t^{*(1)}, t^{*(2)}$ the Nash Equilibria for the pricing games in $\Gm_1$ and $\Gm_2$.
+		Let $\Gm_1 = (N, \ell, c_1)$ and $\Gm_2 = (N, \ell, c_2)$, $c_1, c_2 > 0$.
 		Then
 		\begin{enumerate}[$(i)$]
-			\item $\frac{t^{*(1)}}{t^{*(2)}} = \frac{c_2}{c_1}$
+			\item $t^{*(1)} = \frac{c_2}{c_1} t^{*(2)}$
 			\item $x^{(1)}(t^{*(1)}) = x^{(2)}(t^{*(2)})$
@@
 	\end{lemma}
-	Nash Equilibrium always at the same flow.
+	\begin{proof}
+		\begin{enumerate}[$(i)$]
+			% https://tex.stackexchange.com/a/98399
+			\item
+			$\begin{aligned}[t]
+				t_i^{*(1)} &= B_i^{(1)}(t_{-i}^{*(1)}) \Leftrightarrow \cdots \Leftrightarrow \frac{c_1}{c_2} t_i^{*(1)} = B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i}^{*(1)}\right)
+			\end{aligned}$
+			\item follows from previous lemma.
+			\vspace{-20pt}
+		\end{enumerate}
+	\end{proof}
+	Pricing Nash Equilibrium is always at the same flow.
 \end{frame}
@@
 \section{Step distribution functions}
+
+\begin{frame}{Heterogeneous Pricing Games}
+	Zero money-sensitivity creates issues as it can be exploited.
+	\begin{lemma}
+		Let $(N, \ell, \alpha)$ where $\alpha(p) = 0$ for $p \in [0, \epsilon]$ for some $\epsilon > 0$.\\
+		Then $\exists i \in N$ where $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{n - 1}$.
+	\end{lemma}
+	\begin{proof}
+		Links with $\ell_i(0) = \min_{j \in N} \ell_i(0)$ can select $t_i > \max t_{-i}$ and become the lowest-latency link, with players $\alpha(p) = 0$.
+
+		Those players will never leave as $t_i \rightarrow +\infty$, making $x_i$ fixed and therefore $\lim_{t_i \rightarrow +\infty} \Pi_i(t_i, t_{-i}) = +\infty$.
+	\end{proof}
+\end{frame}
 
@@
 
-	In $2$-link games, $\as(t)^{(1, 2)} = \as(t)$.
-
-	There always exists an $\alpha$ value for which the two link costs are equal.
+	In $2$-link games:
+	\begin{itemize}
+		\item $\as^{(1, 2)}(t) = \as(t)$
+		\item There always exists an $\alpha$ for which all link costs are equal.
+	\end{itemize}
 \end{frame}
@@
 	\begin{lemma}
-		Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$ a heterogeneous game, $t \ne 0$ a given set of tolls and $x^{(1)}(t)$ the Nash equilibrium for $t$.
-		Now let $\Gm_2 = ([2], \ell, \as^{(1)}(t))$ a pseudo-heterogeneous game with latency functions the same as $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as^{(1)}(t)$.
+		Let $\Gm_1 = ([2], \ell, \alpha^{(1)})$, fixed tolls $t \ne 0$ and $\Gm_2 = ([2], \ell, \alpha^{(2)})$ with fixed $\alpha^{(2)}(p) = \as^{(1)}(t)$.
 		Then
@@
 	\begin{example}
-		Let $([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
-		\begin{align*}
+		Let $([2], \ell, \alpha)$ with
+		$
 			\alpha(p) =
@@
 				4 & p \ge \tfrac12
-			\end{cases}&
-		\end{align*}
+			\end{cases}
+		$
 	\end{example}
@@
 			% Left Column: Network Graph
-			\begin{tikzpicture}[scale=1.4, every node/.style={font=\small}]
+			\begin{tikzpicture}[scale=1, baseline=50pt, every node/.style={font=\small}]
 				% Nodes
@@
 				\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
-
-				% Description
-				\node[align=center] at (2, -2) {Network of Example};
 			\end{tikzpicture}
@@
 				% Closed / Open dots
-				\fill[white] (0.2,1) ellipse (0.014 and 0.06);
+				\fill[black] (0.2,1) ellipse (0.014 and 0.06);
 				\draw[black] (0.2,1) ellipse (0.014 and 0.06);
-				\fill[black] (0.2,3) ellipse (0.014 and 0.06);
+				\fill[white] (0.2,3) ellipse (0.014 and 0.06);
 				\draw[black] (0.2,3) ellipse (0.014 and 0.06);
-				\fill[black] (0.5,3) ellipse (0.014 and 0.06);
+				\fill[white] (0.5,3) ellipse (0.014 and 0.06);
 				\draw[black] (0.5,3) ellipse (0.014 and 0.06);
-				\fill[white] (0.5,4) ellipse (0.014 and 0.06);
+				\fill[black] (0.5,4) ellipse (0.014 and 0.06);
 				\draw[black] (0.5,4) ellipse (0.014 and 0.06);
-
-				% Description
-				\node[align=center] at (0.7, -1.7) {Distribution function of Example};
 			\end{tikzpicture}
@@
 		\centering
-		\begin{tikzpicture}[x=3.4cm, y=1cm, every node/.style={font=\small}]
-			% Axes
-			\draw[->] (0,0) -- (-1.1,0);
-			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
-			\draw[->] (0,0) -- (0,4.4) node[above] {$\as(t)$};
-
-			% Tick marks
-			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
-			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
-			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
-			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
-			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
-			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
-			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
-			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
-			\draw (2,0) -- (2,-0.05) node[below] {$2$};
-			\draw (0,1) -- (-0.05,1) node[left] {$1$};
-			\draw (0,3) -- (0.05,3) node[right] {$3$};
-			\draw (0,4) -- (-0.05,4) node[left] {$4$};
-
-			% Function graph
-			% Left side
-			\draw[thick] (-1,1) -- (-2/5,1);
-			\draw[thick] (-2/5,1) -- (-2/15,3);
-			\draw[thick] (-2/15,3) -- (0,3);
-			% Right side
-			\draw[thick] (0,4) -- (1/8,4);
-			\draw[thick] (1/8,4) -- (1/6,3);
-			\draw[thick] (1/6,3) -- (7/15,3);
-			\draw[thick] (7/15,3) -- (7/5,1);
-			\draw[thick] (7/5,1) -- (2,1);
-
-			% Dots
-			\fill[white] (0,3) ellipse (0.02 and 0.066);
-			\draw[black] (0,3) ellipse (0.02 and 0.066);
-			\fill[white] (0,4) ellipse (0.02 and 0.066);
-			\draw[black] (0,4) ellipse (0.02 and 0.066);
-		\end{tikzpicture}
-		\caption{Split function of Example}
-		\label{figure:alpha_step:split}
-	\end{figure}
-\end{frame}
-
-\begin{frame}{Step distribution functions}
-	\begin{figure}
-		\centering
-		\begin{tikzpicture}[x=3.4cm, y=3.4cm, every node/.style={font=\small}]
+		\begin{tikzpicture}[x=3cm, y=3cm, every node/.style={font=\small}]
 			% Axes
@@
 \begin{frame}{Step distribution functions}
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[x=3.4cm, y=1cm, scale=0.8, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-1.1,0);
+			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+			\draw[->] (0,0) -- (0,4.4) node[above] {$\as(t)$};
+
+			% Tick marks
+			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
+			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
+			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
+			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
+			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
+			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
+			\draw (2,0) -- (2,-0.05) node[below] {$2$};
+			\draw (0,1) -- (-0.05,1) node[left] {$1$};
+			\draw (0,3) -- (0.05,3) node[right] {$3$};
+			\draw (0,4) -- (-0.05,4) node[left] {$4$};
+
+			% Function graph
+			% Left side
+			\draw[thick] (-1,1) -- (-2/5,1);
+			\draw[thick] (-2/5,1) -- (-2/15,3);
+			\draw[thick] (-2/15,3) -- (0,3);
+			% Right side
+			\draw[thick] (0,4) -- (1/8,4);
+			\draw[thick] (1/8,4) -- (1/6,3);
+			\draw[thick] (1/6,3) -- (7/15,3);
+			\draw[thick] (7/15,3) -- (7/5,1);
+			\draw[thick] (7/5,1) -- (2,1);
+
+			% Dots
+			\fill[white] (0,3) ellipse (0.02 and 0.066);
+			\draw[black] (0,3) ellipse (0.02 and 0.066);
+			\fill[white] (0,4) ellipse (0.02 and 0.066);
+			\draw[black] (0,4) ellipse (0.02 and 0.066);
+		\end{tikzpicture}
+		\caption{Split function of Example}
+		\label{figure:alpha_step:split}
+	\end{figure}
+\end{frame}
+
+\begin{frame}<presentation:0>[noframenumbering]{Step distribution functions}
 	Notice that when $x_1$ is fixed then $\as$ isn't and vice-versa.\\
@@
 \begin{frame}{Step distribution functions}
+	Let $\Gm_1 = ([2], \ell, \alpha)$ where $\alpha = (\alpha_k)_{k \in [m]}$.
+	\begin{lemma}
+		Let $t \ne 0$ where all players with $\alpha(p) = \alpha_k$ are using the same link for all $k \in [m]$.
+		Then $t$ is not a Nash equilibrium for the pricing game.
+	\end{lemma}
 	\begin{theorem}
-		Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
-		If $\Gm_1$ has a Nash equilibrium for the pricing game at toll $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ a pseudo-heterogeneous game with latency functions the same as the ones in $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as(t^*)$.
+		If $\Gm_1$ has $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ with fixed $\alpha^{(2)}(p) = \as(t^*)$.
 		Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
@@
 		\end{align*}
-		Then $\Gm$ has a Nash Equilibrium for the pricing game at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+		Then $\Gm$ has a N.E. for the pricing game at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
 	\end{example}
@@
 		\centering
-		\begin{tikzpicture}[x=8cm, y=10cm, every node/.style={font=\small}]
+		\begin{tikzpicture}[x=8cm, y=10cm, scale=0.7, every node/.style={font=\small}]
 			% Axes
@@
 		\end{tikzpicture}
-		\\[15pt]
-		\begin{tikzpicture}[x=10cm, y=15cm, every node/.style={font=\small}]
+		\begin{tikzpicture}[x=10cm, y=15cm, scale=0.7, every node/.style={font=\small}]
 			% Axes
@@
 		\end{align*}
-		Then $\Gm$ has no Nash Equilibrium for the pricing game.
+		Then $\Gm$ has no N.E. for the pricing game.
 	\end{example}
@@
 		\centering
-		\begin{tikzpicture}[x=6cm, y=10cm, every node/.style={font=\small}]
+		\begin{tikzpicture}[x=6cm, y=10cm, scale=0.7, every node/.style={font=\small}]
 			% Axes
@@
 		\end{tikzpicture}
-		\\[15pt]
-		\begin{tikzpicture}[x=8cm, y=15cm, every node/.style={font=\small}]
+		\begin{tikzpicture}[x=8cm, y=15cm, scale=0.7, every node/.style={font=\small}]
 			% Axes
@@
 
-\begin{frame}{Step distribution functions}
-	\begin{lemma}
-		Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}, \; m \in N$.
-		Also let $t \ne 0$ a set of tolls for which it holds for all $k \in [m]$ that all players $p$ with $\alpha(p) = \alpha_k$ are using the same link.
-		Then $t$ is not a Nash equilibrium for the pricing game.
-	\end{lemma}
-\end{frame}
-
-\begin{frame}{Step distribution functions}
-	\begin{theorem}
-		Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous pricing game where $\alpha$ is a step function with values $(\alpha_k)_{k \in [m]}$.
-		If $\Gm_1$ has a Nash equilibrium for the pricing game at toll $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ a pseudo-heterogeneous game with latency functions the same as the ones in $\Gm_1$ and fixed distribution function $\alpha^{(2)}(p) = \as(t^*)$.
-		Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
-	\end{theorem}
-\end{frame}
-
-\begin{frame}{Step distribution function}
-	Summary of Algorithm
-	For a given heterogeneous pricing game $\Gm = ([2], \ell, \alpha)$
+\subsection*{Pricing N.E. Algorithm}
+
+\begin{frame}{Step distribution functions | Pricing N.E. Algorithm}
+	\textbf{Summary:} Given $\Gm = ([2], \ell, \alpha), \alpha = (\alpha_k)_{k \in [m]}$
 	\begin{enumerate}
-		\item Consider $\Gm^\prime = ([2], \ell, 1)$ and calculate its pricing Nash equilibrium $t^{*\prime}$ and respective flow $x^\prime(t^{*\prime})$.
-		\item Calculate $\as(t^*)$ as the $\alpha$ value of the lower split flow in $x^\prime(t^{*\prime})$ (valid since $x(t^*) = x^\prime(t^{*\prime})$ from Theorem \ref{theorem:a_step_ne_equiv_fixed}, Lemma \ref{lemma:a_fixed_pricing_ne_relation})
-		\item Calculate the candidate pricing Nash Equilibrium $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$ as well as the respective profits $\Pi_1(t^*), \Pi_2(t^*)$.
-		\item For each $\alpha_k$, value of $\alpha$ different than $\as(t^*)$, and for each link operator $i \in [2]$
+		\item Consider $\Gm^\prime = ([2], \ell, 1)$ and calculate $t^{*\prime}, x^\prime(t^{*\prime})$.
+		\item Calculate $\as(t^*)$ as the $\alpha$ value of the lower split flow in $x^\prime(t^{*\prime})$
+		\item Calculate the candidate $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$ and $\Pi_1(t^*), \Pi_2(t^*)$.
+		\item For each $\alpha_k \ne \as(t^*)$, and for each $i \in [2]$
 		\begin{enumerate}[$4.1$]
-			\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i}^*)$ as well as the tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
+			\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i}^*)$ and tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
 			\item Search for $\Pi_{i, k}$, the max profit for $i$ within those $t_i$ ranges:
 			\begin{enumerate}[$4.2.1$]
-				\item If $B_{i, k}(t_{-i}^*)$ is within the $t_i$ ranges, then $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}^*), t_{-i}^*)$.
-				\item Otherwise, $\Pi_{i, k}$ is the highest profit value among the ($4$) tolls in the edges of the two $t_1$ ranges.
+				\item If $B_{i, k}(t_{-i}^*)$ is within the $t_i$ ranges, $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}^*), t_{-i}^*)$.
+				\item Otherwise, $\Pi_{i, k}$ is max profit among the ranges' edge tolls ($4$).
 			\end{enumerate}
@@
 		\end{enumerate}
-		\item If all of the above checks fail, then $t^*$ is the Nash Equilibrium for the pricing game in $\Gm$, so return it.
-	\end{enumerate}
+		\item If all of the above checks fail, return $t^*$.
+	\end{enumerate}
+	\textbf{Complexity:} $\mathcal{O}(m)$
 \end{frame}
@@
 \section{Future work}
+
+\begin{frame}{Conclusion}
+	In our work
+	\begin{itemize}
+		\item Investigated heterogeneity by defining and analysing $\as$
+		\item Developed a connection between different fixed distribution functions
+		\item Developed an algorithm for $2$-link step distribution functions
+	\end{itemize}
+\end{frame}
 

### 2025-02-09 thesis/slides.tex
Thesis: Pres: Improvements, examples and graphs for Sensitivity Split section

@@
 \begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
-	Tolls $t \in \R_+^{|N|}$ can be assigned to links, affecting player cost.
+	Tolls $t \in \R_+^n$ can be assigned to links, affecting player cost.
 
@@
 \end{center}
-For homogeneous players and tolls $t = \left(4, 2, 1\right)$ we get
-\[x(t) = \left(0, \frac12, \frac12\right)\]
-since $\forall p \in [0, 1]$ it holds $c_2(p) = c_3(p) = 7/2$ and $c_1(p) = 4$.
+For homogeneous players and tolls $t = (3, 2, 1)$
+\[x(t) = \left(\frac15, \frac25, \frac25\right)\]
+since $\ell_2(1/2) + t_2 = \ell_3(1/2) + t_3 = 7/2$ and $\ell_1(0) + t_1 = 4$.
 \end{frame}
@@
 	\begin{block}{Profit}
-		For given set of tolls $t \in \R_+^{|N|}$, link operator $i$ gains profit
+		For given set of tolls $t \in \R_+^n$, link operator $i$ gains profit
 		\[\Pi_i(t) = x_i(t) \cdot t_i\]
@@
 
-\subsection{Heterogeneous networks}
-
-\begin{frame}{Preliminaries | Heterogeneous players}
-	\begin{lemma}
-		For $\Gm = (N, \ell, \alpha)$ with tolls $t$ and flow $x(t)$ the Nash equilibrium for $t$, it holds for all $i, j \in N$ with $x_i(t), x_j(t) > 0$ that
-		\begin{enumerate}[(i)]
-			\item $\ell_i(x_i(t)) < \ell_j(x_j(t))$ iff $t_i > t_j$
-			\item $\ell_i(x_i(t)) = \ell_j(x_j(t))$ iff $t_i = t_j$
-			\item $\ell_i(x_i(t)) > \ell_j(x_j(t))$ iff $t_i < t_j$
-		\end{enumerate}
-	\end{lemma}
-	\begin{proof}
-		Assume $\ell_i(x_i(t)) < \ell_j(x_j(t))$ and $t_i < t_j$ for some $i, j \in N$.
-		Then for \textbf{all} players $c_i(p) < c_j(p)$ so $x_j(t) > 0$ is a contradiction.
-	\end{proof}
-\end{frame}
-
-\begin{frame}{Preliminaries | Heterogeneous players}
-	Latencies are viewed the same for all players.
-
-	Toll order is the same for all players.
-
+\section{Sensitivity split}
+
+\begin{frame}{Sensitivity split | Heterogeneous networks}
+	\begin{center}
+		\begin{multicols}{2}
+			% Left Column: Network Graph
+			\begin{tikzpicture}[scale=1.2, baseline=40pt, every node/.style={font=\small}]
+				% Nodes
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
+
+				% Links
+				\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+				\draw[->, thick] (s) to node[midway, above] {$x + 1$} (t);
+				\draw[->, thick] (s) to[bend right=35] node[midway, above] {$x + 2$} (t);
+			\end{tikzpicture}
+
+			% Right Column: Distribution function Graph
+			\begin{tikzpicture}[x=2.5cm, y=1.2cm, every node/.style={font=\small}]
+				% Axes
+				\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
+				\draw[->] (0,0) -- (0,2.2) node[above] {$\as(p)$};
+
+				% Tick marks
+				\draw (0,0) -- (0,-0.05) node[below] {$0$};
+				\draw (1,0) -- (1,-0.05) node[below] {$1$};
+				\draw (0,1) -- (-0.05,1) node[left] {$1$};
+				\draw (0,2) -- (-0.05,2) node[left] {$2$};
+
+				% Function graph
+				\draw[thick] (0,1) -- (1,2);
+
+				% Description
+				\node[align=center] at (0.7, -0.8) {$\alpha(p) = p + 1$};
+			\end{tikzpicture}
+		\end{multicols}
+	\end{center}
+	For heterogeneous players with $\alpha(p) = p + 1$ and tolls $t = (3, 2, 1)$
+	\[x(t) = \left(\frac{1}{11}, \frac{3}{11}, \frac{7}{11}\right)\]
+\end{frame}
+
+\tikzset{
+	fixed_height/.style={
+		inner sep=0,
+		outer sep=0,
+		minimum height=15pt,
+		align=center
+	}
+}
+
+\begin{frame}{Sensitivity split | Heterogeneous networks}
+	Latencies are the same for all players.
+
+	Toll ordering is the same for all players.
+
+	Toll differences are viewed with different scaling.
+	\\[15pt]
+	\begin{tikzpicture}
+		% Title
+		\node[above,fixed_height] at (3.7,3.3) {$\alpha(0) = 1$};
+
+		% Axes
+		\draw[->] (0,0) -- (7,0) node[right=5,fixed_height] {$c\left(0\right)$};
+		\draw[-] (0,0) -- (0,3.2);
+
+		% Y-bars: Latencies
+		\node[left] at (0,2.5) {$\frac{2}{11}$};
+		\node[left] at (0,1.5) {$\frac{14}{11}$};
+		\node[left] at (0,0.5) {$\frac{29}{11}$};
+		\filldraw[fill=blue!20] (0,2.25) rectangle (2/11,2.75);
+		\filldraw[fill=blue!20] (0,1.25) rectangle (14/11,1.75);
+		\filldraw[fill=blue!20] (0,0.25) rectangle (29/11,0.75);
+
+		% Y-bars: Tolls
+		\filldraw[fill=orange!20] (2/11,2.25) rectangle (35/11,2.75) node[below right] {$3$};
+		\filldraw[fill=orange!20] (14/11,1.25) rectangle (36/11,1.75) node[below right] {$2$};
+		\filldraw[fill=orange!20] (29/11,0.25) rectangle (40/11,0.75) node[below right] {$1$};
+	\end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Heterogeneous networks}
+	Latencies are the same for all players.
+
+	Toll ordering is the same for all players.
+
+	Toll differences are viewed with different scaling.
+	\\[15pt]
+	\begin{tikzpicture}
+		% Title
+		\node[above,fixed_height] at (3.7,3.3) {$\alpha\left(\frac{2}{11}\right) = \frac{13}{11}$};
+
+		% Axes
+		\draw[->] (0,0) -- (7,0) node[right=5,fixed_height] {$c\left(\frac{2}{11}\right)$};
+		\draw[-] (0,0) -- (0,3.2);
+
+		% Y-bars: Latencies
+		\node[left] at (0,2.5) {$\frac{2}{11}$};
+		\node[left] at (0,1.5) {$\frac{14}{11}$};
+		\node[left] at (0,0.5) {$\frac{29}{11}$};
+		\filldraw[fill=blue!20] (0,2.25) rectangle (2/11,2.75);
+		\filldraw[fill=blue!20] (0,1.25) rectangle (14/11,1.75);
+		\filldraw[fill=blue!20] (0,0.25) rectangle (29/11,0.75);
+
+		% Y-bars: Tolls
+		\filldraw[fill=orange!20] (2/11,2.25) rectangle (41/11,2.75) node[below right] {$\frac{39}{11}$};
+		\filldraw[fill=orange!20] (14/11,1.25) rectangle (40/11,1.75) node[below right] {$\frac{26}{11}$};
+		\filldraw[fill=orange!20] (29/11,0.25) rectangle (42/11,0.75) node[below right] {$\frac{13}{11}$};
+	\end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Heterogeneous networks}
+	Latencies are the same for all players.
+
+	Toll ordering is the same for all players.
+
+	Toll differences are viewed with different scaling.
+	\\[15pt]
+	\begin{tikzpicture}
+		% Title
+		\node[above,fixed_height] at (3.7,3.3) {$\alpha(1) = 2$};
+
+		% Axes
+		\draw[->] (0,0) -- (7,0) node[right=5,fixed_height] {$c\left(1\right)$};
+		\draw[-] (0,0) -- (0,3.2);
+
+		% Y-bars: Latencies
+		\node[left] at (0,2.5) {$\frac{2}{11}$};
+		\node[left] at (0,1.5) {$\frac{14}{11}$};
+		\node[left] at (0,0.5) {$\frac{29}{11}$};
+		\filldraw[fill=blue!20] (0,2.25) rectangle (2/11,2.75);
+		\filldraw[fill=blue!20] (0,1.25) rectangle (14/11,1.75);
+		\filldraw[fill=blue!20] (0,0.25) rectangle (29/11,0.75);
+
+		% Y-bars: Tolls
+		\filldraw[fill=orange!20] (2/11,2.25) rectangle (64/11,2.75) node[below right] {$6$};
+		\filldraw[fill=orange!20] (14/11,1.25) rectangle (58/11,1.75) node[below right] {$4$};
+		\filldraw[fill=orange!20] (29/11,0.25) rectangle (51/11,0.75) node[below right] {$2$};
+	\end{tikzpicture}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Heterogeneous networks}
 	Tolls define an ordering of the $N$ links where
@@
 
-%\begin{frame}{Preliminaries | Heterogeneous players}
-%	\begin{example}
-%		Let $([2], \ell, \alpha)$ with $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and $\alpha(p) = p + 1$.
-%	\end{example}
-%	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
-%\end{frame}
-
-\section{Sensitivity split}
-
-\begin{frame}{Sensitivity split}
-	In a heterogeneous game, in practice, each flow user plays a different game.
-
-	In example the users are organised around the one for which $c_1(p) = c_2(p)$.
-
+\begin{frame}{Sensitivity split | Heterogeneous networks}
+	For any pair of links $i, j$
+	\begin{align*}
+		c_i(&p) \le c_j(p) & c_i(p) \ge c_i(p&) \\[10pt]
+		\alpha(p) \le &\frac{\ell_j(x_j) - \ell_i(x_i)}{t_i - t_j} & \frac{\ell_j(x_j) - \ell_i(x_i)}{t_i - t_j}& \le \alpha(p)
+	\end{align*}
 	We need the notion of the money-sensitivity value for which two link costs are equal.
@@
 	\begin{definition}
-		Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
-		We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^N|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
+		Let $(N, \ell, \alpha)$, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$.
+		We define the \textit{money sensitivity split function} for $i, j$ $\as^{(i, j)}: \{t \in \R_+^n|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
 		\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
@@
 \begin{frame}{Sensitivity split}
-	If $t_i \ne t_j$ then assume w.l.o.g. $t_i > t_j \Leftrightarrow \ell_i(x_i) < \ell_j(x_j)$.\\
-	Low money-sensitive players will use link $i$.\\
-	High money-sensitive players will use link $j$.
-
 	\begin{table}[h!]
@@
 	\begin{definition}
-		\label{definition:alpha_flow_sets}
 		Let $(N, \ell, \alpha)$.
@@
 
-\begin{frame}{Sensitivity split}
+\begin{frame}{Sensitivity split | Properties}
 	\begin{lemma}
-		Let $(N, \ell, \alpha)$ and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
-		Then:
+		Let $(N, \ell, \alpha)$ and tolls $t$ where for $i, j \in N$ $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$.
 		\begin{enumerate}[(i)]
@@
 			\item $\as^{(i, j)}(t) \in [\alpha(0), \alpha(1)]$
-			%\item if $\as^{(i, j)}(t) < \alpha(0)$ (or $\as^{(i, j)}(t) > \alpha(1)$) then $x(t) = (0, 1)$ (or $(1, 0)$)
 			\item if $\ell_i(x_i(t)) < \ell_j(x_j(t))$ then
@@
 
-\begin{frame}{Sensitivity split | Monotonicity}
-	\begin{lemma}
-		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t, t^\prime$ such that for some links $i, j \in N$ it holds that $t_i \ne t_j, t_i^\prime \ne t_j^\prime$ and $t_k = t_k^\prime$ $\forall k \in N \setminus \{i, j\}$.
-		If $x_i(t), x_j(t), x_i(t^\prime), x_j(t^\prime) > 0$ and $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0$, then:
+\begin{frame}{Sensitivity split | Properties}
+	\begin{lemma}[Monotonicity]
+		Let $t, t^\prime$ different only for $i, j \in N$ with the same toll ordering and $x_i(t), x_j(t), x_i(t^\prime), x_j(t^\prime) > 0$.
+		Then
 		\begin{enumerate}[(i)]
@@
 
-\begin{frame}{Sensitivity split | Monotonicity}
-	\begin{proof}
-		We prove $(i)$ and $(ii)$ follows symmetrically.\\
-		If $x(t) = x(t^\prime)$ then the property follows from the definition of $\as$.
-		If $x(t) \ne x(t^\prime)$ then assume w.l.o.g. that $x_i(t) > x_i(t^\prime)$, so a player $p$ moved from $i$ to $j$ between $t$ and $t^\prime$.
-		\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
-		Applying the previous lemma gives us
-		\[\as^{(i, j)}(t^\prime) \le \inf A_j(t^\prime) \le \sup A_i(t) \le \as^{(i, j)}(t)\]
-	\end{proof}
-\end{frame}
-
-\begin{frame}{Sensitivity split | Limits}
-	\begin{lemma}
-		Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t$ where $t_i \ne t_j$ and $x_i(t), x_j(t) > 0$ for some links $i, j \in N$.
+\begin{frame}{Sensitivity split | Properties}
+	\begin{lemma}[Limit values]
+		Let $(N, \ell, \alpha)$.
 		Then:
@@
 			\item
-			\begin{flalign*}
-				\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) &= 0 &
-			\end{flalign*}
+			$\begin{aligned}[t]
+				\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) = 0
+			\end{aligned}$
 			\item
-			\begin{flalign*}
-				\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \limsup_{t_i - t_j \rightarrow 0^+} A_i(t) &
-			\end{flalign*}
+			$\begin{aligned}[t]
+				\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) = \limsup_{t_i - t_j \rightarrow 0^+} A_i(t)
+			\end{aligned}$
 		\end{enumerate}
 	\end{lemma}
-\end{frame}
-
-\begin{frame}{Sensitivity split}
+	\begin{corollary}
+		$\begin{aligned}[t]
+			\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) = \alpha(x_i(0))
+		\end{aligned}$
+	\end{corollary}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Properties}
+	\begin{center}
+		\begin{multicols}{2}
+			% Left Column: Network Graph
+			\begin{tikzpicture}[scale=1.2, baseline=40pt, every node/.style={font=\small}]
+				% Nodes
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
+
+				% Links
+				\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+				\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
+			\end{tikzpicture}
+
+			% Right Column: Distribution function Graph
+			\begin{tikzpicture}[x=2.5cm, y=1.2cm, every node/.style={font=\small}]
+				% Axes
+				\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
+				\draw[->] (0,0) -- (0,2.2) node[above] {$\as(p)$};
+
+				% Tick marks
+				\draw (0,0) -- (0,-0.05) node[below] {$0$};
+				\draw (1,0) -- (1,-0.05) node[below] {$1$};
+				\draw (0,1) -- (-0.05,1) node[left] {$1$};
+				\draw (0,2) -- (-0.05,2) node[left] {$2$};
+
+				% Function graph
+				\draw[thick] (0,1) -- (1,2);
+
+				% Description
+				\node[align=center] at (0.7, -0.8) {$\alpha(p) = p + 1$};
+			\end{tikzpicture}
+		\end{multicols}
+	\end{center}
+	\[x(0) = \left(\tfrac23, \tfrac13\right) \qquad \alpha(x_1(0)) = \tfrac53 \quad \alpha(x_2(0)) = \tfrac43\]
+\end{frame}
+
+\begin{frame}{Sensitivity split | Properties}
+	\begin{figure}
+		\centering
+		\begin{tikzpicture}[x=2cm, y=2cm, every node/.style={font=\small}]
+			% Axes
+			\draw[->] (0,0) -- (-1.1,0);
+			\draw[->] (0,0) -- (2.1,0) node[right] {$t_1 - t_2$};
+			\draw[->] (0,0) -- (0,1.2) node[above] {$x_1(t)$};
+
+			% Tick marks
+			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
+			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
+			\draw (2,0) -- (2,-0.05) node[below] {$2$};
+			\draw (0,1) -- (-0.05, 1) node[left] {$1$};
+
+			% Function graph
+			\draw[thick,domain=-1:0] plot (\x,{(2-2*\x)/(3-\x)});
+			\draw[thick,domain=0:2] plot (\x,{(2-\x)/(3+\x)});
+
+			% Dots
+			\fill[black] (0,2/3) ellipse (0.03 and 0.03);
+			\draw[black] (0,2/3) ellipse (0.03 and 0.03);
+			\node[below left] at (0,2/3) {$\frac23$};
+		\end{tikzpicture}
+		\caption{Flow function of link operator $1$ of Example}
+		\label{figure:alpha_simple:flow_example}
+	\end{figure}
+\end{frame}
+
+\begin{frame}{Sensitivity split | Properties}
 	\begin{figure}
@@
 			\draw (0,2) -- (-0.05, 2) node[left] {$2$};
-			\draw (0,4/3) -- (0.05,4/3) node[right] {$4/3$};
-			\draw (0,5/3) -- (-0.05,5/3) node[left] {$5/3$};
+			\draw (0,4/3) -- (0.05,4/3) node[right] {$\frac43$};
+			\draw (0,5/3) -- (-0.05,5/3) node[left] {$\frac53$};
 			\draw (0,1) -- (-0.05,1) node[left] {$1$};
@@
 			% Function graph
-			%\draw[thick] (-1,1) -- (0,4/3);
-			%\draw[thick] (0,5/3) -- (2,1);
 			\draw[thick,domain=-1:0] plot (\x,{4/(3-\x)});
@@
 	\begin{theorem}
-		Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games and $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the (equal) flow on paths for $t = 0$.
-		If $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that
+		Let $\Gm_1 = (N, \ell, \alpha^{(1)}), \Gm_2 = (N, \ell, \alpha^{(2)})$.\\
+		For $x(0) = x^{(1)}(0) = x^{(2)}(0)$, if
 		\[\alpha^{(1)}(p) = \alpha^{(2)}(p), \forall p: p < 1 - \min_{i \in N}\{x_i(0)\}\]
@@
 	For the Example we have
-	\[\max\{x_1(0), x_2(0)\} = \max\{2/3, 1/3\} = 2/3\]
+	\[\max\{x_1(0), x_2(0)\} = \max\left\{\tfrac23, \tfrac13\right\} = \tfrac23\]
 	so if we used a distribution function such as
@@
 		\begin{cases}
-			p + 1 & p \le 2/3 \\
-			\mathrm{e}^p & p > 2/3
+			p + 1 & p \le \tfrac23 \\
+			\mathrm{e}^p & p > \tfrac23
 		\end{cases}

### 2025-02-09 thesis/slides.tex
Thesis: Pres: Final slides, cleanup, graph and general fixes in all Sections

@@
 
-\subsection{Our model}
-
 \begin{frame}{Preliminaries | Our model}
@@
 
-\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level) | Example}
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
 \begin{center}
@@
 
-	Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$).
+	%Equilibrium is indifferent to uniform variations of tolls ($t^\prime = t + c$).
 \end{frame}
@@
 
-\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level) | Example}
+\begin{frame}{Preliminaries | Selfish routing (1\textsuperscript{st} level)}
 	\begin{center}
@@
 	\[x(t) = \left(\frac15, \frac25, \frac25\right)\]
-since $\ell_2(1/2) + t_2 = \ell_3(1/2) + t_3 = 7/2$ and $\ell_1(0) + t_1 = 4$.
+	since $\ell_1\left(\frac15\right) + 3 = \ell_2\left(\frac25\right) + 2 = \ell_3\left(\frac25\right) + 1 = \frac{17}{5}$.
 \end{frame}
@@
 
+\begin{frame}{Preliminaries | Pricing competition (2\textsuperscript{nd} level)}
+	\begin{block}{Full Wardrop support assumption}
+		$x_i(0) > 0$ for all $i \in N$
+	\end{block}
+	\begin{block}{Pricing N.E. uniqueness\footcite{Harks_2019}}
+		If the \textit{full Wardrop support assumption} is satisfied then $t^*$ is unique, $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$.
+	\end{block}
+\end{frame}
+
 \begin{frame}{Preliminaries | Our model}
@@
 
-\subsection{Game equivalence}
-
 \begin{frame}{Preliminaries | Game equivalence}
@@
 \end{frame}
-
-\subsection{Homogeneous networks}
-
-\begin{frame}{Preliminaries | Homogeneous networks}
-	\begin{block}{Flow formula\footcite{Harks_2019}}
-		Define $N(t) = \{i \in N | x_i(t) > 0\}$.
-		For affine latency functions $\ell_i(x) = a_i x + b_i$, $a_i > 0, b_i \ge 0$ and by solving $\ell_i(x_i) + t_i = K$ with $\sum_{i \in N} x_i = 1$, calculate $K$ and get for all $i \in N$
-		\begin{equation*}
-			x_i(t) = \frac{1 + \sum_{j \in N(t)}\frac{b_j + t_j - b_i - t_i}{a_j}}{\sum_{j \in N(t)}\frac{a_i}{a_j}}
-		\end{equation*}
-	\end{block}
-\end{frame}
-
-\begin{frame}{Preliminaries | Homogeneous networks}
-	\begin{block}{Full Wardrop support assumption}
-		$x_i(0) > 0$ for all $i \in N$
-	\end{block}
-	\begin{block}{Pricing N.E. properties\footcite{Harks_2019}}
-		$\Pi_i(t)$ is either linear or quadratic, therefore $|B_i(t_{-i})| = 1$.
-		If the \textit{full Wardrop support assumption} is satisfied then $t^*$ is unique, $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ and
-		\begin{equation*}
-			t_i^* = \left(a_i + \frac{1}{\sum_{j \ne i} \frac{1}{a_j}}\right) \cdot x_i(t^*)
-		\end{equation*}
-	\end{block}
-\end{frame}
-
-%\begin{frame}{Preliminaries | Homogeneous players | Example}
-%	\begin{example}
-%	\end{example}
-%	$x(0) = \left(\frac23, \frac13\right), \; x(3, 2) = \left(\frac14, \frac34\right)$
-%\end{frame}
 
@@
 	\end{center}
-	\[x(0) = \left(\tfrac23, \tfrac13\right) \qquad \alpha(x_1(0)) = \tfrac53 \quad \alpha(x_2(0)) = \tfrac43\]
+	\[x(0) = \left(\frac23, \frac13\right) \qquad \alpha(x_1(0)) = \frac53 \quad \alpha(x_2(0)) = \frac43\]
 \end{frame}
@@
 		\end{tikzpicture}
-		\caption{Flow function of link operator $1$ of Example}
+		\caption{Flow function of link $1$ of Example}
 		\label{figure:alpha_simple:flow_example}
@@
 
-	Also note that 
+	Note that 
 	\[c_i(p) = c \left(\frac1c \ell_i(x_i) + t_i\right)\]
@@
 
-\begin{frame}{Heterogeneous Pricing Games}
+\begin{frame}{Zero money-sensitivity}
 	Zero money-sensitivity creates issues as it can be exploited.
@@
 	\end{example}
-
 	\begin{center}
@@
 			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
-			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
-			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
+			\draw (-2/5,0) -- (-2/5,-0.05) node[left=4,below] {$-\frac25$};
+			\draw (-2/15,0) -- (-2/15,-0.05) node[left=4,below] {$-\frac{2}{15}$};
 			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
-			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
-			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
+			\draw (1/8,0) -- (1/8,-0.05) node[left=1,below] {$\frac18$};
+			\draw (1/6,0) -- (1/6,-0.05) node[right=2,below] {$\frac16$};
 			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
@@
 			% Tick marks
-			\draw (-1,0) -- (-1,-0.05) node[below] {$-1$};
-			\draw (-2/5,0) -- (-2/5,-0.05) node[below] {$-\frac25$};
-			\draw (-2/15,0) -- (-2/15,-0.05) node[below] {$-\frac{2}{15}$};
-			\draw (0,0) -- (0,-0.05) node[below] {$t_2$};
-			\draw (1/8,0) -- (1/8,-0.05) node[below] {$\frac18$};
-			\draw (1/6,0) -- (1/6,-0.05) node[below] {$\frac16$};
-			\draw (7/15,0) -- (7/15,-0.05) node[below] {$\frac{7}{15}$};
-			\draw (7/5,0) -- (7/5,-0.05) node[below] {$\frac75$};
-			\draw (2,0) -- (2,-0.05) node[below] {$2$};
-			\draw (0,1) -- (-0.05,1) node[left] {$1$};
-			\draw (0,3) -- (0.05,3) node[right] {$3$};
-			\draw (0,4) -- (-0.05,4) node[left] {$4$};
+			\draw (-1,0) -- (-1,-0.2) node[below] {$-1$};
+			\draw (-2/5,0) -- (-2/5,-0.2) node[left=4,below] {$-\frac25$};
+			\draw (-2/15,0) -- (-2/15,-0.2) node[left=4,below] {$-\frac{2}{15}$};
+			\draw (0,0) -- (0,-0.2) node[below] {$t_2$};
+			\draw (1/8,0) -- (1/8,-0.2) node[left=1,below] {$\frac18$};
+			\draw (1/6,0) -- (1/6,-0.2) node[right=2,below] {$\frac16$};
+			\draw (7/15,0) -- (7/15,-0.2) node[below] {$\frac{7}{15}$};
+			\draw (7/5,0) -- (7/5,-0.2) node[below] {$\frac75$};
+			\draw (2,0) -- (2,-0.2) node[below] {$2$};
+			\draw (0,1) -- (-0.08,1) node[left=1] {$1$};
+			\draw (0,3) node[right=1] {$3$} -- (0.05,3);
+			\draw (0,4) -- (-0.08,4) node[left=1] {$4$};
 
@@
 	\begin{theorem}
-		If $\Gm_1$ has $t^*$, let $\Gm_2 = ([2], \ell, \as(t^*))$ with fixed $\alpha^{(2)}(p) = \as(t^*)$.
+		If $\Gm_1$ has $t^*$, let $\Gm_2 = ([2], \ell, \alpha^{(2)})$ with fixed $\alpha^{(2)}(p) = \as(t^*)$.
 		Then $t^*$ is a Nash equilibrium for the pricing game in $\Gm_2$.
@@
 	\begin{example}
-		Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous pricing game with latency functions $\ell_1(x) = 2x, \ell_2(x) = x + 1$ and distribution function $\alpha$ such that
-		\begin{align*}
+		Let $\Gm = ([2], \ell, \alpha)$ where
+		$
 			\alpha(p) =
@@
 				4 & p > \tfrac14
-			\end{cases}&
-		\end{align*}
+			\end{cases}
+		$.\\
 		Then $\Gm$ has a N.E. for the pricing game at $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
 	\end{example}
+	\begin{center}
+		\begin{multicols}{2}
+			% Left Column: Network Graph
+			\begin{tikzpicture}[scale=1, baseline=50pt, every node/.style={font=\small}]
+				% Nodes
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
+
+				% Links
+				\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+				\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
+			\end{tikzpicture}
+
+			% Right Column: Distribution function Graph
+			\begin{tikzpicture}[x=3cm, y=0.7cm, every node/.style={font=\small}]
+				% Axes
+				\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
+				\draw[->] (0,0) -- (0,4.2) node[above] {$\as(p)$};
+
+				% Tick marks
+				\draw (0,0) -- (0,-0.05) node[below] {$0$};
+				\draw (0.25,0) -- (0.25,-0.05) node[below] {$\frac14$};
+				\draw (1,0) -- (1,-0.05) node[below] {$1$};
+				\draw (0,3) -- (-0.05,3) node[left] {$3$};
+				\draw (0,4) -- (-0.05,4) node[left] {$4$};
+
+				% Function graph
+				\draw[thick] (0,3) -- (0.25,3);
+				\draw[thick] (0.25,4) -- (1,4);
+
+				% Closed / Open dots
+				\fill[black] (0.25,3) ellipse (0.014 and 0.06);
+				\draw[black] (0.25,3) ellipse (0.014 and 0.06);
+				\fill[white] (0.25,4) ellipse (0.014 and 0.06);
+				\draw[black] (0.25,4) ellipse (0.014 and 0.06);
+			\end{tikzpicture}
+		\end{multicols}
+	\end{center}
+\end{frame}
+
+\begin{frame}{Step distribution functions}
+	If $t^*$ exists, it needs to be at $\as(t^*) = 3$ or $4$.
+
+	Flow will be the same regardless.
+
+	Assume $\Gm^\prime = (N, \ell, 1)$ and we calculate
+	\[t^{*\prime} = \left(\frac53, \frac43\right) \qquad x(t^*) = \left(\frac59, \frac49\right)\]
+
+	Since $t_1 > t_2$, link $1$ has the lower split, so the split is at $\alpha\left(\frac59\right) = 4$.
+
+	Candidate Pricing N.E.:
+	\[t^* = \frac14 t^{*\prime} = \left(\frac{5}{12}, \frac{4}{12}\right)\]
 \end{frame}
@@
 			\draw[->] (0,0) -- (0.7,0) node[right] {$t_1 - t_2$};
-			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};
+			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1\left(t_1, \frac{4}{12}\right)$};
 
 			% Tick marks
-			\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
-			\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
-			\draw (-1/12,0) -- (-1/12,-0.01) node[left=9,below] {$-\frac{1}{12}$};
-			\draw (-1/16,0) -- (-1/16,-0.01) node[right=2,below] {$-\frac{1}{16}$};
-			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
-			\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
-			\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
-			\draw (5/12,0) -- (5/12,-0.01) node[below] {$\frac{5}{12}$};
-			\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
-			\draw (2/3,0) -- (2/3,-0.01) node[below] {$\frac23$};
-			%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
-			%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};
+			\draw (-1/3,0) -- (-1/3,-0.015) node[left=4,below] {$-\frac13$};
+			\draw (-1/4,0) -- (-1/4,-0.015) node[left=4,below] {$-\frac14$};
+			\draw (-1/12,0) -- (-1/12,-0.015) node[left=9,below] {$-\frac{1}{12}$};
+			\draw (-1/16,0) -- (-1/16,-0.015) node[right=4,below] {$-\frac{1}{16}$};
+			%\draw (0,0) -- (0,-0.015) node[below] {$0$};
+			\draw (1/12,0) -- (1/12,-0.015) node[below] {$\frac{1}{12}$};
+			\draw (5/16,0) -- (5/16,-0.015) node[below] {$\frac{5}{16}$};
+			\draw (5/12,0) -- (5/12,-0.015) node[below] {$\frac{5}{12}$};
+			\draw (2/4,0) -- (2/4,-0.015) node[below] {$\frac24$};
+			\draw (2/3,0) -- (2/3,-0.015) node[below] {$\frac23$};
 
 			% Pseudo-heterogeneous profits
-			\draw[gray,dashed,thick,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[above=17,right=-7,black] {$c = 3$};
-			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=10,right=-3,black] {$c = 4$};
+			\draw[gray,dashed,thick,domain=-1/3:2/3] plot (\x,{((2-3*\x)/3)*(1/3+\x)}) node[right=3,above=8,black] {$c = 3$};
+			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[left=23,above=1,black] {$c = 4$};
 
@@
 			\draw[thick] (-1/12,3/16) -- (-1/16, 39/192);
-			\fill[black] (-1/12,3/16) ellipse (0.00625 and 0.005) node[below right] {$\frac{3}{16}$};
-			\fill[black] (-1/16,39/192) ellipse (0.00625 and 0.005) node[above left] {$\frac{39}{192}$};
+			\fill[black] (-1/12,3/16) ellipse (0.00625 and 0.005) node[right=2,below=-1] {$\frac{3}{16}$};
+			\fill[black] (-1/16,39/192) ellipse (0.00625 and 0.005) node[left=7,above=-1] {$\frac{39}{192}$};
 			\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
 			\draw[thick] (5/16,31/192) -- (5/12,3/16);
-			\fill[black] (5/16,31/192) ellipse (0.00625 and 0.005) node[below left] {$\frac{31}{192}$};
-			\fill[black] (5/12,3/16) ellipse (0.00625 and 0.005) node[above right] {$\frac{3}{16}$};
+			\fill[black] (5/16,31/192) ellipse (0.00625 and 0.005) node[left=7,below=-3] {$\frac{31}{192}$};
+			\fill[black] (5/12,3/16) ellipse (0.00625 and 0.005) node[right=7,above=-1] {$\frac{3}{16}$};
 			\draw[thick,domain=5/12:2/3] plot (\x,{((2-3*\x)/3)*(4/12+\x)});
@@
 		\end{tikzpicture}
+		\\[6pt]
 		\begin{tikzpicture}[x=10cm, y=15cm, scale=0.7, every node/.style={font=\small}]
@@
 			\draw[->] (0,0) -- (0.4,0) node[right] {$t_2 - t_1$};
-			\draw[->] (0,0) -- (0,0.2) node[above] {$\Pi_2(t)$};
+			\draw[->] (0,0) -- (0,0.215) node[above] {$\Pi_2\left(\frac{5}{12}, t_2\right)$};
 
@@
 			\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
-			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_1^* = \frac{5}{12}$};
+			\draw (0,0) -- (0,-0.01) node[below] {$0$};
 			\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
@@
 			% Pseudo-heterogeneous profits
-			\draw[gray,dashed,thick,domain=-5/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)}) node[above=15,right=-7,black] {$c = 3$};
-			\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,left=17,black] {$c = 4$};
+			\draw[gray,dashed,thick,domain=-5/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)}) node[right=3,above=8,black] {$c = 3$};
+			\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[left=23,above=1,black] {$c = 4$};
 
@@
 			\draw[thick] (-5/12,0) -- (-5/16,5/64);
-			\fill[black] (-5/12,0) ellipse (0.0045 and 0.003) node[above left] {$0$};
-			\fill[black] (-5/16,5/64) ellipse (0.0045 and 0.003) node[above left] {$\frac{5}{64}$};
+			\fill[black] (-5/12,0) ellipse (0.0045 and 0.003) node[left=4,above=-1] {$0$};
+			\fill[black] (-5/16,5/64) ellipse (0.0045 and 0.003) node[left=4,above=-1] {$\frac{5}{64}$};
 			\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
 			\draw[thick] (1/16,23/192) -- (1/12,1/8);
-			\fill[black] (1/16,23/192) ellipse (0.0045 and 0.003) node[below left] {$\frac{23}{192}$};
-			\fill[black] (1/12,1/8) ellipse (0.0045 and 0.003) node[above right] {$\frac18$};
+			\fill[black] (1/16,23/192) ellipse (0.0045 and 0.003) node[left=4,below=-1] {$\frac{23}{192}$};
+			\fill[black] (1/12,1/8) ellipse (0.0045 and 0.003) node[right=4,above=-1] {$\frac18$};
 			\draw[thick,domain=1/12:1/3] plot (\x,{((1-3*\x)/3)*(5/12+\x)});
@@
 		\end{tikzpicture}
-		\caption{Profit functions for link operators $1$ and $2$ of Example when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+		%\caption{Profit functions for link operators $1$ and $2$ of Example when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
 Red dot indicates the max profit at $t^*$.
 Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
-		\label{figure:alpha_step:profit_ne}
+		%\label{figure:alpha_step:profit_ne}
 	\end{figure}
@@
 				4 & p > \tfrac14
-			\end{cases}&
-		\end{align*}
+			\end{cases}
+		$.\\
 		Then $\Gm$ has no N.E. for the pricing game.
 	\end{example}
+	\begin{center}
+		\begin{multicols}{2}
+			% Left Column: Network Graph
+			\begin{tikzpicture}[scale=1, baseline=50pt, every node/.style={font=\small}]
+				% Nodes
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (s) at (0,0) {$s$};
+				\node[circle, draw, fill=blue!20, minimum size=0.8cm] (t) at (4,0) {$t$};
+
+				% Links
+				\draw[->, thick] (s) to[bend left=35] node[midway, above] {$2x$} (t);
+				\draw[->, thick] (s) to[bend right=35] node[midway, below] {$x + 1$} (t);
+			\end{tikzpicture}
+
+			% Right Column: Distribution function Graph
+			\begin{tikzpicture}[x=3cm, y=0.7cm, every node/.style={font=\small}]
+				% Axes
+				\draw[->] (0,0) -- (1.2,0) node[right] {$p$};
+				\draw[->] (0,0) -- (0,4.2) node[above] {$\as(p)$};
+
+				% Tick marks
+				\draw (0,0) -- (0,-0.05) node[below] {$0$};
+				\draw (0.25,0) -- (0.25,-0.05) node[below] {$\frac14$};
+				\draw (1,0) -- (1,-0.05) node[below] {$1$};
+				\draw (0,2) -- (-0.05,2) node[left] {$2$};
+				\draw (0,4) -- (-0.05,4) node[left] {$4$};
+
+				% Function graph
+				\draw[thick] (0,2) -- (0.25,2);
+				\draw[thick] (0.25,4) -- (1,4);
+
+				% Closed / Open dots
+				\fill[black] (0.25,2) ellipse (0.014 and 0.06);
+				\draw[black] (0.25,2) ellipse (0.014 and 0.06);
+				\fill[white] (0.25,4) ellipse (0.014 and 0.06);
+				\draw[black] (0.25,4) ellipse (0.014 and 0.06);
+			\end{tikzpicture}
+		\end{multicols}
+	\end{center}
 \end{frame}
@@
 			\draw[->] (0,0) -- (1.1,0) node[right] {$t_1 - t_2$};
-			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1(t)$};
+			\draw[->] (0,0) -- (0,0.3) node[above] {$\Pi_1\left(t_1, \frac{4}{12}\right)$};
 
 			% Tick marks
-			\draw (-1/3,0) -- (-1/3,-0.01) node[below] {$-\frac13$};
-			\draw (-1/4,0) -- (-1/4,-0.01) node[below] {$-\frac14$};
-			\draw (-1/8,0) -- (-1/8,-0.01) node[left=5,below] {$-\frac18$};
-			\draw (-1/16,0) -- (-1/16,-0.01) node[below] {$-\frac{1}{16}$};
-			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_2^* = \frac{4}{12}$};
-			\draw (1/12,0) -- (1/12,-0.01) node[below] {$\frac{1}{12}$};
-			\draw (5/16,0) -- (5/16,-0.01) node[below] {$\frac{5}{16}$};
-			\draw (2/4,0) -- (2/4,-0.01) node[below] {$\frac24$};
-			\draw (5/8,0) -- (5/8,-0.01) node[below] {$\frac58$};
-			\draw (1,0) -- (1,-0.01) node[below] {$1$};
-			%\draw (0,2/9) -- (-0.02,2/9) node[left] {$\frac29$};
-			%\draw (0,1/12) -- (0.01,1/12) node[right] {$\frac{1}{12}$};
+			\draw (-1/3,0) -- (-1/3,-0.015) node[left=11,below] {$-\frac13$};
+			\draw (-1/4,0) -- (-1/4,-0.015) node[left=8,below] {$-\frac14$};
+			\draw (-1/8,0) -- (-1/8,-0.015) node[left=8,below] {$-\frac18$};
+			\draw (-1/16,0) -- (-1/16,-0.015) node[right=1,below] {$-\frac{1}{16}$};
+			%\draw (0,0) -- (0,-0.015) node[below] {$0$};
+			\draw (1/12,0) -- (1/12,-0.015) node[below] {$\frac{1}{12}$};
+			\draw (5/16,0) -- (5/16,-0.015) node[below] {$\frac{5}{16}$};
+			\draw (2/4,0) -- (2/4,-0.015) node[below] {$\frac24$};
+			\draw (5/8,0) -- (5/8,-0.015) node[below] {$\frac58$};
+			\draw (1,0) -- (1,-0.015) node[below] {$1$};
 
 			% Pseudo-heterogeneous profits
-			\draw[gray,dashed,thick,domain=-1/3:2/2] plot (\x,{((2-2*\x)/3)*(1/3+\x)}) node[above=20,right=-5,black] {$c = 2$};
-			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[above=15,right,black] {$c = 4$};
+			\draw[gray,dashed,thick,domain=-1/3:2/2] plot (\x,{((2-2*\x)/3)*(1/3+\x)}) node[right=5,above=10,black] {$c = 2$};
+			\draw[gray,dashed,thick,domain=-1/4:2/4] plot (\x,{((2-4*\x)/3)*(1/3+\x)}) node[right=10,above=5,black] {$c = 4$};
 
@@
 			\draw[thick] (-1/8, 5/32) -- (-1/16, 39/192);
-			\fill[black] (-1/8, 5/32) ellipse (0.008333 and 0.005) node[below right] {$\frac{5}{32}$};
-			\fill[black] (-1/16,39/192) ellipse (0.008333 and 0.005) node[above left] {$\frac{39}{192}$};
+			\fill[black] (-1/8, 5/32) ellipse (0.008333 and 0.005) node[right=2,below=-1] {$\frac{5}{32}$};
+			\fill[black] (-1/16,39/192) ellipse (0.008333 and 0.005) node[left=7,above=-1] {$\frac{39}{192}$};
 			\draw[thick,domain=-1/16:5/16] plot (\x,{((2-4*\x)/3)*(4/12+\x)});
 			\draw[thick] (5/16,31/192) -- (5/8,23/96);
-			\fill[black] (5/16,31/192) ellipse (0.008333 and 0.005) node[below left] {$\frac{31}{192}$};
-			\fill[black] (5/8,23/96) ellipse (0.008333 and 0.005) node[above right] {$\frac{23}{96}$};
+			\fill[black] (5/16,31/192) ellipse (0.008333 and 0.005) node[left=7,below=-1] {$\frac{31}{192}$};
+			\fill[black] (5/8,23/96) ellipse (0.008333 and 0.005) node[right=7,above=-1] {$\frac{23}{96}$};
 			\draw[thick,domain=5/8:1] plot (\x,{((2-2*\x)/3)*(4/12+\x)});
@@
 		\end{tikzpicture}
+		\\[6pt]
 		\begin{tikzpicture}[x=8cm, y=15cm, scale=0.7, every node/.style={font=\small}]
@@
 			\draw[->] (0,0) -- (0.6,0) node[right] {$t_2 - t_1$};
-			\draw[->] (0,0) -- (0,0.2) node[above] {$\Pi_2(t)$};
+			\draw[->] (0,0) -- (0,0.215) node[above] {$\Pi_2\left(\frac{5}{12}, t_2\right)$};
 
 			% Tick marks
-			%\draw (-2/3,0) -- (-2/3,-0.01) node[below] {$-\frac23$};
-			\draw (-2/4,0) -- (-2/4,-0.01) node[below] {$-\frac24$};
-			\draw (-5/12,0) -- (-5/12,-0.01) node[below] {$-\frac{5}{12}$};
+			%\draw (-2/4,0) -- (-2/4,-0.01) node[below] {$-\frac24$};
+			\draw (-5/12,0) -- (-5/12,-0.01) node[left=3,below] {$-\frac{5}{12}$};
 			\draw (-5/16,0) -- (-5/16,-0.01) node[below] {$-\frac{5}{16}$};
-			\draw (-1/12,0) -- (-1/12,-0.01) node[below] {$-\frac{1}{12}$};
-			\draw (0,0) -- (0,-0.01) node[below] {$0$} node[below=20] {$t_1^* = \frac{5}{12}$};
-			\draw (1/16,0) -- (1/16,-0.01) node[left=3,below] {$\frac{1}{16}$};
-			\draw (1/12,0) -- (1/12,-0.01) node[right=3,below] {$\frac{1}{12}$};
+			\draw (-1/12,0) -- (-1/12,-0.01) node[left=5,below] {$-\frac{1}{12}$};
+			\draw (0,0) -- (0,-0.01) node[below] {$0$};
+			\draw (1/16,0) -- (1/16,-0.01) node[left=2,below] {$\frac{1}{16}$};
+			\draw (1/12,0) -- (1/12,-0.01) node[right=5,below] {$\frac{1}{12}$};
 			\draw (1/4,0) -- (1/4,-0.01) node[below] {$\frac14$};
 			\draw (1/2,0) -- (1/2,-0.01) node[below] {$\frac12$};
-			%\draw (0,5/36) -- (-0.02,5/36) node[below=7,left] {$\frac{5}{36}$};
 
 			% Pseudo-heterogeneous profits
-			\draw[gray,dashed,thick,domain=-5/12:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)}) node[above=20,right=-5,black] {$c = 2$};
-			\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[above=15,right,black] {$c = 4$};
+			\draw[gray,dashed,thick,domain=-5/12:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)}) node[right=4,above=8,black] {$c = 2$};
+			\draw[gray,dashed,thick,domain=-5/12:1/4] plot (\x,{((1-4*\x)/3)*(5/12+\x)}) node[right=8,above=4,black] {$c = 4$};
 
@@
 			\draw[thick] (-5/12,0) -- (-5/16,5/64);
-			\fill[black] (-5/16,5/64) ellipse (0.008 and 0.004) node[above left] {$\frac{5}{64}$};
+			\fill[black] (-5/16,5/64) ellipse (0.008 and 0.004) node[left=4,above=-1] {$\frac{5}{64}$};
 			\draw[thick,domain=-5/16:1/16] plot (\x,{((1-4*\x)/3)*(5/12+\x)});
 			\draw[thick] (1/16,23/192) -- (1/8,13/96);
-			\fill[black] (1/16,23/192) ellipse (0.008 and 0.004) node[left=6,below] {$\frac{23}{192}$};
-			\fill[black] (1/8,13/96) ellipse (0.008 and 0.004) node[above right] {$\frac{13}{96}$};
+			\fill[black] (1/16,23/192) ellipse (0.008 and 0.004) node[left=4,below=-1] {$\frac{23}{192}$};
+			\fill[black] (1/8,13/96) ellipse (0.008 and 0.004) node[right=7,above=-1] {$\frac{13}{96}$};
 			\draw[thick,domain=1/8:1/2] plot (\x,{((1-2*\x)/3)*(5/12+\x)});
@@
 		\end{tikzpicture}
-		\caption{Profit functions for link operators $1$ and $2$ of Example when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
+		%\caption{Profit functions for link operators $1$ and $2$ of Example when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
 Red dot indicates the max profit at $t^*$.
 Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
-		\label{figure:alpha_step:profit_no_ne}
+		%\label{figure:alpha_step:profit_no_ne}
 	\end{figure}
 \end{frame}
-
-\subsection*{Pricing N.E. Algorithm}
 
@@
 			\end{enumerate}
-			\item If $\Pi_i < \Pi_{i, k}$, then $\Gm$ has no pricing Nash Equilibrium.
+			\item If $\Pi_i < \Pi_{i, k}$, then $\Gm$ has NO pricing Nash Equilibrium.
 		\end{enumerate}
@@
 
-\begin{frame}{Conclusion}
-	In our work
+\begin{frame}{Future work}
+	\textbf{Pseudo-heterogeneous games}
 	\begin{itemize}
-		\item Investigated heterogeneity by defining and analysing $\as$
-		\item Developed a connection between different fixed distribution functions
-		\item Developed an algorithm for $2$-link step distribution functions
+		\item Connection between similar games with different fixed distribution functions
+		\item What happens to flow, tolls, profit when fixed $t_{-i}$?
+		\item (Conjectures in the Appendix)
 	\end{itemize}
+
+	\textbf{Step distribution functions}
+	\begin{itemize}
+		\item Conditions for N.E. existence in $2$-link networks
+		\item $n$-link networks
+		\begin{itemize}
+			\item Complexity of calculating existence
+		\end{itemize}
+	\end{itemize}
 \end{frame}
@@
 \begin{frame}{Future work}
+	\textbf{Continuous distribution functions}
 	\begin{itemize}
-		\item Pseudo-heterogeneous games
-		\item Step distribution functions
-		\begin{itemize}
-			\item $2$-link networks
-			\item $n$-link networks
+		\item No gaps!
+		\item Function series approximation ($m \rightarrow +\infty$)
+		\item Linear $\alpha$ maintains the linear system
+		\item Strange behaviour when $0$ is an accumulation point in $\alpha$
 	\end{itemize}
-		\item Continuous distribution functions
-		\item Function series approximation
-		\item Split function for series-parallel links
-	\end{itemize}
+
+	\textbf{Split function for series-parallel links}
+
+	We hope the tools and intuitions developed here can be useful in any similar future work.
 \end{frame}

### 2025-02-09 thesis/slides.tex
Thesis: Pres: Adds pauses and slide flow with final cleanup and fixes

@@
 \documentclass{beamer}
+%\documentclass[handout]{beamer}
 \usepackage{tikz}
@@
 	Selfish routing can model and solve a variety of real-world problems in economics, transportation and more.
+	\pause
 	\\[20pt]
 	\begin{tikzpicture}[scale=0.9, every node/.style={font=\small,align=center}]
+		\onslide<+->{
 			\draw (0,-0.15) node[below] {Pigou} -- (0,0.15) node[above] {$1920$};
+		}
+		\onslide<+->{
 			\draw (0,0) -- (6,0);
 			\draw (6,-0.15) node[below] {Beckman\\et al.} -- (6,0.15) node[above] {$1956$};
+		}
+		\onslide<+->{
 			\draw (6,0) -- (9,0);
 			\draw (9,-0.15) node[below] {Rosenthal} -- (9,0.15) node[above] {$1973$};
-		\draw (9,0) -- (10,0);
-
+			\draw[->] (9,0) -- (10,0);
+		}
+		\onslide<+->{
 			\draw (0,-2.65) node[below] {Cole\\et al.} -- (0,-2.35) node[above] {$2003$};
+		}
+		\onslide<+->{
 			\draw (0,-2.5) -- (2,-2.5);
 			\draw (2,-2.65) node[below] {Acemoglu\\\& Ozdaglar} -- (2,-2.35) node[above] {$2007$};
+		}
+		\onslide<+->{
 			\draw (2,-2.5) -- (7.5,-2.5);
@@
 			\draw (9,-2.65) node[below] {Harks\\et al.} -- (9,-2.35) node[above] {$2019$};
-		\draw (9,-2.5) -- (10,-2.5);
+			\draw[->] (9,-2.5) -- (10,-2.5);
+		}
 	\end{tikzpicture}
@@
 		\item $\alpha$ the distribution function
-	\end{itemize}
+	\end{itemize}\pause
 	A homogeneous game can be described as $(N, \ell, 1)$.
@@
 	\end{definition}
-	Equivalency means same tolls cause same flow.
+	Equivalency means same tolls cause same flow.\pause
 
@@
 \begin{frame}{Sensitivity split | Heterogeneous networks}
-	Latencies are the same for all players.
+	Latencies are the same for all players.\pause
 
@@
 
-	Toll differences are viewed with different scaling.
+	Toll differences are viewed with different scaling.\pause[1]
 	\\[15pt]
 	\begin{tikzpicture}
-		% Title
-		\node[above,fixed_height] at (3.7,3.3) {$\alpha(0) = 1$};
-
-		% Axes
-		\draw[->] (0,0) -- (7,0) node[right=5,fixed_height] {$c\left(0\right)$};
+		% Axes
+		\draw[->] (0,0) -- (7,0) node[right=5,fixed_height] {$c$};
 		\draw[-] (0,0) -- (0,3.2);
@@
 
+		\onslide<2->{
+			% Title
+			\node[above,fixed_height] at (3.7,3.3) {$\alpha(0) = 1$};
+
+			% Y-axis label
+			\node[right=12,fixed_height] at (7,0) {$(0)$};
+
 			% Y-bars: Tolls
@@
 			\filldraw[fill=orange!20] (29/11,0.25) rectangle (40/11,0.75) node[below right] {$1$};
+		}
 	\end{tikzpicture}
@@
 	For the Example we have
-	\[\max\{x_1(0), x_2(0)\} = \max\left\{\tfrac23, \tfrac13\right\} = \tfrac23\]
+	\[\min\{x_1(0), x_2(0)\} = \max\left\{\tfrac23, \tfrac13\right\} = \tfrac13\]\pause
 	so if we used a distribution function such as
@@
 	\]
-	then $\as(t)$ would remain the same for all $t \in \R_+^n$
+	then $\as(t)$ would remain the same for all valid $t \in \R_+^n$.
 \end{frame}
@@
 \begin{frame}{Pseudo-heterogeneous Pricing Games}
-	Consider distribution functions $\alpha(p) = c$ for some $c > 0$.
+	Consider distribution functions $\alpha(p) = c$ for some $c > 0$.\pause
 
@@
 	\[c_i(p) = \ell_i(x_i) + c t_i\]
-	Behaviour should be homogeneous with tolls "mapped" to $t \rightarrow t/c$.
+	Behaviour should be homogeneous with tolls "mapped" to $t \rightarrow t/c$.\pause
 
@@
 		Then the two games are equivalent.
-	\end{lemma}
+	\end{lemma}\pause
 	\begin{proof}
@@
 \begin{frame}{Pseudo-heterogeneous Pricing Games}
-	We will call such games \textit{pseudo-heterogeneous}.
-
-	Uniform increase in money-sensitivity is equivalent to uniform decrease in latencies (lost for general $\alpha$ functions).
+	We will call such games \textit{pseudo-heterogeneous}.\pause
+
+	Uniform increase in money-sensitivity is equivalent to uniform decrease in latencies (lost for general $\alpha$ functions).\pause
 
@@
 		Then $x^{(1)}(c_2 t) = x^{(2)}(c_1 t)$.
-	\end{lemma}
+	\end{lemma}\pause
 	\begin{proof}
@@
 	\end{lemma}
-	\begin{proof}
-		\begin{enumerate}[$(i)$]
-			% https://tex.stackexchange.com/a/98399
-			\item
-			$\begin{aligned}[t]
-				t_i^{*(1)} &= B_i^{(1)}(t_{-i}^{*(1)}) \Leftrightarrow \cdots \Leftrightarrow \frac{c_1}{c_2} t_i^{*(1)} = B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i}^{*(1)}\right)
-			\end{aligned}$
-			\item follows from previous lemma.
-			\vspace{-20pt}
-		\end{enumerate}
-	\end{proof}
+	%\begin{proof}
+	%	\begin{enumerate}[$(i)$]
+	%		% https://tex.stackexchange.com/a/98399
+	%		\item
+	%		$\begin{aligned}[t]
+	%			t_i^{*(1)} &= B_i^{(1)}(t_{-i}^{*(1)}) \Leftrightarrow \cdots \Leftrightarrow \frac{c_1}{c_2} t_i^{*(1)} = B_i^{(2)}\left(\frac{c_1}{c_2} t_{-i}^{*(1)}\right)
+	%		\end{aligned}$
+	%		\item follows from previous lemma.
+	%		\vspace{-20pt}
+	%	\end{enumerate}
+	%\end{proof}
 	Pricing Nash Equilibrium is always at the same flow.
@@
 		Then $\exists i \in N$ where $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{n - 1}$.
-	\end{lemma}
+	\end{lemma}\pause
 	\begin{proof}
@@
 
-\begin{frame}<presentation:0>[noframenumbering]{Step distribution functions}
-	Notice that when $x_1$ is fixed then $\as$ isn't and vice-versa.\\
-	If the flow is moving, then it does so among players with the same sensitivity type, which is one of the finitely many values $\alpha$ can take.
-	If all players of each sensitivity type are using a single link, then $\as$ can take any value between the lowest and highest $\alpha$ value in the upper and lower split respectively.
-\end{frame}
-
 \begin{frame}{Step distribution functions}
@@
 \begin{frame}{Step distribution functions}
-	If $t^*$ exists, it needs to be at $\as(t^*) = 3$ or $4$.
-
-	Flow will be the same regardless.
+	If $t^*$ exists, it needs to be at $\as(t^*) = 3$ or $4$ (not between).\pause
+
+	Flow will be the same regardless.\pause
 
 	Assume $\Gm^\prime = (N, \ell, 1)$ and we calculate
-	\[t^{*\prime} = \left(\frac53, \frac43\right) \qquad x(t^*) = \left(\frac59, \frac49\right)\]
-
-	Since $t_1 > t_2$, link $1$ has the lower split, so the split is at $\alpha\left(\frac59\right) = 4$.
+	\[t^{*\prime} = \left(\frac53, \frac43\right) \qquad x(t^*) = \left(\frac59, \frac49\right)\]\pause
+
+	Since $t_1 > t_2$, link $1$ has the lower split, so the split is at $\alpha\left(\frac59\right) = 4$.\pause
 
@@
 	\begin{enumerate}
-		\item Consider $\Gm^\prime = ([2], \ell, 1)$ and calculate $t^{*\prime}, x^\prime(t^{*\prime})$.
-		\item Calculate $\as(t^*)$ as the $\alpha$ value of the lower split flow in $x^\prime(t^{*\prime})$
-		\item Calculate the candidate $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$ and $\Pi_1(t^*), \Pi_2(t^*)$.
-		\item For each $\alpha_k \ne \as(t^*)$, and for each $i \in [2]$
+		\item Consider $\Gm^\prime = ([2], \ell, 1)$ and calculate $t^{*\prime}, x^\prime(t^{*\prime})$.\pause
+		\item Calculate $\as(t^*)$ as the $\alpha$ value of the lower split in $x^\prime(t^{*\prime})$.\pause
+		\item Calculate the candidate $t^* = \tfrac{t^{*\prime}}{\as(t^*)}$ and $\Pi_1(t^*), \Pi_2(t^*)$.\pause
+		\item For each $\alpha_k \ne \as(t^*)$, and for each $i \in [2]$:\pause
 		\begin{enumerate}[$4.1$]
-			\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i}^*)$ and tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
-			\item Search for $\Pi_{i, k}$, the max profit for $i$ within those $t_i$ ranges:
+			\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i}^*)$ and tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.\pause
+			\item Search for $\Pi_{i, k}$, the max profit for $i$ within those $t_i$ ranges:\pause
 			\begin{enumerate}[$4.2.1$]
-				\item If $B_{i, k}(t_{-i}^*)$ is within the $t_i$ ranges, $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}^*), t_{-i}^*)$.
+				\item If $B_{i, k}(t_{-i}^*)$ is within the $t_i$ ranges, $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}^*), t_{-i}^*)$.\pause
 				\item Otherwise, $\Pi_{i, k}$ is max profit among the ranges' edge tolls ($4$).
-			\end{enumerate}
+			\end{enumerate}\pause
 			\item If $\Pi_i < \Pi_{i, k}$, then $\Gm$ has NO pricing Nash Equilibrium.
-		\end{enumerate}
+		\end{enumerate}\pause
 		\item If all of the above checks fail, return $t^*$.
-	\end{enumerate}
+	\end{enumerate}\pause
 	\textbf{Complexity:} $\mathcal{O}(m)$
@@
 \begin{frame}{Future work}
-	\textbf{Pseudo-heterogeneous games}
+	\textbf{Pseudo-heterogeneous games}\pause
 	\begin{itemize}
-		\item Connection between similar games with different fixed distribution functions
-		\item What happens to flow, tolls, profit when fixed $t_{-i}$?
+		\item Connection between similar games with different fixed distribution functions\pause
+		\item What happens to flow, tolls, profit when fixed $t_{-i}$?\pause
 		\item (Conjectures in the Appendix)
-	\end{itemize}
-
-	\textbf{Step distribution functions}
+	\end{itemize}\pause
+
+	\textbf{Step distribution functions}\pause
 	\begin{itemize}
-		\item Conditions for N.E. existence in $2$-link networks
-		\item $n$-link networks
+		\item Conditions for N.E. existence in $2$-link networks\pause
+		\item $n$-link networks\pause
 		\begin{itemize}
@@
 \begin{frame}{Future work}
-	\textbf{Continuous distribution functions}
+	\textbf{Continuous distribution functions}\pause
 	\begin{itemize}
-		\item No gaps!
-		\item Function series approximation ($m \rightarrow +\infty$)
-		\item Linear $\alpha$ maintains the linear system
+		\item No gaps!\pause
+		\item Function series approximation ($m \rightarrow +\infty$)\pause
+		\item Linear $\alpha$ maintains the linear system\pause
 		\item Strange behaviour when $0$ is an accumulation point in $\alpha$
-	\end{itemize}
-
-	\textbf{Split function for series-parallel links}
+	\end{itemize}\pause
+
+	\textbf{Split function for series-parallel links}\pause
 

### 2025-02-10 thesis/slides.tex
Thesis: Pres: Final fixes

@@
 		\end{equation*}
-	\end{definition}
+	\end{definition}\pause
 	N.E. always exists and is unique w.r.t. costs for homogeneous\footcite{beckmann1956studies} and heterogeneous\footcites{1973JSP.....7..295S}{MILCHTAICH1996111} networks.
@@
 		Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
-		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+^{|N|}$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
+		$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+^n$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
 	\end{definition}
@@
 
-\begin{frame}{Sensitivity split | Properties}
+\begin{frame}{Sensitivity split | Example}
 	\begin{center}
@@
 	\end{center}
-	\[x(0) = \left(\frac23, \frac13\right) \qquad \alpha(x_1(0)) = \frac53 \quad \alpha(x_2(0)) = \frac43\]
-\end{frame}
-
-\begin{frame}{Sensitivity split | Properties}
+	\[x(0) = \left(\frac23, \frac13\right) \qquad \as(t) = \alpha(\text{lower split flow})\]
+\end{frame}
+
+\begin{frame}{Sensitivity split | Example}
 	\begin{figure}
@@
 
-\begin{frame}{Sensitivity split | Properties}
+\begin{frame}{Sensitivity split | Example}
 	\begin{figure}
@@
 	Assume $\Gm^\prime = (N, \ell, 1)$ and we calculate
-	\[t^{*\prime} = \left(\frac53, \frac43\right) \qquad x(t^*) = \left(\frac59, \frac49\right)\]\pause
+	\[t^{*\prime} = \left(\frac53, \frac43\right) \qquad x^\prime(t^{*\prime}) = \left(\frac59, \frac49\right)\]\pause
 
@@
 \begin{frame}{Step distribution functions | Pricing N.E. Algorithm}
-	\textbf{Summary:} Given $\Gm = ([2], \ell, \alpha), \alpha = (\alpha_k)_{k \in [m]}$
+	\textbf{Summary:} Given $\Gm = ([2], \ell, \alpha), \alpha = (\alpha_k)_{k \in [m]}$\pause
 	\begin{enumerate}
@@
 	\begin{itemize}
-		\item Connection between similar games with different fixed distribution functions\pause
+		\item Insights in fixed distribution function variation\pause
 		\item What happens to flow, tolls, profit when fixed $t_{-i}$?\pause
@@
 		\item Function series approximation ($m \rightarrow +\infty$)\pause
-		\item Linear $\alpha$ maintains the linear system\pause
 		\item Strange behaviour when $0$ is an accumulation point in $\alpha$

### 2025-02-13 thesis/article.tex
Thesis: Final fixes and checks, corrects Th. Lianea title to External Collaborator
Release v1.3

--- 2025-01-16 thesis/article.tex
@@
 							\normalsize {\it {\bf Examination committee:}\\
-								Thanassis Lianeas,\\ School of Electrical and Computer Engineering, National Technical University of Athens.\\
+								Thanasis Lianeas,\\ External Collaborator, ALMA.\\
 								Dimitris Fotakis,\\ School of Electrical and Computer Engineering, National Technical University of Athens.\\
@@
 							\normalsize {\it {\bf Supervisor:}\\
-								Thanassis Lianeas, Lecturer,\\School of Electrical and Computer Engineering,\\
-								National Technical University of Athens.\\
+								Thanasis Lianeas,\\ External Collaborator, ALMA.\\
 							}
@@
 \chapter*{Συνοψη}
-Σε αυτή τη διπλωματική μεταπτυχιακού μελετάμε ένα παίγνιο $2$ επιπέδων όπου, σε ένα δίκτυο με $n$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι διαχειριστές των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
+Σε αυτή τη διπλωματική εργασία μεταπτυχιακού μελετάμε ένα παίγνιο $2$ επιπέδων όπου, σε ένα δίκτυο με $n$ ακμές από μια πηγή $s$ σε ένα στόχο $t$, μια μονάδα ροής θέλει να μετακινηθεί από το $s$ στο $t$ χρησιμοποιώντας την ακμή με το χαμηλότερο κόστος, ενώ οι διαχειριστές των ακμών ανταγωνίζονται για κέρδος βάζοντας δίοδια στις ακμές και δημιουργώντας έτσι ένα παίγνιο συμφόρησης με διόδια.
 Εξετάζουμε μόνο αφινικές καθυστερήσεις για τις ακμές.
@@
 Beginning with the network topology, one can distinguish between parallel networks (our case) or series-parallel ones.
-In addition the flow traversing through the network can either be atomic (finite number of players, each contributing to congestion equally or weighted) or non-atomic (infinite number of players, each contributing to congestion by an non-influencing infinitesimal amount).
+In addition, the flow traversing through the network can either be atomic (finite number of players, each contributing to congestion equally or weighted) or non-atomic (infinite number of players, each contributing to congestion by an non-influencing infinitesimal amount).
 Also the model might admit elastic demand (e.g.
@@
 Most work considers homogeneous network users.
-Heterogeneity has been studied by Schmeilder \cite{1973JSP.....7..295S} while Milchtaich \cite[Prop $3.3$]{doi:10.1287/moor.25.3.349.12220} has contributed through with work on the more general crowding games, a class of games where the cost assigned to each player is affected only by the number of players selecting the same action (or strategy).
+Heterogeneity has been studied by Schmeilder \cite{1973JSP.....7..295S} while Milchtaich \cite[Prop $3.3$]{doi:10.1287/moor.25.3.349.12220} has contributed through his work on the more general crowding games, a class of games where the cost assigned to each player is affected only by the number of players selecting the same action (or strategy).
 Large crowding games are basically less restrictive $n$-link parallel congestion games.
 Also, Cole et al.
-\cite{10.1145/780542.780618} in their work showed that even general heterogeneous networks can be priced so that an optimal routing emerges while computing those efficient tolls can be done in polynomial time for convex latency functions and distribution functions with only finitely many values.
+\cite{10.1145/780542.780618}, in their work, showed that even general heterogeneous networks can be priced so that an optimal routing emerges and computing those efficient tolls can be done in polynomial time for convex latency functions and distribution functions with only finitely many values.
 The latter paper has been one of the main pillars of this thesis.
@@
 
-In this section we will describe the model utilised throughout this thesis.
+In this chapter we will describe the model utilised throughout this thesis.
 If we attempted to call that model by including all of its properties, the result would be a Heterogeneous Non-atomic $n$-link Parallel Network Toll Congestion Pricing Game, so while we will describe each of those properties, we will eventually focus on heterogeneity and the pricing competition, thus calling it a Heterogeneous Pricing Game.
@@
 We consider a directed graph $G = (\{s, t\}, N)$ where $N = \{1,\dots, n\}$ is a set of parallel links from a source node $s$ to a target node $t$.
-For the non-atomic case, there is one unit of traffic that wishes to travel from $s$ to $t$, described as the unit interval $[0, 1]$ endowed with Lebesque measure $\lambda$.
+For the non-atomic case, there is one unit of traffic that wishes to travel from $s$ to $t$, described as the unit interval $[0, 1]$, endowed with Lebesque measure $\lambda$.
 Each point $p \in [0, 1]$ will be called a \textit{player} and will be considered to be non-cooperative and contribute to the traffic by an infinitesimal amount.
@@
 \end{equation*}
-In that case, all links with $x_i > 0$ have equal effective costs, i.e. there exists some $K > 0$ such that for all those links $i$ it holds that $\ell_i(x_1) + t_i = K$.
+In that case, all links with $x_i > 0$ have equal effective costs, i.e. there exists some $K > 0$ such that for all those links $i$ it holds that $\ell_i(x_i) + t_i = K$.
 From a well-known result from Beckman et al.
@@
 
-We can therefore denote by $x(t)$ the flow occurring on that unique up to costs equilibrium for a given set of toll $t$.
-If $t = 0^N$ then the equilibrium is called the \textit{Wardrop equilibrium}.
-It's also worth noting that looking at Lemma \ref{lemma:wardrop_equilibrium}, we can see that what actually matters, with regard to the flow, is the relative difference among the tolls, and not their actual values.
+We can therefore denote by $x(t)$ the flow occurring on that unique -up to costs- equilibrium for a given set of toll $t$.
+If $t = 0^n$ then the equilibrium is called the \textit{Wardrop equilibrium}.
+It's also worth noting that, looking at Lemma \ref{lemma:wardrop_equilibrium}, we can see that what actually matters, with regard to the flow, is the relative difference among the tolls and not their actual values.
 To demonstrate this, if we consider an arbitrary $c \in \R_+$ and tolls $t^\prime = t + c$ then for the same flow $x$ and any other flow $x^\prime$ the sum becomes
@@
 
-With this observation we can see that the case of $t = 0^N$ is equivalent to any toll instance such that $t_1 = t_2 = \dots = t_n$.
+With this observation we can see that the case of $t = 0^n$ is equivalent to any toll instance such that $t_1 = t_2 = \dots = t_n$.
 We will therefore simplify our notation and write $t = 0$ when talking about the game without tolls, though we will in fact mean the entire class $\{t = (c)_{i \in N}, c \in \R_+\}$.
 
-Finally for affine latencies we can calculate $x(t)$ by following the same reasoning as \cite[Prop $3.1$]{Harks_2019}.
-For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^{|N|}$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
+Finally, for affine latencies we can calculate $x(t)$ by following the same reasoning as \cite[Prop $3.1$]{Harks_2019}.
+For $\ell_i(x_i) = a_i x_i + b_i$ with $a_i > 0, b_i \geq 0$ and $t \in \R_+^n$, define $N(t) = \{i \in N | x_i(t) > 0\}$.
 Since $x(t)$ is an equilibrium for $t$ then for all $i \in N(t)$ we get $\ell_i(x_i) + t_i = K$ for some common effective cost $K$.
@@
 
-This property shows us that for a given $t \in \R_+^{|N|}$, if we order the links according to decreasing toll values, then the same link order will have latencies ordered in increasing values (and vice-versa).
+This property shows us that for a given $t \in \R_+^n$, if we order the links according to decreasing toll values, then the same link order will have latencies ordered in increasing values (and vice-versa).
 It is then easy to show that the players using each such link are also ordered with regard to their $\alpha$ values in increasing order.
@@
 	Let $(N, \ell, \alpha)$ a heterogeneous parallel game.
-	For tolls $t \in \R_+^{|N|}$ consider the links in decreasing toll ordering.
+	For tolls $t \in \R_+^n$ consider the links in decreasing toll ordering.
 	It holds that $x_n(t) \ge x_n(0)$.
@@
 	Consider $t^\prime = t - t_n$.
-	From assumption we have $t_n = \min_{i \in N} t_i$, which makes $t^\prime \in \R_+^{|N|}$ with $t_n^\prime = 0$.
+	From assumption we have $t_n = \min_{i \in N} t_i$, which makes $t^\prime \in \R_+^n$ with $t_n^\prime = 0$.
 	Since the flow equilibrium $x(t)$ is dependent only on the toll differences, we get $x(t) = x(t^\prime)$.
@@
 Finally we need to discuss about toll differences again.
-While the definition for $t \in \R_+^{|N|}$ allows any arbitrary value, the meaningful ones actually reside in a more limited space.
-Assume for example that a toll $t$ is such that $x_i(t) = 1$ for some link $i \in N$ with $t_i > 0$ and $x_j(t) = 0$ for all other links $j \ne i$.
+While the definition for $t \in \R_+^n$ allows any arbitrary value, the meaningful ones actually reside in a more limited space.
+Assume, for example, that a toll $t$ is such that $x_i(t) = 1$ for some link $i \in N$ with $t_i > 0$ and $x_j(t) = 0$ for all other links $j \ne i$.
 It's obvious that further decreasing $t_i$ changes nothing for the flow, which is why in any optimisation setup (minimum total cost, maximal profit, etc.) those cases never come into play.
 Same reasoning can be done for increasing $t_i$ in tolls $t$ where $x_i(t) = 0$.
-Therefore there exists an upper bound for the valid toll difference between any two links $i, j \in N$, which can be calculated as the toll difference which even the least sensitive player $0$ (to account for heterogeneity) will view the link with the lowest toll (and all flow) as the one with the lowest cost.
+Therefore, there exists an upper bound for the valid toll difference between any two links $i, j \in N$, which can be calculated as the toll difference which even the least sensitive player $0$ (to account for heterogeneity) will view the link with the lowest toll (and all flow) as the one with the lowest cost.
 In other words, assuming $t_i > t_j$ with all flow in $j$ and $\alpha(0) > 0$ we get
@@
 
-We can easily calculate that $x(0) = (2/3, 1/3)$ with equal cost $4/3$ in both links.
+We can easily calculate $x(0) = (2/3, 1/3)$ with equal cost $4/3$ in both links.
 If tolls $t = (3, 2)$ are assigned to the links, then $x(3, 2) = (1/4, 3/4)$.
 Indeed, since $t_1 > t_2$ then the flow users with the lowest sensitivity will use link $1$, while the more sensitive ones will use link $2$.
-With players ordered in increasing sensitivity order, the less sensitive link $1$ users will have players $p_1 \in [0, 1/4]$ with $\alpha(p_1) \le \alpha(1/4) = 5/4$ and respectively link $2$ users $p_2 \in (1/4, 1]$ (player $x_i$ can be put arbitrarily in link $1$ or $2$) we have $\alpha(p_2) \ge \alpha(1/4) = 5/4$.
+With players ordered in increasing sensitivity order, the less sensitive link $1$ users will have players $p_1 \in [0, 1/4]$ with $\alpha(p_1) \le \alpha(1/4) = 5/4$ and respectively link $2$ users $p_2 \in (1/4, 1]$ (player $x_i$ can be put arbitrarily in link $1$ or $2$) have $\alpha(p_2) \ge \alpha(1/4) = 5/4$.
 Finally, all flow users will view the link latencies similarly as
@@
 while the opposite direction also holds similarly for players in link $2$.
-We postpone the discussion of how that flow can be calculated until Chapter \ref{chapter:split}, as we'll require a better notion of the player who views the two links as equal (in this case player $1/4$).
+We postpone the discussion of how that flow can be calculated until Chapter \ref{chapter:split}, as we'll require a better notion of the player who views the two links as equal (in this case, player $1/4$).
 
@@
 This is seemingly not as much restrictive in practice, as there would be little motivation to add tolls to a route with no traffic.
-From the same work we also get that if the full Wardrop support assumption holds, then $t^*$ is unique \cite[Lemma 3.3]{Harks_2019} while also $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ \cite[Lemma 3.2]{Harks_2019}.
+From the same work we also get that if the full Wardrop support assumption holds, then $t^*$ is unique \cite[Lemma 3.3]{Harks_2019}, while also $x_i(t^*) > 0$ and $t_i^* > 0$ for all $i \in N$ \cite[Lemma 3.2]{Harks_2019}.
 %We will thus assume for all further instances that the full Wardrop support assumption is true.
@@
 Another notion we will need in our analysis is when two games are equivalent.
-This concept will be helpful because in some cases, even though the parameters of a game might change, the players' utilities and respective strategies do not, making the two instances in practice identical.
+This concept will be helpful because, in some cases, even though the parameters of a game might change, the players' relative utilities and respective strategies do not, making the two instances in practice identical.
 For example, similarly to our analysis of toll differences using Lemma \ref{lemma:wardrop_equilibrium}, if we consider the two homogeneous games $(N, \ell, 1)$ and $(N, \ell + c, 1)$ for some $c > 0$, then the flow's behavior will be the same in both of them, resulting in equivalent instances.
@@
 	Let $\Gm_1, \Gm_2$ be two $n$-link Network Congestion Games.
-	$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
+	$\Gm_1$ and $\Gm_2$ are called \textbf{equivalent} if and only if for all tolls $t \in \R_+^n$ it holds that $x^{(1)}(t) = x^{(2)}(t)$, with $x^{(1)}(t), x^{(2)}(t)$ being the Nash Equilibria for $t$ in $\Gm_1, \Gm_2$ respectively.
 \end{definition}
@@
 One of the main difficulties with heterogeneity is that, for a given set of tolls, flow users with different money sensitivity values, view toll values also differently, and therefore, in practice, play different games.
-In the analysis of Example \ref{example:simple_alpha} we can find a first glimpse on how to tackle this issue, as we can see that the flow users on each link are organised around the player that views the two link costs as equal.
+In the analysis of Example \ref{example:simple_alpha}, we can see a first glimpse on how to tackle this issue, as we found out that the flow users on each link are organised around the player that views the two link costs as equal.
 This notion will be the center of this chapter, and using it we will try and describe some properties about all users.
@@
 \end{itemize}
-Remember that we have assumed that $t_1 > t_2 \stackrel{\ref{lemma:latencies_tolls}}{\Leftrightarrow} \ell_1(x_1(t)) < \ell_2(x_2(t))$.
-Therefore the flow in the lower-latency link $1$ has players with $\alpha(p) \le \as(t)$, while the flow in the higher-latency link $2$ has players with $\alpha(p) \ge \as(t)$.
+Remember that we have assumed that $t_1 > t_2 \stackrel{\text{\ref{lemma:latencies_tolls}}}{\Leftrightarrow} \ell_1(x_1(t)) < \ell_2(x_2(t))$.
+Therefore, the flow in the lower-latency link $1$ has players with $\alpha(p) \le \as(t)$, while the flow in the higher-latency link $2$ has players with $\alpha(p) \ge \as(t)$.
 Since the players are sorted in increasing order according to $\alpha$, it helps to view the players in the first case as the "lower" part of the split and respectively the players in the second case as the "upper" part of the split.
@@
 	Let $(N, \ell, \alpha)$ a heterogeneous parallel game, tolls $t$ where $t_i \ne t_j$ for links $i, j \in N$ and $x(t)$ the Nash equilibrium for $t$.
-	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^{|N|}|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
+	We define the \textit{money sensitivity split function} $\as^{(i, j)}: \{t \in \R_+^n|t_i \ne t_j\} \rightarrow (0, +\infty)$ as
 	\[\as^{(i, j)}(t) = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_i - t_j}\]
@@
 When looking at $\alpha$ values, however, a player's $\alpha$ value might deterministically put them in a specific link, depending on how $\alpha$ is defined.
-If in Example \ref{example:simple_alpha} we consider a different distribution function where $\alpha(p) = 1$ for $p < 1/4$ and $\alpha(p) = 2$ otherwise, we'd still get $x(3, 2) = (1/4, 3/4)$ (checked similarly as in the example's analysis) but with player $1/4$ strictly selecting link $2$ (since $\alpha(1/4) = 2$) and no player viewing the two link costs equally.
+If, in Example \ref{example:simple_alpha}, we consider a different distribution function where $\alpha(p) = 1$ for $p < 1/4$ and $\alpha(p) = 2$ otherwise, we'd still get $x(3, 2) = (1/4, 3/4)$ (checked similarly as in the example's analysis) but with player $1/4$ strictly selecting link $2$ (since $\alpha(1/4) = 2$) and no player viewing the two link costs equally.
 We will cover both cases of open and closed intervals by using border bounds on the set of all $\alpha$ values of a link's flow.
@@
 	We define as $A_i(t)$ the set of all possible $\alpha(p)$ values of players $p$ using link $i$ in the Nash equilibrium for $t$.
-	More formally, we define a set function $A_i: \R_+^{|N|} \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
+	More formally, we define a set function $A_i: \R_+^n \rightarrow \mathcal{P}(\R_+)$, where $\mathcal{P}(\R_+)$ is the powerset of $\R_+$, such that
 	\[A_i(t) = \{\alpha(p) | f(p) = j \wedge t_j = t_i\}\]
@@
 
-Notice that with this definition it follows that $A_i(0)$ is the entire domain of $\alpha$ for any $i \in N$.
+Notice that, with this definition, it follows that $A_i(0)$ is the entire domain of $\alpha$ for any $i \in N$.
 We continue with describing some basic properties around the values of $\as$.
@@
 where indeed if $t_i > t_j$ then
-\[t_i > t_j \Leftrightarrow t_i - t_j > 0 \LeftrightarrowArg{(\ref{eq:split_property_cond_tolls_0})} t_i^\prime - t_j^\prime > 0 \Leftrightarrow t_i^\prime > t_j^\prime\]
+\[t_i > t_j \Leftrightarrow t_i - t_j > 0 \LeftrightarrowArg{(\text{\ref{eq:split_property_cond_tolls_0}})} t_i^\prime - t_j^\prime > 0 \Leftrightarrow t_i^\prime > t_j^\prime\]
 and likewise we also get $t_i < t_j \Leftrightarrow t_i^\prime < t_j^\prime$.
@@
 	\label{lemma:split_monotonicity}
-	Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t, t^\prime$ such that for some links $i, j \in N$ it holds that $t_i \ne t_j, t_i^\prime \ne t_j^\prime$ and $t_k = t_k^\prime$ for all other $k \in N \setminus \{i, j\}$.
+	Let $(N, \ell, \alpha)$ a heterogeneous parallel game and tolls $t, t^\prime$ such that $t_i \ne t_j, t_i^\prime \ne t_j^\prime$ for some links $i, j \in N$ and $t_k = t_k^\prime$ for all other $k \in N \setminus \{i, j\}$.
 	If it also holds that $x_i(t), x_j(t), x_i(t^\prime), x_j(t^\prime) > 0$ and $\frac{t_i - t_j}{t_i^\prime - t_j^\prime} > 0$, then the following are true:
@@
 
-	If $x_i(t) = x_i(t^\prime)$, then looking at $\as^{(i, j)}$ we get
+	If $x_i(t) = x_i(t^\prime)$ and $x_j(t) = x_j(t^\prime)$, then looking at $\as^{(i, j)}$ we get
 	\[\as^{(i, j)}(t^\prime) = \frac{\ell_j(x_j(t^\prime)) - \ell_i(x_i(t^\prime))}{t_j^\prime - t_i^\prime} = \frac{\ell_j(x_j(t)) - \ell_i(x_i(t))}{t_j^\prime - t_i^\prime} = \as^{(i, j)}(t) \frac{t_j - t_i}{t_j^\prime - t_i^\prime}\]
@@
 
-	If $x_i(t) > x_i(t^\prime)$ then there exists a player $p$ who is in link $i$ in the Nash equilibrium for $t$ and in link $j$ for the one for $t^\prime$, meaning that by applying (twice) Definition \ref{definition:alpha_flow_sets} we get
+	If $x_i(t) > x_i(t^\prime)$ and $x_j(t) < x_j(t^\prime)$ then there exists a player $p$ who is in link $i$ in the Nash equilibrium for $t$ and in link $j$ for the one for $t^\prime$, meaning that by applying (twice) Definition \ref{definition:alpha_flow_sets} we get
 	\[\inf A_j(t^\prime) \le \alpha(p) \le \sup A_i(t)\]
-	By now carefully applying  (twice) the property from Lemma $\ref{lemma:split_basic}(iii)$ we get
+	By now carefully applying  (twice) the property from Lemma \ref{lemma:split_basic}$(iii)$ we get
 	\[\as^{(i, j)}(t^\prime) \le \inf A_j(t^\prime) \le \sup A_i(t) \le \as^{(i, j)}(t)\]
@@
 		\item
-		\begin{flalign*}
-			\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) &= 0 &
-		\end{flalign*}
+		$\begin{aligned}[t]
+			\lim_{|t_i - t_j| \rightarrow +\infty}\as^{(i, j)}(t) = 0
+		\end{aligned}$
 		\item
-		\begin{flalign*}
-			\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) &= \limsup_{t_i - t_j \rightarrow 0^+} A_i(t) &
-		\end{flalign*}
+		$\begin{aligned}[t]
+			\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t) = \limsup_{t_i - t_j \rightarrow 0^+} A_i(t)
+		\end{aligned}$
 	\end{enumerate}
@@
 The above show that $\as(t)$ is continuous for all $t \ne 0$, approaches $0$ at large toll differences and increases as that difference approaches $0$, thus making the side limits around $0$ have different values (apart from the very specific case where $x_1(0) = x_2(0)$).
-At this point we should also mention that at the toll difference bounds we discussed in Chapter \ref{chapter:preliminaries}, $\as$ takes the value of the least sensitive player, i.e. $\alpha(0)$.
-
-We apply this on Example \ref{example:simple_alpha} to solidify this.
+At this point, we should also mention that, at the toll difference bounds we discussed in Chapter \ref{chapter:preliminaries}, $\as$ takes the value of the least sensitive player, i.e. $\alpha(0)$.
+
+We apply this on Example \ref{example:simple_alpha} to solidify it.
 Since $\alpha$ is continuous we get from Corollary \ref{corollary:split_asymptotic_continuous} that
@@
 	 From Lemmas \ref{lemma:split_asymptotic} and \ref{lemma:split_monotonicity} (also look the discussion at the function characterisation above) we get that, for $t_i - t_j$ in $(-\infty, 0)$ and $(0, +\infty)$, $\as$ is non-decreasing and non-increasing respectively.
-	 Therefore $\as$ is upper bounded by its sided limits as $t_i - t_j \rightarrow 0$, which means that for all $t$ in the domain of $\as$ we get
+	 Therefore, $\as$ is upper bounded by its side limits as $t_i - t_j \rightarrow 0$, which means that for all $t$ in the domain of $\as$ we get
 	 \[\as^{(i j)}(t) \le \max\left\{\lim_{t_i - t_j \rightarrow 0^+} \as^{(i, j)}(t), \lim_{t_i - t_j \rightarrow 0^-} \as^{(i, j)}(t)\right\}\]
-	 which in turn, after applying Lemma \ref{lemma:split_asymptotic}$(ii)$ while noticing that $t_i - t_j \rightarrow 0^-$ is equivalent to $t_j - t_i \rightarrow 0^+$, becomes
+	 which in turn, after applying Lemma \ref{lemma:split_asymptotic}$(ii)$, while noticing that $t_i - t_j \rightarrow 0^-$ is equivalent to $t_j - t_i \rightarrow 0^+$, becomes
 	 \[\as^{(i, j)}(t) \le \max\left\{\limsup_{t_i - t_j \rightarrow 0^+} A_i(t), \limsup_{t_j - t_i \rightarrow 0^+} A_j(t)\right\}\]
@@
 	Let $\Gm_1 = (N, \ell, \alpha^{(1)})$ and $\Gm_2 = (N, \ell, \alpha^{(2)})$ be two heterogeneous parallel games with the same number of links $n = |N|$  and latency functions $\ell$.
-	For $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t \in \R_+^{|N|}$ in $\Gm_1, \Gm_2$ respectively, denote as $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the equal flow on paths between $\Gm_1$ and $\Gm_2$ for $t = 0$.
+	For $x^{(1)}(t), x^{(2)}(t)$ the Nash equilibria for $t \in \R_+^n$ in $\Gm_1, \Gm_2$ respectively, denote as $x(0) = x^{(1)}(0) = x^{(2)}(0)$ the equal flow on paths between $\Gm_1$ and $\Gm_2$ for $t = 0$.
 	If the distribution functions $\alpha^{(1)}$ and $\alpha^{(2)}$ are such that
@@
 \begin{proof}
-	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \forall t \in \R_+^{|N|}$.
+	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \forall t \in \R_+^n$.
 	It's already stated that the equality holds for $t = 0$.
@@
 those games be $\Gm_1$ and $\Gm_2$ respectively.
-	So if we take $\Gm_1$ where $p$ in the lower split, then it holds that $p$ is not in $x_n^{(1)}$, since the link with the highest toll is always the upper split with regard to all others.
+	So if we take $\Gm_1$ where $p$ is in the lower split, then it holds that $p$ is not in $x_n^{(1)}$, since the link with the highest toll is always the upper split with regard to all others.
 	Therefore $p < 1 - x_n^{(1)}$ and from Lemma \ref{lemma:xn_xn0_lower_bound} we then get $p < 1 - x_n(0) < 1 - \min_{i \in N}\{x_i(0)\}$, which from the hypothesis leads us to $\alpha^{(1)}(p) = \alpha^{(2)}(p)$.
@@
 \]
-then $\as$ would still behave the same way as those $(2/3, 1]$ players will always be in the upper split regardless of their $\alpha$ value.
+then $\as$ would still behave the same way, as those $(2/3, 1]$ players will always be in the upper split regardless of their $\alpha$ value.
 
@@
 We will then proceed to analyse games with fixed distribution functions, where in Lemma \ref{lemma:a_fixed_homogeneous} we will show that such games are, as intuition suggests, equivalent to homogeneous games.
-Special interest will then be on comparing such games, specifically those with the same setup but different fixed $\alpha$ functions, as Lemma \ref{lemma:a_fixed_c_relation} will reveal that, uniformly varying the player sensitivity, maps the toll values around the same flow.
+Special interest will then be on comparing such games, specifically those with the same setup but different fixed $\alpha$ functions, as Lemma \ref{lemma:a_fixed_c_relation} will reveal that, uniformly varying the player sensitivity maps toll values around the same flow.
 The tools and notions built above will prove extremely useful when we next analyse games with step distribution functions, where we'll restrict our analysis to instances with $2$ links to simplify our work.
@@
 	Let $i \in N$ be a link for which $\ell_i(0) = \min_{j \in N} \ell_i(0)$.
-	Then $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{|N| - 1}$.
+	Then $B_i(t_{-i})$ is unbounded for all $t_{-i} \in \R_+^{n - 1}$.
 \end{lemma}
@@
 	The condition of $\ell_i(0) = \min_{j \in N} \ell_i(0)$, then, ensures that link $i$ will always have flow, i.e.
-$x_i(t) > 0, \forall t \in \R_+^{|N|}$, since if $x_i(t) = 0$ for some set of tolls $t$, then $i$ becomes a lowest-latency link meaning that at least some of the players with $\alpha(p) = 0$ view this as the lowest cost, a contradiction.
+$x_i(t) > 0, \forall t \in \R_+^n$, since if $x_i(t) = 0$ for some set of tolls $t$, then $i$ becomes a lowest-latency link, meaning that at least some of the players with $\alpha(p) = 0$ view this as the lowest cost, a contradiction.
 
@@
 We therefore need the restriction of $\alpha(p) > 0$ when $p > 0$ in order for our pricing game to have an equilibrium.
-The main interest in the above lemma is the fact that it affects the lowest-latency, and therefore highest-toll, link, meaning that regardless of how high the highest toll is, some players will always remain in that link.
+The main interest in the above lemma is the fact that it affects the lowest-latency, and therefore highest-toll, link, meaning that, regardless of how high the highest toll is, some players will always remain in that link.
 Intuitively, it describes the fact that having no toll fear makes a player not motivated to leave the link, which in turn means having little control over those players using toll regulations.
@@
 \begin{proof}
-	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^{|N|}$, where $x^{(1)}(t), x^{(2)}(t)$ the respective Nash Equilibrium for $t$ in $\Gm_1, \Gm_2$.
+	It suffices to show that $x^{(1)}(t) = x^{(2)}(t), \; \forall t \in \R_+^n$, where $x^{(1)}(t), x^{(2)}(t)$ the respective Nash Equilibrium for $t$ in $\Gm_1, \Gm_2$.
 	Since $\Gm_2$ is homogeneous, we can use Lemma \ref{lemma:wardrop_equilibrium} to get that for any other flow $x^{(2)}$ it holds that
@@
 	Notice that $\ell_i^{(1)}(x_i) + c t_i$ is the link cost of link $i$ for players in $\Gm_1$, given flow $x_i$ and toll $t_i$.
-	Regardless of the heterogeneity of our users, since the above inequality holds, then for flow $x^{(2)}(t)$ in $\Gm_1$ it will also hold for any other flow $x_i^{(1)} = x^{(2)}$.
+	Regardless of the heterogeneity of our users, since the above inequality holds, then for flow $x^{(2)}(t)$ in $\Gm_1$ it will also hold for any other flow $x^{(1)} = x^{(2)}$.
 	It follows that any flow movement from $x^{(2)}(t)$ will again put players in links with larger link costs, making $x^{(2)}(t)$ a Nash Equilibrium for $t$ in $\Gm_1$ as well.
 	Uniqueness of the equilibrium with regard to costs finally gives us $x^{(1)}(t) = x^{(2)}(t)$.
-	Since the above hold for all $t \in \R_+^{|N|}$, we conclude from Definition \ref{definition:game_equivalence} that $\Gm_1, \Gm_2$ are equivalent.
+	Since the above hold for all $t \in \R_+^n$, we conclude from Definition \ref{definition:game_equivalence} that $\Gm_1, \Gm_2$ are equivalent.
 \end{proof}
-Since a heterogeneous game with a fixed distribution function is, in practice, homogeneous with regard to the flow behaviour, we will also use, when relevant, the term \textit{pseudo-heterogeneous game} to describe such flows more easily.
+Since a heterogeneous game with a fixed distribution function is, in practice, homogeneous with regard to the flow behaviour, we will also use, when relevant, the term \textit{pseudo-heterogeneous game} to describe such games more easily.
 
 Intuitively, the above means that increasing the money sensitivity of all players in a game is equivalent to proportionally decreasing the traffic that flows create on all links.
-Unfortunately this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
+Unfortunately, this correspondence  disappears for non-fixed distribution functions, since, in the general setting, a flow might consist of players with different money sensitivity values depending on the tolls, thus loosing the $1-1$ relation between the latency function values and the distribution function ones.
 We discuss more about the relation between time and money sensitivity in Chapter \ref{chapter:future_work}.
@@
 		%\item Obvious since for $t = 0$ the flow in both $\Gm_1, \Gm_2$ play a homogeneous game with common latencies $\ell$, which makes the two games identical and therefore $x^{(1)}(0) = x^{(2)}(0)$.
-		\item Consider the homogeneous games $\Gm_3 = (N, \frac{\ell}{c_1}, 1)$ and $\Gm_4 = (N, \frac{\ell}{c_2}, 1)$, for which it follows from Lemma \ref{lemma:a_fixed_homogeneous} that they are equivalent to $\Gm_1, \Gm_2$ respectively, meaning that for all $t \in \R_+^{|N|}$ we have $x^{(1)}(t) = x^{(3)}(t)$ and $x^{(2)}(t) = x^{(4)}(t)$.
+		\item Consider the homogeneous games $\Gm_3 = (N, \frac{\ell}{c_1}, 1)$ and $\Gm_4 = (N, \frac{\ell}{c_2}, 1)$, for which it follows from Lemma \ref{lemma:a_fixed_homogeneous} that they are equivalent to $\Gm_1, \Gm_2$ respectively, meaning that for all $t \in \R_+^n$ we have $x^{(1)}(t) = x^{(3)}(t)$ and $x^{(2)}(t) = x^{(4)}(t)$.
 		If we now assign tolls $c_2 t$ to $\Gm_3$, then from Lemma \ref{lemma:wardrop_equilibrium} we get that for any other flow $x^{(3)}$ it holds that
@@
 	\begin{enumerate}[$(i)$]
-		\item $\frac{t^{*(1)}}{t^{*(2)}} = \frac{c_2}{c_1}$
+		\item $c_1 \dot t^{*(1)} = c_2 \dot t^{*(2)}$
 		\item $x^{(1)}(t^{*(1)}) = x^{(2)}(t^{*(2)})$
@@
 		\[
-			B_i^{(1)}(t_{-i}^{*(1)}) = \frac{c_1}{c_1} \cdot B_i^{(1)}\left(\frac{c_2}{c_2} t_{-i}^{*(1)}\right) \stackrel{\ref{lemma:a_fixed_c_relation}}{=} \frac{c_2}{c_1} \cdot B_i^{(2)}\left(\frac{c_1}{c_2}t_{-i}^{*(1)}\right)
+			B_i^{(1)}(t_{-i}^{*(1)}) = \frac{c_1}{c_1} \cdot B_i^{(1)}\left(\frac{c_2}{c_2} t_{-i}^{*(1)}\right) \stackrel{\text{\ref{lemma:a_fixed_c_relation}}}{=} \frac{c_2}{c_1} \cdot B_i^{(2)}\left(\frac{c_1}{c_2}t_{-i}^{*(1)}\right)
 		\]
@@
 		\[
-			x^{(1)}(t^{*(1)}) \stackrel{(i)}{=} x^{(1)}\left(\tfrac{c_2}{c_1}t^{*(2)}\right) \stackrel{\ref{lemma:a_fixed_c_relation}}{=} x^{(2)}(t^{*(2)})
+			x^{(1)}(t^{*(1)}) \stackrel{(i)}{=} x^{(1)}\left(\tfrac{c_2}{c_1}t^{*(2)}\right) \stackrel{\text{\ref{lemma:a_fixed_c_relation}}}{=} x^{(2)}(t^{*(2)})
 		\]
@@
 		\item $x^{(1)}(t) = x^{(2)}(t)$
-		\item $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$ for each respective link operator $i$
+		\item $\Pi_i^{(1)}(t) = \Pi_i^{(2)}(t)$ for all $i \in N$
 	\end{enumerate}
@@
 			% Closed / Open dots
-			\fill[white] (0.2,1) ellipse (0.014 and 0.06);
+			\fill[black] (0.2,1) ellipse (0.014 and 0.06);
 			\draw[black] (0.2,1) ellipse (0.014 and 0.06);
-			\fill[black] (0.2,3) ellipse (0.014 and 0.06);
+			\fill[white] (0.2,3) ellipse (0.014 and 0.06);
 			\draw[black] (0.2,3) ellipse (0.014 and 0.06);
-			\fill[black] (0.5,3) ellipse (0.014 and 0.06);
+			\fill[white] (0.5,3) ellipse (0.014 and 0.06);
 			\draw[black] (0.5,3) ellipse (0.014 and 0.06);
-			\fill[white] (0.5,4) ellipse (0.014 and 0.06);
+			\fill[black] (0.5,4) ellipse (0.014 and 0.06);
 			\draw[black] (0.5,4) ellipse (0.014 and 0.06);
@@
 With a reasoning similar to that of Example \ref{example:simple_alpha} (since again $\alpha(0) = 1$) we get that the toll difference bounds are $t_1 - t_2 \le 2$ and $t_2 - t_1 \le 1$, which means that we can restrict our focus to $t_1 - t_2 \in [-1, 2]$.
-We also know at which flows the behaviour of the network will change, which are exactly the flows where each all player of each sensitivity type are using a single link, i.e.
+We also know at which flows the behaviour of the network will change, which are exactly the flows where all players of each sensitivity type are using a single link, i.e.
 the flows $(4/5, 1/5), (1/2, 1/2), (1/5, 4/5)$, e.g.
@@
 
-What one may first notice from those figures, is that when $x_1$ is fixed then $\as$ isn't and vice-versa.
+What one may first notice, from those figures, is that when $x_1$ is fixed then $\as$ isn't and vice-versa.
 This happens due to the fact that we have a step distribution function, therefore if the flow is moving, then it does so among players with the same sensitivity type, which is one of the finitely many values $\alpha$ can take.
-Inversely, if all players of each sensitivity type are using a single link, then $\as$ can take any value between the lowest and highest $\alpha$ value in the upper and lower split respectively.
-
-Considering now the pricing competition game and looking at the profit function $\Pi_1(t)$, we can already notice from Figure \ref{figure:alpha_step:flow} that in the toll difference intervals where the flow remains the same, $\Pi_1(t)$ will be strictly increasing as $t_1$ also does.
+Inversely, if all players of each sensitivity type are using a single link, then $\as$ can take any value between the highest and lowest $\alpha$ value in the lower and upper split respectively.
+
+Considering now the pricing competition game and looking at the profit function $\Pi_1(t)$, we can already notice from Figure \ref{figure:alpha_step:flow} that, in the toll difference intervals where the flow remains the same, $\Pi_1(t)$ will be strictly increasing as $t_1$ also does.
 In extension, in terms of profit maximisation, it follows that max profit will never be within those intervals.
@@
 	If $\as(t) < \alpha_{k + 1}$, then a symmetrical argument can be made by selecting as $i$ the link operator of the link with the higher toll.
-	Note that an increase in $t_i$ now causes the toll difference $t_{-i} - t_i$ to decrease which may increase $\as(t)$, so we again need to consider that the $t_i^\prime$ increase is arbitrarily small to ensure $\as(t_i^\prime, t_{-i}) < \alpha_{k + 1}$.
+	Note that an increase in $t_i$ now causes the toll difference $t_{-i} - t_i$ to decrease, which may increase $\as(t)$, so we again need to consider that the $t_i^\prime$ increase is arbitrarily small to ensure $\as(t_i^\prime, t_{-i}) < \alpha_{k + 1}$.
 	The rest of the argument continues as before.
@@
 The above lemma shows us that the Nash Equilibrium for the pricing game (if existent at all) does not reside in tolls for which $\as$ is in-between the values of $\alpha$.
-We complement this idea with the following Theorem, one of the main results of this chapter, where we will show that if that Nash Equilibrium exists, then it has to happen for some specific flow.
+We complement this idea with the following Theorem, one of the main results of this chapter, from which it follows that, if that Nash Equilibrium exists, then it has to happen for some specific flow.
 
@@
 leading us to focus on profit for different sensitivity splits.
-Unsurprisingly, there is a heavy dependence on the definition of the distribution function, which we illustrate in the following examples.
+Unsurprisingly, there is a heavy dependence on the definition of the distribution function, which we illustrate in the following two examples.
 
@@
 	Since Lemma \ref{lemma:a_fixed_pricing_ne_relation} suggests that the flow at that equilibrium will be the same regardless of the value of $c$, we calculate the one from the homogeneous game $G^{\prime} = ([2], \ell, 1)$.
-	We can calculate the latter equilibrium $t^{*\prime}$ by solving the system of equations with \ref{eq:homogeneous_x_i} and \ref{eq:homogeneous_pricing_ne_i}, from which we get $t^{*\prime} = \left(\tfrac53, \tfrac43\right)$ with $x^\prime(t^{*\prime}) = \left(\tfrac59, \tfrac49\right)$.
+	We can calculate the latter equilibrium $t^{*\prime}$ by solving the system of equations in \ref{eq:homogeneous_x_i} and \ref{eq:homogeneous_pricing_ne_i}, from which we get $t^{*\prime} = \left(\tfrac53, \tfrac43\right)$ with $x^\prime(t^{*\prime}) = \left(\tfrac59, \tfrac49\right)$.
 	Such a flow split puts the flow of link $1$ in the lower split and link $2$ in the upper split, making $\as(t^*) = \alpha(x_1(t^{*\prime})) = \alpha(5/9) = 4$.
@@
 	\[
-		t^* = \frac13 t^{*\prime} = \left(\frac{5}{12}, \frac{4}{12}\right) \qquad x(t^*) = x^\prime(t^{*\prime}) = \left(\frac59, \frac49\right)
-	\]
-	We're only left to check whether $t^*$ satisfies the definition of a Nash Equilibrium, i.e. whether each link operator has a max profit toll in response to the opposing one.
-	We will therefore need to calculate the profit functions for each link, for which, thanks to \ref{lemma:heterogenous_flow_equiv_fixed}$(ii)$, we can use the respective pseudo-heterogeneous profit functions for each $c = 2, 3$.
+		t^* = \frac14 t^{*\prime} = \left(\frac{5}{12}, \frac{4}{12}\right) \qquad x(t^*) = x^\prime(t^{*\prime}) = \left(\frac59, \frac49\right)
+	\]
+	We're only left with checking whether $t^*$ satisfies the definition of a Nash Equilibrium, i.e. whether each link operator has a max profit toll in response to the opposing one.
+	We will therefore need to calculate the profit functions for each link, for which, thanks to \ref{lemma:heterogenous_flow_equiv_fixed}$(ii)$, we can use the respective pseudo-heterogeneous profit functions for $c = 2, 3$.
 	We can then take the profit definition, formula \ref{eq:homogeneous_x_i} for $2$ links as well as Lemma \ref{lemma:a_fixed_c_relation}$(ii)$ and get for $\Gm_c$
@@
 	\caption{Profit functions for link operators $1$ and $2$ of Example \ref{example:a_step_profit_ne} when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
-Red dot indicates the max profit at $t^*$.
+Red dots indicate the max profit at $t^*$.
 Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
@@
 	\[
-		B_1\left(\frac{4}{12}\right) = \frac58 \ne \frac{5}{12} \qquad B_2\left(\frac{5}{12}\right) = \frac{4}{12}
+		B_1\left(\frac{4}{12}\right) = \frac{23}{24} \ne \frac{5}{12} \qquad B_2\left(\frac{5}{12}\right) = \frac{4}{12}
 	\]
@@
 	\caption{Profit functions for link operators $1$ and $2$ of Example \ref{example:a_step_profit_no_ne} when opposed against the candidate Nash Equilibrium $t^* = \left(\tfrac{5}{12}, \tfrac{4}{12}\right)$.
-Red dot indicates the max profit at $t^*$.
+Red dots indicate the max profit at $t^*$.
 Black dots indicate tolls when relevant intervals start or end for the respective pseudo-heterogeneous profits (dashed lines) they correspond.}
@@
 
-It seems apparent, from the previous two examples, that the criteria, for a candidate pricing Nash equilibrium to maintain its maximality among tolls at different $\alpha_k$ values, are heavily dependent on the function's definition, i.e.
+It seems apparent, from the previous two examples, that the criteria for a candidate pricing Nash equilibrium to maintain its maximality among tolls at different $\alpha_k$ values are heavily dependent on the function's definition, i.e.
 the sensitivity values as well as the amount of flow corresponding to them.
@@
 	\begin{enumerate}[$4.1$]
-		\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i}^*)$ as well as the tolls $t_{i, k}$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
+		\item Consider $\Gm_k = ([2], \ell, \alpha_k)$ and calculate $B_{i, k}(t_{-i}^*)$ as well as the tolls $t_i$ for which $\as(t_i, t_{-i}^*) = \alpha_k$, resulting in two toll ranges for $t_i$.
 		\item Search for $\Pi_{i, k}$, the max profit for $i$ within those $t_i$ ranges:
@@
 			\item If $B_{i, k}(t_{-i}^*)$ is within the $t_i$ ranges, then $\Pi_{i, k} = \Pi_i(B_{i, k}(t_{-i}^*), t_{-i}^*)$.
-			\item Otherwise, $\Pi_{i, k}$ is the highest profit value among the ($4$) tolls in the edges of the two $t_1$ ranges.
+			\item Otherwise, $\Pi_{i, k}$ is the highest profit value among the ($4$) tolls in the edges of the two $t_i$ ranges.
 		\end{enumerate}
@@
 \begin{theorem}
-	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous game with latency functions $\ell = (\ell_1(x), \ell_2(x))_{i \in [2]} = (a_ix + b_i)_{i \in [2]}$ and $\alpha$ a step distribution function with values $(\alpha_k)_{k \in [m]}$.
+	Let $\Gm = ([2], \ell, \alpha)$ a heterogeneous game with latency functions $\ell = (\ell_i(x))_{i \in [2]} = (a_ix + b_i)_{i \in [2]}$ and $\alpha$ a step distribution function with values $(\alpha_k)_{k \in [m]}$.
 	Then Algorithm \ref{algorithm:step_ne_pricing} with input $(\ell, \alpha)$ decides existence and calculates the Nash Equilibrium for the pricing game in $\Gm$ in $\mathcal{O}(m)$ time.
@@
 	Indeed, if we consider from the definition of $\alpha$ the border players $p_k^-, p_k^+$ for which $\alpha(p) = \alpha_k$ when $p_k^- < p < p_k^+$, then the possible link splits are those where $x_1$ (arbitrarily chosen) has flow such that $x_1 = p_k^-, p_k^+, 1 - p_k^+, 1 - p_k^-$.
-	Solving the cost equality equation for $t_2 - t_1$ (and by substituting $x_2$ for $1 - x_1$) we get the formula of \texttt{TollDiff} function in \algref{algorithm:step_helper_functions}{function:toll_diff}, and by then using it in the above four cases for $x_1$, we get from each of the two pairs a min and a max toll difference, each belonging to a different split, for which a set of tolls $t$ is in that range if and only if $\as(t) = \alpha_k$.
+	Solving the cost equality equation for $t_2 - t_1$ (and by substituting $x_2$ for $1 - x_1$) we get the formula of \texttt{TollDiff} function in \algref{algorithm:step_helper_functions}{function:toll_diff}, and by then using it in the above four cases for $x_1$, we get from each of the two pairs a min and a max toll difference, each belonging to a different split, for which a set of tolls $t$ is in those ranges if and only if $\as(t) = \alpha_k$.
 
@@
 	\]
-	thus finding opposing toll $t_{-i} = \frac{2 a_i + a_{-i} + b_i - b_{-i}}{\alpha_k}$ for which the best response is to take the entire flow.
+	thus finding opposing toll $t_{-i} = \frac{2 a_i + a_{-i} + b_i - b_{-i}}{\alpha_k}$, for which the best response is to take the entire flow.
 	Any higher $t_{-i}$ will therefore also have as best response to take the entire flow, leading to a best response toll of $t_i = t_{-i} - \frac{a_i + b_i - b_{-i}}{\alpha_k}$.
@@
 	Otherwise, since $\Pi_i(t)$ is concave from the analysis of Harkes et al.
-\cite{Harks_2019}, not taking a max value at a range follows that profit is either non-decreasing or non-increasing in that range, resulting in its local maximum achieved at one of its edge values.
+\cite{Harks_2019}, not taking a max value at a range follows that profit is either non-decreasing or non-increasing in that range, resulting in its local maximum to be achieved at one of its edge values.
 	So, in that case, we calculate all edge profit values from the two ranges and keep the overall max value.
@@
 
-	We should also mention that we've on purpose ignored invalid toll difference cases.
-	Theorem \ref{theorem:alpha_upper_irrelevant} shows us there might be sensitivity values that are irrelevant to the game.
-	The algorithm will ignore those cases, however, as the \texttt{TollDiff} function will return $t_i < 0$, resulting in $\Pi_i < 0$, which will be skipped when looking for max profit values.
-
-	Finally, regarding the complexity of Algorithm \ref{algorithm:step_ne_pricing}, we can easily see that it mostly consists of base operations with a \texttt{for} loop taking at most $m - 1$ iterations, resulting in a time complexity of $\mathcal{O}(m)$.
+	We should also mention that we've ignored invalid toll difference cases on purpose.
+	Theorem \ref{theorem:alpha_upper_irrelevant} also shows us there might be sensitivity values that are irrelevant to the game.
+	The algorithm will ignore all those cases, however, as the \texttt{TollDiff} function will return $t_i < 0$, resulting in $\Pi_i < 0$, which will be skipped later when looking for max profit values.
+
+	Finally, regarding the complexity of Algorithm \ref{algorithm:step_ne_pricing}, we can easily see that it mostly consists of base operations, with only a \texttt{for} loop taking at most $m - 1$ iterations, resulting in a time complexity of $\mathcal{O}(m)$.
 \end{proof}
@@
 
-Having conducted this analysis partially, we include in the Appendix the (incomplete) propositions \ref{lemma:a_fixed_t_iM}, \ref{lemma:a_fixed_x12}, \ref{corollary:a_fixed_x12_calc} and \ref{lemma:a_fixed_t_i0}, which try to describe that relation between flow and profit, among similar games with varying fixed sensitivity, for the same opposing $t_{-i}$.
+Having conducted this analysis partially, we include in the Appendix the (incomplete) propositions \ref{lemma:a_fixed_t_iM}, \ref{lemma:a_fixed_x12}, \ref{corollary:a_fixed_x12_calc} and \ref{lemma:a_fixed_t_i0}, which try to describe that relation between flow and profit among similar games with varying fixed sensitivity for the same opposing $t_{-i}$.
 We hope this work can be used as a basis for any further investigation on the property relations between similar pseudo-heterogeneous games.
@@
 A natural question pending from Chapter \ref{chapter:pricing_equilibria} is whether any of the properties described for step distribution functions for $2$-link networks can be extended for $n$-link parallel ones.
-The main issue with that potential extension is that, even for $3$-link parallel networks, the notion of a single user viewing all link costs equally is lost, as different sensitivity splits between any two pairs of links will make is so that no sensitivity value can view them all equal.
+The main issue with that potential extension is that, even for $3$-link parallel networks, the notion of a single user viewing all link costs equally is lost, as different sensitivity splits between any two pairs of links will make it so that no sensitivity value can view their cost all as equal.
 
 A different approach is therefore required to study step distribution functions for $n$-link parallel heterogeneous networks, with possible directions being investigating the different sensitivity splits among the links, running simulations, or even focusing on the algorithmic aspect of the game, where complexity results regarding the calculation or simply decision of a Nash Equilibrium can also give us further insights into the game's properties.
-Finally, another (maybe odd) way to characterise the pricing game for some $n$-link networks, would be proving it never exists for $n \ge 3$ under some conditions, a possibility which the authors have suspected.
-The main motivation for such a suspicion, is that even for $n = 3$, with the condition of having different sensitivity splits between the two consecutive pairs of links (with regard to a toll ordering on links), the respective sub-games of those pairs will likely display a behaviour similar to $2$-link networks, thus each converging to their own toll equilibrium and never reaching one overall.
+Finally, another way to characterise the pricing game for some $n$-link networks, would be proving it never exists for $n \ge 3$ under some conditions, a possibility which the author have suspected.
+The main motivation for such a suspicion is that, even for $n = 3$, with the condition of having different sensitivity splits between the two consecutive pairs of links (with regard to a toll ordering on links), the respective sub-games of those pairs will likely display a behaviour similar to $2$-link networks, thus each converging to their own pricing equilibrium and never reaching one overall.
 
@@
 	Let $(N, \ell, \alpha)$ a heterogeneous parallel game with distribution function $\alpha$ such that $\alpha(0) = 0$ and $0$ is an accumulation point.
-	For all $t \in \R_+^{|N|}$, if $x_1(t)$ the lowest-latency link in the link ordering of $t$, then $x_1(t) > 0$.
+	For all $t \in \R_+^n$, if $x_1(t)$ the lowest-latency link in the link ordering of $t$, then $x_1(t) > 0$.
 \end{lemma}
@@
 	By the definition of an accumulation point, we get for $0$ in $\alpha$ that $\forall \delta > 0 \; \exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \delta$.
-	Therefore $\forall t \in \R_+^{|N|}$ if $\delta = \min_{i \in N \setminus \{1\}}\as^{(1, i)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(1, i)}(t)$ for all $i \in N \setminus \{1\}$, which means that the lowest-latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t) > 0$.
+	Therefore $\forall t \in \R_+^n$ if $\delta = \min_{i \in N \setminus \{1\}}\as^{(1, i)}(t)$ then $\exists \epsilon > 0: p < \epsilon \Rightarrow \alpha(p) < \as^{(1, i)}(t)$ for all $i \in N \setminus \{1\}$, which means that the lowest-latency link will always have flow some $\epsilon > 0$, and therefore $x_1(t) > 0$.
 \end{proof}
@@
 	For any link $i$ and any $t_j \in t_{-i}$ consider the respective element of $D_i$, which is $B_i(t_{-i}) - t_j$.
-	For affine latency functions, we can calculate the best response functions $B_i(t_{-i})$ for each link operator $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$ we get
+	For affine latency functions, we can calculate the best response functions $B_i(t_{-i})$ for each link operator $i$, by solving first order conditions on $\Pi_i(t_i, t_{-i})$ for $t_i$.
 	\begin{equation}
@@
 
-which is in turn non-increasing with regard to $t_{-i}$ (\ref{lemma:tolls_diff}).
 Therefore, as $t_{-i}$ increases, the best response gets decreasing difference with $t_{-i}$, thus taking more flow in $x_i$.
@@
 	\label{lemma:a_fixed_t_i0}
-	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_2)$ two pseudo-heterogeneous pricing games with same latency functions $\ell$ and distribution functions $\alpha(p) = c_1$ and $\alpha^{(2)}(p) = c_2 > c_1 > 0$ respectively.
+	Let $\Gm_1 = ([2], \ell, c_1)$ and $\Gm_2 = ([2], \ell, c_2)$ two pseudo-heterogeneous pricing games with same latency functions $\ell$ and distribution functions $\alpha^{(1)}(p) = c_1$ and $\alpha^{(2)}(p) = c_2 > c_1 > 0$ respectively.
 	Also let $t_{-i_0}^{(1)}, t_{-i_0}^{(2)}$ the respective tolls for which $B_i^{(1)}(t_{-i_0}^{(1)}) = t_{-i_0}^{(1)}$ and $B_i^{(1)}(t_{-i_0}^{(2)}) = t_{-i_0}^{(2)}$.
@@
 		\item Consider the function $\Pi_i(t_{-i}) = \max_{t_i > 0}\Pi_i^{(1)}(t_i, t_{-i}) - \max_{t_i > 0}\Pi_i^{(2)}(t_i, t_{-i})$.
-		Then for $t_{-i} = t_{-i_0}^{(2)}$, in $\Gm_2$ by definition, the best response for link operator $i$ is to play the same toll as in the other link, therefore they get max profit at $x_i^{(2)}(0) t_{-i_0}^{(2)}$.
+		Then for $t_{-i} = t_{-i_0}^{(2)}$, the best response for link operator $i$ in $\Gm_2$, by definition, is to play the same toll as in the other link, therefore they get max profit at $x_i^{(2)}(0) t_{-i_0}^{(2)}$.
 		In $\Gm_1$ now, since $t_{-i_0}^{(2)} < t_{-i_0}^{(1)}$, Lemma \ref{lemma:tolls_diff} gives us
 		\[
-			B_i^{(1)}(t_{-i_0}^{(2)}) - t_{-i_0}^{(2)} \ge B_i^{(1)}(t_{-i_0}^{(1)}) - t_{-i_0}^{(1)} \Rightarrow B_i^{(1)}(t_{-i_0}^{(2)}) > t_{-i_0}^{(2)}
+			B_i^{(1)}(t_{-i_0}^{(2)}) - t_{-i_0}^{(2)} > B_i^{(1)}(t_{-i_0}^{(1)}) - t_{-i_0}^{(1)} \Rightarrow B_i^{(1)}(t_{-i_0}^{(2)}) > t_{-i_0}^{(2)}
 		\]
@@
 For step distribution functions, this set can be the domains of each of its finitely different values $\alpha_1 < \ldots < \alpha_m$.
-As such, $\forall k \in [m]$ we denote as $A_k$ the closed set of all players $p$ in $[0, 1]$ for whom $\alpha(p) = \alpha_k$.
-Obviously $\cup_{k=1}^m A_k = [0, 1]$ and from the assumption that $\alpha$ is non-decreasing we also get $A_k$ convex $\forall k \in [m]$.
+As such, $\forall k \in [m]$ we denote as $P_k$ the closed set of all players $p$ in $[0, 1]$ for whom $\alpha(p) = \alpha_k$.
+Obviously $\cup_{k=1}^m P_k = [0, 1]$ and from the assumption that $\alpha$ is non-decreasing we also get $P_k$ convex $\forall k \in [m]$.
 When looking at the flow (and consequently profit) of a specific link $i$, however, the split behaviour of the distribution function makes it possible for different flows having the same money sensitivity split.
@@
 \begin{definition}
-	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function and $(A_k)_{k \in [m]}$ the partition of $[0, 1]$ that is defined by the domain of $\alpha$.
-	Then for link operator $i$ the definition of $\Pi_i$ is extended for an interval $A_k$ as
+	Let $\Gm_1 = ([2], \ell, \alpha)$ a heterogeneous game where $\alpha$ is a step function and $(P_k)_{k \in [m]}$ the partition of $[0, 1]$ that is defined by the domain of $\alpha$.
+	Then for link operator $i$ the definition of $\Pi_i$ is extended for an interval $P_k$ as
 	\[
@@
 For $t_1 - t_2 \ge 2$, the latency difference is fixed at $\ell_2(1) - \ell_1(0) = 2$, while for $t_2 - t_1 \ge 1$ it's fixed at $\ell_1(1) - \ell_2(0) = 1$.
-So as $|t_1 - t_2| \rightarrow 0$ in each case $\as$ becomes respectively
+So as $|t_1 - t_2| \rightarrow +\infty$ in each case, $\as$ becomes respectively
 \[
@@
 Notice that the condition $\alpha(p) > 0$ when $p > 0$ holds for this example, however in this case $0$ is an accumulation point for $\alpha$.
-Lemma \ref{lemma:split_basic}$(iii)$, combined with the fact that $\alpha$ is continuous, gives us that $\as(t) = \alpha(x_i(t))$ for $x_i$ is the lower split flow.
+Lemma \ref{lemma:split_basic}$(iii)$, combined with the fact that $\alpha$ is continuous, gives us that $\as(t) = \alpha(x_i(t))$ for $x_i$ the lower split flow.
 
@@
 First we calculate the toll difference bounds we discussed in Chapter \ref{chapter:preliminaries}.
-If all flow is in link $1$ then $t_2 - t_1 = \frac{\ell_1(1) - \ell_2(0)}{\alpha(0)} = 1$, while if all flow is in link $2$ then $t_1 - t_2 = \frac{\ell_2(1) - \ell_1(0)}{\alpha(0)} = 2$ therefore
+If all flow is in link $1$ then $t_2 - t_1 = \frac{\ell_1(1) - \ell_2(0)}{\alpha(0)} = 1$, while if all flow is in link $2$ then $t_1 - t_2 = \frac{\ell_2(1) - \ell_1(0)}{\alpha(0)} = 2$, therefore
 \[t_2 - t_1 \le 1 \qquad t_1 - t_2 \le 2\]
@@
 
-\subparagraph{Gathering all the above} we see that link operator $1$, when searching for the best response toll, will compare all profits that tolls in each case provide, so we calculate them.
+\subparagraph{Gathering all the above} we see that link operator $1$, when searching for the best response toll, will compare all profits that tolls provide in each case, so we calculate them.
 \[
@@
 if $t_1 < 1/10$ then only $t_2$ such that $t_1 - t_2 < 1/10$ can be picked).
-Finally we get
+Finally, we get
 
@@
 			\frac{t_1 + 1}2, & t_1 \le \frac15 \\
-			\frac{5 t_1 + 1}{10}, & \frac15 < t_1 < frac25 \\
+			\frac{5 t_1 + 1}{10}, & \frac15 < t_1 < \frac25 \\
 			t_1 - \frac1{10}, & \frac25 \le t_1 \le \frac{10 + 2 \sqrt{15}}5 \\
@@
 
-With the above functions, we can show by simulating best response sequences in Python, that there is no Nash Equilibrium for the pricing game in $\Gm$.
+With the above functions, we can show, by simulating best response sequences in Python, that there is no Nash Equilibrium for the pricing game in $\Gm$.
 

### 2025-02-13 thesis/simulations.py
Thesis: Code: Adds Python simulation script for Examples 6.8 (p+1 variation) and 6.9

@@ -1,0 +1,111 @@
+import numpy as np
+
+"""This script runs some basic simulations based on pre-calculated
+    best response functions from heterogeneous parallel network games.
+    
+    For a more feature-rich implementation of those games including
+    calculating best response functions or tolled flow on basic
+    distribution functions, refer to the Parallel-Games library at:
+    https://github.com/Getekid/Parallel-Games
+    https://github.com/Getekid/Parallel-Games/blob/demo/demo.ipynb (Demo)
+"""
+
+
+def run(best_response_1, best_response_2, n_experiments=20, n_rounds=30):
+    """Runs some basic simulations based on pre-calculated best response functions.
+
+    Args:
+        best_response_1 (callable): The best response function from link operator 1.
+        best_response_2 (callable): The best response function from link operator 2.
+        n_experiments (int): The number of experiments to run.
+        n_rounds (int): The number of rounds to simulate. In each round,
+            all link operators take turns and change their toll to their best response one.
+
+    Returns:
+        (np.array): A list of the tolls played in each round.
+            If an equilibrium exists, the tolls sequences should converge to it.
+    """
+    # We only need to initialise tolls for link operator 2,
+    # as 1 will immediately update theirs with their best response.
+    tolls_init_2 = np.random.uniform(0, 10, n_experiments)
+
+    tolls = np.zeros((n_experiments, n_rounds, 2))
+    for e in range(n_experiments):
+        for r in range(n_rounds):
+            tolls[e, r, 0] = best_response_1(tolls[e, r - 1, 1] if r > 0 else tolls_init_2[e])
+            tolls[e, r, 1] = best_response_2(tolls[e, r, 0])
+
+    return tolls
+
+
+class Example68Plus1:
+    """This class contains the best response functions from the variation of Example 6.8
+        in the thesis article, when using distribution function a(p) = p + 1.
+
+    The game should have a Nash Equilibrium at ~(1.1464, 0.9268).
+    """
+
+    @staticmethod
+    def best_response_1(t2):
+        if t2 < 1.2:
+            return t2 - 3 + np.sqrt(5 * (3 - t2))
+        elif t2 <= 1.5:
+            return t2
+        elif t2 < 5:
+            return t2 + 3 - np.sqrt(2 * t2 + 6)
[…]
